### 2015-03-08 paper.tex
adding content

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage[dvips]{epsfig}
\usepackage[spanish]{babel}
%\usepackage[latin1]{inputenc}

\def\CC{{C\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}~}
\addtolength{\textfloatsep}{-0.5cm}
\addtolength{\intextsep}{-0.5cm}

%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
\title{books prediction}

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo et al.
}
\institute{Department of Architecture and Computer Technology. CITIC \\
           University of Granada (Spain) \\
~\\
           e-mail: {\tt pacv@ugr.es}}

\date{}

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

the abstract

\end{abstract}

%********************************************************************************
\section{Introduction and State of the Art}

%********************************************************************************
\section{The problem}

%********************************************************************************
\section{Methodology}

%********************************************************************************
\section{Experiments and Results}

%********************************************************************************
\section{Conclusions and Future Work}

%********************************************************************************
\section*{Acknowledgements}
This work has been supported in part by SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity), SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17 GENIL project (CEI-BIOTIC Granada).

%********************************************************************************
\bibliographystyle{plain}
\bibliography{refs}

\end{document}

### 2015-06-27 paper.tex
añadiendo contenido
añadiendo texto para la Intro y S-of-Art, aún en español, porque muchos términos no sé aún cómo traducirlos

@@
 \usepackage[spanish]{babel}
-%\usepackage[latin1]{inputenc}
+\usepackage[latin1]{inputenc}
 
@@
 %%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
-\title{books prediction}
+\title{Use of forecasting models for new book publishing}
 
@@
 
-the abstract
+% Cuando se edita un nuevo libro, es importante determinar el número de ejemplares que se van a imprimir en papel en cada edición, ya que a la editorial puede suponerle un alto coste imprimir volúmenes que finalmente no se vendan.
+% Así pues, se hace necesario disponer de herramientas automáticas, basadas en algoritmos de extracción de la información que ofrezcan estimaciones de la cantidad de copias de cierto libro que se pueden llegar a vender.
+% En ese sentido, en colaboración con la empresa PRM Consultores S.C.A.
+se ha llevado a cabo el análisis de un conjunto de datos que describen la tirada editorial en los últimos años.
+Como parte del estudio, se han aplicado diversos métodos de clasificación y predicción para determinar cuántos libros se pueden llegar a vender.
+
+Muchas empresas ven la estimación de las ventas de un nuevo producto como uno de las tareas más complicadas de llevar a cabo, ya que en muchos casos no suele haber datos históricos que sirvan de guía.
+
+Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
+
+Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose.
+Así pues, un sistema automático de predicción de ventas de libros para estimar la tirada editorial sería de gran ayuda para las empresas editoriales.
+
+En la bibliografía se proponen diferentes métodos de predicción de ventas, principalmente para la industria de la moda.
+En esos trabajos, cuando las ventas son estables, con una tendencia clara a lo largo del tiempo, los métodos clásicos son una buena opción.
+Sin embargo, en el caso de nuevos productos, tales como la publicación para su venta de un nuevo libro, los métodos clásicos no funcionan bien.
+
+En este trabajo se propone el uso de un método basado en reglas de decisión para abordar el problema de la predicción de la tirada editorial.
+Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
 
@@
 \section{Introduction and State of the Art}
+
+% A partir de datos históricos de tiradas editoriales se plantea el uso de varios modelos basados en redes neuronales artificiales para la clasificación y predicción de la tirada de nuevos títulos editoriales.
+
+% En principio, los datos de que se dispone para entrenar los modelos son: autor del libro, materia, precio, editorial, ventas netas y tirada.
+
+% Como primer objetivo se define el conjunto de datos y se estudian las entradas actuales para los modelos de predicción y las que se podrían obtener para mejorar las predicciones.
+
+% Se espera obtener modelos basados en redes neuronales capaces de realizar predicciones de la tirada global.
+
+A una empresa, lanzar un nuevo producto le supone un alto riesgo debido a la complejidad de los procesos de producción y distribución.
+En este ámbito, disponer de estimaciones de futuras ventas del nuevo producto resulta extremadamente importante \cite{ChingChin2010}.
+
+La industria editorial se basa en varios pasos y procesos productivos
+
+La publicación de un libro requiere de varios pasos
+
+Además, la distribución es importante y juega un papel importante
+
+Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes y afecten a la distribución. 
+Una de esas decisiones es el número de ejemplares a imprimir.
+
+Un sistema de predicción debe tener en cuenta varios detalles del ámbito de las editoriales.
+
+La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
+
+En el ámbito de la industria de la moda se trata d eun problema muy complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se ha abordado con diversos métodos en las últimas décadas \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
+
+Interesa imprimir un número de ejemplares suficiente pero sin pasarse, ya que los no vendidos suponen pérdidas, mientras que si se imprimieron de menos, siempre se pueden imprimir más.
+
+El uso de una herramienta de predicción es útil si se usa adecuadamente, y para ello conviene conocer el producto, las características de las ventas y la forma de distribuirlo, ya que son detalles que afectan al proceso \cite{Armstrong2001,SThomassey2014}.
+
+En la industria editorial influyen diversos factores que hacen que las ventas fluctúen. Estos factores no suelen ser controlables y en ocasiones no son conocidos.
+Algunos tienen que ver con las decisiones sobre compras, otros con el tráfico de mercancías o con la estrategia de distribución \cite{Little1998}.
+
+El impacto que tienen es difícil de estimar y no es constante en el tiempo, de ahí la dificultad de identificarlos adecuadamente y medir su influencia \cite{DeToni2000}. 
+Además, algunas pueden presentar correlaciones entre ellas. Dichas correlaciones pueden detectarse utilizando métodos de análisis de datos, como el SOM (y otros de R) \textbf{ESPECIFICAR CUÁLES}
+
+El proceso habitual de predicción de ventas se basa en el uso de algún tipo de software que generan una predicción que sirve como base u orientación, pero que finalmente refina un experto, ya que la empresa requiere un modelo interpretable y entendible.
+Generalmente las editoriales usan datos históricos y es un experto el que aplica su conocimiento y usa diversas variables externas para obtener predicciones bastante adecuadas.
+Por ejemplo, el experto puede subir o bajar la predicción de las ventas en función de algún periodo de ofertas.
+Sin embargo, los análisis son imprecisos y pueden no tener todas las variables en cuenta.
+Además, el proceso suele ser tedioso para un conjunto considerable de datos, e incluso,diferentes expertos pueden llegar a diferentes predicciones a partir de los mismos datos.
+
+Es por estas razones que la industria requiere que se adapten mejores técnicas de predicción a sus necesidades para realizar estimaciones de las ventas.
+
+El uso de herramientas de predicción puede ser beneficioso para una empresa editorial para optimizar la producción y así mejorar sus ganancias o minimizar pérdidas \cite{Zhao2001}.
+Un ejemplo es la optimización de las ventas \cite{Mattila2002}, mejorando el margen de ganancia al vender toda la tirada editorial.
+
+%---------- estado del arte
+
+En la bibliografía se pueden encontrar diversas propuestas para llevar a cabo la predicción de ventas en diferentes áreas.
+Por un lado, ciertos métodos cualitativos se basan en la experiencia de expertos, mientras que los métodos basados en el análisis de series temporales utilizan información histórica para hacer las predicciones \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
+
+El uso de métodos de predicción de series temporales es quizás la técnica más usada para la predicción de ventas.
+Entre las técnicas más conocidas destacan las técnicas estadísticas \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
+Sin embargo, la eficiencia de estas técnicas depende en gran medida del campo de aplicación y de los datos que conforman el problema.
+Concretamente, aquellas técnicas que requieren de una gran cantidad de datos no son las más apropiadas para realizar la predicción de ventas de nuevos productos \cite{ChingChin2010}.
+
+En cualquier caso, en diversos trabajos ha quedado demostrado que una reducción de los errores de predicción en las ventas da como resultado una mejora en la cadena de producción \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
+
+Por otro lado, diferentes autores han propuesto métricas para determinar la bondad de las estimaciones.
+Sin embargo, las más comunmente utilizadas por las empresas son las basadas en el análisis de los errores cometidos (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.
+
+Finalmente, existen casos en los que las predicciones se ven influenciadas por variables externas que hay que tener en cuenta, como la estacionalidad, promociones o modas \cite{Lapide1999}.
+Algunos autores proponen reducir las variaciones en los datos causadas por esas variables para mejorar la precisión de las predicciones \cite{Sheikh2003,Schrieber2005}.
+% p.ej.
+separar los datos relativos a una estación de otras para clasificar por separado.
+
+Por el tipo de problema que queremos abordar en este artículo, los métodos clásicos de predicción no son útiles, por lo que deberemos analizarlos previamente con otras herramientas.
+Además, puesto que las editoriales necesitan modelos que expliquen las predicciones ofrecidas, ciertos métodos tipo caja negra pueden no resultar adecuados a igualdad de precisión en las predicciones.
+
+%---------- final de la intro
+
+El resto del paper está organizado como sigue...
 
@@
 
+La predicción de ventas en la industria editorial es un problema muy challenging durante los últimos años.
+
+Diferentes técnicas de datamining pueden ser muy útiles cuando no hay datos históricos disponibles.
+
+%---------- trabajos futuros
+
+Puesto que hay algunas características que pueden afectar a la venta de productos de forma significativa, otra forma de mejorar las predicciones de ventas podría ser realizar un estudio en profundidad del efecto de la aplicación de descuentos y promociones.
+
 %********************************************************************************

### 2015-06-27 paper.tex
añadiendo
en la secc. Methodology

@@
 %%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
-\title{Use of forecasting models for new book publishing}
+\title{Using forecasting models for new book publishing}
 
@@
 \author {
-P.A. Castillo et al.
+P.A. Castillo, A.M. Mora, J.J. Merelo,  et al.
 }
@@
 
+Este paper aborda el problema de la predicción de la tirada editorial.
+No existe una metodología estándar para resolver el problema general de la predicción de ventas. 
+Así pues, en este estudio se han seguido los siguientes pasos:
+
+\subsection{Data collection and analysis}
+
+Las predicciones suelen basarse en datos históricos de las cuales extraer series temporales y patrones. 
+Sin embargo, en el caso de nuevos productos, como es el caso de la edición de nuevos libros, es complicado observar patrones pasados ya que no hay disponibles datos históricos de las ventas \cite{ChingChin2010}.
+
+\subsection{Selecting an appropriate forecasting method}
+
+\subsection{Applying forecasting methods to solve the problem}
+
 %********************************************************************************

### 2015-06-27 paper.tex
en la secc. Methodology

@@
 Este paper aborda el problema de la predicción de la tirada editorial.
-No existe una metodología estándar para resolver el problema general de la predicción de ventas. 
+
+Hay varias dificultades inherentes al problema de la predicción de ventas de nuevos productos: la limitación en la cantidad de datos disponibles, la aplicación de los diferentes métodos y la elección del más adecuado de ellos.
+
+Además, no existe una metodología estándar para resolver el problema general de la predicción de ventas. 
 Así pues, en este estudio se han seguido los siguientes pasos:
@@
 
+\textbf{TODO:} FALTA CONTAR DE DONDE HAN SALIDO LOS DATOS, SU ESTRUCTURA, COMO SE HAN ANALIZADO Y TRATADO PARA REDUCIR EL NUMERO DE ENTRADAS, ETC.
+
 \subsection{Selecting an appropriate forecasting method}
 
+Como se ha comentado anteriormente, existen diferentes métodos de predicción disponibles en la bibliografía, cada uno con una serie de parámetros diferente que pueden influir en los resultados.
+
+\textbf{TODO:} FALTA CONTAR AQUI LOS METODOS QUE SE HAN UTILIZADO EN ESTE TRABAJO, SUS PARAMETROS, ETC.
+
 \subsection{Applying forecasting methods to solve the problem}
+
+Una vez que se han determinado los métodos a utilizar y los parámetros de ejecución, se utilizará un conjunto de datos para obtener el modelo de predicción y posteriormente se comprobará su bondad ante datos no vistos previamente.
+
+\textbf{TODO:} FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS (RESULTADOS QUE SE COMENTARAN EN LA SIGUIENTE SECCION)
 

### 2015-07-21 paper.tex
traduciendo

@@
 
-Muchas empresas ven la estimación de las ventas de un nuevo producto como uno de las tareas más complicadas de llevar a cabo, ya que en muchos casos no suele haber datos históricos que sirvan de guía.
-
-Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
-
-Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose.
+% Muchas empresas ven la estimación de las ventas de un nuevo producto como uno de las tareas más complicadas de llevar a cabo, ya que en muchos casos no suele haber datos históricos que sirvan de guía.
+Many companies must face, as one of the most difficult tasks to accomplish, new product sales estimation, since in many cases no historical data to serve as guide is available.
+% Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
+Moreover, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
+% Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose.
 Así pues, un sistema automático de predicción de ventas de libros para estimar la tirada editorial sería de gran ayuda para las empresas editoriales.

### 2015-07-21 paper.tex
traduciendo

@@
 Así pues, un sistema automático de predicción de ventas de libros para estimar la tirada editorial sería de gran ayuda para las empresas editoriales.
-
-En la bibliografía se proponen diferentes métodos de predicción de ventas, principalmente para la industria de la moda.
+That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling.
+Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
+% En la bibliografía se proponen diferentes métodos de predicción de ventas, principalmente para la industria de la moda.
 En esos trabajos, cuando las ventas son estables, con una tendencia clara a lo largo del tiempo, los métodos clásicos son una buena opción.

### 2015-07-21 paper.tex
traduciendo

@@
 Sin embargo, en el caso de nuevos productos, tales como la publicación para su venta de un nuevo libro, los métodos clásicos no funcionan bien.
-
-En este trabajo se propone el uso de un método basado en reglas de decisión para abordar el problema de la predicción de la tirada editorial.
+In the literature, different methods of sales prediction, mainly for the fashion industry are proposed. 
+In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
+However, in the case of new products, such as a new book publishing, classical methods do not work properly.
+% En este trabajo se propone el uso de un método basado en reglas de decisión para abordar el problema de la predicción de la tirada editorial.
 Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.

### 2015-07-21 paper.tex
traduciendo

@@
 Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
-
+In this paper, a rule-based decision method is proposed to address the problem of predicting the publishing roll. 
+This method has been validated by the company that provided the data, as the obtained models provide information on the decision process and does not require human intervention, nor for the operation or for interpretation.
 \end{abstract}

### 2015-07-21 paper.tex
traduciendo

@@
 
-A una empresa, lanzar un nuevo producto le supone un alto riesgo debido a la complejidad de los procesos de producción y distribución.
+% A una empresa, lanzar un nuevo producto le supone un alto riesgo debido a la complejidad de los procesos de producción y distribución.
 En este ámbito, disponer de estimaciones de futuras ventas del nuevo producto resulta extremadamente importante \cite{ChingChin2010}.
+A company that intends launching a new product has a high risk due to the complexity of the production and distribution processes. 
+In this scope, having accurate estimates of future sales of the new product is extremely important \cite{ChingChin2010}.
 

### 2015-07-21 paper.tex
traduciendo

@@
 
-La industria editorial se basa en varios pasos y procesos productivos
-
-La publicación de un libro requiere de varios pasos
-
-Además, la distribución es importante y juega un papel importante
+% La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
+The publishing industry is based on very particular and established production processes, and publishing a book requires several steps, between whom the distribution is important and plays an important role.
 

### 2015-07-21 paper.tex
traduciendo

@@
 
-Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes y afecten a la distribución. 
-Una de esas decisiones es el número de ejemplares a imprimir.
+% Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
+The publishing process and individual decisions at each step are very important. One of those decisions is the number of copies to print.
 

### 2015-07-22 paper.tex
traduciendo

@@
 
-Un sistema de predicción debe tener en cuenta varios detalles del ámbito de las editoriales.
+% Así pues, un sistema de predicción debe tener en cuenta muchos detalles acerca del funcionamiento del proceso editorial.
+Thus, a suitable prediction system for new book publishing should take into account many details about how the editorial process works.
 
-La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
+%La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
+Implementing a good forecasting tool requires not only a good study of the state of the art in this field, but also an accurate knowledge of the operations and challenges facing the publishing industry and its supply chain.
 

### 2015-07-22 paper.tex
traduciendo

@@
 
-En el ámbito de la industria de la moda se trata d eun problema muy complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se ha abordado con diversos métodos en las últimas décadas \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
+En el ámbito de la industria de la moda se trata de un problema muy complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se ha abordado con diversos métodos en las últimas décadas \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
 

### 2015-07-22 paper.tex
traduciendo

@@
 
-%La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
+% La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
 Implementing a good forecasting tool requires not only a good study of the state of the art in this field, but also an accurate knowledge of the operations and challenges facing the publishing industry and its supply chain.
 
-En el ámbito de la industria de la moda se trata de un problema muy complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se ha abordado con diversos métodos en las últimas décadas \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
+% En el ámbito de la industria de la moda se trata de un problema muy complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se ha abordado con diversos métodos en las últimas décadas \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
+In the field of fashion industry it is very complex problem, subject to certain requirements \cite{SThomassey2014} and has been faced using various methods in recent decades \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
 
-Interesa imprimir un número de ejemplares suficiente pero sin pasarse, ya que los no vendidos suponen pérdidas, mientras que si se imprimieron de menos, siempre se pueden imprimir más.
+% Interesa imprimir un número de ejemplares suficiente pero sin pasarse, ya que los no vendidos suponen pérdidas, mientras que si se imprimieron de menos, siempre se pueden imprimir más.
+In the field of publishing industry, it is more important printing an adequate number of copies but not too much, as the unsold volumes will lead to losses, whereas if the number of printed copies was not enough, you can always print more.
 
-El uso de una herramienta de predicción es útil si se usa adecuadamente, y para ello conviene conocer el producto, las características de las ventas y la forma de distribuirlo, ya que son detalles que afectan al proceso \cite{Armstrong2001,SThomassey2014}.
+% El uso de una herramienta de predicción es útil si se usa adecuadamente, y para ello conviene conocer el producto, las características de las ventas y la forma de distribuirlo, ya que son detalles que afectan al proceso \cite{Armstrong2001,SThomassey2014}.
+Thus, using a predictive tool is very useful when used properly; in this sense, it is very important to know the product, the characteristics of sales and how to distribute it, as those details affect the process \cite{Armstrong2001,SThomassey2014}.
 

### 2015-07-22 paper.tex
traduciendo

@@
 
-En la industria editorial influyen diversos factores que hacen que las ventas fluctúen. Estos factores no suelen ser controlables y en ocasiones no son conocidos.
+% En la industria editorial influyen diversos factores que hacen que las ventas fluctúen.
+Estos factores no suelen ser controlables y en ocasiones no son conocidos.
 Algunos tienen que ver con las decisiones sobre compras, otros con el tráfico de mercancías o con la estrategia de distribución \cite{Little1998}.
+The publishing industry is influenced by various factors that make sales fluctuate. 
+These factors are usually not controllable and even, sometimes are not known.
+Some have to do with decisions on purchases, others with freight traffic, and others with the distribution strategy \cite{Little1998}.
 
-El impacto que tienen es difícil de estimar y no es constante en el tiempo, de ahí la dificultad de identificarlos adecuadamente y medir su influencia \cite{DeToni2000}. 
-Además, algunas pueden presentar correlaciones entre ellas. Dichas correlaciones pueden detectarse utilizando métodos de análisis de datos, como el SOM (y otros de R) \textbf{ESPECIFICAR CUÁLES}
+% El impacto que tienen es difícil de estimar y no es constante en el tiempo, de ahí la dificultad de identificarlos adecuadamente y medir su influencia \cite{DeToni2000}.
+Además, algunas pueden presentar correlaciones entre ellas.
+Sin embargo, dichas correlaciones pueden detectarse utilizando métodos de análisis de datos, como el SOM (y otros de R) \textbf{ESPECIFICAR CUÁLES}
 

### 2015-07-22 paper.tex
traduciendo

@@
 Sin embargo, dichas correlaciones pueden detectarse utilizando métodos de análisis de datos, como el SOM (y otros de R) \textbf{ESPECIFICAR CUÁLES}
+Their impact is difficult to estimate and it is not constant over time, hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
+In addition, some may have correlations between them. 
+However, these correlations can be detected using data analysis methods, such as SOM or R  \textbf{ESPECIFICAR CUÁLES}
 

### 2015-07-22 paper.tex
traduciendo

@@
 
-El proceso habitual de predicción de ventas se basa en el uso de algún tipo de software que generan una predicción que sirve como base u orientación, pero que finalmente refina un experto, ya que la empresa requiere un modelo interpretable y entendible.
-Generalmente las editoriales usan datos históricos y es un experto el que aplica su conocimiento y usa diversas variables externas para obtener predicciones bastante adecuadas.
+% Generalmente las editoriales usan datos históricos y es un experto el que aplica su conocimiento y usa diversas variables externas para obtener predicciones bastante adecuadas. 
+% El proceso habitual de predicción de ventas se basa en el uso de algún tipo de software que genera una predicción que sirve como base u orientación, pero que finalmente refina un experto, ya que la empresa requiere un modelo interpretable y entendible.
 Por ejemplo, el experto puede subir o bajar la predicción de las ventas en función de algún periodo de ofertas. 
 Sin embargo, los análisis son imprecisos y pueden no tener todas las variables en cuenta. 
-Además, el proceso suele ser tedioso para un conjunto considerable de datos, e incluso,diferentes expertos pueden llegar a diferentes predicciones a partir de los mismos datos.
+Además, el proceso suele ser tedioso para un conjunto considerable de datos, e incluso, diferentes expertos pueden llegar a diferentes predicciones a partir de los mismos datos.
+
+Publishers usually use historical data and an expert analyzes that data and apply his knowledge using external variables to obtain quite appropriate predictions.
+However, in recent years the sales prediction task is based on the use of some software that generates a prediction. 
+This is used as the basis or guidance that an expert can tune, as the company might require an interpretable and understandable model.
 

### 2015-07-22 paper.tex
traduciendo

@@
 % Generalmente las editoriales usan datos históricos y es un experto el que aplica su conocimiento y usa diversas variables externas para obtener predicciones bastante adecuadas.
-% El proceso habitual de predicción de ventas se basa en el uso de algún tipo de software que genera una predicción que sirve como base u orientación, pero que finalmente refina un experto, ya que la empresa requiere un modelo interpretable y entendible.
+El proceso habitual de predicción de ventas se basa en el uso de algún tipo de software que genera una predicción que sirve como base u orientación, pero que finalmente refina un experto, ya que la empresa requiere un modelo interpretable y entendible.
 Por ejemplo, el experto puede subir o bajar la predicción de las ventas en función de algún periodo de ofertas.
@@
 Además, el proceso suele ser tedioso para un conjunto considerable de datos, e incluso, diferentes expertos pueden llegar a diferentes predicciones a partir de los mismos datos.
-
 Publishers usually use historical data and an expert analyzes that data and apply his knowledge using external variables to obtain quite appropriate predictions.
@@
 This is used as the basis or guidance that an expert can tune, as the company might require an interpretable and understandable model.
+For example, the expert might increase or decrease the sales prediction based on some period of offers.
+However, the obtained analysis can be imprecise and may not take all the variables into account.
+In addition, the process is often tedious, especially when the amount of data is large, and even, different experts can reach different predictions from the same data set.
 

### 2015-07-22 paper.tex
traduciendo

@@
 
-Es por estas razones que la industria requiere que se adapten mejores técnicas de predicción a sus necesidades para realizar estimaciones de las ventas.
+% Es por estas razones que la industria requiere que se adapten mejores técnicas de predicción a sus necesidades para realizar estimaciones de las ventas.
+For these reasons, the industry requires the best suited forecasting techniques to be adopted so that, estimating sales task is carried out properly.
 
-El uso de herramientas de predicción puede ser beneficioso para una empresa editorial para optimizar la producción y así mejorar sus ganancias o minimizar pérdidas \cite{Zhao2001}.
+% El uso de herramientas de predicción puede ser beneficioso para una empresa editorial para optimizar la producción y así mejorar sus ganancias o minimizar pérdidas \cite{Zhao2001}.
 Un ejemplo es la optimización de las ventas \cite{Mattila2002}, mejorando el margen de ganancia al vender toda la tirada editorial.

### 2015-07-22 paper.tex
traduciendo

@@
 % La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
-The publishing industry is based on very particular and established production processes, and publishing a book requires several steps, between whom the distribution is important and plays an important role.
-
+In this sense, the publishing industry is based on very particular and established production processes, and publishing a book requires several steps, between whom the distribution is important and plays an important role.
 % Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
@@
 Un ejemplo es la optimización de las ventas \cite{Mattila2002}, mejorando el margen de ganancia al vender toda la tirada editorial.
+Using predictive tools can benefit a publishing company to optimize production and improve their profits or minimize losses \cite{Zhao2001}. 
+An example is the optimization of sales \cite{Mattila2002} by improving profit margins by selling the whole publishing roll.
 
+\bigskip
 %---------- estado del arte
@@
 
+\bigskip
 %---------- final de la intro
 
-El resto del paper está organizado como sigue...
+The rest of this paper is structured as follows:
+%Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography to BLA BLA BLA.
+Section \ref{sec:methodology} briefly describes the EA algorithm, and analyzes the parameters we propose to evaluate.
+This section also presents the experimental setup and the methodology considered in the study. 
+Section \ref{sec:experiments} details the statistical study based on ANOVA. 
+Obtained results are analyzed in order to establish the most suitable values.
+Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.
 
@@
 \section{The problem}
+\label{sec:problem}
 
@@
 \section{Methodology}
+\label{sec:methodology}
 
@@
 \section{Experiments and Results}
+\label{sec:experiments}
+
+aquí hay que contar los experimentos realizados y presentar los resultados obtenidos
 
@@
 \section{Conclusions and Future Work}
+\label{sec:conclusionsAndFutureWork}
 

### 2015-07-22 paper.tex
traduciendo

@@
 %Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography to BLA BLA BLA.
-Section \ref{sec:methodology} briefly describes the EA algorithm, and analyzes the parameters we propose to evaluate.
-This section also presents the experimental setup and the methodology considered in the study. 
-Section \ref{sec:experiments} details the statistical study based on ANOVA. 
-Obtained results are analyzed in order to establish the most suitable values.
+Section \ref{sec:problem} describes the new book publishing problem, followed by Section \ref{sec:methodology} where the experimental setup and the methodology considered in the study is presented. 
+Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
 Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.
@@
 
+Este paper aborda el problema de la predicción de la tirada editorial.
+
+Describir en detalle el problema de la tirada editorial. 
+Comentar que se ha colaborado con la empresa Trevenque, y qué datos nos ha pasado.
+Indicar qué variables externas afectarán a las predicciones, etc.
+
 %********************************************************************************
@@
 \label{sec:methodology}
-
-Este paper aborda el problema de la predicción de la tirada editorial.
 
@@
 
+%-------------------------------------------------
 \subsection{Data collection and analysis}
@@
 
+%-------------------------------------------------
 \subsection{Selecting an appropriate forecasting method}
@@
 
+%-------------------------------------------------
 \subsection{Applying forecasting methods to solve the problem}

### 2015-07-23 paper.tex
traduciendo

@@
 
-En la bibliografía se pueden encontrar diversas propuestas para llevar a cabo la predicción de ventas en diferentes áreas.
+% En la bibliografía se pueden encontrar diversas propuestas para llevar a cabo la predicción de ventas en diferentes áreas.
 Por un lado, ciertos métodos cualitativos se basan en la experiencia de expertos, mientras que los métodos basados en el análisis de series temporales utilizan información histórica para hacer las predicciones \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
+In the literature several proposals to perform the prediction of sales in different areas can be found. 
+On the one hand, several qualitative methods are based on an expert experience, while time series prediction methods are based on using historical data to make predictions \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
 

### 2015-07-23 paper.tex
traduciendo

@@
 
-El uso de métodos de predicción de series temporales es quizás la técnica más usada para la predicción de ventas.
+%El uso de métodos de predicción de series temporales es quizás la técnica más usada para la predicción de ventas.
 Entre las técnicas más conocidas destacan las técnicas estadísticas \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}.
-Sin embargo, la eficiencia de estas técnicas depende en gran medida del campo de aplicación y de los datos que conforman el problema.
+Using time series prediction methods is perhaps the most used technique to tackle the sales forecasting task.
+In this sense, among the most popular techniques include statistical techniques \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
+% Sin embargo, la eficiencia de estas técnicas depende en gran medida del campo de aplicación y de los datos que conforman el problema.
 Concretamente, aquellas técnicas que requieren de una gran cantidad de datos no son las más apropiadas para realizar la predicción de ventas de nuevos productos \cite{ChingChin2010}.

### 2015-07-23 paper.tex
traduciendo

@@
 Concretamente, aquellas técnicas que requieren de una gran cantidad de datos no son las más apropiadas para realizar la predicción de ventas de nuevos productos \cite{ChingChin2010}.
+However, the efficiency of these techniques depends largely on the field of application and the problem data. 
+Specifically, techniques that require a large amount of data for predicting sales of new products are not the most suitable for this task \cite{ChingChin2010}.
 
-En cualquier caso, en diversos trabajos ha quedado demostrado que una reducción de los errores de predicción en las ventas da como resultado una mejora en la cadena de producción \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
+% En cualquier caso, en diversos trabajos ha quedado demostrado que una reducción de los errores de predicción en las ventas da como resultado una mejora en la cadena de producción \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
+Anyway, several studies have demonstrated that improving sale predictions (a reduction of forecasting errors) results in an improvement in the production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
 

### 2015-07-23 paper.tex
traduciendo

@@
 
-Por otro lado, diferentes autores han propuesto métricas para determinar la bondad de las estimaciones.
+% Por otro lado, diferentes autores han propuesto métricas para determinar la bondad de las estimaciones.
 Sin embargo, las más comunmente utilizadas por las empresas son las basadas en el análisis de los errores cometidos (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.
+On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
+However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.
 

### 2015-07-23 paper.tex
traduciendo

@@
 
-Finalmente, existen casos en los que las predicciones se ven influenciadas por variables externas que hay que tener en cuenta, como la estacionalidad, promociones o modas \cite{Lapide1999}.
+% Finalmente, existen casos en los que las predicciones se ven influenciadas por variables externas que hay que tener en cuenta, como la estacionalidad, promociones o modas \cite{Lapide1999}.
 Algunos autores proponen reducir las variaciones en los datos causadas por esas variables para mejorar la precisión de las predicciones \cite{Sheikh2003,Schrieber2005}.
@@
 separar los datos relativos a una estación de otras para clasificar por separado.
+Finally, in many cases the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions \cite{Lapide1999}.
+In this sense, some authors propose reducing variations in the data caused by such variables to improve the accuracy of predictions
+ \cite{Sheikh2003,Schrieber2005}.
 

### 2015-07-23 paper.tex
traduciendo

@@
 
-Por el tipo de problema que queremos abordar en este artículo, los métodos clásicos de predicción no son útiles, por lo que deberemos analizarlos previamente con otras herramientas.
+% Por el tipo de problema que queremos abordar en este artículo, los métodos clásicos de predicción no son útiles, por lo que deberemos analizarlos previamente con otras herramientas.
 Además, puesto que las editoriales necesitan modelos que expliquen las predicciones ofrecidas, ciertos métodos tipo caja negra pueden no resultar adecuados a igualdad de precisión en las predicciones.
+Taking into account the kind of problem we address in this paper, the classical forecasting methods are not useful. 
+Thus, we must analyze raw data using other tools, prior to apply forecasting techniques.
+In addition, since publishers need models to explain obtained predictions, black box forecasting methods may not be suitable for this problem.
 

### 2015-08-06 paper.tex
añado la descripción inicial del problema (conj. variables ofrecido por Trevenque)

@@
 In addition, some may have correlations between them. 
-However, these correlations can be detected using data analysis methods, such as SOM or R  \textbf{ESPECIFICAR CUÁLES}
+However, these correlations can be detected using data analysis methods, such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.
 
@@
 
-Este paper aborda el problema de la predicción de la tirada editorial.
+This paper faces the new book publishing problem using different prediction methods.
 
-Describir en detalle el problema de la tirada editorial. 
-Comentar que se ha colaborado con la empresa Trevenque, y qué datos nos ha pasado.
-Indicar qué variables externas afectarán a las predicciones, etc.
+\textbf{Describir en detalle el problema de la tirada editorial.}
+
+A lo largo de esta investigación se colaboró con la empresa Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}, una compañía que ofrece sistemas de gestión y servicios para librerías, editoriales y distribuidoras.
+
+La empresa Trevenque, cuyo experto asesoró esta investigación, facilitó un conjunto de datos inicial consistente en 3159 libros. 
+Para cada libro, se incluye información acerca del precio, lugares donde se han puesto a la venta, materia, editorial, ventas, devoluciones, entre otros datos.
+Table \ref{tabla:paramsOrig} shows the original set of parameters describing each book.
+
+\begin{table}[!h]
+\caption{Parameters describing a book, as provided by the company Trevenque.}
+\label{tabla:paramsOrig}
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline
+
+\begin{minipage}{2.3in} \begin{verbatim}
+referencia
+autor
+pvp
+materia1
+materia2
+materia3
+editorial
+coleccion
+encuadernacion
+tirada
+venta_total
+venta_grandes_superficies
+venta_delegados
+venta_resto
+venta1anio_total
+venta1anio_grandes_superficies
+venta1anio_delegados
+venta1anio_resto
+colocado_total
+colocado_grandes_superficies
+colocado_delegados
+colocado_resto
+colocado1anio_total
+colocado1anio_grandes_superficies
+colocado1anio_delegados
+\end{verbatim} \end{minipage}     &
+
+\begin{minipage}{2.3in} \begin{verbatim}
+colocado1anio_resto
+reimpresiones
+numero_reimpresiones
+devolucion_total
+devolucion_grandes_superficies
+devolucion_delegados
+devolucion_resto
+devolucion1anio_total
+devolucion1anio_grandes_superficies
+devolucion1anio_delegados
+devolucion1anio_resto
+obsequios
+ejemplares_distribuidos_en_novedad
+puntos_vta_total
+puntos_vta_grandes_superficies
+puntos_vta_delegados
+puntos_vta_resto
+puntos_vta1anio_total
+puntos_vta1anio_grandes_superficies
+puntos_vta1anio_delegados
+puntos_vta1anio_resto
+semanas_venta
+entorno_venta_positivo
+entorno_venta_medio
+entorno_venta_negativo
+\end{verbatim} \end{minipage}    \\
+
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+En el problema de la predicción de ventas de nuevos libros afectan diversas variables propias del libro en cuestión, como por ejemplo el autor, el precio, la materia o la editorial.
+
+Sin embargo, existen otras variables externas que también afectan a las ventas de un nuevo libro.
+Se trata de cuestiones como la estacionalidad, modas o promociones.
+Estas otras variables no medibles y que los métodos de predicción clásicos no pueden procesar y que un experto debe tener en cuenta modificando la predicción ofrecida por el método automático.
 

### 2015-08-07 paper.tex
descripción del proceso, indicando qué archivos vamos a usar
añadidas las tablas de variables que describen los libros

@@
 Para cada libro, se incluye información acerca del precio, lugares donde se han puesto a la venta, materia, editorial, ventas, devoluciones, entre otros datos.
-Table \ref{tabla:paramsOrig} shows the original set of parameters describing each book.
+Table \ref{tabla:paramsOrig50} shows the original set of parameters describing each book.
 
@@
 \caption{Parameters describing a book, as provided by the company Trevenque.}
-\label{tabla:paramsOrig}
+\label{tabla:paramsOrig50}
 \begin{center}
@@
 Además, no existe una metodología estándar para resolver el problema general de la predicción de ventas. 
-Así pues, en este estudio se han seguido los siguientes pasos:
+Habitualmente es necesario un análisis previo de los datos para eliminar las variables que describen el producto y que no aportan información útil para realizar el proceso de predicción.
+
+Thus, in this study there are three main stages: 
+\begin{itemize}
+  \item  First, after the editorial company has provided the raw data, taken directly from its database, a selection variables process is carried out.
+In this stage, a SOM cluster method is used to analyze data, to eliminate unrelated variables and to select the best variables to be considered in the forecasted model.
+
+  \item  Then, several forecasting methods has to be tested. In this stage different forecasting methods are used to obtain sales forecasts from the data provided.
+
+  \item  Finally, in some cases, it is necessary a third stage where experienced managers adjust subjectively the results obtained using the forecasting methods.
+They might manually adjust the forecasting results taking into account their knowledge in industry experience and their perception about trends.
+
+\end{itemize}
 
@@
 
-\textbf{TODO:} FALTA CONTAR DE DONDE HAN SALIDO LOS DATOS, SU ESTRUCTURA, COMO SE HAN ANALIZADO Y TRATADO PARA REDUCIR EL NUMERO DE ENTRADAS, ETC.
+\textbf{TODO:} FALTA CONTAR COMO SE HAN ANALIZADO Y TRATADO LOS DATOS PARA REDUCIR EL NUMERO DE ENTRADAS, ETC.
+
+Table \ref{tabla:params43} shows the set of variables describing a book after analizyng the original dataset using the SOM to select the best variables to be considered.
+
+\begin{table}[!h]
+\caption{Variables describing a book, after analizyng the original dataset provided by the company Trevenque using the SOM to select the best variables to be considered.}
+\label{tabla:params43}
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline
+
+\begin{minipage}{2.3in} \begin{verbatim}
+puntos_vta1anio_grandes_superficies
+venta1anio_resto
+entorno_venta_negativo
+colocado1anio_grandes_superficies
+devolucion_total
+reimpresiones
+venta1anio_grandes_superficies
+puntos_vta1anio_total
+ejemplares_distribuidos_en_novedad
+tirada
+numero_reimpresiones
+devolucion_grandes_superficies
+puntos_vta1anio_resto
+venta_resto
+puntos_vta_delegados
+devolucion_resto
+puntos_vta1anio_delegados
+entorno_venta_positivo
+colocado1anio_resto
+puntos_vta_resto
+devolucion1anio_total
+devolucion_delegados
+\end{verbatim} \end{minipage}     &
+
+\begin{minipage}{2.3in} \begin{verbatim}
+venta_grandes_superficies
+colocado1anio_total
+puntos_vta_total
+colocado_grandes_superficies
+colocado1anio_delegados
+puntos_vta_grandes_superficies
+venta1anio_total
+entorno_venta_medio
+semanas_venta
+colocado_delegados
+autor
+venta1anio_delegados
+obsequios
+devolucion1anio_grandes_superficies
+venta_delegados
+colocado_resto
+devolucion1anio_delegados
+colocado_total
+devolucion1anio_resto
+pvp
+venta_total (output)
+\end{verbatim} \end{minipage}    \\
+
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Table \ref{tabla:params13} shows the set of variables describing a book after a second analisys carried out along the company experienced manager to select the best variables to be considered.
+
+\begin{table}[!h]
+\caption{Variables describing a book, after a second analisys carried out along the company experienced manager to select the best variables to be considered to solve the sales forecasting problem.}
+\label{tabla:params13}
+\begin{center}
+\begin{tabular}{|c|}
+\hline
+
+\begin{minipage}{2.3in} \begin{verbatim}
+devolucion_total
+reimpresiones
+puntos_vta1anio_total
+ejemplares_distribuidos_en_novedad
+numero_reimpresiones
+devolucion1anio_total
+colocado1anio_total
+puntos_vta_total
+semanas_venta
+colocado_total
+pvp
+tirada
+venta_total (output)
+\end{verbatim} \end{minipage}     \\
+
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Table \ref{tabla:params7} shows the final set of variables describing a book, taking into account the company experienced manager knowledge.
+
+\begin{table}[!h]
+\caption{Final set of variables describing a book, taking into account the company experienced manager knowledge, to be considered to solve the sales forecasting problem.}
+\label{tabla:params7}
+\begin{center}
+\begin{tabular}{|c|}
+\hline
+
+\begin{minipage}{2.3in} \begin{verbatim}
+ejemplares_distribuidos_en_novedad
+puntos_vta_total
+colocado_total
+pvp
+materia
+editorial
+venta_total (output)
+\end{verbatim} \end{minipage}     \\
+
+\hline
+\end{tabular}
+\end{center}
+\end{table}
 
@@
 
+ %  Hemos usado:
+ % weka.classifiers.trees.M5P
+ % weka.classifiers.functions.LinearRegression
+ % weka.classifiers.functions.SMOreg
+ % weka.classifiers.lazy.IBk
+
 %-------------------------------------------------
@@
 \textbf{TODO:} FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS (RESULTADOS QUE SE COMENTARAN EN LA SIGUIENTE SECCION)
+
+  %  
+  %  El proceso que seguimos, resumido para el paper, es:
+  %  
+  %  [43 entradas] en 2013-01 vamos a tomar 
+  %  	pb_noneg.csv para obtener pb_ventas.csv (es el pb_ventas.arff)
+  %  
+  %  [13 entradas] en 2013-02-08 vamos a tomar 
+  %  	controlado_reducido.csv.arff (197 líneas)
+  %  	pbenero.csv.arff (5656 líneas)
+  %  
+  %  [7 entradas; materia editorial] en 2013-02-25 vamos a tomar
+  %  	pbRAWtrn.arff
+  %  	pbRAWtst.arff
+  %
 

### 2015-08-07 paper.tex
añadidas los nombres de métodos de predicción usados
añadidas los nombres de métodos de predicción usados (también el MLP)
quito el paquete BABEL, para que no ponga RESUMEN y REFERENCIAS :)
añado para traducir los nombres de variables que describen los libros
añadiendo diversas explicaciones + las dos imágenes-SOM (por hacer)

@@
 \usepackage[dvips]{epsfig}
-\usepackage[spanish]{babel}
+%\usepackage[spanish]{babel}
 \usepackage[latin1]{inputenc}
@@
 
-This paper faces the new book publishing problem using different prediction methods.
+Sales forecasting in editorial industry is a very complex problem.
+The main issue of this paper is to compute forecasting of the sales for new unpublished-books, for which no historical data is available.
+Thus, this paper faces the new book publishing problem using different prediction methods and using as inputs the historical sales data related to other yet published books, and some descriptive variables relative to the new unpublished-book.
 
-\textbf{Describir en detalle el problema de la tirada editorial.}
+En el caso de libros ya publicados, se dispone de datos históricos que ayudan a la generación de modelos predictivos. 
+Sin embargo, en el caso de nuevos libros, sólo ciertos datos descriptivos están disponibles.
+
+An additional issue is the dificulty to compare our model with classical forecasting methods, such as time series prediction methods, since books do not have specific sales time series.
 
@@
 La empresa Trevenque, cuyo experto asesoró esta investigación, facilitó un conjunto de datos inicial consistente en 3159 libros. 
-Para cada libro, se incluye información acerca del precio, lugares donde se han puesto a la venta, materia, editorial, ventas, devoluciones, entre otros datos.
+En este conjunto, para cada libro se incluye información descriptiva del libro, como son el precio, lugares donde se han puesto a la venta, materia, editorial, ventas, devoluciones, entre otros datos.
 Table \ref{tabla:paramsOrig50} shows the original set of parameters describing each book.
@@
 
+Finally, in order to compute the forecasting errors of the different methods, the following standard criteria have been selected: Mean absolute error, Root mean squared error, Relative absolute error and Root relative squared error.
+
 %-------------------------------------------------
@@
 
-\textbf{TODO:} FALTA CONTAR COMO SE HAN ANALIZADO Y TRATADO LOS DATOS PARA REDUCIR EL NUMERO DE ENTRADAS, ETC.
+Además, de todas las variables descriptivas de un nuevo libro, algunas influirán en las predicciones aportando información, mientras que otras pueden resultar superfluas e incluso redundantes.
 
-Table \ref{tabla:params43} shows the set of variables describing a book after analizyng the original dataset using the SOM to select the best variables to be considered.
+Así pues, a partir del conjunto inicial de variables, se aplicó el SOM \cite{kohonen1998} con el objetivo de reducir la dimensionalidad de los datos de entrada y elegir un conjunto de variables adecuado.
+
+\textbf{FALTA EXPLICAR EN UN PAR DE PÁRRAFOS QUÉ ES EL SOM DE KOHONEN.} 
+This method is usually applied to analyze data as similar items tend to be mapped close together, while those items dissimilar, are mapped apart.
+Also, the SOM graph represents and highlight very clearly those regions (clusters) with high training sample concentration and fewer where the samples are scarce.
+
+En un primer paso, el experto analizó las 50 variables de entrada que describen cada libro para eliminar algunas que estimó como suplerfuas.
+Table \ref{tabla:params43} shows the set of variables describing a book (43 total inputs) that the expert manager determined as non-superfluous or non-redundant.
 
 \begin{table}[!h]
-\caption{Variables describing a book, after analizyng the original dataset provided by the company Trevenque using the SOM to select the best variables to be considered.}
+\caption{Variables describing a book (43 total inputs), after the expert manager analized the original dataset provided by the company Trevenque to remove some inputs.}
 \label{tabla:params43}
@@
 
-Table \ref{tabla:params13} shows the set of variables describing a book after a second analisys carried out along the company experienced manager to select the best variables to be considered.
+Then, after analizyng the original dataset using the SOM to select the best variables to be considered, and taking into account the knowledge of the company experienced manager, 13 inputs were considered.
+Figure \ref{fig:som43} shows the initial analisys of dataset using the total of 43 descriptive inputs per book.
+Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.
+
+\begin{figure}[!h] 
+\begin{center}
+\includegraphics{som43.eps} \\
+\caption{\small{Análisis de los datos iniciales, usando 43 variables descriptivas por libro, utilizando el SOM.}}
+\label{fig:som43}
+\end{center}
+\end{figure}
 
 \begin{table}[!h]
-\caption{Variables describing a book, after a second analisys carried out along the company experienced manager to select the best variables to be considered to solve the sales forecasting problem.}
+\caption{Variables describing a book (13 total inputs), after the second analisys carried out using the SOM along with the company experienced manager to select the best variables to be considered to solve the sales forecasting problem.}
 \label{tabla:params13}
@@
 
+Finally, after analizyng the dataset with 13 descriptive inputs per book, and paying attention to the company experienced manager's recommendations, 7 inputs were considered; specifically, variables \emph{editorial} and \emph{materia} were included, while \emph{devolucion\_total, reimpresiones, puntos\_vta1anio\_total, numero\_reimpresiones, devolucion1anio\_total, colocado1anio\_total, semanas\_venta, tirada} were discarded.
+Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on the total of 13 descriptive inputs per book.
+This, along with the expert manager knowledge determined the final 7 inputs to be considered.
 Table \ref{tabla:params7} shows the final set of variables describing a book, taking into account the company experienced manager knowledge.
+
+\begin{figure}[!h] 
+\begin{center}
+\includegraphics{som13.eps} \\
+\caption{\small{Análisis de los datos iniciales, usando 13 variables descriptivas por libro, utilizando el SOM.}}
+\label{fig:som13}
+\end{center}
+\end{figure}
 
@@
 
-\textbf{TODO:} FALTA CONTAR AQUI LOS METODOS QUE SE HAN UTILIZADO EN ESTE TRABAJO, SUS PARAMETROS, ETC.
+Sin embargo, dado que en el caso de nuevos libros sólo ciertos datos descriptivos están disponibles (frente a datos históricos de ventas de libros ya publicados), no todos los métodos predictivos se pueden usar en este problema concreto.
 
- %  Hemos usado:
+Así pues, en esta investigación se propusieron para su evaluación los siguientes métodos:
+
+\begin{itemize}
+
  % weka.classifiers.trees.M5P
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
+ \item
+
  % weka.classifiers.functions.LinearRegression
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
+ \item
+
  % weka.classifiers.functions.SMOreg
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
+ \item
+
  % weka.classifiers.lazy.IBk 
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
+ \item
+
+ % weka.classifiers.functions.MultilayerPerceptron
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
+ \item
+
+\end{itemize}
 
@@
 
-Diferentes técnicas de datamining pueden ser muy útiles cuando no hay datos históricos disponibles.
+Para resolver este problmea, diferentes técnicas de datamining pueden ser muy útiles, al no haber datos históricos disponibles de las ventas.
+
+La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
+En este sentido, los árboles de decisión resultaron ser un modelo muy adecuado debido a la facilidad para explicar cómo se obtiene dicha predicción a partir de las variables descriptivas del nuevo libro.
+Esto, frente a los modelos tipo black-box como las ANN fue determinante desde el punto de vista de las necesidades de los expertos y la empresa.
+
+This research provides a new direction in the sales forecasting area using different soft-computing techniques.
+Moreover, proposed method could be implemented, not only in the editorial industry, but also in other domains where the specificity of products is similar, and might be of interest to other academic researches and industrial practitioners.
 
@@
 
-Puesto que hay algunas características que pueden afectar a la venta de productos de forma significativa, otra forma de mejorar las predicciones de ventas podría ser realizar un estudio en profundidad del efecto de la aplicación de descuentos y promociones.
+Como trabajos futuros sería interesante comparar las predicciones de los modelos obtenidos con otros basados en métodos de soft-computing, como genetic programming o fuzzy logic.
+
+Por otro lado, puesto que hay algunas características que pueden afectar a la venta de productos de forma significativa, otra forma de mejorar las predicciones de ventas podría ser realizar un estudio en profundidad del efecto de la aplicación de descuentos y promociones.
 

### 2015-08-08 paper.tex
añadiendo los 5 métodos de predicción utilizados
añadiendo contenido

@@
 Sales forecasting in editorial industry is a very complex problem.
+There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use.
+
 The main issue of this paper is to compute forecasting of the sales for new unpublished-books, for which no historical data is available.
@@
 En el caso de libros ya publicados, se dispone de datos históricos que ayudan a la generación de modelos predictivos. 
-Sin embargo, en el caso de nuevos libros, sólo ciertos datos descriptivos están disponibles.
+Sin embargo, en el caso de nuevos libros no hay datos históricos que ayuden a definir patrones, y sólo ciertos datos descriptivos están disponibles.
 
@@
 Estas otras variables no medibles y que los métodos de predicción clásicos no pueden procesar y que un experto debe tener en cuenta modificando la predicción ofrecida por el método automático. 
+Las empresas editoriales suelen finalmente definir reglas o índices para ajustar subjetivamente los resultados de predicción.
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
- \item
+ \item M5P trees
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
- \item
+ \item Linear Regression
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
- \item
+ \item Support Vector Machine for Regression (SMOreg)
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
- \item
+ \item K-nearest neighbours classifier (IBk)
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
- \item
+ \item Multilayer Perceptron
 

### 2015-08-08 paper.tex
añadiendo contenido

@@
 Many companies must face, as one of the most difficult tasks to accomplish, new product sales estimation, since in many cases no historical data to serve as guide is available.
+Moreover, some of them lack the knowledge about forecasting methods and they can only make decisions based on the expert sales managers.
 % Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
-Moreover, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
+Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
 % Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose.
@@
 A company that intends launching a new product has a high risk due to the complexity of the production and distribution processes. 
+A newly launched product is also new to the company, and sales forecasts can be based on the experience of similar products.
 In this scope, having accurate estimates of future sales of the new product is extremely important \cite{ChingChin2010}.
@@
 In the field of publishing industry, it is more important printing an adequate number of copies but not too much, as the unsold volumes will lead to losses, whereas if the number of printed copies was not enough, you can always print more.
+Thus, it is extremely important to forecast the sales a new book might achieve.
 
@@
 En el caso de libros ya publicados, se dispone de datos históricos que ayudan a la generación de modelos predictivos. 
-Sin embargo, en el caso de nuevos libros no hay datos históricos que ayuden a definir patrones, y sólo ciertos datos descriptivos están disponibles.
+Sin embargo, en el caso de nuevos libros no hay datos históricos que ayuden a definir patrones, y sólo ciertos datos descriptivos están disponibles, por lo que no todos los métodos de predicción se pueden utilizar \cite{Madsen2008}.
 
@@
 In this stage, a SOM cluster method is used to analyze data, to eliminate unrelated variables and to select the best variables to be considered in the forecasted model.
+This task may help to identify leading indicators to be used by the forecasting methods in order to improve the accuracy of future forecasts.
 
@@
 
-Así pues, en esta investigación se propusieron para su evaluación los siguientes métodos:
+Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used:
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
- \item M5P trees
+ \item M5 Model trees and rules: The original algorithm M5 was proposed by Quinlan \cite{Quinlan1992} and afterwards Wang \cite{Wang1997} made improvements.
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
- \item Support Vector Machine for Regression (SMOreg)
+ \item Support Vector Machine for Regression (SMOreg): This algorithm was proposed by Shevade et al \cite{Shevade1999}.
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
- \item K-nearest neighbours classifier (IBk)
+ \item K-nearest neighbours classifier (IBk): \cite{Aha1991}
 
@@
 
-%-------------------------------------------------
-\subsection{Applying forecasting methods to solve the problem}
+The objective is finding the most appropriate forecasting method that minimizes the error between the forecast and the actual sales for each new book published.
 
-Una vez que se han determinado los métodos a utilizar y los parámetros de ejecución, se utilizará un conjunto de datos para obtener el modelo de predicción y posteriormente se comprobará su bondad ante datos no vistos previamente.
+%********************************************************************************
+\section{Experiments and Results}
+\label{sec:experiments}
 
-\textbf{TODO:} FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS (RESULTADOS QUE SE COMENTARAN EN LA SIGUIENTE SECCION)
+Una vez que se han determinado los métodos a utilizar y los parámetros de ejecución, se aplicarán a los conjuntos de datos para obtener los modelos de predicción y posteriormente se comprobará su bondad ante datos no vistos previamente.
+
+\textbf{TODO:} FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS
 
@@
   %
-
-%********************************************************************************
-\section{Experiments and Results}
-\label{sec:experiments}
-
-aquí hay que contar los experimentos realizados y presentar los resultados obtenidos
 

### 2015-08-08 paper.tex
añadiendo referencias

@@
 separar los datos relativos a una estación de otras para clasificar por separado.
-Finally, in many cases the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions \cite{Lapide1999}.
+Finally, in many cases the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions \cite{Lapide1999,ChernWSF15}.
 In this sense, some authors propose reducing variations in the data caused by such variables to improve the accuracy of predictions
@@
 Sales forecasting in editorial industry is a very complex problem.
-There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use.
+There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.
 
@@
 En el caso de libros ya publicados, se dispone de datos históricos que ayudan a la generación de modelos predictivos. 
-Sin embargo, en el caso de nuevos libros no hay datos históricos que ayuden a definir patrones, y sólo ciertos datos descriptivos están disponibles, por lo que no todos los métodos de predicción se pueden utilizar \cite{Madsen2008}.
+Sin embargo, en el caso de nuevos libros no hay datos históricos que ayuden a definir patrones, y sólo ciertos datos descriptivos están disponibles, por lo que no todos los métodos de predicción se pueden utilizar \cite{Madsen2008,ChernWSF15}.
 

### 2015-08-09 paper.tex
añadimos más detalles sobre el proceso

@@
 
-En un primer paso, el experto analizó las 50 variables de entrada que describen cada libro para eliminar algunas que estimó como suplerfuas.
+As stated in Section \ref{sec:problem}, an expert sales manager colaborated in this research in the stage of data analysis.
+Thus, the process was as follows:
+\begin{itemize}
+  \item First, the expert removed superfluous variables, and dimensionality was reduced from 50 to 43 inputs.
+  \item Then, the expert, using his knowledge and the information obtained analyzing the SOM results, removed some inputs, reducing the number of variables describing a book from 43 to 13.
+  \item The company asked to include the information about \emph{editorial} and \emph{materia}.
+Thus, in a new iteration, taking into account the expert's advice and the información obtained analyzing the SOM results, the number of inputs was decreased to 7.
+  \item In a third step, several forecasting methods were used on the obtained dataset, and the best was choosen to obtain an accurate predicting model.
+  \item Finally, some information about the new book, such as \emph{author}, although not included in the obtained models, was taken into account by the expert sales manager to modify the forecasted results.
+\end{itemize}
+
+Más concretamente, en un primer paso, el experto analizó las 50 variables de entrada que describen cada libro para eliminar algunas que estimó como suplerfuas.
 Table \ref{tabla:params43} shows the set of variables describing a book (43 total inputs) that the expert manager determined as non-superfluous or non-redundant.
@@
 
-Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used:
+Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
+Well known forecasting methods implemented in the Weka\footnote{{\tt http://www.cs.waikato.ac.nz/ml/weka/} tool \cite{Hall2009,Witten2011} have been choosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using these methods.
 
+Specifically, following forecasting methods are proposed:
 \begin{itemize}

### 2015-08-09 paper.tex
nueva figura

@@
 
-Thus, in this study there are three main stages: 
+\begin{figure}[!h] 
+\begin{center}
+\includegraphics{stages.eps} \\
+\caption{\small{Three main stages in this research: data analysis, (2) forecasting methods testing, and (3) subjectively adjusting the obtained results.}}
+\label{fig:stages}
+\end{center}
+\end{figure}
+
+Thus, in this study there are three main stages (see Figure \ref{fig:stages} for details): 
 \begin{itemize}
   \item  First, after the editorial company has provided the raw data, taken directly from its database, a selection variables process is carried out.
-In this stage, a SOM cluster method is used to analyze data, to eliminate unrelated variables and to select the best variables to be considered in the forecasted model.
+In this stage, an expert sales manager, using the information obtained analyzing the SOM cluster method results, removes some unrelated variables and selects the best variables to be considered in the forecasted model.
 This task may help to identify leading indicators to be used by the forecasting methods in order to improve the accuracy of future forecasts.
@@
 \end{itemize}
+
+  %  
+  %  El proceso que seguimos, resumido para el paper, es:
+  %  
+  %  [43 entradas] en 2013-01 vamos a tomar 
+  %  	pb_noneg.csv para obtener pb_ventas.csv (es el pb_ventas.arff)
+  %  	y hacer el SOM
+  %  
+  %  [13 entradas] en 2013-02-08 vamos a tomar 
+  %  	controlado_reducido.csv.arff (197 líneas)
+  %  	pbenero.csv.arff (5656 líneas)
+  %  	y hacer el SOM
+  %  
+  %  [7 entradas; materia editorial] en 2013-02-25 vamos a tomar
+  %  	pbRAWtrn.arff
+  %  	pbRAWtst.arff
+  %
 

### 2015-08-10 paper.tex
arreglando un error de compilación-LaTeX

@@
 Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
-Well known forecasting methods implemented in the Weka\footnote{{\tt http://www.cs.waikato.ac.nz/ml/weka/} tool \cite{Hall2009,Witten2011} have been choosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using these methods.
+Well known forecasting methods implemented in the Weka\footnote{{\tt http://www.cs.waikato.ac.nz/ml/weka/}} tool \cite{Hall2009,Witten2011} have been choosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using these methods.
 

### 2015-08-10 paper.tex
añadidas las tablas para mostrar los resultados (aún no están obtenidos todos)

@@
 \begin{center}
-\includegraphics{stages.eps} \\
+  \epsfig{file=stages.eps,width=7cm}
 \caption{\small{Three main stages in this research: data analysis, (2) forecasting methods testing, and (3) subjectively adjusting the obtained results.}}
@@
 
-Finally, in order to compute the forecasting errors of the different methods, the following standard criteria have been selected: Mean absolute error, Root mean squared error, Relative absolute error and Root relative squared error.
+Finally, in the literature different error measures can be found to report the results obtained using the prediction methods. 
+Those error measurements are also called error functions or cost functions. 
+%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
+
+In any case, we recommend using widely accepted standard equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} in order to compare obtained results with those presented in other research papers using other methods.
+That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.
+
+Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
+
+\begin{itemize}
+  \item \emph{Mean Absolute Error} (MAE):
+        \begin{equation}\label{eq:MAE}
+            MAE = \frac{1}{n}\sum_{i=1}^n {\mid p_i - o_i\mid}
+        \end{equation}
+
+  \item \emph{Root Mean Squared Error} (RMSE):
+        \begin{equation}\label{eq:RMSE}
+            RMSE = \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 }
+        \end{equation}
+
+  \item \emph{Relative absolute error} (RAE):
+        \begin{equation}\label{eq:RAE}
+            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid p_{i-1} - o_i\mid} }
+        \end{equation}
+
+  \item \emph{Root relative squared error} (RRSE):
+        \begin{equation}\label{eq:RRSE}
+            % RRSE = \frac{ \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 } }{ \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_{i-1} - o_i)}^2 } }
+            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(p_{i-1} - o_i)}^2 }  }
+        \end{equation}
+\end{itemize}
+where $o_i$ is the individual data $i = {1,...,n}$ and $p_i$ is the obtained prediction.
 
@@
 \begin{center}
-\includegraphics{som43.eps} \\
+  \epsfig{file=som43.eps,width=\textwidth}
 \caption{\small{Análisis de los datos iniciales, usando 43 variables descriptivas por libro, utilizando el SOM.}}
@@
 \begin{center}
-\includegraphics{som13.eps} \\
+  \epsfig{file=som13.eps,width=\textwidth}
 \caption{\small{Análisis de los datos iniciales, usando 13 variables descriptivas por libro, utilizando el SOM.}}
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
- \item Support Vector Machine for Regression (SMOreg): This algorithm was proposed by Shevade et al \cite{Shevade1999}.
+ \item Support Vector Machine for Regression (SVM): This algorithm was proposed by Shevade et al \cite{Shevade1999}.
 
@@
 
+% Mean absolute error MAE
+% Root mean squared error RMSE
+% Relative absolute error RAE
+% Root relative squared error RRSE
+
+ % [Pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
+Obtained results using the different forecasting methods on the dataset with 13 variables per book can be shown in Table \ref{tabla:results13}:
+\begin{table*}[!h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline 
+ Method 	& Time (sec.) 	& MAE 			& RMSE 			& RAE 			& RRSE 			\\
+\hline
+  MP5 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+  LR 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+  SVM 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+  KNN 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+  MLP 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+\end{tabular}
+\end{center}
+\caption{\small{Results (errors and time) obtained using the different forecasting methods on the dataset with 13 variables per book.}}
+\label{tabla:results13}
+\end{table*}
+
+ % [Pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
+Obtained results using the different forecasting methods on the dataset with 7 variables per book can be shown in Table \ref{tabla:results7}:
+\begin{table*}[!h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline 
+ Method 	& Time (sec.) 	& MAE 			& RMSE 			& RAE 			& RRSE 			\\
+\hline
+  MP5 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+  LR 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+  SVM 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+  KNN 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+  MLP 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+\hline
+\end{tabular}
+\end{center}
+\caption{\small{Results (errors and time) obtained using the different forecasting methods on the dataset with 7 variables per book.}}
+\label{tabla:results7}
+\end{table*}
+
 %********************************************************************************

### 2015-08-12 paper.tex
Cambiado título y comentado abstract
cerrando issue #1
cerrando issue: Closes #1
Storing changes

@@
 %%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
-\title{Using forecasting models for new book publishing}
+\title{Predicting sales of newly published books}
 
@@
 Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
-In this paper, a rule-based decision method is proposed to address the problem of predicting the publishing roll. 
+In this paper, a rule-based decision method is proposed to address the
+problem of predicting the publishing roll. 
+% It's not proposed. It just obtained the best result with WEKA. 
 This method has been validated by the company that provided the data, as the obtained models provide information on the decision process and does not require human intervention, nor for the operation or for interpretation.
 \end{abstract}
+%El abstract no me gusta nada. Debería ir a la introducción. Hay que
+%enmarcar el problema (hace falta predecir las ventas para no imprimir
+%más de la cuenta) hacer una resumen de lo hecho y decir el
+%resultado. Lo más importante es, ¿cuál es el selling point?
 
@@
 Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.
+% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
+% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
+% datos serios de análisis estadístico de las variables.
 
@@
   \epsfig{file=som43.eps,width=\textwidth}
-\caption{\small{Análisis de los datos iniciales, usando 43 variables descriptivas por libro, utilizando el SOM.}}
+\caption{\small{Análisis de los datos iniciales, usando 43 variables
+    descriptivas por libro, utilizando el SOM.}}
+% Además, no es un análisis, es una evolución temporal de un solo
+% entrenamiento.  - JJ
 \label{fig:som43}
@@
 
-Finally, after analizyng the dataset with 13 descriptive inputs per book, and paying attention to the company experienced manager's recommendations, 7 inputs were considered; specifically, variables \emph{editorial} and \emph{materia} were included, while \emph{devolucion\_total, reimpresiones, puntos\_vta1anio\_total, numero\_reimpresiones, devolucion1anio\_total, colocado1anio\_total, semanas\_venta, tirada} were discarded.
+Finally, after analizyng the dataset with 13 descriptive inputs per
+book, and paying attention to the company experienced manager's
+recommendations, 7 inputs were considered; specifically, variables
+\emph{editorial} and \emph{materia} were included, while
+\emph{devolucion\_total, reimpresiones, puntos\_vta1anio\_total,
+  numero\_reimpresiones, devolucion1anio\_total, colocado1anio\_total,
+  semanas\_venta, tirada} were discarded.  
+% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
+% ¿Análisis de varianza? - jj
 Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on the total of 13 descriptive inputs per book.

### 2015-08-12 paper.tex
comentarios
Contestando a @pacastillo

@@
 Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
-In this paper, a rule-based decision method is proposed to address the
-problem of predicting the publishing roll. 
+In this paper, a rule-based decision method is proposed to address the problem of predicting the publishing roll. 
 % It's not proposed. It just obtained the best result with WEKA. 
@@
 \end{abstract}
+
  %El abstract no me gusta nada. Debería ir a la introducción. Hay que
  %enmarcar el problema (hace falta predecir las ventas para no imprimir
-%más de la cuenta) hacer una resumen de lo hecho y decir el
+ %más de la cuenta) hacer un resumen de lo hecho y decir el
  %resultado. Lo más importante es, ¿cuál es el selling point?
@@
 	% datos serios de análisis estadístico de las variables. 
-
+	% [Pedro] ¿a qué gráficas te refieres? ¿a las tablas de las variables?
+% NO, a fig:som43, creo, porque ha desaparecido. - JJ
 \begin{figure}[!h] 
 \begin{center}
-  \epsfig{file=som43.eps,width=\textwidth}
-\caption{\small{Análisis de los datos iniciales, usando 43 variables
-    descriptivas por libro, utilizando el SOM.}}
-% Además, no es un análisis, es una evolución temporal de un solo
-% entrenamiento.  - JJ
+\begin{tabular}{c}
+  \epsfig{file=som43vars.eps,width=11cm} \\
+  \epsfig{file=som43umatrix.eps,width=5cm}
+\end{tabular}
+\caption{\small{Initial data analysis, using 43 descriptive variables per bok, using SOM.}}
+	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
+	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
+	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
+        % Sería más bien exploratory data analysis o data visualization. Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
 \label{fig:som43}
@@
 \begin{table}[!h]
-\caption{Variables describing a book (13 total inputs), after the second analisys carried out using the SOM along with the company experienced manager to select the best variables to be considered to solve the sales forecasting problem.}
+\caption{Variables that describe every book, 13 in total, after the
+  second analysis carried out using the SOM along with the company
+  experienced manager % él no hizo el análisis. No cuela con ``along
+                      % with'' - JJ
+to select the best variables to be considered to
+  solve the sales forecasting problem.} 
 \label{tabla:params13}
@@
 	% ¿Análisis de varianza? - jj
+	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
 Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on the total of 13 descriptive inputs per book.
@@
 \begin{center}
-  \epsfig{file=som13.eps,width=\textwidth}
-\caption{\small{Análisis de los datos iniciales, usando 13 variables descriptivas por libro, utilizando el SOM.}}
+\begin{tabular}{c}
+  \epsfig{file=som13vars.eps,width=11cm} \\
+  \epsfig{file=som13umatrix.eps,width=5cm}
+\end{tabular}
+\caption{\small{Análisis de los datos iniciales, usando 13 variables
+    descriptivas por libro, utilizando el SOM.}}
+%describir de forma más precisa: visualización usando UMatrix de... - JJ
 \label{fig:som13}
@@
 
-\textbf{TODO:} FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS
+\textbf{TODO:} % FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS
 

### 2015-08-12 paper.tex
comentarios

@@
 \end{tabular}
-\caption{\small{Initial data analysis, using 43 descriptive variables per bok, using SOM.}}
+\caption{\small{Initial data analysis, using 43 descriptive variables per book, using SOM.}}
 	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
@@
   second analysis carried out using the SOM along with the company
-  experienced manager % él no hizo el análisis. No cuela con ``along
-                      % with'' - JJ
+  experienced manager % él no hizo el análisis. No cuela con ``along with'' - JJ
 to select the best variables to be considered to

### 2015-08-13 paper.tex
More abstract questions and stuff
And change of references.

@@
 Sin embargo, en el caso de nuevos productos, tales como la publicación para su venta de un nuevo libro, los métodos clásicos no funcionan bien.
-In the literature, different methods of sales prediction, mainly for the fashion industry are proposed. 
+% In the literature, different methods of sales prediction, mainly for
+% the fashion industry are proposed. 
+% Esto no pega nada en el abstract - JJ
 In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
@@
 Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
-In this paper, a rule-based decision method is proposed to address the problem of predicting the publishing roll. 
-% It's not proposed. It just obtained the best result with WEKA. 
-This method has been validated by the company that provided the data, as the obtained models provide information on the decision process and does not require human intervention, nor for the operation or for interpretation.
+In this paper, a rule-based decision method is proposed to address the
+problem of predicting the publishing roll.  
+% It's not proposed. It just obtained the best result with WEKA. - JJ 
+% Publishing roll? ¿Qué es? - JJ
+This method has been validated by the company that provided the data
+and incorporated in a business intelligence tool for publishing houses,
+since the obtained models provide information on the decision process and
+does not require human intervention either for the operation or for
+interpretation.
 \end{abstract}

### 2015-08-13 paper.tex
Changed abstract
The abstract now makes enphasis on the main sales point, which is data processing, not the method itself, which has used a classical package. Please @pacastillo check it out.

@@
 Como parte del estudio, se han aplicado diversos métodos de clasificación y predicción para determinar cuántos libros se pueden llegar a vender.
-
 % Muchas empresas ven la estimación de las ventas de un nuevo producto como uno de las tareas más complicadas de llevar a cabo, ya que en muchos casos no suele haber datos históricos que sirvan de guía.
-Many companies must face, as one of the most difficult tasks to accomplish, new product sales estimation, since in many cases no historical data to serve as guide is available.
-Moreover, some of them lack the knowledge about forecasting methods and they can only make decisions based on the expert sales managers.
+%% Many companies must face, as one of the most difficult tasks to
+%% accomplish, new product sales estimation, since in many cases no
+%% historical data to serve as guide is available. 
+%% Moreover, some of them lack the knowledge about forecasting methods
+%% and they can only make decisions based on the expert sales
+  %% managers. 
+% Eliminado esto.
+When a new book is published the publishing house faces the problem of
+how many books should be printed. Printing too many is the main issue,
+since it implies a loss of investment. That is why it is an issue to
+print the right amount of book, and do so even before the book has
+reached shelves. That is the problem we try to solve in this paper.
 % Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
-Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
+%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
 % Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose.
 Así pues, un sistema automático de predicción de ventas de libros para estimar la tirada editorial sería de gran ayuda para las empresas editoriales.
-That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling.
+%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling.
 Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
-% En la bibliografía se proponen diferentes métodos de predicción de ventas, principalmente para la industria de la moda.
-En esos trabajos, cuando las ventas son estables, con una tendencia clara a lo largo del tiempo, los métodos clásicos son una buena opción.
-Sin embargo, en el caso de nuevos productos, tales como la publicación para su venta de un nuevo libro, los métodos clásicos no funcionan bien.
+% En la bibliografía se proponen diferentes métodos de predicción de
+% ventas, principalmente para la industria de la moda. En esos
+% trabajos, cuando las ventas son estables, con una tendencia clara a
+% lo largo del tiempo, los métodos clásicos son una buena opción. Sin
+% embargo, en el caso de nuevos productos, tales como la publicación
+% para su venta de un nuevo libro, los métodos clásicos no funcionan
+% bien. 
 % In the literature, different methods of sales prediction, mainly for
@@
 % Esto no pega nada en el abstract - JJ
-In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
-However, in the case of new products, such as a new book publishing, classical methods do not work properly.
+%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
+%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
 % En este trabajo se propone el uso de un método basado en reglas de decisión para abordar el problema de la predicción de la tirada editorial.
 Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
-In this paper, a rule-based decision method is proposed to address the
-problem of predicting the publishing roll.  
+%In this paper, a rule-based decision method is proposed to address the
+%problem of predicting the publishing roll.  
 % It's not proposed. It just obtained the best result with WEKA. - JJ 
 % Publishing roll? ¿Qué es? - JJ
-This method has been validated by the company that provided the data
+In this paper, which works with data on published books in Spain, we
+first apply a data visualization and preprocessing strategy to find
+out what are the relevant variables in the prediction of sales, and
+then use standard data mining software to predict sales, and from them
+deduce print roll, based on those variables. Our work discovers which
+are the most relevant variables when predicting sales, and is
+eventually able to predict sales with remarkable accuracy. In fact,
+this method has been validated by the company that provided the data 
 and incorporated in a business intelligence tool for publishing houses,

### 2015-08-13 paper.tex
Revised introduction

@@
 En este ámbito, disponer de estimaciones de futuras ventas del nuevo producto resulta extremadamente importante \cite{ChingChin2010}.
-A company that intends launching a new product has a high risk due to the complexity of the production and distribution processes. 
-A newly launched product is also new to the company, and sales forecasts can be based on the experience of similar products.
-In this scope, having accurate estimates of future sales of the new product is extremely important \cite{ChingChin2010}.
+A company that intends to release a new product has a high risk due to
+the complexity of the production and distribution processes. A newly
+launched product is also new to the company, and sales forecasts can
+only be based on the experience of similar products. 
+In this scope, having accurate estimates of future sales of the new
+product is extremely important \cite{ChingChin2010} so that production
+runs do not exceed predicted sales.
 
 % La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
-In this sense, the publishing industry is based on very particular and established production processes, and publishing a book requires several steps, between whom the distribution is important and plays an important role.
+In this sense, the publishing industry is based on very particular and
+established production process, and publishing a book requires several
+steps, between which the distribution is important and plays an
+important role. 
 % Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
-The publishing process and individual decisions at each step are very important. One of those decisions is the number of copies to print.
+The publishing process and individual decisions at each step are very
+important. One of those decisions is the number of copies to print. % ¿Esto que tiene que ver con la frase anterior? - JJ
 
 % Así pues, un sistema de predicción debe tener en cuenta muchos detalles acerca del funcionamiento del proceso editorial.
-Thus, a suitable prediction system for new book publishing should take into account many details about how the editorial process works.
+Thus, a suitable prediction system for new books should take into
+account many details about how the editorial process works. % y? - JJ
 
 % La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
-Implementing a good forecasting tool requires not only a good study of the state of the art in this field, but also an accurate knowledge of the operations and challenges facing the publishing industry and its supply chain.
+Implementing a good forecasting tool requires not only a good study of
+the state of the art in this field, but also an accurate knowledge of
+the operations and challenges facing the publishing industry and its
+supply chain. % ¿eso es lo que vamos a hacer? - JJ
 
-% En el ámbito de la industria de la moda se trata de un problema muy complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se ha abordado con diversos métodos en las últimas décadas \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
-In the field of fashion industry it is very complex problem, subject to certain requirements \cite{SThomassey2014} and has been faced using various methods in recent decades \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
+% En el ámbito de la industria de la moda se trata de un problema muy
+% complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se
+% ha abordado con diversos métodos en las últimas décadas
+% \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}. 
+% Pero ¿a santo de qué viene aquí la industria de la moda? Habrá que
+% introducirlo diciendo... El problema de la industria similar es
+% parecido a otras industrias, etc, etc...
+
+In the field of fashion predicting sales is very complex problem, subject
+to certain requirements \cite{SThomassey2014} and has been faced using
+various methods in recent decades
+\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.  % Este
+                                % párrafo no dice absolutamente nada
+                                % ni aporta nada. Si se menciona la
+                                % industria de la moda, es que vamos a
+                                % aprender algo de ella. ¿Cuáles son
+                                % los requisitos? ¿Cuáles son los
+                                % métodos? ¿Vamos a aprender de ellos?
+                                % - JJ
 
 % Interesa imprimir un número de ejemplares suficiente pero sin pasarse, ya que los no vendidos suponen pérdidas, mientras que si se imprimieron de menos, siempre se pueden imprimir más.
-In the field of publishing industry, it is more important printing an adequate number of copies but not too much, as the unsold volumes will lead to losses, whereas if the number of printed copies was not enough, you can always print more.
-Thus, it is extremely important to forecast the sales a new book might achieve.
+In the field of publishing industry, it is more important printing an
+adequate number of copies but not too much, as the unsold volumes will
+lead to losses, whereas if the number of printed copies was not
+enough, you can always print more. Thus, it is extremely important to
+forecast the sales a new book might achieve. % Hala, otro salto. ¿Qué
+                                % tiene que ver esto con el párrafo
+                                % anterior? - JJ
 
 % El uso de una herramienta de predicción es útil si se usa adecuadamente, y para ello conviene conocer el producto, las características de las ventas y la forma de distribuirlo, ya que son detalles que afectan al proceso \cite{Armstrong2001,SThomassey2014}.
-Thus, using a predictive tool is very useful when used properly; in this sense, it is very important to know the product, the characteristics of sales and how to distribute it, as those details affect the process \cite{Armstrong2001,SThomassey2014}.
+Thus, using a predictive tool is very useful when used properly; in
+this sense, it is very important to know the product, the
+characteristics of sales and how to distribute it, as those details
+affect the process \cite{Armstrong2001,SThomassey2014}. % ¿Esto
+                                % también pasa en la industria de la
+                                % moda. ¿Qué vamos a usar de esto? - JJ
 
@@
 Algunos tienen que ver con las decisiones sobre compras, otros con el tráfico de mercancías o con la estrategia de distribución \cite{Little1998}.
-The publishing industry is influenced by various factors that make sales fluctuate. 
-These factors are usually not controllable and even, sometimes are not known.
-Some have to do with decisions on purchases, others with freight traffic, and others with the distribution strategy \cite{Little1998}.
+Book sales are influenced by various factors that make
+them fluctuate.  These factors are usually not controllable and
+sometimes unknown. 
+Some have to do with decisions on purchases, others with freight
+traffic, and others with the distribution strategy
+\cite{Little1998}. % ¿Qué hacen todas estas cosas? ¿Vamos a tenerlas
+                   % en cuenta?
 
@@
 Using predictive tools can benefit a publishing company to optimize production and improve their profits or minimize losses \cite{Zhao2001}. 
-An example is the optimization of sales \cite{Mattila2002} by improving profit margins by selling the whole publishing roll.
+An example is the optimization of sales \cite{Mattila2002} by
+improving profit margins by selling the whole publishing roll.
 
@@
 In the literature several proposals to perform the prediction of sales in different areas can be found. 
-On the one hand, several qualitative methods are based on an expert experience, while time series prediction methods are based on using historical data to make predictions \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
+On the one hand, several qualitative methods are based on an expert
+experience, while time series prediction methods are based on using
+historical data to make predictions
+\cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
+                                % dicho cuál es el problema. Tienes
+                                % que decir claramente qué tienes y
+                                % qué quieres. - JJ
 
@@
 Entre las técnicas más conocidas destacan las técnicas estadísticas \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}.
-Using time series prediction methods is perhaps the most used technique to tackle the sales forecasting task.
+Using time series prediction methods is perhaps the most used
+technique to tackle the sales forecasting task. 
 In this sense, among the most popular techniques include statistical techniques \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
@@
 
-Sales forecasting in editorial industry is a very complex problem.
+Sales forecasting in editorial industry is a very complex
+problem. %hala, vuelta la burra al trigo - JJ
 There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.
@@
 Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
-Well known forecasting methods implemented in the Weka\footnote{{\tt http://www.cs.waikato.ac.nz/ml/weka/}} tool \cite{Hall2009,Witten2011} have been choosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using these methods.
+Well known forecasting methods implemented in the Weka tool
+\cite{Hall2009,Witten2011} have been choosen, as these methods are
+widely known, and could be very helpful for practitioners to reproduce
+experiments and even to solve similar sales prediction problems using
+these methods. % eliminado el pie de página, es mejor usar referencias
+               % - JJ
 
@@
 \section*{Acknowledgements}
-This work has been supported in part by SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity), SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17 GENIL project (CEI-BIOTIC Granada).
+This work has been supported in part by SIPESCA (Programa Operativo
+FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and
+TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
+SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14
+(Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
+IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17
+GENIL project (CEI-BIOTIC Granada). % ¿Y el contrato con Trevenque?  - JJ
 

### 2015-08-14 paper.tex
More comments for @pacastillo

@@
 Además, el proceso suele ser tedioso para un conjunto considerable de datos, e incluso, diferentes expertos pueden llegar a diferentes predicciones a partir de los mismos datos.
-Publishers usually use historical data and an expert analyzes that data and apply his knowledge using external variables to obtain quite appropriate predictions.
-However, in recent years the sales prediction task is based on the use of some software that generates a prediction. 
-This is used as the basis or guidance that an expert can tune, as the company might require an interpretable and understandable model.
-For example, the expert might increase or decrease the sales prediction based on some period of offers.
-However, the obtained analysis can be imprecise and may not take all the variables into account.
-In addition, the process is often tedious, especially when the amount of data is large, and even, different experts can reach different predictions from the same data set.
-
+Publishers generally use historical data and an expert analyzes that
+data and applies his knowledge using external variables to obtain quite
+appropriate predictions. % ¿cita para esto?  - JJ
+However, in recent years the sales are forecasted using an
+application. % ¿Cita para esto? - JJ
+This is used as the foundation over which an expert applies his
+knowledge, as the company might require an interpretable and
+understandable model. For example, the expert might increase or
+decrease the sales prediction based on season or sales period.
+However, the obtained analysis can be imprecise and may not take all
+the variables into account. 
+In addition, the process is often tedious, especially when the amount
+of data is large, and even, different experts can reach different
+predictions from the same data set. % We NEED a reference for this!!!
+                                % - JJ
 % Es por estas razones que la industria requiere que se adapten mejores técnicas de predicción a sus necesidades para realizar estimaciones de las ventas.
-For these reasons, the industry requires the best suited forecasting techniques to be adopted so that, estimating sales task is carried out properly.
+For these reasons, the industry requires the best suited forecasting
+techniques to be adopted so that, estimating sales task is carried out
+properly.
 
@@
 %---------- estado del arte
+% ¿Su propia sección? En ese caso, todo lo del estado del arte de
+% arriba debería eliminarse - JJ
 
@@
 Por un lado, ciertos métodos cualitativos se basan en la experiencia de expertos, mientras que los métodos basados en el análisis de series temporales utilizan información histórica para hacer las predicciones \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
-In the literature several proposals to perform the prediction of sales in different areas can be found. 
+In the literature several proposals to perform the prediction of sales
+in different areas can be found.  %frase que no dice nada. ¿Por qué no
+                                %empiezas enmarcando el estado del
+                                %arte? Methods to predict book sales
+                                %have been generally based on ... - JJ
 On the one hand, several qualitative methods are based on an expert
@@
     descriptivas por libro, utilizando el SOM.}}
-%describir de forma más precisa: visualización usando UMatrix de... - JJ
+%describir de forma más precisa: visualización usando UMatrix de... -
+%JJ
+% ¡y usar nombres en inglés para las variables! - JJ
 \label{fig:som13}
@@
 
- % [Pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
+ % [Pedro] los resultados aún no están terminados de calcular. Pongo
+ % unos números cualquiera.
+% ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a
+% seleccionar uno? - JJ
 Obtained results using the different forecasting methods on the dataset with 13 variables per book can be shown in Table \ref{tabla:results13}:
@@
 \end{center}
-\caption{\small{Results (errors and time) obtained using the different forecasting methods on the dataset with 13 variables per book.}}
+\caption{\small{Results (errors and time) obtained using the different
+    forecasting methods on the dataset with 13 variables per book.}} 
 \label{tabla:results13}

### 2015-08-14 paper.tex
creando la sección de estado del arte

@@
 
-% Cuando se edita un nuevo libro, es importante determinar el número de ejemplares que se van a imprimir en papel en cada edición, ya que a la editorial puede suponerle un alto coste imprimir volúmenes que finalmente no se vendan.
-% Así pues, se hace necesario disponer de herramientas automáticas, basadas en algoritmos de extracción de la información que ofrezcan estimaciones de la cantidad de copias de cierto libro que se pueden llegar a vender.
-% En ese sentido, en colaboración con la empresa PRM Consultores S.C.A.
-se ha llevado a cabo el análisis de un conjunto de datos que describen la tirada editorial en los últimos años.
-Como parte del estudio, se han aplicado diversos métodos de clasificación y predicción para determinar cuántos libros se pueden llegar a vender.
-% Muchas empresas ven la estimación de las ventas de un nuevo producto como uno de las tareas más complicadas de llevar a cabo, ya que en muchos casos no suele haber datos históricos que sirvan de guía.
 %% Many companies must face, as one of the most difficult tasks to
@@
 reached shelves. That is the problem we try to solve in this paper.
-% Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
 %Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
-% Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose.
-Así pues, un sistema automático de predicción de ventas de libros para estimar la tirada editorial sería de gran ayuda para las empresas editoriales.
 %That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling.
 Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
-% En la bibliografía se proponen diferentes métodos de predicción de
-% ventas, principalmente para la industria de la moda. En esos
-% trabajos, cuando las ventas son estables, con una tendencia clara a
-% lo largo del tiempo, los métodos clásicos son una buena opción. Sin
-% embargo, en el caso de nuevos productos, tales como la publicación
-% para su venta de un nuevo libro, los métodos clásicos no funcionan
-% bien. 
 % In the literature, different methods of sales prediction, mainly for
@@
 %However, in the case of new products, such as a new book publishing, classical methods do not work properly.
-% En este trabajo se propone el uso de un método basado en reglas de decisión para abordar el problema de la predicción de la tirada editorial.
-Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
 %In this paper, a rule-based decision method is proposed to address the
@@
 
- %El abstract no me gusta nada. Debería ir a la introducción. Hay que
- %enmarcar el problema (hace falta predecir las ventas para no imprimir
- %más de la cuenta) hacer un resumen de lo hecho y decir el
- %resultado. Lo más importante es, ¿cuál es el selling point?
+%********************************************************************************
+\section{Introduction}
 
-%********************************************************************************
-\section{Introduction and State of the Art}
+% A partir de datos históricos de tiradas editoriales se plantea el uso de varios modelos para la clasificación y predicción de la tirada de nuevos títulos editoriales.
 
-% A partir de datos históricos de tiradas editoriales se plantea el uso de varios modelos basados en redes neuronales artificiales para la clasificación y predicción de la tirada de nuevos títulos editoriales.
-
-% En principio, los datos de que se dispone para entrenar los modelos son: autor del libro, materia, precio, editorial, ventas netas y tirada.
-
-% Como primer objetivo se define el conjunto de datos y se estudian las entradas actuales para los modelos de predicción y las que se podrían obtener para mejorar las predicciones.
-
-% Se espera obtener modelos basados en redes neuronales capaces de realizar predicciones de la tirada global.
-
-% A una empresa, lanzar un nuevo producto le supone un alto riesgo debido a la complejidad de los procesos de producción y distribución.
-En este ámbito, disponer de estimaciones de futuras ventas del nuevo producto resulta extremadamente importante \cite{ChingChin2010}.
 A company that intends to release a new product has a high risk due to
@@
 
-% La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
 In this sense, the publishing industry is based on very particular and
@@
 important role. 
-% Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
 The publishing process and individual decisions at each step are very
-important. One of those decisions is the number of copies to print. % ¿Esto que tiene que ver con la frase anterior? - JJ
-
-% Así pues, un sistema de predicción debe tener en cuenta muchos detalles acerca del funcionamiento del proceso editorial.
+important. 
+% One of those decisions is the number of copies to print. 
+  % ¿Esto que tiene que ver con la frase anterior? - JJ
 Thus, a suitable prediction system for new books should take into
@@
 
-% La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
 Implementing a good forecasting tool requires not only a good study of
@@
 
-% En el ámbito de la industria de la moda se trata de un problema muy
-% complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se
-% ha abordado con diversos métodos en las últimas décadas
-% \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}. 
-% Pero ¿a santo de qué viene aquí la industria de la moda? Habrá que
 % introducirlo diciendo... El problema de la industria similar es
 % parecido a otras industrias, etc, etc...
-
 In the field of fashion predicting sales is very complex problem, subject
@@
 
-% Interesa imprimir un número de ejemplares suficiente pero sin pasarse, ya que los no vendidos suponen pérdidas, mientras que si se imprimieron de menos, siempre se pueden imprimir más.
 In the field of publishing industry, it is more important printing an
@@
 
-% El uso de una herramienta de predicción es útil si se usa adecuadamente, y para ello conviene conocer el producto, las características de las ventas y la forma de distribuirlo, ya que son detalles que afectan al proceso \cite{Armstrong2001,SThomassey2014}.
 Thus, using a predictive tool is very useful when used properly; in
@@
 
-% En la industria editorial influyen diversos factores que hacen que las ventas fluctúen.
-Estos factores no suelen ser controlables y en ocasiones no son conocidos.
-Algunos tienen que ver con las decisiones sobre compras, otros con el tráfico de mercancías o con la estrategia de distribución \cite{Little1998}.
 Book sales are influenced by various factors that make
@@
 Some have to do with decisions on purchases, others with freight
-traffic, and others with the distribution strategy
-\cite{Little1998}. % ¿Qué hacen todas estas cosas? ¿Vamos a tenerlas
-                   % en cuenta?
+traffic, and others with the distribution strategy \cite{Little1998}. 
+  % ¿Qué hacen todas estas cosas? ¿Vamos a tenerlas en cuenta?
 
-% El impacto que tienen es difícil de estimar y no es constante en el tiempo, de ahí la dificultad de identificarlos adecuadamente y medir su influencia \cite{DeToni2000}.
-Además, algunas pueden presentar correlaciones entre ellas.
-Sin embargo, dichas correlaciones pueden detectarse utilizando métodos de análisis de datos, como el SOM (y otros de R) \textbf{ESPECIFICAR CUÁLES}
-Their impact is difficult to estimate and it is not constant over time, hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
+Their impact is difficult to estimate and it is not constant over time, 
+hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
 In addition, some may have correlations between them. 
-However, these correlations can be detected using data analysis methods, such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.
+However, these correlations can be detected using data analysis methods, 
+such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
+or stepwise regression analysis (SRA) \cite{Chang2009}.
 
-% Generalmente las editoriales usan datos históricos y es un experto el que aplica su conocimiento y usa diversas variables externas para obtener predicciones bastante adecuadas.
-El proceso habitual de predicción de ventas se basa en el uso de algún tipo de software que genera una predicción que sirve como base u orientación, pero que finalmente refina un experto, ya que la empresa requiere un modelo interpretable y entendible.
-Por ejemplo, el experto puede subir o bajar la predicción de las ventas en función de algún periodo de ofertas.
-Sin embargo, los análisis son imprecisos y pueden no tener todas las variables en cuenta.
-Además, el proceso suele ser tedioso para un conjunto considerable de datos, e incluso, diferentes expertos pueden llegar a diferentes predicciones a partir de los mismos datos.
 Publishers generally use historical data and an expert analyzes that
@@
 of data is large, and even, different experts can reach different
-predictions from the same data set. % We NEED a reference for this!!!
-                                % - JJ
-% Es por estas razones que la industria requiere que se adapten mejores técnicas de predicción a sus necesidades para realizar estimaciones de las ventas.
+predictions from the same data set. % We NEED a reference for this!!! - JJ
+
 For these reasons, the industry requires the best suited forecasting
@@
 
-% El uso de herramientas de predicción puede ser beneficioso para una empresa editorial para optimizar la producción y así mejorar sus ganancias o minimizar pérdidas \cite{Zhao2001}.
-Un ejemplo es la optimización de las ventas \cite{Mattila2002}, mejorando el margen de ganancia al vender toda la tirada editorial.
-Using predictive tools can benefit a publishing company to optimize production and improve their profits or minimize losses \cite{Zhao2001}. 
+Using predictive tools can benefit a publishing company to optimize 
+production and improve their profits or minimize losses \cite{Zhao2001}. 
 An example is the optimization of sales \cite{Mattila2002} by
@@
 
-\bigskip
-%---------- estado del arte
-% ¿Su propia sección? En ese caso, todo lo del estado del arte de
-% arriba debería eliminarse - JJ
+The rest of this paper is structured as follows:
+Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to the prediction of sales.
+Then, Section \ref{sec:problem} describes the new book publishing problem, followed by Section \ref{sec:methodology} where the experimental setup and the methodology considered in the study is presented.
+Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
+Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.
 
-% En la bibliografía se pueden encontrar diversas propuestas para llevar a cabo la predicción de ventas en diferentes áreas.
-Por un lado, ciertos métodos cualitativos se basan en la experiencia de expertos, mientras que los métodos basados en el análisis de series temporales utilizan información histórica para hacer las predicciones \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
+%********************************************************************************
+\section{State of the art}
+\label{sec:soa}
+
 In the literature several proposals to perform the prediction of sales
@@
 
-%El uso de métodos de predicción de series temporales es quizás la técnica más usada para la predicción de ventas.
-Entre las técnicas más conocidas destacan las técnicas estadísticas \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}.
 Using time series prediction methods is perhaps the most used
 technique to tackle the sales forecasting task. 
-In this sense, among the most popular techniques include statistical techniques \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
-% Sin embargo, la eficiencia de estas técnicas depende en gran medida del campo de aplicación y de los datos que conforman el problema.
-Concretamente, aquellas técnicas que requieren de una gran cantidad de datos no son las más apropiadas para realizar la predicción de ventas de nuevos productos \cite{ChingChin2010}.
+In this sense, among the most popular techniques include 
+statistical techniques \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
 However, the efficiency of these techniques depends largely on the field of application and the problem data. 
@@
 
-% En cualquier caso, en diversos trabajos ha quedado demostrado que una reducción de los errores de predicción en las ventas da como resultado una mejora en la cadena de producción \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
 Anyway, several studies have demonstrated that improving sale predictions (a reduction of forecasting errors) results in an improvement in the production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
 
-% Por otro lado, diferentes autores han propuesto métricas para determinar la bondad de las estimaciones.
-Sin embargo, las más comunmente utilizadas por las empresas son las basadas en el análisis de los errores cometidos (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.
 On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
@@
 
-% Finalmente, existen casos en los que las predicciones se ven influenciadas por variables externas que hay que tener en cuenta, como la estacionalidad, promociones o modas \cite{Lapide1999}.
-Algunos autores proponen reducir las variaciones en los datos causadas por esas variables para mejorar la precisión de las predicciones \cite{Sheikh2003,Schrieber2005}.
-% p.ej.
-separar los datos relativos a una estación de otras para clasificar por separado.
 Finally, in many cases the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions \cite{Lapide1999,ChernWSF15}.
@@
 
-% Por el tipo de problema que queremos abordar en este artículo, los métodos clásicos de predicción no son útiles, por lo que deberemos analizarlos previamente con otras herramientas.
-Además, puesto que las editoriales necesitan modelos que expliquen las predicciones ofrecidas, ciertos métodos tipo caja negra pueden no resultar adecuados a igualdad de precisión en las predicciones.
 Taking into account the kind of problem we address in this paper, the classical forecasting methods are not useful. 
@@
 In addition, since publishers need models to explain obtained predictions, black box forecasting methods may not be suitable for this problem.
-
-\bigskip
-%---------- final de la intro
-
-The rest of this paper is structured as follows:
-%Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography to BLA BLA BLA.
-Section \ref{sec:problem} describes the new book publishing problem, followed by Section \ref{sec:methodology} where the experimental setup and the methodology considered in the study is presented. 
-Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
-Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.
 

### 2015-08-15 paper.tex
Revising abstract

@@
 how many books should be printed. Printing too many is the main issue,
-since it implies a loss of investment. That is why it is an issue to
-print the right amount of book, and do so even before the book has
-reached shelves. That is the problem we try to solve in this paper.
+since it implies a loss of investment due to inventory excess. That is
+why in this paper we are tackling the problem or predicting sales to 
+print the right amount of books, doing so even before the book has
+reached shelves, which is when printing occurs. 
 %Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
@@
 % Publishing roll? ¿Qué es? - JJ
-In this paper, which works with data on published books in Spain, we
+In this paper, which works with data on published books for several years in Spain, we
 first apply a data visualization and preprocessing strategy to find
@@
 
-% A partir de datos históricos de tiradas editoriales se plantea el uso de varios modelos para la clasificación y predicción de la tirada de nuevos títulos editoriales.
+% A partir de datos históricos de tiradas editoriales se plantea el
+% uso de varios modelos para la clasificación y predicción de la
+% tirada de nuevos títulos editoriales.
 
@@
 
-The rest of this paper is structured as follows:
-Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to the prediction of sales.
-Then, Section \ref{sec:problem} describes the new book publishing problem, followed by Section \ref{sec:methodology} where the experimental setup and the methodology considered in the study is presented.
+The rest of this paper is structured as follows: next, 
+Section \ref{sec:soa} presents a comprehensive review of the
+approaches found in the bibliography related to the prediction of
+sales from product characteristics. 
+Then, Section \ref{sec:problem} describes the new book publishing
+problem, % no es el problema de publicación, es el problema de venta
+         % de libros sin publicar. Habrá que buscar un nombre - JJ
+ followed by Section \ref{sec:methodology} where the
+experimental setup and the methodology considered in the study is
+presented.  
 Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
-Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.
+Finally, conclusions and future work are presented in Section
+\ref{sec:conclusionsAndFutureWork}.
 

### 2015-08-17 paper.tex
arreglando la introducción

@@
 runs do not exceed predicted sales. 
+Indeed, several studies have demonstrated that improving sale predictions 
+(a reduction of forecasting errors) results in an improvement in the 
+production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
 
-In this sense, the publishing industry is based on very particular and
-established production process, and publishing a book requires several
-steps, between which the distribution is important and plays an
-important role. 
-The publishing process and individual decisions at each step are very
-important. 
-% One of those decisions is the number of copies to print. 
+% In this sense, the publishing industry is based on very particular and
+% established production process, and publishing a book requires several
+% steps, between which the distribution is important and plays an
+% important role. The publishing process and individual decisions at each step are very
+% important. One of those decisions is the number of copies to print. 
   % ¿Esto que tiene que ver con la frase anterior? - JJ
-Thus, a suitable prediction system for new books should take into
-account many details about how the editorial process works. % y? - JJ
+% Thus, a suitable prediction system for new books should take into
+% account many details about how the editorial process works. % y? - JJ
 
-Implementing a good forecasting tool requires not only a good study of
-the state of the art in this field, but also an accurate knowledge of
-the operations and challenges facing the publishing industry and its
-supply chain. % ¿eso es lo que vamos a hacer? - JJ
-
-% introducirlo diciendo... El problema de la industria similar es
-% parecido a otras industrias, etc, etc...
-In the field of fashion predicting sales is very complex problem, subject
-to certain requirements \cite{SThomassey2014} and has been faced using
-various methods in recent decades
-\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.  % Este
-                                % párrafo no dice absolutamente nada
-                                % ni aporta nada. Si se menciona la
-                                % industria de la moda, es que vamos a
-                                % aprender algo de ella. ¿Cuáles son
-                                % los requisitos? ¿Cuáles son los
-                                % métodos? ¿Vamos a aprender de ellos?
-                                % - JJ
+% Implementing a good forecasting tool requires not only a good study of
+% the state of the art in this field, but also an accurate knowledge of
+% the operations and challenges facing the publishing industry and its
+% supply chain. % ¿eso es lo que vamos a hacer? - JJ
 
@@
 lead to losses, whereas if the number of printed copies was not
-enough, you can always print more. Thus, it is extremely important to
-forecast the sales a new book might achieve. % Hala, otro salto. ¿Qué
-                                % tiene que ver esto con el párrafo
-                                % anterior? - JJ
+enough, you can always print more. 
+Thus, it is extremely important using predictive tools to optimize 
+production and improve the publishing company profits or minimize losses \cite{Zhao2001}
+by forecasting the sales a new book might achieve. 
+An example is the optimization of sales \cite{Mattila2002} by
+improving profit margins by selling the whole publishing roll.  
+% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...
 
-Thus, using a predictive tool is very useful when used properly; in
-this sense, it is very important to know the product, the
-characteristics of sales and how to distribute it, as those details
-affect the process \cite{Armstrong2001,SThomassey2014}. % ¿Esto
-                                % también pasa en la industria de la
-                                % moda. ¿Qué vamos a usar de esto? - JJ
-
-Book sales are influenced by various factors that make
-them fluctuate.  These factors are usually not controllable and
+However, accurately using a predictive tool is a difficult task as
+book sales are influenced by various factors that make
+them fluctuate and usually they might be not controllable and
 sometimes unknown. 
@@
 traffic, and others with the distribution strategy \cite{Little1998}.
-  % ¿Qué hacen todas estas cosas? ¿Vamos a tenerlas en cuenta?
 
+Thus, it is very important to know the product and the variables that
+might affect the sales, and how an expert manager can eventually 
+take them into account \cite{Armstrong2001,SThomassey2014}. 
+                                % ¿Esto también pasa en la industria de la
+                                % moda. ¿Qué vamos a usar de esto? - JJ
+                                % [Pedro] esto iba referido a la Industria Editorial.
 Their impact is difficult to estimate and it is not constant over time, 
@@
 
-Publishers generally use historical data and an expert analyzes that
-data and applies his knowledge using external variables to obtain quite
-appropriate predictions. % ¿cita para esto?  - JJ
-However, in recent years the sales are forecasted using an
-application. % ¿Cita para esto? - JJ
-This is used as the foundation over which an expert applies his
-knowledge, as the company might require an interpretable and
-understandable model. For example, the expert might increase or
-decrease the sales prediction based on season or sales period.
-However, the obtained analysis can be imprecise and may not take all
-the variables into account. 
-In addition, the process is often tedious, especially when the amount
+In this research, the problem of how many books should be printed 
+when a new book is published is faced using data provided by the 
+Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
+The company's expert sales managers analized historical data 
+and applied their knowledge using external variables to calculate
+appropriate predictions, for example, increasing or decreasing the 
+sales prediction based on season or sales period.
+                        % varias citas - JJ
+                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
+                        %  y que así era como funcionaban hasta ese momento.
+%In any case, in general companies usually use a forecasting model and then, an expert applies his knowledge, as the company might require an interpretable and understandable model.
+
+However, carrying out the analysis and forecasting process as described,
+may lead to an imprecise analysis and may not take all the variables into account. 
+In addition, the process might be tedious, especially when the amount
 of data is large, and even, different experts can reach different
-predictions from the same data set. % We NEED a reference for this!!! - JJ
+predictions from the same data set \cite{ChingChin2010,Sanders1994}.
 
@@
 techniques to be adopted so that, estimating sales task is carried out
-properly.
+properly and in an automatic way.
 
-Using predictive tools can benefit a publishing company to optimize 
-production and improve their profits or minimize losses \cite{Zhao2001}. 
-An example is the optimization of sales \cite{Mattila2002} by
-improving profit margins by selling the whole publishing roll.
+With this in mind, i this paper a data visualization and preprocessing strategy to find
+out what are the relevant variables describing a book in the prediction 
+of book sales is proposed; then several standard data mining models 
+for sales forecasting are evaluated so a publishing company 
+can deduce and optimize print roll.
 
@@
 sales from product characteristics. 
-Then, Section \ref{sec:problem} describes the new book publishing
-problem, % no es el problema de publicación, es el problema de venta
+Then, Section \ref{sec:problem} describes the 
+problem of how many books should be printed when a new book is published, 
+        % no es el problema de publicación, es el problema de venta
         % de libros sin publicar. Habrá que buscar un nombre - JJ
+        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
  followed by Section \ref{sec:methodology} where the
@@
 %********************************************************************************
-\section{State of the art}
+\section{Sales forecasting. State of the art}
 \label{sec:soa}
@@
 In the literature several proposals to perform the prediction of sales
-in different areas can be found.  %frase que no dice nada. ¿Por qué no
-                                %empiezas enmarcando el estado del
-                                %arte? Methods to predict book sales
-                                %have been generally based on ... - JJ
+in different fields can be found. % frase que no dice nada. ¿Por qué no empiezas enmarcando el estado del
+                                % arte? Methods to predict book sales have been generally based on ... - JJ
+                                % [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
+                                %  por eso quiero enfocarlo desde el punto de vista de la predicción 
+                                %  de ventas en general, que sí hay bastante en muchos campos.
 On the one hand, several qualitative methods are based on an expert
-experience, while time series prediction methods are based on using
-historical data to make predictions
+experience, while time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
+are based on using historical data to make predictions
 \cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
@@
 
-Using time series prediction methods is perhaps the most used
-technique to tackle the sales forecasting task. 
-In this sense, among the most popular techniques include 
-statistical techniques \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
-However, the efficiency of these techniques depends largely on the field of application and the problem data. 
-Specifically, techniques that require a large amount of data for predicting sales of new products are not the most suitable for this task \cite{ChingChin2010}.
+Although using time series prediction methods is perhaps the most used
+technique to tackle the sales forecasting task, the efficiency of these 
+techniques depends largely on the field of application and the problem data. 
+Specifically, techniques that require a large amount of data for predicting 
+sales of new products are not the most suitable for this task \cite{ChingChin2010}.
 
-Anyway, several studies have demonstrated that improving sale predictions (a reduction of forecasting errors) results in an improvement in the production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
+Thus, in the last years, different analysis and forecasting methods 
+have been proposed for sales forecasting in several industry fields. %similar to the publishing industry.
 
-On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
-However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.
+  %[Pedro] el caso de la industria de la moda es muy similar al de la 
+  % publicación de nuevos libros, ya que no hay datos históricos 
+  % de un nuevo producto, y hay que echar mano de productos similares
+  % o simplemente de los datos que describen el nuevo producto.
+In the fashion industry, very similar to the publishing industry, 
+predicting sales is a very complex problem, subject
+to certain specific requirements \cite{SThomassey2014}.
+This task has been faced using various methods in recent decades
+  %[Pedro] me falta describir las aproximaciones
+\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
 
-Finally, in many cases the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions \cite{Lapide1999,ChernWSF15}.
-In this sense, some authors propose reducing variations in the data caused by such variables to improve the accuracy of predictions
+  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre
+  % New tea product
+  % New cosmetic product
+  % New soft drink product
+
+  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre 
+  % sales forecasting in printed circuit board industry
+
+Finally, in many cases the predictions are influenced by external 
+variables that must be taken into account, such as seasonality, 
+promotions or fashions \cite{Lapide1999,ChingChin2010,ChernWSF15}.
+In this sense, some authors propose reducing variations in the data 
+caused by such variables to improve the accuracy of predictions
  \cite{Sheikh2003,Schrieber2005}.
 
-Taking into account the kind of problem we address in this paper, the classical forecasting methods are not useful. 
-Thus, we must analyze raw data using other tools, prior to apply forecasting techniques.
-In addition, since publishers need models to explain obtained predictions, black box forecasting methods may not be suitable for this problem.
+%On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
+%However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.
+
+Taking into account the kind of problem we address in this paper, the 
+classical forecasting methods are not useful. 
+Thus, we must analyze raw data using other tools, prior to apply 
+forecasting techniques.
+In addition, since publishers need models to explain obtained predictions, 
+black box forecasting methods may not be suitable for this problem, so 
+models based on rules are proposed.
 
@@
 
-Sales forecasting in editorial industry is a very complex
-problem. %hala, vuelta la burra al trigo - JJ
+%Sales forecasting in editorial industry is a very complex problem. 
+        %hala, vuelta la burra al trigo - JJ
+        %[Pedro] ea, lo quito
 There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.
@@
 \hline
+
+  %[Pedro] me falta poner ya los nombres traducidos (y usarlos para los SOM)
 
@@
 
- % [Pedro] los resultados aún no están terminados de calcular. Pongo
- % unos números cualquiera.
-% ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a
-% seleccionar uno? - JJ
+  %[pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
+  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
+  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
+  % en algunos calculan muchos más, pero estos son los más usados.
 Obtained results using the different forecasting methods on the dataset with 13 variables per book can be shown in Table \ref{tabla:results13}:
@@
 \section*{Acknowledgements}
-This work has been supported in part by SIPESCA (Programa Operativo
-FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and
+This work has been supported in part by PreTEL (PRM Consultores - Trevenque),
+SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and
 TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
@@
 IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17
-GENIL project (CEI-BIOTIC Granada). % ¿Y el contrato con Trevenque?  - JJ
+GENIL project (CEI-BIOTIC Granada). 
+    % ¿Y el contrato con Trevenque?  - JJ
+    %[pedro] añadido
 

### 2015-08-18 paper.tex
contestando algunos comentarios
contestando algunos comentarios más
contestando algunos comentarios más.
arreglando (rehaciendo) la sección del estado del arte
SoA: comentando sobre la ausencia de trabajos sobre predicción de ventas de libros.
añado los resultados de MP5, LR y KNN. Aún faltan los de SVM y MLP
Completo la tabla results13 . Aún faltan los de SVM y MLP en la tabla results7
Ya están los resultados de SVM para tabla results7 . Aún faltan los de MLP en la tabla results7
rehaciendo el estado del arte

@@
                         %  y que así era como funcionaban hasta ese momento.
+
 %In any case, in general companies usually use a forecasting model and then, an expert applies his knowledge, as the company might require an interpretable and understandable model.
@@
 
-In the literature several proposals to perform the prediction of sales
-in different fields can be found. % frase que no dice nada. ¿Por qué no empiezas enmarcando el estado del
-                                % arte? Methods to predict book sales have been generally based on ... - JJ
 % [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
-                                %  por eso quiero enfocarlo desde el punto de vista de la predicción 
-                                %  de ventas en general, que sí hay bastante en muchos campos.
-On the one hand, several qualitative methods are based on an expert
-experience, while time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
-are based on using historical data to make predictions
-\cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
-                                % dicho cuál es el problema. Tienes
-                                % que decir claramente qué tienes y
-                                % qué quieres. - JJ
+%  por eso quiero comenzar hablando de la aplicación de métodos
+%  de predicción en la industria en general, que sí hay bastante bibliografía.
 
-Although using time series prediction methods is perhaps the most used
-technique to tackle the sales forecasting task, the efficiency of these 
-techniques depends largely on the field of application and the problem data. 
-Specifically, techniques that require a large amount of data for predicting 
+% In the literature several proposals to perform the prediction of sales in different fields can be found. 
+In the last years, different analysis and forecasting methods, such as
+regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001} 
+have been applyed in different industry sectors, i.e. electricity consumption, traffic flow or sales forecasting.
+
+Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
+is perhaps the most used technique to tackle the sales forecasting problems, 
+the efficiency of these techniques depends largely on the field of application 
+and the problem data as they require a large amount of data for predicting 
 sales of new products are not the most suitable for this task \cite{ChingChin2010}.
 
-Thus, in the last years, different analysis and forecasting methods 
-have been proposed for sales forecasting in several industry fields. %similar to the publishing industry.
+This is the new book sales forecasting case, for which no historical data 
+to make predictions \cite{ChingChin2010,FaderHardie2005,Madsen2008} is available
+and only some descriptive variables relative to the new unpublished-book are available.
 
-  %[Pedro] el caso de la industria de la moda es muy similar al de la 
-  % publicación de nuevos libros, ya que no hay datos históricos 
-  % de un nuevo producto, y hay que echar mano de productos similares
-  % o simplemente de los datos que describen el nuevo producto.
-In the fashion industry, very similar to the publishing industry, 
-predicting sales is a very complex problem, subject
-to certain specific requirements \cite{SThomassey2014}.
-This task has been faced using various methods in recent decades
-  %[Pedro] me falta describir las aproximaciones
-\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
+Methods used to predict book sales have been generally based on experts' 
+experience who analyzed data about sales, and taking into account their knowledge 
+in industry experience and their perception about trends, could make decisions
+on the companies production (how many books should be printed when a new book is published).
+This a complex problem as the predictions are influenced by external variables 
+that must be taken into account, such as seasonality, promotions or fashions 
+that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.
 
-  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre
+  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
+  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
+  %  o aconsejar acerca de la cantidad de libros a imprimir.
+  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
+  %  sobre "Use Blog Information As Book Sales Prediction":
+  %     Moon2010ICSSSM
+  %     Moon2010ICEC
+Recently, some works propose \cite{Moon2010ICSSSM,Moon2010ICEC} analyzing 
+relationships between on-line information and book sales.
+Specifically, authors propose using the number of blog references as an indicator of book sales.
+Different sales patterns are observed by analyzing data obtained.
+In any case, in this research, historical data from published books is used, 
+and the proposed methodology can not be usable in the problem of unpublished-books sales prediction.
+
+%
+% pasar a contar los casos de la predicción de ventas en la 
+% industria de la moda (SThomassey2014) y de nuevos productos (ChingChin2010)
+%
+% Son problemas muy similares, ya que no hay datos históricos de los nuevos productos,
+% al igual que no los hay sobre ventas, y en los que además influyen mucho las variables 
+% externas (estacionalidad, modas, fama del author, etc).
+% Hay que echar mano de productos similares o simplemente de los datos que describen el nuevo producto.
+%
+
+Some authors have faced the problem of forecasting sales of new products using 
+different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
+Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
+decision trees for sales forecasting in textile-appared fashion industry, 
+a very similar issue to the new book publishing problem.
+The same problem was previously faced by Xia et al \cite{Xia2012} using a 
+forecasting method based on extreme learning machine with adaptive metrics of inputs.
+Complexity of this problem is due to the lack of historical data, short lifetime 
+of the large number of items, and due to the influence of variables such as promotions, 
+fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.
+
+  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
   % New tea product
@@
 
-  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre 
-  % sales forecasting in printed circuit board industry
+  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
+  % sales forecasting in printed circuit board industry.
 
-Finally, in many cases the predictions are influenced by external 
-variables that must be taken into account, such as seasonality, 
-promotions or fashions \cite{Lapide1999,ChingChin2010,ChernWSF15}.
-In this sense, some authors propose reducing variations in the data 
-caused by such variables to improve the accuracy of predictions
- \cite{Sheikh2003,Schrieber2005}.
+%Finally, although different authors have proposed metrics to determine 
+%the accuracy of estimates, most companies use metrics based on the analysis 
+%of errors, i.e. MAE or RMSE \cite{ChingChin2010,Madsen2008}.
 
-%On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
-%However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.
-
-Taking into account the kind of problem we address in this paper, the 
-classical forecasting methods are not useful. 
-Thus, we must analyze raw data using other tools, prior to apply 
-forecasting techniques.
+Taking into account the kind of problem we address in this paper, 
+a new product sales prediction for which no historical data is available,
+the classical forecasting methods based on time series are not adequate. 
+Thus, in this paper the relevant variables in the prediction of sales are determined
+using data visualization tools and then, standard data mining software 
+to predict sales is used to deduce print roll.
 In addition, since publishers need models to explain obtained predictions, 
 black box forecasting methods may not be suitable for this problem, so 
-models based on rules are proposed.
+models based on rules are tested as an alternative.
 
@@
 %One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
-
 In any case, we recommend using widely accepted standard equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} in order to compare obtained results with those presented in other research papers using other methods.
@@
 	% datos serios de análisis estadístico de las variables. 
-	% [Pedro] ¿a qué gráficas te refieres? ¿a las tablas de las variables?
-% NO, a fig:som43, creo, porque ha desaparecido. - JJ
+	% [Pedro] sí, estoy de acuerdo. Esto va con el ISSUE #6
 \begin{figure}[!h] 
@@
     descriptivas por libro, utilizando el SOM.}}
-%describir de forma más precisa: visualización usando UMatrix de... -
-%JJ
+% describir de forma más precisa: visualización usando UMatrix de... - JJ
 % ¡y usar nombres en inglés para las variables! - JJ
+%[pedro] es el siguiente arreglo que le haré mañana al paper    ;)
 \label{fig:som13}
@@
 
-  %[pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
+  %[pedro] ya están todos los resultados de tabla:results13 para MP5, LR, KNN, SVM y MLP
+
   % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
@@
 \hline
-  MP5 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  MP5 		& 2.94 $\pm$ 0.51 	& 65.49 	& 133.73 	& 11.10 	& 9.17 	  \\
 \hline
-  LR 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  LR 		  & 0.33 $\pm$ 0.07 	& 100.813 & 257.63 	& 17.09 	& 17.67 	\\
 \hline
-  SVM 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  SVM 		& 49.10 $\pm$ 8.05	& 52.30	  & 139.45	& 8.87    & 9.56  	\\
 \hline
-  KNN 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  KNN 		& 0.03 $\pm$ 0.01 	& 198.16 	& 542.93 	& 33.59 	& 37.24 	\\
 \hline
-  MLP 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  MLP 		& 12.70 $\pm$ 3.08 	& 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
 \hline
@@
 
- % [Pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
+  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
+  % faltan AUN los de MLP
+
   Obtained results using the different forecasting methods on the dataset with 7 variables per book can be shown in Table \ref{tabla:results7}:
@@
 \hline
-  MP5 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  MP5     & 7.39 $\pm$ 1.75   & 117.78   & 260.05  & 18.51   & 17.00  \\
 \hline
-  LR 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  LR      & 40.59 $\pm$ 12.94 & 120.29  & 252.91  & 18.91   & 16.54   \\
 \hline
-  SVM 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  SVM     & 1547.91 $\pm$ 365.55 & 109.30  & 251.16   & 17.18     & 16.42   \\
 \hline
-  KNN 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  KNN     & 0.02 $\pm$ 0.01   & 293.98  & 1071.52  & 46.21   & 70.06   \\
 \hline
-  MLP 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
+  MLP     & 3265.71 $\pm$ 813.37   & 992.97 $\pm$ 0   & 1755.62 $\pm$ 0  & 156.07 $\pm$ 0   & 114.79 $\pm$ 0   \\
 \hline

### 2015-08-18 paper.tex
rehaciendo el estado del arte
Más preguntas y sugerencias para revisar por @pacastillo

@@
 \usepackage[dvips]{epsfig}
-%\usepackage[spanish]{babel}
 \usepackage[latin1]{inputenc}
@@
 the complexity of the production and distribution processes. A newly
+% tienes que enmarcar el problema. Se trata de productos culturales
+% con soporte físico y con ventas relativamente pequeñas. Libros,
+% discos, no sé si alguna cosa más. - JJ
 launched product is also new to the company, and sales forecasts can
@@
 
-In the field of publishing industry, it is more important printing an
+In the field of publishing industry, the challenge is to print an
 adequate number of copies but not too much, as the unsold volumes will
@@
 such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
-or stepwise regression analysis (SRA) \cite{Chang2009}.
+or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
+                                % do? What are the results?
 
@@
 regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001} 
-have been applyed in different industry sectors, i.e. electricity consumption, traffic flow or sales forecasting.
+have been applied in different industry sectors, i.e. electricity
+consumption, traffic flow or sales forecasting. % ¿Y qué? Esta frase
+                                % no aporta nada. La primera frase
+                                % tiene que enmarcar el estado del
+                                % arte - JJ
 
@@
   % sales forecasting in printed circuit board industry.
-
-%Finally, although different authors have proposed metrics to determine 
-%the accuracy of estimates, most companies use metrics based on the analysis 
-%of errors, i.e. MAE or RMSE \cite{ChingChin2010,Madsen2008}.
 
@@
 
-Finally, in the literature different error measures can be found to report the results obtained using the prediction methods. 
+%Finally, although different authors have proposed metrics to determine 
+%the accuracy of estimates, most companies use metrics based on the analysis 
+%of errors, i.e. MAE or RMSE \cite{ChingChin2010,Madsen2008}.
+
+Finally, in the literature different error measures can be found to report 
+the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
 Those error measurements are also called error functions or cost functions. 
 %One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
-In any case, we recommend using widely accepted standard equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} in order to compare obtained results with those presented in other research papers using other methods.
-That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.
+In any case, we recommend using widely accepted standard 
+equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} 
+in order to compare obtained results with those presented in other research 
+papers using other methods.
+That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
+implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
+or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.
 
-Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
+Specifically, in order to compute the forecasting errors of the different methods, 
+Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) 
+and Root relative squared error (RRSE) have been selected:
 

### 2015-08-18 paper.tex
traduciendo los nombres de variables

@@
 \begin{minipage}{2.3in} \begin{verbatim}
-referencia
-autor
-pvp
-materia1
-materia2
-materia3
-editorial
-coleccion
-encuadernacion
-tirada
-venta_total
-venta_grandes_superficies
-venta_delegados
-venta_resto
-venta1anio_total
-venta1anio_grandes_superficies
-venta1anio_delegados
-venta1anio_resto
-colocado_total
-colocado_grandes_superficies
-colocado_delegados
-colocado_resto
-colocado1anio_total
-colocado1anio_grandes_superficies
-colocado1anio_delegados
+REFERENCE
+AUTHOR
+RETAIL PRICE
+SUBJECT-MATTER1
+SUBJECT-MATTER2
+SUBJECT-MATTER3
+EDITORIAL
+COLLECTION
+BOOKBINDING
+PRINT-RUN
+TOTAL SALES
+MALLS SALES
+DELEGATES SALES
+REST OF SALES
+TOTAL SALES FIRST YEAR
+MALL SALES FIRST YEAR
+DELEGATES SALES FIRST YEAR
+REST OF SALES FIRST YEAR
+TOTAL DISTRIBUTED
+MALLS DISTRIBUTED
+DELEGATES DISTRIBUTED
+REST OF DISTRIBUTED
+TOTAL DISTRIBUTED FIRST YEAR
+MALLS DISTRIBUTED FIRST YEAR
+DELEGATES DISTRIBUTED FIRST YEAR
 \end{verbatim} \end{minipage}     &
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-colocado1anio_resto
-reimpresiones
-numero_reimpresiones
-devolucion_total
-devolucion_grandes_superficies
-devolucion_delegados
-devolucion_resto
-devolucion1anio_total
-devolucion1anio_grandes_superficies
-devolucion1anio_delegados
-devolucion1anio_resto
-obsequios
-ejemplares_distribuidos_en_novedad
-puntos_vta_total
-puntos_vta_grandes_superficies
-puntos_vta_delegados
-puntos_vta_resto
-puntos_vta1anio_total
-puntos_vta1anio_grandes_superficies
-puntos_vta1anio_delegados
-puntos_vta1anio_resto
-semanas_venta
-entorno_venta_positivo
-entorno_venta_medio
-entorno_venta_negativo
+REST OF DISTRIBUTED FIRST YEAR
+REPRINTS
+NUMBER OF REPRINTS
+TOTAL DEVOLUTIONS
+MALLS DEVOLUTIONS
+DELEGATES DEVOLUTIONS
+REST OF DEVOLUTIONS
+TOTAL DEVOLUTIONS FIRT YEAR
+MALLS DEVOLUTIONS FIRST YEAR
+DELEGATES DEVOLUTIONS FIRST YEAR
+REST OF DEVOLUTIONS FIRST YEAR
+GIFTS
+UNITS DISTRIBUTED IN FIRST EDITION
+TOTAL SELLING POINTS
+MALLS SELLING POINTS
+DELEGATES SELLING POINTS
+REST OF SELLING POINTS
+TOTAL SELLING POINTS FIRST YEAR
+MALLS SELLING POINTS FIRST YEAR
+DELEGATES SELLING POINTS FIRST YEAR
+REST OF SELLING POINTS FIRST YEAR
+WEEKS ON SALE
+POSITIVE SALE MARKET
+MEDIUM SALE MARKET
+NEGATIVE SALE MARKET
 \end{verbatim} \end{minipage}    \\
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-puntos_vta1anio_grandes_superficies
-venta1anio_resto
-entorno_venta_negativo
-colocado1anio_grandes_superficies
-devolucion_total
-reimpresiones
-venta1anio_grandes_superficies
-puntos_vta1anio_total
-ejemplares_distribuidos_en_novedad
-tirada
-numero_reimpresiones
-devolucion_grandes_superficies
-puntos_vta1anio_resto
-venta_resto
-puntos_vta_delegados
-devolucion_resto
-puntos_vta1anio_delegados
-entorno_venta_positivo
-colocado1anio_resto
-puntos_vta_resto
-devolucion1anio_total
-devolucion_delegados
+MALLS SELLING POINTS FIRST YEAR
+REST OF SALES FIRST YEAR
+NEGATIVE SALE MARKET
+MALLS DISTRIBUTED FIRST YEAR
+TOTAL DEVOLUTIONS
+REPRINTS
+MALL SALES FIRST YEAR
+TOTAL SELLING POINTS FIRST YEAR
+UNITS DISTRIBUTED IN FIRST EDITION
+PRINT-RUN
+NUMBER OF REPRINTS
+MALLS DEVOLUTIONS
+REST OF SELLING POINTS FIRST YEAR
+REST OF SALES
+DELEGATES SELLING POINTS
+REST OF DEVOLUTIONS
+DELEGATES SELLING POINTS FIRST YEAR
+POSITIVE SALE MARKET
+REST OF DISTRIBUTED FIRST YEAR
+REST OF SELLING POINTS
+TOTAL DEVOLUTIONS FIRT YEAR
+DELEGATES DEVOLUTIONS
 \end{verbatim} \end{minipage}     &
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-venta_grandes_superficies
-colocado1anio_total
-puntos_vta_total
-colocado_grandes_superficies
-colocado1anio_delegados
-puntos_vta_grandes_superficies
-venta1anio_total
-entorno_venta_medio
-semanas_venta
-colocado_delegados
-autor
-venta1anio_delegados
-obsequios
-devolucion1anio_grandes_superficies
-venta_delegados
-colocado_resto
-devolucion1anio_delegados
-colocado_total
-devolucion1anio_resto
-pvp
-venta_total (output)
+MALLS SALES
+TOTAL DISTRIBUTED FIRST YEAR
+TOTAL SELLING POINTS
+MALLS DISTRIBUTED
+DELEGATES DISTRIBUTED FIRST YEAR
+MALLS SELLING POINTS
+TOTAL SALES FIRST YEAR
+MEDIUM SALE MARKET
+WEEKS ON SALE
+DELEGATES DISTRIBUTED
+AUTHOR
+DELEGATES SALES FIRST YEAR
+GIFTS
+MALLS DEVOLUTIONS FIRST YEAR
+DELEGATES SALES
+REST OF DISTRIBUTED
+DELEGATES DEVOLUTIONS FIRST YEAR
+TOTAL DISTRIBUTED
+REST OF DEVOLUTIONS FIRST YEAR
+RETAIL PRICE
+TOTAL SALES (output)
 \end{verbatim} \end{minipage}    \\

### 2015-08-18 paper.tex
traducidos los nombres de variables en el .tex

@@
   % New soft drink product
+In \cite{ChingChin2010}, a decision-support system for new product sales forecasting 
+is proposed to solve three real-world sales forecasting problems involving new tea, 
+cosmetic, and soft drink products taking into account quantitative variables. 
+In this study, it is assumed that products are classified based on their sales 
+pattern so that products in the same class would have similar sales pattern.
+However, as the authors state, proposed system can not deal with qualitative 
+date related to the products, and even more real-world cases, such as consumer 
+electronics and fashion products, should be examined, as these industries 
+introduce new products every season.
 
@@
   % sales forecasting in printed circuit board industry.
+In those cases where there is historical data available, classical time series 
+forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
+model integrating K-mean and fuzzy neural networks to forecast the future sales 
+of a printed circuit board is proposed.
 
@@
         %hala, vuelta la burra al trigo - JJ
-        %[Pedro] ea, lo quito
+        %[Pedro] ea, lo quito   :)
 There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.
@@
 \hline
-
-  %[Pedro] me falta poner ya los nombres traducidos (y usarlos para los SOM)
 
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-devolucion_total
-reimpresiones
-puntos_vta1anio_total
-ejemplares_distribuidos_en_novedad
-numero_reimpresiones
-devolucion1anio_total
-colocado1anio_total
-puntos_vta_total
-semanas_venta
-colocado_total
-pvp
-tirada
-venta_total (output)
+TOTAL DEVOLUTIONS
+REPRINTS
+TOTAL SELLING POINTS FIRST YEAR
+UNITS DISTRIBUTED IN FIRST EDITION
+NUMBER OF REPRINTS
+TOTAL DEVOLUTIONS FIRT YEAR
+TOTAL DISTRIBUTED FIRST YEAR
+TOTAL SELLING POINTS
+WEEKS ON SALE
+TOTAL DISTRIBUTED
+RETAIL PRICE
+PRINT-RUN
+TOTAL SALES (output)
 \end{verbatim} \end{minipage}     \\
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-ejemplares_distribuidos_en_novedad
-puntos_vta_total
-colocado_total
-pvp
-materia
-editorial
-venta_total (output)
+UNITS DISTRIBUTED IN FIRST EDITION
+TOTAL SELLING POINTS
+TOTAL DISTRIBUTED
+RETAIL PRICE
+SUBJECT-MATTER
+EDITORIAL
+TOTAL SALES (output)
 \end{verbatim} \end{minipage}     \\

### 2015-08-19 paper.tex
traducido el texto en español + arreglada una traducción en el archivo de traduccion de nombres de variables

@@
 % Publishing roll? ¿Qué es? - JJ
-In this paper, which works with data on published books for several years in Spain, we
-first apply a data visualization and preprocessing strategy to find
+In this paper, which works with data on published books for several years in 
+Spain, we first apply a data visualization and preprocessing strategy to find
 out what are the relevant variables in the prediction of sales, and
@@
 
-With this in mind, i this paper a data visualization and preprocessing strategy to find
-out what are the relevant variables describing a book in the prediction 
+With this in mind, i this paper a data visualization and preprocessing strategy 
+to find out what are the relevant variables describing a book in the prediction 
 of book sales is proposed; then several standard data mining models 
@@
 presented.  
-Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
-Finally, conclusions and future work are presented in Section
+Section \ref{sec:experiments} reports and analyzes the obtained results with a 
+real data set. Finally, conclusions and future work are presented in Section
 \ref{sec:conclusionsAndFutureWork}.
@@
 In the last years, different analysis and forecasting methods, such as
-regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001} 
+regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} 
+or fuzzy systems \cite{Mastorocostas2001} 
 have been applied in different industry sectors, i.e. electricity
@@
 relationships between on-line information and book sales.
-Specifically, authors propose using the number of blog references as an indicator of book sales.
+Specifically, authors propose using the number of blog references as an indicator 
+of book sales.
 Different sales patterns are observed by analyzing data obtained.
 In any case, in this research, historical data from published books is used, 
-and the proposed methodology can not be usable in the problem of unpublished-books sales prediction.
+and the proposed methodology can not be usable in the problem of unpublished-books 
+sales prediction.
 
@@
 Complexity of this problem is due to the lack of historical data, short lifetime 
-of the large number of items, and due to the influence of variables such as promotions, 
-fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.
+of the large number of items, and due to the influence of variables such as 
+promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.
 
@@
   % New soft drink product
-In \cite{ChingChin2010}, a decision-support system for new product sales forecasting 
-is proposed to solve three real-world sales forecasting problems involving new tea, 
-cosmetic, and soft drink products taking into account quantitative variables. 
+In \cite{ChingChin2010}, a decision-support system for new product sales 
+forecasting is proposed to solve three real-world sales forecasting problems 
+involving new tea, cosmetic, and soft drink products taking into account 
+quantitative variables. 
 In this study, it is assumed that products are classified based on their sales 
@@
         %[Pedro] ea, lo quito   :)
-There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.
+There are several difficulties inherent to the new book sales forecasting, 
+such as dealing with limited data, finding adequate forecasting methods, and 
+selecting the best method to use \cite{ChingChin2010}.
 
-The main issue of this paper is to compute forecasting of the sales for new unpublished-books, for which no historical data is available.
-Thus, this paper faces the new book publishing problem using different prediction methods and using as inputs the historical sales data related to other yet published books, and some descriptive variables relative to the new unpublished-book.
+The main issue of this paper is to compute forecasting of the sales for 
+new unpublished-books, for which no historical data is available.
+Thus, this paper faces the new book publishing problem using different 
+prediction methods and using as inputs the historical sales data related 
+to other yet published books, and some descriptive variables relative to 
+the new unpublished-book.
 
-En el caso de libros ya publicados, se dispone de datos históricos que ayudan a la generación de modelos predictivos. 
-Sin embargo, en el caso de nuevos libros no hay datos históricos que ayuden a definir patrones, y sólo ciertos datos descriptivos están disponibles, por lo que no todos los métodos de predicción se pueden utilizar \cite{Madsen2008,ChernWSF15}.
+In the case of already published books, available historical data might help 
+to generate predictive models.
+However, in the case of new books there is no historical data to define patterns, 
+and only some descriptive data about the new book is available.
+In these cases not any forecasting method can be used\cite{Madsen2008,ChernWSF15}.
 
-An additional issue is the dificulty to compare our model with classical forecasting methods, such as time series prediction methods, since books do not have specific sales time series.
+An additional issue is the dificulty to compare our model with classical 
+forecasting methods, such as time series prediction methods, since books 
+do not have specific sales time series.
 
-A lo largo de esta investigación se colaboró con la empresa Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}, una compañía que ofrece sistemas de gestión y servicios para librerías, editoriales y distribuidoras.
+Throughout this research we collaborated with the company Trevenque Editorial\footnote{{\tt http://editorial.trevenque.es}}, 
+a company that provides management systems and services for libraries, publishers 
+and distributors.
 
-La empresa Trevenque, cuyo experto asesoró esta investigación, facilitó un conjunto de datos inicial consistente en 3159 libros. 
-En este conjunto, para cada libro se incluye información descriptiva del libro, como son el precio, lugares donde se han puesto a la venta, materia, editorial, ventas, devoluciones, entre otros datos.
-Table \ref{tabla:paramsOrig50} shows the original set of parameters describing each book.
+Trevenque company, whose expert manager advised this research, provided 
+the initial data set consisting of 3159 books.
+In this data set, descriptive information for each book includes price, 
+selling points, matter, publisher, sales, returns, among other information.
+Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
+each book.
 
@@
 RETAIL PRICE
-SUBJECT-MATTER1
-SUBJECT-MATTER2
-SUBJECT-MATTER3
+MATTER1
+MATTER2
+MATTER3
 EDITORIAL
@@
 
-En el problema de la predicción de ventas de nuevos libros afectan diversas variables propias del libro en cuestión, como por ejemplo el autor, el precio, la materia o la editorial.
+In this prediction problem, several variables related to the own book affect 
+the forecasts, such as author, price, matter or publisher.
 
-Sin embargo, existen otras variables externas que también afectan a las ventas de un nuevo libro.
-Se trata de cuestiones como la estacionalidad, modas o promociones.
-Estas otras variables no medibles y que los métodos de predicción clásicos no pueden procesar y que un experto debe tener en cuenta modificando la predicción ofrecida por el método automático. 
-Las empresas editoriales suelen finalmente definir reglas o índices para ajustar subjetivamente los resultados de predicción.
+However, there are other external variables that also affect the sales of 
+a new book, such as those related to seasonality, trends or promotions, 
+that classical prediction methods can not deal with.
+However, an expert can consider them to modify the forecast obtained by 
+the automatic method. Even publishing companies tend to define rules or 
+indexes to subjectively adjust the results of prediction based on external data.
 
@@
 
-Hay varias dificultades inherentes al problema de la predicción de ventas de nuevos productos: la limitación en la cantidad de datos disponibles, la aplicación de los diferentes métodos y la elección del más adecuado de ellos.
-
-Además, no existe una metodología estándar para resolver el problema general de la predicción de ventas. 
-Habitualmente es necesario un análisis previo de los datos para eliminar las variables que describen el producto y que no aportan información útil para realizar el proceso de predicción.
+There are several issues inherent to the problem of predicting sales of new 
+products: the limitation on the amount of data available, the application of 
+different methods and choose the most suitable of them.
+In addition, there is no a standard methodology to solve the general problem 
+of sales forecasting.
+Usually, a preliminary analysis of the data is carried out to eliminate those 
+variables that describe the product but do not provide useful information during 
+the prediction process.
 
@@
   \epsfig{file=stages.eps,width=7cm}
-\caption{\small{Three main stages in this research: data analysis, (2) forecasting methods testing, and (3) subjectively adjusting the obtained results.}}
+\caption{\small{Three main stages in this research: data analysis, (2) forecasting 
+methods testing, and (3) subjectively adjusting the obtained results.}}
 \label{fig:stages}
@@
 
-Thus, in this study there are three main stages (see Figure \ref{fig:stages} for details): 
+Thus, in this study there are three main stages (see Figure \ref{fig:stages} 
+for details): 
 \begin{itemize}
-  \item  First, after the editorial company has provided the raw data, taken directly from its database, a selection variables process is carried out.
-In this stage, an expert sales manager, using the information obtained analyzing the SOM cluster method results, removes some unrelated variables and selects the best variables to be considered in the forecasted model.
-This task may help to identify leading indicators to be used by the forecasting methods in order to improve the accuracy of future forecasts.
 
-  \item  Then, several forecasting methods has to be tested. In this stage different forecasting methods are used to obtain sales forecasts from the data provided.
+  \item  First, after the editorial company has provided the raw data, taken 
+  directly from its database, a selection variables process is carried out. 
+  In this stage, an expert sales manager, using the information obtained 
+  analyzing the SOM cluster method results, removes some unrelated variables 
+  and selects the best variables to be considered in the forecasted model. 
+  This task may help to identify leading indicators to be used by the 
+  forecasting methods in order to improve the accuracy of future forecasts.
 
-  \item  Finally, in some cases, it is necessary a third stage where experienced managers adjust subjectively the results obtained using the forecasting methods.
-They might manually adjust the forecasting results taking into account their knowledge in industry experience and their perception about trends.
+  \item  Then, several forecasting methods has to be tested. In this stage 
+  different forecasting methods are used to obtain sales forecasts from the 
+  data provided.
+
+  \item  Finally, in some cases, it is necessary a third stage where experienced 
+  managers adjust subjectively the results obtained using the forecasting methods. 
+  They might manually adjust the forecasting results taking into account their 
+  knowledge in industry experience and their perception about trends.
 
@@
 Specifically, in order to compute the forecasting errors of the different methods, 
-Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) 
-and Root relative squared error (RRSE) have been selected:
+Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
+error (RAE) and Root relative squared error (RRSE) have been selected:
 
@@
         \begin{equation}\label{eq:RRSE}
-            % RRSE = \frac{ \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 } }{ \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_{i-1} - o_i)}^2 } }
             RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(p_{i-1} - o_i)}^2 }  }
@@
 \textbf{FALTA EXPLICAR EN UN PAR DE PÁRRAFOS QUÉ ES EL SOM DE KOHONEN.} 
-This method is usually applied to analyze data as similar items tend to be mapped close together, while those items dissimilar, are mapped apart.
-Also, the SOM graph represents and highlight very clearly those regions (clusters) with high training sample concentration and fewer where the samples are scarce.
+This method is usually applied to analyze data as similar items tend to be 
+mapped close together, while those items dissimilar, are mapped apart.
+Also, the SOM graph represents and highlight very clearly those regions (clusters) 
+with high training sample concentration and fewer where the samples are scarce.
 
-As stated in Section \ref{sec:problem}, an expert sales manager colaborated in this research in the stage of data analysis.
-Thus, the process was as follows:
+As stated in Section \ref{sec:problem}, an expert sales manager colaborated in 
+this research in the stage of data analysis. Thus, the process was as follows:
 \begin{itemize}
-  \item First, the expert removed superfluous variables, and dimensionality was reduced from 50 to 43 inputs.
-  \item Then, the expert, using his knowledge and the information obtained analyzing the SOM results, removed some inputs, reducing the number of variables describing a book from 43 to 13.
-  \item The company asked to include the information about \emph{editorial} and \emph{materia}.
-Thus, in a new iteration, taking into account the expert's advice and the información obtained analyzing the SOM results, the number of inputs was decreased to 7.
-  \item In a third step, several forecasting methods were used on the obtained dataset, and the best was choosen to obtain an accurate predicting model.
-  \item Finally, some information about the new book, such as \emph{author}, although not included in the obtained models, was taken into account by the expert sales manager to modify the forecasted results.
+  \item First, the expert removed superfluous variables, and dimensionality was 
+  reduced from 50 to 43 inputs.
+  \item Then, the expert, using his knowledge and the information obtained 
+  analyzing the SOM results, removed some inputs, reducing the number of 
+  variables describing a book from 43 to 13.
+  \item The company asked to include the information about \emph{editorial} 
+  and \emph{materia}. Thus, in a new iteration, taking into account the expert's 
+  advice and the información obtained analyzing the SOM results, the number of 
+  inputs was decreased to 7.
+  \item In a third step, several forecasting methods were used on the obtained 
+  dataset, and the best was choosen to obtain an accurate predicting model.
+  \item Finally, some information about the new book, such as \emph{author}, 
+  although not included in the obtained models, was taken into account by 
+  the expert sales manager to modify the forecasted results. 
 \end{itemize}
@@
 
-Más concretamente, en un primer paso, el experto analizó las 50 variables de entrada que describen cada libro para eliminar algunas que estimó como suplerfuas.
-Table \ref{tabla:params43} shows the set of variables describing a book (43 total inputs) that the expert manager determined as non-superfluous or non-redundant.
+More specifically, in a first step, the expert analyzed the 50 input variables 
+describing each book to remove those that were suplerfuas.
+Table \ref{tabla:params43} shows the set of variables describing a book 
+(43 total inputs) that the expert manager determined as non-superfluous or 
+non-redundant.
 
 \begin{table}[!h]
-\caption{Variables describing a book (43 total inputs), after the expert manager analized the original dataset provided by the company Trevenque to remove some inputs.}
+\caption{Variables describing a book (43 total inputs), after the expert 
+manager analized the original dataset provided by the company Trevenque to 
+remove some inputs.}
 \label{tabla:params43}
@@
 
-Then, after analizyng the original dataset using the SOM to select the best variables to be considered, and taking into account the knowledge of the company experienced manager, 13 inputs were considered.
-Figure \ref{fig:som43} shows the initial analisys of dataset using the total of 43 descriptive inputs per book.
-Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.
+Then, after analizyng the original dataset using the SOM to select the best 
+variables to be considered, and taking into account the knowledge of the company 
+experienced manager, 13 inputs were considered. 
+Figure \ref{fig:som43} shows the initial analisys of dataset using the total 
+of 43 descriptive inputs per book.
+Table \ref{tabla:params13} shows the set of variables describing a book after 
+the second analisys.
 	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
@@
 \end{tabular}
-\caption{\small{Initial data analysis, using 43 descriptive variables per book, using SOM.}}
+\caption{\small{Initial data analysis, using 43 descriptive variables per book, 
+using SOM.}}
 	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
@@
 	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
-        % Sería más bien exploratory data analysis o data visualization. Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
+        % Sería más bien exploratory data analysis o data visualization. 
+        % Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
 \label{fig:som43}
@@
 recommendations, 7 inputs were considered; specifically, variables
-\emph{editorial} and \emph{materia} were included, while
-\emph{devolucion\_total, reimpresiones, puntos\_vta1anio\_total,
-  numero\_reimpresiones, devolucion1anio\_total, colocado1anio\_total,
-  semanas\_venta, tirada} were discarded.  
+\emph{EDITORIAL} and \emph{MATTER} were included, while
+\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
+  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
+  WEEKS ON SALE, PRINT-RUN} were discarded.  
 	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
@@
 	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
-Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on the total of 13 descriptive inputs per book.
-This, along with the expert manager knowledge determined the final 7 inputs to be considered.
-Table \ref{tabla:params7} shows the final set of variables describing a book, taking into account the company experienced manager knowledge.
+Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on 
+the total of 13 descriptive inputs per book.
+This, along with the expert manager knowledge determined the final 7 inputs 
+to be considered.
+Table \ref{tabla:params7} shows the final set of variables describing a book, 
+taking into account the company experienced manager knowledge.
 
@@
 \begin{table}[!h]
-\caption{Final set of variables describing a book, taking into account the company experienced manager knowledge, to be considered to solve the sales forecasting problem.}
+\caption{Final set of variables describing a book, taking into account the company 
+experienced manager knowledge, to be considered to solve the sales forecasting problem.}
 \label{tabla:params7}
@@
 RETAIL PRICE
-SUBJECT-MATTER
+MATTER
 EDITORIAL
@@
 
-Como se ha comentado anteriormente, existen diferentes métodos de predicción disponibles en la bibliografía, cada uno con una serie de parámetros diferente que pueden influir en los resultados.
+As previously stated, there are many prediction methods available in the 
+literature, each one with a different parameter set that may affect the 
+obtained results.
 
-Sin embargo, dado que en el caso de nuevos libros sólo ciertos datos descriptivos están disponibles (frente a datos históricos de ventas de libros ya publicados), no todos los métodos predictivos se pueden usar en este problema concreto.
+However, as in the case of new books only some descriptive data is available 
+(compared to those cases in which historical data on sales of published books 
+is available), not all forecasting methods can be used in this specific problem.
 
-Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
+Thus, in this research five forecasting methods, based on the literature 
+review in the introduction 
+\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
 Well known forecasting methods implemented in the Weka tool
@@
 experiments and even to solve similar sales prediction problems using
-these methods. % eliminado el pie de página, es mejor usar referencias
-               % - JJ
+these methods. % eliminado el pie de página, es mejor usar referencias - JJ
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
- \item M5 Model trees and rules: The original algorithm M5 was proposed by Quinlan \cite{Quinlan1992} and afterwards Wang \cite{Wang1997} made improvements.
+ \item M5 Model trees and rules: The original algorithm M5 was proposed by 
+ Quinlan \cite{Quinlan1992} and afterwards Wang \cite{Wang1997} made improvements.
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
- \item Support Vector Machine for Regression (SVM): This algorithm was proposed by Shevade et al \cite{Shevade1999}.
+ \item Support Vector Machine for Regression (SVM): This algorithm was proposed 
+ by Shevade et al \cite{Shevade1999}.
 
@@
 
-The objective is finding the most appropriate forecasting method that minimizes the error between the forecast and the actual sales for each new book published.
+The objective is finding the most appropriate forecasting method that minimizes 
+the error between the forecast and the actual sales for each new book published.
 
@@
 
-Una vez que se han determinado los métodos a utilizar y los parámetros de ejecución, se aplicarán a los conjuntos de datos para obtener los modelos de predicción y posteriormente se comprobará su bondad ante datos no vistos previamente.
+Once  the methods to be applied have determined as well as their execution 
+parameters, they must be applied to data sets to obtain the prediction models 
+for each one. Later on, the models ability must be validated on non-previously 
+seen data.
 
@@
   % en algunos calculan muchos más, pero estos son los más usados. 
-Obtained results using the different forecasting methods on the dataset with 13 variables per book can be shown in Table \ref{tabla:results13}:
+Obtained results using the different forecasting methods on the dataset with 13 
+variables per book can be shown in Table \ref{tabla:results13}:
 \begin{table*}[!h]
@@
   % faltan AUN los de MLP
-
-  Obtained results using the different forecasting methods on the dataset with 7 variables per book can be shown in Table \ref{tabla:results7}:
+Obtained results using the different forecasting methods on the dataset with 7 
+variables per book can be shown in Table \ref{tabla:results7}:
 \begin{table*}[!h]
@@
 \end{center}
-\caption{\small{Results (errors and time) obtained using the different forecasting methods on the dataset with 7 variables per book.}}
+\caption{\small{Results (errors and time) obtained using the different 
+forecasting methods on the dataset with 7 variables per book.}}
 \label{tabla:results7}

### 2015-08-19 paper.tex
un detalle en las tablas de datos: RAE y RRSE son porcentajes
completada la sección de Conclusiones

@@
 % Publishing roll? ¿Qué es? - JJ
+%[Pedro] en la traducción de términos Antonio propone traducirlo como "print run". Lo pongo así.
 In this paper, which works with data on published books for several years in 
@@
 then use standard data mining software to predict sales, and from them
-deduce print roll, based on those variables. Our work discovers which
+deduce print-run, based on those variables. Our work discovers which
 are the most relevant variables when predicting sales, and is
@@
 An example is the optimization of sales \cite{Mattila2002} by
-improving profit margins by selling the whole publishing roll.  
+improving profit margins by selling the whole print-run. %publishing roll.  
 % [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...
+% Antonio propone traducirlo como "print run". Lo pongo así.
 
@@
 
-With this in mind, i this paper a data visualization and preprocessing strategy 
+With this in mind, in this paper a data visualization and preprocessing strategy 
 to find out what are the relevant variables describing a book in the prediction 
@@
 for sales forecasting are evaluated so a publishing company 
-can deduce and optimize print roll.
+can deduce and optimize print-run.
 
@@
 using data visualization tools and then, standard data mining software 
-to predict sales is used to deduce print roll.
+to predict sales is used to deduce print-run.
 In addition, since publishers need models to explain obtained predictions, 
@@
 \textbf{FALTA EXPLICAR EN UN PAR DE PÁRRAFOS QUÉ ES EL SOM DE KOHONEN.}
+
 This method is usually applied to analyze data as similar items tend to be 
@@
 \hline 
- Method 	& Time (sec.) 	  & MAE 			& RMSE 		& RAE 		& RRSE 		\\
+ Method 	& Time (sec.) 	  & MAE 			& RMSE 		& RAE (\%)		& RRSE (\%) 		\\
 \hline
@@
   %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
-  % faltan AUN los de MLP
+  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
 Obtained results using the different forecasting methods on the dataset with 7 
@@
 \hline 
- Method   & Time (sec.)     & MAE       & RMSE    & RAE     & RRSE      \\
+ Method   & Time (sec.)     & MAE       & RMSE    & RAE (\%)     & RRSE (\%)      \\
 \hline
-  MP5     & 7.39 $\pm$ 1.75   & 117.78   & 260.05  & 18.51   & 17.00  \\
+  MP5     & 7.77 $\pm$ 1.15   & 117.78   & 260.05  & 18.51   & 17.00  \\
 \hline
-  LR      & 40.59 $\pm$ 12.94 & 120.29  & 252.91  & 18.91   & 16.54   \\
+  LR      & 41.72 $\pm$ 8.41 & 120.29  & 252.91  & 18.91   & 16.54   \\
 \hline
-  SVM     & 1547.91 $\pm$ 365.55 & 109.30  & 251.16   & 17.18     & 16.42   \\
+  SVM     & 1652.20 $\pm$ 283.50 & 109.30  & 251.16   & 17.18     & 16.42   \\
 \hline
-  KNN     & 0.02 $\pm$ 0.01   & 293.98  & 1071.52  & 46.21   & 70.06   \\
+  KNN     & 0.03 $\pm$ 0.01   & 293.98  & 1071.52  & 46.21   & 70.06   \\
 \hline
-  MLP     & 3265.71 $\pm$ 813.37   & 992.97 $\pm$ 0   & 1755.62 $\pm$ 0  & 156.07 $\pm$ 0   & 114.79 $\pm$ 0   \\
+  MLP     & 3646.76 $\pm$ 64.83   & 705.69 $\pm$ 77.22   & 1608.69 $\pm$ 42.96  & 110.92 $\pm$ 12.14   & 105.18 $\pm$ 2.81   \\
 \hline
@@
 
-La predicción de ventas en la industria editorial es un problema muy challenging durante los últimos años.
+In this paper, the problem of how many books should be printed 
+when a new book is published is faced using several data-mining and
+forecasting methods.
 
-Para resolver este problmea, diferentes técnicas de datamining pueden ser muy útiles, al no haber datos históricos disponibles de las ventas.
+This is a very challenging problem in this industry, because printing a higher 
+number of volumnes than those finally sold will lead to losses, 
+while printing an adequate number of copies will optimize sales and company earnings.
+In addition, there are several difficulties inherent to the new book sales forecasting, 
+such as dealing with limited data, finding adequate forecasting methods, and 
+selecting the best method to use.
 
-La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
-En este sentido, los árboles de decisión resultaron ser un modelo muy adecuado debido a la facilidad para explicar cómo se obtiene dicha predicción a partir de las variables descriptivas del nuevo libro.
-Esto, frente a los modelos tipo black-box como las ANN fue determinante desde el punto de vista de las necesidades de los expertos y la empresa.
+%La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
+A data set consisting of 3159 books provided by the Spanish 
+publishing company Trevenque Editorial has been used.
 
-This research provides a new direction in the sales forecasting area using different soft-computing techniques.
-Moreover, proposed method could be implemented, not only in the editorial industry, but also in other domains where the specificity of products is similar, and might be of interest to other academic researches and industrial practitioners.
+In this paper, a data visualization method has been used to find out what are 
+the relevant variables describing a book in the prediction of book sales.
+Then, several standard data mining models for sales forecasting have been used 
+to forecast new book sales, and from them deduce print-run, based on those variables.
+
+The most relevant variables when predicting sales have been determined, 
+while unrelated or superfluous ones have been removed, 
+and sales predictions have been obtained using five different forecasting 
+standard methods.
+Proposed method was validated by the company and incorporated in a business 
+intelligence tool for publishing houses.
+
+In this sense, the decision trees proved to be a suitable model because of the ease 
+to explain how the prediction is obtained from the variables that describe the new book. 
+This, compared to the black-box models such as the ANN was decisive from the point 
+of view of the needs of experts and the company.
+
+This research provides a new direction in the sales forecasting area using 
+different soft-computing techniques.
+Moreover, proposed method could be implemented, not only in the editorial 
+industry, but also in other domains where the specificity of products is similar, 
+and might be of interest to other academic researches and industrial practitioners.
 
@@
 
-Como trabajos futuros sería interesante comparar las predicciones de los modelos obtenidos con otros basados en métodos de soft-computing, como genetic programming o fuzzy logic.
+As future work, it would be interesting comparing the obtained forecasting results 
+with other methods based on soft-computing, such as genetic programming or fuzzy logic.
 
-Por otro lado, puesto que hay algunas características que pueden afectar a la venta de productos de forma significativa, otra forma de mejorar las predicciones de ventas podría ser realizar un estudio en profundidad del efecto de la aplicación de descuentos y promociones.
+Furthermore, since there are some characteristics that may affect product sales 
+significantly, another way to improve sales predictions could be making a thorough 
+study of the effect of the application of discounts and promotions.
 
@@
 This work has been supported in part by PreTEL (PRM Consultores - Trevenque),
-SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and
-TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
+SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 
+and TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
 SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14

### 2015-08-19 paper.tex
traducido al inglés completamente (y a unos 80 caracteres por línea)

@@
 
-Las predicciones suelen basarse en datos históricos de las cuales extraer series temporales y patrones. 
-Sin embargo, en el caso de nuevos productos, como es el caso de la edición de nuevos libros, es complicado observar patrones pasados ya que no hay disponibles datos históricos de las ventas \cite{ChingChin2010}.
+In general, historical data is used to make time series, and from them extracting 
+common patterns and obtaining accurate predictions.
+However, in the case of new products, such as the issue of new books, past patterns 
+is difficult to observe as there is no available historical sales data \cite{ChingChin2010}.
 
-Además, de todas las variables descriptivas de un nuevo libro, algunas influirán en las predicciones aportando información, mientras que otras pueden resultar superfluas e incluso redundantes.
+In addition, among the variables describing a new book, some may affect 
+predictions (those variables provide information), while others may not be 
+necessary and even redundant.
 
-Así pues, a partir del conjunto inicial de variables, se aplicó el SOM \cite{kohonen1998} con el objetivo de reducir la dimensionalidad de los datos de entrada y elegir un conjunto de variables adecuado.
+Thus, from the initial set of variables, the SOM \cite{kohonen1998} was applied 
+in order to reduce the dimensionality of the input data and to choose an 
+appropriate set of variables.
 

### 2015-08-20 paper.tex
añado la descripción de los 5 métodos utilizados. Closes #10

@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
- \item M5 Model trees and rules: The original algorithm M5 was proposed by 
- Quinlan \cite{Quinlan1992} and afterwards Wang \cite{Wang1997} made improvements.
+ \item \emph{M5 Model trees}: 
+A decision tree consists of answer-nodes, that indicate a class, and decision-nodes, 
+that contain an attribute name and branches to other sub-decision trees.
+Building a decision tree can be done using many algorithms, i.e. ID3 and C4.5 \cite{Quinlan1986}.
+However, in order to use this model in regression problems, some authors have 
+extended the model using methods such as the M5 model tree \cite{Quinlan1986,Quinlan1992,Wang1997,WittenFrank2000}, 
+by combining a conventional decision tree and generating linear regression functions at the nodes.
+
+The construction of a model tree is similar to that of classical decision 
+trees \cite{Solomatine2004}:
+The process breaks the input space of the training data through decision points 
+(nodes) to assign a linear model suitable for that sub-area of the input space. 
+This process may lead to a complex model tree.
+
+Model tree models can learn and tackle tasks with high dimensionality (up to 
+hundreds of attributes) and generate reproducible and comprehensible representations, 
+what makes them potentially more successful in the eyes of decision makers.
+
+The final model consists of the collection of linear sub-models that brings the 
+required non-linearity in dealing with the regression problem
+and both the predicted values at the answer-nodes along with the path from the 
+root to that node is given as a result.
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
- \item Linear Regression
+ \item \emph{Linear Regression}:
+ Linear regression \cite{Cohen2003,Yan2009,Rencher2102} method models the 
+relationship between a scalar dependent variable (outcome) and several independent 
+variables (predictor) over the range of values in the data set. 
+In this statistical technique, data is modeled using linear functions to estimate 
+unknown model parameters, examining the linear correlations between independent 
+and dependent variables.
+
+This method of regression provides an adequate and interpretable description of 
+how the input affects the output as it models the dependent variable as a linear 
+function of the independent variables. Moreover, the linear relation can be 
+solved using the least squares method, that minimizes the error between the 
+actual data and the regression line \cite{McClendon2015}.
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
- \item Support Vector Machine for Regression (SVM): This algorithm was proposed 
- by Shevade et al \cite{Shevade1999}.
+ \item \emph{Support Vector Machine for Regression (SVM)}:
+Support vector machine (SVM) \cite{Cortes1995,Shevade1999} method is based on  
+statistical learning theory and has succesfully used in classification and  
+regression problems \cite{Cao2003,Jari2008}.
+
+In classification problems the algorithm searchs for an optimal hyperplane 
+that separates two classes, maximizing the margin between two classes. 
+In the case of regression the algorithm chooses a hyperplane close to as many 
+of the data points as possible, minimizing the sum of the distances from 
+the data points to the hyperplane. 
+In both cases, the hyperplane is defined by a subset of training set samples 
+(called support vectors).
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
- \item K-nearest neighbours classifier (IBk): \cite{Aha1991}
+ \item \emph{k-Nearest Neighbours (kNN)}: 
+The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
+wich the unknown instances are classified by relating them to the known 
+instances using a distance measurement/function (Euclidean, Minkowsky or minimax).
+
+The main idea behind the algorithm is that two instances far enough in the space, 
+taking into account the distance function, are less likely to belong to the 
+same class than two closely situated instances.
+
+The classification algorithm locates the nearest neighbour in instance space and 
+asigns the class of that neighbour to the unknown instance.
+In order to improve the robustness of the model, several neighbours can be 
+located, assigning the resulting class to an unclassified vector using the 
+closest k vectors found in the training set by majority vote.
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
- \item Multilayer Perceptron
+ \item \emph{Multilayer Perceptron}:
+A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
+artificial neural network model that maps the input data onto an appropriate output. 
+It is an artificial neural network generally used for classification or 
+approximation problems.
+
+This model is a generalization of the standard linear perceptron that uses several 
+layers of nodes (called neurons) and that is able to solve linearly inseparable 
+problems \cite{SteinwenderBitzer2003}.
+Each neuron consists of a linear combination of weighted inputs which is passed 
+though a non-linear activation function to produce its output.
+
+This kind of artificial neural network is trained using a supervised learning 
+technique called back-propagation.
+This training method was developed independly by Werbos \cite{Werbos1974}, 
+Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
+in updating the weights of the output layer neurons once the erroneous output 
+has been obtained, and then, propagating the succesive weight layers back to 
+the input layer.
+
+A key issue when designing an MLP is the number of hidden layers of neurons.
+Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
+create classifying regions of any kind. This result was then confirmed in later 
+works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
 

### 2015-08-21 paper.tex
Descritos los 5 métodos utilizados. Closes #4
Traducido completamente (ya no queda texto en español). Closes #8
arreglos menores...

@@
 
-Throughout this research we collaborated with the company Trevenque Editorial\footnote{{\tt http://editorial.trevenque.es}}, 
+Throughout this research we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
 a company that provides management systems and services for libraries, publishers 
@@
 The objective is finding the most appropriate forecasting method that minimizes 
-the error between the forecast and the actual sales for each new book published.
+the error between the obtained forecast and the actual sales for each new book 
+published.
 
@@
 
-Once  the methods to be applied have determined as well as their execution 
-parameters, they must be applied to data sets to obtain the prediction models 
-for each one. Later on, the models ability must be validated on non-previously 
-seen data.
-
-\textbf{TODO:} % FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS
+Once the methods to be applied have been chosen, they must be applied to data sets 
+to obtain the prediction models for each one. 
+Later on, the models ability must be validated on non-previously seen data.
+
+\textbf{TODO: FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS}
 
@@
 \end{table*}
+
+\textbf{TODO: FALTA COMENTAR LOS RESULTADOS OBTENIDOS CON LOS 5 MÉTODOS.}
 

### 2015-08-21 paper.tex
comenzando la sección Experiments and Results

@@
 Later on, the models ability must be validated on non-previously seen data.
-
-\textbf{TODO: FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS}
+Specifically, instead of using the conventional validation strategy based on 
+using a training set and later on a testing set (unknown data against which 
+the model must be tested), a cross-validation technique \cite{Geisser1993,Kohavi1995,Devijver1982} 
+has been used to estimate how accurately the predictive model will perform in 
+practice. %, limiting at the same time the overfitting problem.
 
@@
 
-% Mean absolute error MAE
-% Root mean squared error RMSE
-% Relative absolute error RAE
-% Root relative squared error RRSE
-
-  %[pedro] ya están todos los resultados de tabla:results13 para MP5, LR, KNN, SVM y MLP
-
+\textbf{TODO: FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS}
+
+% Comentar que:
+% - se ha usado la implementación de estos 5 métodos del paquete WEKA
+% - se han realizado 30 ejecuciones con cada método
+% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU @ 3.00GHz (4 cores), 16 GB RAM
+% - 
+% - 
+% Preparar tests estadísticos para ver si hay diferencias en los errores entre métodos.
+% - 
+% -
+
+% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
   % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
@@
 \textbf{TODO: FALTA COMENTAR LOS RESULTADOS OBTENIDOS CON LOS 5 MÉTODOS.}
+
+% - indicar qué método da mejores resultados
+% - indicar qué método es tipo "caja-negra" y cuáles ofrecen modelos "explicables"
+% - 
+% -
 

### 2015-08-21 paper.tex
completando el estado del arte

@@
   % sales forecasting in printed circuit board industry.
-In those cases where there is historical data available, classical time series 
+In those cases where historical data is available, classical time series 
 forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
@@
 of a printed circuit board is proposed.
+A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
+historical data along online reviews, reviewer characteristics and review 
+influences to understand how electronic word-of-mouth affects product sales. 
+Proposed method is suitable in those sales forecasting problems with abundant 
+online reviews and historical data.
 

### 2015-08-21 paper.tex
completando el estado del arte
comentando los resultados obtenidos con cada método, tanto en cuanto al tiempo como en cuanto al error

@@
 A company that intends to release a new product has a high risk due to
-the complexity of the production and distribution processes. A newly
+the complexity of the production and distribution processes. 
 % tienes que enmarcar el problema. Se trata de productos culturales
@@
 % discos, no sé si alguna cosa más. - JJ
-launched product is also new to the company, and sales forecasts can
+A newly launched product is also new to the company, and sales forecasts can
 only be based on the experience of similar products. 
@@
 extended the model using methods such as the M5 model tree \cite{Quinlan1986,Quinlan1992,Wang1997,WittenFrank2000}, 
-by combining a conventional decision tree and generating linear regression functions at the nodes.
+by combining a conventional decision tree and generating linear regression 
+functions at the nodes.
 
@@
 (called support vectors).
+%This method works well even if the space is highly dimensional and the problem is not linearly separable.
 
@@
 \hline
-  SVM     & 1652.20 $\pm$ 283.50 & 109.30  & 251.16   & 17.18     & 16.42   \\
+  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
 \hline
@@
 
-\textbf{TODO: FALTA COMENTAR LOS RESULTADOS OBTENIDOS CON LOS 5 MÉTODOS.}
-
+% - indicar pros y contras de los diferentes métodos
 % - indicar qué método da mejores resultados
 % - indicar qué método es tipo "caja-negra" y cuáles ofrecen modelos "explicables"
-% - 
-% -
+
+M5P model obtained good results, both in time and error, and as stated before, 
+this method can learn and tackle tasks with high dimensionality
+and it generates reproducible and comprehensible representations that provide 
+information on the decision process and does not require human intervention 
+either for the operation or for interpretation. Thus, it is very suitable in 
+order to be incorporated in a publishing company processes.
+
+The Linear Regression model outperforms other complex methods, both in time 
+(as it is a simple method to train) and in obtained errors.
+However, more powerful models, that obtain better results, can be obtained in 
+comparable time.
+
+Taking into account the SVM model obtained results, this method obtains the best
+errors. Even when used using the default parameter values it exhibit a good 
+generalization performance.
+However, it is much slower than the others to build the model, not only when 
+using the data set with 13 input variables, but when using the data set with 
+7 input variables (including \emph{EDITORIAL} and \emph{MATTER}).
+
+kNN is the faster method used in this study, as it is the simpler method.
+However, the model is slow when classifying (as there are a large number of 
+training examples), and it exhibit a poor generalization ability, as it does not 
+learn anything from the training data.
+
+As far as the Multilayer Perceptron, its main drawbacks are both the cost of model 
+building (not only parameter and weights setting, but also time to train the 
+network) and the fact that it is a back-box model, and thus, it is difficult 
+to explain how the forecasts are obtained.
+In these experiments, the MLP requires a higher time than other methods, but also
+the obtained errors are worse as no parameter tuning to build the models have
+been carried out.
+Also, the difficulty to process information related to variables \emph{EDITORIAL} 
+and \emph{MATTER} might affect the worse results obtained on the final dataset.
+
+Finally, paying attention to the cost in time to obtain the forecasting models 
+and their accuracy, the M5P model is the most adequate to solve the problem of 
+how many books should be printed when a new book is published.
+This forecasting method, as an additional advantage, can be used for products 
+with historical sales data and for new products with little or no historical 
+data available.
 
@@
 Then, several standard data mining models for sales forecasting have been used 
-to forecast new book sales, and from them deduce print-run, based on those variables.
+to forecast new book sales, and from them deduce print-run, based on those 
+variables.
 
@@
 standard methods.
-Proposed method was validated by the company and incorporated in a business 
-intelligence tool for publishing houses.
-
-In this sense, the decision trees proved to be a suitable model because of the ease 
-to explain how the prediction is obtained from the variables that describe the new book. 
-This, compared to the black-box models such as the ANN was decisive from the point 
-of view of the needs of experts and the company.
-
-This research provides a new direction in the sales forecasting area using 
-different soft-computing techniques.
+Not only the obtained forecasting error has been taking into account to evaluate
+those methods, but also the the cost of model building as parameter setting and 
+the required time to train the model.
+
+In this sense, the decision trees proved to be a suitable model because of the 
+ease to explain how the prediction is obtained from the variables that describe 
+the new book. 
+This, compared to the black-box models such as the artificial neural network 
+was decisive from the point of view of the needs of experts and the company.
+Moreover, proposed method was validated by the company and incorporated in a 
+business intelligence tool for publishing houses.
+
+Overall, this study contributes to the literature by proposing the use of different 
+soft-computing standard techniques to solve a new challenging problem.
 Moreover, proposed method could be implemented, not only in the editorial 
@@
 with other methods based on soft-computing, such as genetic programming or fuzzy logic.
+Moreover, as default parameters have been used for proposed forecasting methods,
+it would be of interest carrying out some parameter tuning procedure in order to
+improve obtained results.
 

### 2015-08-22 paper.tex
comentando los resultados obtenidos

@@
 Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
-The company's expert sales managers analized historical data 
+The company's expert sales managers analyzed historical data 
 and applied their knowledge using external variables to calculate
@@
 
+Table \ref{tabla:results13} shows obtained results (time to build the model and 
+error) after applying the proposed forecasting methods on the dataset with 13 
+variables per book.
+In this dataset, every book is described using numerical variables, and thus, 
+processing the data to build the different models is a fast task despite the 
+number of instances.
+
 % Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
@@
   % en algunos calculan muchos más, pero estos son los más usados. 
-Obtained results using the different forecasting methods on the dataset with 13 
-variables per book can be shown in Table \ref{tabla:results13}:
 \begin{table*}[!h]
@@
 
+Obtained results (time to build the model and error) using the different 
+forecasting methods on the dataset with 7 variables per book can be shown 
+in Table \ref{tabla:results7}.
+Although in this dataset each book is described using a smaller number of 
+variables, two categorical variables, \emph{EDITORIAL} and \emph{MATTER}, are 
+included, what that makes harder to process the instances and build the different 
+models.
+
   %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
   % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
-Obtained results using the different forecasting methods on the dataset with 7 
-variables per book can be shown in Table \ref{tabla:results7}:
 \begin{table*}[!h]
@@
 \hline
-  MLP     & 3646.76 $\pm$ 64.83 & 705.69 $\pm$ 77.22   & 1608.69 $\pm$ 42.96  & 110.92 $\pm$ 12.14   & 105.18 $\pm$ 2.81   \\
+  MLP     & 3595.24 $\pm$ 97.50 & 691.84 $\pm$ 82.71   & 1619.92 $\pm$ 91.67  & 108.74 $\pm$ 13.00   & 105.91 $\pm$ 5.99   \\
 \hline
@@
 
+% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
+Paying attention to the obtained results shown in tables \ref{tabla:results13} 
+and \ref{tabla:results7}, using those categorical variables as part of a big 
+data set makes the problem hard to solve, both in required time to build the 
+forecasting models as well as in the obtained errors.
+However, as stated before, Trevenque expert sales manager, taking into account 
+his knowledge in industry experience and their perceptions, decided that 
+\emph{EDITORIAL} and \emph{MATTER} should taken into account.
+
 % - indicar pros y contras de los diferentes métodos
@@
 
-M5P model obtained good results, both in time and error, and as stated before, 
-this method can learn and tackle tasks with high dimensionality
-and it generates reproducible and comprehensible representations that provide 
-information on the decision process and does not require human intervention 
-either for the operation or for interpretation. Thus, it is very suitable in 
-order to be incorporated in a publishing company processes.
+As far as the different methods is concerned, M5P model obtained good results, 
+both in time and error, and as stated before, this method can learn and tackle 
+tasks with high dimensionality and it generates reproducible and comprehensible 
+representations that provide information on the decision process and does not 
+require human intervention either for the operation or for interpretation. 
+Thus, it is very suitable in order to be incorporated in a publishing company 
+processes.
 

### 2015-08-22 paper.tex
comentando cómo se han ejecutado los métodos (y arreglando algunos otros detalles)

@@
 
-  %  
   %  El proceso que seguimos, resumido para el paper, es:
@@
   %  	pbRAWtst.arff
-  %
-
-\textbf{TODO: FALTA CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS}
-
-% Comentar que:
+
+% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
 % - se ha usado la implementación de estos 5 métodos del paquete WEKA
 % - se han realizado 30 ejecuciones con cada método
-% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU @ 3.00GHz (4 cores), 16 GB RAM
+% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
 % -
-% - 
-% Preparar tests estadísticos para ver si hay diferencias en los errores entre métodos.
-% - 
-% -
+
+Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
+(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE_1.7.0_72.
+
+Proposed methods (M5P, LR, SVM, kNN, MLP) have been selected for this study from 
+the Weka implementation, and they were run 30 times with the Weka default parameter 
+settings and a different random initialization seed for each run.
 
@@
 \hline
-  MP5 		& 2.94 $\pm$ 0.51 	  & 65.49 	& 133.73 	& 11.10 	 & 9.17 	  \\
+  M5P 		& 2.94 $\pm$ 0.51 	  & 65.49 	& 133.73 	& 11.10 	 & 9.17 	  \\
 \hline
@@
 \hline
-  KNN 		& 0.03 $\pm$ 0.01 	  & 198.16 	& 542.93 	& 33.59 	 & 37.24 	\\
+  kNN 		& 0.03 $\pm$ 0.01 	  & 198.16 	& 542.93 	& 33.59 	 & 37.24 	\\
 \hline
@@
 \hline
-  MP5     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
+  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
 \hline
@@
 \hline
-  KNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
+  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
 \hline
@@
 and \emph{MATTER} might affect the worse results obtained on the final dataset.
+
+%[Pedro] ¿aplicamos tests estadísticos para ver si hay diferencias entre métodos?
 

### 2015-08-23 paper.tex
arreglando un error de compilación

@@
 \author {
-P.A. Castillo, A.M. Mora, J.J. Merelo,  et al.
+P.A. Castillo, A.M. Mora, J.J. Merelo, \\ A.J. Fern\'andez-Ares, P. Garc\'{\i}a-S\'anchez, M.G. Arenas
 }
@@
 Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
-(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE_1.7.0_72.
+(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.
 

### 2015-08-24 paper.tex
Fixing typos and grammar errors and added coments for @pacastillo

@@
 since it implies a loss of investment due to inventory excess. That is
-why in this paper we are tackling the problem or predicting sales to 
+why in this paper we are tackling the problem or predicting sales to %FERGU: The problem ON predicting, no?
 print the right amount of books, doing so even before the book has
@@
 sometimes unknown. 
-Some have to do with decisions on purchases, others with freight
+Some have to do with decisions on purchases, others with freight %FERGU: El Some have to do me suena raro
 traffic, and others with the distribution strategy \cite{Little1998}.
@@
 experimental setup and the methodology considered in the study is
-presented.  
+presented.  %FERGU: mejor described para no repetir
 Section \ref{sec:experiments} reports and analyzes the obtained results with a 
@@
 %********************************************************************************
-\section{Sales forecasting. State of the art}
+\section{Sales forecasting. State of the art} %FERGU: State of the art on sales forecasting?
 \label{sec:soa}
@@
 Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
-is perhaps the most used technique to tackle the sales forecasting problems, 
+is perhaps the most used technique to tackle the sales forecasting problems, %FERGU: terminar esta frase con punto en vez de coma para que no sea larga
 the efficiency of these techniques depends largely on the field of application 
@@
 Different sales patterns are observed by analyzing data obtained.
-In any case, in this research, historical data from published books is used, 
+In any case, in this research, historical data from published books is used, %FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso
 and the proposed methodology can not be usable in the problem of unpublished-books 
@@
 Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
-decision trees for sales forecasting in textile-appared fashion industry, 
+decision trees for sales forecasting in textile-appared fashion industry, %FERGU: appared? apparel, creo
 a very similar issue to the new book publishing problem.
@@
   % New soft drink product
-In \cite{ChingChin2010}, a decision-support system for new product sales 
+In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
 forecasting is proposed to solve three real-world sales forecasting problems 
@@
 In this study, it is assumed that products are classified based on their sales 
-pattern so that products in the same class would have similar sales pattern.
+pattern so that products in the same class would have similar sales pattern. %FERGU: "_a_ similar sales pattern", mejor? 
 However, as the authors state, proposed system can not deal with qualitative 
@@
 influences to understand how electronic word-of-mouth affects product sales. 
-Proposed method is suitable in those sales forecasting problems with abundant 
+Proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method? 
 online reviews and historical data.
@@
 However, in the case of new books there is no historical data to define patterns, 
-and only some descriptive data about the new book is available.
-In these cases not any forecasting method can be used\cite{Madsen2008,ChernWSF15}.
-
-An additional issue is the dificulty to compare our model with classical 
+and only some descriptive data about the new book is available. %FERGU: data es plural. is->are
+In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.
+
+An additional issue is the difficulty to compare our model with classical 
 forecasting methods, such as time series prediction methods, since books 
@@
 
-Throughout this research we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
+Throughout this research, we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
 a company that provides management systems and services for libraries, publishers 
@@
 
-Trevenque company, whose expert manager advised this research, provided 
+Trevenque company, whose expert manager advised this research, provided %FERGU: los párrafos anteriores son un poco dispersos, puedes quitar los puntos y aparte y agruparlos por temas (por ejemplo, todo lo de Trevenque debería de ir en un párrafo)
 the initial data set consisting of 3159 books.
@@
 In addition, there is no a standard methodology to solve the general problem 
-of sales forecasting.
+of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
 Usually, a preliminary analysis of the data is carried out to eliminate those 
@@
 
-Thus, in this study there are three main stages (see Figure \ref{fig:stages} 
+Thus, in this study there are three main stages (see Figure \ref{fig:stages} %FERGU: there are->we propose
 for details): 
@@
 
-  \item  Then, several forecasting methods has to be tested. In this stage 
+  \item  Then, several forecasting methods have to be tested. In this stage 
   different forecasting methods are used to obtain sales forecasts from the 
@@
 In any case, we recommend using widely accepted standard 
-equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} 
+equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} %FERGU: mejor tratar esto como una referencia, ya que es un texto
 in order to compare obtained results with those presented in other research 
@@
 
-Specifically, in order to compute the forecasting errors of the different methods, 
+Specifically, in order to compute the forecasting errors of the different methods, %FERGU: quitar este salto de linea y unirlo al párrafo de arriba
 Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
@@
 Also, the SOM graph represents and highlight very clearly those regions (clusters) 
-with high training sample concentration and fewer where the samples are scarce.
-
-As stated in Section \ref{sec:problem}, an expert sales manager colaborated in 
+with high training sample concentration and fewer where the samples are scarce. %FERGU: mencionarlo en la intro
+
+As stated in Section \ref{sec:problem}, an expert sales manager collaborated in 
 this research in the stage of data analysis. Thus, the process was as follows:
@@
   \item The company asked to include the information about \emph{editorial} 
-  and \emph{materia}. Thus, in a new iteration, taking into account the expert's 
-  advice and the información obtained analyzing the SOM results, the number of 
+  and \emph{materia}. Thus, in a new iteration, taking into account the expert's %FERGU: materia no existe en inglés. Subject?
+  advice and the information obtained analyzing the SOM results, the number of 
   inputs was decreased to 7.
   \item In a third step, several forecasting methods were used on the obtained 
-  dataset, and the best was choosen to obtain an accurate predicting model.
+  dataset, and the best was chosen to obtain an accurate predicting model.
   \item Finally, some information about the new book, such as \emph{author}, 
@@
 More specifically, in a first step, the expert analyzed the 50 input variables 
-describing each book to remove those that were suplerfuas.
+describing each book to remove those that were superfluous.
 Table \ref{tabla:params43} shows the set of variables describing a book 
@@
 \end{table}
-
-Then, after analizyng the original dataset using the SOM to select the best 
+%FERGU: para ahorrar espacio se puede hacer la tabla inversa: variables que se han quitado (las 7)
+Then, after analyzing the original dataset using the SOM to select the best %FERGU: parametros o framework SOM usados?
 variables to be considered, and taking into account the knowledge of the company 
 experienced manager, 13 inputs were considered. 
-Figure \ref{fig:som43} shows the initial analisys of dataset using the total 
+Figure \ref{fig:som43} shows the initial analysis of dataset using the total 
 of 43 descriptive inputs per book.
 Table \ref{tabla:params13} shows the set of variables describing a book after 
-the second analisys.
+the second analysis.
 	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
@@
 \end{tabular}
-\caption{\small{Initial data analysis, using 43 descriptive variables per book, 
+\caption{\small{Initial data analysis, using 43 descriptive variables per book, %FERGU: la figura está en español, pero ya lo sabréis :P
 using SOM.}}
@@
 
-Finally, after analizyng the dataset with 13 descriptive inputs per
+Finally, after analyzing the dataset with 13 descriptive inputs per %FERGU: describis los resultados antes de explicar que volveis a hacer SOM
 book, and paying attention to the company experienced manager's
 recommendations, 7 inputs were considered; specifically, variables
-\emph{EDITORIAL} and \emph{MATTER} were included, while
+\emph{EDITORIAL} and \emph{MATTER} were included, while %FERGU: vale, no useis MATTER, usad mejor SUBJECT (MATTER es materia de física, creo xD)
 \emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
@@
 	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
-Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on 
+Figure \ref{fig:som13} shows the initial analysis of dataset using the SOM on 
 the total of 13 descriptive inputs per book.
@@
 \end{tabular}
-\caption{\small{Análisis de los datos iniciales, usando 13 variables
-    descriptivas por libro, utilizando el SOM.}}
+\caption{\small{Analysis of the initial data, using 13 descriptive variables per book, using the SOM.}} % Análisis de los datos iniciales, usando 13 variables descriptivas por libro, utilizando el SOM.}} %FERGU: teniais esto en español, lo he traducido al inglés :)
 % describir de forma más precisa: visualización usando UMatrix de... - JJ
@@
 
-However, as in the case of new books only some descriptive data is available 
+However, as in the case of new books only some descriptive data is available %FERGU: data es plural. is->are
 (compared to those cases in which historical data on sales of published books 
@@
 Well known forecasting methods implemented in the Weka tool
-\cite{Hall2009,Witten2011} have been choosen, as these methods are
+\cite{Hall2009,Witten2011} have been chosen, as these methods are
 widely known, and could be very helpful for practitioners to reproduce
@@
 
-Specifically, following forecasting methods are proposed:
+Specifically, the following forecasting methods are proposed:
 \begin{itemize}
@@
 Support vector machine (SVM) \cite{Cortes1995,Shevade1999} method is based on  
-statistical learning theory and has succesfully used in classification and  
+statistical learning theory and has successfully used in classification and  
 regression problems \cite{Cao2003,Jari2008}.
 
-In classification problems the algorithm searchs for an optimal hyperplane 
+In classification problems the algorithm searches for an optimal hyperplane 
 that separates two classes, maximizing the margin between two classes. 
@@
 The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
-wich the unknown instances are classified by relating them to the known 
+which the unknown instances are classified by relating them to the known 
 instances using a distance measurement/function (Euclidean, Minkowsky or minimax).
@@
 The classification algorithm locates the nearest neighbour in instance space and 
-asigns the class of that neighbour to the unknown instance.
+assigns the class of that neighbour to the unknown instance.
 In order to improve the robustness of the model, several neighbours can be 
@@
 technique called back-propagation.
-This training method was developed independly by Werbos \cite{Werbos1974}, 
+This training method was developed independently by Werbos \cite{Werbos1974}, 
 Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
 in updating the weights of the output layer neurons once the erroneous output 
-has been obtained, and then, propagating the succesive weight layers back to 
+has been obtained, and then, propagating the successive weight layers back to 
 the input layer.
@@
 forecasting methods on the dataset with 7 variables per book.}}
-\label{tabla:results7}
+\label{tabla:results7} %FERGU: es normal que con menos variables tarde más?
 \end{table*}
@@
 his knowledge in industry experience and their perceptions, decided that 
-\emph{EDITORIAL} and \emph{MATTER} should taken into account.
+\emph{EDITORIAL} and \emph{MATTER} should be taken into account.
 
@@
 
-Taking into account the SVM model obtained results, this method obtains the best
+Taking into account the SVM model obtained results, this method obtains the best %FERGU: "the best errors" no se sabe si es lo mejor o lo peor xDD Pon "worst results" o así
 errors. Even when used using the default parameter values it exhibit a good 
@@
 However, it is much slower than the others to build the model, not only when 
-using the data set with 13 input variables, but when using the data set with 
+using the data set with 13 input variables, but when using the data set with %FERGU: a veces pones dataset: unificarlo
 7 input variables (including \emph{EDITORIAL} and \emph{MATTER}).
@@
 %La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
-A data set consisting of 3159 books provided by the Spanish 
+A data set consisting of 3159 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
 publishing company Trevenque Editorial has been used.
@@
 Moreover, proposed method was validated by the company and incorporated in a 
-business intelligence tool for publishing houses.
+business intelligence tool for publishing houses. %FERGU: no hay más info de esto? estaría guay describirlo
+
+%FERGU: no mencionais el SOM en las conclusiones
 

### 2015-08-24 paper.tex
contestando comentarios de Pablo

@@
 since it implies a loss of investment due to inventory excess. That is
-why in this paper we are tackling the problem or predicting sales to %FERGU: The problem ON predicting, no?
+why in this paper we are tackling the problem on predicting sales to %FERGU: The problem ON predicting, no? ¡gracias!
 print the right amount of books, doing so even before the book has
@@
 %********************************************************************************
-\section{Sales forecasting. State of the art} %FERGU: State of the art on sales forecasting?
+\section{State of the art on sales forecasting} %FERGU: State of the art on sales forecasting?  ok  ;)
 \label{sec:soa}
@@
 Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
-is perhaps the most used technique to tackle the sales forecasting problems, %FERGU: terminar esta frase con punto en vez de coma para que no sea larga
-the efficiency of these techniques depends largely on the field of application 
+is perhaps the most used technique to tackle the sales forecasting problems. 
+%FERGU: terminar esta frase con punto en vez de coma para que no sea larga.   OK
+The efficiency of these techniques depends largely on the field of application 
 and the problem data as they require a large amount of data for predicting 
@@
   %     Moon2010ICEC
-Recently, some works propose \cite{Moon2010ICSSSM,Moon2010ICEC} analyzing 
-relationships between on-line information and book sales.
+Recently, some works propose analyzing relationships between on-line information 
+and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}.
 Specifically, authors propose using the number of blog references as an indicator 
@@
 Different sales patterns are observed by analyzing data obtained.
-In any case, in this research, historical data from published books is used, %FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso
+In any case, Moon et al \cite{Moon2010ICSSSM,Moon2010ICEC} used historical data from published books, 
+%FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso.   ok
 and the proposed methodology can not be usable in the problem of unpublished-books 
@@
 Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
-decision trees for sales forecasting in textile-appared fashion industry, %FERGU: appared? apparel, creo
+decision trees for sales forecasting in textile-apparel fashion industry, %FERGU: appared? apparel, creo.  ¡sí!
 a very similar issue to the new book publishing problem.
@@
 In this study, it is assumed that products are classified based on their sales 
-pattern so that products in the same class would have similar sales pattern. %FERGU: "_a_ similar sales pattern", mejor? 
+pattern so that products in the same class would have a similar sales pattern. %FERGU: "_a_ similar sales pattern", mejor? ok
 However, as the authors state, proposed system can not deal with qualitative 
@@
 influences to understand how electronic word-of-mouth affects product sales. 
-Proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method? 
+The proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method?    ok
 online reviews and historical data.
@@
 However, in the case of new books there is no historical data to define patterns, 
-and only some descriptive data about the new book is available. %FERGU: data es plural. is->are
+and only some descriptive data about the new book is available. 
+%FERGU: data es plural. is->are   ...a mí me suena bien con "is"   ¡una segunda opinión!   ;)
 In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.
@@
 In this data set, descriptive information for each book includes price, 
-selling points, matter, publisher, sales, returns, among other information.
+selling points, subject, publisher, sales, returns, among other information.
 Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
@@
 RETAIL PRICE
-MATTER1
-MATTER2
-MATTER3
+SUBJECT1
+SUBJECT2
+SUBJECT3
 EDITORIAL
@@
 In this prediction problem, several variables related to the own book affect 
-the forecasts, such as author, price, matter or publisher.
+the forecasts, such as author, price, subject or publisher.
 
@@
 
-Thus, in this study there are three main stages (see Figure \ref{fig:stages} %FERGU: there are->we propose
+Thus, in this study we propose three main stages (see Figure \ref{fig:stages} %FERGU: there are->we propose
 for details): 
@@
 or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.
-
-Specifically, in order to compute the forecasting errors of the different methods, %FERGU: quitar este salto de linea y unirlo al párrafo de arriba
+Specifically, in order to compute the forecasting errors of the different methods, 
+%FERGU: quitar este salto de linea y unirlo al párrafo de arriba.    ok
 Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
@@
 %FERGU: para ahorrar espacio se puede hacer la tabla inversa: variables que se han quitado (las 7)
+%[pedro] no entiendo muy bien a qué te refieres...
+
 Then, after analyzing the original dataset using the SOM to select the best %FERGU: parametros o framework SOM usados?
@@
 recommendations, 7 inputs were considered; specifically, variables
-\emph{EDITORIAL} and \emph{MATTER} were included, while %FERGU: vale, no useis MATTER, usad mejor SUBJECT (MATTER es materia de física, creo xD)
+\emph{EDITORIAL} and \emph{SUBJECT} were included, while %FERGU: vale, no useis SUBJECT, usad mejor SUBJECT (SUBJECT es materia de física, creo xD).    ok, ¡gracias!
 \emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
@@
 RETAIL PRICE
-MATTER
+SUBJECT
 EDITORIAL
@@
 Although in this dataset each book is described using a smaller number of 
-variables, two categorical variables, \emph{EDITORIAL} and \emph{MATTER}, are 
+variables, two categorical variables, \emph{EDITORIAL} and \emph{SUBJECT}, are 
 included, what that makes harder to process the instances and build the different 
@@
 forecasting methods on the dataset with 7 variables per book.}}
-\label{tabla:results7} %FERGU: es normal que con menos variables tarde más?
+\label{tabla:results7} %FERGU: es normal que con menos variables tarde más? Sí, el uso de MATERIA y EDITORIAL hacen que el conjunto sea endiablado.
 \end{table*}
@@
 his knowledge in industry experience and their perceptions, decided that 
-\emph{EDITORIAL} and \emph{MATTER} should be taken into account.
+\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.
 
@@
 
-Taking into account the SVM model obtained results, this method obtains the best %FERGU: "the best errors" no se sabe si es lo mejor o lo peor xDD Pon "worst results" o así
+Taking into account the SVM model obtained results, this method obtains the lower 
+%FERGU: "the best errors" no se sabe si es lo mejor o lo peor xDD Pon "worst results" o así
 errors. Even when used using the default parameter values it exhibit a good 
@@
 using the data set with 13 input variables, but when using the data set with %FERGU: a veces pones dataset: unificarlo
-7 input variables (including \emph{EDITORIAL} and \emph{MATTER}).
+7 input variables (including \emph{EDITORIAL} and \emph{SUBJECT}).
 
@@
 Also, the difficulty to process information related to variables \emph{EDITORIAL} 
-and \emph{MATTER} might affect the worse results obtained on the final dataset.
+and \emph{SUBJECT} might affect the worse results obtained on the final dataset.
 

### 2015-08-25 paper.tex
contestando comentarios de Pablo
Revisado abstract corregido @fergunet

@@
 \author {
-P.A. Castillo, A.M. Mora, J.J. Merelo, \\ A.J. Fern\'andez-Ares, P. Garc\'{\i}a-S\'anchez, M.G. Arenas
+P.A. Castillo, A.M. Mora, J.J. Merelo, P. Garc\'{\i}a-S\'anchez, \\ A.J. Fern\'andez-Ares, M.G. Arenas, P. de las Cuevas
 }
@@
 \begin{abstract}
-
-%% Many companies must face, as one of the most difficult tasks to
-%% accomplish, new product sales estimation, since in many cases no
-%% historical data to serve as guide is available. 
-%% Moreover, some of them lack the knowledge about forecasting methods
-%% and they can only make decisions based on the expert sales
-  %% managers. 
-% Eliminado esto.
-When a new book is published the publishing house faces the problem of
-how many books should be printed. Printing too many is the main issue,
-since it implies a loss of investment due to inventory excess. That is
-why in this paper we are tackling the problem on predicting sales to %FERGU: The problem ON predicting, no? ¡gracias!
+When a new book is published the publisher faces the problem of
+how many books should be printed for delivery to bookstores. Printing too many is the main issue,
+since it implies a loss of investment due to inventory excess. In this
+paper we are tackling the problem of predicting total sales in order to %FERGU: The
+                                %problem ON predicting, no? ¡gracias!  
+% of predicting -  JJ
 print the right amount of books, doing so even before the book has
-reached shelves, which is when printing occurs. 
-%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
-%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling.
-Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
-% In the literature, different methods of sales prediction, mainly for
-% the fashion industry are proposed. 
-% Esto no pega nada en el abstract - JJ
-%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
-%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
-%In this paper, a rule-based decision method is proposed to address the
-%problem of predicting the publishing roll.  
-% It's not proposed. It just obtained the best result with WEKA. - JJ 
-% Publishing roll? ¿Qué es? - JJ
-%[Pedro] en la traducción de términos Antonio propone traducirlo como "print run". Lo pongo así.
-In this paper, which works with data on published books for several years in
-Spain, we first apply a data visualization and preprocessing strategy to find
-out what are the relevant variables in the prediction of sales, and
+reached shelves. 
+In this paper, which works with several years of data on published books in
+Spain, we first apply a data visualization and preprocessing strategy
+in order to find
+out what are the variables that have some impact on sales, and
 then use standard data mining software to predict sales, and from them
-deduce print-run, based on those variables. Our work discovers which
-are the most relevant variables when predicting sales, and is
+deduce print-run, based on those variables. Our work focuses then in  discovering which
+are the most relevant variables when predicting sales and is
 eventually able to predict sales with remarkable accuracy. In fact,
 this method has been validated by the company that provided the data 
-and incorporated in a business intelligence tool for publishing houses,
-since the obtained models provide information on the decision process and
-does not require human intervention either for the operation or for
+and incorporated in a business intelligence tool for publishers,
+since the obtained models provide guidance on the decision process of
+publishing a book and do not require human intervention either for the operation or for
 interpretation.

### 2015-08-25 paper.tex
Revisa intro y términos

@@
 
-% A partir de datos históricos de tiradas editoriales se plantea el
-% uso de varios modelos para la clasificación y predicción de la
-% tirada de nuevos títulos editoriales.
-
-A company that intends to release a new product has a high risk due to
-the complexity of the production and distribution processes. 
+Publishing a book, as releasing any other product, implies several
+types of risks and costs due to
+the complexity and expenses of the production and distribution processes. 
 % tienes que enmarcar el problema. Se trata de productos culturales
@@
 
-In the field of publishing industry, the challenge is to print an
-adequate number of copies but not too much, as the unsold volumes will
-lead to losses, whereas if the number of printed copies was not
-enough, you can always print more. 
+Book publishers, as well as other content producers, release new {\em
+  products} more frequently than other industries and thus face the
+problem of predicting sales quite often. The issue, in this case, is to print an
+adequate number of copies but not too many, as the unsold volumes will
+lead to losses and sunk inventory cost, whereas if the number of printed copies was not
+enough, you can always print more. In this sense, errors in one or the
+other direction do not have the same importance, although a temporal
+scarcity of a book that is selling well is also a problem.
+
 Thus, it is extremely important using predictive tools to optimize 
 production and improve the publishing company profits or minimize losses \cite{Zhao2001}
-by forecasting the sales a new book might achieve. 
+by forecasting the sales a new book might achieve. This is the
+objective we have in this paper.
 An example is the optimization of sales \cite{Mattila2002} by

### 2015-08-25 paper.tex
arreglando una traducción de términos

@@
 REST OF SELLING POINTS FIRST YEAR
-WEEKS ON SALE
+WEEKS FOR SALE
 POSITIVE SALE MARKET
@@
 MEDIUM SALE MARKET
-WEEKS ON SALE
+WEEKS FOR SALE
 DELEGATES DISTRIBUTED
@@
 TOTAL SELLING POINTS
-WEEKS ON SALE
+WEEKS FOR SALE
 TOTAL DISTRIBUTED
@@
   NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
-  WEEKS ON SALE, PRINT-RUN} were discarded.  
+  WEEKS FOR SALE, PRINT-RUN} were discarded.  
 	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?

### 2015-08-29 paper.tex
Some corrections adds to @fergunet

@@
 In those cases where historical data is available, classical time series 
-forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
-model integrating K-mean and fuzzy neural networks to forecast the future sales 
+forecasting methods can be applied, which is what they do in \cite{Chang2009}, where a hybrid 
+model integrating K-means and fuzzy neural networks to forecast the future sales 
 of a printed circuit board is proposed.
@@
 Taking into account the kind of problem we address in this paper,
-a new product sales prediction for which no historical data is available,
-the classical forecasting methods based on time series are not adequate. 
+prediction of sales of 
+a new product for which no historical data is available,
+the classical forecasting methods based on time series are not
+adequate, although they can obviously be used once the book has been
+for sale. 
 Thus, in this paper the relevant variables in the prediction of sales are determined
@@
 In any case, we recommend using widely accepted standard 
-equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} %FERGU: mejor tratar esto como una referencia, ya que es un texto
+equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm}
+% FERGU: mejor tratar esto como una referencia, ya que es un texto
+% Efectivamente- JJ
 in order to compare obtained results with those presented in other research 
@@
 implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
-or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.
+or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are
+proposed.
+% no se deben usar footnotes donde debiera haber referencias. - JJ
 Specifically, in order to compute the forecasting errors of the different methods, 
@@
 
-As future work, it would be interesting comparing the obtained forecasting results 
+As future work, it would be interesting to compare the obtained forecasting results 
 with other methods based on soft-computing, such as genetic programming or fuzzy logic.
@@
 study of the effect of the application of discounts and promotions.
+
+Finally, there are some variables over which the published has some
+control once the book has been published, such as the initial print
+run or the books given out as gifts to reviewers or what proportion is
+going to be sent to each possible point of sale. This can be
+incorporated into an optimization model that optimizes those values to
+obtain desired sales. This is left as future work.
 
@@
 \end{document}
+%%% Local Variables:
+%%% ispell-local-dictionary: "english"
+%%% End:

### 2015-09-10 paper.tex
updating table results (MLP)
resultados de las dos tablas completos
Problem section rewritten
I have put the second paragraph in front. Please @pacastillo check the second to see if it's still relevant. (I don't think so)

@@
 since it implies a loss of investment due to inventory excess. In this
-paper we are tackling the problem of predicting total sales in order to %FERGU: The
-                                %problem ON predicting, no? ¡gracias!  
-% of predicting -  JJ
+paper we are tackling the problem of predicting total sales in order to 
 print the right amount of books, doing so even before the book has
@@
 
-%Sales forecasting in editorial industry is a very complex problem. 
-        %hala, vuelta la burra al trigo - JJ
-        %[Pedro] ea, lo quito   :)
-There are several difficulties inherent to the new book sales forecasting, 
-such as dealing with limited data, finding adequate forecasting methods, and 
-selecting the best method to use \cite{ChingChin2010}.
-
-The main issue of this paper is to compute forecasting of the sales for 
-new unpublished-books, for which no historical data is available.
-Thus, this paper faces the new book publishing problem using different 
-prediction methods and using as inputs the historical sales data related 
-to other yet published books, and some descriptive variables relative to 
-the new unpublished-book.
+The main issue of this paper is to forecast sales for 
+unpublished books for which no historical data is available, just some
+descriptive variables relative to the new book. In order to do that,
+training data includes historical sales data for all books published
+in Spain for several years, including those descriptive variables.
+
+%Después de esto no sé si merece la pena dejar este párrafo.
+Forecasting sales of new books is a problem with issues 
+such as dealing with limited data, finding adequate forecasting methods and 
+selecting the best method to use \cite{ChingChin2010}. % He cambiado
+                                % esto, pero sigue sin decir
+                                % absolutamente nada. "The problem"
+                                % tiene que describir el problema: qué
+                                % queremos hacer, qué tenemos - JJ
 
@@
 
-  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
-  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
+  %[pedro] ya están todos los resultados de de tabla:results7 (MP5, LR, KNN, SVM, MLP)
 \begin{table*}[!h]
@@
 \hline
-  MLP     & 3595.24 $\pm$ 97.50 & 691.84 $\pm$ 82.71   & 1619.92 $\pm$ 91.67  & 108.74 $\pm$ 13.00   & 105.91 $\pm$ 5.99   \\
+  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
 \hline

### 2015-09-10 paper.tex
Entering the "problem description"
With lots of material to move or eliminate.

@@
 in Spain for several years, including those descriptive variables. 
-
+%
+%%% Principio de párrafos a eliminar o mover a estado del arte.
 %Después de esto no sé si merece la pena dejar este párrafo.
@@
 
+% Este párrafo o se borra o se traslada al estado del arte. Aquí hay
+% que contar cuál es el problema y qué se tiene. No se puede volver a
+% repetir lo de antes.
 In the case of already published books, available historical data might help 
@@
 
+% Vale, más issues. Este párrafo también puede quedar fuera. Ya has
+% dicho que no se puede usar la serie histórica.
 An additional issue is the difficulty to compare our model with classical 
@@
 a company that provides management systems and services for libraries, publishers 
-and distributors.
-
-Trevenque company, whose expert manager advised this research, provided %FERGU: los párrafos anteriores son un poco dispersos, puedes quitar los puntos y aparte y agruparlos por temas (por ejemplo, todo lo de Trevenque debería de ir en un párrafo)
-the initial data set consisting of 3159 books.
-In this data set, descriptive information for each book includes price, 
-selling points, subject, publisher, sales, returns, among other information.
+and distributors. % Esto tampoco viene a cuento. Se dice en la intro o
+                  % se cuenta como gente que nos ha proporcionado los
+                  % datos y nos contrató para hacerlo.
+
+Trevenque company, whose expert manager advised this research,
+provided %FERGU: los párrafos anteriores son un poco dispersos, puedes
+         %quitar los puntos y aparte y agruparlos por temas (por
+         %ejemplo, todo lo de Trevenque debería de ir en un párrafo) 
+% O borrarlos - JJ
+%% Fin de párrafos a eliminar.
+This initial data set, provided in the framework of a contract by
+Trevenque Editorial, included 3159 books, and included descriptive information for each book includes price, 
+points of sale, subject, publisher, sales, returns, among other information.
 Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 

### 2015-09-11 paper.tex
Revised English and practically removed Problem section refs #6 #11
updating terms in the .tex file

@@
 AUTHOR
-RETAIL PRICE
+RETAIL PRICER
 SUBJECT1
@@
 TOTAL SALES
-MALLS SALES
-DELEGATES SALES
+DEPARTMENT STORES SALES
+SALES THROUGH DELEGATES
 REST OF SALES
@@
 TOTAL DISTRIBUTED
-MALLS DISTRIBUTED
-DELEGATES DISTRIBUTED
-REST OF DISTRIBUTED
+DISTRIBUTED THROUGH DEPARTMENT STORES
+DISTRIBUTED THROUGH DELEGATES
+DISTRIBUTED - REST
 TOTAL DISTRIBUTED FIRST YEAR
-MALLS DISTRIBUTED FIRST YEAR
-DELEGATES DISTRIBUTED FIRST YEAR
+DISTRIBUTED THROUGH DEPARTMENT STORES FIRST YEAR
+DISTRIBUTED THROUGH DELEGATES FIRST YEAR
 \end{verbatim} \end{minipage}     &
@@
 NUMBER OF REPRINTS
-TOTAL DEVOLUTIONS
-MALLS DEVOLUTIONS
-DELEGATES DEVOLUTIONS
-REST OF DEVOLUTIONS
-TOTAL DEVOLUTIONS FIRT YEAR
-MALLS DEVOLUTIONS FIRST YEAR
-DELEGATES DEVOLUTIONS FIRST YEAR
-REST OF DEVOLUTIONS FIRST YEAR
+TOTAL RETURNS
+RETURNS - DEPARTMENT STORES
+DELEGATES RETURNS
+REST OF RETURNS
+TOTAL RETURNS FIRT YEAR
+RETURNS -  DEPARTMENT STORES  FIRST YEAR
+DELEGATES RETURNS FIRST YEAR
+REST OF RETURNS FIRST YEAR
 GIFTS
-UNITS DISTRIBUTED IN FIRST EDITION
-TOTAL SELLING POINTS
-MALLS SELLING POINTS
-DELEGATES SELLING POINTS
-REST OF SELLING POINTS
-TOTAL SELLING POINTS FIRST YEAR
-MALLS SELLING POINTS FIRST YEAR
-DELEGATES SELLING POINTS FIRST YEAR
-REST OF SELLING POINTS FIRST YEAR
+UNITS DISTRIBUTED AS NOVELTY
+TOTAL POINTS OF SALE
+POINTS OF SALE - DEPARTMENT STORES
+DELEGATES POINTS OF SALE
+REST OF POINTS OF SALE
+TOTAL POINTS OF SALE FIRST YEAR
+DEPARTMENT STORES POINTS OF SALE FIRST YEAR
+DELEGATES POINTS OF SALE FIRST YEAR
+REST OF POINTS OF SALE FIRST YEAR
 WEEKS FOR SALE
-POSITIVE SALE MARKET
-MEDIUM SALE MARKET
-NEGATIVE SALE MARKET
+POSITIVE SALES ENVIRONMENT
+MEDIUM SALES ENVIRONMENT
+NEGATIVE SALES ENVIRONMENT
 \end{verbatim} \end{minipage}    \\
@@
 In this prediction problem, several variables related to the own book affect 
-the forecasts, such as author, price, subject or publisher.
+the forecasts, such as author, price, subject or publisher. %This has
+                                %to be grounded by the experiment and
+                                %graphs.
 
@@
 the automatic method. Even publishing companies tend to define rules or 
-indexes to subjectively adjust the results of prediction based on external data.
+indexes to subjectively adjust the results of prediction based on
+external data. %so what?
 
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-MALLS SELLING POINTS FIRST YEAR
+DEPARTMENT STORES POINTS OF SALE FIRST YEAR
 REST OF SALES FIRST YEAR
-NEGATIVE SALE MARKET
-MALLS DISTRIBUTED FIRST YEAR
-TOTAL DEVOLUTIONS
+NEGATIVE SALES ENVIRONMENT
+DISTRIBUTED THROUGH DEPARTMENT STORES FIRST YEAR
+TOTAL RETURNS
 REPRINTS
 MALL SALES FIRST YEAR
-TOTAL SELLING POINTS FIRST YEAR
-UNITS DISTRIBUTED IN FIRST EDITION
+TOTAL POINTS OF SALE FIRST YEAR
+UNITS DISTRIBUTED AS NOVELTY
 PRINT-RUN
 NUMBER OF REPRINTS
-MALLS DEVOLUTIONS
-REST OF SELLING POINTS FIRST YEAR
+RETURNS - DEPARTMENT STORES
+REST OF POINTS OF SALE FIRST YEAR
 REST OF SALES
-DELEGATES SELLING POINTS
-REST OF DEVOLUTIONS
-DELEGATES SELLING POINTS FIRST YEAR
-POSITIVE SALE MARKET
+DELEGATES POINTS OF SALE
+REST OF RETURNS
+DELEGATES POINTS OF SALE FIRST YEAR
+POSITIVE SALES ENVIRONMENT
 REST OF DISTRIBUTED FIRST YEAR
-REST OF SELLING POINTS
-TOTAL DEVOLUTIONS FIRT YEAR
-DELEGATES DEVOLUTIONS
+REST OF POINTS OF SALE
+TOTAL RETURNS FIRT YEAR
+DELEGATES RETURNS
 \end{verbatim} \end{minipage}     &
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-MALLS SALES
+DEPARTMENT STORES SALES
 TOTAL DISTRIBUTED FIRST YEAR
-TOTAL SELLING POINTS
-MALLS DISTRIBUTED
-DELEGATES DISTRIBUTED FIRST YEAR
-MALLS SELLING POINTS
+TOTAL POINTS OF SALE
+DISTRIBUTED THROUGH DEPARTMENT STORES
+DISTRIBUTED THROUGH DELEGATES FIRST YEAR
+POINTS OF SALE - DEPARTMENT STORES
 TOTAL SALES FIRST YEAR
-MEDIUM SALE MARKET
+MEDIUM SALES ENVIRONMENT
 WEEKS FOR SALE
-DELEGATES DISTRIBUTED
+DISTRIBUTED THROUGH DELEGATES
 AUTHOR
@@
 GIFTS
-MALLS DEVOLUTIONS FIRST YEAR
-DELEGATES SALES
-REST OF DISTRIBUTED
-DELEGATES DEVOLUTIONS FIRST YEAR
+RETURNS -  DEPARTMENT STORES  FIRST YEAR
+SALES THROUGH DELEGATES
+DISTRIBUTED - REST
+DELEGATES RETURNS FIRST YEAR
 TOTAL DISTRIBUTED
-REST OF DEVOLUTIONS FIRST YEAR
-RETAIL PRICE
+REST OF RETURNS FIRST YEAR
+RETAIL PRICER
 TOTAL SALES (output)
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-TOTAL DEVOLUTIONS
+TOTAL RETURNS
 REPRINTS
-TOTAL SELLING POINTS FIRST YEAR
-UNITS DISTRIBUTED IN FIRST EDITION
+TOTAL POINTS OF SALE FIRST YEAR
+UNITS DISTRIBUTED AS NOVELTY
 NUMBER OF REPRINTS
-TOTAL DEVOLUTIONS FIRT YEAR
+TOTAL RETURNS FIRT YEAR
 TOTAL DISTRIBUTED FIRST YEAR
-TOTAL SELLING POINTS
+TOTAL POINTS OF SALE
 WEEKS FOR SALE
 TOTAL DISTRIBUTED
-RETAIL PRICE
+RETAIL PRICER
 PRINT-RUN

### 2015-09-17 paper.tex
Añadiendo descripción de SOM
Y un par de citas

@@
 
-\textbf{FALTA EXPLICAR EN UN PAR DE PÁRRAFOS QUÉ ES EL SOM DE KOHONEN.}
+SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organization, configures the output units into a topological representation of the original data.
+It tries to imitate the self-organization done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus.
+SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organize data so as to disclose so far unknown patterns or structures.
+It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem.
+The main property of the SOM is that it makes a nonlinear projection from a high-dimensional data space (one dimension per variable) on a regular, low-dimensional (usually 2D) grid of neurons, called units.
+SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons.
+It allows us to visualize any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure.
+High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.
+
+SOMs (and U-Matrix) are usually applied for visualize natural structures in the data and their relations, as well as the natural groupings that could be among them.
+In addition, SOM makes easy the estimation of the variables that have more influence on these groupings.
+Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recognizer.
 

### 2015-10-13 paper.tex
adding some references

@@
   \item  First, after the editorial company has provided the raw data, taken 
-  directly from its database, a selection variables process is carried out. 
-  In this stage, an expert sales manager, using the information obtained 
-  analyzing the SOM cluster method results, removes some unrelated variables 
-  and selects the best variables to be considered in the forecasted model. 
+  directly from its database, a feature selection is carried out, as it is 
+  an effective dimensionality reduction technique and an essential preprocessing 
+  method to remove noise features \cite{Balaji2004}. The idea of these 
+  algorithms is searching the space of attribute subsets to find out which one 
+  in the data works best for classification or prediction.
+  In this stage, the information obtained using several feature selection 
+  methods as well as analyzing the SOM cluster method results is used to 
+  remove some unrelated variables and selects the best variables to be 
+  considered in the forecasted model. % we will use pre-sales data.
   This task may help to identify leading indicators to be used by the 

### 2015-10-13 paper.tex
removing the old text related to the variable selection process

@@
 However, in the case of new products, such as the issue of new books, past patterns 
-is difficult to observe as there is no available historical sales data \cite{ChingChin2010}.
+is difficult to observe as there is no available historical sales data 
+\cite{ChingChin2010} (only pre-sales data is available in this problem).
 
@@
 
-Thus, from the initial set of variables, the SOM \cite{kohonen1998} was applied 
-in order to reduce the dimensionality of the input data and to choose an 
-appropriate set of variables.
+Moreover, the algorithm runing times grow with the number of features, and thus 
+making the algorithm impractical for problems with a large number of features 
+\cite{Selvakuberan2008}. Feature selection task is usually carried out by 
+searching through all possible combinations of features, evaluating each one.
+
+During the evaluation, the set of all possible features is analyzed in order 
+to find the best set of features, ranking them according to some metric.
+In this process, the feature's predictive ability along with the degree 
+of redundancy between them is considered.
+
+Thus, in order to reduce the dimensionality of the input data and to choose an 
+appropriate set of variables, both the SOM \cite{kohonen1998} method and several 
+feature selection methods have been applied.
 
@@
 Also, the SOM graph represents and highlight very clearly those regions (clusters) 
-with high training sample concentration and fewer where the samples are scarce. %FERGU: mencionarlo en la intro
-
-As stated in Section \ref{sec:problem}, an expert sales manager collaborated in 
-this research in the stage of data analysis. Thus, the process was as follows:
-\begin{itemize}
-  \item First, the expert removed superfluous variables, and dimensionality was 
-  reduced from 50 to 43 inputs.
-  \item Then, the expert, using his knowledge and the information obtained 
-  analyzing the SOM results, removed some inputs, reducing the number of 
-  variables describing a book from 43 to 13.
-  \item The company asked to include the information about \emph{editorial} 
-  and \emph{materia}. Thus, in a new iteration, taking into account the expert's %FERGU: materia no existe en inglés. Subject?
-  advice and the information obtained analyzing the SOM results, the number of 
-  inputs was decreased to 7.
-  \item In a third step, several forecasting methods were used on the obtained 
-  dataset, and the best was chosen to obtain an accurate predicting model.
-  \item Finally, some information about the new book, such as \emph{author}, 
-  although not included in the obtained models, was taken into account by 
-  the expert sales manager to modify the forecasted results. 
-\end{itemize}
-
-  %  
-  %  El proceso que seguimos, resumido para el paper, es:
-  %  
-  %  [43 entradas] en 2013-01 vamos a tomar 
-  %  	pb_noneg.csv para obtener pb_ventas.csv (es el pb_ventas.arff)
-  %  	y hacer el SOM
-  %  
-  %  [13 entradas] en 2013-02-08 vamos a tomar 
-  %  	controlado_reducido.csv.arff (197 líneas)
-  %  	pbenero.csv.arff (5656 líneas)
-  %  	y hacer el SOM
-  %  
-  %  [7 entradas; materia editorial] en 2013-02-25 vamos a tomar
-  %  	pbRAWtrn.arff
-  %  	pbRAWtst.arff
-  %
-
-More specifically, in a first step, the expert analyzed the 50 input variables 
-describing each book to remove those that were superfluous.
-Table \ref{tabla:params43} shows the set of variables describing a book 
-(43 total inputs) that the expert manager determined as non-superfluous or 
-non-redundant.
-
-\begin{table}[!h]
-\caption{Variables describing a book (43 total inputs), after the expert 
-manager analized the original dataset provided by the company Trevenque to 
-remove some inputs.}
-\label{tabla:params43}
-\begin{center}
-\begin{tabular}{|c|c|}
-\hline
-
-\begin{minipage}{2.3in} \begin{verbatim}
-DEPARTMENT STORES POINTS OF SALE FIRST YEAR
-REST OF SALES FIRST YEAR
-NEGATIVE SALES ENVIRONMENT
-DISTRIBUTED THROUGH DEPARTMENT STORES FIRST YEAR
-TOTAL RETURNS
-REPRINTS
-MALL SALES FIRST YEAR
-TOTAL POINTS OF SALE FIRST YEAR
-UNITS DISTRIBUTED AS NOVELTY
-PRINT-RUN
-NUMBER OF REPRINTS
-RETURNS - DEPARTMENT STORES
-REST OF POINTS OF SALE FIRST YEAR
-REST OF SALES
-DELEGATES POINTS OF SALE
-REST OF RETURNS
-DELEGATES POINTS OF SALE FIRST YEAR
-POSITIVE SALES ENVIRONMENT
-REST OF DISTRIBUTED FIRST YEAR
-REST OF POINTS OF SALE
-TOTAL RETURNS FIRT YEAR
-DELEGATES RETURNS
-\end{verbatim} \end{minipage}     &
-
-\begin{minipage}{2.3in} \begin{verbatim}
-DEPARTMENT STORES SALES
-TOTAL DISTRIBUTED FIRST YEAR
-TOTAL POINTS OF SALE
-DISTRIBUTED THROUGH DEPARTMENT STORES
-DISTRIBUTED THROUGH DELEGATES FIRST YEAR
-POINTS OF SALE - DEPARTMENT STORES
-TOTAL SALES FIRST YEAR
-MEDIUM SALES ENVIRONMENT
-WEEKS FOR SALE
-DISTRIBUTED THROUGH DELEGATES
-AUTHOR
-DELEGATES SALES FIRST YEAR
-GIFTS
-RETURNS -  DEPARTMENT STORES  FIRST YEAR
-SALES THROUGH DELEGATES
-DISTRIBUTED - REST
-DELEGATES RETURNS FIRST YEAR
-TOTAL DISTRIBUTED
-REST OF RETURNS FIRST YEAR
-RETAIL PRICER
-TOTAL SALES (output)
-\end{verbatim} \end{minipage}    \\
-
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-%FERGU: para ahorrar espacio se puede hacer la tabla inversa: variables que se han quitado (las 7)
-%[pedro] no entiendo muy bien a qué te refieres...
-
-Then, after analyzing the original dataset using the SOM to select the best %FERGU: parametros o framework SOM usados?
-variables to be considered, and taking into account the knowledge of the company 
-experienced manager, 13 inputs were considered. 
-Figure \ref{fig:som43} shows the initial analysis of dataset using the total 
-of 43 descriptive inputs per book.
-Table \ref{tabla:params13} shows the set of variables describing a book after 
-the second analysis.
-	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
-	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
-	% datos serios de análisis estadístico de las variables. 
-	% [Pedro] sí, estoy de acuerdo. Esto va con el ISSUE #6
-\begin{figure}[!h] 
-\begin{center}
-\begin{tabular}{c}
-  \epsfig{file=som43vars.eps,width=11cm} \\
-  \epsfig{file=som43umatrix.eps,width=5cm}
-\end{tabular}
-\caption{\small{Initial data analysis, using 43 descriptive variables per book, %FERGU: la figura está en español, pero ya lo sabréis :P
-using SOM.}}
-	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
-	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
-	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
-        % Sería más bien exploratory data analysis o data visualization. 
-        % Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
-\label{fig:som43}
-\end{center}
-\end{figure}
-
-\begin{table}[!h]
-\caption{Variables that describe every book, 13 in total, after the
-  second analysis carried out using the SOM along with the company
-  experienced manager % él no hizo el análisis. No cuela con ``along with'' - JJ
-to select the best variables to be considered to
-  solve the sales forecasting problem.} 
-\label{tabla:params13}
-\begin{center}
-\begin{tabular}{|c|}
-\hline
-
-\begin{minipage}{2.3in} \begin{verbatim}
-TOTAL RETURNS
-REPRINTS
-TOTAL POINTS OF SALE FIRST YEAR
-UNITS DISTRIBUTED AS NOVELTY
-NUMBER OF REPRINTS
-TOTAL RETURNS FIRT YEAR
-TOTAL DISTRIBUTED FIRST YEAR
-TOTAL POINTS OF SALE
-WEEKS FOR SALE
-TOTAL DISTRIBUTED
-RETAIL PRICER
-PRINT-RUN
-TOTAL SALES (output)
-\end{verbatim} \end{minipage}     \\
-
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Finally, after analyzing the dataset with 13 descriptive inputs per %FERGU: describis los resultados antes de explicar que volveis a hacer SOM
-book, and paying attention to the company experienced manager's
-recommendations, 7 inputs were considered; specifically, variables
-\emph{EDITORIAL} and \emph{SUBJECT} were included, while %FERGU: vale, no useis SUBJECT, usad mejor SUBJECT (SUBJECT es materia de física, creo xD).    ok, ¡gracias!
-\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
-  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
-  WEEKS FOR SALE, PRINT-RUN} were discarded.  
-	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
-	% ¿Análisis de varianza? - jj
-	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
-Figure \ref{fig:som13} shows the initial analysis of dataset using the SOM on 
-the total of 13 descriptive inputs per book.
-This, along with the expert manager knowledge determined the final 7 inputs 
-to be considered.
-Table \ref{tabla:params7} shows the final set of variables describing a book, 
-taking into account the company experienced manager knowledge.
-
-\begin{figure}[!h] 
-\begin{center}
-\begin{tabular}{c}
-  \epsfig{file=som13vars.eps,width=11cm} \\
-  \epsfig{file=som13umatrix.eps,width=5cm}
-\end{tabular}
-\caption{\small{Analysis of the initial data, using 13 descriptive variables per book, using the SOM.}} % Análisis de los datos iniciales, usando 13 variables descriptivas por libro, utilizando el SOM.}} %FERGU: teniais esto en español, lo he traducido al inglés :)
-% describir de forma más precisa: visualización usando UMatrix de... - JJ
-% ¡y usar nombres en inglés para las variables! - JJ
-%[pedro] es el siguiente arreglo que le haré mañana al paper    ;)
-\label{fig:som13}
-\end{center}
-\end{figure}
-
-\begin{table}[!h]
-\caption{Final set of variables describing a book, taking into account the company 
-experienced manager knowledge, to be considered to solve the sales forecasting problem.}
-\label{tabla:params7}
-\begin{center}
-\begin{tabular}{|c|}
-\hline
-
-\begin{minipage}{2.3in} \begin{verbatim}
-UNITS DISTRIBUTED IN FIRST EDITION
-TOTAL SELLING POINTS
-TOTAL DISTRIBUTED
-RETAIL PRICE
-SUBJECT
-EDITORIAL
-TOTAL SALES (output)
-\end{verbatim} \end{minipage}     \\
-
-\hline
-\end{tabular}
-\end{center}
-\end{table}
+with high training sample concentration and fewer where the samples are scarce. 
+%FERGU: mencionarlo en la intro
+
+As far as the feature selection methods are concerned, both a correlation-based 
+feature subset evaluation method (CfsSubsetEval) \cite{Hall1998} and an 
+adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation 
+method \cite{RobnikSikonja1997} are used with two search criteria: BestFirst, 
+that searches the space of feature subsets by greedy hill-climbing augmented 
+with a backtracking facility, and Ranker, that ranks features by their individual 
+evaluations.
 

### 2015-10-13 paper.tex
add new contents explaining the feature selection methods used
fixing some broken refs

@@
   an effective dimensionality reduction technique and an essential preprocessing 
-  method to remove noise features \cite{Balaji2004}. The idea of these 
+  method to remove noise features \cite{Krishnapuram2004}. The idea of these 
   algorithms is searching the space of attribute subsets to find out which one 
@@
 
+%
+% TODO: explicar los resultados obtenidos en la selección de variables (1) con el SOM (2) con los métodos de selecc. vars.
+%
+
 Once the methods to be applied have been chosen, they must be applied to data sets 
@@
 practice. %, limiting at the same time the overfitting problem.
-
-  %  El proceso que seguimos, resumido para el paper, es:
-  %  
-  %  [43 entradas] en 2013-01 vamos a tomar 
-  %  	pb_noneg.csv para obtener pb_ventas.csv (es el pb_ventas.arff)
-  %  
-  %  [13 entradas] en 2013-02-08 vamos a tomar 
-  %  	controlado_reducido.csv.arff (197 líneas)
-  %  	pbenero.csv.arff (5656 líneas)
-  %  
-  %  [7 entradas; materia editorial] en 2013-02-25 vamos a tomar
-  %  	pbRAWtrn.arff
-  %  	pbRAWtst.arff
 

### 2015-10-16 paper.tex
results section

@@
 
-%
-% TODO: explicar los resultados obtenidos en la selección de variables (1) con el SOM (2) con los métodos de selecc. vars.
-%
-
 Once the methods to be applied have been chosen, they must be applied to data sets 
@@
 
+%
+% TODO: explicar los resultados obtenidos en la selección de variables: 
+%  (1) con el SOM, (2) con los métodos de selecc. vars.
+%
 % CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
@@
 % - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
-% -
+To do so, in a first stage, the feature selection process has been carried out 
+using both the CfsSubsetEval \cite{Hall1998} (a correlation-based feature subset 
+evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
+adaptation of relief for attribute estimation) evaluation methods.
+
+% con ReliefFAttributeEval salen seleccionadas (9):
+% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
+Using the ReliefFAttributeEval feature selection method, and taking into account 
+the best ranked atributes, the following variables have been selected: 
+\emph{print_run, num_reprints, tot_points_sale, tot_points_sale_1st_year, reprints, distrib_novelty, weeks_sale, total_sales}.
+
+% con CfsSubsetEval salen seleccionadas (4):
+% num_reprints tot_points_sale print_run + total_sales
+Using the CfsSubsetEval feature selection method, the following variables have 
+been selected: \emph{num_reprints, tot_points_sale, print_run, total_sales}.
+
+% como tercer método, se ha usado el SOM; tras interpretar los mapas, se
+% seleccionaron las variables más adecuadas.
+Then, an exhaustive analisys of the SOM results was carried out in order to 
+determine the best variables to be considered to buid the forecasting model.
+
+\textbf{ TODO: add the SOM analisys }
+
+Once the different reduced datasets have been obtained, proposed methods 
+(M5P, LR, SVM, kNN, MLP) have been selected for this study from 
+the Weka implementation, and they were run 30 times with the Weka default parameter 
+settings and a different random initialization seed for each run.
 
@@
 (4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.
-
-Proposed methods (M5P, LR, SVM, kNN, MLP) have been selected for this study from 
-the Weka implementation, and they were run 30 times with the Weka default parameter 
-settings and a different random initialization seed for each run.
 

### 2015-10-16 paper.tex
working in the results section

@@
 This initial data set, provided in the framework of a contract by
-Trevenque Editorial, included 3159 books, and included descriptive information for each book includes price, 
-points of sale, subject, publisher, sales, returns, among other information.
+Trevenque Editorial, included 3159 books, and included descriptive information 
+for each book, such as price, points of sale, subject, publisher, sales, returns, 
+among other information.
 Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-REFERENCE
-AUTHOR
-RETAIL PRICER
-SUBJECT1
-SUBJECT2
-SUBJECT3
-EDITORIAL
-COLLECTION
-BOOKBINDING
-PRINT-RUN
-TOTAL SALES
-DEPARTMENT STORES SALES
-SALES THROUGH DELEGATES
-REST OF SALES
-TOTAL SALES FIRST YEAR
-MALL SALES FIRST YEAR
-DELEGATES SALES FIRST YEAR
-REST OF SALES FIRST YEAR
-TOTAL DISTRIBUTED
-DISTRIBUTED THROUGH DEPARTMENT STORES
-DISTRIBUTED THROUGH DELEGATES
-DISTRIBUTED - REST
-TOTAL DISTRIBUTED FIRST YEAR
-DISTRIBUTED THROUGH DEPARTMENT STORES FIRST YEAR
-DISTRIBUTED THROUGH DELEGATES FIRST YEAR
+reference
+author
+retail pricer
+subject1
+subject2
+subject3
+editorial
+collection
+bookbinding
+print-run
+total sales
+department stores sales
+sales through delegates
+rest of sales
+total sales first year
+mall sales first year
+delegates sales first year
+rest of sales first year
+total distributed
+distributed through department stores
+distributed through delegates
+distributed - rest
+total distributed first year
+distributed through department stores first year
+distributed through delegates first year
 \end{verbatim} \end{minipage}     &
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-REST OF DISTRIBUTED FIRST YEAR
-REPRINTS
-NUMBER OF REPRINTS
-TOTAL RETURNS
-RETURNS - DEPARTMENT STORES
-DELEGATES RETURNS
-REST OF RETURNS
-TOTAL RETURNS FIRT YEAR
-RETURNS -  DEPARTMENT STORES  FIRST YEAR
-DELEGATES RETURNS FIRST YEAR
-REST OF RETURNS FIRST YEAR
-GIFTS
-UNITS DISTRIBUTED AS NOVELTY
-TOTAL POINTS OF SALE
-POINTS OF SALE - DEPARTMENT STORES
-DELEGATES POINTS OF SALE
-REST OF POINTS OF SALE
-TOTAL POINTS OF SALE FIRST YEAR
-DEPARTMENT STORES POINTS OF SALE FIRST YEAR
-DELEGATES POINTS OF SALE FIRST YEAR
-REST OF POINTS OF SALE FIRST YEAR
-WEEKS FOR SALE
-POSITIVE SALES ENVIRONMENT
-MEDIUM SALES ENVIRONMENT
-NEGATIVE SALES ENVIRONMENT
+rest of distributed first year
+reprints
+number of reprints
+total returns
+returns - department stores
+delegates returns
+rest of returns
+total returns firt year
+returns -  department stores  first year
+delegates returns first year
+rest of returns first year
+gifts
+units distributed as novelty
+total points of sale
+points of sale - department stores
+delegates points of sale
+rest of points of sale
+total points of sale first year
+department stores points of sale first year
+delegates points of sale first year
+rest of points of sale first year
+weeks for sale
+positive sales environment
+medium sales environment
+negative sales environment
 \end{verbatim} \end{minipage}    \\
@@
 evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
-adaptation of relief for attribute estimation) evaluation methods.
+adaptation of relief for attribute estimation) evaluation methods, implemented 
+in the Weka tool.
 
@@
 the best ranked atributes, the following variables have been selected: 
-\emph{print_run, num_reprints, tot_points_sale, tot_points_sale_1st_year, reprints, distrib_novelty, weeks_sale, total_sales}.
+\emph{print-run, number of reprints, total points of sale, total points of sale 1st year, reprints, units distributed as novelty, weeks for sale, total sales}.
 
@@
 Using the CfsSubsetEval feature selection method, the following variables have 
-been selected: \emph{num_reprints, tot_points_sale, print_run, total_sales}.
+been selected: \emph{number of reprints, total points of sale, print-run, total sales}.
 
@@
 
+%
+% TODO: falta incluir aquí el análisis de los mapas SOM.
+% Determinar las variables a usar, según el SOM
 \textbf{ TODO: add the SOM analisys }
+% una vez hecho, hay que hacer las ejecuciones para ese dataset.
 
@@
 the Weka implementation, and they were run 30 times with the Weka default parameter 
-settings and a different random initialization seed for each run.
+settings and a different random initialization seed for each run and each dataset.
 
@@
 (4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.
+
+% datasets:
+%  original (all vars)
+%  4 vars
+%  9 vars
+%  SOM selected vars
 

### 2015-10-19 paper.tex
working in the results section (updating tables)

@@
 the best ranked atributes, the following variables have been selected: 
-\emph{print-run, number of reprints, total points of sale, total points of sale 1st year, reprints, units distributed as novelty, weeks for sale, total sales}.
+\emph{print-run, number of reprints, total points of sale, total points of sale 
+first year, reprints, units distributed as novelty, weeks for sale, total sales}.
 
@@
 % datasets:
-%  original (all vars)
+%  original (16 vars)
 %  4 vars
@@
 
-Table \ref{tabla:results13} shows obtained results (time to build the model and 
-error) after applying the proposed forecasting methods on the dataset with 13 
-variables per book.
-In this dataset, every book is described using numerical variables, and thus, 
-processing the data to build the different models is a fast task despite the 
-number of instances.
+Table \ref{tabla:resultsT} shows obtained results (time to build the model and 
+error) after applying the proposed forecasting methods on the original dataset,
+using the 16 available variables per book.
+In this dataset, every book is described using not only numerical variables, 
+but using two additional categorical variables, \emph{editorial} and \emph{collection}, 
+what makes harder to process the instances and build the different models.
 
@@
 \caption{\small{Results (errors and time) obtained using the different
-    forecasting methods on the dataset with 13 variables per book.}} 
-\label{tabla:results13}
+    forecasting methods on the original dataset (16 variables per book).}} 
+\label{tabla:resultsT}
 \end{table*}
@@
 Obtained results (time to build the model and error) using the different 
-forecasting methods on the dataset with 7 variables per book can be shown 
-in Table \ref{tabla:results7}.
-Although in this dataset each book is described using a smaller number of 
-variables, two categorical variables, \emph{EDITORIAL} and \emph{SUBJECT}, are 
-included, what that makes harder to process the instances and build the different 
-models.
+forecasting methods on the dataset with 9 variables per book (obtained 
+using the ReliefFAttributeEval feature selection method) can be shown 
+in Table \ref{tabla:results9}.
+In this dataset, every book is described using numerical variables, and thus, 
+processing the data to build the different models is a fast task.
 
-  %[pedro] ya están todos los resultados de de tabla:results7 (MP5, LR, KNN, SVM, MLP)
 \begin{table*}[!h]
@@
 \caption{\small{Results (errors and time) obtained using the different 
-forecasting methods on the dataset with 7 variables per book.}}
-\label{tabla:results7} %FERGU: es normal que con menos variables tarde más? Sí, el uso de MATERIA y EDITORIAL hacen que el conjunto sea endiablado.
+forecasting methods on the dataset with 9 variables per book.}}
+\label{tabla:results9}
+\end{table*}
+
+Finally, obtained results (time to build the model and error) using the different 
+forecasting methods on the dataset with 4 variables per book (obtained 
+using the CfsSubsetEval feature selection method) can be shown 
+in Table \ref{tabla:results4}.
+As in the previous case, in this dataset every book is described using numerical 
+variables. Thus, due to the number of features per book, building the different 
+models is faster than in the previous cases.
+
+\begin{table*}[!h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline 
+ Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
+\hline
+  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
+\hline
+  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
+\hline
+  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
+\hline
+  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
+\hline
+  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
+\hline
+\end{tabular}
+\end{center}
+\caption{\small{Results (errors and time) obtained using the different 
+forecasting methods on the dataset with 4 variables per book.}}
+\label{tabla:results4}
 \end{table*}

### 2015-10-19 paper.tex
working in the results section (updating tables and comments)

@@
 % TODO: falta incluir aquí el análisis de los mapas SOM.
-% Determinar las variables a usar, según el SOM
+%*************************************** Determinar las variables a usar, según el SOM
 \textbf{ TODO: add the SOM analisys }
@@
 \hline
-  M5P 		& 2.94 $\pm$ 0.51 	  & 65.49 	& 133.73 	& 11.10 	 & 9.17 	  \\
-\hline
-  LR 		  & 0.33 $\pm$ 0.07 	  & 100.813 & 257.63 	& 17.09 	 & 17.67 	\\
-\hline
-  SVM 		& 49.10 $\pm$ 8.05	  & 52.30	  & 139.45	& 8.87     & 9.56  	\\
-\hline
-  kNN 		& 0.03 $\pm$ 0.01 	  & 198.16 	& 542.93 	& 33.59 	 & 37.24 	\\
-\hline
-  MLP 		& 12.70 $\pm$ 3.08 	  & 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
+  M5P 		& 23.13 $\pm$ 4.22    & 197.48  & 577.28  & 35.21    & 41.85  \\
+\hline
+  LR 		  & 3327.87 $\pm$ 607.58& 247.22 & 561.67  & 44.08    & 40.71    \\
+\hline
+  SVM 		& 5425.68 $\pm$ 990.59& 215.69  & 574.76  & 38.46    & 41.66  \\
+\hline
+  kNN 		& 0.02 $\pm$ 0.00     & 302.07 	& 924.94 	& 53.86 	 & 67.05 	\\
+\hline
+  MLP 		& - 	  & - 	& - 	& - 	& - 	\\
 \hline
@@
 \caption{\small{Results (errors and time) obtained using the different
-    forecasting methods on the original dataset (16 variables per book).}} 
+    forecasting methods on the original dataset (16 variables per book). 
+    In this case, due to the categorial variables, the MLP could not be run.}} 
 \label{tabla:resultsT}
 \end{table*}
+
+%***************************************
+\textbf{ TODO: add the table of results obtained using the variables selected taking into account the SOM analysis }
 
@@
 \hline
-  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
-\hline
-  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
-\hline
-  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
-\hline
-  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
-\hline
-  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
+  M5P     & 2.27 $\pm$ 0.02     & 195.97  & 629.33  & 34.94    & 45.62  \\
+\hline
+  LR      & 0.38 $\pm$ 0.01     & 256.19  & 549.19  & 45.68    & 39.81   \\
+\hline
+  SVM     & 132.64 $\pm$ 2.86   & 230.66  & 613.27  & 41.12    & 44.45   \\
+\hline
+  kNN     & 0.06 $\pm$ 0.01     & 214.76  & 551.33  & 38.29    & 39.96   \\
+\hline
+  MLP     & 130.77 $\pm$ 1.51   & 326.60 $\pm$ 75.77 & 687.61 $\pm$ 55.70  & 58.23 $\pm$ 13.51  & 49.84 $\pm$ 4.04   \\
 \hline
@@
 \hline
-  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
-\hline
-  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
-\hline
-  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
-\hline
-  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
-\hline
-  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
+  M5P     & 2.02 $\pm$ 0.01     & 205.52  & 556.90  & 36.64     & 40.37  \\
+\hline
+  LR      & 0.32 $\pm$ 0.00     & 261.04  & 547.42  & 46.54     & 39.68   \\
+\hline
+  SVM     & 81.74 $\pm$ 1.66    & 242.26  & 606.07   & 43.19    & 43.93   \\
+\hline
+  kNN     & 0.05 $\pm$ 0.00     & 216.05  & 506.34  & 38.52    & 36.70   \\
+\hline
+  MLP     & 47.80 $\pm$ 0.51    & 318.29 $\pm$ 43.96 & 587.50 $\pm$ 51.50  & 56.75 $\pm$ 7.84  & 42.59 $\pm$ 3.73   \\
 \hline
@@
 % - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
-Paying attention to the obtained results shown in tables \ref{tabla:results13} 
-and \ref{tabla:results7}, using those categorical variables as part of a big 
-data set makes the problem hard to solve, both in required time to build the 
-forecasting models as well as in the obtained errors.
-However, as stated before, Trevenque expert sales manager, taking into account 
-his knowledge in industry experience and their perceptions, decided that 
-\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.
+Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
+\ref{tabla:results9} and \ref{tabla:results4}, using those categorical variables 
+as part of a big data set makes the problem hard to solve, both in required 
+time to build the forecasting models as well as in the obtained errors.
+Moreover, some methods are unable to build the models in a reasonable time.
+%However, as stated before, Trevenque expert sales manager, taking into account 
+%his knowledge in industry experience and their perceptions, decided that 
+%\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.
 
@@
 Taking into account the SVM model obtained results, this method obtains the lower 
-%FERGU: "the best errors" no se sabe si es lo mejor o lo peor xDD Pon "worst results" o así
 errors. Even when used using the default parameter values it exhibit a good 
@@
 However, it is much slower than the others to build the model, not only when 
-using the data set with 13 input variables, but when using the data set with %FERGU: a veces pones dataset: unificarlo
-7 input variables (including \emph{EDITORIAL} and \emph{SUBJECT}).
+using the dataset with categorical input variables, but also when using the 
+datasets with numerical variables.
 
@@
 to explain how the forecasts are obtained.
-In these experiments, the MLP requires a higher time than other methods, but also
-the obtained errors are worse as no parameter tuning to build the models have
-been carried out.
-Also, the difficulty to process information related to variables \emph{EDITORIAL} 
-and \emph{SUBJECT} might affect the worse results obtained on the final dataset.
+Moreover, in these experiments it has been seen the difficulty to process 
+information related to categorial variables, such as \emph{editorial} and 
+\emph{collection}.
 

### 2015-10-19 paper.tex
working in the results section (updating tables and comments)

@@
 %*************************************** Determinar las variables a usar, según el SOM
-\textbf{ TODO: add the SOM analisys }
+\textbf{ TODO: add the SOM analysis }
 % una vez hecho, hay que hacer las ejecuciones para ese dataset.
@@
 
+Obtained results (time to build the model and error) using the different 
+forecasting methods on the dataset with X variables per book (obtained 
+using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
+%In this dataset, every book is described using numerical variables, and thus, 
+%processing the data to build the different models is a fast task.
 %***************************************
-\textbf{ TODO: add the table of results obtained using the variables selected taking into account the SOM analysis }
+% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
+\begin{table*}[!h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline 
+ Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
+\hline
+  M5P     & x $\pm$ y     & x  & x  & x    & x  \\
+\hline
+  LR      & x $\pm$ y     & x  & x  & x    & x  \\
+\hline
+  SVM     & x $\pm$ y     & x  & x  & x    & x  \\
+\hline
+  kNN     & x $\pm$ y     & x  & x  & x    & x  \\
+\hline
+  MLP     & x $\pm$ y   & x $\pm$ y & x $\pm$ y  & x $\pm$ y  & x $\pm$ y   \\
+\hline
+\end{tabular}
+\end{center}
+\caption{\small{Results (errors and time) obtained using the different 
+forecasting methods on the dataset obtained after the SOM analysis.}}
+\label{tabla:resultsSOM}
+\end{table*}
 

### 2015-10-19 paper.tex
comments on figures

@@
 
+\begin{figure}[!h] 
+\begin{center}
+  \epsfig{file=fig_time.eps,width=7cm}
+\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one).
+Plot shows that using categorical variables as part of the dataset makes the problem hard to solve.
+As was expected, simpler methods are much faster to build the model than the complex ones.}}
+\label{fig:time}
+\end{center}
+\end{figure}
+
+\begin{figure}[!h] 
+\begin{center}
+  \epsfig{file=fig_rae.eps,width=7cm}
+\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one).
+The M5P model obtains the lowest errors, whatever the dataset used.}}
+\label{fig:rae}
+\end{center}
+\end{figure}
+
 % - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
 Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
-\ref{tabla:results9} and \ref{tabla:results4}, using those categorical variables 
-as part of a big data set makes the problem hard to solve, both in required 
-time to build the forecasting models as well as in the obtained errors.
+\ref{tabla:resultsSOM}, \ref{tabla:results9} and \ref{tabla:results4}, 
+as well as the figures \ref{fig:time} and \ref{fig:rae}, 
+using those categorical variables as part of a big dataset makes the problem 
+hard to solve, both in required time to build the forecasting models as well as 
+in the obtained errors.
 Moreover, some methods are unable to build the models in a reasonable time.
@@
 
-The Linear Regression model outperforms other complex methods, both in time 
+The Linear Regression model outperforms some other complex methods, both in time 
 (as it is a simple method to train) and in obtained errors.
-However, more powerful models, that obtain better results, can be obtained in 
-comparable time.
-
-Taking into account the SVM model obtained results, this method obtains the lower 
-errors. Even when used using the default parameter values it exhibit a good 
-generalization performance.
+However not in all cases, as more powerful models that obtain better results 
+can be obtained in comparable time.
+
+Taking into account the SVM model obtained results, this method obtains comparable 
+errors to those of M5P. Even when used using the default parameter values it exhibit 
+a good generalization performance.
 However, it is much slower than the others to build the model, not only when 

### 2015-10-22 paper.tex
changing the type of graphics (from 3D-bars to line plot grouped by color)
updating Tables of Results (16-vars)
fixing&improving the text, tanking into account some comments (thanks)

@@
 such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
-or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
-                                % do? What are the results?
+or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they do? What are the results?
 
@@
 when a new book is published is faced using data provided by the 
-Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
-The company's expert sales managers analyzed historical data 
+Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}},
+a company that provides management systems and services for libraries, 
+publishers and distributors. 
+Usually, the company's expert sales managers analyzed historical data 
 and applied their knowledge using external variables to calculate
@@
                         %  y que así era como funcionaban hasta ese momento.
-
-%In any case, in general companies usually use a forecasting model and then, an expert applies his knowledge, as the company might require an interpretable and understandable model.
-
+%In any case, in general companies usually use a forecasting model and then, 
+%an expert applies his knowledge, as the company might require an 
+%interpretable and understandable model. 
 However, carrying out the analysis and forecasting process as described,
@@
 
-This is the new book sales forecasting case, for which no historical data 
-to make predictions \cite{ChingChin2010,FaderHardie2005,Madsen2008} is available
-and only some descriptive variables relative to the new unpublished-book are available.
+This is the new book sales forecasting case, a problem with issues such as 
+dealing with limited data, finding adequate forecasting methods and selecting 
+the best method to use \cite{ChingChin2010}.
+In the case of new unpublished-books, there is no historical data to define 
+patterns, and only some descriptive data about the new book is available 
+\cite{ChingChin2010,FaderHardie2005,Madsen2008}.
+Thus, not any timeseries-based forecasting method can be used \cite{Madsen2008,ChernWSF15}.
+
+%This is the new book sales forecasting case, for which no historical data to make predictions is available \cite{ChingChin2010,FaderHardie2005,Madsen2008} and only some descriptive variables relative to the new unpublished-book are available.
+
+%Forecasting sales of new books is a problem with issues such as dealing with limited data, finding adequate forecasting methods and selecting the best method to use \cite{ChingChin2010}.
+
+%In the case of already published books, available historical data might help to generate predictive models.
+%However, in the case of new books there is no historical data to define patterns, and only some descriptive data about the new book is available. 
+%In these cases not any timeseries-based forecasting method can be used \cite{Madsen2008,ChernWSF15}.
+
+%An additional issue is the difficulty to compare our model with classical forecasting methods, such as time series prediction methods, since books do not have specific sales time series.
 
@@
 in Spain for several years, including those descriptive variables.
-%
+
 %%% Principio de párrafos a eliminar o mover a estado del arte.
-%Después de esto no sé si merece la pena dejar este párrafo.
-Forecasting sales of new books is a problem with issues 
-such as dealing with limited data, finding adequate forecasting methods and 
-selecting the best method to use \cite{ChingChin2010}. % He cambiado
-                                % esto, pero sigue sin decir
-                                % absolutamente nada. "The problem"
-                                % tiene que describir el problema: qué
-                                % queremos hacer, qué tenemos - JJ
-
-% Este párrafo o se borra o se traslada al estado del arte. Aquí hay
-% que contar cuál es el problema y qué se tiene. No se puede volver a
-% repetir lo de antes.
-In the case of already published books, available historical data might help 
-to generate predictive models.
-However, in the case of new books there is no historical data to define patterns, 
-and only some descriptive data about the new book is available. 
-%FERGU: data es plural. is->are   ...a mí me suena bien con "is"   ¡una segunda opinión!   ;)
-In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.
-
-% Vale, más issues. Este párrafo también puede quedar fuera. Ya has
-% dicho que no se puede usar la serie histórica.
-An additional issue is the difficulty to compare our model with classical 
-forecasting methods, such as time series prediction methods, since books 
-do not have specific sales time series.
-
-Throughout this research, we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
-a company that provides management systems and services for libraries, publishers 
-and distributors. % Esto tampoco viene a cuento. Se dice en la intro o
-                  % se cuenta como gente que nos ha proporcionado los
-                  % datos y nos contrató para hacerlo.
-
-Trevenque company, whose expert manager advised this research,
-provided %FERGU: los párrafos anteriores son un poco dispersos, puedes
-         %quitar los puntos y aparte y agruparlos por temas (por
-         %ejemplo, todo lo de Trevenque debería de ir en un párrafo) 
-% O borrarlos - JJ
 %% Fin de párrafos a eliminar.
-This initial data set, provided in the framework of a contract by
+  % [pedro] eliminados
+
+The initial data set, provided in the framework of a contract by
 Trevenque Editorial, included 3159 books, and included descriptive information 
@@
 \hline
-  M5P 		& 23.13 $\pm$ 4.22    & 197.48  & 577.28  & 35.21    & 41.85  \\
-\hline
-  LR 		  & 3327.87 $\pm$ 607.58& 247.22 & 561.67  & 44.08    & 40.71    \\
-\hline
-  SVM 		& 5425.68 $\pm$ 990.59& 215.69  & 574.76  & 38.46    & 41.66  \\
+  M5P 		& 24.24 $\pm$ 0.96    & 197.48  & 577.28  & 35.21    & 41.85  \\
+\hline
+  LR 		  & 3533.84 $\pm$ 178.38& 247.22 & 561.67  & 44.08    & 40.71    \\
+\hline
+  SVM 		& 5586.96 $\pm$ 139.71& 215.69  & 574.76  & 38.46    & 41.66  \\
 \hline
@@
 \begin{center}
-  \epsfig{file=fig_time.eps,width=7cm}
+  \epsfig{file=fig_time.eps,width=11cm}
 \caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one).
@@
 \begin{center}
-  \epsfig{file=fig_rae.eps,width=7cm}
+  \epsfig{file=fig_rae.eps,width=11cm}
 \caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one).

### 2015-10-22 paper.tex
fixing&improving the text, tanking into account some comments (thanks)

@@
 
-\begin{minipage}{2.3in} \begin{verbatim}
+\begin{minipage}{2.45in} \begin{verbatim}
 reference
@@
 total sales
-department stores sales
+dept stores sales
 sales through delegates
 rest of sales
-total sales first year
-mall sales first year
-delegates sales first year
-rest of sales first year
+total sales 1st year
+mall sales 1st year
+delegates sales 1st year
+rest of sales 1st year
 total distributed
-distributed through department stores
+distributed through dept stores
 distributed through delegates
 distributed - rest
-total distributed first year
-distributed through department stores first year
-distributed through delegates first year
+total distributed 1st year
+distrib. through dept stores 1st year
+distrib. through delegates 1st year
 \end{verbatim} \end{minipage}     &
@@
 \begin{minipage}{2.3in} \begin{verbatim}
-rest of distributed first year
+rest of distributed 1st year
 reprints
@@
 total returns
-returns - department stores
+returns - dept stores
 delegates returns
@@
 total returns firt year
-returns -  department stores first year
-delegates returns first year
-rest of returns first year
+returns -  dept stores 1st year
+delegates returns 1st year
+rest of returns 1st year
 gifts
@@
 total points of sale
-points of sale - department stores
+points of sale - dept stores
 delegates points of sale
 rest of points of sale
-total points of sale first year
-department stores points of sale first year
-delegates points of sale first year
-rest of points of sale first year
+total points of sale 1st year
+dept stores points of sale 1st year
+delegates points of sale 1st year
+rest of points of sale 1st year
 weeks for sale
@@
 
-In this prediction problem, several variables related to the own book affect 
-the forecasts, such as author, price, subject or publisher. %This has
-                                %to be grounded by the experiment and
-                                %graphs.
-
-However, there are other external variables that also affect the sales of 
-a new book, such as those related to seasonality, trends or promotions, 
-that classical prediction methods can not deal with.
+In this prediction problem there are other external variables that also affect 
+the sales of a new book, such as those related to seasonality, trends or 
+promotions, that classical prediction methods can not deal with.
 However, an expert can consider them to modify the forecast obtained by 
@@
   \epsfig{file=stages.eps,width=7cm}
-\caption{\small{Three main stages in this research: data analysis, (2) forecasting 
+\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
 methods testing, and (3) subjectively adjusting the obtained results.}}
@@
 
-Thus, in this study we propose three main stages (see Figure \ref{fig:stages} %FERGU: there are->we propose
-for details): 
+Thus, in this study two main stages are proposed: 
 \begin{itemize}
@@
 
-  \item  Finally, in some cases, it is necessary a third stage where experienced 
-  managers adjust subjectively the results obtained using the forecasting methods. 
+\end{itemize}
+
+In some cases, depending on the company needs and after obtaining the forecasting 
+results, it is necessary a third stage where experienced 
+managers adjust subjectively the results obtained using the forecasting methods 
+(see Figure \ref{fig:stages} for details). 
 They might manually adjust the forecasting results taking into account their 
 knowledge in industry experience and their perception about trends.
-
-\end{itemize}
 
@@
 \emph{print-run, number of reprints, total points of sale, total points of sale 
-first year, reprints, units distributed as novelty, weeks for sale, total sales}.
+1st year, reprints, units distributed as novelty, weeks for sale, total sales}.
 
@@
 %*************************************** Determinar las variables a usar, según el SOM
+\textbf{ TODO: add the SOM analysis }
+
+\textbf{ TODO: add the SOM analysis }
+
 \textbf{ TODO: add the SOM analysis }
@@
 Obtained results (time to build the model and error) using the different 
-forecasting methods on the dataset with X variables per book (obtained 
+forecasting methods on the dataset \textbf{with X variables} per book (obtained 
 using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
@@
 the new book. 
-This, compared to the black-box models such as the artificial neural network 
-was decisive from the point of view of the needs of experts and the company.
+This, compared to the black-box models such as the artificial neural network, 
+was decisive from the point of view of the needs of experts and Trevenque company.
 Moreover, proposed method was validated by the company and incorporated in a 
@@
 \section*{Acknowledgements}
-This work has been supported in part by PreTEL (PRM Consultores - Trevenque),
-SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 
-and TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
-SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14
-(Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
-IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17
-GENIL project (CEI-BIOTIC Granada). 
-    % ¿Y el contrato con Trevenque?  - JJ
-    %[pedro] añadido
+This work has been supported in part by 
+PreTEL (PRM Consultores - Trevenque),
+TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
+SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), 
+PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
+IX Convocatoria de Proyectos de Investigaci{\'o}n), 
+and PYR-2014-17 GENIL project (CEI-BIOTIC Granada).
 

### 2015-10-30 paper.tex
fixing&improving the text, tanking into account some comments (thanks)
fixing a detail

@@
 Obtained results (time to build the model and error) using the different 
-forecasting methods on the dataset \textbf{with X variables} per book (obtained 
+forecasting methods on the dataset with 7 variables per book (obtained 
 using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
@@
 Obtained results (time to build the model and error) using the different 
-forecasting methods on the dataset with 9 variables per book (obtained 
+forecasting methods on the dataset with 8 variables per book (obtained 
 using the ReliefFAttributeEval feature selection method) can be shown 
@@
 Plot shows that using categorical variables as part of the dataset makes the problem hard to solve.
-As was expected, simpler methods are much faster to build the model than the complex ones.}}
+As expected, simpler methods are much faster to build the model than the complex ones.}}
 \label{fig:time}

### 2015-10-31 paper.tex
results obtained using the dataset with features selected using SOM
adding details about the features selected using the SOM

@@
 
-\textbf{ TODO: add the SOM analysis }
+After the SOM analysis, the following variables have been selected: 
+\emph{retail pricer, reprints, number of reprints, gifts, units distributed as novelty, print-run, total sales }.
 
@@
 \hline
-  M5P     & x $\pm$ y     & x  & x  & x    & x  \\
-\hline
-  LR      & x $\pm$ y     & x  & x  & x    & x  \\
-\hline
-  SVM     & x $\pm$ y     & x  & x  & x    & x  \\
-\hline
-  kNN     & x $\pm$ y     & x  & x  & x    & x  \\
-\hline
-  MLP     & x $\pm$ y   & x $\pm$ y & x $\pm$ y  & x $\pm$ y  & x $\pm$ y   \\
+  M5P     & 1.74 $\pm$ 0.10     & 218.81  & 661.85  & 39.01    & 47.98  \\
+\hline
+  LR      & 0.27 $\pm$ 0.02     & 258.82  & 582.74  & 46.15    & 42.24  \\
+\hline
+  SVM     & 45.58 $\pm$ 1.89    & 240.18  & 614.30  & 42.82    & 44.53  \\
+\hline
+  kNN     & 0.04 $\pm$ 0.00     & 221.21  & 520.17  & 39.44    & 37.71  \\
+\hline
+  MLP     & 8.99 $\pm$ 0.10   & 353.70 $\pm$ 57.74 & 624.87 $\pm$ 86.77  & 63.06 $\pm$ 10.29  & 45.30 $\pm$ 6.29   \\
 \hline
@@
 \caption{\small{Results (errors and time) obtained using the different 
-forecasting methods on the dataset obtained after the SOM analysis.}}
+forecasting methods on the dataset obtained after the SOM analysis (7 variables per book).}}
 \label{tabla:resultsSOM}
@@
 \caption{\small{Results (errors and time) obtained using the different 
-forecasting methods on the dataset with 9 variables per book.}}
+forecasting methods on the dataset obtained using the ReliefFAttributeEval 
+feature selection method (8 variables per book).}}
 \label{tabla:results9}
@@
 \caption{\small{Results (errors and time) obtained using the different 
-forecasting methods on the dataset with 4 variables per book.}}
+forecasting methods on the dataset obtained using the CfsSubsetEval 
+feature selection method (4 variables per book).}}
 \label{tabla:results4}
@@
   \epsfig{file=fig_time.eps,width=11cm}
-\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one).
+\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one).
 Plot shows that using categorical variables as part of the dataset makes the problem hard to solve.
@@
   \epsfig{file=fig_rae.eps,width=11cm}
-\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one).
+\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one).
 The M5P model obtains the lowest errors, whatever the dataset used.}}

### 2015-11-03 paper.tex
Adding Feature Reduction = F. extraction + F. selection description

@@
 making the algorithm impractical for problems with a large number of features 
-\cite{Selvakuberan2008}. Feature selection task is usually carried out by 
-searching through all possible combinations of features, evaluating each one.
-
-During the evaluation, the set of all possible features is analyzed in order 
-to find the best set of features, ranking them according to some metric.
-In this process, the feature's predictive ability along with the degree 
-of redundancy between them is considered.
+\cite{Selvakuberan2008}.
+Feature reduction is a task that is usually applied in these kind of situations, having two ways of performance \cite{kittler1986feature}: feature extraction and feature selection.
+%Feature selection task is usually carried out by 
+%searching through all possible combinations of features, evaluating each one.
+
+% During the evaluation, the set of all possible features is analyzed in order 
+% to find the best set of features, ranking them according to some metric.
+% In this process, the feature's predictive ability along with the degree 
+% of redundancy between them is considered.
+
+Feature extraction is a ``transformation-based approach", therefore it transforms the original meaning of the features.
+This approach involves simplifying the amount of resources for accurately describing a large set of data, thus is employed when the semantics of the original dataset will not be needed by any future process.
+On the contrary, feature selection attempts to retain the meaning of the original feature set.
+It is part of what is called semantic-preserving techniques, known as ``selection-based approaches".
+By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}.
 

### 2015-11-03 paper.tex
Little grammar error and comment

@@
 However, in the case of new products, such as the issue of new books, past patterns 
-is difficult to observe as there is no available historical sales data 
+are difficult to observe as there is no available historical sales data 
 \cite{ChingChin2010} (only pre-sales data is available in this problem).
+% (Paloma) - Se deberían evitar paréntetis.
 

### 2015-11-03 paper.tex
Re-writing description of feature reduction techniques

@@
 Feature extraction is a ``transformation-based approach", therefore it transforms the original meaning of the features.
-This approach involves simplifying the amount of resources for accurately describing a large set of data, thus is employed when the semantics of the original dataset will not be needed by any future process.
+This approach involves creating a subset of new features by combinations of the existing features, thus is employed when the semantics of the original dataset will not be needed by any future process.
 On the contrary, feature selection attempts to retain the meaning of the original feature set.
@@
 By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}.
-
-Thus, in order to reduce the dimensionality of the input data and to choose an 
-appropriate set of variables, both the SOM \cite{kohonen1998} method and several 
-feature selection methods have been applied.
+In the problem this work assesses, it is very important to maintain the semantics of the set of initial variables, and therefore several feature selection methods have been applied.
+
+In addition, in order to reduce the dimensionality of the input data and to choose an 
+appropriate set of variables, the SOM \cite{kohonen1998} method has been also applied.
 
@@
 
-As far as the feature selection methods are concerned, both a correlation-based 
-feature subset evaluation method (CfsSubsetEval) \cite{Hall1998} and an 
-adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation 
-method \cite{RobnikSikonja1997} are used with two search criteria: BestFirst, 
-that searches the space of feature subsets by greedy hill-climbing augmented 
-with a backtracking facility, and Ranker, that ranks features by their individual 
-evaluations.
+As far as the feature selection methods are concerned, Weka separates the process in two parts:
+\begin{itemize}
+  \item Attribute evaluator: This is the method by which the feature subsets are assessed.
+In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) \cite{Hall1998} and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method \cite{RobnikSikonja1997} are used.
+  \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator.
+Two search criteria have been used in this work: BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility, and Ranker, that ranks features by their individual evaluations.
+\end{itemize}
 

### 2015-11-03 paper.tex
Adding information about cfssubseteval

@@
   \item Attribute evaluator: This is the method by which the feature subsets are assessed.
-In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) \cite{Hall1998} and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method \cite{RobnikSikonja1997} are used.
+In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method \cite{RobnikSikonja1997} are used.
+  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
+(predictive of) the class, yet uncorrelated with (not predictive of) each other''.
+This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.
+The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation.
+In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.
+``Relief'' is the second evaluator used in this work.
   \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator.

### 2015-11-03 paper.tex
Adding description of relief

@@
   \item Attribute evaluator: This is the method by which the feature subsets are assessed.
-In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method \cite{RobnikSikonja1997} are used.
+In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method are used.
+
   The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
@@
 In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.
+
 ``Relief'' is the second evaluator used in this work.
+It is important to note that the relief method implemented in Weka is an updated version \cite{RobnikSikonja1997}, called RRELIEFF, of the original by Kira \& Rendell \cite{Kira1992}.
+The algorithm works by evaluating single attributes, and not whole subsets of attributes as CFS does.
+Also, it is applicable even working with both nominal and numeric features, without the need for transformations.
+For this algorithm, the weight of an attribute depends on the difference of an attribute value inside an instance with its neighbors, being these the nearest instance of the same class, and the nearest of the different class.
+Therefore, a good attribute is that which gives similar values fos instances of the same class, and different values for instances of different class.
   \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator.
-Two search criteria have been used in this work: BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility, and Ranker, that ranks features by their individual evaluations.
+With regard to the used search criteria, it is important to take into account that CFS evaluates attribute subsets, and Relief evaluates attributes separately.
+
+For this reason, 
+%have been used in this work: BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility, and Ranker, that ranks features by their individual evaluations.
 \end{itemize}

### 2015-11-03 paper.tex
Finishing feature selection techniques description. @pacastillo, @jj and @fergunet can review now

@@
 
-For this reason, 
-%have been used in this work: BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility, and Ranker, that ranks features by their individual evaluations.
+For this reason, the search method used with CFS has been BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility.
+On the other hand, Ranker is the searching criteria used with the Relief evaluator.
+This method ranks features by their individual evaluations.
 \end{itemize}
+
+Finally, Section \ref{sec:experiments} provides a comparison between the feature reduction through SOM, and the feature selection techniques that have been described.
 

### 2015-11-03 paper.tex
Añadida la tabla de variables a petición de @pacv

@@
 \usepackage{amssymb}
+\usepackage{amsmath}
 \usepackage[dvips]{epsfig}
@@
 been selected: \emph{number of reprints, total points of sale, print-run, total sales}.
+%FERGU: podeis quitar estos parrafos de variables porque ya está la tabla :)
 
@@
 
+\begin{table}
+\begin{tabular}[htb]{|c|c|c|c|c|}
+\hline
+Variable  & PreSales & ReliefFAttributeEval  & SOM & CfsSubsetEval \\ \hline \hline
+subject1    & $\checkmark$  &   &   &   \\ \hline
+subject2    & $\checkmark$  &   &   &   \\ \hline
+subject3    & $\checkmark$  &   &   &   \\ \hline
+editorial   & $\checkmark$  &   &   &   \\ \hline
+collection  & $\checkmark$  &   &   &   \\ \hline
+binding   & $\checkmark$  &   &   &   \\ \hline
+ret\_pricer    & $\checkmark$  &   & $\checkmark$  &   \\ \hline
+reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
+num\_reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
+gifts   & $\checkmark$  &   & $\checkmark$  &   \\ \hline
+distrib\_novelty   & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
+tot\_points\_sale   & $\checkmark$  & $\checkmark$  &   & $\checkmark$  \\ \hline
+tot\_points\_sale\_1st\_year    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
+weeks\_sale    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
+print\_run   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
+total\_sales   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
+
+\end{tabular}
+\caption{Variables used in each method.} %PABLO: Poned este caption bien
+\label{tab:varmethods}
+\end{table}
+
+Table \ref{tab:varmethods} shows the used variables used in each step. %Pablo: poner también esta frase mejor 
 Once the different reduced datasets have been obtained, proposed methods 

### 2015-12-27 paper.tex
updating things

@@
 In any case, we recommend using widely accepted standard 
-equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm}
-% FERGU: mejor tratar esto como una referencia, ya que es un texto
-% Efectivamente- JJ
-in order to compare obtained results with those presented in other research 
+equations \cite{gepsoft} in order to compare obtained results with those presented in other research 
 papers using other methods.
 That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
-implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
-or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are
+implemented in tools like Weka \cite{pentaho,Witten2011} 
+or R \cite{otexts,Hyndman2013}, are
 proposed.
-% no se deben usar footnotes donde debiera haber referencias. - JJ
 Specifically, in order to compute the forecasting errors of the different methods, 
-%FERGU: quitar este salto de linea y unirlo al párrafo de arriba.    ok
 Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
@@
 % TODO: falta incluir aquí el análisis de los mapas SOM.
-%*************************************** Determinar las variables a usar, según el SOM
+%***************************************
 \textbf{ TODO: add the SOM analysis }
@@
 \textbf{ TODO: add the SOM analysis }
-% una vez hecho, hay que hacer las ejecuciones para ese dataset.
 

### 2016-01-07 paper.tex
Un par de chuminás
Ahora le meto caña. :D
Abstract e intro revisados
Comentarios con etiqueta 'Antonio'

@@
 %%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
-\title{Predicting sales of newly published books}
+\title{Enhancing the sales prediction of newly published books by means of computational intelligence methods}
+
+% Antonio - El título habría que cambiarlo a otro más descriptivo, creo yo. A ver si os gusta este
 
@@
 }
-\institute{Department of Architecture and Computer Technology. CITIC \\
-           University of Granada (Spain) \\
-~\\
+\institute{Department of Computer Architecture and Computer Technology.\\
+CITIC-ETSIIT. University of Granada (Spain) \\
            e-mail: {\tt pacv@ugr.es}}
@@
 \begin{abstract}
-When a new book is published the publisher faces the problem of
+When a new book is launched the publisher faces the problem of
 how many books should be printed for delivery to bookstores. Printing too many is the main issue,
@@
 reached shelves. 
-In this paper, which works with several years of data on published books in
-Spain, we first apply a data visualization and preprocessing strategy
-in order to find
-out what are the variables that have some impact on sales, and
-then use standard data mining software to predict sales, and from them
-deduce print-run, based on those variables. Our work focuses then in  discovering which
-are the most relevant variables when predicting sales and is
-eventually able to predict sales with remarkable accuracy. In fact,
-this method has been validated by the company that provided the data 
-and incorporated in a business intelligence tool for publishers,
-since the obtained models provide guidance on the decision process of
-publishing a book and do not require human intervention either for the operation or for
-interpretation.
+Several years 
+% Antonio - Decir cuántos años son, que no me acuerdo.
+of data on published books in Spain have been processed by means of data visualization and other feature selection techniques.
+The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
+The described methodology improves the forecasting running time and is eventually able to predict sales with remarkable accuracy.
+Moreover, the proposed method has been validated by the company that provided the data and incorporated in a business intelligence tool for publishers,
+since the obtained models provide a reliable guidance on the decision process of
+publishing a book, without human intervention 
+either for the operation or for interpretation.
+% Antonio - esto es cierto??? :D
 \end{abstract}
@@
 %********************************************************************************
+
 \section{Introduction}
@@
 types of risks and costs due to
-the complexity and expenses of the production and distribution processes. 
+the complexity and derived expenses of the production and distribution processes. 
 % tienes que enmarcar el problema. Se trata de productos culturales
@@
 % discos, no sé si alguna cosa más. - JJ
-A newly launched product is also new to the company, and sales forecasts can
-only be based on the experience of similar products. 
-In this scope, having accurate estimates of future sales of the new
-product is extremely important \cite{ChingChin2010} so that production
+A newly launched product could be, additionally, completely new to the company (not a new version or edition of a previous product), and sales forecasts can
+only be based on the experience of other similar products. 
+In this scope, having accurate estimations of future sales of the new
+product is extremely important \cite{ChingChin2010}, so that production
 runs do not exceed predicted sales. 
 Indeed, several studies have demonstrated that improving sale predictions 
-(a reduction of forecasting errors) results in an improvement in the 
-production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
+(a reduction of forecasting errors) results in an enhancing in the 
+production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
 
@@
 Book publishers, as well as other content producers, release new {\em
-  products} more frequently than other industries and thus face the
+  products} more frequently than other industries, so that they face the
 problem of predicting sales quite often. The issue, in this case, is to print an
 adequate number of copies but not too many, as the unsold volumes will
-lead to losses and sunk inventory cost, whereas if the number of printed copies was not
-enough, you can always print more. In this sense, errors in one or the
-other direction do not have the same importance, although a temporal
-scarcity of a book that is selling well is also a problem.
-
-Thus, it is extremely important using predictive tools to optimize 
-production and improve the publishing company profits or minimize losses \cite{Zhao2001}
-by forecasting the sales a new book might achieve. This is the
-objective we have in this paper.
+lead to losses and sunk inventory cost, 
+% Antonio - 'sunk inventory cost' es corecto?
+whereas if the number of printed copies was not enough, you can always print more. 
+% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema.
+Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción.
+;)
+% Se podría señalar, por ejemplo:
+% - repetición de costes de distribución
+% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
+% - algunas más... :D
+In this sense, errors in one or the other direction do not have the same impact, although a temporal scarcity of a book that is selling well is also a problem.
+% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
+
+Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimize production and to improve the publishing company profits or minimize losses \cite{Zhao2001}.
+This is the main objective of this paper.
 An example is the optimization of sales \cite{Mattila2002} by
-improving profit margins by selling the whole print-run. %publishing roll.  
-% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...
-% Antonio propone traducirlo como "print run". Lo pongo así.
-
-However, accurately using a predictive tool is a difficult task as
-book sales are influenced by various factors that make
-them fluctuate and usually they might be not controllable and
-sometimes unknown. 
-Some have to do with decisions on purchases, others with freight %FERGU: El Some have to do me suena raro
-traffic, and others with the distribution strategy \cite{Little1998}.
+improving profit margins by selling the whole print-run. 
+% Antonio - podrías extender un poco el ejemplo? Es decir, describir un poco más lo que se hace en ese trabajo. ;)
+
+However, designing such an accurate predictive tool is a difficult task in this scope, as book sales are influenced by several factors that make them fluctuate and, moreover, usually they might be not controllable and even unknown.
+For instance, some are related with decisions on purchases, others with freight 
+traffic, or others with the distribution strategy \cite{Little1998}.
 
 Thus, it is very important to know the product and the variables that
-might affect the sales, and how an expert manager can eventually 
-take them into account \cite{Armstrong2001,SThomassey2014}. 
+might affect the sales, and how an expert manager takes them into account \cite{Armstrong2001,SThomassey2014}. 
                                 % ¿Esto también pasa en la industria de la
@@
 
-In this research, the problem of how many books should be printed 
+In this research, the problem of how many units should be printed 
 when a new book is published is faced using data provided by the 
 Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}},
-a company that provides management systems and services for libraries, 
+a company that provides management systems and services for book shops,
+% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
 publishers and distributors. 
 Usually, the company's expert sales managers analyzed historical data 
-and applied their knowledge using external variables to calculate
-appropriate predictions, for example, increasing or decreasing the 
-sales prediction based on season or sales period.
+and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
                         % varias citas - JJ
@@
 %interpretable and understandable model. 
-However, carrying out the analysis and forecasting process as described,
-may lead to an imprecise analysis and may not take all the variables into account. 
+However, carrying out the analysis and forecasting process as a human expert,
+may lead to a 'fuzzy-like' analysis, which may not take all the variables into account. 
 In addition, the process might be tedious, especially when the amount
-of data is large, and even, different experts can reach different
-predictions from the same data set \cite{ChingChin2010,Sanders1994}.
+of data is quite large, and even, different experts can reach different
+predictions from the same dataset \cite{ChingChin2010,Sanders1994}.
 
@@
 techniques to be adopted so that, estimating sales task is carried out
-properly and in an automatic way.
-
-With this in mind, in this paper a data visualization and preprocessing strategy 
-to find out what are the relevant variables describing a book in the prediction 
-of book sales is proposed; then several standard data mining models 
+reliably, accurately, and in an automatic way.
+
+With this issue in mind, in this paper a data visualization and preprocessing strategy to find out what are the relevant variables describing a book in the prediction of book sales is proposed; then several standard data mining models
 for sales forecasting are evaluated so a publishing company 
 can deduce and optimize print-run.
+% Antonio - cambiar este párrafo para describirlo como un proceso en dos pasos:
+% - análisis y extracción
+% - predicción
+
+% Antonio - Además habría que justificar bien (con citas) el por qué de la extracción/selección de características, por ejemplo:
+% - menor tiempo de procesamiento
+% - mejores resultados (si algunas variables interfieren entre sí)
 
@@
 Section \ref{sec:experiments} reports and analyzes the obtained results with a 
-real data set. Finally, conclusions and future work are presented in Section
+real dataset. Finally, conclusions and future work are presented in Section
 \ref{sec:conclusionsAndFutureWork}. 
+% Antonio - TODO: rescribir con los contenidos finales del artículo. ;)
 
@@
 
-The initial data set, provided in the framework of a contract by
+The initial dataset, provided in the framework of a contract by
 Trevenque Editorial, included 3159 books, and included descriptive information 
@@
 
-\begin{table}[!h]
+\begin{table}[!ht]
 \caption{Parameters describing a book, as provided by the company Trevenque.}
@@
 
-\begin{figure}[!h] 
+\begin{figure}[!ht] 
 \begin{center}
@@
 relationship between a scalar dependent variable (outcome) and several independent 
-variables (predictor) over the range of values in the data set. 
+variables (predictor) over the range of values in the dataset. 
 In this statistical technique, data is modeled using linear functions to estimate 
@@
 
-Once the methods to be applied have been chosen, they must be applied to data sets 
+Once the methods to be applied have been chosen, they must be applied to datasets 
 to obtain the prediction models for each one. 
@@
   % en algunos calculan muchos más, pero estos son los más usados. 
-\begin{table*}[!h]
+\begin{table*}[!ht]
 \begin{center}
@@
 % TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
-\begin{table*}[!h]
+\begin{table*}[!ht]
 \begin{center}
@@
 
-\begin{table*}[!h]
+\begin{table*}[!ht]
 \begin{center}
@@
 %La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
-A data set consisting of 3159 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
+A dataset consisting of 3159 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
 publishing company Trevenque Editorial has been used.

### 2016-01-14 paper.tex
Revisado SotA
Varias correcciones y comentarios con la etiqueta 'Antonio'

@@
 %  de predicción en la industria en general, que sí hay bastante bibliografía.
-
-% In the literature several proposals to perform the prediction of sales in different fields can be found. 
-In the last years, different analysis and forecasting methods, such as
-regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} 
-or fuzzy systems \cite{Mastorocostas2001} 
-have been applied in different industry sectors, i.e. electricity
-consumption, traffic flow or sales forecasting. % ¿Y qué? Esta frase
+% Antonio - me parece bien
+
+% Antonio - Cosas generales a mejorar en el SotA:
+% - habría que comparar más veces este trabajo con lo que hacen otros, destacando nuestras diferencias. Sólo se menciona al final de la sección
+% - habría que destacar claramente ls aportes de este trabajo al SotA, cómo hace que avance ;)
+% - habría que incluir citas a artículos de la revista que elijamos y comentarlos aquí
+
+Sales forecasting is a problem which has been addressed several times in the literature.
+Most of the studies have been conducted using different analysis and forecasting methods, such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001}, applied to different industrial sectors.
+% ¿Y qué? Esta frase
 % no aporta nada. La primera frase
@@
 % arte - JJ
-
-Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
+% Antonio - la he intentado mejorar.
+
+Specifically, Time-Series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
 is perhaps the most used technique to tackle the sales forecasting problems. 
 %FERGU: terminar esta frase con punto en vez de coma para que no sea larga.   OK
-The efficiency of these techniques depends largely on the field of application 
-and the problem data as they require a large amount of data for predicting 
-sales of new products are not the most suitable for this task \cite{ChingChin2010}.
-
-This is the new book sales forecasting case, a problem with issues such as 
-dealing with limited data, finding adequate forecasting methods and selecting 
-the best method to use \cite{ChingChin2010}.
-In the case of new unpublished-books, there is no historical data to define 
-patterns, and only some descriptive data about the new book is available 
-\cite{ChingChin2010,FaderHardie2005,Madsen2008}.
-Thus, not any timeseries-based forecasting method can be used \cite{Madsen2008,ChernWSF15}.
+The efficiency of these techniques strongly depends on the field of application 
+and the correctness of the problem data. However, since they require a large amount of data for predicting sales, these methods are not the most suitable for this task \cite{ChingChin2010}.
+
+This is the case of new book sales forecasting, a problem with issues such as 
+dealing with quite limited data (just a few variables are known in advance) or the existence of several categorical values (which are harder to be processed).
+Given these issues, finding adequate forecasting techniques and selecting
+the best method to use is also a problem \cite{ChingChin2010}.
+Moreover, in the case of new unpublished-books, there is no historical data to define patterns, and only some descriptive data about the new book are available 
+\cite{ChingChin2010,FaderHardie2005,Madsen2008}. Thus, not any time-series forecasting method can be used \cite{Madsen2008,ChernWSF15}.
 
@@
 
-Methods used to predict book sales have been generally based on experts' 
-experience who analyzed data about sales, and taking into account their knowledge 
-in industry experience and their perception about trends, could make decisions
-on the companies production (how many books should be printed when a new book is published).
-This a complex problem as the predictions are influenced by external variables 
-that must be taken into account, such as seasonality, promotions or fashions 
-that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.
+For this reason, usually the methods used to predict book sales have been generally based on experts' experience.
+They analyze data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
+This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.
 
@@
 and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}.
-Specifically, authors propose using the number of blog references as an indicator 
-of book sales.
+Specifically, Moon et al.
+propose using the number of blog references as an indicator of the success of a book, and thus its sales.
 Different sales patterns are observed by analyzing data obtained.
-In any case, Moon et al \cite{Moon2010ICSSSM,Moon2010ICEC} used historical data from published books, 
+% Antonio - describir esos 'sales patterns'. ;)
+%
+However, the authors used in these papers historical data from published books, 
 %FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso.   ok
-and the proposed methodology can not be usable in the problem of unpublished-books 
-sales prediction.
+so their proposed methodology can not be applied in the problem of unpublished-books sales prediction.
 
@@
 
-Some authors have faced the problem of forecasting sales of new products using 
-different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
-Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
-decision trees for sales forecasting in textile-apparel fashion industry, %FERGU: appared? apparel, creo.  ¡sí!
-a very similar issue to the new book publishing problem.
-The same problem was previously faced by Xia et al \cite{Xia2012} using a 
-forecasting method based on extreme learning machine with adaptive metrics of inputs.
-Complexity of this problem is due to the lack of historical data, short lifetime 
-of the large number of items, and due to the influence of variables such as 
-promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.
+In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
+% Antonio - quizá habría que comentar alguno o todos bervemente...
+%
+In the same line, Thomassey et al.
+\cite{SThomassey2014} propose using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, %FERGU: appared?
+apparel, creo.
+¡sí!
+a very similar issue to the new book publishing one.
+The same problem was previously faced by Xia et al. \cite{Xia2012} using a 
+forecasting method based on extreme machine learning with adaptive metrics of inputs.
+% Antonio - of -> as???
+The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
+% Antonio - ver si está bien el cambio 'large number' -> 'majority'
+and on the influence of variables such as promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
 
@@
 In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
-forecasting is proposed to solve three real-world sales forecasting problems 
-involving new tea, cosmetic, and soft drink products taking into account 
-quantitative variables. 
-In this study, it is assumed that products are classified based on their sales 
-pattern so that products in the same class would have a similar sales pattern. %FERGU: "_a_ similar sales pattern", mejor? ok
-However, as the authors state, proposed system can not deal with qualitative 
-date related to the products, and even more real-world cases, such as consumer 
-electronics and fashion products, should be examined, as these industries 
-introduce new products every season.
+forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.
+% Antonio - qué significa eso?
+In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern.
+%FERGU: "_a_ similar sales pattern", mejor?
+ok
+However, as the authors state, the proposed system can not deal with qualitative 
+data related to the products. Moreover, real-world cases, such as consumer 
+electronics and fashion products, should be deeply analyzed, as these industries 
+present/launch new products every season.
 
@@
 In those cases where historical data is available, classical time series 
-forecasting methods can be applied, which is what they do in \cite{Chang2009}, where a hybrid 
-model integrating K-means and fuzzy neural networks to forecast the future sales 
-of a printed circuit board is proposed.
-A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
+forecasting methods can be applied, which is what the authors do in \cite{Chang2009}, where a hybrid model integrating K-means and fuzzy neural networks to forecast the future sales of a printed circuit board is proposed.
+A similar method is described by Chern et al. \cite{ChernWSF15}, who analyze 
 historical data along online reviews, reviewer characteristics and review 
-influences to understand how electronic word-of-mouth affects product sales. 
-The proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method?    ok
-online reviews and historical data.
-
-Taking into account the kind of problem we address in this paper,
-prediction of sales of 
-a new product for which no historical data is available,
-the classical forecasting methods based on time series are not
-adequate, although they can obviously be used once the book has been
-for sale. 
-Thus, in this paper the relevant variables in the prediction of sales are determined
-using data visualization tools and then, standard data mining software 
-to predict sales is used to deduce print-run.
+influences to understand how electronic `word-of-mouth' influences product sales.
+The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.
+
+Thus, taking into account the kind of problem we address in this paper, i.e.
+the prediction of sales of a new product for which no historical data is available, the classical forecasting methods based on time-series are not
+adequate, although they can obviously be used once the book has been launched for sale. 
+In our work the relevant variables in the prediction of sales are identified
+by means of data visualization and feature selection methods. Then, machine learning techniques are applied to predict sales and to infer the ideal print-run of a book.
 In addition, since publishers need models to explain obtained predictions, 
-black box forecasting methods may not be suitable for this problem, so 
-models based on rules are tested as an alternative.
+`black box' forecasting methods may not be suitable, so models based on decision rules have been tested as an alternative.
 
@@
 
-Moreover, the algorithm runing times grow with the number of features, and thus 
+Moreover, the algorithm running times grow with the number of features, and thus 
 making the algorithm impractical for problems with a large number of features 

### 2016-01-14 paper.tex
Quitada la figura 1

@@
 
-\begin{figure}[!ht] 
-\begin{center}
-  \epsfig{file=stages.eps,width=7cm}
-\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
-methods testing, and (3) subjectively adjusting the obtained results.}}
-\label{fig:stages}
-\end{center}
-\end{figure}
+\hspace{2cm}
+\begin{verbatim}
+Stage 1: Collecting and analyze data
+		- Variables selection
+ 		- Data preprocesing
+Stage 2: Select the best forecasting method
+ 		- Obtaining and evaluating forecasting models
+ 		- Calculate forecasting values
+Stage 3: Subjectively adjust obtained results
+		- Apply additional expert knowledge, such as information 
+ 		  about seasonality, trends, etc.
+\end{verbatim}
+
+% Maribel: quito la figura por el issue asignado por antonio mora.
+%\begin{figure}[!ht] 
+%\begin{center}
+%  \epsfig{file=stages.eps,width=7cm}
+%\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
+%methods testing, and (3) subjectively adjusting the obtained results.}}
+%\label{fig:stages}
+%\end{center}
+%\end{figure}
 
@@
 
-In some cases, depending on the company needs and after obtaining the forecasting 
-results, it is necessary a third stage where experienced 
-managers adjust subjectively the results obtained using the forecasting methods 
-(see Figure \ref{fig:stages} for details). 
+%In some cases, depending on the company needs and after obtaining the forecasting  results, it is necessary a third stage where experienced managers adjust subject1ively the results obtained using the forecasting methods (see Figure \ref{fig:stages} for details).
+Esta frase no aporta nada que no esté dicho ya antes en los comentarios de las tres etapas que antes estaban en una figura, así que quito la frase entera: Maribel
+
 They might manually adjust the forecasting results taking into account their 

### 2016-01-20 paper.tex
adding Hossam as co-author (I'll add his contributions later)

@@
 \author {
-P.A. Castillo, A.M. Mora, J.J. Merelo, P. Garc\'{\i}a-S\'anchez, \\ A.J. Fern\'andez-Ares, M.G. Arenas, P. de las Cuevas
+P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Fariss$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
 }
-\institute{Department of Computer Architecture and Computer Technology.\\
-CITIC-ETSIIT. University of Granada (Spain) \\
-           e-mail: {\tt pacv@ugr.es}}
+\institute{
+$^1$Department of Computer Architecture and Computer Technology. CITIC. University of Granada (Spain)\\
+$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
+           e-mail: {\tt pacv@ugr.es}
+}
 

### 2016-01-22 paper.tex
including the SOM figures + several updates

@@
 
-After the SOM analysis, the following variables have been selected: 
+\begin{figure}[!ht] 
+\begin{center}
+  \epsfig{file=SOM_25x16_pre_venta.eps,width=15cm}
+\caption{\small{SOM analysis.}}
+\label{fig:somanalysis}
+\end{center}
+\end{figure}
+
+\begin{figure}[!ht] 
+\begin{center}
+  \epsfig{file=UMATRIX_25x16_pre_venta.eps,width=15cm}
+\caption{\small{SOM UMATRIX.}}
+\label{fig:somumatrix}
+\end{center}
+\end{figure}
+
+After the SOM analysis (see Figures \ref{fig:somanalysis} and \ref{fig:somumatrix}), the following variables have been selected: 
 \emph{retail pricer, reprints, number of reprints, gifts, units distributed as novelty, print-run, total sales }.
@@
 \section*{Acknowledgements}
-This work has been supported in part by 
+
+This work has been supported in part by projects 
 PreTEL (PRM Consultores - Trevenque),
-TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
+TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitiveness), 
 SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), 
-PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
-IX Convocatoria de Proyectos de Investigaci{\'o}n), 
-and PYR-2014-17 GENIL project (CEI-BIOTIC Granada).
+PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), 
+PROY-PP2015-06 (Plan Propio 2015 UGR), 
+and project CEI2015-MP-V17 of the Microprojects program 2015 from CEI BioTIC Granada.
 

### 2016-01-25 paper.tex
cerrando issue: Closes #17
adding figures: Closes #16

@@
 
+\subsubsection{Experimental setup}
+
+    \textbf{ TODO: details about the method parameters }
+
+\subsubsection{Obtained results}
+
 Once the methods to be applied have been chosen, they must be applied to datasets 
@@
 
+%*************************************** SOM ANALISYS
 % como tercer método, se ha usado el SOM; tras interpretar los mapas, se
@@
 
-%
-% TODO: falta incluir aquí el análisis de los mapas SOM.
-%***************************************
-\textbf{ TODO: add the SOM analysis }
-
-\begin{figure}[!ht] 
+Further important prepocessing steps are carried out before applying the SOM analysis.
+First, in order to label the U-matrix with total-sales values, this variable is converted from numerical to categorical.
+Five categories have been created to represent the quantities of sales of each book: Very Low (VL), Low (L), Medium (M), High (H) and Very High (VH).
+Table \ref{table:freq} shows the ranges of total-sales that correspond to each category along with the number of books that fall in.
+Table \ref{table:freq} and Figure \ref{fig:count} reveal more information about the nature of the dataset.
+We can notice that most of 77\% of the book are categorized as VL and L with limited number of sales.
+On the other side, the books that achieved more than 2000 sold copies are just around 4\%.
+This makes the problem of identifying those two categories much harder.
+The new categorical feature is used to replace the old numerical Total Sales feature in the SOM analysis.
+
+\begin{table*}[ht]
+\caption{Categories corresponding to total-sales variable. }
+\centering{}%
+\begin{tabular}{|c|c|c|c|}
+\hline 
+Category & Range of total sales & Count & Ratio\tabularnewline
+\hline 
+\hline 
+Very Low & 1-100 & 2233 & 36.71\%\tabularnewline
+\hline 
+Low & 100-500 & 2323 & 38.19\%\tabularnewline
+\hline 
+Medium & 500-2000 & 1239 & 20.37\%\tabularnewline
+\hline 
+High & 2000-5000 & 224 & 3.68\%\tabularnewline
+\hline 
+Very High & $>$5000 & 64 & 1.05\%\tabularnewline
+\hline 
+\end{tabular}
+\label{table:freq}
+\end{table*}
+
+\begin{figure*}[ht]
 \begin{center}
-  \epsfig{file=SOM_25x16_pre_venta.eps,width=15cm}
-\caption{\small{SOM analysis.}}
-\label{fig:somanalysis}
+\includegraphics[scale=0.60]{freq-sales}
 \end{center}
-\end{figure}
-
-\begin{figure}[!ht] 
+\caption{Number of books in each category.}
+\label{fig:count}
+\end{figure*}
+
+Second, two categorical features (i.e; Editorial and Collection) are removed from the analysis since they have large number of unique different values and therefore they are less informative.
+Moreover, four features (i.e; Subject1, Subject2, Subject3 and Book-bining) have more than 10\% missing values so they are removed also.
+
+Finally, the resulted dataset consisted of ten features including the new Total Sales categorical feature.
+The SOM algorithm is trained based on the nine numerical variables while the new total-sales variable is used to label this data.
+The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data.
+The best SOM training results are obtained with a final quantization error of 0.691 and topographic error of 0.046.
+
+Figure \ref{fig:componentplanes} shows the U-matrix and component variables resulted from SOM training.
+The term component is used in SOM to refer to the features.
+The component planes in Figure \ref{fig:componentplanes} show the trend of values of the the prototype vectors of the SOM map units.
+These values are represented as colors.
+The colorbar on the right of each component plane shows the indication of each color.
+On the other side, the U-matrix on the top left corner shows the distances between the adjacent units.
+It is important to note that high values in the matrix indicates large distance between the units of the map.
+It can be noticed also that there are more hexagons in the U-matrix than component planes since the distances between units is also represented as hexagons.
+
+In Figure \ref{fig:Umatrix} we label the U-matrix with the Total Sales categories.
+It can be clearly shown that the SOM algorithm has successfully clustered the labels of the Total Sales into clear identified regions.
+In the top of the U-matrix the VL category is located.
+The L category appears in the middle of the matrix.
+Most of the M category appears in bottom-right corner while the H and VH categories are concentrated in the bottom-left corner.
+Inspecting the component \texttt{distrib\_novelity}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components have the highest similarity to the clusters shown in the U-matrix.
+Based on this analysis, those features will be selected for the next stage.
+
+\begin{figure*}[ht]
 \begin{center}
-  \epsfig{file=UMATRIX_25x16_pre_venta.eps,width=15cm}
-\caption{\small{SOM UMATRIX.}}
-\label{fig:somumatrix}
+\includegraphics[scale=0.80]{fig1}
 \end{center}
-\end{figure}
-
-After the SOM analysis (see Figures \ref{fig:somanalysis} and \ref{fig:somumatrix}), the following variables have been selected: 
-\emph{retail pricer, reprints, number of reprints, gifts, units distributed as novelty, print-run, total sales }.
-
-\textbf{ TODO: add the SOM analysis }
+\caption{U-matrix and component planes.}
+\label{fig:componentplanes}
+\end{figure*}
+
+\begin{figure*}[http]
+\centering
+    \begin{subfigure}[b]{0.32\textwidth}            
+            \includegraphics[scale=0.50]{Umatrix.eps}
+            \caption{U-matrix}
+            \label{fig:Um}
+    \end{subfigure}%
+    \begin{subfigure}[b]{0.32\textwidth}  
+            \includegraphics[scale=0.50]{Labels.eps}
+            \caption{Labels}
+            \label{L}
+    \end{subfigure}
+
+    \caption{Labeling the U-matrix using the Total Sales variable.}
+\label{fig:Umatrix}
+\end{figure*}
+
+%*************************************** SOM ANALISYS
 
@@
   % en algunos calculan muchos más, pero estos son los más usados. 
-\begin{table*}[!ht]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline 
- Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
-\hline
-  M5P 		& 24.24 $\pm$ 0.96    & 197.48  & 577.28  & 35.21    & 41.85  \\
-\hline
-  LR 		  & 3533.84 $\pm$ 178.38& 247.22 & 561.67  & 44.08    & 40.71    \\
-\hline
-  SVM 		& 5586.96 $\pm$ 139.71& 215.69  & 574.76  & 38.46    & 41.66  \\
-\hline
-  kNN 		& 0.02 $\pm$ 0.00     & 302.07 	& 924.94 	& 53.86 	 & 67.05 	\\
-\hline
-  MLP 		& - 	  & - 	& - 	& - 	& - 	\\
+\begin{table*}[h]
+\caption{Results (errors and time) obtained using the different forecasting
+methods on the original dataset (16 variables per book). In this case,
+due to the categorial variables, the MLP could not be run.}
+\label{tabla:resultsT}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+Base & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
+\hline 
+\hline 
+M5P & 0.9076 & \textbf{202.1547} & 591.0257 & \textbf{35.31}\% & 42.10\% & 39.73\tabularnewline
+\hline 
+LR & 0.9204 & 255.0526 & 548.0975 & 44.5527 & 39.10\% & 0.03\tabularnewline
+\hline 
+SVM & \textbf{0.9402} & 203.4416 & \textbf{481.7528} & 35.54\% & \textbf{34.37}\% & 308.31\tabularnewline
+\hline 
+kNN & 0.7273 & 310.4078 & 993.2663 & 54.22\% & 70.85\% & 0\tabularnewline
+\hline 
+MLP & 0.9197 & 289.7393 & 585.6445 & 50.61\% & 41.78\% & 82.08\tabularnewline
 \hline 
 \end{tabular}
-\end{center}
-\caption{\small{Results (errors and time) obtained using the different
-    forecasting methods on the original dataset (16 variables per book). 
-    In this case, due to the categorial variables, the MLP could not be run.}} 
-\label{tabla:resultsT}
 \end{table*}
@@
 using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
-%In this dataset, every book is described using numerical variables, and thus, 
-%processing the data to build the different models is a fast task.
-%***************************************
-% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
-\begin{table*}[!ht]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline 
- Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
-\hline
-  M5P     & 1.74 $\pm$ 0.10     & 218.81  & 661.85  & 39.01    & 47.98  \\
-\hline
-  LR      & 0.27 $\pm$ 0.02     & 258.82  & 582.74  & 46.15    & 42.24  \\
-\hline
-  SVM     & 45.58 $\pm$ 1.89    & 240.18  & 614.30  & 42.82    & 44.53  \\
-\hline
-  kNN     & 0.04 $\pm$ 0.00     & 221.21  & 520.17  & 39.44    & 37.71  \\
-\hline
-  MLP     & 8.99 $\pm$ 0.10   & 353.70 $\pm$ 57.74 & 624.87 $\pm$ 86.77  & 63.06 $\pm$ 10.29  & 45.30 $\pm$ 6.29   \\
+\begin{table*}[h]
+\caption{Results (errors and time) obtained using the different forecasting methods
+on the dataset obtained using the SOM feature selection method (6 variables
+per book).}
+\label{tabla:resultsSOM}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+Base  & Correlation coefficient (\%)  & MAE  & RMSE  & RAE(\%)  & RRSE (\%)  & Time(sec)\tabularnewline
+\hline 
+\hline 
+M5P  & 0.9161 & \textbf{198.8864} & 562.2113 & \textbf{34.74}\% & 40.11\% & 0.76\tabularnewline
+\hline 
+LR  & 0.9179 & 263.1702 & 556.3372 & 45.97\% & 39.69\% & 0.07\tabularnewline
+\hline 
+SVM  & \textbf{0.9388} & 207.7159 & \textbf{486.8913} & 36.28\% & \textbf{34.73}\% & 157.87\tabularnewline
+\hline 
+kNN  & 0.9304 & 202.0939 & 525.4642 & 35.30\% & 37.48\% & 0\tabularnewline
+\hline 
+MLP  & 0.9193 & 305.78 & 590.8412 & 53.41\% & 42.15\% & 25.83\tabularnewline
 \hline 
 \end{tabular}
-\end{center}
-\caption{\small{Results (errors and time) obtained using the different 
-forecasting methods on the dataset obtained after the SOM analysis (7 variables per book).}}
-\label{tabla:resultsSOM}
 \end{table*}
@@
 
-\begin{table*}[!ht]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline 
- Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
-\hline
-  M5P     & 2.27 $\pm$ 0.02     & 195.97  & 629.33  & 34.94    & 45.62  \\
-\hline
-  LR      & 0.38 $\pm$ 0.01     & 256.19  & 549.19  & 45.68    & 39.81   \\
-\hline
-  SVM     & 132.64 $\pm$ 2.86   & 230.66  & 613.27  & 41.12    & 44.45   \\
-\hline
-  kNN     & 0.06 $\pm$ 0.01     & 214.76  & 551.33  & 38.29    & 39.96   \\
-\hline
-  MLP     & 130.77 $\pm$ 1.51   & 326.60 $\pm$ 75.77 & 687.61 $\pm$ 55.70  & 58.23 $\pm$ 13.51  & 49.84 $\pm$ 4.04   \\
+\begin{table*}[h]
+\caption{Results (errors and time) obtained using the different forecasting methods
+on the dataset obtained using the ReliefFAttributeEval feature selection method (8
+variables per book).}
+\label{tabla:results9}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+RAE & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
+\hline 
+\hline 
+M5P & 0.9131 & \textbf{197.2886} & 580.328 & \textbf{34.46}\% & 41.40\% & 0.74\tabularnewline
+\hline 
+LR & 0.9209 & 254.3979 & 546.3899 & 44.44\% & 38.98\% & 0.03\tabularnewline
+\hline 
+SVM & \textbf{0.9394} & 204.2075 & \textbf{484.2617} & 35.67\% & \textbf{34.54}\% & 232.99\tabularnewline
+\hline 
+kNN & 0.9103 & 222.0827 & 597.8885 & 38.79\% & 42.65\% & 0\tabularnewline
+\hline 
+MLP & 0.9199 & 296.3581 & 575.9623 & 51.77\% & 41.09\% & 32.52\tabularnewline
 \hline 
 \end{tabular}
-\end{center}
-\caption{\small{Results (errors and time) obtained using the different 
-forecasting methods on the dataset obtained using the ReliefFAttributeEval 
-feature selection method (8 variables per book).}}
-\label{tabla:results9}
 \end{table*}
@@
 
-\begin{table*}[!ht]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline 
- Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
-\hline
-  M5P     & 2.02 $\pm$ 0.01     & 205.52  & 556.90  & 36.64     & 40.37  \\
-\hline
-  LR      & 0.32 $\pm$ 0.00     & 261.04  & 547.42  & 46.54     & 39.68   \\
-\hline
-  SVM     & 81.74 $\pm$ 1.66    & 242.26  & 606.07   & 43.19    & 43.93   \\
-\hline
-  kNN     & 0.05 $\pm$ 0.00     & 216.05  & 506.34  & 38.52    & 36.70   \\
-\hline
-  MLP     & 47.80 $\pm$ 0.51    & 318.29 $\pm$ 43.96 & 587.50 $\pm$ 51.50  & 56.75 $\pm$ 7.84  & 42.59 $\pm$ 3.73   \\
+\begin{table*}[h]
+\caption{Results (errors and time) obtained using the different forecasting methods
+on the dataset obtained using the CfsSubsetEval feature selection method (4 variables
+per book).}
+\label{tabla:results4}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+CFS & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
+\hline 
+\hline 
+M5P & 0.9255 & \textbf{206.6638} & 531.306 & \textbf{36.10}\% & 37.90\% & 0.56\tabularnewline
+\hline 
+LR & 0.9194 & 259.3791 & 551.2005 & 45.31\% & 39.32\% & 0.05\tabularnewline
+\hline 
+SVM & \textbf{0.9342} & 213.0254 &\textbf{ 502.4048} & 37.21\% & \textbf{35.84}\% & 70.12\tabularnewline
+\hline 
+kNN & 0.9285 & 220.6548 & 527.7374 & 38.54\% & 37.65\% & 0\tabularnewline
+\hline 
+MLP & 0.9047 & 369.3486 & 646.1241 & 64.52\% & 46.09\% & 10.93\tabularnewline
 \hline 
 \end{tabular}
-\end{center}
-\caption{\small{Results (errors and time) obtained using the different 
-forecasting methods on the dataset obtained using the CfsSubsetEval 
-feature selection method (4 variables per book).}}
-\label{tabla:results4}
 \end{table*}
 
-\begin{figure}[!ht] 
-\begin{center}
-  \epsfig{file=fig_time.eps,width=11cm}
-\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one).
+    \textbf{ TODO: comment the following figures: conv2 , conv2ReliefAttributeEval , conv2CfsSubsetEval , conv2SOM }
+
+\begin{figure*}[http]
+\centering
+    \begin{subfigure}[b]{0.32\textwidth}            
+            \includegraphics[scale=0.32]{m5p.eps}
+            \caption{M5P}
+            \label{fig:M5P}
+    \end{subfigure}%
+    \begin{subfigure}[b]{0.32\textwidth}  
+            \includegraphics[scale=0.32]{lr.eps}
+            \caption{LR}
+            \label{fig:LR}
+    \end{subfigure}
+      \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{svm.eps}
+            \caption{SVM}
+            \label{SVM}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{knn.eps}
+            \caption{k-NN}
+            \label{fig:k-NN}
+    \end{subfigure}
+      \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{mlp.eps}
+            \caption{MLP}
+            \label{MLP}
+    \end{subfigure}
+    \caption{Actual VS predicted sales for M5P, LR, SVM, k-NN, MLP models.}
+\label{conv2}
+\end{figure*}
+
+\begin{figure*}[http]
+\centering
+    \begin{subfigure}[b]{0.32\textwidth}            
+            \includegraphics[scale=0.32]{m5p_RAE.eps}
+            \caption{M5P}
+            \label{fig:M5P1}
+    \end{subfigure}%
+    \begin{subfigure}[b]{0.32\textwidth}  
+            \includegraphics[scale=0.32]{lr_RAE.eps}
+            \caption{LR}
+            \label{fig:LR1}
+    \end{subfigure}
+      \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{svm_RAE.eps}
+            \caption{SVM}
+            \label{SVM1}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{knn_RAE.eps}
+            \caption{k-NN}
+            \label{fig:k-NN1}
+    \end{subfigure}
+      \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{mlp_RAE.eps}
+            \caption{MLP}
+            \label{MLP1}
+    \end{subfigure}
+    \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
+\label{conv2ReliefAttributeEval}
+\end{figure*}
+
+\begin{figure*}[http]
+\centering
+    \begin{subfigure}[b]{0.32\textwidth}            
+            \includegraphics[scale=0.32]{m5p_CFS.eps}
+            \caption{M5P}
+            \label{fig:M5P2}
+    \end{subfigure}%
+    \begin{subfigure}[b]{0.32\textwidth}  
+            \includegraphics[scale=0.32]{lr_CFS.eps}
+            \caption{LR}
+            \label{fig:LR2}
+    \end{subfigure}
+      \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{svm_CFS.eps}
+            \caption{SVM}
+            \label{SVM2}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{knn_CFS.eps}
+            \caption{k-NN}
+            \label{fig:k-NN2}
+    \end{subfigure}
+      \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{mlp_CFS.eps}
+            \caption{MLP}
+            \label{MLP2}
+    \end{subfigure}
+    \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
+\label{conv2CfsSubsetEval}
+\end{figure*}
+
+\begin{figure*}[http]
+\centering
+    \begin{subfigure}[b]{0.32\textwidth}            
+            \includegraphics[scale=0.32]{m5p_SOM.eps}
+            \caption{M5P}
+            \label{fig:M5P2}
+    \end{subfigure}%
+    \begin{subfigure}[b]{0.32\textwidth}  
+            \includegraphics[scale=0.32]{lr_SOM.eps}
+            \caption{LR}
+            \label{fig:LR2}
+    \end{subfigure}
+      \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{svm_SOM.eps}
+            \caption{SVM}
+            \label{SVM2}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{knn_SOM.eps}
+            \caption{k-NN}
+            \label{fig:k-NN2}
+    \end{subfigure}
+      \begin{subfigure}[b]{0.32\textwidth}
+            \includegraphics[scale=0.32]{mlp_SOM.eps}
+            \caption{MLP}
+            \label{MLP2}
+    \end{subfigure}
+    \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
+\label{conv2SOM}
+\end{figure*}
+
+%\begin{figure}[!ht] 
+%\begin{center}
+%  \epsfig{file=fig_time.eps,width=11cm}
+%\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one).
 Plot shows that using categorical variables as part of the dataset makes the problem hard to solve.
 As expected, simpler methods are much faster to build the model than the complex ones.}}
-\label{fig:time}
-\end{center}
-\end{figure}
-
-\begin{figure}[!ht] 
-\begin{center}
-  \epsfig{file=fig_rae.eps,width=11cm}
-\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one).
+%\label{fig:time}
+%\end{center}
+%\end{figure}
+
+%\begin{figure}[!ht] 
+%\begin{center}
+%  \epsfig{file=fig_rae.eps,width=11cm}
+%\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one).
 The M5P model obtains the lowest errors, whatever the dataset used.}}
-\label{fig:rae}
-\end{center}
-\end{figure}
+%\label{fig:rae}
+%\end{center}
+%\end{figure}
 
@@
 \ref{tabla:resultsSOM}, \ref{tabla:results9} and \ref{tabla:results4},
-as well as the figures \ref{fig:time} and \ref{fig:rae}, 
 using those categorical variables as part of a big dataset makes the problem 

### 2016-01-25 paper.tex
adding SOM figures
adding contents provided by Hossam

@@
 
-\subsubsection{Experimental setup}
+\subsection{Experimental setup}
 
@@
 
-\subsubsection{Obtained results}
+\subsection{Obtained results}
 
@@
 \begin{center}
-\includegraphics[scale=0.60]{freq-sales}
+\includegraphics[scale=0.60]{freq_sales.eps}
 \end{center}
@@
 
-In Figure \ref{fig:Umatrix} we label the U-matrix with the Total Sales categories.
+In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales categories.
 It can be clearly shown that the SOM algorithm has successfully clustered the labels of the Total Sales into clear identified regions.
@@
 \begin{center}
-\includegraphics[scale=0.80]{fig1}
+\includegraphics[scale=0.4]{SOM_figure.eps}
 \end{center}
@@
 \begin{figure*}[http] 
-\centering
-    \begin{subfigure}[b]{0.32\textwidth}            
-            \includegraphics[scale=0.50]{Umatrix.eps}
-            \caption{U-matrix}
-            \label{fig:Um}
-    \end{subfigure}%
-    \begin{subfigure}[b]{0.32\textwidth}  
-            \includegraphics[scale=0.50]{Labels.eps}
-            \caption{Labels}
-            \label{L}
-    \end{subfigure}
-
-    \caption{Labeling the U-matrix using the Total Sales variable.}
+\begin{center} 
+\begin{tabular}{cc}
+\includegraphics[scale=0.55]{Umatrix.eps}  &
+\includegraphics[scale=0.55]{Labels.eps}  \\
+U-matrix & Labels 
+\end{tabular}
+\end{center} 
+\caption{Labeling the U-matrix using the total-sales variable.}
 \label{fig:Umatrix} 
@@
 \begin{figure*}[http] 
-\centering
-    \begin{subfigure}[b]{0.32\textwidth}            
-            \includegraphics[scale=0.32]{m5p.eps}
-            \caption{M5P}
-            \label{fig:M5P}
-    \end{subfigure}%
-    \begin{subfigure}[b]{0.32\textwidth}  
-            \includegraphics[scale=0.32]{lr.eps}
-            \caption{LR}
-            \label{fig:LR}
-    \end{subfigure}
-      \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{svm.eps}
-            \caption{SVM}
-            \label{SVM}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{knn.eps}
-            \caption{k-NN}
-            \label{fig:k-NN}
-    \end{subfigure}
-      \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{mlp.eps}
-            \caption{MLP}
-            \label{MLP}
-    \end{subfigure}
+\begin{center} 
+\begin{tabular}{ccc}
+\includegraphics[scale=0.22]{m5p.eps}  &
+\includegraphics[scale=0.22]{lr.eps}   &
+\includegraphics[scale=0.22]{svm.eps}  \\
+M5P & LR & SVM 
+\end{tabular}
+\begin{tabular}{cc}
+\includegraphics[scale=0.22]{knn.eps}  &
+\includegraphics[scale=0.22]{mlp.eps}  \\
+k-NN & MLP
+\end{tabular}
+\end{center} 
 \caption{Actual VS predicted sales for M5P, LR, SVM, k-NN, MLP models.}
@@
 \begin{figure*}[http] 
-\centering
-    \begin{subfigure}[b]{0.32\textwidth}            
-            \includegraphics[scale=0.32]{m5p_RAE.eps}
-            \caption{M5P}
-            \label{fig:M5P1}
-    \end{subfigure}%
-    \begin{subfigure}[b]{0.32\textwidth}  
-            \includegraphics[scale=0.32]{lr_RAE.eps}
-            \caption{LR}
-            \label{fig:LR1}
-    \end{subfigure}
-      \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{svm_RAE.eps}
-            \caption{SVM}
-            \label{SVM1}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{knn_RAE.eps}
-            \caption{k-NN}
-            \label{fig:k-NN1}
-    \end{subfigure}
-      \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{mlp_RAE.eps}
-            \caption{MLP}
-            \label{MLP1}
-    \end{subfigure}
+\begin{center} 
+\begin{tabular}{ccc}
+\includegraphics[scale=0.22]{m5p_RAE.eps}  &
+\includegraphics[scale=0.22]{lr_RAE.eps}   &
+\includegraphics[scale=0.22]{svm_RAE.eps}  \\
+M5P & LR & SVM 
+\end{tabular}
+\begin{tabular}{cc}
+\includegraphics[scale=0.22]{knn_RAE.eps}  &
+\includegraphics[scale=0.22]{mlp_RAE.eps}  \\
+k-NN & MLP
+\end{tabular}
+\end{center} 
 \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
@@
 \begin{figure*}[http] 
-\centering
-    \begin{subfigure}[b]{0.32\textwidth}            
-            \includegraphics[scale=0.32]{m5p_CFS.eps}
-            \caption{M5P}
-            \label{fig:M5P2}
-    \end{subfigure}%
-    \begin{subfigure}[b]{0.32\textwidth}  
-            \includegraphics[scale=0.32]{lr_CFS.eps}
-            \caption{LR}
-            \label{fig:LR2}
-    \end{subfigure}
-      \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{svm_CFS.eps}
-            \caption{SVM}
-            \label{SVM2}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{knn_CFS.eps}
-            \caption{k-NN}
-            \label{fig:k-NN2}
-    \end{subfigure}
-      \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{mlp_CFS.eps}
-            \caption{MLP}
-            \label{MLP2}
-    \end{subfigure}
+\begin{center} 
+\begin{tabular}{ccc}
+\includegraphics[scale=0.22]{m5p_CFS.eps}  &
+\includegraphics[scale=0.22]{lr_CFS.eps}   &
+\includegraphics[scale=0.22]{svm_CFS.eps}  \\
+M5P & LR & SVM 
+\end{tabular}
+\begin{tabular}{cc}
+\includegraphics[scale=0.22]{knn_CFS.eps}  &
+\includegraphics[scale=0.22]{mlp_CFS.eps}  \\
+k-NN & MLP
+\end{tabular}
+\end{center} 
 \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
@@
 \begin{figure*}[http] 
-\centering
-    \begin{subfigure}[b]{0.32\textwidth}            
-            \includegraphics[scale=0.32]{m5p_SOM.eps}
-            \caption{M5P}
-            \label{fig:M5P2}
-    \end{subfigure}%
-    \begin{subfigure}[b]{0.32\textwidth}  
-            \includegraphics[scale=0.32]{lr_SOM.eps}
-            \caption{LR}
-            \label{fig:LR2}
-    \end{subfigure}
-      \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{svm_SOM.eps}
-            \caption{SVM}
-            \label{SVM2}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{knn_SOM.eps}
-            \caption{k-NN}
-            \label{fig:k-NN2}
-    \end{subfigure}
-      \begin{subfigure}[b]{0.32\textwidth}
-            \includegraphics[scale=0.32]{mlp_SOM.eps}
-            \caption{MLP}
-            \label{MLP2}
-    \end{subfigure}
+\begin{center} 
+\begin{tabular}{ccc}
+\includegraphics[scale=0.22]{m5p_SOM.eps}  &
+\includegraphics[scale=0.22]{lr_SOM.eps}   &
+\includegraphics[scale=0.22]{svm_SOM.eps}  \\
+M5P & LR & SVM 
+\end{tabular}
+\begin{tabular}{cc}
+\includegraphics[scale=0.22]{knn_SOM.eps}  &
+\includegraphics[scale=0.22]{mlp_SOM.eps}  \\
+k-NN & MLP
+\end{tabular}
+\end{center} 
 \caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}

### 2016-01-26 paper.tex
adding Experimental-Setup subsection

@@
 
-    \textbf{ TODO: details about the method parameters }
+In most of data mining and machine algorithms, the values of some parameters could have a high influence on its performance.
+In our experiments, the best value of $k$ in the $k$-nearest neighbor was empirically found at $k=3$.
+For SVM, the widely used Radial Basis Function (RBF) kernel is selected.
+As reported in several studies, RBF kernel has a reliable performance and can analyze higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}.
+Two important parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of the RBF kernel.
+We apply grid search which is the most common approach to find $C$ and $\gamma$.
+The best performance of SVM was found at $C=200$ and Gamma $\gamma = 0.01$.
+For MLP, we apply it with one hidden layer since it was proven in the literature that an MLP with one hidden layer can approximate any continuous or discontinuous function \cite{hornik1989multilayer,mirjalili2014let}.
+However, there is no rule of thumb on selecting the best number of neurons in the hidden layer.
+One suggested method that is followed in this work is to set the number of neurons in the hidden layer to $2 \times I + 1$ where $I$ is the number of inputs in the dataset \cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.
+
+All experiments are performed using 10-folds cross validation.
+The dataset is partitioned into 10 parts where the training process is carried out on 9 parts then the resulted model is tested on the left 10th part.
+This process is repeated 10 times, each time the model is trained using different 9 parts.
+At the end of the process the 10 evaluation results on the testing parts are averaged.
 
@@
 
-    \textbf{ TODO: comment the following figures: conv2 , conv2ReliefAttributeEval , conv2CfsSubsetEval , conv2SOM }
+In Figures \ref{conv2}, \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} we depict scatter plots for the values of the actual total sales values against the predicted ones obtained by the developed models.
+Those figures also show the correlation between the two variables and the proportion of variation in actual total sales that is explained by the predicted ones. 
+Figure \ref{conv2} corresponds to the results obtained using all available features without performing any feature selection method.
+In this figure, it can be noticed that SVM achieved the best results by explaining 88.2\% of the actual values while $k$-NN showed very poor results with only 49.8\%.
+Figures \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} show same plots after performing ReliefAttributeEval, CfsSubsetEval and SOM feature selection methods, respectively.
+According to these figures, we can notice that there wasn't almost any significant degradation in the performance of the M5P, LR, SVM and MLP. 
+On the other side, the performance of $k$-NN was dramatically improved after the feature selection process by explaining 84.5\% of variation on average.
 

### 2016-02-02 paper.tex
Problem description
Revised, fixed some things and new text added ;)

@JJ please enhance Table 1

@@
 %********************************************************************************
-\section{The problem}
+\section{Problem description}
 \label{sec:problem}
 
-The main issue of this paper is to forecast sales for 
-unpublished books for which no historical data is available, just some
-descriptive variables relative to the new book. In order to do that,
-training data includes historical sales data for all books published
-in Spain for several years, including those descriptive variables.
-
-%%% Principio de párrafos a eliminar o mover a estado del arte.
-%% Fin de párrafos a eliminar.
-  % [pedro] eliminados
-
-The initial dataset, provided in the framework of a contract by
-Trevenque Editorial, included 3159 books, and included descriptive information 
-for each book, such as price, points of sale, subject, publisher, sales, returns, 
-among other information.
-Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
-each book.
+The main objective of this paper is to forecast sales for 
+unpublished books for which no historical data is available. Instead, just some
+descriptive and pre-sales known variables related to the new book.
+In order to do that, we have used a training dataset which includes historical sales data for a big amount of books published in Spain for several years, with a set of 50 features or variables per pattern.
+
+The initial dataset, provided in the framework of a contract by Trevenque Editorial S.L., included 3159 books. Table \ref{tabla:paramsOrig50} shows the initial set of variables describing each book.
 
 \begin{table}[!ht]
-\caption{Parameters describing a book, as provided by the company Trevenque.}
+\caption{Parameters describing a book, provided by the company Trevenque S.L.}
 \label{tabla:paramsOrig50}
@@
 rest of returns
-total returns firt year
+total returns first year
 returns -  dept stores 1st year
@@
 
+% Antonio - briefly describe the variables
+
 In this prediction problem there are other external variables that also affect 
@@
 indexes to subjectively adjust the results of prediction based on
-external data. %so what?
+external data. 
+Thus, the proposed method, will analyse the provided data and variables and will yield a forecast of sales according to them.
+This result could be used as a reference for a human expert, who would consider it in his/her own prediction process.
 
@@
   % en algunos calculan muchos más, pero estos son los más usados. 
-\begin{table*}[h]
+\begin{table*}[ht]
 \caption{Results (errors and time) obtained using the different forecasting
@@
 using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
-\begin{table*}[h]
+\begin{table*}[ht]
 \caption{Results (errors and time) obtained using the different forecasting methods
@@
 
-\begin{table*}[h]
+\begin{table*}[ht]
 \caption{Results (errors and time) obtained using the different forecasting methods

### 2016-02-02 paper.tex
Methodology review

@@
 
-There are several issues inherent to the problem of predicting sales of new 
-products: the limitation on the amount of data available, the application of 
-different methods and choose the most suitable of them.
-In addition, there is no a standard methodology to solve the general problem 
-of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
-Usually, a preliminary analysis of the data is carried out to eliminate those 
-variables that describe the product but do not provide useful information during 
-the prediction process.
+There is no a standard methodology to solve the general problem of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
+In this work we have followed these steps:
 
@@
 \begin{verbatim}
-  Stage 1: Collecting and analyze data
-		- Variables selection
- 		- Data preprocesing
-  Stage 2: Select the best forecasting method
- 		- Obtaining and evaluating forecasting models
- 		- Calculate forecasting values
-  Stage 3: Subjectively adjust obtained results
+  Step 1: Collect and analyse data
+       - Data preprocessing
+       - Feature selection
+  Step 2: Select the best forecasting method
+       - Evaluate forecasting models
+       - Perform forecast
+  Step 3: Subjectively adjust obtained results
       - Apply additional expert knowledge, such as information 
- 	 	  about seasonality, trends, etc.
+        about seasonality or trends.
 \end{verbatim}
 
-% Maribel: quito la figura por el issue asignado por antonio mora.
-%\begin{figure}[!ht] 
-%\begin{center}
-%  \epsfig{file=stages.eps,width=7cm}
-%\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
-%methods testing, and (3) subjectively adjusting the obtained results.}}
-%\label{fig:stages}
-%\end{center}
-%\end{figure}
-
-Thus, in this study two main stages are proposed: 
-\begin{itemize}
-
-  \item  First, after the editorial company has provided the raw data, taken 
-  directly from its database, a feature selection is carried out, as it is 
-  an effective dimensionality reduction technique and an essential preprocessing 
-  method to remove noise features \cite{Krishnapuram2004}. The idea of these 
-  algorithms is searching the space of attribute subsets to find out which one 
-  in the data works best for classification or prediction.
-  In this stage, the information obtained using several feature selection 
-  methods as well as analyzing the SOM cluster method results is used to 
-  remove some unrelated variables and selects the best variables to be 
-  considered in the forecasted model. % we will use pre-sales data.
-  This task may help to identify leading indicators to be used by the 
-  forecasting methods in order to improve the accuracy of future forecasts.
-
-  \item  Then, several forecasting methods have to be tested. In this stage 
-  different forecasting methods are used to obtain sales forecasts from the 
-  data provided.
-
-\end{itemize}
-
-%In some cases, depending on the company needs and after obtaining the forecasting  results, it is necessary a third stage where experienced managers adjust subject1ively the results obtained using the forecasting methods (see Figure \ref{fig:stages} for details).
-Esta frase no aporta nada que no esté dicho ya antes en los comentarios de las tres etapas que antes estaban en una figura, así que quito la frase entera: Maribel
-
-They might manually adjust the forecasting results taking into account their 
-knowledge in industry experience and their perception about trends.
+%Usually, a preliminary analysis of the data is carried out to eliminate those 
+%variables that describe the product but do not provide useful information during 
+%the prediction process.
+
+The steps are described i the following paragraphs.
+
+First, after the editorial company has provided the raw data, extracted directly from its database, a preprocessing method is performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance.
+Moreover, the initial set of variables is reduced by an expert to use just those that can be known in advance when a new book is launched, i.e.
+\textit{pre-sales data}.
+
+Then, a Feature Selection process \cite{kittler1986feature} is carried out, as it is an effective dimensionality reduction technique and an essential preprocessing method to remove `noisy' (non-useful) features \cite{Krishnapuram2004}.
+The aim of these algorithms is exploring the space of attributes to find out which subset of them yield the best results in a classification or prediction problem.
+  In this stage, both, numerical and visualisation-based approaches has been applied, in order to select the best variables for the forecasting methods.
+  This task may also help to identify leading indicators to be considered by a human expert ti do predictions.
+
+After this process, several forecasting methods have been tested, considering different approaches, such as rule- or tree-based, together with numerical methods. 
+% Antonio - is 'numerical' the best term for these kind of methods?
+The obtained results are then compared.
 
@@
 
-Finally, in the literature different error measures can be found to report 
-the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
+In the literature different error measures can be found to evaluate the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
 Those error measurements are also called error functions or cost functions. 
 %One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
-In any case, we recommend using widely accepted standard 
-equations \cite{gepsoft} in order to compare obtained results with those presented in other research 
-papers using other methods.
-That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
-implemented in tools like Weka \cite{pentaho,Witten2011} 
-or R \cite{otexts,Hyndman2013}, are
-proposed.
-Specifically, in order to compute the forecasting errors of the different methods, 
-Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
-error (RAE) and Root relative squared error (RRSE) have been selected:
+We have used the widely accepted standard equations \cite{gepsoft} in order to compare the obtained results with those presented in other research papers using other methods.
+That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka \cite{pentaho,Witten2011} 
+or R \cite{otexts,Hyndman2013}, are considered.
+Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
 
@@
 
+The created forecasting models and results, along with the selected subset of features, are analysed and presented to the experts in order to aid his/her decision.
+They might manually adjust the forecasting results taking into account their knowledge in industry experience and their perception about trends.
+
 %-------------------------------------------------
@@
 common patterns and obtaining accurate predictions.
-However, in the case of new products, such as the issue of new books, past patterns 
-are difficult to observe as there is no available historical sales data 
-\cite{ChingChin2010} (only pre-sales data is available in this problem).
+However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
+\cite{ChingChin2010} (only pre-sales data are available in this problem).
 % (Paloma) - Se deberían evitar paréntetis.
@@
 
-Feature extraction is a ``transformation-based approach", therefore it transforms the original meaning of the features.
+Feature extraction is a ``transformation-based approach'', therefore it transforms the original meaning of the features.
 This approach involves creating a subset of new features by combinations of the existing features, thus is employed when the semantics of the original dataset will not be needed by any future process.

### 2016-02-02 paper.tex
Fixing my name
some comments about SOM have been fixed and Table3 is changed accordingly

@@
 \author {
-P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Fariss$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
+P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Faris$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
 }
@@
 Most of the M category appears in bottom-right corner while the H and VH categories are concentrated in the bottom-left corner.
-Inspecting the component \texttt{distrib\_novelity}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components have the highest similarity to the clusters shown in the U-matrix.
+By inspecting \texttt{num\_novility}, \texttt{gifts}, \texttt{distrib\_novelity}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components, it can be noticed that they have the highest similarity to the clusters shown in the U-matrix.
 Based on this analysis, those features will be selected for the next stage.
@@
 binding   & $\checkmark$  &   &   &   \\ \hline
-ret\_pricer    & $\checkmark$  &   & $\checkmark$  &   \\ \hline
-reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
+ret\_pricer    & $\checkmark$  &   &   &   \\ \hline
+reprints    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
 num\_reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
@@
 distrib\_novelty   & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
-tot\_points\_sale   & $\checkmark$  & $\checkmark$  &   & $\checkmark$  \\ \hline
-tot\_points\_sale\_1st\_year    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
+tot\_points\_sale   & $\checkmark$  & $\checkmark$  & $\checkmark$   & $\checkmark$  \\ \hline
+tot\_points\_sale\_1st\_year    & $\checkmark$  & $\checkmark$  &  $\checkmark$ &   \\ \hline
 weeks\_sale    & $\checkmark$  & $\checkmark$  &   &   \\ \hline

### 2016-02-02 paper.tex
Some typos and British English revision

--- 2016-02-02 paper.tex
@@
 % Antonio - Decir cuántos años son, que no me acuerdo.
-of data on published books in Spain have been processed by means of data visualization and other feature selection techniques.
+of data on published books in Spain have been processed by means of data visualisation and other feature selection techniques.
 The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
@@
 
-Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimize production and to improve the publishing company profits or minimize losses \cite{Zhao2001}.
+Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimise production and to improve the publishing company profits or minimise losses \cite{Zhao2001}.
 This is the main objective of this paper.
-An example is the optimization of sales \cite{Mattila2002} by
+An example is the optimisation of sales \cite{Mattila2002} by
 improving profit margins by selling the whole print-run. 
@@
 when a new book is published is faced using data provided by the 
-Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}},
+Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
 a company that provides management systems and services for book shops,
@@
 publishers and distributors. 
-Usually, the company's expert sales managers analyzed historical data 
+Usually, the company's expert sales managers analysed historical data 
 and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
@@
 However, carrying out the analysis and forecasting process as a human expert,
-may lead to a 'fuzzy-like' analysis, which may not take all the variables into account. 
+may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
 In addition, the process might be tedious, especially when the amount
@@
 
-With this issue in mind, in this paper a data visualization and preprocessing strategy to find out what are the relevant variables describing a book in the prediction of book sales is proposed; then several standard data mining models
+With this issue in mind, in this paper a data visualisation and preprocessing strategy to find out what are the relevant variables describing a book in the prediction of book sales is proposed; then several standard data mining models
 for sales forecasting are evaluated so a publishing company 
-can deduce and optimize print-run.
+can deduce and optimise print-run.
 % Antonio - cambiar este párrafo para describirlo como un proceso en dos pasos:
@@
 %********************************************************************************
-\section{State of the art on sales forecasting} %FERGU: State of the art on sales forecasting?  ok  ;)
+\section{State of the art on sales forecasting} 
 \label{sec:soa}
@@
 the best method to use is also a problem \cite{ChingChin2010}.
-Moreover, in the case of new unpublished-books, there is no historical data to define patterns, and only some descriptive data about the new book are available 
+Moreover, in the case of new unpublished-books, there are no historical data to define patterns, and only some descriptive data about the new book are available 
 \cite{ChingChin2010,FaderHardie2005,Madsen2008}. Thus, not any time-series forecasting method can be used \cite{Madsen2008,ChernWSF15}.
 
-%This is the new book sales forecasting case, for which no historical data to make predictions is available \cite{ChingChin2010,FaderHardie2005,Madsen2008} and only some descriptive variables relative to the new unpublished-book are available.
-
-%Forecasting sales of new books is a problem with issues such as dealing with limited data, finding adequate forecasting methods and selecting the best method to use \cite{ChingChin2010}.
-
-%In the case of already published books, available historical data might help to generate predictive models.
-%However, in the case of new books there is no historical data to define patterns, and only some descriptive data about the new book is available. 
-%In these cases not any timeseries-based forecasting method can be used \cite{Madsen2008,ChernWSF15}.
-
-%An additional issue is the difficulty to compare our model with classical forecasting methods, such as time series prediction methods, since books do not have specific sales time series.
-
 For this reason, usually the methods used to predict book sales have been generally based on experts' experience.
-They analyze data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
+They analyse data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
 This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.
@@
 propose using the number of blog references as an indicator of the success of a book, and thus its sales.
-Different sales patterns are observed by analyzing data obtained.
+Different sales patterns are observed by analysing data obtained.
 % Antonio - describir esos 'sales patterns'. ;)
@@
 However, the authors used in these papers historical data from published books, 
-%FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso.   ok
 so their proposed methodology can not be applied in the problem of unpublished-books sales prediction.
@@
   % sales forecasting in printed circuit board industry.
-In those cases where historical data is available, classical time series 
-forecasting methods can be applied, which is what the authors do in \cite{Chang2009}, where a hybrid model integrating K-means and fuzzy neural networks to forecast the future sales of a printed circuit board is proposed.
-A similar method is described by Chern et al. \cite{ChernWSF15}, who analyze 
+In those cases where historical data are available, classical time series 
+forecasting methods can be applied, which is what the authors do in \cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy neural networks to forecast the future sales of a printed circuit board is proposed.
+A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
 historical data along online reviews, reviewer characteristics and review 
@@
 Thus, taking into account the kind of problem we address in this paper, i.e.
-the prediction of sales of a new product for which no historical data is available, the classical forecasting methods based on time-series are not
+the prediction of sales of a new product for which no historical data are available, the classical forecasting methods based on time-series are not
 adequate, although they can obviously be used once the book has been launched for sale. 
 In our work the relevant variables in the prediction of sales are identified
-by means of data visualization and feature selection methods. Then, machine learning techniques are applied to predict sales and to infer the ideal print-run of a book.
+by means of data visualisation and feature selection methods. Then, machine learning techniques are applied to predict sales and to infer the ideal print-run of a book.
 In addition, since publishers need models to explain obtained predictions, 
@@
 The main objective of this paper is to forecast sales for 
-unpublished books for which no historical data is available. Instead, just some
-descriptive and pre-sales known variables related to the new book.
+unpublished books for which no historical data are available. Instead, just some
+descriptive and variables known in advance related to the new book.
 In order to do that, we have used a training dataset which includes historical sales data for a big amount of books published in Spain for several years, with a set of 50 features or variables per pattern.
@@
 author
-retail pricer
+retail price
 subject1
@@
 In this work we have followed these steps:
-
-\hspace{2cm}
+%\hspace{2cm}
 \begin{verbatim}
@@
 
-The steps are described i the following paragraphs.
-
 First, after the editorial company has provided the raw data, extracted directly from its database, a preprocessing method is performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance.
@@
 
-In general, historical data is used to make time series, and from them extracting 
+In general, historical data are used to make time series, and from them extracting 
 common patterns and obtaining accurate predictions.
@@
 
-SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organization, configures the output units into a topological representation of the original data.
-It tries to imitate the self-organization done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus.
-SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organize data so as to disclose so far unknown patterns or structures.
+SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organisation, configures the output units into a topological representation of the original data.
+It tries to imitate the self-organisation done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus.
+SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organise data so as to disclose so far unknown patterns or structures.
 It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem.
@@
 SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons.
-It allows us to visualize any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure.
+It allows us to visualise any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure.
 High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.
 
-SOMs (and U-Matrix) are usually applied for visualize natural structures in the data and their relations, as well as the natural groupings that could be among them.
+SOMs (and U-Matrix) are usually applied for visualise natural structures in the data and their relations, as well as the natural groupings that could be among them.
 In addition, SOM makes easy the estimation of the variables that have more influence on these groupings.
-Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recognizer.
-
-This method is usually applied to analyze data as similar items tend to be 
+Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.
+
+This method is usually applied to analyse data as similar items tend to be 
 mapped close together, while those items dissimilar, are mapped apart.
@@
 (predictive of) the class, yet uncorrelated with (not predictive of) each other''.
-This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.
+This evaluator needs the numeric features to be transformed to nominal features first, by being discretised.
 The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation.
@@
 Also, it is applicable even working with both nominal and numeric features, without the need for transformations.
-For this algorithm, the weight of an attribute depends on the difference of an attribute value inside an instance with its neighbors, being these the nearest instance of the same class, and the nearest of the different class.
-Therefore, a good attribute is that which gives similar values fos instances of the same class, and different values for instances of different class.
+For this algorithm, the weight of an attribute depends on the difference of an attribute value inside an instance with its neighbours, being these the nearest instance of the same class, and the nearest of the different class.
+Therefore, a good attribute is that which gives similar values for instances of the same class, and different values for instances of different class.
   \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator.
@@
 
-However, as in the case of new books only some descriptive data is available %FERGU: data es plural. is->are
+However, as in the case of new books only some descriptive data are available %FERGU: data es plural. is->are
 (compared to those cases in which historical data on sales of published books 
@@
 experiments and even to solve similar sales prediction problems using
-these methods. % eliminado el pie de página, es mejor usar referencias - JJ
+these methods.
 
@@
 variables (predictor) over the range of values in the dataset. 
-In this statistical technique, data is modeled using linear functions to estimate 
-unknown model parameters, examining the linear correlations between independent 
-and dependent variables.
+In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.
 
@@
 function of the independent variables. Moreover, the linear relation can be 
-solved using the least squares method, that minimizes the error between the 
+solved using the least squares method, that minimises the error between the 
 actual data and the regression line \cite{McClendon2015}.
@@
 In classification problems the algorithm searches for an optimal hyperplane 
-that separates two classes, maximizing the margin between two classes. 
+that separates two classes, maximising the margin between two classes. 
 In the case of regression the algorithm chooses a hyperplane close to as many 
-of the data points as possible, minimizing the sum of the distances from 
+of the data points as possible, minimising the sum of the distances from 
 the data points to the hyperplane. 
@@
 located, assigning the resulting class to an unclassified vector using the 
-closest k vectors found in the training set by majority vote.
+closest $k$ vectors found in the training set by majority vote.
 
@@
 
-This model is a generalization of the standard linear perceptron that uses several 
+This model is a generalisation of the standard linear perceptron that uses several 
 layers of nodes (called neurons) and that is able to solve linearly inseparable 
@@
 
-The objective is finding the most appropriate forecasting method that minimizes 
+The objective is finding the most appropriate forecasting method that minimises 
 the error between the obtained forecast and the actual sales for each new book 
@@
 In most of data mining and machine algorithms, the values of some parameters could have a high influence on its performance.
-In our experiments, the best value of $k$ in the $k$-nearest neighbor was empirically found at $k=3$.
+In our experiments, the best value of $k$ in the $k$-nearest neighbour was empirically found at $k=3$.
 For SVM, the widely used Radial Basis Function (RBF) kernel is selected.
-As reported in several studies, RBF kernel has a reliable performance and can analyze higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}.
+As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}.
 Two important parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of the RBF kernel.
@@
 
-Once the methods to be applied have been chosen, they must be applied to datasets 
-to obtain the prediction models for each one. 
+Once the methods to be applied have been chosen, they must be applied to the datasets to obtain the prediction models for each one. 
 Later on, the models ability must be validated on non-previously seen data.
@@
 has been used to estimate how accurately the predictive model will perform in 
-practice. %, limiting at the same time the overfitting problem.
+practise. %, limiting at the same time the overfitting problem.
 
@@
 Using the ReliefFAttributeEval feature selection method, and taking into account 
-the best ranked atributes, the following variables have been selected: 
+the best ranked attributes, the following variables have been selected: 
 \emph{print-run, number of reprints, total points of sale, total points of sale 
@@
 % seleccionaron las variables más adecuadas.
-Then, an exhaustive analisys of the SOM results was carried out in order to 
-determine the best variables to be considered to buid the forecasting model.
-
-Further important prepocessing steps are carried out before applying the SOM analysis.
+Then, an exhaustive analysis of the SOM results was carried out in order to 
+determine the best variables to be considered to build the forecasting model.
+
+Further important preprocessing steps are carried out before applying the SOM analysis.
 First, in order to label the U-matrix with total-sales values, this variable is converted from numerical to categorical.
@@
 Table \ref{table:freq} and Figure \ref{fig:count} reveal more information about the nature of the dataset.
-We can notice that most of 77\% of the book are categorized as VL and L with limited number of sales.
+We can notice that most of 77\% of the book are categorised as VL and L with limited number of sales.
 On the other side, the books that achieved more than 2000 sold copies are just around 4\%.
@@
 Second, two categorical features (i.e; Editorial and Collection) are removed from the analysis since they have large number of unique different values and therefore they are less informative.
-Moreover, four features (i.e; Subject1, Subject2, Subject3 and Book-bining) have more than 10\% missing values so they are removed also.
+Moreover, four features (i.e; Subject1, Subject2, Subject3 and Book-binding) have more than 10\% missing values so they are removed also.
 
@@
 The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data.
-The best SOM training results are obtained with a final quantization error of 0.691 and topographic error of 0.046.
+The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.
 
@@
 The term component is used in SOM to refer to the features.
-The component planes in Figure \ref{fig:componentplanes} show the trend of values of the the prototype vectors of the SOM map units.
-These values are represented as colors.
-The colorbar on the right of each component plane shows the indication of each color.
+The component planes in Figure \ref{fig:componentplanes} show the trend of values of the prototype vectors of the SOM map units.
+These values are represented as colours.
+The colorbar on the right of each component plane shows the indication of each colour.
 On the other side, the U-matrix on the top left corner shows the distances between the adjacent units.
@@
 Most of the M category appears in bottom-right corner while the H and VH categories are concentrated in the bottom-left corner.
-Inspecting the component \texttt{distrib\_novelity}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components have the highest similarity to the clusters shown in the U-matrix.
+By inspecting \texttt{num\_reprints}, \texttt{gifts}, \texttt{distrib\_novelty}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components, it can be noticed that they have the highest similarity to the clusters shown in the U-matrix.
 Based on this analysis, those features will be selected for the next stage.
@@
 \hline
-Variable  & PreSales & ReliefFAttributeEval  & SOM & CfsSubsetEval \\ \hline \hline
+Variable  & Pre-Sales & ReliefFAttributeEval  & SOM & CfsSubsetEval \\ \hline \hline
 subject1    & $\checkmark$  &   &   &   \\ \hline
@@
 binding   & $\checkmark$  &   &   &   \\ \hline
-ret\_pricer    & $\checkmark$  &   & $\checkmark$  &   \\ \hline
-reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
+ret\_price    & $\checkmark$  &   &   &   \\ \hline
+reprints    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
 num\_reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
@@
 the Weka implementation, and they were run 30 times with the Weka default parameter 
-settings and a different random initialization seed for each run and each dataset.
+settings and a different random initialisation seed for each run and each dataset.
 
@@
 methods on the original dataset (16 variables per book). In this case,
-due to the categorial variables, the MLP could not be run.}
+due to the categorical variables, the MLP could not be run.}
 \label{tabla:resultsT}
@@
 errors to those of M5P. Even when used using the default parameter values it exhibit 
-a good generalization performance.
+a good generalisation performance.
 However, it is much slower than the others to build the model, not only when 
@@
 However, the model is slow when classifying (as there are a large number of 
-training examples), and it exhibit a poor generalization ability, as it does not 
+training examples), and it exhibit a poor generalisation ability, as it does not 
 learn anything from the training data.
@@
 Moreover, in these experiments it has been seen the difficulty to process 
-information related to categorial variables, such as \emph{editorial} and 
+information related to categorical variables, such as \emph{editorial} and 
 \emph{collection}.
@@
 This is a very challenging problem in this industry, because printing a higher 
-number of volumnes than those finally sold will lead to losses, 
-while printing an adequate number of copies will optimize sales and company earnings.
+number of volumes than those finally sold will lead to losses, 
+while printing an adequate number of copies will optimise sales and company earnings.
 In addition, there are several difficulties inherent to the new book sales forecasting, 
@@
 A dataset consisting of 3159 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
-publishing company Trevenque Editorial has been used.
-
-In this paper, a data visualization method has been used to find out what are 
+publishing company Trevenque Editorial S.L. has been used.
+
+In this paper, a data visualisation method has been used to find out what are 
 the relevant variables describing a book in the prediction of book sales.
@@
 Not only the obtained forecasting error has been taking into account to evaluate
-those methods, but also the the cost of model building as parameter setting and 
+those methods, but also the cost of model building as parameter setting and 
 the required time to train the model.
@@
 
-%---------- trabajos futuros
+%---------- trabajo futuro
 
@@
 going to be sent to each possible point of sale. This can be
-incorporated into an optimization model that optimizes those values to
+incorporated into an optimisation model that optimises those values to
 obtain desired sales. This is left as future work.
@@
 This work has been supported in part by projects 
-PreTEL (PRM Consultores - Trevenque),
+PreTEL (PRM Consultores - Trevenque S.L.),
 TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitiveness), 

### 2016-02-06 paper.tex
Modificaciones al texto y varias preguntas para @pacv y @amorag. He borrado mis comentarios anteriores ya resueltos

@@
 since it implies a loss of investment due to inventory excess. In this
-paper we are tackling the problem of predicting total sales in order to 
+paper, we are tackling the problem of predicting total sales in order to 
 print the right amount of books, doing so even before the book has
-reached shelves. 
+reached the shelves. 
 Several years 
@@
 runs do not exceed predicted sales. 
-Indeed, several studies have demonstrated that improving sale predictions 
+Indeed, several studies have demonstrated that improving sales predictions 
 (a reduction of forecasting errors) results in an enhancing in the 
+%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
 production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
@@
 whereas if the number of printed copies was not enough, you can always print more. 
+%FERGU: el you ese es muy coloquial, reescribir
 % Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema.
@@
 % Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
+%FERGU: lo de one or the other direction creo que confunde
 
@@
 This is the main objective of this paper.
+%FERGU: entonces el objetivo es desarrollar una herramienta? La metodología? Dejarlo más claro en todos los sitios
 An example is the optimisation of sales \cite{Mattila2002} by
@@
 However, designing such an accurate predictive tool is a difficult task in this scope, as book sales are influenced by several factors that make them fluctuate and, moreover, usually they might be not controllable and even unknown.
-For instance, some are related with decisions on purchases, others with freight 
+%FERGU: "moreover, usually" son dos adverbios juntos y queda un poco raro 
+For instance, some are related to decisions on purchases, others with freight 
+%FERGU: some factors para dejarlo claro
 traffic, or others with the distribution strategy \cite{Little1998}.
@@
 In addition, some may have correlations between them. 
+%FERGU: some ... variables, no?
 However, these correlations can be detected using data analysis methods, 
@@
 may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
+%FERGU: fuzzy-like existe? suena raruno :P
 In addition, the process might be tedious, especially when the amount
@@
 is perhaps the most used technique to tackle the sales forecasting problems. 
-%FERGU: terminar esta frase con punto en vez de coma para que no sea larga.   OK
 The efficiency of these techniques strongly depends on the field of application 
@@
 They analyse data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
+%FERGU: quitad los paréntesis :)
 This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.
@@
   %     Moon2010ICEC
-Recently, some works propose analyzing relationships between on-line information 
+Recently, some works have proposed analyzing relationships between on-line information 
 and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}.
 Specifically, Moon et al.
-propose using the number of blog references as an indicator of the success of a book, and thus its sales.
+propose using the number of blog references as an indicator of the success of a book, and thus, its sales.
 Different sales patterns are observed by analysing data obtained.
 % Antonio - describir esos 'sales patterns'. ;)
-%
+% FERGU: y también cuales son esos 'data obtained'
 However, the authors used in these papers historical data from published books, 
-so their proposed methodology can not be applied in the problem of unpublished-books sales prediction.
+so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
+%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?
 
@@
 %
-In the same line, Thomassey et al.
-\cite{SThomassey2014} propose using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, %FERGU: appared?
-apparel, creo.
-¡sí!
+In the same line, Thomassey et al. \cite{SThomassey2014} propose using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
 a very similar issue to the new book publishing one.
@@
 and on the influence of variables such as promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
+%FERGU: completar con: "In our case, these ideas ..."
 
@@
 In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern. 
-%FERGU: "_a_ similar sales pattern", mejor?
-ok
 However, as the authors state, the proposed system can not deal with qualitative 
@@
 The main objective of this paper is to forecast sales for 
+%FERGU: el objetivo es la herramienta o la predicción?
 unpublished books for which no historical data are available. Instead, just some
+%FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
 descriptive and variables known in advance related to the new book.
@@
 the sales of a new book, such as those related to seasonality, trends or 
-promotions, that classical prediction methods can not deal with.
+promotions, that classical prediction methods can not deal with. %FERGU: por qué?
 However, an expert can consider them to modify the forecast obtained by 
@@
 There is no a standard methodology to solve the general problem of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
-In this work we have followed these steps:
+In this work we have followed these steps: %FERGU: por qué estos steps y no otros? Ponerlo aquí. Esta metodología es general o solo para este paper?
 %\hspace{2cm}
@@
 The aim of these algorithms is exploring the space of attributes to find out which subset of them yield the best results in a classification or prediction problem.
-  In this stage, both, numerical and visualisation-based approaches has been applied, in order to select the best variables for the forecasting methods.
-  This task may also help to identify leading indicators to be considered by a human expert ti do predictions.
+  In this stage, both, numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting methods.
+  This task may also help to identify leading indicators to be considered by a human expert to make predictions.
 
@@
 % Antonio - is 'numerical' the best term for these kind of methods?
+%FERGU: OJO que en esta sección a veces usáis el presente perfecto (have been) y otras el presente (is performed)
 The obtained results are then compared.
@@
 Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
+%FERGU: have been selected for this methodology, for this work... algo así
 
@@
 
+%FERGU: poner aquí algo de un párrafo que explique como se valida la metodología
+
 %-------------------------------------------------
 \subsection{Data collection and analysis}
+%FERGU: The first step in our methodology is...
 
@@
 Feature extraction is a ``transformation-based approach'', therefore it transforms the original meaning of the features.
-This approach involves creating a subset of new features by combinations of the existing features, thus is employed when the semantics of the original dataset will not be needed by any future process.
+This approach involves creating a subset of new features by combinations of the existing features, thus it is employed when the semantics of the original dataset will not be needed by any future process.
 On the contrary, feature selection attempts to retain the meaning of the original feature set.
@@
 
-SOMs (and U-Matrix) are usually applied for visualise natural structures in the data and their relations, as well as the natural groupings that could be among them.
+SOMs (and U-Matrix) are usually applied to visualise natural structures in the data and their relations, as well as the natural groupings that could be among them.
 In addition, SOM makes easy the estimation of the variables that have more influence on these groupings.
 Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.
+%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
 
@@
 
-As far as the feature selection methods are concerned, Weka separates the process in two parts:
+As far as the feature selection methods are concerned, Weka separates the process into two parts:
+%FERGU: por qué mencionamos a Weka aquí y no antes?
 \begin{itemize}
@@
 
-However, as in the case of new books only some descriptive data are available %FERGU: data es plural. is->are
+However, as in the case of new books only some descriptive data are available 
 (compared to those cases in which historical data on sales of published books 

### 2016-02-23 paper.tex
Local changes

--- 2016-02-02 paper.tex
@@
 To do so, in a first stage, the feature selection process has been carried out 
-using both the CfsSubsetEval \cite{Hall1998} (a correlation-based feature subset 
+using both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset 
 evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
@@
 % print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
-Using the ReliefFAttributeEval feature selection method, and taking into account 
+Using the {\tt ReliefFAttributeEval} feature selection method, and taking into account 
 the best ranked attributes, the following variables have been selected: 
@@
 % num_reprints tot_points_sale print_run + total_sales
-Using the CfsSubsetEval feature selection method, the following variables have 
+Using the {\tt CfsSubsetEval} feature selection method, the following variables have 
 been selected: \emph{number of reprints, total points of sale, print-run, total sales}.
@@
 % seleccionaron las variables más adecuadas.
-Then, an exhaustive analysis of the SOM results was carried out in order to 
+Then, an analysis of the SOM results has been carried out in order to 
 determine the best variables to be considered to build the forecasting model.
@@
 Further important preprocessing steps are carried out before applying the SOM analysis.
-First, in order to label the U-matrix with total-sales values, this variable is converted from numerical to categorical.
-Five categories have been created to represent the quantities of sales of each book: Very Low (VL), Low (L), Medium (M), High (H) and Very High (VH).
-Table \ref{table:freq} shows the ranges of total-sales that correspond to each category along with the number of books that fall in.
-Table \ref{table:freq} and Figure \ref{fig:count} reveal more information about the nature of the dataset.
-We can notice that most of 77\% of the book are categorised as VL and L with limited number of sales.
-On the other side, the books that achieved more than 2000 sold copies are just around 4\%.
-This makes the problem of identifying those two categories much harder.
-The new categorical feature is used to replace the old numerical Total Sales feature in the SOM analysis.
+First, in order to label the U-matrix with total-sales values, this
+variable is converted from numerical to categorical. Five categories
+have been created to represent the quantities of sales of each book:
+Very Low (VL), Low (L), Medium (M), High (H) and Very High (VH). Table
+\ref{table:freq} shows the ranges of total-sales that correspond to
+each category along with the number of books that fall in. Table
+\ref{table:freq} and Figure \ref{fig:count} reveal more information
+about the nature of the dataset. We can notice that most of 77\% of
+the book are categorised as VL and L with limited number of sales. On
+the other side, the books that achieved more than 2000 sold copies are
+just around 4\%. This makes the problem of identifying those two
+categories much harder. The new categorical feature is used to replace
+the old numerical Total Sales feature in the SOM analysis.
 
@@
 
-Second, two categorical features (i.e; Editorial and Collection) are removed from the analysis since they have large number of unique different values and therefore they are less informative.
-Moreover, four features (i.e; Subject1, Subject2, Subject3 and Book-binding) have more than 10\% missing values so they are removed also.
-
-Finally, the resulted dataset consisted of ten features including the new Total Sales categorical feature.
-The SOM algorithm is trained based on the nine numerical variables while the new total-sales variable is used to label this data.
-The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data.
-The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.
-
-Figure \ref{fig:componentplanes} shows the U-matrix and component variables resulted from SOM training.
-The term component is used in SOM to refer to the features.
-The component planes in Figure \ref{fig:componentplanes} show the trend of values of the prototype vectors of the SOM map units.
-These values are represented as colours.
-The colorbar on the right of each component plane shows the indication of each colour.
-On the other side, the U-matrix on the top left corner shows the distances between the adjacent units.
-It is important to note that high values in the matrix indicates large distance between the units of the map.
-It can be noticed also that there are more hexagons in the U-matrix than component planes since the distances between units is also represented as hexagons.
-
-In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales categories.
-It can be clearly shown that the SOM algorithm has successfully clustered the labels of the Total Sales into clear identified regions.
-In the top of the U-matrix the VL category is located.
-The L category appears in the middle of the matrix.
-Most of the M category appears in bottom-right corner while the H and VH categories are concentrated in the bottom-left corner.
-By inspecting \texttt{num\_reprints}, \texttt{gifts}, \texttt{distrib\_novelty}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components, it can be noticed that they have the highest similarity to the clusters shown in the U-matrix.
-Based on this analysis, those features will be selected for the next stage.
+Second, two categorical features (i.e; Editorial and Collection) are
+removed from the analysis since they have large number of unique
+different values and therefore they are less informative. Moreover,
+four features (i.e; Subject1, Subject2, Subject3 and Book-binding)
+have more than 10\% missing values so they are removed also.
+
+Finally, the resulted dataset consisted of ten features including the
+new Total Sales categorical feature. The SOM algorithm is trained
+based on the nine numerical variables while the new total-sales
+variable is used to label this data. The SOM algorithm is applied with
+a large map size of $26 \times 16$  in order to represent the
+data. The best SOM training results are obtained with a final
+quantisation error of 0.691 and topographic error of 0.046.
+
+Figure \ref{fig:componentplanes} shows the U-matrix and component
+variables resulted from SOM training. The term component is used in
+SOM to refer to the features. The component planes in Figure
+\ref{fig:componentplanes} show the trend of values of the prototype
+vectors of the SOM map units. These values are represented as
+colours. The colorbar on the right of each component plane shows the
+indication of each colour. On the other side, the U-matrix on the top
+left corner shows the distances between the adjacent units. It is
+important to note that high values in the matrix indicates large
+distance between the units of the map. It can be noticed also that
+there are more hexagons in the U-matrix than component planes since
+the distances between units is also represented as hexagons.
+
+In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales
+categories. It can be clearly shown that the SOM algorithm has
+successfully clustered the labels of the Total Sales into clear
+identified regions. In the top of the U-matrix the VL category is
+located. The L category appears in the middle of the matrix. Most of
+the M category appears in bottom-right corner while the H and VH
+categories are concentrated in the bottom-left corner.
+By inspecting \texttt{num\_reprints}, \texttt{gifts},
+\texttt{distrib\_novelty}, \texttt{tot\_points\_sale},
+\texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run}
+components, it can be noticed that they have the highest similarity to
+the clusters shown in the U-matrix. Based on this analysis, those
+features will be selected for the next stage.
 
@@
 error) after applying the proposed forecasting methods on the original dataset,
-using the 16 available variables per book.
+using the 16 variables that describe each book.
 In this dataset, every book is described using not only numerical variables, 
-but using two additional categorical variables, \emph{editorial} and \emph{collection}, 
-what makes harder to process the instances and build the different models.
+but also two additional categorical variables, \emph{editorial} and \emph{collection}, 
+which could, a priori, make harder to process the instances and build the different models.
 
@@
   % en algunos calculan muchos más, pero estos son los más usados. 
+% OK
 \begin{table*}[ht]

### 2016-02-25 paper.tex
Changes in Methodology
According to what we have finally done

@@
 \institute{
-$^1$Department of Computer Architecture and Computer Technology. CITIC. University of Granada (Spain)\\
+$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
 $^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
@@
 
-There is no a standard methodology to solve the general problem of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
-In this work we have followed these steps: %FERGU: por qué estos steps y no otros? Ponerlo aquí. Esta metodología es general o solo para este paper?
+There is not a standard methodology to solve the general problem of sales forecasting. The steps we have followed in this paper are described below.
+% Antonio - quito esto porque ya no es lo que se ha hecho. El objetivo del paper no es la metodología a seguir, eso es estándar. ;)
+%FERGU: hacer más hincapié de esto en la intro entonces
+%In this work we have followed these steps: %FERGU: por qué estos steps y no otros? Ponerlo aquí. Esta metodología es general o solo para este paper?
 %\hspace{2cm}
-\begin{verbatim}
-  Step 1: Collect and analyse data
-       - Data preprocessing
-       - Feature selection
-  Step 2: Select the best forecasting method
-       - Evaluate forecasting models
-       - Perform forecast
-  Step 3: Subjectively adjust obtained results
-      - Apply additional expert knowledge, such as information 
-        about seasonality or trends.
-\end{verbatim}
+%\begin{verbatim}
+%  Step 1: Collect and analyse data
+%       - Data preprocessing
+%       - Feature selection
+%  Step 2: Select the best forecasting method
+%       - Evaluate forecasting models
+%       - Perform forecast
+%  Step 3: Subjectively adjust obtained results
+%      - Apply additional expert knowledge, such as information 
+%        about seasonality or trends.
+%\end{verbatim}
 
@@
 
-First, after the editorial company has provided the raw data, extracted directly from its database, a preprocessing method is performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance.
-Moreover, the initial set of variables is reduced by an expert to use just those that can be known in advance when a new book is launched, i.e.
+First, after the editorial company has provided the raw data (extracted directly from its database), a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance.
+Moreover, the initial set of variables (presented in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to use just those that can be known in advance when a new book is launched, i.e.
 \textit{pre-sales data}.
 
-Then, a Feature Selection process \cite{kittler1986feature} is carried out, as it is an effective dimensionality reduction technique and an essential preprocessing method to remove `noisy' (non-useful) features \cite{Krishnapuram2004}.
-The aim of these algorithms is exploring the space of attributes to find out which subset of them yield the best results in a classification or prediction problem.
-  In this stage, both, numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting methods.
+Then, a Feature Selection (FS) process \cite{kittler1986feature} has been carried out, as it is an effective dimensionality reduction technique and an essential preprocessing method to discard `noisy' (non-useful) features \cite{Krishnapuram2004}.
+The aim of these algorithms is exploring the space of attributes to find out which subset of them yields the best results in a classification or prediction problem.
+  In this stage, both, numerical and visualisation-based approaches have been applied in this paper, in order to select the best variables for the forecasting 
+methods.
+% Antonio - Decidir si es 'forecasting' o 'regression' (o si son indiferentes) y usarlo siempre en el texto
   This task may also help to identify leading indicators to be considered by a human expert to make predictions.
+
+Moreover, the application of FS also aims to reduce the computational time for building the forecasting models, along with the complexity of the obtained models themselves.
+This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (editors).
 
@@
 %FERGU: OJO que en esta sección a veces usáis el presente perfecto (have been) y otras el presente (is performed)
-The obtained results are then compared.
-
-%Finally, although different authors have proposed metrics to determine 
-%the accuracy of estimates, most companies use metrics based on the analysis 
-%of errors, i.e. MAE or RMSE \cite{ChingChin2010,Madsen2008}.
-
-In the literature different error measures can be found to evaluate the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
-Those error measurements are also called error functions or cost functions. 
-%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
-We have used the widely accepted standard equations \cite{gepsoft} in order to compare the obtained results with those presented in other research papers using other methods.
-That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka \cite{pentaho,Witten2011} 
-or R \cite{otexts,Hyndman2013}, are considered.
+% Antonio - Corregido. ;)
+
+The obtained results are then compared and analysed, considering, in addition to the obtained \textit{correlation coefficient}, some error measurements from the literature \cite{ChingChin2010,Madsen2008}.
+Those are also called error functions or cost functions.
+We have considered the widely accepted standard equations \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011}
+or R \cite{otexts,Hyndman2013}.
 Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
@@
 %FERGU: poner aquí algo de un párrafo que explique como se valida la metodología
+% Antonio - TODO: esto habrá que explicarlo mejor cuando esté hecho y veamos lo que sale. ;)
 

### 2016-02-26 paper.tex
Some more text in Methodology

@@
 
-After this process, several forecasting methods have been tested, considering different approaches, such as rule- or tree-based, together with numerical methods. 
+After this process, several forecasting techniques have been tested, such as rule- or tree-based, together with numerical methods. 
 % Antonio - is 'numerical' the best term for these kind of methods?
@@
 % Antonio - Corregido. ;)
-
-The obtained results are then compared and analysed, considering, in addition to the obtained \textit{correlation coefficient}, some error measurements from the literature \cite{ChingChin2010,Madsen2008}.
-Those are also called error functions or cost functions.
-We have considered the widely accepted standard equations \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011}
-or R \cite{otexts,Hyndman2013}.
+%
+The obtained results have been compared and analysed, computing, in addition to the obtained \textit{correlation coefficient}, some error measures from the literature \cite{ChingChin2010,Madsen2008}.
+We have considered the widely accepted standard formulae \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
 Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
 %FERGU: have been selected for this methodology, for this work... algo así
+% Antonio - ya se ha dicho. ;)
 
@@
 
-The created forecasting models and results, along with the selected subset of features, are analysed and presented to the experts in order to aid his/her decision.
+Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (editorials) in order to prove the value of the proposal.
+Some specific interpretable models have been created as a final result of the work.
+The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).
+
+%The created forecasting models and results, along with the selected subset of features, are analysed and presented to the experts in order to aid his/her decision.
 They might manually adjust the forecasting results taking into account their knowledge in industry experience and their perception about trends.

### 2016-02-26 paper.tex
Random Forest description

@@
 
-In general, historical data are used to make time series, and from them extracting 
-common patterns and obtaining accurate predictions.
+In general, historical data are used to make time series, and from them extracting common patterns and obtaining accurate predictions.
 However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
@@
 
-In addition, in order to reduce the dimensionality of the input data and to choose an 
-appropriate set of variables, the SOM \cite{kohonen1998} method has been also applied.
-
-SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organisation, configures the output units into a topological representation of the original data.
+In addition, in order to reduce the dimensionality of the input data and to choose an appropriate set of variables, the Self-Organizing Map (SOM) \cite{kohonen1998} method has been also applied.
+
+Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organisation, configures the output units into a topological representation of the original data.
 It tries to imitate the self-organisation done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus.
@@
 %FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
+% Antonio - arreglado
 
@@
 mapped close together, while those items dissimilar, are mapped apart.
-Also, the SOM graph represents and highlight very clearly those regions (clusters) 
-with high training sample concentration and fewer where the samples are scarce. 
+Also, the SOM graph represents and highlight very clearly those regions (clusters) with high training sample concentration and fewer where the samples are scarce. 
 %FERGU: mencionarlo en la intro
 
-As far as the feature selection methods are concerned, Weka separates the process into two parts:
+As far as the feature selection methods are concerned, Weka software separates the process into two parts:
 %FERGU: por qué mencionamos a Weka aquí y no antes?
+% Antonio - se ha mencionado, pero sí, habría que destacarlo un poco más desde la intro quizá.
 \begin{itemize}
   \item Attribute evaluator: This is the method by which the feature subsets are assessed.
-In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method are used.
+In this work, both a correlation-based feature subset evaluation method ({\tt CfsSubsetEval}) and an adaptation of relief for attribute estimation ({\tt ReliefFAttributeEval}) evaluation method are used.
 
@@
 
+ % weka.classifiers.lazy.IBk 
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
+ \item \emph{k-Nearest Neighbours (kNN)}: 
+The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
+which the unknown instances are classified by relating them to the known 
+instances using a distance measurement/function (Euclidean, Minkowsky or minimax).
+
+The main idea behind the algorithm is that two instances far enough in the space, 
+taking into account the distance function, are less likely to belong to the 
+same class than two closely situated instances.
+
+The classification algorithm locates the nearest neighbour in instance space and 
+assigns the class of that neighbour to the unknown instance.
+In order to improve the robustness of the model, several neighbours can be 
+located, assigning the resulting class to an unclassified vector using the 
+closest $k$ vectors found in the training set by majority vote.
+
+ \item \emph{Random Forest}: This method is based in the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm.
+It was proposed by Breiman \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution.
+The result is the average of the generated trees during the process.
+
  % weka.classifiers.functions.LinearRegression
@@
 
- % weka.classifiers.lazy.IBk 
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
- \item \emph{k-Nearest Neighbours (kNN)}: 
-The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
-which the unknown instances are classified by relating them to the known 
-instances using a distance measurement/function (Euclidean, Minkowsky or minimax).
-
-The main idea behind the algorithm is that two instances far enough in the space, 
-taking into account the distance function, are less likely to belong to the 
-same class than two closely situated instances.
-
-The classification algorithm locates the nearest neighbour in instance space and 
-assigns the class of that neighbour to the unknown instance.
-In order to improve the robustness of the model, several neighbours can be 
-located, assigning the resulting class to an unclassified vector using the 
-closest $k$ vectors found in the training set by majority vote.
+% Antonio - MLP no se ha aplicado al final...
 
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
- \item \emph{Multilayer Perceptron}:
-A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
-artificial neural network model that maps the input data onto an appropriate output. 
-It is an artificial neural network generally used for classification or 
-approximation problems.
-
-This model is a generalisation of the standard linear perceptron that uses several 
-layers of nodes (called neurons) and that is able to solve linearly inseparable 
-problems \cite{SteinwenderBitzer2003}.
-Each neuron consists of a linear combination of weighted inputs which is passed 
-though a non-linear activation function to produce its output.
-
-This kind of artificial neural network is trained using a supervised learning 
-technique called back-propagation.
-This training method was developed independently by Werbos \cite{Werbos1974}, 
-Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
-in updating the weights of the output layer neurons once the erroneous output 
-has been obtained, and then, propagating the successive weight layers back to 
-the input layer.
-
-A key issue when designing an MLP is the number of hidden layers of neurons.
-Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
-create classifying regions of any kind. This result was then confirmed in later 
-works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
+% \item \emph{Multilayer Perceptron}:
+%A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
+%artificial neural network model that maps the input data onto an appropriate output. 
+%It is an artificial neural network generally used for classification or 
+%approximation problems.
+%
+%This model is a generalisation of the standard linear perceptron that uses several 
+%layers of nodes (called neurons) and that is able to solve linearly inseparable 
+%problems \cite{SteinwenderBitzer2003}.
+%Each neuron consists of a linear combination of weighted inputs which is passed 
+%though a non-linear activation function to produce its output.
+%
+%This kind of artificial neural network is trained using a supervised learning 
+%technique called back-propagation.
+%This training method was developed independently by Werbos \cite{Werbos1974}, 
+%Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
+%in updating the weights of the output layer neurons once the erroneous output 
+%has been obtained, and then, propagating the successive weight layers back to 
+%the input layer.
+%
+%A key issue when designing an MLP is the number of hidden layers of neurons.
+%Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
+%create classifying regions of any kind. This result was then confirmed in later 
+%works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
 

### 2016-03-14 paper.tex
Description of Pre-sales data
Justification of some decisions in this regard

@@
 \usepackage[latin1]{inputenc}
+\usepackage{url}
 
@@
 
-%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
 \author {
@@
 rest of returns
-total returns first year
+total returns 1st year
 returns -  dept stores 1st year
@@
 %-------------------------------------------------
-\subsection{Data collection and analysis}
-%FERGU: The first step in our methodology is...
+\subsection{Data collection}
 
@@
 However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
-\cite{ChingChin2010} (only pre-sales data are available in this problem).
-% (Paloma) - Se deberían evitar paréntetis.
-
-In addition, among the variables describing a new book, some may affect 
+\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem.
+
+Moreover, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
+those whose value don't depend on the book sales.
+So, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
+
+\begin{table}
+\caption{Considered pre-sales features and their types. It also shows the names of the variables used in the applied methods.}
+\label{tabla:params_pre_sales}
+\begin{center}
+\begin{tabular}{|c|l|l|c|c|}
+\hline 
+No. & Feature Name & Variable & Type & Input/Output\\
+\hline 
+1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
+2 & main subject (code) & \texttt{subject1} & numerical & input\\
+3 &  editorial + collection (joint code) & \texttt{collection} & categorical & input\\
+4 & bookbinding (code) & \texttt{binding} & categorical & input\\
+5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
+6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
+7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
+8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
+9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
+10 & print run & \texttt{print\_run} & numerical & input\\
+\hline 
+\hline
+11 & total sales & \texttt{total\_sales} & numerical & output\\
+\hline 
+\end{tabular}
+\end{center}
+\end{table}
+
+As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods.
+\texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by an editor.
+In addition, this variable could be interesting to be used to test the prediction model, once it is built.
+So the editor could try different values for it and see what the predictor yields, in order to take the best decision.
+
+Initially, there were three different features describing the subjects and subsubjects of every book \textit{subject1,2,3} (see Table \ref{tabla:paramsOrig50}), but for most of the patterns (books) there is no value for subjects2 and 3, so we have discarded these features.
+
+Regarding the feature \textit{editorial}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
+In addition, we think it is not really relevant for the accuracy of the models and, moreover, editors will not consider the results in other editorials for predicting its own sales.
+% Antonio - Think about this... should we mention this?
+
+Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the editor, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass.
+So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance.
+The same reasoning can be applied to subclasses.
+
+%-------------------------------------------------
+\subsection{Data preprocessing and initial analysis}
+
+Once a dataset has been composed it must be preprocessed, i.e.
+it should be revised in order to fix the existing errors (such as wrong or duplicated patterns), or to complete (or address) the absence of information, for instance.
+The aim is looking for the correctness, homogeneity and completeness of the data.
+
+After this, the features describing every pattern are frequently analysed.
+In this case, among the variables describing a new book, some may affect 
 predictions (those variables provide information), while others may not be 

### 2016-03-14 paper.tex
Rewritten and revised Intro and SoA
They have to be rewritten completely. The SoA is the usual this guys do this, some other guys do that. We should present an argument for our paper, along the lines of

* Prediction is usually based on time series forecasting (refs) or, in some cases, in x or y from blogs (refs).
* however, predicting the reaction to new products is hard for two reasons: no historial data (refs) and difficult processing of available variables: categorical, non-relevant, whatever (refs).
* Even so, these guys (refs) have managed to do this and that, but they are black box (ref

@@
 Several years 
-% Antonio - Decir cuántos años son, que no me acuerdo.
-of data on published books in Spain have been processed by means of data visualisation and other feature selection techniques.
-The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
-The described methodology improves the forecasting running time and is eventually able to predict sales with remarkable accuracy.
-Moreover, the proposed method has been validated by the company that provided the data and incorporated in a business intelligence tool for publishers,
+% % Antonio - Decir cuántos años son, que no me acuerdo.
+% of data on published books in Spain have been processed by means of
+% data visualisation %visualization does not "process". I propose an alternative
+%  and other feature selection techniques. 
+We have been working on a data set that includes the complete sales
+data for books published in Spain across several years. After an
+initial exploratory phase using visualization techniques, we have
+applied several feature selection techniques in order
+to find out what are the variables that have more impact on sales, and
+then used machine learning to create a model and forecast sales. 
+The described methodology improves the forecasting running time  %with
+                                %respect to what?- JJ
+and is
+eventually able to predict sales with remarkable accuracy. Moreover,
+the proposed method was validated by the company that provided
+the data and incorporated in a business intelligence tool for
+publishers, % We shouldn't say this, it's outside the bounds of the
+            % paper. Besides, it was a different technique - JJ
 since the obtained models provide a reliable guidance on the decision process of
@@
 % Antonio - esto es cierto??? :D
+% We should simply say: 
+% The method presented here provides a reliable data processing
+% technique for editorial data and also yields a reasonable result
+% that allows publishers to forecast sales and then create the
+% appropriate print run without incurring in losses. 
+%
+% Besides, if this is true:
+% It also provides a method that is able to provide insight on the
+% decisions that have an influence on the print run for publishers. 
 \end{abstract}
@@
 
-Publishing a book, as releasing any other product, implies several
+Publishing a book, as releasing any other cultural product with a
+physical substrate, implies several
 types of risks and costs due to
-the complexity and derived expenses of the production and distribution processes. 
-% tienes que enmarcar el problema. Se trata de productos culturales
-% con soporte físico y con ventas relativamente pequeñas. Libros,
-% discos, no sé si alguna cosa más. - JJ
-A newly launched product could be, additionally, completely new to the company (not a new version or edition of a previous product), and sales forecasts can
-only be based on the experience of other similar products. 
-In this scope, having accurate estimations of future sales of the new
+the complexity, and derived expenses, of the production and
+distribution processes.  When a company is faced with the problem or
+releasing a completely new product, in the sense that it is an unknown
+author or a new topic with no track record, sales forecasts can
+only be based on the experience obtained from other similar products,
+but the definition of ``similar'' itself is obscure and, sometimes,
+subjective. Even if it is a known author or topic, having accurate
+estimations of future sales of the new 
 product is extremely important \cite{ChingChin2010}, so that production
-runs do not exceed predicted sales. 
+runs do not exceed predicted sales by too much. 
 Indeed, several studies have demonstrated that improving sales predictions 
-(a reduction of forecasting errors) results in an enhancing in the 
+(a reduction of forecasting errors) results in an enhancement in the 
 %FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
 production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
+%which should be obvious from the get go, don't know why you need 4
+%papers to affirm that - JJ
 
@@
 
-Book publishers, as well as other content producers, release new {\em
-  products} more frequently than other industries, so that they face the
+The problem is specially acute for book publishers, who, among other
+content providers, release new {\em products} more frequently than
+other industries, so that they face the 
 problem of predicting sales quite often. The issue, in this case, is to print an
@@
 % Antonio - 'sunk inventory cost' es corecto?
-whereas if the number of printed copies was not enough, you can always print more. 
+% Sí, pero corecto no lo es. - JJ
+whereas if the number of printed copies was not enough, a new print
+run can be made, resulting in temporary losses due to lack of supply;
+a real problem, to be sure, but less dire than having too many unsold
+books.  
 %FERGU: el you ese es muy coloquial, reescribir
@@
 % - algunas más... :D
-In this sense, errors in one or the other direction do not have the same impact, although a temporal scarcity of a book that is selling well is also a problem.
+% Corregido - JJ
+In this sense, errors in one or the other direction do not have the same impact.
 % Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
 %FERGU: lo de one or the other direction creo que confunde
-
-Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimise production and to improve the publishing company profits or minimise losses \cite{Zhao2001}.
-This is the main objective of this paper.
+% Lo que habría que decir es hablar de cómo hemos tratado una u otra
+% cosa. ¿Estamos sesgando hacia predecir menos ventas de las que
+% habría? ¿O simplemente es por tener un poco de background? Igual
+% deberíamos haberlas tratado de forma diferente. - JJ
+
+Thus, it is extremely important to develop an accurate predictive method
+which could accurately forecast the future sales a new book will
+achieve, in order to optimise production, improve the publishing
+company profits or minimise losses \cite{Zhao2001}. This is the main
+objective of this paper. 
 %FERGU: entonces el objetivo es desarrollar una herramienta? La metodología? Dejarlo más claro en todos los sitios
@@
 improving profit margins by selling the whole print-run. 
-% Antonio - podrías extender un poco el ejemplo? Es decir, describir un poco más lo que se hace en ese trabajo. ;)
-
-However, designing such an accurate predictive tool is a difficult task in this scope, as book sales are influenced by several factors that make them fluctuate and, moreover, usually they might be not controllable and even unknown.
+% Antonio - podrías extender un poco el ejemplo? Es decir, describir
+% un poco más lo que se hace en ese trabajo. ;)
+% An example of what? Does that go there? - JJ
+
+However, designing such an accurate predictive tool is a difficult
+task in this scope, as book sales are influenced by several factors
+that make them fluctuate and, moreover, usually they might be not
+controllable and even unknown. 
 %FERGU: "moreover, usually" son dos adverbios juntos y queda un poco raro 
@@
 %FERGU: some factors para dejarlo claro
-traffic, or others with the distribution strategy \cite{Little1998}.
+traffic, or others with the distribution strategy \cite{Little1998}. % This paragraph is rather useless - JJ
 
@@
 such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
-or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they do? What are the results?
-
-In this research, the problem of how many units should be printed 
+or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
+                                % do? What are the results?
+% This is a state of the art? Are we already in the state of the art?
+% - JJ
+
+In the research published in this paper, the problem of how many units should be printed 
 when a new book is published is faced using data provided by the 
 Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
-a company that provides management systems and services for book shops,
+a company that provides management systems and services for bookshops,
 % Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
@@
 Usually, the company's expert sales managers analysed historical data 
-and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
-                        % varias citas - JJ
+and applied their knowledge using external variables to compute
+correct estimations (predictions), for instance, she can decide
+increasing or decreasing the sales prediction based on season or sales
+period.                         % varias citas - JJ
                         % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
@@
 techniques to be adopted so that, estimating sales task is carried out
-reliably, accurately, and in an automatic way.
-
-With this issue in mind, in this paper a data visualisation and preprocessing strategy to find out what are the relevant variables describing a book in the prediction of book sales is proposed; then several standard data mining models
+reliably, accurately, and in an automatic way. % Iterative. Another
+                                % useless paragraph - JJ
+
+With this issue in mind, in this paper a data visualisation and
+preprocessing strategy to find out what are the relevant variables
+describing a book in the prediction of book sales is proposed; then
+several standard data mining models  
 for sales forecasting are evaluated so a publishing company 
@@
 % - predicción
+After this initial processing phase, we apply machine learning
+techniques to create a sales model and use it to predict them.
 
@@
 % - mejores resultados (si algunas variables interfieren entre sí)
+% - Permiten saber qué variables son las que influyen realmente en el
+% resultado. Esto es lo único importante - JJ
 
@@
 
-Sales forecasting is a problem which has been addressed several times in the literature.
-Most of the studies have been conducted using different analysis and forecasting methods, such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001}, applied to different industrial sectors.
+Sales forecasting is a problem which has been addressed several times
+in the literature. Most of the studies have been conducted using
+different analysis and forecasting methods, such as regression models
+\cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy
+systems \cite{Mastorocostas2001}, applied to different industrial
+sectors. 
 % ¿Y qué? Esta frase
@@
 % Antonio - la he intentado mejorar.
+% Muchas cosas de la intro tendrían que venir aquí, al estado del
+% arte. Habría que reescribir la intro. - JJ
 
 Specifically, Time-Series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
-is perhaps the most used technique to tackle the sales forecasting problems. 
-The efficiency of these techniques strongly depends on the field of application 
-and the correctness of the problem data. However, since they require a large amount of data for predicting sales, these methods are not the most suitable for this task \cite{ChingChin2010}.
-
-This is the case of new book sales forecasting, a problem with issues such as 
-dealing with quite limited data (just a few variables are known in advance) or the existence of several categorical values (which are harder to be processed).
-Given these issues, finding adequate forecasting techniques and selecting
-the best method to use is also a problem \cite{ChingChin2010}.
-Moreover, in the case of new unpublished-books, there are no historical data to define patterns, and only some descriptive data about the new book are available 
-\cite{ChingChin2010,FaderHardie2005,Madsen2008}. Thus, not any time-series forecasting method can be used \cite{Madsen2008,ChernWSF15}.
-
-For this reason, usually the methods used to predict book sales have been generally based on experts' experience.
-They analyse data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
+is perhaps the most used technique to tackle the sales forecasting
+problems. The efficiency of these techniques strongly depends on the field of application 
+and the correctness of the problem data. However, since they require a
+large amount of data for predicting sales, these methods are not the
+most suitable for this task \cite{ChingChin2010}. And they cannot be
+applied before the book is published, as is the objective of this
+paper.
+
+In this case, just a few variables are known in advance
+\cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
+them are categorical, harder to process, even more so if the number
+of categories is high. Given these issues, finding adequate
+forecasting techniques and selecting  
+the best method to use is also a problem \cite{ChingChin2010}. % Qualify this citation - jj
+
+% Thus, not any time-series forecasting method can be used
+% \cite{Madsen2008,ChernWSF15}. 
+% Qualify those references!!! What do they say?
+
+For this reason, usually the methods used to predict book sales have
+been generally based on experts' experience.% Reference - JJ
+ They analyse data about
+sales and, taking into account their knowledge in industry, their
+experience, and their perception about trends, could make decisions on
+the companies production (how many books should be printed when a new
+book is published). 
 %FERGU: quitad los paréntesis :)
-This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.
-
+% Fergu: quítalos tú, tío, aquí puede editar todo el mundo - JJ
+This is a complex problem, since the predictions are influenced by
+external variables that must be taken into account, such as
+seasonality, promotions or fashions that expert managers might
+subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
+                                % has something to do with the
+                                % previous paragraph? Put it there!!! 
+%
   %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
@@
 Recently, some works have proposed analyzing relationships between on-line information 
-and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}.
-Specifically, Moon et al.
-propose using the number of blog references as an indicator of the success of a book, and thus, its sales.
-Different sales patterns are observed by analysing data obtained.
+and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
+et al. propose using the number of blog references as an indicator of
+the success of a book, and thus, its sales. Different sales patterns
+are observed by analysing data obtained. 
 % Antonio - describir esos 'sales patterns'. ;)
@@
 In those cases where historical data are available, classical time series 
-forecasting methods can be applied, which is what the authors do in \cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy neural networks to forecast the future sales of a printed circuit board is proposed.
+forecasting methods can be applied, which is what the authors do in
+\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
+neural networks to forecast the future sales of a printed circuit
+board is proposed. % We have been talking above that above and SAID IT
+                   % DIDN'T WORK? Why do we say it here again?
 A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
@@
 In addition, since publishers need models to explain obtained predictions, 
-`black box' forecasting methods may not be suitable, so models based on decision rules have been tested as an alternative.
+`black box' forecasting methods may not be suitable, so models based
+on decision rules have been tested as an alternative.
 

### 2016-03-14 paper.tex
Mainly comments on the paper
And I think the UMatrix should be moved to Section 3, giving it some more weight. Besides, UMatrix is done for exploratory data analysis and to examine the problem, so it corresponds to "problem description". It is really _not_ part of data processing, because you don't extract any conclusion that excludes or includes variables (I think). Please @amorag check this out.

@@
 board is proposed. % We have been talking above that above and SAID IT
-                   % DIDN'T WORK? Why do we say it here again?
+                   % DIDN'T WORK? Why do we say it here again? - JJ
 A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
@@
 %FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
-descriptive and variables known in advance related to the new book.
-In order to do that, we have used a training dataset which includes historical sales data for a big amount of books published in Spain for several years, with a set of 50 features or variables per pattern.
-
-The initial dataset, provided in the framework of a contract by Trevenque Editorial S.L., included 3159 books. Table \ref{tabla:paramsOrig50} shows the initial set of variables describing each book.
+descriptive and variables known in advance related to the new book. In
+order to do that, we have used a training dataset which includes
+historical sales data for a big amount of books published in Spain for
+several years, with a set of 50 features or variables per pattern.
+
+The initial dataset, provided in the framework of a contract by
+Trevenque Editorial S.L., included 3159 books. Table
+\ref{tabla:paramsOrig50} shows the initial set of variables describing
+each book.
 
@@
 external data. 
-Thus, the proposed method, will analyse the provided data and variables and will yield a forecast of sales according to them.
-This result could be used as a reference for a human expert, who would consider it in his/her own prediction process.
+Thus, the proposed method, will analyse the provided data and
+variables and will yield a forecast of sales according to them. This
+result could be used as a reference for a human expert, who would
+consider it in his/her own prediction process.
+
+% This section is too short and really does not describe the problem
+% to its full extent. First, it should say if some of these variables
+% were discarded for some reason. Group the variables we have in those
+% available to publisher and those that can be used afterwards. And
+% then give an idea of the complexity of the problem and how difficult
+% it should be to find a solution - JJ
 
@@
 
-First, after the editorial company has provided the raw data (extracted directly from its database), a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance.
-Moreover, the initial set of variables (presented in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to use just those that can be known in advance when a new book is launched, i.e.
-\textit{pre-sales data}.
-
-Then, a Feature Selection (FS) process \cite{kittler1986feature} has been carried out, as it is an effective dimensionality reduction technique and an essential preprocessing method to discard `noisy' (non-useful) features \cite{Krishnapuram2004}.
-The aim of these algorithms is exploring the space of attributes to find out which subset of them yields the best results in a classification or prediction problem.
+First, after the editorial company has provided the raw data
+(extracted directly from its database), a preprocessing method has
+% This should go to the previous section. 
+been performed in order to remove incorrect or incoherent patterns,
+such as those with null values in required variables, or with negative
+sales, for instance. Moreover, the initial set of variables (presented
+in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
+use just those that can be known in advance when a new book is
+launched, i.e. \textit{pre-sales data}.
+
+% You have to present the problem and not the solution. It's not "what
+% you did last summer", it is SCIENCE. Why did you think FS was
+% needed? What procedure did you use for it?
+Then, a Feature Selection (FS) process \cite{kittler1986feature} has
+been carried out, as it is an effective dimensionality reduction
+technique and an essential preprocessing method to discard `noisy'
+(non-useful) features \cite{Krishnapuram2004}. The aim of these
+% Did you know there were noisy features? Why? 
+% You should include in the previous section an exploratory data
+% analysis that describes the range of variables, how many categories
+% those variables have, and so an do forth - JJ 
+algorithms is exploring the space of attributes to find out which
+subset of them yields the best results in a classification or
+prediction problem. 
   In this stage, both, numerical and visualisation-based approaches have been applied in this paper, in order to select the best variables for the forecasting 
@@
 \begin{table}
-\caption{Considered pre-sales features and their types. It also shows the names of the variables used in the applied methods.}
+% Shouldn't this table go to "Problem description"? It is a
+% preliminary selection - JJ
+\caption{Considered pre-sales features and their types. It also shows
+  the names of the variables used in the applied methods.} 
 \label{tabla:params_pre_sales}
@@
 
-Once a dataset has been composed it must be preprocessed, i.e.
-it should be revised in order to fix the existing errors (such as wrong or duplicated patterns), or to complete (or address) the absence of information, for instance.
-The aim is looking for the correctness, homogeneity and completeness of the data.
+Once a dataset has been composed it must be preprocessed, i.e. it
+should be revised in order to fix the existing errors (such as wrong
+or duplicated patterns), or to complete (or address) the absence of
+information, for instance. The aim is looking for the correctness,
+homogeneity and completeness of the data. % useless paragraph - JJ
+
+%You need to lay out to the reader what you are going to do here. In
+%order to reach objective x, we need to do y, that is why we use
+%z. After using z, we prove that we have done y and thus reached
+%objective x. For instance
+% A exploratory data analysis that shows the distribution of variables
+% as well as a priori clusters is the first phase in any data
+% processing method
+% (BTW, you should include data visualization in problem description,
+% because it shows the distribution of problem variables and then
+% suggests ways to deal with it) - JJ
+% and so on...
 
@@
 
-Moreover, the algorithm running times grow with the number of features, and thus 
-making the algorithm impractical for problems with a large number of features 
-\cite{Selvakuberan2008}.
-Feature reduction is a task that is usually applied in these kind of situations, having two ways of performance \cite{kittler1986feature}: feature extraction and feature selection.
+% You have to justify its application to this particular problem. What
+% was the runnning time with all variables? What reduction was your
+% target? - JJ
+Moreover, the algorithm running time grows with the number of
+features, making it impractical for problems with a large number of features 
+\cite{Selvakuberan2008}. Feature reduction is a task that is usually
+applied in these kind of situations, having two ways of performance
+\cite{kittler1986feature}: feature extraction and feature selection.  
+% two ways of performance? WTF? Do you mean "being performed in two
+% different ways?" - JJ
 %Feature selection task is usually carried out by 
@@
 
-Feature extraction is a ``transformation-based approach'', therefore it transforms the original meaning of the features.
-This approach involves creating a subset of new features by combinations of the existing features, thus it is employed when the semantics of the original dataset will not be needed by any future process.
-On the contrary, feature selection attempts to retain the meaning of the original feature set.
-It is part of what is called semantic-preserving techniques, known as ``selection-based approaches".
-By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}.
-In the problem this work assesses, it is very important to maintain the semantics of the set of initial variables, and therefore several feature selection methods have been applied.
-
-In addition, in order to reduce the dimensionality of the input data and to choose an appropriate set of variables, the Self-Organizing Map (SOM) \cite{kohonen1998} method has been also applied.
-
-Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organisation, configures the output units into a topological representation of the original data.
-It tries to imitate the self-organisation done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus.
-SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organise data so as to disclose so far unknown patterns or structures.
-It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem.
-The main property of the SOM is that it makes a nonlinear projection from a high-dimensional data space (one dimension per variable) on a regular, low-dimensional (usually 2D) grid of neurons, called units.
-SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons.
-It allows us to visualise any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure.
-High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.
-
-SOMs (and U-Matrix) are usually applied to visualise natural structures in the data and their relations, as well as the natural groupings that could be among them.
-In addition, SOM makes easy the estimation of the variables that have more influence on these groupings.
-Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.
+Feature extraction is a ``transformation-based approach'', therefore
+it transforms the original meaning of the features. This approach
+involves creating a subset of new features by combinations of the
+existing features, thus it is employed when the semantics of the
+original dataset will not be needed by any future process. On the
+contrary, feature selection attempts to retain the meaning of the
+original feature set. It is part of what is called semantic-preserving
+techniques, known as ``selection-based approaches". By searching
+through all possible combinations of features, the aim of these
+techniques is to determine a minimal feature subset to reduce
+processing time, while obtaining the same or higher accuracy as the
+initial feature set \cite{liu1998feature}. In the problem this work
+addresses, it is very important to maintain the semantics of the set of
+initial variables, and therefore several feature selection methods
+have been applied.
+
+In addition, in order to reduce the dimensionality of the input data
+and to choose an appropriate set of variables, the Self-Organizing Map
+(SOM) \cite{kohonen1998} method has been also applied. % Why? Is that
+                                % one of the two forms of feature
+                                % selection? What do we expect to
+                                % learn from it? - JJ
+
+Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that
+uses an unsupervised training algorithm and which, through a process
+called self-organisation, configures the output units into a
+topological representation of the original data. It tries to imitate
+the self-organisation done in the sensory cortex of the human brain,
+where neighbouring neurons are activated by similar stimulus. SOM
+belongs to a general class of neural network methods, which are
+non-linear regression techniques that can be trained to learn or find
+relationships between inputs and outputs or to organise data so as to
+disclose so far unknown patterns or structures. It is usually used as
+a clustering/classification tool or used to find unknown relationships
+between a set of variables that describe a problem. The main property
+of the SOM is that it makes a nonlinear projection from a
+high-dimensional data space (one dimension per variable) on a regular,
+low-dimensional (usually 2D) grid of neurons, called units. 
+SOM is further processed using Ultsch method \cite{UmatUlts}, the
+Unified distance matrix (U-matrix), which uses SOM's codevectors
+(vectors of variables of the problem) as data source and generates a
+matrix where each component is a distance measure between two adjacent
+neurons. It allows us to visualise any multi-variated dataset in a
+two-dimensional display, so we can detect topological relations among
+neurons and infer about the input data structure. High values in the
+U-matrix represent a frontier region between clusters, and low values
+represent a high degree of similarities among neurons on that region,
+clusters .
+
+SOMs (and U-Matrix) are usually applied to visualise natural
+structures in the data and their relations, as well as the natural
+groupings that could be among them. In addition, SOM makes easy the
+estimation of the variables that have more influence on these
+groupings. Other statistical and soft computing tools can also be used
+for this purpose, but since Kohonen's SOMs offers a visual way of
+doing it, it is much more intuitive, and takes advantage of the
+capabilities of the human brain as a pattern recogniser. 
 %FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
 % Antonio - arreglado 
+% And this is going to be useful because... - JJ
 
@@
 mapped close together, while those items dissimilar, are mapped apart.
-Also, the SOM graph represents and highlight very clearly those regions (clusters) with high training sample concentration and fewer where the samples are scarce. 
+Also, the SOM graph represents and highlight very clearly those
+regions (clusters) with high training sample concentration and fewer
+where the samples are scarce.  
 %FERGU: mencionarlo en la intro
+% Which is interesting because... JJ
 

### 2016-03-14 paper.tex
A very extensive rearrangement of the problem description and results section should be done.
Please @amorag revise comments and so on.

@@
 experiments and even to solve similar sales prediction problems using
-these methods.
-
-Specifically, the following forecasting methods are proposed:
+these methods. % Why these and not others? Exploratory data analysis?
+               % - JJ
+
+Specifically, the following forecasting methods are proposed: % Proposed why? - JJ
 \begin{itemize}
@@
 
+%An intro should go here - JJ
+
 \subsection{Experimental setup}
 
-In most of data mining and machine algorithms, the values of some parameters could have a high influence on its performance.
-In our experiments, the best value of $k$ in the $k$-nearest neighbour was empirically found at $k=3$.
-For SVM, the widely used Radial Basis Function (RBF) kernel is selected.
-As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}.
-Two important parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of the RBF kernel.
-We apply grid search which is the most common approach to find $C$ and $\gamma$.
-The best performance of SVM was found at $C=200$ and Gamma $\gamma = 0.01$.
-For MLP, we apply it with one hidden layer since it was proven in the literature that an MLP with one hidden layer can approximate any continuous or discontinuous function \cite{hornik1989multilayer,mirjalili2014let}.
-However, there is no rule of thumb on selecting the best number of neurons in the hidden layer.
-One suggested method that is followed in this work is to set the number of neurons in the hidden layer to $2 \times I + 1$ where $I$ is the number of inputs in the dataset \cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.
-
-All experiments are performed using 10-folds cross validation.
-The dataset is partitioned into 10 parts where the training process is carried out on 9 parts then the resulted model is tested on the left 10th part.
-This process is repeated 10 times, each time the model is trained using different 9 parts.
-At the end of the process the 10 evaluation results on the testing parts are averaged.
+In most data mining and machine learning algorithms, the values of
+some parameters have a high influence on its performance. In our
+experiments, the best value of $k$ in the $k$-nearest neighbour was
+empirically found at $k=3$. % What???? - JJ
+ For SVM, the widely used Radial Basis
+Function (RBF) kernel is selected. As reported in several studies, RBF
+kernel has a reliable performance and can analyse higher dimensional
+data \cite{yu2004ec,chao2015construction,huang2006ga}. Two important
+parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of
+the RBF kernel. We apply grid search which is the most common approach
+to find $C$ and $\gamma$. The best performance of SVM was found at
+$C=200$ and Gamma $\gamma = 0.01$. For MLP, we apply it with one
+hidden layer since it was proven in the literature that an MLP with
+one hidden layer can approximate any continuous or discontinuous
+function \cite{hornik1989multilayer,mirjalili2014let}. However, there
+is no rule of thumb on selecting the best number of neurons in the
+hidden layer. One suggested method that is followed in this work is to
+set the number of neurons in the hidden layer to $2 \times I + 1$
+where $I$ is the number of inputs in the dataset
+\cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.
+
+All experiments are performed using 10-fold cross validation. The
+dataset is partitioned into 10 parts where the training process is
+carried out on 9 parts then the resulted model is tested on the left
+10th part. This process is repeated 10 times, each time the model is
+trained using different 9 parts. At the end of the process the 10
+evaluation results on the testing parts are averaged.
 
@@
 \caption{Number of books in each category.}
+%This should go also to exploratory data analysis, that is, problem
+%description - JJ
 \label{fig:count}
@@
 In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales
-categories. It can be clearly shown that the SOM algorithm has
+categories. It can be clearly seen that the SOM algorithm has
 successfully clustered the labels of the Total Sales into clear
-identified regions. In the top of the U-matrix the VL category is
+identified regions. %So what? - JJ
+ In the top of the U-matrix the VL category is
 located. The L category appears in the middle of the matrix. Most of
@@
 categories are concentrated in the bottom-left corner.
+% OK, this means that these features are more or less clearly
+% separable. But the problem is that the UMatrix shows only 2, maybe 3
+% clusters: vh and H. That's it. If you know UMatrix, that's what you
+% see - JJ
 By inspecting \texttt{num\_reprints}, \texttt{gifts},
@@
 features will be selected for the next stage.
+%  This is not a result, it is data preprocessing. You should have
+%  included it in the 4th section. All results do not need to go into
+%  the "REsults" section, only the final results. 
+% Besides, are you using this or feature selection for selecting
+% features?
 
@@
 \end{center} 
-\caption{Actual VS predicted sales for M5P, LR, SVM, k-NN, MLP models.}
+\caption{Actual vs. predicted sales for M5P, LR, SVM, k-NN, MLP
+  models.}
+% You should use a log-log scale here to see it more clearly. Besides,
+% please say in a comment the script you are using to generate it, we
+% are going to need it later on - JJ
 \label{conv2}

### 2016-03-29 paper.tex
comentarios
New structure and results in experiments
Still several contents to add and change

@@
 
-% Antonio - El título habría que cambiarlo a otro más descriptivo, creo yo. A ver si os gusta este
-
 %%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
 \author {
-P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Faris$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
+P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
 }
@@
 data for books published in Spain across several years. After an
-initial exploratory phase using visualization techniques, we have
+initial exploratory phase using visualisation techniques, we have
 applied several feature selection techniques in order
@@
 presented.  %FERGU: mejor described para no repetir
-Section \ref{sec:experiments} reports and analyzes the obtained results with a 
+Section \ref{sec:experiments} reports and analyses the obtained results with a 
 real dataset. Finally, conclusions and future work are presented in Section
@@
   %     Moon2010ICEC
-Recently, some works have proposed analyzing relationships between on-line information 
+Recently, some works have proposed analysing relationships between on-line information 
 and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
@@
 data related to the products. Moreover, real-world cases, such as consumer 
-electronics and fashion products, should be deeply analyzed, as these industries 
+electronics and fashion products, should be deeply analysed, as these industries 
 present/launch new products every season.
@@
                    % DIDN'T WORK? Why do we say it here again? - JJ
+                   % No, above we said that the efficiency depends on the field 
+                   % of application and the available problem data. - pedro
 A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
@@
 influences to understand how electronic `word-of-mouth' influences product sales. 
-The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.
+The proposed method is suitable for those sales forecasting problems 
+with a big amount of online reviews and historical data.
 
@@
 \subsection{Data preprocessing and initial analysis}
+\label{subsec:data_preproces}
 
@@
 
-Specifically, the following forecasting methods are proposed: % Proposed why? - JJ
+Specifically, the following forecasting methods are proposed: 
+        % Proposed why? - JJ
+        % because those methods were those that could lead with the problem data - pedro
 \begin{itemize}
@@
 
-%An intro should go here - JJ
+% An intro should go here - JJ
+% Antonio - done
+
+This section presents the experiments conducted over the dataset considering the pre-sales variables forecasting new book sales.
+Feature selection techniques have been also applied in order to test their utility by comparing the obtained results.
+
+We have analysed the whole dataset (all the editorials), but also performed some experiments considering specific editorials as example cases.
+The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for editors.
+
+%--------------------------------------------------------------------------
 
@@
 
-All experiments are performed using 10-fold cross validation. The
-dataset is partitioned into 10 parts where the training process is
-carried out on 9 parts then the resulted model is tested on the left
-10th part. This process is repeated 10 times, each time the model is
-trained using different 9 parts. At the end of the process the 10
-evaluation results on the testing parts are averaged.
-
-\subsection{Obtained results}
-
-Once the methods to be applied have been chosen, they must be applied to the datasets to obtain the prediction models for each one. 
-Later on, the models ability must be validated on non-previously seen data.
-Specifically, instead of using the conventional validation strategy based on 
-using a training set and later on a testing set (unknown data against which 
-the model must be tested), a cross-validation technique \cite{Geisser1993,Kohavi1995,Devijver1982} 
-has been used to estimate how accurately the predictive model will perform in 
-practise. %, limiting at the same time the overfitting problem.
-
-%
-% TODO: explicar los resultados obtenidos en la selección de variables: 
-%  (1) con el SOM, (2) con los métodos de selecc. vars.
-%
-% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
-% - se ha usado la implementación de estos 5 métodos del paquete WEKA
-% - se han realizado 30 ejecuciones con cada método
-% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
-To do so, in a first stage, the feature selection process has been carried out 
-using both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset 
-evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
-adaptation of relief for attribute estimation) evaluation methods, implemented 
-in the Weka tool.
-
-% con ReliefFAttributeEval salen seleccionadas (9):
-% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
-Using the {\tt ReliefFAttributeEval} feature selection method, and taking into account 
-the best ranked attributes, the following variables have been selected: 
-\emph{print-run, number of reprints, total points of sale, total points of sale 
-1st year, reprints, units distributed as novelty, weeks for sale, total sales}.
-
-% con CfsSubsetEval salen seleccionadas (4):
-% num_reprints tot_points_sale print_run + total_sales
-Using the {\tt CfsSubsetEval} feature selection method, the following variables have 
-been selected: \emph{number of reprints, total points of sale, print-run, total sales}.
-%FERGU: podeis quitar estos parrafos de variables porque ya está la tabla :)
-
-%*************************************** SOM ANALISYS
-% como tercer método, se ha usado el SOM; tras interpretar los mapas, se
-% seleccionaron las variables más adecuadas.
-Then, an analysis of the SOM results has been carried out in order to 
-determine the best variables to be considered to build the forecasting model.
-
-Further important preprocessing steps are carried out before applying the SOM analysis.
-First, in order to label the U-matrix with total-sales values, this
-variable is converted from numerical to categorical. Five categories
-have been created to represent the quantities of sales of each book:
-Very Low (VL), Low (L), Medium (M), High (H) and Very High (VH). Table
-\ref{table:freq} shows the ranges of total-sales that correspond to
-each category along with the number of books that fall in. Table
-\ref{table:freq} and Figure \ref{fig:count} reveal more information
-about the nature of the dataset. We can notice that most of 77\% of
-the book are categorised as VL and L with limited number of sales. On
-the other side, the books that achieved more than 2000 sold copies are
-just around 4\%. This makes the problem of identifying those two
-categories much harder. The new categorical feature is used to replace
-the old numerical Total Sales feature in the SOM analysis.
-
-\begin{table*}[ht]
-\caption{Categories corresponding to total-sales variable. }
+All experiments are performed using 10-fold cross validation \cite{Geisser1993,Kohavi1995,Devijver1982}.
+The dataset is partitioned into 10 parts where the training process is carried out on 9 parts then the resulted model is tested on the left 10th part.
+This process is repeated 10 times, each time the model is trained using different 9 parts.
+At the end of the process the 10 evaluation results on the testing parts are averaged.
+This technique is used to estimate how accurately the predictive model will perform in practise, limiting, at the same time, the overfitting problem.
+
+In addition, due to the stochastic component present in some of the methods and also in order to evaluate the running time, 30 repetitions of each experiment have been done per method.
+Then the average and standard deviation have been computed.
+
+***TODO***: talking about the machines used
+
+%Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
+%(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.
+
+%--------------------------------------------------------------------------
+
+\subsection{Results for all the editors}
+\label{subsec:results_all_editors}
+
+In the first experiment, forecasting methods have been applied to the whole dataset.
+All the pre-sales features have been considered.
+Obtained results are presented in Table \ref{tab:all_editors_no_fs}.
+
+\begin{table}
+\caption{Predicting Total sales for all editors (all the features). 30 repetitions, 10-fold cross validation.
+\label{tab:all_editors_no_fs}}
 \centering{}%
-\begin{tabular}{|c|c|c|c|}
-\hline 
-Category & Range of total sales & Count & Ratio\tabularnewline
-\hline 
-\hline 
-Very Low & 1-100 & 2233 & 36.71\%\tabularnewline
-\hline 
-Low & 100-500 & 2323 & 38.19\%\tabularnewline
-\hline 
-Medium & 500-2000 & 1239 & 20.37\%\tabularnewline
-\hline 
-High & 2000-5000 & 224 & 3.68\%\tabularnewline
-\hline 
-Very High & $>$5000 & 64 & 1.05\%\tabularnewline
-\hline 
-\end{tabular}
-\label{table:freq}
-\end{table*}
-
-\begin{figure*}[ht]
-\begin{center}
-\includegraphics[scale=0.60]{freq_sales.eps}
-\end{center}
-\caption{Number of books in each category.}
-%This should go also to exploratory data analysis, that is, problem
-%description - JJ
-\label{fig:count}
-\end{figure*}
-
-Second, two categorical features (i.e; Editorial and Collection) are
-removed from the analysis since they have large number of unique
-different values and therefore they are less informative. Moreover,
+\begin{tabular}{|c|l|l|l|l|l|l|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+K-NN & 0.787 $\pm$ 0.08 & 272.294 $\pm$ 32.38 & 840.594 $\pm$ 240.11 & 47.475 $\pm$ 3.39 & 63.072 $\pm$ 10.29 & 0.001 $\pm$ 0.01\tabularnewline
+\hline
+M5P & 0.890 $\pm$ 0.09 & 214.365 $\pm$ 22.96 & 634.229 $\pm$ 307.76 & 37.457 $\pm$ 3.12 & 48.324 $\pm$ 25.16 & 18.845 $\pm$ 0.61\tabularnewline
+\hline 
+Random Forest & 0.840 $\pm$ 0.05 & 253.365 $\pm$ 29.43 & 788.937 $\pm$ 282.01 & 44.164 $\pm$ 2.76 & 57.766 $\pm$ 8.15 & 4.906 $\pm$ 0.12\tabularnewline
+\hline 
+Linear Regression & 0.872 $\pm$ 0.07 & 308.679 $\pm$ 25.44 & 680.905 $\pm$ 226.41 & 54.053 $\pm$ 4.38 & 52.130 $\pm$ 18.29 & 984.687 $\pm$ 128.21\tabularnewline
+\hline 
+SVM & 0.876 $\pm$ 0.04 & 248.763 $\pm$ 27.49 & 732.641 $\pm$ 260.56 & 43.371 $\pm$ 2.35 & 53.471 $\pm$ 6.29 & 6169.239 $\pm$ 281.49\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+***TODO***: the results show...
+
+%--------------------------------------------------------------------------
+
+\subsection{Feature selection}
+\label{subsec:feature_selection}
+
+In this second experiment, different feature selection processes have been applied.
+
+***TODO***: The aim of these techniques is to reduce the number of features to consider...
+% Antonio - TODO: explain the aim of FS in these experiments.
+
+We have used both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.
+
+Then, the dataset has been projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
+An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features Editorial and Collection have been
+removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
+However, since they have a large number of unique different values this would be finally impracticable and useless.
+
+Moreover,
 four features (i.e; Subject1, Subject2, Subject3 and Book-binding)
@@
 
-Finally, the resulted dataset consisted of ten features including the
-new Total Sales categorical feature. The SOM algorithm is trained
-based on the nine numerical variables while the new total-sales
-variable is used to label this data. The SOM algorithm is applied with
-a large map size of $26 \times 16$  in order to represent the
-data. The best SOM training results are obtained with a final
-quantisation error of 0.691 and topographic error of 0.046.
+***TODO***: describe the parameters of SOM (size, neighbourhood shape, etc) and obtained quantisation and topographical errors.
+
+% The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data.
+The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.
 
@@
 
-In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales
-categories. It can be clearly seen that the SOM algorithm has
-successfully clustered the labels of the Total Sales into clear
-identified regions. %So what? - JJ
- In the top of the U-matrix the VL category is
-located. The L category appears in the middle of the matrix. Most of
-the M category appears in bottom-right corner while the H and VH
-categories are concentrated in the bottom-left corner.
-% OK, this means that these features are more or less clearly
-% separable. But the problem is that the UMatrix shows only 2, maybe 3
-% clusters: vh and H. That's it. If you know UMatrix, that's what you
-% see - JJ
-By inspecting \texttt{num\_reprints}, \texttt{gifts},
-\texttt{distrib\_novelty}, \texttt{tot\_points\_sale},
-\texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run}
-components, it can be noticed that they have the highest similarity to
-the clusters shown in the U-matrix. Based on this analysis, those
-features will be selected for the next stage.
-%  This is not a result, it is data preprocessing. You should have
-%  included it in the 4th section. All results do not need to go into
-%  the "REsults" section, only the final results. 
-% Besides, are you using this or feature selection for selecting
-% features?
+***TODO***: Justify the selected features by SOM (why have we chosen them?).
 
@@
 \begin{center}
-\includegraphics[scale=0.4]{SOM_figure.eps}
+\includegraphics[scale=0.4]{som_planes.eps}
 \end{center}
@@
 
-\begin{figure*}[http] 
-\begin{center} 
-\begin{tabular}{cc}
-\includegraphics[scale=0.55]{Umatrix.eps}  &
-\includegraphics[scale=0.55]{Labels.eps}  \\
-U-matrix & Labels 
-\end{tabular}
-\end{center} 
-\caption{Labeling the U-matrix using the total-sales variable.}
-\label{fig:Umatrix} 
-\end{figure*}
-
-%*************************************** SOM ANALISYS
+%\begin{figure*}[http] 
+%\begin{center} 
+%\begin{tabular}{cc}
+%\includegraphics[scale=0.55]{Umatrix.eps}  &
+%\includegraphics[scale=0.55]{Labels.eps}  \\
+%U-matrix & Labels 
+%\end{tabular}
+%\end{center} 
+%\caption{Labeling the U-matrix using the total-sales variable.}
+%\label{fig:Umatrix} 
+%\end{figure*}
+
+The selected features per method are shown in Table \ref{tab:features_selected}.
 
 \begin{table}
-\begin{tabular}[htb]{|c|c|c|c|c|}
-\hline
-Variable  & Pre-Sales & ReliefFAttributeEval  & SOM & CfsSubsetEval \\ \hline \hline
-subject1    & $\checkmark$  &   &   &   \\ \hline
-subject2    & $\checkmark$  &   &   &   \\ \hline
-subject3    & $\checkmark$  &   &   &   \\ \hline
-editorial   & $\checkmark$  &   &   &   \\ \hline
-collection  & $\checkmark$  &   &   &   \\ \hline
-binding   & $\checkmark$  &   &   &   \\ \hline
-ret\_price    & $\checkmark$  &   &   &   \\ \hline
-reprints    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
-num\_reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
-gifts   & $\checkmark$  &   & $\checkmark$  &   \\ \hline
-distrib\_novelty   & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
-tot\_points\_sale   & $\checkmark$  & $\checkmark$  & $\checkmark$   & $\checkmark$  \\ \hline
-tot\_points\_sale\_1st\_year    & $\checkmark$  & $\checkmark$  &  $\checkmark$ &   \\ \hline
-weeks\_sale    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
-print\_run   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
-total\_sales   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
-
-\end{tabular}
-\caption{Variables used in each method.} %PABLO: Poned este caption bien
-\label{tab:varmethods}
+\caption{Features selected by each method 
+\label{tab:features_selected}}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|}
+\hline 
+No. & Feature & ReliefFAttributeEva & CfsSubsetEval & SOM\tabularnewline
+\hline 
+1 & ret\_price & $\checkmark$ &  & $\checkmark$\tabularnewline
+\hline 
+2 & subject1 & $\checkmark$ & $\checkmark$ & $\checkmark$\tabularnewline
+\hline 
+3 &  Editorial+Collection &  &  & \tabularnewline
+\hline 
+4 & binding &  &  & \tabularnewline
+\hline 
+5 & gifts & $\checkmark$ &  & $\checkmark$\tabularnewline
+\hline 
+6 & distrib\_novelty & $\checkmark$ &  & \tabularnewline
+\hline 
+7 & tot\_points\_sale & $\checkmark$ &  & $\checkmark$\tabularnewline
+\hline 
+8 & tot\_points\_sale\_1st\_year & $\checkmark$ &  & \tabularnewline
+\hline 
+9 & weeks\_sale & $\checkmark$ &  & $\checkmark$\tabularnewline
+\hline 
+10 & print\_run & $\checkmark$ & $\checkmark$ & $\checkmark$\tabularnewline
+\hline 
+\end{tabular}
 \end{table}
 
-Table \ref{tab:varmethods} shows the used variables used in each step. %Pablo: poner también esta frase mejor 
-Once the different reduced datasets have been obtained, proposed methods 
-(M5P, LR, SVM, kNN, MLP) have been selected for this study from 
-the Weka implementation, and they were run 30 times with the Weka default parameter 
-settings and a different random initialisation seed for each run and each dataset.
-
-Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
-(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.
+% Antonio - TODO: change the names (and font format) to the same as variables in previous tables
+
+*************** TO CHANGE WITH THE NEW RESULTS **************
+
+\subsection{Obtained results}
 

### 2016-03-30 paper.tex
New results and changes in experiments
Several things to be done in 'TO DOs' along the text

@@
 \begin{abstract}
+***TO DO***: rewrite this considering the new contents and results\\
+
 When a new book is launched the publisher faces the problem of
@@
 
+***TO DO***: complete this considering the new contents and results\\
+
 Publishing a book, as releasing any other cultural product with a
@@
 % resultado. Esto es lo único importante - JJ
+
+***TO DO***: rewrite this considering the new structure of the paper\\
 
@@
 \caption{Considered pre-sales features and their types. It also shows
-  the names of the variables used in the applied methods.} 
+  the names of the variables used in the applied methods and if everyone is an input (independent) or an output (dependent) variable.} 
 \label{tabla:params_pre_sales}
@@
 \hline 
-No. & Feature Name & Variable & Type & Input/Output\\
+No. & Feature Name & Variable & Type & In/Out\\
 \hline 
@@
 In the first experiment, forecasting methods have been applied to the whole dataset.
-All the pre-sales features have been considered.
-Obtained results are presented in Table \ref{tab:all_editors_no_fs}.
+All the pre-sales features have been considered, also including the categorical ones, which make harder to process the instances and build the different models.
+SVM for instance, must previously transform these categories into numbers in order to deal with the data, which means the creation of a different (and new) variable per possible value.
+Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
+% Antonio - Sam, verify this, please
+
+Correlation coefficient, error measures and time to build the model have been computed for every method. Obtained results are presented in Table \ref{tab:all_editors_no_fs}.
 
@@
 \centering{}%
+%{\scriptsize
 \begin{tabular}{|c|l|l|l|l|l|l|}
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-K-NN & 0.787 $\pm$ 0.08 & 272.294 $\pm$ 32.38 & 840.594 $\pm$ 240.11 & 47.475 $\pm$ 3.39 & 63.072 $\pm$ 10.29 & 0.001 $\pm$ 0.01\tabularnewline
-\hline
-M5P & 0.890 $\pm$ 0.09 & 214.365 $\pm$ 22.96 & 634.229 $\pm$ 307.76 & 37.457 $\pm$ 3.12 & 48.324 $\pm$ 25.16 & 18.845 $\pm$ 0.61\tabularnewline
-\hline 
-Random Forest & 0.840 $\pm$ 0.05 & 253.365 $\pm$ 29.43 & 788.937 $\pm$ 282.01 & 44.164 $\pm$ 2.76 & 57.766 $\pm$ 8.15 & 4.906 $\pm$ 0.12\tabularnewline
-\hline 
-Linear Regression & 0.872 $\pm$ 0.07 & 308.679 $\pm$ 25.44 & 680.905 $\pm$ 226.41 & 54.053 $\pm$ 4.38 & 52.130 $\pm$ 18.29 & 984.687 $\pm$ 128.21\tabularnewline
-\hline 
-SVM & 0.876 $\pm$ 0.04 & 248.763 $\pm$ 27.49 & 732.641 $\pm$ 260.56 & 43.371 $\pm$ 2.35 & 53.471 $\pm$ 6.29 & 6169.239 $\pm$ 281.49\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-***TODO***: the results show...
+ & Corr. coeffic  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P & 0.890 $\pm$ 0.09 & 214.365 $\pm$ 22.96 & 634.229 $\pm$ 307.76 & 37.457 $\pm$ 3.12 & 48.324 $\pm$ 25.16 & 18.845 $\pm$ 0.61\\
+\hline
+K-NN & 0.787 $\pm$ 0.08 & 272.294 $\pm$ 32.38 & 840.594 $\pm$ 240.11 & 47.475 $\pm$ 3.39 & 63.072 $\pm$ 10.29 & 0.001 $\pm$ 0.01\\
+\hline 
+Random Forest & 0.840 $\pm$ 0.05 & 253.365 $\pm$ 29.43 & 788.937 $\pm$ 282.01 & 44.164 $\pm$ 2.76 & 57.766 $\pm$ 8.15 & 4.906 $\pm$ 0.12\\
+\hline 
+Linear Regression & 0.872 $\pm$ 0.07 & 308.679 $\pm$ 25.44 & 680.905 $\pm$ 226.41 & 54.053 $\pm$ 4.38 & 52.130 $\pm$ 18.29 & 984.687 $\pm$ 128.21\\
+\hline 
+SVM & 0.876 $\pm$ 0.04 & 248.763 $\pm$ 27.49 & 732.641 $\pm$ 260.56 & 43.371 $\pm$ 2.35 & 53.471 $\pm$ 6.29 & 6169.239 $\pm$ 281.49\\
+\hline 
+\end{tabular}
+%}
+\end{table}
+
+***TODO***: Revise and fix the following text...
+
+As far as the different methods is concerned, M5P model obtained good results, 
+both in time and error, and as stated before, this method can learn and tackle 
+tasks with high dimensionality and it generates reproducible and comprehensible 
+representations that provide information on the decision process and does not 
+require human intervention either for the operation or for interpretation. 
+Thus, it is very suitable in order to be incorporated in a publishing company 
+processes.
+
+The Linear Regression model outperforms some other complex methods, both in time 
+(as it is a simple method to train) and in obtained errors.
+However not in all cases, as more powerful models that obtain better results 
+can be obtained in comparable time.
+
+Taking into account the SVM model obtained results, this method obtains comparable 
+errors to those of M5P. Even when used using the default parameter values it exhibit 
+a good generalisation performance.
+However, it is much slower than the others to build the model, not only when 
+using the dataset with categorical input variables, but also when using the 
+datasets with numerical variables.
+
+kNN is the faster method used in this study, as it is the simpler method.
+However, the model is slow when classifying (as there are a large number of 
+training examples), and it exhibit a poor generalisation ability, as it does not 
+learn anything from the training data.
+
+Moreover, in these experiments it has been seen the difficulty to process 
+information related to categorical variables, such as \emph{editorial} and 
+\emph{collection}.
+
+%[Pedro] ¿aplicamos tests estadísticos para ver si hay diferencias entre métodos?
+
+Finally, paying attention to the cost in time to obtain the forecasting models 
+and their accuracy, the M5P model is the most adequate to solve the problem of 
+how many books should be printed when a new book is published.
+This forecasting method, as an additional advantage, can be used for products 
+with historical sales data and for new products with little or no historical 
+data available.
 
@@
 
-The selected features per method are shown in Table \ref{tab:features_selected}.
+The selected features per method are shown in Table \ref{tab:features_selected}. Logically, just the independent or input variables are considered.
 
 \begin{table}
-\caption{Features selected by each method 
+\caption{Input features/variables selected by each method
 \label{tab:features_selected}}
@@
 \hline 
-No. & Feature & ReliefFAttributeEva & CfsSubsetEval & SOM\tabularnewline
-\hline 
-1 & ret\_price & $\checkmark$ &  & $\checkmark$\tabularnewline
-\hline 
-2 & subject1 & $\checkmark$ & $\checkmark$ & $\checkmark$\tabularnewline
-\hline 
-3 &  Editorial+Collection &  &  & \tabularnewline
-\hline 
-4 & binding &  &  & \tabularnewline
-\hline 
-5 & gifts & $\checkmark$ &  & $\checkmark$\tabularnewline
-\hline 
-6 & distrib\_novelty & $\checkmark$ &  & \tabularnewline
-\hline 
-7 & tot\_points\_sale & $\checkmark$ &  & $\checkmark$\tabularnewline
-\hline 
-8 & tot\_points\_sale\_1st\_year & $\checkmark$ &  & \tabularnewline
-\hline 
-9 & weeks\_sale & $\checkmark$ &  & $\checkmark$\tabularnewline
-\hline 
-10 & print\_run & $\checkmark$ & $\checkmark$ & $\checkmark$\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-% Antonio - TODO: change the names (and font format) to the same as variables in previous tables
-
-*************** TO CHANGE WITH THE NEW RESULTS **************
-
-\subsection{Obtained results}
-
-% datasets:
-%  original (16 vars)
-%  4 vars
-%  9 vars
-%  SOM selected vars
-
-Table \ref{tabla:resultsT} shows obtained results (time to build the model and 
-error) after applying the proposed forecasting methods on the original dataset,
-using the 16 variables that describe each book.
-In this dataset, every book is described using not only numerical variables, 
-but also two additional categorical variables, \emph{editorial} and \emph{collection}, 
-which could, a priori, make harder to process the instances and build the different models.
-
-% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
-  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
-  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
-  % en algunos calculan muchos más, pero estos son los más usados. 
-% OK
-\begin{table*}[ht]
-\caption{Results (errors and time) obtained using the different forecasting
-methods on the original dataset (16 variables per book). In this case,
-due to the categorical variables, the MLP could not be run.}
-\label{tabla:resultsT}
+No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
+\hline 
+1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+2 & \texttt{subject1} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
+\hline 
+3 &  \texttt{collection} &  &  & \\
+\hline 
+4 & \texttt{binding} &  &  & \\
+\hline 
+5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
+\hline 
+7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
+\hline 
+9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+10 & \texttt{print\_run} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
+\hline 
+\end{tabular}
+\end{table}
+
+Thus, we have run the same experiments as in Section \ref{subsec:results_all_editors} with the whole dataset (all the editors), but considering the selected features by each method.
+The results are shown in Table
+
+\begin{table}
+
 \centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-Base & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
-\hline 
-\hline 
-M5P & 0.9076 & \textbf{202.1547} & 591.0257 & \textbf{35.31}\% & 42.10\% & 39.73\tabularnewline
-\hline 
-LR & 0.9204 & 255.0526 & 548.0975 & 44.5527 & 39.10\% & 0.03\tabularnewline
-\hline 
-SVM & \textbf{0.9402} & 203.4416 & \textbf{481.7528} & 35.54\% & \textbf{34.37}\% & 308.31\tabularnewline
-\hline 
-kNN & 0.7273 & 310.4078 & 993.2663 & 54.22\% & 70.85\% & 0\tabularnewline
-\hline 
-MLP & 0.9197 & 289.7393 & 585.6445 & 50.61\% & 41.78\% & 82.08\tabularnewline
-\hline 
-\end{tabular}
-\end{table*}
-
-Obtained results (time to build the model and error) using the different 
-forecasting methods on the dataset with 7 variables per book (obtained 
-using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
-\begin{table*}[ht]
-\caption{Results (errors and time) obtained using the different forecasting methods
-on the dataset obtained using the SOM feature selection method (6 variables
-per book).}
-\label{tabla:resultsSOM}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-Base  & Correlation coefficient (\%)  & MAE  & RMSE  & RAE(\%)  & RRSE (\%)  & Time(sec)\tabularnewline
-\hline 
-\hline 
-M5P  & 0.9161 & \textbf{198.8864} & 562.2113 & \textbf{34.74}\% & 40.11\% & 0.76\tabularnewline
-\hline 
-LR  & 0.9179 & 263.1702 & 556.3372 & 45.97\% & 39.69\% & 0.07\tabularnewline
-\hline 
-SVM  & \textbf{0.9388} & 207.7159 & \textbf{486.8913} & 36.28\% & \textbf{34.73}\% & 157.87\tabularnewline
-\hline 
-kNN  & 0.9304 & 202.0939 & 525.4642 & 35.30\% & 37.48\% & 0\tabularnewline
-\hline 
-MLP  & 0.9193 & 305.78 & 590.8412 & 53.41\% & 42.15\% & 25.83\tabularnewline
-\hline 
-\end{tabular}
-\end{table*}
-
-Obtained results (time to build the model and error) using the different 
-forecasting methods on the dataset with 8 variables per book (obtained 
-using the ReliefFAttributeEval feature selection method) can be shown 
-in Table \ref{tabla:results9}.
-In this dataset, every book is described using numerical variables, and thus, 
-processing the data to build the different models is a fast task.
-
-\begin{table*}[ht]
-\caption{Results (errors and time) obtained using the different forecasting methods
-on the dataset obtained using the ReliefFAttributeEval feature selection method (8
-variables per book).}
-\label{tabla:results9}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-RAE & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
-\hline 
-\hline 
-M5P & 0.9131 & \textbf{197.2886} & 580.328 & \textbf{34.46}\% & 41.40\% & 0.74\tabularnewline
-\hline 
-LR & 0.9209 & 254.3979 & 546.3899 & 44.44\% & 38.98\% & 0.03\tabularnewline
-\hline 
-SVM & \textbf{0.9394} & 204.2075 & \textbf{484.2617} & 35.67\% & \textbf{34.54}\% & 232.99\tabularnewline
-\hline 
-kNN & 0.9103 & 222.0827 & 597.8885 & 38.79\% & 42.65\% & 0\tabularnewline
-\hline 
-MLP & 0.9199 & 296.3581 & 575.9623 & 51.77\% & 41.09\% & 32.52\tabularnewline
-\hline 
-\end{tabular}
-\end{table*}
-
-Finally, obtained results (time to build the model and error) using the different 
-forecasting methods on the dataset with 4 variables per book (obtained 
-using the CfsSubsetEval feature selection method) can be shown 
-in Table \ref{tabla:results4}.
-As in the previous case, in this dataset every book is described using numerical 
-variables. Thus, due to the number of features per book, building the different 
-models is faster than in the previous cases.
-
-\begin{table*}[ht]
-\caption{Results (errors and time) obtained using the different forecasting methods
-on the dataset obtained using the CfsSubsetEval feature selection method (4 variables
-per book).}
-\label{tabla:results4}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-CFS & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
-\hline 
-\hline 
-M5P & 0.9255 & \textbf{206.6638} & 531.306 & \textbf{36.10}\% & 37.90\% & 0.56\tabularnewline
-\hline 
-LR & 0.9194 & 259.3791 & 551.2005 & 45.31\% & 39.32\% & 0.05\tabularnewline
-\hline 
-SVM & \textbf{0.9342} & 213.0254 &\textbf{ 502.4048} & 37.21\% & \textbf{35.84}\% & 70.12\tabularnewline
-\hline 
-kNN & 0.9285 & 220.6548 & 527.7374 & 38.54\% & 37.65\% & 0\tabularnewline
-\hline 
-MLP & 0.9047 & 369.3486 & 646.1241 & 64.52\% & 46.09\% & 10.93\tabularnewline
-\hline 
-\end{tabular}
-\end{table*}
-
-In Figures \ref{conv2}, \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} we depict scatter plots for the values of the actual total sales values against the predicted ones obtained by the developed models.
-Those figures also show the correlation between the two variables and the proportion of variation in actual total sales that is explained by the predicted ones. 
-Figure \ref{conv2} corresponds to the results obtained using all available features without performing any feature selection method.
+\caption{Predicting Total sales for all editors based on features selected
+by each method.
+\label{tab:results_all_editors_fs}}
+
+% RELIEFATTRIBUTEEVAL
+\begin{tabular}{|c|l|l|l|l|l|l|}
+\hline 
+\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P & 0.892 $\pm$0.102 & 211.147 $\pm$22.41 & 616.347 $\pm$321.254 & 36.928 $\pm$3.414 & 47.299 $\pm$26.827 & 0.4906 $\pm$0.0223\\
+\hline 
+K-NN & 0.869 $\pm$0.087 & 231.782 $\pm$24.246 & 668.028 $\pm$205.135 & 40.483 $\pm$3.058 & 51.276 $\pm$16.807 & 0.0015 $\pm$0.0042\\
+\hline 
+Random Forest & 0.91 $\pm$0.048 & 198.16 $\pm$19.499 & 589.353 $\pm$195.801 & 34.61 $\pm$2.27 & 44.209 $\pm$11.634 & 3.633 $\pm$0.2039\\
+\hline 
+Linear Regression & 0.864 $\pm$0.081 & 346.875 $\pm$25.395 & 695.897 $\pm$242.49 & 60.754 $\pm$4.549 & 53.164 $\pm$19.432 & 0.0124 $\pm$0.0072\\
+\hline 
+SVM & 0.842 $\pm$0.039 & 252.868 $\pm$33.384 & 858.26 $\pm$318.225 & 44.012 $\pm$3.038 & 62.22 $\pm$7.148 & 38.9667 $\pm$5.7518\\
+\hline 
+\end{tabular}
+
+% CFSSUBEVAL
+\begin{tabular}{|c|l|l|l|l|l|l|}
+\hline 
+\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
+\hline
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P & 0.873 $\pm$0.09 & 266.777 $\pm$23.117 & 662.319 $\pm$245.272 & 46.66 $\pm$3.247 & 50.9 $\pm$20.35 & 0.4103 $\pm$0.0428\\
+\hline 
+K-NN & 0.84 $\pm$0.099 & 289.092 $\pm$22.834 & 743.917 $\pm$260.45 & 50.591 $\pm$3.496 & 57.301 $\pm$22.899 & 0.001 $\pm$0.0006\\
+\hline 
+Random Forest & 0.85 $\pm$0.106 & 278.417 $\pm$23.073 & 714.134 $\pm$278.654 & 48.713 $\pm$3.434 & 55.264 $\pm$24.412 & 2.479 $\pm$0.1264\\
+\hline 
+Linear Regression & 0.859 $\pm$0.062 & 356.35 $\pm$22.43 & 708.056 $\pm$195.145 & 62.423 $\pm$4.216 & 53.974 $\pm$14.053 & 0.0067 $\pm$0.0009\\
+\hline 
+SVM & 0.86 $\pm$0.063 & 288.474 $\pm$30.322 & 817.562 $\pm$253.237 & 50.302 $\pm$2.375 & 60.266 $\pm$5.675 & 32.7252 $\pm$5.7438\\
+\hline
+\end{tabular}\\
+
+% SOM
+\begin{tabular}{|c|l|l|l|l|l|l|}
+\hline 
+\multicolumn{7}{|c|}{\textit{SOM}}\\
+\hline
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P & 0.866 $\pm$0.104 & 234.091 $\pm$23.186 & 699.563 $\pm$317.196 & 40.924 $\pm$3.248 & 53.698 $\pm$26.867 & 0.4754 $\pm$0.1228\\
+\hline 
+K-NN & 0.868 $\pm$0.086 & 237.91 $\pm$25.344 & 665.639 $\pm$212.05 & 41.547 $\pm$3.141 & 50.96 $\pm$16.721 & 0.0009 $\pm$0.0035\\
+\hline 
+Random Forest & 0.898 $\pm$0.051 & 211.867 $\pm$20.072 & 617.776 $\pm$187.155 & 37.017 $\pm$2.461 & 46.581 $\pm$11.144 & 2.932 $\pm$0.1083\\
+\hline 
+Linear Regression & 0.855 $\pm$0.075 & 351.993 $\pm$23.72 & 714.756 $\pm$214.213 & 61.65 $\pm$4.278 & 54.665 $\pm$16.881 & 0.0113 $\pm$0.0074\\
+\hline 
+SVM & 0.845 $\pm$0.035 & 267.706 $\pm$33.819 & 888.331 $\pm$308.932 & 46.604 $\pm$2.865 & 64.62 $\pm$5.445 & 32.2689 $\pm$4.7404\\
+\hline 
+\end{tabular}
+
+\end{table}
+
+***TO DO***: comment the results
+
+***TO DO***: Think if including the graphs (scatter plots).
+
+%In Figures \ref{conv2}, \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} we depict scatter plots for the values of the actual total sales values against the predicted ones obtained by the developed models.
+%Those figures also show the correlation between the two variables and the proportion of variation in actual total sales that is explained by the predicted ones. 
+%Figure \ref{conv2} corresponds to the results obtained using all available features without performing any feature selection method.
 In this figure, it can be noticed that SVM achieved the best results by explaining 88.2\% of the actual values while $k$-NN showed very poor results with only 49.8\%.
-Figures \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} show same plots after performing ReliefAttributeEval, CfsSubsetEval and SOM feature selection methods, respectively.
-According to these figures, we can notice that there wasn't almost any significant degradation in the performance of the M5P, LR, SVM and MLP. 
-On the other side, the performance of $k$-NN was dramatically improved after the feature selection process by explaining 84.5\% of variation on average.
-
-\begin{figure*}[http] 
-\begin{center} 
-\begin{tabular}{ccc}
-\includegraphics[scale=0.22]{m5p.eps}  &
-\includegraphics[scale=0.22]{lr.eps}   &
-\includegraphics[scale=0.22]{svm.eps}  \\
-M5P & LR & SVM 
-\end{tabular}
-\begin{tabular}{cc}
-\includegraphics[scale=0.22]{knn.eps}  &
-\includegraphics[scale=0.22]{mlp.eps}  \\
-k-NN & MLP
-\end{tabular}
-\end{center} 
-\caption{Actual vs. predicted sales for M5P, LR, SVM, k-NN, MLP
-  models.}
+%Figures \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} show same plots after performing ReliefAttributeEval, CfsSubsetEval and SOM feature selection methods, respectively.
+%According to these figures, we can notice that there wasn't almost any significant degradation in the performance of the M5P, LR, SVM and MLP. 
+%On the other side, the performance of $k$-NN was dramatically improved after the feature selection process by explaining 84.5\% of variation on average.
+%
+%
+%\begin{figure*}[http] 
+%\begin{center} 
+%\begin{tabular}{ccc}
+%\includegraphics[scale=0.22]{m5p.eps}  &
+%\includegraphics[scale=0.22]{lr.eps}   &
+%\includegraphics[scale=0.22]{svm.eps}  \\
+%M5P & LR & SVM 
+%\end{tabular}
+%\begin{tabular}{cc}
+%\includegraphics[scale=0.22]{knn.eps}  &
+%\includegraphics[scale=0.22]{mlp.eps}  \\
+%k-NN & MLP
+%\end{tabular}
+%\end{center} 
+%\caption{Actual vs. predicted sales for M5P, LR, SVM, k-NN, MLP
+%  models.}
 % You should use a log-log scale here to see it more clearly. Besides,
@@
 % are going to need it later on - JJ
-\label{conv2}
-\end{figure*}
-
-\begin{figure*}[http] 
-\begin{center} 
-\begin{tabular}{ccc}
-\includegraphics[scale=0.22]{m5p_RAE.eps}  &
-\includegraphics[scale=0.22]{lr_RAE.eps}   &
-\includegraphics[scale=0.22]{svm_RAE.eps}  \\
-M5P & LR & SVM 
-\end{tabular}
-\begin{tabular}{cc}
-\includegraphics[scale=0.22]{knn_RAE.eps}  &
-\includegraphics[scale=0.22]{mlp_RAE.eps}  \\
-k-NN & MLP
-\end{tabular}
-\end{center} 
-\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
-\label{conv2ReliefAttributeEval}
-\end{figure*}
-
-\begin{figure*}[http] 
-\begin{center} 
-\begin{tabular}{ccc}
-\includegraphics[scale=0.22]{m5p_CFS.eps}  &
-\includegraphics[scale=0.22]{lr_CFS.eps}   &
-\includegraphics[scale=0.22]{svm_CFS.eps}  \\
-M5P & LR & SVM 
-\end{tabular}
-\begin{tabular}{cc}
-\includegraphics[scale=0.22]{knn_CFS.eps}  &
-\includegraphics[scale=0.22]{mlp_CFS.eps}  \\
-k-NN & MLP
-\end{tabular}
-\end{center} 
-\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
-\label{conv2CfsSubsetEval}
-\end{figure*}
-
-\begin{figure*}[http] 
-\begin{center} 
-\begin{tabular}{ccc}
-\includegraphics[scale=0.22]{m5p_SOM.eps}  &
-\includegraphics[scale=0.22]{lr_SOM.eps}   &
-\includegraphics[scale=0.22]{svm_SOM.eps}  \\
-M5P & LR & SVM 
-\end{tabular}
-\begin{tabular}{cc}
-\includegraphics[scale=0.22]{knn_SOM.eps}  &
-\includegraphics[scale=0.22]{mlp_SOM.eps}  \\
-k-NN & MLP
-\end{tabular}
-\end{center} 
-\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
-\label{conv2SOM}
-\end{figure*}
+%\label{conv2}
+%\end{figure*}
+%
+%
+%\begin{figure*}[http] 
+%\begin{center} 
+%\begin{tabular}{ccc}
+%\includegraphics[scale=0.22]{m5p_RAE.eps}  &
+%\includegraphics[scale=0.22]{lr_RAE.eps}   &
+%\includegraphics[scale=0.22]{svm_RAE.eps}  \\
+%M5P & LR & SVM 
+%\end{tabular}
+%\begin{tabular}{cc}
+%\includegraphics[scale=0.22]{knn_RAE.eps}  &
+%\includegraphics[scale=0.22]{mlp_RAE.eps}  \\
+%k-NN & MLP
+%\end{tabular}
+%\end{center} 
+%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
+%\label{conv2ReliefAttributeEval}
+%\end{figure*}
+%
+%
+%\begin{figure*}[http] 
+%\begin{center} 
+%\begin{tabular}{ccc}
+%\includegraphics[scale=0.22]{m5p_CFS.eps}  &
+%\includegraphics[scale=0.22]{lr_CFS.eps}   &
+%\includegraphics[scale=0.22]{svm_CFS.eps}  \\
+%M5P & LR & SVM 
+%\end{tabular}
+%\begin{tabular}{cc}
+%\includegraphics[scale=0.22]{knn_CFS.eps}  &
+%\includegraphics[scale=0.22]{mlp_CFS.eps}  \\
+%k-NN & MLP
+%\end{tabular}
+%\end{center} 
+%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
+%\label{conv2CfsSubsetEval}
+%\end{figure*}
+%
+%
+%\begin{figure*}[http] 
+%\begin{center} 
+%\begin{tabular}{ccc}
+%\includegraphics[scale=0.22]{m5p_SOM.eps}  &
+%\includegraphics[scale=0.22]{lr_SOM.eps}   &
+%\includegraphics[scale=0.22]{svm_SOM.eps}  \\
+%M5P & LR & SVM 
+%\end{tabular}
+%\begin{tabular}{cc}
+%\includegraphics[scale=0.22]{knn_SOM.eps}  &
+%\includegraphics[scale=0.22]{mlp_SOM.eps}  \\
+%k-NN & MLP
+%\end{tabular}
+%\end{center} 
+%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
+%\label{conv2SOM}
+%\end{figure*}
 
@@
 % - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
-Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
-\ref{tabla:resultsSOM}, \ref{tabla:results9} and \ref{tabla:results4},
-using those categorical variables as part of a big dataset makes the problem 
-hard to solve, both in required time to build the forecasting models as well as 
-in the obtained errors.
-Moreover, some methods are unable to build the models in a reasonable time.
+%Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
+%\ref{tabla:resultsSOM}, \ref{tabla:results9} and \ref{tabla:results4},
+%using those categorical variables as part of a big dataset makes the problem 
+%hard to solve, both in required time to build the forecasting models as well as 
+%in the obtained errors.
+
+%Moreover, some methods are unable to build the models in a reasonable time.
 %However, as stated before, Trevenque expert sales manager, taking into account 
@@
 
-As far as the different methods is concerned, M5P model obtained good results, 
-both in time and error, and as stated before, this method can learn and tackle 
-tasks with high dimensionality and it generates reproducible and comprehensible 
-representations that provide information on the decision process and does not 
-require human intervention either for the operation or for interpretation. 
-Thus, it is very suitable in order to be incorporated in a publishing company 
-processes.
-
-The Linear Regression model outperforms some other complex methods, both in time 
-(as it is a simple method to train) and in obtained errors.
-However not in all cases, as more powerful models that obtain better results 
-can be obtained in comparable time.
-
-Taking into account the SVM model obtained results, this method obtains comparable 
-errors to those of M5P. Even when used using the default parameter values it exhibit 
-a good generalisation performance.
-However, it is much slower than the others to build the model, not only when 
-using the dataset with categorical input variables, but also when using the 
-datasets with numerical variables.
-
-kNN is the faster method used in this study, as it is the simpler method.
-However, the model is slow when classifying (as there are a large number of 
-training examples), and it exhibit a poor generalisation ability, as it does not 
-learn anything from the training data.
-
-As far as the Multilayer Perceptron, its main drawbacks are both the cost of model 
-building (not only parameter and weights setting, but also time to train the 
-network) and the fact that it is a back-box model, and thus, it is difficult 
-to explain how the forecasts are obtained.
-Moreover, in these experiments it has been seen the difficulty to process 
-information related to categorical variables, such as \emph{editorial} and 
-\emph{collection}.
-
-%[Pedro] ¿aplicamos tests estadísticos para ver si hay diferencias entre métodos?
-
-Finally, paying attention to the cost in time to obtain the forecasting models 
-and their accuracy, the M5P model is the most adequate to solve the problem of 
-how many books should be printed when a new book is published.
-This forecasting method, as an additional advantage, can be used for products 
-with historical sales data and for new products with little or no historical 
-data available.
+%********************************************************************************
+
+\section{Example Cases}
+\label{example_cases}
+
+This section will present some experiments conducted on the data concerning four different example cases, namely:
+\begin{itemize}
+    \item best seller editorial
+    \item medium seller editorial
+    \item best varied editorial
+    \item medium varied editorial
+\end{itemize}
+
+***TO DO ***: better describe (number of instances) and justify the special cases (why we have chosen them).
+
+%--------------------------------------------------------------------------
+
+\subsection{Sales forecasting with all pre-sales features}
+\label{subsec:case_sales_all_features}
+
+Case 1-A: Developing prediction models to predict Total sales for
+Editor704 (An editor with the most number of different books sold) - 293
+instances.
+
+\begin{table}
+\caption{Predicting Total sales for Editor704}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.889 $\pm$0.074 & 71.258 $\pm$21.291 & 125.19 $\pm$50.085 & 39.251 $\pm$11.769 & 47.495 $\pm$15.933 & 0.046 $\pm$0.0278\tabularnewline
+\hline 
+K-NN & 0.826 $\pm$0.1 & 87.602 $\pm$23.206 & 158.629 $\pm$54.164 & 47.621 $\pm$10.32 & 59.168 $\pm$14.428 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+Random Forest & 0.871 $\pm$0.082 & 74.634 $\pm$22.166 & 139.743 $\pm$54.357 & 40.618 $\pm$10.214 & 52.219 $\pm$16.267 & 0.1069 $\pm$0.0053\tabularnewline
+\hline 
+Linear Regression & 0.838 $\pm$0.089 & 97.513 $\pm$18.874 & 155.273 $\pm$45.562 & 54.172 $\pm$13.598 & 60.314 $\pm$21.168 & 0.0069 $\pm$0.0012\tabularnewline
+\hline 
+SVM & 0.874 $\pm$0.066 & 78.743 $\pm$22.254 & 147.295 $\pm$57.99 & 42.428 $\pm$7.826 & 53.286 $\pm$9.351 & 0.0598 $\pm$0.0157\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editor-UDLU11 (An editor with a medium number of different books sold) - 180
+instances.
+
+\begin{table}
+\caption{Predicting Total sales for Editor-UDLU11}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.775 $\pm$0.15 & 573.405 $\pm$192.219 & 860.313 $\pm$456.217 & 58.26 $\pm$15.867 & 65.997 $\pm$29.447 & 0.0238 $\pm$0.0018\tabularnewline
+\hline 
+K-NN & 0.732 $\pm$0.163 & 596.615 $\pm$205.368 & 933.058 $\pm$356.108 & 60.619 $\pm$17.854 & 71.363 $\pm$22.336 & 0 $\pm$0.0002\tabularnewline
+\hline 
+Random Forest & 0.867 $\pm$0.073 & 449.161 $\pm$127.796 & 671.758 $\pm$212.739 & 45.575 $\pm$9.8 & 51.372 $\pm$11.159 & 0.0606 $\pm$0.005\tabularnewline
+\hline 
+Linear Regression & 0.733 $\pm$0.195 & 680.157 $\pm$263.788 & 1103.971 $\pm$850.685 & 69.775 $\pm$27.238 & 86.106 $\pm$71.316 & 0.0024 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.804 $\pm$0.122 & 529.349 $\pm$172.496 & 846.013 $\pm$341.117 & 53.26 $\pm$11.915 & 63.539 $\pm$18.247 & 0.029 $\pm$0.0151\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editor-UDL929 (The best selling editor) - 216 instances.
+
+\begin{table}
+\caption{Predicting Total sales for Editor-UDL929 (460752 sales) }
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.9 $\pm$0.098 & 670.244 $\pm$181.047 & 1065.337 $\pm$413.835 & 40.833 $\pm$10.858 & 43.561 $\pm$19.866 & 0.0302 $\pm$0.0016\tabularnewline
+\hline 
+K-NN & 0.733 $\pm$0.192 & 1057.212 $\pm$385.036 & 1875.849 $\pm$916.958 & 61.879 $\pm$12.366 & 68.747 $\pm$15.978 & 0 $\pm$0.0001\tabularnewline
+\hline 
+Random Forest & 0.876 $\pm$0.108 & 771.825 $\pm$326.339 & 1490.492 $\pm$930.576 & 45.399 $\pm$14.137 & 55.912 $\pm$31.703 & 0.0777 $\pm$0.0041\tabularnewline
+\hline 
+Linear Regression & 0.863 $\pm$0.118 & 922.334 $\pm$289.01 & 1399.844 $\pm$619.623 & 56.107 $\pm$16.171 & 56.425 $\pm$25.091 & 0.0045 $\pm$0.0006\tabularnewline
+\hline 
+SVM & 0.867 $\pm$0.1 & 873.222 $\pm$345.164 & 1621.478 $\pm$985.241 & 50.847 $\pm$11.83 & 57.232 $\pm$20.404 & 0.0423 $\pm$0.016\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editor-UDLW12 (The median selling editor)- 97 instances.
+
+\begin{table}
+\caption{Predicting Total sales for Editor-UDLW12 (2635 sales) }
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.832 $\pm$0.24 & 14.179 $\pm$6.615 & 23.82 $\pm$11.86 & 43.405 $\pm$20.387 & 55.787 $\pm$30.474 & 0.0089 $\pm$0.0016\tabularnewline
+\hline 
+K-NN & 0.793 $\pm$0.236 & 15.34 $\pm$8.706 & 26.571 $\pm$16.635 & 46.2 $\pm$23.768 & 60.09 $\pm$35.205 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+Random Forest & 0.858 $\pm$0.172 & 14.185 $\pm$6.692 & 23.569 $\pm$11.831 & 42.534 $\pm$16.799 & 53.295 $\pm$23.408 & 0.0321 $\pm$0.0044\tabularnewline
+\hline 
+Linear Regression & 0.821 $\pm$0.252 & 14.62 $\pm$7.917 & 24.793 $\pm$15.076 & 44.573 $\pm$24.265 & 56.854 $\pm$35.071 & 0.0019 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.835 $\pm$0.21 & 14.01 $\pm$7.608 & 25.612 $\pm$15.297 & 40.663 $\pm$16.026 & 53.276 $\pm$18.45 & 0.0198 $\pm$0.0146\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+%--------------------------------------------------------------------------
+
+\subsection{Sales forecasting with feature selection}
+\label{subsec:case_sales_feature_selection}
+
+***TO DO***: choose the best Feature selection method and apply just this one (ReliefAttributeEval???). There are too many tables I think.
+We could add an appendix or so with the rest of results if you want.
+
+Case 1-A: Developing prediction models to predict Total sales for
+Editor704 with ReliefFAttributeEval feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor704 (ReliefFAttributeEval-FS) }
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.893 $\pm$0.075 & 69.699 $\pm$19.853 & 122.48 $\pm$47.284 & 38.486 $\pm$11.531 & 46.677 $\pm$16.018 & 0.0275 $\pm$0.003\tabularnewline
+\hline 
+K-NN & 0.856 $\pm$0.101 & 78.393 $\pm$24.118 & 147.075 $\pm$58.023 & 42.577 $\pm$10.988 & 54.416 $\pm$15.542 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+Random Forest & 0.877 $\pm$0.079 & 73.134 $\pm$22.949 & 137.604 $\pm$56.143 & 39.785 $\pm$10.689 & 51.348 $\pm$16.98 & 0.1282 $\pm$0.0137\tabularnewline
+\hline 
+Linear Regression & 0.873 $\pm$0.06 & 89.719 $\pm$18.306 & 140.653 $\pm$47.12 & 49.452 $\pm$10.495 & 53.196 $\pm$14.156 & 0.0008 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.877 $\pm$0.069 & 77.301 $\pm$22.249 & 146.462 $\pm$57.679 & 41.665 $\pm$7.994 & 53.098 $\pm$9.505 & 0.045 $\pm$0.0159\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-A: Developing prediction models to predict Total sales for
+Editor704 with CfsSubsetEval feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor704 (CfsSubsetEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.801 $\pm$0.092 & 104.874 $\pm$21.376 & 174.571 $\pm$47.332 & 58.111 $\pm$14.731 & 67.577 $\pm$22.612 & 0.0178 $\pm$0.0028\tabularnewline
+\hline 
+K-NN & 0.782 $\pm$0.116 & 99.45 $\pm$24.305 & 170.827 $\pm$46.342 & 54.529 $\pm$12.277 & 65.864 $\pm$18.338 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+Random Forest & 0.776 $\pm$0.128 & 101.933 $\pm$23.664 & 180.557 $\pm$51.203 & 56.098 $\pm$13.624 & 69.862 $\pm$23.274 & 0.0738 $\pm$0.003\tabularnewline
+\hline 
+Linear Regression & 0.801 $\pm$0.096 & 106.617 $\pm$21.523 & 173.179 $\pm$46.584 & 59.109 $\pm$14.958 & 67.527 $\pm$24.529 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.818 $\pm$0.075 & 94.285 $\pm$25.516 & 180.536 $\pm$62.67 & 50.792 $\pm$8.477 & 65.624 $\pm$6.245 & 0.0382 $\pm$0.0183\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-A: Developing prediction models to predict Total sales for
+Editor704 with SOM feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor704 (SOM-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.892 $\pm$0.066 & 71.536 $\pm$18.953 & 123.061 $\pm$42.132 & 39.426 $\pm$10.597 & 47.204 $\pm$15.159 & 0.0307 $\pm$0.0067\tabularnewline
+\hline 
+K-NN & 0.858 $\pm$0.093 & 79.422 $\pm$21.473 & 140.948 $\pm$44.928 & 43.342 $\pm$10.072 & 53.313 $\pm$14.374 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+Random Forest & 0.877 $\pm$0.08 & 73.981 $\pm$20.909 & 134.107 $\pm$51.698 & 40.475 $\pm$10.512 & 50.413 $\pm$16.378 & 0.1035 $\pm$0.0076\tabularnewline
+\hline 
+Linear Regression & 0.875 $\pm$0.062 & 88.697 $\pm$16.338 & 135.029 $\pm$35.176 & 49.076 $\pm$10.471 & 51.972 $\pm$13.648 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.878 $\pm$0.057 & 81.087 $\pm$22.477 & 154.823 $\pm$59.93 & 43.651 $\pm$7.364 & 55.716 $\pm$7.153 & 0.0309 $\pm$0.0033\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editor-UDLU11 with ReliefFAttributeEval feature selection
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDLU11 (ReliefFAttributeEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.766 $\pm$0.168 & 592.493 $\pm$209.249 & 894.757 $\pm$508.14 & 60.206 $\pm$18.221 & 69.138 $\pm$37.353 & 0.0166 $\pm$0.0011\tabularnewline
+\hline 
+K-NN & 0.827 $\pm$0.093 & 486.96 $\pm$140.273 & 741.808 $\pm$238.557 & 49.268 $\pm$10.504 & 56.62 $\pm$12.591 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+Random Forest & 0.853 $\pm$0.089 & 455.7 $\pm$123.958 & 686.536 $\pm$198.157 & 46.319 $\pm$10.195 & 53.029 $\pm$13.054 & 0.07 $\pm$0.0028\tabularnewline
+\hline 
+Linear Regression & 0.644 $\pm$0.202 & 817.214 $\pm$331.164 & 1324.047 $\pm$1090.851 & 83.217 $\pm$32.006 & 101.895 $\pm$87.829 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.714 $\pm$0.142 & 644.424 $\pm$203.425 & 1009.656 $\pm$371.828 & 64.474 $\pm$11.701 & 75.542 $\pm$15.994 & 0.0182 $\pm$0.0012\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editor-UDLU11 with CfsSubsetEval feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDLU11 (CfsSubsetEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.64 $\pm$0.232 & 777.935 $\pm$342.04 & 1305.28 $\pm$1075.291 & 78.373 $\pm$30.4 & 99.857 $\pm$85.431 & 0.0134 $\pm$0.0012\tabularnewline
+\hline 
+K-NN & 0.648 $\pm$0.181 & 702.701 $\pm$181.407 & 1008.391 $\pm$305.871 & 71.407 $\pm$13.951 & 78.469 $\pm$22.695 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+Random Forest & 0.653 $\pm$0.193 & 685.556 $\pm$195.277 & 1021.374 $\pm$352.882 & 69.74 $\pm$16.956 & 79.373 $\pm$26.977 & 0.0466 $\pm$0.0023\tabularnewline
+\hline 
+Linear Regression & 0.67 $\pm$0.234 & 857.222 $\pm$308.686 & 1352.26 $\pm$945.314 & 86.095 $\pm$24.253 & 102.893 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.648 $\pm$0.23 & 879.912 $\pm$280.326 & 1402.822 $\pm$593.437 & 87.739 $\pm$15.273 & 105.402 $\pm$37.729 & 0.0168 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editor-UDLU11 with SOM feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDLU11 (SOM-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.79 $\pm$0.138 & 573.246 $\pm$167.882 & 827.554 $\pm$388.162 & 58.421 $\pm$14.138 & 63.975 $\pm$25.632 & 0.0153 $\pm$0.0015\tabularnewline
+\hline 
+K-NN & 0.836 $\pm$0.098 & 492.179 $\pm$126.856 & 727.326 $\pm$209.877 & 50.117 $\pm$10.688 & 56.136 $\pm$12.894 & 0 $\pm$0.0002\tabularnewline
+\hline 
+Random Forest & 0.856 $\pm$0.084 & 446.245 $\pm$119.79 & 673.455 $\pm$189.06 & 45.384 $\pm$9.778 & 52.236 $\pm$13.088 & 0.0594 $\pm$0.0049\tabularnewline
+\hline 
+Linear Regression & 0.71 $\pm$0.188 & 723.735 $\pm$247.959 & 1108.74 $\pm$736.165 & 74.136 $\pm$24.906 & 85.956 $\pm$59.994 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.716 $\pm$0.147 & 640.136 $\pm$206.459 & 1017.018 $\pm$376.134 & 63.961 $\pm$11.873 & 76.103 $\pm$16.796 & 0.0189 $\pm$0.0014\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editor-UDL929 with ReliefFAttributeEval feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDL929 (ReliefFAttributeEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.905 $\pm$0.1 & 661.81 $\pm$186.171 & 1070.235 $\pm$425.658 & 40.176 $\pm$10.502 & 43.555 $\pm$19.769 & 0.0198 $\pm$0.0018\tabularnewline
+\hline 
+K-NN & 0.878 $\pm$0.114 & 751.542 $\pm$270.905 & 1257.821 $\pm$615.656 & 44.571 $\pm$10.886 & 48.616 $\pm$18.727 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+Random Forest & 0.883 $\pm$0.11 & 735.044 $\pm$326.9 & 1420.43 $\pm$941.619 & 43.561 $\pm$15.883 & 54.357 $\pm$35.307 & 0.095 $\pm$0.0086\tabularnewline
+\hline 
+Linear Regression & 0.884 $\pm$0.113 & 868.179 $\pm$208.648 & 1231.227 $\pm$454.862 & 53.383 $\pm$14.672 & 50.598 $\pm$22.037 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.876 $\pm$0.099 & 860.485 $\pm$334.669 & 1560.048 $\pm$962.637 & 49.978 $\pm$9.607 & 55.069 $\pm$17.762 & 0.0232 $\pm$0.0028\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editor-UDL929 with CfsSubsetEval feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDL929 (CfsSubsetEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.88 $\pm$0.126 & 738.28 $\pm$188.534 & 1141.786 $\pm$472.025 & 45.452 $\pm$13.622 & 47.58 $\pm$24.835 & 0.0169 $\pm$0.0016\tabularnewline
+\hline 
+K-NN & 0.853 $\pm$0.145 & 825.191 $\pm$235.337 & 1280.334 $\pm$523.058 & 50.228 $\pm$14.065 & 51.419 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+Random Forest & 0.864 $\pm$0.138 & 790.09 $\pm$225.858 & 1245.227 $\pm$584.231 & 48.216 $\pm$13.792 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
+\hline 
+Linear Regression & 0.866 $\pm$0.123 & 936.557 $\pm$204.458 & 1329.237 $\pm$480.786 & 58.037 $\pm$16.921 & 55.408 $\pm$25.623 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.868 $\pm$0.12 & 940.386 $\pm$344.161 & 1648.503 $\pm$1026.038 & 54.498 $\pm$7.122 & 56.166 $\pm$7.8 & 0.0201 $\pm$0.0021\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editor-UDL929 with SOM feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDL929 (SOM-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.897 $\pm$0.098 & 685.667 $\pm$185.988 & 1116.42 $\pm$478.062 & 42.092 $\pm$12.822 & 46.308 $\pm$24.612 & 0.02 $\pm$0.0035\tabularnewline
+\hline 
+K-NN & 0.89 $\pm$0.101 & 746.448 $\pm$250.762 & 1203.407 $\pm$564.836 & 44.361 $\pm$9.734 & 46.251 $\pm$14.413 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+Random Forest & 0.895 $\pm$0.094 & 708.244 $\pm$264.518 & 1270.262 $\pm$708.817 & 42.135 $\pm$12.446 & 49.066 $\pm$26.594 & 0.0801 $\pm$0.0058\tabularnewline
+\hline 
+Linear Regression & 0.866 $\pm$0.129 & 894.084 $\pm$206.603 & 1282.833 $\pm$451.866 & 55.287 $\pm$15.923 & 53.738 $\pm$24.698 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.871 $\pm$0.101 & 908.562 $\pm$348.195 & 1608.767 $\pm$972.552 & 52.632 $\pm$8.746 & 55.945 $\pm$12.493 & 0.0221 $\pm$0.0024\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editor-UDLW12 with ReliefFAttributeEval feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDLW12 (ReliefFAttributeEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.837 $\pm$0.241 & 13.853 $\pm$6.557 & 23.189 $\pm$11.795 & 42.353 $\pm$20.326 & 54.078 $\pm$30.055 & 0.0063 $\pm$0.0014\tabularnewline
+\hline 
+K-NN & 0.772 $\pm$0.296 & 14.178 $\pm$6.631 & 23.645 $\pm$11.029 & 43.367 $\pm$19.229 & 56.996 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
+\hline 
+Random Forest & 0.867 $\pm$0.161 & 13.628 $\pm$6.673 & 22.797 $\pm$11.806 & 41.066 $\pm$17.705 & 52.431 $\pm$26.232 & 0.0304 $\pm$0.0025\tabularnewline
+\hline 
+Linear Regression & 0.844 $\pm$0.246 & 12.789 $\pm$6.645 & 21.521 $\pm$12.543 & 39.467 $\pm$23.345 & 50.14 $\pm$35.261 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.852 $\pm$0.187 & 13.217 $\pm$7.386 & 24.407 $\pm$15.087 & 38.24 $\pm$15.41 & 50.463 $\pm$17.973 & 0.0139 $\pm$0.0016\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editor-UDLW12 with CfsSubsetEval feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDLW12 (CfsSubsetEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.816 $\pm$0.219 & 15.671 $\pm$6.584 & 25.632 $\pm$11.838 & 47.931 $\pm$18.812 & 60.719 $\pm$31.747 & 0.0059 $\pm$0.0015\tabularnewline
+\hline 
+K-NN & 0.752 $\pm$0.267 & 15.732 $\pm$7.726 & 26.68 $\pm$14.816 & 48.578 $\pm$24.769 & 66.231 $\pm$48.588 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+Random Forest & 0.751 $\pm$0.264 & 15.61 $\pm$7.191 & 26.831 $\pm$13.355 & 47.381 $\pm$20.099 & 64.652 $\pm$38.664 & 0.0224 $\pm$0.0027\tabularnewline
+\hline 
+Linear Regression & 0.816 $\pm$0.218 & 15.674 $\pm$6.546 & 25.492 $\pm$11.628 & 47.97 $\pm$18.85 & 60.276 $\pm$30.617 & 0.0002 $\pm$0.0004\tabularnewline
+\hline 
+SVM & 0.818 $\pm$0.211 & 17.711 $\pm$9.704 & 31.951 $\pm$19.261 & 50.073 $\pm$14.926 & 65.121 $\pm$16.362 & 0.0129 $\pm$0.0009\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editor-UDLW12 with SOM feature selection.
+
+\begin{table}[h!]
+\caption{Predicting Total sales for Editor-UDLW12 (SOM-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 0.86 $\pm$0.188 & 13.84 $\pm$6.753 & 23.94 $\pm$11.638 & 41.65 $\pm$17.557 & 55.439 $\pm$27.128 & 0.006 $\pm$0.0012\tabularnewline
+\hline 
+K-NN & 0.74 $\pm$0.293 & 15.926 $\pm$8.521 & 28.281 $\pm$16.283 & 48.827 $\pm$25.885 & 68.75 $\pm$48.849 & 0 $\pm$0.0002\tabularnewline
+\hline 
+Random Forest & 0.855 $\pm$0.187 & 13.661 $\pm$6.469 & 22.51 $\pm$11.026 & 41.378 $\pm$17.87 & 52.198 $\pm$27.088 & 0.0262 $\pm$0.0019\tabularnewline
+\hline 
+Linear Regression & 0.854 $\pm$0.214 & 14.586 $\pm$7.129 & 24.404 $\pm$12.87 & 44.813 $\pm$23.647 & 57.727 $\pm$38.631 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 0.844 $\pm$0.184 & 14.177 $\pm$7.959 & 26.487 $\pm$16.539 & 40.931 $\pm$16.652 & 54.366 $\pm$20.004 & 0.0133 $\pm$0.0013\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+%--------------------------------------------------------------------------
+
+\subsection{Decision trees for best seller}
+\label{subsec:decision_trees}
+
+In this section we show the output of one of the models built during the regression, namely we present one of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate an useful decision-aid tool for and expert (editor) to see what sales can be expected for the different values of the input variables (including the print-run).
+
+***TO DO:*** better explain this
+
+We have considered the best seller editorial as a good example case to show.
+
+Figure \ref{fig:decision_tree_best_seller} depicts the obtained decision tree for the best seller editorial (UDL929).
+The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales.
+This tree has been created considering the 10 pre-sales features.
+
+\begin{figure}[!ht] 
+\begin{center}
+  \epsfig{file=decision_tree_no_fs.eps,width=12cm}
+\caption{Decision Tree built by the M5P method for the best seller editorial with all the pre-sales features.}
+\label{fig:decision_tree_best_seller}
+\end{center}
+\end{figure}
+
+***TO DO***: comments on the figure\\
+
+Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same editorial (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results.
+
+***TO DO***: better justify this\\
+
+\begin{figure}[!ht] 
+\begin{center}
+  \epsfig{file=decision_tree_fs.eps,width=12cm}
+\caption{Decision Tree built by the M5P method for the best seller editorial with the features selected by the ReliefAttributeEval method.}
+\label{fig:decision_tree_best_seller_fs}
+\end{center}
+\end{figure}
+
+***TO DO***: comments on the figure\\
 
@@
 \label{sec:conclusionsAndFutureWork}
+
+***TO DO***: rewrite these conclusions with the new experiments, examples and results\\
 
@@
 
+***TO DO***: revise the projects\\
+
 This work has been supported in part by projects 

### 2016-03-31 paper.tex
Changes and comments

@@
 \begin{abstract}
-***TO DO***: rewrite this considering the new contents and results\\
+% ***TO DO***: rewrite this considering the new contents and results\\
 
@@
 
-***TO DO***: complete this considering the new contents and results\\
+%***TO DO***: complete this considering the new contents and results\\
 
@@
 
-***TO DO***: rewrite this considering the new structure of the paper\\
+% ***TO DO***: rewrite this considering the new structure of the paper\\
 
@@
 
-***TO DO***: comment the results
-
-***TO DO***: Think if including the graphs (scatter plots).
+% ***TO DO***: comment the results
+
+% ***TO DO***: Think about including the graphs (scatter plots).
 
@@
 
-***TO DO ***: better describe (number of instances) and justify the special cases (why we have chosen them).
+% ***TO DO ***: describe better  (number of instances) and justify the special cases (why we have chosen them).
 

### 2016-04-06 paper.tex
New version with fixed tables
Removed superfluous files
Description of special cases

--- 2016-03-30 paper.tex
@@
 \hline 
- & Corr. coeffic  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P & 0.890 $\pm$ 0.09 & 214.365 $\pm$ 22.96 & 634.229 $\pm$ 307.76 & 37.457 $\pm$ 3.12 & 48.324 $\pm$ 25.16 & 18.845 $\pm$ 0.61\\
-\hline
-K-NN & 0.787 $\pm$ 0.08 & 272.294 $\pm$ 32.38 & 840.594 $\pm$ 240.11 & 47.475 $\pm$ 3.39 & 63.072 $\pm$ 10.29 & 0.001 $\pm$ 0.01\\
-\hline 
-Random Forest & 0.840 $\pm$ 0.05 & 253.365 $\pm$ 29.43 & 788.937 $\pm$ 282.01 & 44.164 $\pm$ 2.76 & 57.766 $\pm$ 8.15 & 4.906 $\pm$ 0.12\\
-\hline 
-Linear Regression & 0.872 $\pm$ 0.07 & 308.679 $\pm$ 25.44 & 680.905 $\pm$ 226.41 & 54.053 $\pm$ 4.38 & 52.130 $\pm$ 18.29 & 984.687 $\pm$ 128.21\\
-\hline 
-SVM & 0.876 $\pm$ 0.04 & 248.763 $\pm$ 27.49 & 732.641 $\pm$ 260.56 & 43.371 $\pm$ 2.35 & 53.471 $\pm$ 6.29 & 6169.239 $\pm$ 281.49\\
-\hline 
-\end{tabular}
+ & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+M5P  & 89.0 $\pm$ 0.09  & 214.37 $\pm$ 22.96  & 634.23 $\pm$ 307.76  & 37.46 $\pm$ 3.12  & 48.32 $\pm$ 25.16  & 18.85 $\pm$ 0.61\tabularnewline
+\hline 
+K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  & 0.001 $\pm$ 0.01\tabularnewline
+\hline 
+RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
+\hline 
+LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
+\hline 
+SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
+\hline 
+\end{tabular}%}
 %}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P & 0.892 $\pm$0.102 & 211.147 $\pm$22.41 & 616.347 $\pm$321.254 & 36.928 $\pm$3.414 & 47.299 $\pm$26.827 & 0.4906 $\pm$0.0223\\
-\hline 
-K-NN & 0.869 $\pm$0.087 & 231.782 $\pm$24.246 & 668.028 $\pm$205.135 & 40.483 $\pm$3.058 & 51.276 $\pm$16.807 & 0.0015 $\pm$0.0042\\
-\hline 
-Random Forest & 0.91 $\pm$0.048 & 198.16 $\pm$19.499 & 589.353 $\pm$195.801 & 34.61 $\pm$2.27 & 44.209 $\pm$11.634 & 3.633 $\pm$0.2039\\
-\hline 
-Linear Regression & 0.864 $\pm$0.081 & 346.875 $\pm$25.395 & 695.897 $\pm$242.49 & 60.754 $\pm$4.549 & 53.164 $\pm$19.432 & 0.0124 $\pm$0.0072\\
-\hline 
-SVM & 0.842 $\pm$0.039 & 252.868 $\pm$33.384 & 858.26 $\pm$318.225 & 44.012 $\pm$3.038 & 62.22 $\pm$7.148 & 38.9667 $\pm$5.7518\\
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
+\hline 
+K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 & 0.002 $\pm$0.004\\
+\hline 
+RF & 91.0 $\pm$0.05 & 198.16 $\pm$19.50 & 589.35 $\pm$195.80 & 34.61 $\pm$2.27 & 44.21 $\pm$11.63 & 3.63 $\pm$0.20\\
+\hline 
+LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
+\hline 
+SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
 \hline 
@@
 \hline
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P & 0.873 $\pm$0.09 & 266.777 $\pm$23.117 & 662.319 $\pm$245.272 & 46.66 $\pm$3.247 & 50.9 $\pm$20.35 & 0.4103 $\pm$0.0428\\
-\hline 
-K-NN & 0.84 $\pm$0.099 & 289.092 $\pm$22.834 & 743.917 $\pm$260.45 & 50.591 $\pm$3.496 & 57.301 $\pm$22.899 & 0.001 $\pm$0.0006\\
-\hline 
-Random Forest & 0.85 $\pm$0.106 & 278.417 $\pm$23.073 & 714.134 $\pm$278.654 & 48.713 $\pm$3.434 & 55.264 $\pm$24.412 & 2.479 $\pm$0.1264\\
-\hline 
-Linear Regression & 0.859 $\pm$0.062 & 356.35 $\pm$22.43 & 708.056 $\pm$195.145 & 62.423 $\pm$4.216 & 53.974 $\pm$14.053 & 0.0067 $\pm$0.0009\\
-\hline 
-SVM & 0.86 $\pm$0.063 & 288.474 $\pm$30.322 & 817.562 $\pm$253.237 & 50.302 $\pm$2.375 & 60.266 $\pm$5.675 & 32.7252 $\pm$5.7438\\
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P & 87.0 $\pm$0.09 & 266.78 $\pm$23.12 & 662.32 $\pm$245.27 & 46.66 $\pm$3.25 & 50.9 $\pm$20.35 & 0.41 $\pm$0.04\\
+\hline 
+K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 & 0.001 $\pm$0.001\\
+\hline 
+RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
+\hline 
+LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
+\hline 
+SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
 \hline
@@
 % SOM
-\begin{tabular}{|c|l|l|l|l|l|l|}
-\hline 
-\multicolumn{7}{|c|}{\textit{SOM}}\\
-\hline
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P & 0.866 $\pm$0.104 & 234.091 $\pm$23.186 & 699.563 $\pm$317.196 & 40.924 $\pm$3.248 & 53.698 $\pm$26.867 & 0.4754 $\pm$0.1228\\
-\hline 
-K-NN & 0.868 $\pm$0.086 & 237.91 $\pm$25.344 & 665.639 $\pm$212.05 & 41.547 $\pm$3.141 & 50.96 $\pm$16.721 & 0.0009 $\pm$0.0035\\
-\hline 
-Random Forest & 0.898 $\pm$0.051 & 211.867 $\pm$20.072 & 617.776 $\pm$187.155 & 37.017 $\pm$2.461 & 46.581 $\pm$11.144 & 2.932 $\pm$0.1083\\
-\hline 
-Linear Regression & 0.855 $\pm$0.075 & 351.993 $\pm$23.72 & 714.756 $\pm$214.213 & 61.65 $\pm$4.278 & 54.665 $\pm$16.881 & 0.0113 $\pm$0.0074\\
-\hline 
-SVM & 0.845 $\pm$0.035 & 267.706 $\pm$33.819 & 888.331 $\pm$308.932 & 46.604 $\pm$2.865 & 64.62 $\pm$5.445 & 32.2689 $\pm$4.7404\\
-\hline 
-\end{tabular}
-
+\centering{}% SOM
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
+\hline 
+ &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
+\hline 
+K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  & 0.001 $\pm$0.004\tabularnewline
+\hline 
+RF & 89.8 $\pm$0.05  & 211.87 $\pm$20.07  & 617.78 $\pm$187.16  & 37.02 $\pm$2.46  & 46.58 $\pm$11.14  & 2.93 $\pm$0.11\tabularnewline
+\hline 
+LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
+\hline 
+SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
+\hline 
+\end{tabular}
 \end{table}
@@
 
-***TO DO ***: better describe (number of instances) and justify the special cases (why we have chosen them).
+***TO DO ***: Justify the special cases (why we have chosen them).
+
+Table XX shows the details of each of these editorials.
+
+\begin{table}
+\caption{Description of editorials considered as special cases.
+\label{tab:desc_editorials}}
+\centering{}%
+\begin{tabular}{|r|l|l|l|}
+\hline 
+ & Different books sold & Total copies sold & Description\\
+\hline 
+\textit{All editorials} & 6083 & 3201645 & 209 editorials\\
+\hline 
+\textit{UDL704} & 293 & 58236 & Editorial with most different\\ 
+       &     &       & books sold\\
+\hline 
+\textit{UDLU11} & 180 & 249481 & Editorial with medium number\\ 
+       &     &       &  of different books sold\\
+\hline 
+\textit{UDL929} & 216 & 460752 & Best selling editorial\\
+\hline 
+\textit{UDLW12} & 97 & 2635 & Medium selling editorial\\
+\hline 
+\end{tabular}
+\end{table}
 
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.889 $\pm$0.074 & 71.258 $\pm$21.291 & 125.19 $\pm$50.085 & 39.251 $\pm$11.769 & 47.495 $\pm$15.933 & 0.046 $\pm$0.0278\tabularnewline
-\hline 
-K-NN & 0.826 $\pm$0.1 & 87.602 $\pm$23.206 & 158.629 $\pm$54.164 & 47.621 $\pm$10.32 & 59.168 $\pm$14.428 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-Random Forest & 0.871 $\pm$0.082 & 74.634 $\pm$22.166 & 139.743 $\pm$54.357 & 40.618 $\pm$10.214 & 52.219 $\pm$16.267 & 0.1069 $\pm$0.0053\tabularnewline
-\hline 
-Linear Regression & 0.838 $\pm$0.089 & 97.513 $\pm$18.874 & 155.273 $\pm$45.562 & 54.172 $\pm$13.598 & 60.314 $\pm$21.168 & 0.0069 $\pm$0.0012\tabularnewline
-\hline 
-SVM & 0.874 $\pm$0.066 & 78.743 $\pm$22.254 & 147.295 $\pm$57.99 & 42.428 $\pm$7.826 & 53.286 $\pm$9.351 & 0.0598 $\pm$0.0157\tabularnewline
+ &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
+\hline 
+K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
+\hline 
+LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
 \hline 
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.775 $\pm$0.15 & 573.405 $\pm$192.219 & 860.313 $\pm$456.217 & 58.26 $\pm$15.867 & 65.997 $\pm$29.447 & 0.0238 $\pm$0.0018\tabularnewline
-\hline 
-K-NN & 0.732 $\pm$0.163 & 596.615 $\pm$205.368 & 933.058 $\pm$356.108 & 60.619 $\pm$17.854 & 71.363 $\pm$22.336 & 0 $\pm$0.0002\tabularnewline
-\hline 
-Random Forest & 0.867 $\pm$0.073 & 449.161 $\pm$127.796 & 671.758 $\pm$212.739 & 45.575 $\pm$9.8 & 51.372 $\pm$11.159 & 0.0606 $\pm$0.005\tabularnewline
-\hline 
-Linear Regression & 0.733 $\pm$0.195 & 680.157 $\pm$263.788 & 1103.971 $\pm$850.685 & 69.775 $\pm$27.238 & 86.106 $\pm$71.316 & 0.0024 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.804 $\pm$0.122 & 529.349 $\pm$172.496 & 846.013 $\pm$341.117 & 53.26 $\pm$11.915 & 63.539 $\pm$18.247 & 0.029 $\pm$0.0151\tabularnewline
+ & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
+\hline 
+K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
+\hline 
+RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
+\hline 
+LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
 \hline 
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.9 $\pm$0.098 & 670.244 $\pm$181.047 & 1065.337 $\pm$413.835 & 40.833 $\pm$10.858 & 43.561 $\pm$19.866 & 0.0302 $\pm$0.0016\tabularnewline
-\hline 
-K-NN & 0.733 $\pm$0.192 & 1057.212 $\pm$385.036 & 1875.849 $\pm$916.958 & 61.879 $\pm$12.366 & 68.747 $\pm$15.978 & 0 $\pm$0.0001\tabularnewline
-\hline 
-Random Forest & 0.876 $\pm$0.108 & 771.825 $\pm$326.339 & 1490.492 $\pm$930.576 & 45.399 $\pm$14.137 & 55.912 $\pm$31.703 & 0.0777 $\pm$0.0041\tabularnewline
-\hline 
-Linear Regression & 0.863 $\pm$0.118 & 922.334 $\pm$289.01 & 1399.844 $\pm$619.623 & 56.107 $\pm$16.171 & 56.425 $\pm$25.091 & 0.0045 $\pm$0.0006\tabularnewline
-\hline 
-SVM & 0.867 $\pm$0.1 & 873.222 $\pm$345.164 & 1621.478 $\pm$985.241 & 50.847 $\pm$11.83 & 57.232 $\pm$20.404 & 0.0423 $\pm$0.016\tabularnewline
+ & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
+\hline 
+K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
+\hline 
+RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
+\hline 
+LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
 \hline 
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.832 $\pm$0.24 & 14.179 $\pm$6.615 & 23.82 $\pm$11.86 & 43.405 $\pm$20.387 & 55.787 $\pm$30.474 & 0.0089 $\pm$0.0016\tabularnewline
-\hline 
-K-NN & 0.793 $\pm$0.236 & 15.34 $\pm$8.706 & 26.571 $\pm$16.635 & 46.2 $\pm$23.768 & 60.09 $\pm$35.205 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-Random Forest & 0.858 $\pm$0.172 & 14.185 $\pm$6.692 & 23.569 $\pm$11.831 & 42.534 $\pm$16.799 & 53.295 $\pm$23.408 & 0.0321 $\pm$0.0044\tabularnewline
-\hline 
-Linear Regression & 0.821 $\pm$0.252 & 14.62 $\pm$7.917 & 24.793 $\pm$15.076 & 44.573 $\pm$24.265 & 56.854 $\pm$35.071 & 0.0019 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.835 $\pm$0.21 & 14.01 $\pm$7.608 & 25.612 $\pm$15.297 & 40.663 $\pm$16.026 & 53.276 $\pm$18.45 & 0.0198 $\pm$0.0146\tabularnewline
+ & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
+\hline 
+K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
+\hline 
+LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
+\hline 
+SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor704 (ReliefFAttributeEval-FS) }
-
 \centering{}%
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.893 $\pm$0.075 & 69.699 $\pm$19.853 & 122.48 $\pm$47.284 & 38.486 $\pm$11.531 & 46.677 $\pm$16.018 & 0.0275 $\pm$0.003\tabularnewline
-\hline 
-K-NN & 0.856 $\pm$0.101 & 78.393 $\pm$24.118 & 147.075 $\pm$58.023 & 42.577 $\pm$10.988 & 54.416 $\pm$15.542 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-Random Forest & 0.877 $\pm$0.079 & 73.134 $\pm$22.949 & 137.604 $\pm$56.143 & 39.785 $\pm$10.689 & 51.348 $\pm$16.98 & 0.1282 $\pm$0.0137\tabularnewline
-\hline 
-Linear Regression & 0.873 $\pm$0.06 & 89.719 $\pm$18.306 & 140.653 $\pm$47.12 & 49.452 $\pm$10.495 & 53.196 $\pm$14.156 & 0.0008 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.877 $\pm$0.069 & 77.301 $\pm$22.249 & 146.462 $\pm$57.679 & 41.665 $\pm$7.994 & 53.098 $\pm$9.505 & 0.045 $\pm$0.0159\tabularnewline
+ & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
+\hline 
+K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
+\hline 
+LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
+\hline 
+SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor704 (CfsSubsetEval-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.801 $\pm$0.092 & 104.874 $\pm$21.376 & 174.571 $\pm$47.332 & 58.111 $\pm$14.731 & 67.577 $\pm$22.612 & 0.0178 $\pm$0.0028\tabularnewline
-\hline 
-K-NN & 0.782 $\pm$0.116 & 99.45 $\pm$24.305 & 170.827 $\pm$46.342 & 54.529 $\pm$12.277 & 65.864 $\pm$18.338 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-Random Forest & 0.776 $\pm$0.128 & 101.933 $\pm$23.664 & 180.557 $\pm$51.203 & 56.098 $\pm$13.624 & 69.862 $\pm$23.274 & 0.0738 $\pm$0.003\tabularnewline
-\hline 
-Linear Regression & 0.801 $\pm$0.096 & 106.617 $\pm$21.523 & 173.179 $\pm$46.584 & 59.109 $\pm$14.958 & 67.527 $\pm$24.529 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.818 $\pm$0.075 & 94.285 $\pm$25.516 & 180.536 $\pm$62.67 & 50.792 $\pm$8.477 & 65.624 $\pm$6.245 & 0.0382 $\pm$0.0183\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
+\hline 
+K-NN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
+\hline 
+LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor704 (SOM-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.892 $\pm$0.066 & 71.536 $\pm$18.953 & 123.061 $\pm$42.132 & 39.426 $\pm$10.597 & 47.204 $\pm$15.159 & 0.0307 $\pm$0.0067\tabularnewline
-\hline 
-K-NN & 0.858 $\pm$0.093 & 79.422 $\pm$21.473 & 140.948 $\pm$44.928 & 43.342 $\pm$10.072 & 53.313 $\pm$14.374 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-Random Forest & 0.877 $\pm$0.08 & 73.981 $\pm$20.909 & 134.107 $\pm$51.698 & 40.475 $\pm$10.512 & 50.413 $\pm$16.378 & 0.1035 $\pm$0.0076\tabularnewline
-\hline 
-Linear Regression & 0.875 $\pm$0.062 & 88.697 $\pm$16.338 & 135.029 $\pm$35.176 & 49.076 $\pm$10.471 & 51.972 $\pm$13.648 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.878 $\pm$0.057 & 81.087 $\pm$22.477 & 154.823 $\pm$59.93 & 43.651 $\pm$7.364 & 55.716 $\pm$7.153 & 0.0309 $\pm$0.0033\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
+\hline 
+K-NN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
+\hline 
+LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDLU11 (ReliefFAttributeEval-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.766 $\pm$0.168 & 592.493 $\pm$209.249 & 894.757 $\pm$508.14 & 60.206 $\pm$18.221 & 69.138 $\pm$37.353 & 0.0166 $\pm$0.0011\tabularnewline
-\hline 
-K-NN & 0.827 $\pm$0.093 & 486.96 $\pm$140.273 & 741.808 $\pm$238.557 & 49.268 $\pm$10.504 & 56.62 $\pm$12.591 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-Random Forest & 0.853 $\pm$0.089 & 455.7 $\pm$123.958 & 686.536 $\pm$198.157 & 46.319 $\pm$10.195 & 53.029 $\pm$13.054 & 0.07 $\pm$0.0028\tabularnewline
-\hline 
-Linear Regression & 0.644 $\pm$0.202 & 817.214 $\pm$331.164 & 1324.047 $\pm$1090.851 & 83.217 $\pm$32.006 & 101.895 $\pm$87.829 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.714 $\pm$0.142 & 644.424 $\pm$203.425 & 1009.656 $\pm$371.828 & 64.474 $\pm$11.701 & 75.542 $\pm$15.994 & 0.0182 $\pm$0.0012\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
+\hline 
+K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
+\hline 
+LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDLU11 (CfsSubsetEval-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.64 $\pm$0.232 & 777.935 $\pm$342.04 & 1305.28 $\pm$1075.291 & 78.373 $\pm$30.4 & 99.857 $\pm$85.431 & 0.0134 $\pm$0.0012\tabularnewline
-\hline 
-K-NN & 0.648 $\pm$0.181 & 702.701 $\pm$181.407 & 1008.391 $\pm$305.871 & 71.407 $\pm$13.951 & 78.469 $\pm$22.695 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-Random Forest & 0.653 $\pm$0.193 & 685.556 $\pm$195.277 & 1021.374 $\pm$352.882 & 69.74 $\pm$16.956 & 79.373 $\pm$26.977 & 0.0466 $\pm$0.0023\tabularnewline
-\hline 
-Linear Regression & 0.67 $\pm$0.234 & 857.222 $\pm$308.686 & 1352.26 $\pm$945.314 & 86.095 $\pm$24.253 & 102.893 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.648 $\pm$0.23 & 879.912 $\pm$280.326 & 1402.822 $\pm$593.437 & 87.739 $\pm$15.273 & 105.402 $\pm$37.729 & 0.0168 $\pm$0.001\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+K-NN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 65.3 $\pm$0.19 & 685.56 $\pm$195.28 & 1021.37 $\pm$352.88 & 69.74 $\pm$16.96 & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
+\hline 
+LR & 67.0 $\pm$0.23\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDLU11 (SOM-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.79 $\pm$0.138 & 573.246 $\pm$167.882 & 827.554 $\pm$388.162 & 58.421 $\pm$14.138 & 63.975 $\pm$25.632 & 0.0153 $\pm$0.0015\tabularnewline
-\hline 
-K-NN & 0.836 $\pm$0.098 & 492.179 $\pm$126.856 & 727.326 $\pm$209.877 & 50.117 $\pm$10.688 & 56.136 $\pm$12.894 & 0 $\pm$0.0002\tabularnewline
-\hline 
-Random Forest & 0.856 $\pm$0.084 & 446.245 $\pm$119.79 & 673.455 $\pm$189.06 & 45.384 $\pm$9.778 & 52.236 $\pm$13.088 & 0.0594 $\pm$0.0049\tabularnewline
-\hline 
-Linear Regression & 0.71 $\pm$0.188 & 723.735 $\pm$247.959 & 1108.74 $\pm$736.165 & 74.136 $\pm$24.906 & 85.956 $\pm$59.994 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.716 $\pm$0.147 & 640.136 $\pm$206.459 & 1017.018 $\pm$376.134 & 63.961 $\pm$11.873 & 76.103 $\pm$16.796 & 0.0189 $\pm$0.0014\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
+\hline 
+K-NN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.6 $\pm$0.08 & 446.25 $\pm$119.79 & 673.46 $\pm$189.06 & 45.38 $\pm$9.78 & 52.24 $\pm$13.09 & 0.0594 $\pm$0.0049\tabularnewline
+\hline 
+LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDL929 (ReliefFAttributeEval-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.905 $\pm$0.1 & 661.81 $\pm$186.171 & 1070.235 $\pm$425.658 & 40.176 $\pm$10.502 & 43.555 $\pm$19.769 & 0.0198 $\pm$0.0018\tabularnewline
-\hline 
-K-NN & 0.878 $\pm$0.114 & 751.542 $\pm$270.905 & 1257.821 $\pm$615.656 & 44.571 $\pm$10.886 & 48.616 $\pm$18.727 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-Random Forest & 0.883 $\pm$0.11 & 735.044 $\pm$326.9 & 1420.43 $\pm$941.619 & 43.561 $\pm$15.883 & 54.357 $\pm$35.307 & 0.095 $\pm$0.0086\tabularnewline
-\hline 
-Linear Regression & 0.884 $\pm$0.113 & 868.179 $\pm$208.648 & 1231.227 $\pm$454.862 & 53.383 $\pm$14.672 & 50.598 $\pm$22.037 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.876 $\pm$0.099 & 860.485 $\pm$334.669 & 1560.048 $\pm$962.637 & 49.978 $\pm$9.607 & 55.069 $\pm$17.762 & 0.0232 $\pm$0.0028\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
+\hline 
+LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDL929 (CfsSubsetEval-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.88 $\pm$0.126 & 738.28 $\pm$188.534 & 1141.786 $\pm$472.025 & 45.452 $\pm$13.622 & 47.58 $\pm$24.835 & 0.0169 $\pm$0.0016\tabularnewline
-\hline 
-K-NN & 0.853 $\pm$0.145 & 825.191 $\pm$235.337 & 1280.334 $\pm$523.058 & 50.228 $\pm$14.065 & 51.419 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-Random Forest & 0.864 $\pm$0.138 & 790.09 $\pm$225.858 & 1245.227 $\pm$584.231 & 48.216 $\pm$13.792 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
-\hline 
-Linear Regression & 0.866 $\pm$0.123 & 936.557 $\pm$204.458 & 1329.237 $\pm$480.786 & 58.037 $\pm$16.921 & 55.408 $\pm$25.623 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.868 $\pm$0.12 & 940.386 $\pm$344.161 & 1648.503 $\pm$1026.038 & 54.498 $\pm$7.122 & 56.166 $\pm$7.8 & 0.0201 $\pm$0.0021\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 88.0 $\pm$0.13 & 738.28 $\pm$188.53 & 1141.79 $\pm$472.025 & 45.45 $\pm$13.62 & 47.58 $\pm$24.84 & 0.017 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDL929 (SOM-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.897 $\pm$0.098 & 685.667 $\pm$185.988 & 1116.42 $\pm$478.062 & 42.092 $\pm$12.822 & 46.308 $\pm$24.612 & 0.02 $\pm$0.0035\tabularnewline
-\hline 
-K-NN & 0.89 $\pm$0.101 & 746.448 $\pm$250.762 & 1203.407 $\pm$564.836 & 44.361 $\pm$9.734 & 46.251 $\pm$14.413 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-Random Forest & 0.895 $\pm$0.094 & 708.244 $\pm$264.518 & 1270.262 $\pm$708.817 & 42.135 $\pm$12.446 & 49.066 $\pm$26.594 & 0.0801 $\pm$0.0058\tabularnewline
-\hline 
-Linear Regression & 0.866 $\pm$0.129 & 894.084 $\pm$206.603 & 1282.833 $\pm$451.866 & 55.287 $\pm$15.923 & 53.738 $\pm$24.698 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.871 $\pm$0.101 & 908.562 $\pm$348.195 & 1608.767 $\pm$972.552 & 52.632 $\pm$8.746 & 55.945 $\pm$12.493 & 0.0221 $\pm$0.0024\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 89.7 $\pm$0.10 & 685.67 $\pm$185.99 & 1116.42 $\pm$478.06 & 42.09 $\pm$12.8 & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
+\hline 
+K-NN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDLW12 (ReliefFAttributeEval-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.837 $\pm$0.241 & 13.853 $\pm$6.557 & 23.189 $\pm$11.795 & 42.353 $\pm$20.326 & 54.078 $\pm$30.055 & 0.0063 $\pm$0.0014\tabularnewline
-\hline 
-K-NN & 0.772 $\pm$0.296 & 14.178 $\pm$6.631 & 23.645 $\pm$11.029 & 43.367 $\pm$19.229 & 56.996 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
-\hline 
-Random Forest & 0.867 $\pm$0.161 & 13.628 $\pm$6.673 & 22.797 $\pm$11.806 & 41.066 $\pm$17.705 & 52.431 $\pm$26.232 & 0.0304 $\pm$0.0025\tabularnewline
-\hline 
-Linear Regression & 0.844 $\pm$0.246 & 12.789 $\pm$6.645 & 21.521 $\pm$12.543 & 39.467 $\pm$23.345 & 50.14 $\pm$35.261 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.852 $\pm$0.187 & 13.217 $\pm$7.386 & 24.407 $\pm$15.087 & 38.24 $\pm$15.41 & 50.463 $\pm$17.973 & 0.0139 $\pm$0.0016\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
+\hline 
+K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
+\hline 
+RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
+\hline 
+LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDLW12 (CfsSubsetEval-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.816 $\pm$0.219 & 15.671 $\pm$6.584 & 25.632 $\pm$11.838 & 47.931 $\pm$18.812 & 60.719 $\pm$31.747 & 0.0059 $\pm$0.0015\tabularnewline
-\hline 
-K-NN & 0.752 $\pm$0.267 & 15.732 $\pm$7.726 & 26.68 $\pm$14.816 & 48.578 $\pm$24.769 & 66.231 $\pm$48.588 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-Random Forest & 0.751 $\pm$0.264 & 15.61 $\pm$7.191 & 26.831 $\pm$13.355 & 47.381 $\pm$20.099 & 64.652 $\pm$38.664 & 0.0224 $\pm$0.0027\tabularnewline
-\hline 
-Linear Regression & 0.816 $\pm$0.218 & 15.674 $\pm$6.546 & 25.492 $\pm$11.628 & 47.97 $\pm$18.85 & 60.276 $\pm$30.617 & 0.0002 $\pm$0.0004\tabularnewline
-\hline 
-SVM & 0.818 $\pm$0.211 & 17.711 $\pm$9.704 & 31.951 $\pm$19.261 & 50.073 $\pm$14.926 & 65.121 $\pm$16.362 & 0.0129 $\pm$0.0009\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 75.1 $\pm$0.26 & 15.61 $\pm$7.19 & 26.83 $\pm$13.36 & 47.38 $\pm$20.10 & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
+\hline 
+LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & 25.49 $\pm$11.63 & 47.97 $\pm$18.85 & 60.28 $\pm$30.62 & 0.0002 $\pm$0.0004\tabularnewline
+\hline 
+SVM & 81.8 $\pm$0.21 & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
 \hline 
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \caption{Predicting Total sales for Editor-UDLW12 (SOM-FS)}
@@
 \hline 
- & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 0.86 $\pm$0.188 & 13.84 $\pm$6.753 & 23.94 $\pm$11.638 & 41.65 $\pm$17.557 & 55.439 $\pm$27.128 & 0.006 $\pm$0.0012\tabularnewline
-\hline 
-K-NN & 0.74 $\pm$0.293 & 15.926 $\pm$8.521 & 28.281 $\pm$16.283 & 48.827 $\pm$25.885 & 68.75 $\pm$48.849 & 0 $\pm$0.0002\tabularnewline
-\hline 
-Random Forest & 0.855 $\pm$0.187 & 13.661 $\pm$6.469 & 22.51 $\pm$11.026 & 41.378 $\pm$17.87 & 52.198 $\pm$27.088 & 0.0262 $\pm$0.0019\tabularnewline
-\hline 
-Linear Regression & 0.854 $\pm$0.214 & 14.586 $\pm$7.129 & 24.404 $\pm$12.87 & 44.813 $\pm$23.647 & 57.727 $\pm$38.631 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 0.844 $\pm$0.184 & 14.177 $\pm$7.959 & 26.487 $\pm$16.539 & 40.931 $\pm$16.652 & 54.366 $\pm$20.004 & 0.0133 $\pm$0.0013\tabularnewline
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 86.0 $\pm$0.19 & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
+\hline 
+K-NN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.5 $\pm$0.19 & 13.66 $\pm$6.47 & 22.51 $\pm$11.03 & 41.38 $\pm$17.87 & 52.20 $\pm$27.09 & 0.026 $\pm$0.0019\tabularnewline
+\hline 
+LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
 \hline 
@@
 
-Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same editorial (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results.
+Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same editorial (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).
 

### 2016-04-09 paper.tex
Adds emails

@@
 %%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
-\title{Enhancing the sales prediction of newly published books by means of computational intelligence methods}
+\title{Enhancing the prediction of sales for newly published books by
+  means of computational intelligence methods}
 
@@
 $^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
-           e-mail: {\tt pacv@ugr.es}
+e-mail: {\tt pacv@ugr.es, amorag@geneura.ugr.es,
+  jmerelo@geneura.ugr.es, pgarcia@geneura.ugr.es,
+  antares.es@gmail.com, mgarenas@ugr.es, palomacd@ugr.es}
 }

### 2016-04-09 paper.tex
Revising abstract
Please @amoragar have a look.

@@
 \begin{abstract}
-***TO DO***: rewrite this considering the new contents and results\\
+%***TO DO***: rewrite this considering the new contents and results\\
 
@@
 reached the shelves. 
-Several years 
 % % Antonio - Decir cuántos años son, que no me acuerdo.
@@
 data for books published in Spain across several years. After an
-initial exploratory phase using visualisation techniques, we have
+initial exploratory analysis phase using visualisation techniques, we have
 applied several feature selection techniques in order
 to find out what are the variables that have more impact on sales, and
-then used machine learning to create a model and forecast sales. 
-The described methodology improves the forecasting running time  %with
+then used machine learning to create a model and forecast sales. The
+initial methodology was used in a commercial product by Grupo
+Trevenque, but the methodology described here improves the forecasting running time  %with
                                 %respect to what?- JJ
 and is
-eventually able to predict sales with remarkable accuracy. Moreover,
-the proposed method was validated by the company that provided
-the data and incorporated in a business intelligence tool for
-publishers, % We shouldn't say this, it's outside the bounds of the
+eventually able to predict sales from pre-publication data with
+remarkable accuracy, thus creating a useful tool for publishers, for whom
+% Moreover,
+% the proposed method was validated by the company that provided
+% the data and incorporated in a business intelligence tool for
+% publishers, % We shouldn't say this, it's outside the bounds of the
             % paper. Besides, it was a different technique - JJ
-since the obtained models provide a reliable guidance on the decision process of
+obtained models provide a reliable guidance on the decision process of
 publishing a book, without human intervention 

### 2016-04-09 paper.tex
Revising the introduction
refs #21 but also #19

@@
 
-***TO DO***: complete this considering the new contents and results\\
-
-Publishing a book, as releasing any other cultural product with a
+%***TO DO***: complete this considering the new contents and results\\
+% Instead of just writing this you should say what has changed and
+% what should be changed. For instance, the paragraph below probably
+% shouldn't - JJ 
+Publishing a book, in the same way as releasing any other cultural product with a
 physical substrate, implies several
@@
 the complexity, and derived expenses, of the production and
-distribution processes.  When a company is faced with the problem or
+distribution and storage processes.  When a company is faced with the problem or
 releasing a completely new product, in the sense that it is an unknown
@@
 Thus, it is extremely important to develop an accurate predictive method
-which could accurately forecast the future sales a new book will
-achieve, in order to optimise production, improve the publishing
+which could forecast the future sales a new book will
+achieve, in order to optimise production schedules, improve the publishing
 company profits or minimise losses \cite{Zhao2001}. This is the main
 objective of this paper. 
-%FERGU: entonces el objetivo es desarrollar una herramienta? La metodología? Dejarlo más claro en todos los sitios
+%FERGU: entonces el objetivo es desarrollar una herramienta? La
+%metodología? Dejarlo más claro en todos los sitios
+% Un método predictivo. Lo deja muy claro - JJ
 An example is the optimisation of sales \cite{Mattila2002} by
@@
 % un poco más lo que se hace en ese trabajo. ;)
-% An example of what? Does that go there? - JJ
-
-However, designing such an accurate predictive tool is a difficult
-task in this scope, as book sales are influenced by several factors
-that make them fluctuate and, moreover, usually they might be not
-controllable and even unknown. 
-%FERGU: "moreover, usually" son dos adverbios juntos y queda un poco raro 
-For instance, some are related to decisions on purchases, others with freight 
-%FERGU: some factors para dejarlo claro
-traffic, or others with the distribution strategy \cite{Little1998}. % This paragraph is rather useless - JJ
+% An example of what? Does that go there or to the state of the art? - JJ
+
+The accuracy of the predictive method we intend to design is affected
+negatively by several factors, related to decisions on purchases, to freight 
+traffic, or with the distribution strategy \cite{Little1998}. % This
+                                % paragraph is rather useless - JJ
+% I have changed the paragraph completely, but still don't know what
+% this is doing here - JJ
 
@@
 a company that provides management systems and services for bookshops,
-% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
 publishers and distributors. 
@@
 correct estimations (predictions), for instance, she can decide
-increasing or decreasing the sales prediction based on season or sales
-period.                         % varias citas - JJ
-                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
-                        %  y que así era como funcionaban hasta ese momento.
-%In any case, in general companies usually use a forecasting model and then, 
-%an expert applies his knowledge, as the company might require an 
-%interpretable and understandable model. 
+increasing or decreasing the sales forecast based on season or sales
+period.                          
 However, carrying out the analysis and forecasting process as a human expert,
-may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
-%FERGU: fuzzy-like existe? suena raruno :P
+may lead to imprecise predictions which may not take all the variables into account. 
 In addition, the process might be tedious, especially when the amount
 of data is quite large, and even, different experts can reach different
-predictions from the same dataset \cite{ChingChin2010,Sanders1994}.
-
-For these reasons, the industry requires the best suited forecasting
-techniques to be adopted so that, estimating sales task is carried out
-reliably, accurately, and in an automatic way. % Iterative. Another
-                                % useless paragraph - JJ
+predictions from the same dataset \cite{ChingChin2010,Sanders1994}. A
+initial version of this method was developed under contract with that
+company and eventually integrated in their product. This paper
+represents an improved version of that method based on the same data.
 
@@
 
-***TO DO***: rewrite this considering the new structure of the paper\\
+%***TO DO***: rewrite this considering the new structure of the paper\\
 
@@
 problem of how many books should be printed when a new book is published, 
-        % no es el problema de publicación, es el problema de venta
-        % de libros sin publicar. Habrá que buscar un nombre - JJ
-        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
 experimental setup and the methodology considered in the study is
-presented.  %FERGU: mejor described para no repetir
-Section \ref{sec:experiments} reports and analyses the obtained results with a 
+presented.  Section \ref{sec:experiments} reports and analyses the obtained results with a 
 real dataset. Finally, conclusions and future work are presented in Section

### 2016-04-19 paper.tex
Mainly rewriting of sentences
And calls to @amorag and @pacastillo to revise abstract adn introduction.

@@
 %***TO DO***: rewrite this considering the new contents and results\\
-
-When a new book is launched the publisher faces the problem of
-how many books should be printed for delivery to bookstores. Printing too many is the main issue,
-since it implies a loss of investment due to inventory excess. In this
-paper, we are tackling the problem of predicting total sales in order to 
-print the right amount of books, doing so even before the book has
-reached the shelves. 
-% % Antonio - Decir cuántos años son, que no me acuerdo.
-% of data on published books in Spain have been processed by means of
-% data visualisation %visualization does not "process". I propose an alternative
-%  and other feature selection techniques. 
-We have been working on a data set that includes the complete sales
-data for books published in Spain across several years. After an
-initial exploratory analysis phase using visualisation techniques, we have
-applied several feature selection techniques in order
-to find out what are the variables that have more impact on sales, and
-then used machine learning to create a model and forecast sales. The
-initial methodology was used in a commercial product by Grupo
-Trevenque, but the methodology described here improves the forecasting running time  %with
+% Has it been done?
+
+When a new book is launched the publisher faces the problem of how
+many books should be printed for delivery to bookstores; printing too
+many is the main issue, since it implies a loss of investment due to
+inventory excess. In this paper, we are tackling the problem of
+predicting total sales in order to print the right amount of books and
+doing so even before the book has reached the stores.  We have been
+working on a data set that includes the complete sales data for books
+published in Spain across several years. After an initial exploratory
+analysis phase using visualisation techniques, we have applied several
+feature selection techniques in order to find out what are the
+variables that have more impact on sales, and then used machine
+learning to create a model and forecast sales. The initial methodology
+was used in a commercial product by Grupo Trevenque, but the
+methodology described here improves the running time %with
                                 %respect to what?- JJ
-and is
-eventually able to predict sales from pre-publication data with
-remarkable accuracy, thus creating a useful tool for publishers, for whom
-% Moreover,
-% the proposed method was validated by the company that provided
-% the data and incorporated in a business intelligence tool for
-% publishers, % We shouldn't say this, it's outside the bounds of the
-            % paper. Besides, it was a different technique - JJ
-obtained models provide a reliable guidance on the decision process of
-publishing a book, without human intervention 
-either for the operation or for interpretation. 
+and is eventually able to predict sales from pre-publication data with
+remarkable accuracy, thus creating a useful tool for publishers, for
+whom obtained models can provide a reliable guidance on the decision
+process of publishing a book, without human intervention either for
+the operation or for interpretation.
 % Antonio - esto es cierto??? :D
@@
 types of risks and costs due to
-the complexity, and derived expenses, of the production and
-distribution and storage processes.  When a company is faced with the problem or
-releasing a completely new product, in the sense that it is an unknown
+the complexity, and derived expenses, of the production,
+distribution and storage processes; most of these costs are associated
+to the number of books actually printed. But the problem is further
+complicated for completely new products, in the sense that it is an unknown
 author or a new topic with no track record, sales forecasts can
@@
 %papers to affirm that - JJ
+%please someone address this - JJ
 

### 2016-04-19 paper.tex
Revising the state of the art.
it still has many suggestions and things to address. First thing, it lacks a narrative. The state of the art should be possibly resumed in a sentence, such as
"So far, most forecasting techniques have been based on previous sales. Very few have used, like we do in this paper, pre-sales data. So this is what we are doing here and we will improve methods"

Please @fergunet @amorag @pacastillo take a long hard look at it, and as done before address suggestions and issues and erase them when done.

@@
 
-Sales forecasting is a problem which has been addressed several times
-in the literature. Most of the studies have been conducted using
-different analysis and forecasting methods, such as regression models
+% Sales forecasting is a problem which has been addressed several times
+% in the literature.
+% This sentence is useless
+In the past, sales prediction has been performed using methods such as  regression models
 \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy 
@@
 % arte. Habría que reescribir la intro. - JJ
-
-Specifically, Time-Series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
+% ¿Qué usan esos métodos? - JJ
+
+Specifically, time-series prediction methods
+\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
 is perhaps the most used technique to tackle the sales forecasting
@@
 \cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
-them are categorical, harder to process, even more so if the number
+them are categorical, which makes them harder to process, even more so if the number
 of categories is high. Given these issues, finding adequate
@@
 the best method to use is also a problem \cite{ChingChin2010}. % Qualify this citation - jj
+% And it's the 3rd time you cite ChingChin!!! - JJ
 
@@
 
-Thus, taking into account the kind of problem we address in this paper, i.e.
-the prediction of sales of a new product for which no historical data are available, the classical forecasting methods based on time-series are not
+Thus, taking into account the kind of problem we address in this
+paper, i.e. the prediction of sales of a new product for which no
+historical data are available, the classical forecasting methods based
+on time-series are not 
 adequate, although they can obviously be used once the book has been launched for sale. 

### 2016-04-20 paper.tex
addressing comments in the experiments

@@
 
-In the first experiment, forecasting methods have been applied to the whole dataset.
-All the pre-sales features have been considered, also including the categorical ones, which make harder to process the instances and build the different models.
-SVM for instance, must previously transform these categories into numbers in order to deal with the data, which means the creation of a different (and new) variable per possible value.
+In the first stage of the experiments, forecasting methods have been applied to the whole dataset.
+All the pre-sales features have been considered, including the categorical ones, which make it harder to process the instances and build the different models.
+SVM for instance, must previously transform these categories into binary variables in order to deal with the data, which means the creation of a different (and new) variable per each possible value.
 Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
 % Antonio - Sam, verify this, please
+% Sam - reviewed and fixed
 
@@
 
-In this second experiment, different feature selection processes have been applied.
-
-***TODO***: The aim of these techniques is to reduce the number of features to consider...
+In the second stage of the experiments, different feature selection methods have been applied.
+The aim of these methods is to reduce the number of features considered in developing the forecasting models which consequently simplify the complexity of the models, improve their interpretability and decrease the training time.
+The simpler models generated after performing feature selection could give the decision maker a better insight on the underlying process by identifying the more influencing variables.
+
 % Antonio - TODO: explain the aim of FS in these experiments.
+% Sam : Done
 

### 2016-04-22 paper.tex
Moving tables to Appendix

@@
 \usepackage{url}
+\usepackage{appendix}
 
@@
 Case 1-A: Developing prediction models to predict Total sales for
-Editor704 (An editor with the most number of different books sold) - 293
+Editorial704 (An editorial with the most number of different books sold) - 293
 instances.
@@
 \begin{table}
-\caption{Predicting Total sales for Editor704}
+\caption{Predicting Total sales for Editorial704}
 
@@
 Case 1-B: Developing prediction models to predict Total sales for
-Editor-UDLU11 (An editor with a medium number of different books sold) - 180
-instances.
+Editorial-UDLU11 (An editorial with a medium number of different books sold) - 180 instances.
 
 \begin{table}
-\caption{Predicting Total sales for Editor-UDLU11}
+\caption{Predicting Total sales for Editorial-UDLU11}
 
@@
 Case 2-A: Developing prediction models to predict Total sales for
-Editor-UDL929 (The best selling editor) - 216 instances.
+Editorial-UDL929 (The best selling editorial) - 216 instances.
 
 \begin{table}
-\caption{Predicting Total sales for Editor-UDL929 (460752 sales) }
+\caption{Predicting Total sales for Editorial-UDL929 (460752 sales) }
 
@@
 Case 2-B: Developing prediction models to predict Total sales for
-Editor-UDLW12 (The median selling editor)- 97 instances.
+Editorial-UDLW12 (The median selling editor)- 97 instances.
 
 \begin{table}
-\caption{Predicting Total sales for Editor-UDLW12 (2635 sales) }
+\caption{Predicting Total sales for Editorial-UDLW12 (2635 sales) }
 
@@
 
-***TO DO***: choose the best Feature selection method and apply just this one (ReliefAttributeEval???). There are too many tables I think.
-We could add an appendix or so with the rest of results if you want.
+***TO DO***: explain we have chosen the best Feature selection method (ReliefAttributeEval???). The rest of tables have been moved to an appendix.
 
 Case 1-A: Developing prediction models to predict Total sales for
-Editor704 with ReliefFAttributeEval feature selection.
+Editorial704 with ReliefFAttributeEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editor704 (ReliefFAttributeEval-FS) }
+\caption{Predicting Total sales for Editorial704 (ReliefFAttributeEval-FS) }
 \centering{}%
@@
 
-Case 1-A: Developing prediction models to predict Total sales for
-Editor704 with CfsSubsetEval feature selection.
+Case 1-B: Developing prediction models to predict Total sales for
+Editorial-UDLU11 with ReliefFAttributeEval feature selection
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editor704 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for Editorial-UDLU11 (ReliefFAttributeEval-FS)}
 
@@
 \hline 
-M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
-\hline 
-K-NN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
-\hline 
-LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 1-A: Developing prediction models to predict Total sales for
-Editor704 with SOM feature selection.
+M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
+\hline 
+K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
+\hline 
+LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editorial-UDL929 with ReliefFAttributeEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editor704 (SOM-FS)}
+\caption{Predicting Total sales for Editorial-UDL929 (ReliefFAttributeEval-FS)}
 
@@
 \hline 
-M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
-\hline 
-K-NN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
-\hline 
-LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 1-B: Developing prediction models to predict Total sales for
-Editor-UDLU11 with ReliefFAttributeEval feature selection
+M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
+\hline 
+LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editorial-UDLW12 with ReliefFAttributeEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDLU11 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for Editorial-UDLW12 (ReliefFAttributeEval-FS)}
 
@@
 \hline 
-M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
-\hline 
-K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
-\hline 
-LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 1-B: Developing prediction models to predict Total sales for
-Editor-UDLU11 with CfsSubsetEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDLU11 (CfsSubsetEval-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
-\hline 
-K-NN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 65.3 $\pm$0.19 & 685.56 $\pm$195.28 & 1021.37 $\pm$352.88 & 69.74 $\pm$16.96 & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
-\hline 
-LR & 67.0 $\pm$0.23\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 1-B: Developing prediction models to predict Total sales for
-Editor-UDLU11 with SOM feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDLU11 (SOM-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
-\hline 
-K-NN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
-\hline 
-RF & 85.6 $\pm$0.08 & 446.25 $\pm$119.79 & 673.46 $\pm$189.06 & 45.38 $\pm$9.78 & 52.24 $\pm$13.09 & 0.0594 $\pm$0.0049\tabularnewline
-\hline 
-LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-A: Developing prediction models to predict Total sales for
-Editor-UDL929 with ReliefFAttributeEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDL929 (ReliefFAttributeEval-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
-\hline 
-LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-A: Developing prediction models to predict Total sales for
-Editor-UDL929 with CfsSubsetEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDL929 (CfsSubsetEval-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 88.0 $\pm$0.13 & 738.28 $\pm$188.53 & 1141.79 $\pm$472.025 & 45.45 $\pm$13.62 & 47.58 $\pm$24.84 & 0.017 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
-\hline 
-LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-A: Developing prediction models to predict Total sales for
-Editor-UDL929 with SOM feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDL929 (SOM-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 89.7 $\pm$0.10 & 685.67 $\pm$185.99 & 1116.42 $\pm$478.06 & 42.09 $\pm$12.8 & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
-\hline 
-K-NN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
-\hline 
-LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-B: Developing prediction models to predict Total sales for
-Editor-UDLW12 with ReliefFAttributeEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDLW12 (ReliefFAttributeEval-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
 M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
@@
 SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-B: Developing prediction models to predict Total sales for
-Editor-UDLW12 with CfsSubsetEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDLW12 (CfsSubsetEval-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 75.1 $\pm$0.26 & 15.61 $\pm$7.19 & 26.83 $\pm$13.36 & 47.38 $\pm$20.10 & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
-\hline 
-LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & 25.49 $\pm$11.63 & 47.97 $\pm$18.85 & 60.28 $\pm$30.62 & 0.0002 $\pm$0.0004\tabularnewline
-\hline 
-SVM & 81.8 $\pm$0.21 & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-B: Developing prediction models to predict Total sales for
-Editor-UDLW12 with SOM feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editor-UDLW12 (SOM-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 86.0 $\pm$0.19 & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
-\hline 
-K-NN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
-\hline 
-RF & 85.5 $\pm$0.19 & 13.66 $\pm$6.47 & 22.51 $\pm$11.03 & 41.38 $\pm$17.87 & 52.20 $\pm$27.09 & 0.026 $\pm$0.0019\tabularnewline
-\hline 
-LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
 \hline 
@@
 
+%----------------------------------------------------------------------
+
+\appendix
+\section{APENDIX TABLES}
+
+Case 1-A: Developing prediction models to predict Total sales for
+Editorial704 with CfsSubsetEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editorial704 (CfsSubsetEval-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
+\hline 
+K-NN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
+\hline 
+LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-A: Developing prediction models to predict Total sales for
+Editorial704 with SOM feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editorial704 (SOM-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
+\hline 
+K-NN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
+\hline 
+LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+%-----------------------------------
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editorial-UDLU11 with CfsSubsetEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editorial-UDLU11 (CfsSubsetEval-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+K-NN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 65.3 $\pm$0.19 & 685.56 $\pm$195.28 & 1021.37 $\pm$352.88 & 69.74 $\pm$16.96 & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
+\hline 
+LR & 67.0 $\pm$0.23\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editorial-UDLU11 with SOM feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editorial-UDLU11 (SOM-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
+\hline 
+K-NN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.6 $\pm$0.08 & 446.25 $\pm$119.79 & 673.46 $\pm$189.06 & 45.38 $\pm$9.78 & 52.24 $\pm$13.09 & 0.0594 $\pm$0.0049\tabularnewline
+\hline 
+LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+%-----------------------------------
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editorial-UDL929 with CfsSubsetEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editorial-UDL929 (CfsSubsetEval-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 88.0 $\pm$0.13 & 738.28 $\pm$188.53 & 1141.79 $\pm$472.025 & 45.45 $\pm$13.62 & 47.58 $\pm$24.84 & 0.017 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editorial-UDL929 with SOM feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editorial-UDL929 (SOM-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 89.7 $\pm$0.10 & 685.67 $\pm$185.99 & 1116.42 $\pm$478.06 & 42.09 $\pm$12.8 & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
+\hline 
+K-NN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+%-----------------------------------
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editorial-UDLW12 with CfsSubsetEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editorial-UDLW12 (CfsSubsetEval-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 75.1 $\pm$0.26 & 15.61 $\pm$7.19 & 26.83 $\pm$13.36 & 47.38 $\pm$20.10 & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
+\hline 
+LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & 25.49 $\pm$11.63 & 47.97 $\pm$18.85 & 60.28 $\pm$30.62 & 0.0002 $\pm$0.0004\tabularnewline
+\hline 
+SVM & 81.8 $\pm$0.21 & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editorial-UDLW12 with SOM feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editorial-UDLW12 (SOM-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 86.0 $\pm$0.19 & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
+\hline 
+K-NN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.5 $\pm$0.19 & 13.66 $\pm$6.47 & 22.51 $\pm$11.03 & 41.38 $\pm$17.87 & 52.20 $\pm$27.09 & 0.026 $\pm$0.0019\tabularnewline
+\hline 
+LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
 \end{document}

### 2016-04-23 paper.tex
new description for SOM

@@
 
-Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that
-uses an unsupervised training algorithm and which, through a process
-called self-organisation, configures the output units into a
-topological representation of the original data. It tries to imitate
-the self-organisation done in the sensory cortex of the human brain,
-where neighbouring neurons are activated by similar stimulus. SOM
-belongs to a general class of neural network methods, which are
-non-linear regression techniques that can be trained to learn or find
-relationships between inputs and outputs or to organise data so as to
-disclose so far unknown patterns or structures. It is usually used as
-a clustering/classification tool or used to find unknown relationships
-between a set of variables that describe a problem. The main property
-of the SOM is that it makes a nonlinear projection from a
-high-dimensional data space (one dimension per variable) on a regular,
-low-dimensional (usually 2D) grid of neurons, called units. 
-SOM is further processed using Ultsch method \cite{UmatUlts}, the
-Unified distance matrix (U-matrix), which uses SOM's codevectors
-(vectors of variables of the problem) as data source and generates a
-matrix where each component is a distance measure between two adjacent
-neurons. It allows us to visualise any multi-variated dataset in a
-two-dimensional display, so we can detect topological relations among
-neurons and infer about the input data structure. High values in the
-U-matrix represent a frontier region between clusters, and low values
-represent a high degree of similarities among neurons on that region,
-clusters .
-
-SOMs (and U-Matrix) are usually applied to visualise natural
-structures in the data and their relations, as well as the natural
-groupings that could be among them. In addition, SOM makes easy the
-estimation of the variables that have more influence on these
-groupings. Other statistical and soft computing tools can also be used
-for this purpose, but since Kohonen's SOMs offers a visual way of
-doing it, it is much more intuitive, and takes advantage of the
-capabilities of the human brain as a pattern recogniser. 
+%--- new SOM description % -Sam
+
+SOM is a type of unsupervised neural networks inspired by the topographical organization of the sensory cortex of human brain \cite{kohonen1998}.
+It maps highly dimensional data into a lower dimensional space where similar data patterns are located in more adjacent areas on the grid.
+
+SOM is a very useful analysis tool for visualizing complex data with high number of variables in a simple geometric planes.
+Therefore, it could be used for different tasks like features reduction and data clustering and visualization.
+
+Basically, SOM consists of two layers; input layer and output layer (also known as Kohen layer).
+Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e.; units).
+This means that every neuron is linked to every input in the input layer.
+
+The learning process of SOM is an iterative process applied in two stages.
+First, the weights of the network are initialized randomly then the n-dimensional input vectors are presented to the network sequentially so the distance between the weights of the neurons and the inputs are computed using the simple Euclidean distance.
+In the second stage, the neuron which has the shortest distance with the presented input vector is updated along with its neighbor neurons.
+This neuron is called the best matching unit (BMU).
+The goal of the learning process is to minimize the neighborhood distance in the output clusters.
+
+When the learning process is done a visual representation method like the Unified Distance Matrix, or U-matrix for short, is used to visualize the distances between neurons in the output space.
+In the U-matrix, the distance between adjacent neurons is measured and assigned different colors.
+Dark colors between neurons indicate large distances (boundaries) while light colors represent similar areas (clusters).
+
+%---
+
 %FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?

### 2016-04-24 paper.tex
addressing some comments + removing others + SoA-first-paragraph

@@
 
-%***TO DO***: complete this considering the new contents and results\\
-% Instead of just writing this you should say what has changed and
-% what should be changed. For instance, the paragraph below probably
-% shouldn't - JJ 
 Publishing a book, in the same way as releasing any other cultural product with a
-physical substrate, implies several
-types of risks and costs due to
+physical substrate, implies several types of risks and costs due to
 the complexity, and derived expenses, of the production,
@@
 subjective. Even if it is a known author or topic, having accurate
-estimations of future sales of the new 
-product is extremely important \cite{ChingChin2010}, so that production
-runs do not exceed predicted sales by too much. 
+estimations of future sales of the new product is extremely important, so 
+that production runs do not exceed predicted sales by too much. 
 Indeed, several studies have demonstrated that improving sales predictions 
 (a reduction of forecasting errors) results in an enhancement in the 
-%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
-production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
-%which should be obvious from the get go, don't know why you need 4
-%papers to affirm that - JJ
-%please someone address this - JJ
+production process \cite{Fildes2010,Saeed2008}.
 
@@
 lead to losses and sunk inventory cost, 
-% Antonio - 'sunk inventory cost' es corecto?
-% Sí, pero corecto no lo es. - JJ
 whereas if the number of printed copies was not enough, a new print
@@
 
-% [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
-%  por eso quiero comenzar hablando de la aplicación de métodos
-%  de predicción en la industria en general, que sí hay bastante bibliografía.
-% Antonio - me parece bien
-
-% Antonio - Cosas generales a mejorar en el SotA:
-% - habría que comparar más veces este trabajo con lo que hacen otros, destacando nuestras diferencias. Sólo se menciona al final de la sección
-% - habría que destacar claramente ls aportes de este trabajo al SotA, cómo hace que avance ;)
-% - habría que incluir citas a artículos de la revista que elijamos y comentarlos aquí
-
-% Sales forecasting is a problem which has been addressed several times
-% in the literature.
-% This sentence is useless
-In the past, sales prediction has been performed using methods such as  regression models
-\cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy 
-systems \cite{Mastorocostas2001}, applied to different industrial
-sectors. 
-% ¿Y qué? Esta frase
-% no aporta nada. La primera frase
-% tiene que enmarcar el estado del
-% arte - JJ
-% Antonio - la he intentado mejorar.
-% Muchas cosas de la intro tendrían que venir aquí, al estado del
-% arte. Habría que reescribir la intro. - JJ
-% ¿Qué usan esos métodos? - JJ
+As far as we know, no previous attempt can be found in the literature in which 
+prediction methods have been applied to estimate the print run. 
+However, similar techniques to those proposed in this paper, e.g. 
+regression models \cite{Papalexopoulos1990}, 
+neural networks \cite{Yoo1999} 
+or fuzzy systems \cite{Mastorocostas2001}, 
+have been applied to solve sales prediction problems in other industrial sectors.
 
@@
 experience, and their perception about trends, could make decisions on
-the companies production (how many books should be printed when a new
-book is published). 
-%FERGU: quitad los paréntesis :)
-% Fergu: quítalos tú, tío, aquí puede editar todo el mundo - JJ
+the companies production, i.e. how many books should be printed when a new
+book is published. 
 This is a complex problem, since the predictions are influenced by

### 2016-04-24 paper.tex
improving introduction: Closes #6

@@
 achieve, in order to optimise production schedules, improve the publishing
-company profits or minimise losses \cite{Zhao2001}. This is the main
-objective of this paper. 
-%FERGU: entonces el objetivo es desarrollar una herramienta? La
-%metodología? Dejarlo más claro en todos los sitios
-% Un método predictivo. Lo deja muy claro - JJ
-An example is the optimisation of sales \cite{Mattila2002} by
+company profits or minimise losses \cite{Zhao2001}, 
+being this the main objective of this paper: optimizing sales and
 improving profit margins by selling the whole print-run.
-% Antonio - podrías extender un poco el ejemplo? Es decir, describir
-% un poco más lo que se hace en ese trabajo. ;)
-% An example of what? Does that go there or to the state of the art? - JJ
-
-The accuracy of the predictive method we intend to design is affected
+
+In any case, the accuracy of the predictive method we intend to design is affected
 negatively by several factors, related to decisions on purchases, to freight 

### 2016-04-24 paper.tex
improving introduction: Closes #16
removing some old-comments in the introduction: Closes #18
improving the SoA: Closes #15

@@
 negatively by several factors, related to decisions on purchases, to freight 
-traffic, or with the distribution strategy \cite{Little1998}. % This
-                                % paragraph is rather useless - JJ
-% I have changed the paragraph completely, but still don't know what
-% this is doing here - JJ
-
+traffic, or with the distribution strategy \cite{Little1998}.
 Thus, it is very important to know the product and the variables that
-might affect the sales, and how an expert manager takes them into account \cite{Armstrong2001,SThomassey2014}. 
-                                % ¿Esto también pasa en la industria de la
-                                % moda. ¿Qué vamos a usar de esto? - JJ
-                                % [Pedro] esto iba referido a la Industria Editorial.
+might affect the sales, and how an expert manager takes them into 
+account \cite{Armstrong2001,SThomassey2014}. 
 Their impact is difficult to estimate and it is not constant over time, 
@@
 In addition, some may have correlations between them. 
-%FERGU: some ... variables, no?
 However, these correlations can be detected using data analysis methods, 
@@
 of data is quite large, and even, different experts can reach different
-predictions from the same dataset \cite{ChingChin2010,Sanders1994}. A
+predictions from the same dataset \cite{Sanders1994}. A
 initial version of this method was developed under contract with that
@@
 them are categorical, which makes them harder to process, even more so if the number
-of categories is high. Given these issues, finding adequate
-forecasting techniques and selecting  
-the best method to use is also a problem \cite{ChingChin2010}. % Qualify this citation - jj
-% And it's the 3rd time you cite ChingChin!!! - JJ
+of categories is high. As stated in those works, given these issues, finding adequate
+forecasting techniques and selecting the best method to use is also a problem.
 

### 2016-04-24 paper.tex
clarifying some details in SoA: Closes #12

@@
 most suitable for this task \cite{ChingChin2010}. And they cannot be
-applied before the book is published, as is the objective of this
-paper.
+applied before the book is published, as is the objective of this paper.
 
@@
 forecasting techniques and selecting the best method to use is also a problem.
-
-% Thus, not any time-series forecasting method can be used
-% \cite{Madsen2008,ChernWSF15}. 
-% Qualify those references!!! What do they say?
 
@@
 seasonality, promotions or fashions that expert managers might
-subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
+subjectively apply \cite{Lapide1999,ChernWSF15}. % This
                                 % has something to do with the

### 2016-04-26 paper.tex
Had made some changes

--- 2016-04-24 paper.tex
@@
 \usepackage{url}
-\usepackage{appendix}
 
@@
 
+%***TO DO***: complete this considering the new contents and results\\
+% Instead of just writing this you should say what has changed and
+% what should be changed. For instance, the paragraph below probably
+% shouldn't - JJ 
 Publishing a book, in the same way as releasing any other cultural product with a
-physical substrate, implies several types of risks and costs due to
+physical substrate, implies several
+types of risks and costs due to
 the complexity, and derived expenses, of the production,
@@
 subjective. Even if it is a known author or topic, having accurate
-estimations of future sales of the new product is extremely important, so 
-that production runs do not exceed predicted sales by too much. 
+estimations of future sales of the new 
+product is extremely important \cite{ChingChin2010}, so that production
+runs do not exceed predicted sales by too much. 
 Indeed, several studies have demonstrated that improving sales predictions 
 (a reduction of forecasting errors) results in an enhancement in the 
-production process \cite{Fildes2010,Saeed2008}.
+%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
+production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
+%which should be obvious from the get go, don't know why you need 4
+%papers to affirm that - JJ
+%please someone address this - JJ
 
@@
 lead to losses and sunk inventory cost, 
+% Antonio - 'sunk inventory cost' es corecto?
+% Sí, pero corecto no lo es. - JJ
 whereas if the number of printed copies was not enough, a new print
@@
 achieve, in order to optimise production schedules, improve the publishing
-company profits or minimise losses \cite{Zhao2001}, 
-being this the main objective of this paper: optimizing sales and
+company profits or minimise losses \cite{Zhao2001}. This is the main
+objective of this paper. 
+%FERGU: entonces el objetivo es desarrollar una herramienta? La
+%metodología? Dejarlo más claro en todos los sitios
+% Un método predictivo. Lo deja muy claro - JJ
+An example is the optimisation of sales \cite{Mattila2002} by
 improving profit margins by selling the whole print-run. 
-
-In any case, the accuracy of the predictive method we intend to design is affected
+% Antonio - podrías extender un poco el ejemplo? Es decir, describir
+% un poco más lo que se hace en ese trabajo. ;)
+% An example of what? Does that go there or to the state of the art? - JJ
+
+The accuracy of the predictive method we intend to design is affected
 negatively by several factors, related to decisions on purchases, to freight 
@@
 
+% We should also mention what data we actually mean, I don't think
+% we've published it here. - JJ
+
 With this issue in mind, in this paper a data visualisation and
@@
 
-As far as we know, no previous attempt can be found in the literature in which 
-prediction methods have been applied to estimate the print run. 
-However, similar techniques to those proposed in this paper, e.g. 
-regression models \cite{Papalexopoulos1990}, 
-neural networks \cite{Yoo1999} 
-or fuzzy systems \cite{Mastorocostas2001}, 
-have been applied to solve sales prediction problems in other industrial sectors.
+% [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
+%  por eso quiero comenzar hablando de la aplicación de métodos
+%  de predicción en la industria en general, que sí hay bastante bibliografía.
+% Antonio - me parece bien
+
+% Antonio - Cosas generales a mejorar en el SotA:
+% - habría que comparar más veces este trabajo con lo que hacen otros, destacando nuestras diferencias. Sólo se menciona al final de la sección
+% - habría que destacar claramente ls aportes de este trabajo al SotA, cómo hace que avance ;)
+% - habría que incluir citas a artículos de la revista que elijamos y comentarlos aquí
+
+% Sales forecasting is a problem which has been addressed several times
+% in the literature.
+% This sentence is useless
+In the past, sales prediction has been performed using methods such as  regression models
+\cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy 
+systems \cite{Mastorocostas2001}, applied to different industrial
+sectors. 
+% ¿Y qué? Esta frase
+% no aporta nada. La primera frase
+% tiene que enmarcar el estado del
+% arte - JJ
+% Antonio - la he intentado mejorar.
+% Muchas cosas de la intro tendrían que venir aquí, al estado del
+% arte. Habría que reescribir la intro. - JJ
+% ¿Qué usan esos métodos? - JJ
 
@@
 experience, and their perception about trends, could make decisions on
-the companies production, i.e. how many books should be printed when a new
-book is published. 
+the companies production (how many books should be printed when a new
+book is published). 
+%FERGU: quitad los paréntesis :)
+% Fergu: quítalos tú, tío, aquí puede editar todo el mundo - JJ
 This is a complex problem, since the predictions are influenced by
@@
 
-%--- new SOM description % -Sam
-
-SOM is a type of unsupervised neural networks inspired by the topographical organization of the sensory cortex of human brain \cite{kohonen1998}.
-It maps highly dimensional data into a lower dimensional space where similar data patterns are located in more adjacent areas on the grid.
-
-SOM is a very useful analysis tool for visualizing complex data with high number of variables in a simple geometric planes.
-Therefore, it could be used for different tasks like features reduction and data clustering and visualization.
-
-Basically, SOM consists of two layers; input layer and output layer (also known as Kohen layer).
-Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e.; units).
-This means that every neuron is linked to every input in the input layer.
-
-The learning process of SOM is an iterative process applied in two stages.
-First, the weights of the network are initialized randomly then the n-dimensional input vectors are presented to the network sequentially so the distance between the weights of the neurons and the inputs are computed using the simple Euclidean distance.
-In the second stage, the neuron which has the shortest distance with the presented input vector is updated along with its neighbor neurons.
-This neuron is called the best matching unit (BMU).
-The goal of the learning process is to minimize the neighborhood distance in the output clusters.
-
-When the learning process is done a visual representation method like the Unified Distance Matrix, or U-matrix for short, is used to visualize the distances between neurons in the output space.
-In the U-matrix, the distance between adjacent neurons is measured and assigned different colors.
-Dark colors between neurons indicate large distances (boundaries) while light colors represent similar areas (clusters).
-
-%---
-
+Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that
+uses an unsupervised training algorithm and which, through a process
+called self-organisation, configures the output units into a
+topological representation of the original data. It tries to imitate
+the self-organisation done in the sensory cortex of the human brain,
+where neighbouring neurons are activated by similar stimulus. SOM
+belongs to a general class of neural network methods, which are
+non-linear regression techniques that can be trained to learn or find
+relationships between inputs and outputs or to organise data so as to
+disclose so far unknown patterns or structures. It is usually used as
+a clustering/classification tool or used to find unknown relationships
+between a set of variables that describe a problem. The main property
+of the SOM is that it makes a nonlinear projection from a
+high-dimensional data space (one dimension per variable) on a regular,
+low-dimensional (usually 2D) grid of neurons, called units. 
+SOM is further processed using Ultsch method \cite{UmatUlts}, the
+Unified distance matrix (U-matrix), which uses SOM's codevectors
+(vectors of variables of the problem) as data source and generates a
+matrix where each component is a distance measure between two adjacent
+neurons. It allows us to visualise any multi-variated dataset in a
+two-dimensional display, so we can detect topological relations among
+neurons and infer about the input data structure. High values in the
+U-matrix represent a frontier region between clusters, and low values
+represent a high degree of similarities among neurons on that region,
+clusters .
+
+SOMs (and U-Matrix) are usually applied to visualise natural
+structures in the data and their relations, as well as the natural
+groupings that could be among them. In addition, SOM makes easy the
+estimation of the variables that have more influence on these
+groupings. Other statistical and soft computing tools can also be used
+for this purpose, but since Kohonen's SOMs offers a visual way of
+doing it, it is much more intuitive, and takes advantage of the
+capabilities of the human brain as a pattern recogniser. 
 %FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
@@
 % And this is going to be useful because... - JJ
+% This is copied from the HIV paper. Please rephrase and adapt to the
+% particular venue - JJ
 
@@
 
-***TODO***: talking about the machines used
-
+%***TODO***: talking about the machines used
+% Please don't use real text for TODOs- JJ
 %Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
@@
 
-\subsection{Results for all the editors}
+\subsection{Results for all editors}
 \label{subsec:results_all_editors}
 
-In the first stage of the experiments, forecasting methods have been applied to the whole dataset.
-All the pre-sales features have been considered, including the categorical ones, which make it harder to process the instances and build the different models.
-SVM for instance, must previously transform these categories into binary variables in order to deal with the data, which means the creation of a different (and new) variable per each possible value.
-Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
+In the first experiment, forecasting methods have been applied to the
+whole dataset. All the pre-sales features have been considered, also
+including the categorical ones, which make harder to process the
+instances and build the different models. SVM for instance, must
+previously transform these categories into numbers in order to deal
+with the data, which means the creation of a different (and new)
+variable per possible value. Thus, in the case of editorial or
+collection this would imply the definition of hundreds of new
+variables. 
 % Antonio - Sam, verify this, please
-% Sam - reviewed and fixed
+% Sam is Hossam? - JJ
 
@@
 
-***TODO***: Revise and fix the following text...
+%***TODO***: Revise and fix the following text...
 
@@
 
-In the second stage of the experiments, different feature selection methods have been applied.
-The aim of these methods is to reduce the number of features considered in developing the forecasting models which consequently simplify the complexity of the models, improve their interpretability and decrease the training time.
-The simpler models generated after performing feature selection could give the decision maker a better insight on the underlying process by identifying the more influencing variables.
-
+In this second experiment, different feature selection processes have been applied.
+
+***TODO***: The aim of these techniques is to reduce the number of features to consider...
 % Antonio - TODO: explain the aim of FS in these experiments.
-% Sam : Done
 
@@
 Case 1-A: Developing prediction models to predict Total sales for
-Editorial704 (An editorial with the most number of different books sold) - 293
+Editor704 (An editor with the most number of different books sold) - 293
 instances.
@@
 \begin{table}
-\caption{Predicting Total sales for Editorial704}
+\caption{Predicting Total sales for Editor704}
 
@@
 Case 1-B: Developing prediction models to predict Total sales for
-Editorial-UDLU11 (An editorial with a medium number of different books sold) - 180 instances.
+Editor-UDLU11 (An editor with a medium number of different books sold) - 180
+instances.
 
 \begin{table}
-\caption{Predicting Total sales for Editorial-UDLU11}
+\caption{Predicting Total sales for Editor-UDLU11}
 
@@
 Case 2-A: Developing prediction models to predict Total sales for
-Editorial-UDL929 (The best selling editorial) - 216 instances.
+Editor-UDL929 (The best selling editor) - 216 instances.
 
 \begin{table}
-\caption{Predicting Total sales for Editorial-UDL929 (460752 sales) }
+\caption{Predicting Total sales for Editor-UDL929 (460752 sales) }
 
@@
 Case 2-B: Developing prediction models to predict Total sales for
-Editorial-UDLW12 (The median selling editor)- 97 instances.
+Editor-UDLW12 (The median selling editor)- 97 instances.
 
 \begin{table}
-\caption{Predicting Total sales for Editorial-UDLW12 (2635 sales) }
+\caption{Predicting Total sales for Editor-UDLW12 (2635 sales) }
 
@@
 
-***TO DO***: explain we have chosen the best Feature selection method (ReliefAttributeEval???). The rest of tables have been moved to an appendix.
+***TO DO***: choose the best Feature selection method and apply just this one (ReliefAttributeEval???). There are too many tables I think.
+We could add an appendix or so with the rest of results if you want.
 
 Case 1-A: Developing prediction models to predict Total sales for
-Editorial704 with ReliefFAttributeEval feature selection.
+Editor704 with ReliefFAttributeEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial704 (ReliefFAttributeEval-FS) }
+\caption{Predicting Total sales for Editor704 (ReliefFAttributeEval-FS) }
 \centering{}%
@@
 
-Case 1-B: Developing prediction models to predict Total sales for
-Editorial-UDLU11 with ReliefFAttributeEval feature selection
+Case 1-A: Developing prediction models to predict Total sales for
+Editor704 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLU11 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for Editor704 (CfsSubsetEval-FS)}
 
@@
 \hline 
-M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
-\hline 
-K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
-\hline 
-LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-A: Developing prediction models to predict Total sales for
-Editorial-UDL929 with ReliefFAttributeEval feature selection.
+M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
+\hline 
+K-NN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
+\hline 
+LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-A: Developing prediction models to predict Total sales for
+Editor704 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDL929 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for Editor704 (SOM-FS)}
 
@@
 \hline 
-M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
-\hline 
-LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-B: Developing prediction models to predict Total sales for
-Editorial-UDLW12 with ReliefFAttributeEval feature selection.
+M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
+\hline 
+K-NN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
+\hline 
+LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editor-UDLU11 with ReliefFAttributeEval feature selection
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLW12 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for Editor-UDLU11 (ReliefFAttributeEval-FS)}
 
@@
 \hline 
+M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
+\hline 
+K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
+\hline 
+LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editor-UDLU11 with CfsSubsetEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editor-UDLU11 (CfsSubsetEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+K-NN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 65.3 $\pm$0.19 & 685.56 $\pm$195.28 & 1021.37 $\pm$352.88 & 69.74 $\pm$16.96 & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
+\hline 
+LR & 67.0 $\pm$0.23\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 1-B: Developing prediction models to predict Total sales for
+Editor-UDLU11 with SOM feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editor-UDLU11 (SOM-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
+\hline 
+K-NN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.6 $\pm$0.08 & 446.25 $\pm$119.79 & 673.46 $\pm$189.06 & 45.38 $\pm$9.78 & 52.24 $\pm$13.09 & 0.0594 $\pm$0.0049\tabularnewline
+\hline 
+LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editor-UDL929 with ReliefFAttributeEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editor-UDL929 (ReliefFAttributeEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
+\hline 
+LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editor-UDL929 with CfsSubsetEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editor-UDL929 (CfsSubsetEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 88.0 $\pm$0.13 & 738.28 $\pm$188.53 & 1141.79 $\pm$472.025 & 45.45 $\pm$13.62 & 47.58 $\pm$24.84 & 0.017 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-A: Developing prediction models to predict Total sales for
+Editor-UDL929 with SOM feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editor-UDL929 (SOM-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 89.7 $\pm$0.10 & 685.67 $\pm$185.99 & 1116.42 $\pm$478.06 & 42.09 $\pm$12.8 & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
+\hline 
+K-NN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editor-UDLW12 with ReliefFAttributeEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editor-UDLW12 (ReliefFAttributeEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
 M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
@@
 SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editor-UDLW12 with CfsSubsetEval feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editor-UDLW12 (CfsSubsetEval-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 75.1 $\pm$0.26 & 15.61 $\pm$7.19 & 26.83 $\pm$13.36 & 47.38 $\pm$20.10 & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
+\hline 
+LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & 25.49 $\pm$11.63 & 47.97 $\pm$18.85 & 60.28 $\pm$30.62 & 0.0002 $\pm$0.0004\tabularnewline
+\hline 
+SVM & 81.8 $\pm$0.21 & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+\end{tabular}
+\end{table}
+
+Case 2-B: Developing prediction models to predict Total sales for
+Editor-UDLW12 with SOM feature selection.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for Editor-UDLW12 (SOM-FS)}
+
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 86.0 $\pm$0.19 & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
+\hline 
+K-NN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.5 $\pm$0.19 & 13.66 $\pm$6.47 & 22.51 $\pm$11.03 & 41.38 $\pm$17.87 & 52.20 $\pm$27.09 & 0.026 $\pm$0.0019\tabularnewline
+\hline 
+LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
 \hline 
@@
 
-%----------------------------------------------------------------------
-
-\appendix
-\section{APENDIX TABLES}
-
-Case 1-A: Developing prediction models to predict Total sales for
-Editorial704 with CfsSubsetEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editorial704 (CfsSubsetEval-FS)}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
-\hline 
-K-NN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
-\hline 
-LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 1-A: Developing prediction models to predict Total sales for
-Editorial704 with SOM feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editorial704 (SOM-FS)}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
-\hline 
-K-NN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
-\hline 
-LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-%-----------------------------------
-
-Case 1-B: Developing prediction models to predict Total sales for
-Editorial-UDLU11 with CfsSubsetEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLU11 (CfsSubsetEval-FS)}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
-\hline 
-K-NN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 65.3 $\pm$0.19 & 685.56 $\pm$195.28 & 1021.37 $\pm$352.88 & 69.74 $\pm$16.96 & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
-\hline 
-LR & 67.0 $\pm$0.23\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 1-B: Developing prediction models to predict Total sales for
-Editorial-UDLU11 with SOM feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLU11 (SOM-FS)}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
-\hline 
-K-NN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
-\hline 
-RF & 85.6 $\pm$0.08 & 446.25 $\pm$119.79 & 673.46 $\pm$189.06 & 45.38 $\pm$9.78 & 52.24 $\pm$13.09 & 0.0594 $\pm$0.0049\tabularnewline
-\hline 
-LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-%-----------------------------------
-
-Case 2-A: Developing prediction models to predict Total sales for
-Editorial-UDL929 with CfsSubsetEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDL929 (CfsSubsetEval-FS)}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 88.0 $\pm$0.13 & 738.28 $\pm$188.53 & 1141.79 $\pm$472.025 & 45.45 $\pm$13.62 & 47.58 $\pm$24.84 & 0.017 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
-\hline 
-LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-A: Developing prediction models to predict Total sales for
-Editorial-UDL929 with SOM feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDL929 (SOM-FS)}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 89.7 $\pm$0.10 & 685.67 $\pm$185.99 & 1116.42 $\pm$478.06 & 42.09 $\pm$12.8 & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
-\hline 
-K-NN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
-\hline 
-LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-%-----------------------------------
-
-Case 2-B: Developing prediction models to predict Total sales for
-Editorial-UDLW12 with CfsSubsetEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLW12 (CfsSubsetEval-FS)}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 75.1 $\pm$0.26 & 15.61 $\pm$7.19 & 26.83 $\pm$13.36 & 47.38 $\pm$20.10 & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
-\hline 
-LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & 25.49 $\pm$11.63 & 47.97 $\pm$18.85 & 60.28 $\pm$30.62 & 0.0002 $\pm$0.0004\tabularnewline
-\hline 
-SVM & 81.8 $\pm$0.21 & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-B: Developing prediction models to predict Total sales for
-Editorial-UDLW12 with SOM feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLW12 (SOM-FS)}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 86.0 $\pm$0.19 & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
-\hline 
-K-NN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
-\hline 
-RF & 85.5 $\pm$0.19 & 13.66 $\pm$6.47 & 22.51 $\pm$11.03 & 41.38 $\pm$17.87 & 52.20 $\pm$27.09 & 0.026 $\pm$0.0019\tabularnewline
-\hline 
-LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
 \end{document}

### 2016-04-26 paper.tex

--- 2016-04-24 paper.tex
@@
 
-\subsection{Results for all the editors}
+\subsection{Results for all editors}
 \label{subsec:results_all_editors}
 
-In the first stage of the experiments, forecasting methods have been applied to the whole dataset.
-All the pre-sales features have been considered, including the categorical ones, which make it harder to process the instances and build the different models.
-SVM for instance, must previously transform these categories into binary variables in order to deal with the data, which means the creation of a different (and new) variable per each possible value.
-Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
-% Antonio - Sam, verify this, please
-% Sam - reviewed and fixed
+In the first stage of the experiments, forecasting methods have been
+applied to the whole dataset. All the pre-sales features have been
+considered, including the categorical ones, which make it harder to
+process the instances and build the different models. SVM for
+instance, must previously transform these categories into binary
+variables in order to deal with the data, which means the creation of
+a different (and new) variable per each possible value. Thus, in the
+case of editorial or collection this would imply the definition of
+hundreds of new variables.
 
@@
 
-***TODO***: describe the parameters of SOM (size, neighbourhood shape, etc) and obtained quantisation and topographical errors.
+%***TODO***: describe the parameters of SOM (size, neighbourhood shape, etc) and obtained quantisation and topographical errors.
 
@@
 
-***TODO***: Justify the selected features by SOM (why have we chosen them?).
+%***TODO***: Justify the selected features by SOM (why have we chosen them?).
 
@@
 
-***TO DO***: comment the results
-
-***TO DO***: Think if including the graphs (scatter plots).
+%***TO DO***: comment the results
+
+%***TO DO***: Think if including the graphs (scatter plots).
 
@@
 
-***TO DO ***: Justify the special cases (why we have chosen them).
+%***TO DO ***: Justify the special cases (why we have chosen them).
 

### 2016-04-26 paper.tex
updating the experiments section
Adding description of special editorial cases

@@
 %***TODO***: talking about the machines used
+% Done - %---  Sam
 % Please don't use real text for TODOs- JJ
@@
 %(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.
+
+All experiments have been conducted on an  Intel(R) Core(TM) i5-2400 CPU at 3.10Ghz with a memory of 4 GB running Windows 7 professional 32bit operating system and Java JRE\_1.7.0\_72.
 
@@
 
-This section will present some experiments conducted on the data concerning four different example cases, namely:
+This section presents further experiments conducted on data concerning four interesting special editorial cases.
+These editorials were selected as representative cases which could be very interesting for decision makers and managers in the domain.
+The four cases are described as follows:
+
 \begin{itemize}
-    \item best seller editorial
-    \item medium seller editorial
-    \item best varied editorial
-    \item medium varied editorial
+    \item Best seller editorial: this case represents the editorial that sells the highest number of copies regardless the title of the books sold.
+Therefore, it is an example of a case on a higher business scale.
+    \item Medium seller editorial: this represents an editorial that sells medium number of copies compared to the other editorials (Medium business scale). 
+    \item Highest variation editorial: this is an example of an editorial that follows a strategy in publishing a very wide range of different titles.
+    \item Medium varied editorial: this case represents an editorial that has a median rank between the other editorial regarding the variety of titles sold.
 \end{itemize}
 
-%***TO DO ***: Justify the special cases (why we have chosen them).
-
-Table XX shows the details of each of these editorials.
+Table \ref{Table:special_cases} shows the details of each of the selected editorials.
 
@@
 \end{tabular}
+\label{Table:special_cases}
 \end{table}

### 2016-04-26 paper.tex
Describing the experiments of the special cases

@@
 %
-%\begin{figure*}[http] 
-%\begin{center} 
-%\begin{tabular}{ccc}
-%\includegraphics[scale=0.22]{m5p.eps}  &
-%\includegraphics[scale=0.22]{lr.eps}   &
-%\includegraphics[scale=0.22]{svm.eps}  \\
-%M5P & LR & SVM 
-%\end{tabular}
-%\begin{tabular}{cc}
-%\includegraphics[scale=0.22]{knn.eps}  &
-%\includegraphics[scale=0.22]{mlp.eps}  \\
-%k-NN & MLP
-%\end{tabular}
-%\end{center} 
-%\caption{Actual vs. predicted sales for M5P, LR, SVM, k-NN, MLP
-%  models.}
-% You should use a log-log scale here to see it more clearly. Besides,
-% please say in a comment the script you are using to generate it, we
-% are going to need it later on - JJ
-%\label{conv2}
-%\end{figure*}
-%
-%
-%\begin{figure*}[http] 
-%\begin{center} 
-%\begin{tabular}{ccc}
-%\includegraphics[scale=0.22]{m5p_RAE.eps}  &
-%\includegraphics[scale=0.22]{lr_RAE.eps}   &
-%\includegraphics[scale=0.22]{svm_RAE.eps}  \\
-%M5P & LR & SVM 
-%\end{tabular}
-%\begin{tabular}{cc}
-%\includegraphics[scale=0.22]{knn_RAE.eps}  &
-%\includegraphics[scale=0.22]{mlp_RAE.eps}  \\
-%k-NN & MLP
-%\end{tabular}
-%\end{center} 
-%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
-%\label{conv2ReliefAttributeEval}
-%\end{figure*}
-%
-%
-%\begin{figure*}[http] 
-%\begin{center} 
-%\begin{tabular}{ccc}
-%\includegraphics[scale=0.22]{m5p_CFS.eps}  &
-%\includegraphics[scale=0.22]{lr_CFS.eps}   &
-%\includegraphics[scale=0.22]{svm_CFS.eps}  \\
-%M5P & LR & SVM 
-%\end{tabular}
-%\begin{tabular}{cc}
-%\includegraphics[scale=0.22]{knn_CFS.eps}  &
-%\includegraphics[scale=0.22]{mlp_CFS.eps}  \\
-%k-NN & MLP
-%\end{tabular}
-%\end{center} 
-%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
-%\label{conv2CfsSubsetEval}
-%\end{figure*}
-%
-%
-%\begin{figure*}[http] 
-%\begin{center} 
-%\begin{tabular}{ccc}
-%\includegraphics[scale=0.22]{m5p_SOM.eps}  &
-%\includegraphics[scale=0.22]{lr_SOM.eps}   &
-%\includegraphics[scale=0.22]{svm_SOM.eps}  \\
-%M5P & LR & SVM 
-%\end{tabular}
-%\begin{tabular}{cc}
-%\includegraphics[scale=0.22]{knn_SOM.eps}  &
-%\includegraphics[scale=0.22]{mlp_SOM.eps}  \\
-%k-NN & MLP
-%\end{tabular}
-%\end{center} 
-%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
-%\label{conv2SOM}
-%\end{figure*}
-
-%\begin{figure}[!ht] 
-%\begin{center}
-%  \epsfig{file=fig_time.eps,width=11cm}
-%\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one).
-Plot shows that using categorical variables as part of the dataset makes the problem hard to solve.
-As expected, simpler methods are much faster to build the model than the complex ones.}}
-%\label{fig:time}
-%\end{center}
-%\end{figure}
-
-%\begin{figure}[!ht] 
-%\begin{center}
-%  \epsfig{file=fig_rae.eps,width=11cm}
-%\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one).
-The M5P model obtains the lowest errors, whatever the dataset used.}}
-%\label{fig:rae}
-%\end{center}
-%\end{figure}
 
@@
 
-\section{Example Cases}
+\section{Experiments of special editorial cases}
 \label{example_cases}
@@
 
-Table \ref{Table:special_cases} shows the details of each of the selected editorials.
+Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected editorials.
 
@@
 
-%--------------------------------------------------------------------------
-
-\subsection{Sales forecasting with all pre-sales features}
-\label{subsec:case_sales_all_features}
+The experiments applied on the selected special cases follow the same methodology used previously for the whole dataset.
+First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (ReliefAttributeEval, CfsSubsetEval and SOM) are used to reduce the features in each case.
+Finally, the classification models are applied again on the reduce datasets to evaluate their performance.
 
@@
 \caption{Predicting Total sales for Editorial704}
-
 \centering{}%
@@
 \caption{Predicting Total sales for Editorial-UDLU11}
-
 \centering{}%
@@
 \caption{Predicting Total sales for Editorial-UDL929 (460752 sales) }
-
 \centering{}%
@@
 \caption{Predicting Total sales for Editorial-UDLW12 (2635 sales) }
-
 \centering{}%
@@
 
-\subsection{Sales forecasting with feature selection}
-\label{subsec:case_sales_feature_selection}
+%\subsection{Sales forecasting with feature selection}
+%\label{subsec:case_sales_feature_selection}
 

### 2016-04-26 paper.tex
updating the experiments section

@@
 \centering{}%
-\begin{tabular}{|r|l|l|l|}
-\hline 
- & Different books sold & Total copies sold & Description\\
+\begin{tabular}{|c|l|l|l|}
+\hline 
+ Case & Different books sold & Total copies sold & Description\\
 \hline 
 \textit{All editorials} & 6083 & 3201645 & 209 editorials\\
+\hline 
+\textit{UDL929} & 216 & 460752 & Best selling editorial\\
+\hline 
+\textit{UDLW12} & 97 & 2635 & Medium selling editorial\\
 \hline 
@@
 \hline
-\textit{UDL929} & 216 & 460752 & Best selling editorial\\
-\hline 
-\textit{UDLW12} & 97 & 2635 & Medium selling editorial\\
-\hline 
+
 \end{tabular}
@@
 The experiments applied on the selected special cases follow the same methodology used previously for the whole dataset.
-First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (ReliefAttributeEval, CfsSubsetEval and SOM) are used to reduce the features in each case.
-Finally, the classification models are applied again on the reduce datasets to evaluate their performance.
-
-Case 1-A: Developing prediction models to predict Total sales for
-Editorial704 (An editorial with the most number of different books sold) - 293
-instances.
+First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (ReliefAttributeEval, CfsSubsetEval and SOM) are used to reduce the set of features in each case.
+Finally, the classification models are applied again on the reduced datasets to evaluate their performance.
+
+Evaluation results of the developed models (without performing any feature selection method) for the selected four cases are shown in Table \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
 
 \begin{table}
-\caption{Predicting Total sales for Editorial704}
+\caption{Predicting Total sales for Editorial-UDL929 (The best selling editorial) }
 \centering{}%
@@
 \hline 
+M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
+\hline 
+K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
+\hline 
+RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
+\hline 
+LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
+\hline 
+\end{tabular}
+\label{Table:case1results}
+\end{table}
+
+\begin{table}
+\caption{Predicting Total sales for Editorial-UDLW12 (The median selling editorial) }
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
+\hline 
+K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
+\hline 
+LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
+\hline 
+SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
+\hline 
+\end{tabular}
+\label{Table:case2results}
+\end{table}
+
+\begin{table}
+\caption{Predicting Total sales for Editorial704 (highest number of different titles sold)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+\hline 
 M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
@@
 \end{tabular}
-\end{table}
-
-Case 1-B: Developing prediction models to predict Total sales for
-Editorial-UDLU11 (An editorial with a medium number of different books sold) - 180 instances.
+\label{Table:case3results}
+\end{table}
 
 \begin{table}
-\caption{Predicting Total sales for Editorial-UDLU11}
+\caption{Predicting Total sales for Editorial-UDLU11 (medium number of different books sold))}
 \centering{}%
@@
 \end{tabular}
-\end{table}
-
-Case 2-A: Developing prediction models to predict Total sales for
-Editorial-UDL929 (The best selling editorial) - 216 instances.
-
-\begin{table}
-\caption{Predicting Total sales for Editorial-UDL929 (460752 sales) }
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
-\hline 
-K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
-\hline 
-RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
-\hline 
-LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
-\hline 
-SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-B: Developing prediction models to predict Total sales for
-Editorial-UDLW12 (The median selling editor)- 97 instances.
-
-\begin{table}
-\caption{Predicting Total sales for Editorial-UDLW12 (2635 sales) }
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
-\hline 
-K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
-\hline 
-LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
-\hline 
-SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
-\hline 
-\end{tabular}
+\label{Table:case4results}
 \end{table}

### 2016-04-27 paper.tex
Fixing a few things

@@
 
-SOM is a type of unsupervised neural networks inspired by the topographical organization of the sensory cortex of human brain \cite{kohonen1998}.
+SOM is a type of unsupervised neural network inspired by the topographical organization of the sensory cortex of human brain \cite{kohonen1998}.
 It maps highly dimensional data into a lower dimensional space where similar data patterns are located in more adjacent areas on the grid.
-
-SOM is a very useful analysis tool for visualizing complex data with high number of variables in a simple geometric planes.
-Therefore, it could be used for different tasks like features reduction and data clustering and visualization.
+It is a very useful analysis tool for visualizing complex data with high number of variables in a simple geometric plane.
+Therefore, it could be used for different tasks such as feature selection and data clustering and visualization.
 
 Basically, SOM consists of two layers; input layer and output layer (also known as Kohen layer).
-Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e.; units).
+Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e.
+units).
 This means that every neuron is linked to every input in the input layer.

### 2016-04-28 paper.tex
Assigning TODOS

@@
 
-%***TODO***: talking about the machines used
-% Done - %---  Sam
-% Please don't use real text for TODOs- JJ
-%Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
-%(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.
-
 All experiments have been conducted on an  Intel(R) Core(TM) i5-2400 CPU at 3.10Ghz with a memory of 4 GB running Windows 7 professional 32bit operating system and Java JRE\_1.7.0\_72.
@@
 
-As far as the different methods is concerned, M5P model obtained good results, 
+As far as the different methods are concerned, M5P model obtained good results, 
 both in time and error, and as stated before, this method can learn and tackle 
@@
 
-% Antonio - TODO: explain the aim of FS in these experiments.
-% Sam : Done
-
 We have used both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.
@@
 
-%***TODO***: describe the parameters of SOM (size, neighbourhood shape, etc) and obtained quantisation and topographical errors.
-
-% The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data.
+The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data.
 The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.
@@
 %***TODO***: Justify the selected features by SOM (why have we chosen them?).
+% Sam will do it
 
@@
 %***TO DO***: comment the results
+% Sam will do it - JJ
 
@@
 
-***TO DO***: explain we have chosen the best Feature selection method (ReliefAttributeEval???). The rest of tables have been moved to an appendix.
+%***TO DO***: explain we have chosen the best Feature selection method (ReliefAttributeEval???). The rest of tables have been moved to an appendix.
+%Sam will do it - JJ
 
@@
 
-***TO DO:*** better explain this
-
-We have considered the best seller editorial as a good example case to show.
+%***TO DO:*** better explain this
+% Sam will do it
+
+We have considered the publisher that sells the most as a good example case to show.
 
@@
 
-***TO DO***: better justify this\\
+%***TO DO***: better justify this\\
 
@@
 
-***TO DO***: comments on the figure\\
+%***TO DO***: comments on the figure\\
 
@@
 
-***TO DO***: rewrite these conclusions with the new experiments, examples and results\\
+%***TO DO***: rewrite these conclusions with the new experiments, examples and results\\
 

### 2016-04-28 paper.tex
Commenting out comments
References #23. All text-written editorial words are changed to publishing house, and editor is publisher now

@@
 subject3
-editorial
+publisher
 collection
@@
 
-First, after the editorial company has provided the raw data
+First, after the publishing house has provided the raw data
 (extracted directly from its database), a preprocessing method has
@@
 Moreover, the application of FS also aims to reduce the computational time for building the forecasting models, along with the complexity of the obtained models themselves.
-This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (editors).
+This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).
 
@@
 
-Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (editorials) in order to prove the value of the proposal.
+Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing houses) in order to prove the value of the proposal.
 Some specific interpretable models have been created as a final result of the work.
@@
 2 & main subject (code) & \texttt{subject1} & numerical & input\\
-3 &  editorial + collection (joint code) & \texttt{collection} & categorical & input\\
+3 &  publisher + collection (joint code) & \texttt{collection} & categorical & input\\
 4 & bookbinding (code) & \texttt{binding} & categorical & input\\
@@
 As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods.
-\texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by an editor.
+\texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
 In addition, this variable could be interesting to be used to test the prediction model, once it is built.
-So the editor could try different values for it and see what the predictor yields, in order to take the best decision.
+So the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
 
@@
 
-Regarding the feature \textit{editorial}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
-In addition, we think it is not really relevant for the accuracy of the models and, moreover, editors will not consider the results in other editorials for predicting its own sales.
+Regarding the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
+In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing houses for predicting its own sales.
 % Antonio - Think about this... should we mention this?
 
-Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the editor, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass.
+Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass.
 So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance.
@@
 
-We have analysed the whole dataset (all the editorials), but also performed some experiments considering specific editorials as example cases.
-The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for editors.
+We have analysed the whole dataset (all the publishing houses), but also performed some experiments considering specific publishing houses as example cases.
+The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for publishers.
 
@@
 
-\subsection{Results for all editors}
-\label{subsec:results_all_editors}
+\subsection{Results for all publishers}
+\label{subsec:results_all_publishers}
 
@@
 a different (and new) variable per each possible value. Thus, in the
-case of editorial or collection this would imply the definition of
+case of \emph{publisher} or \emph{collection} this would imply the definition of
 hundreds of new variables.
 
-Correlation coefficient, error measures and time to build the model have been computed for every method. Obtained results are presented in Table \ref{tab:all_editors_no_fs}.
+Correlation coefficient, error measures and time to build the model have been computed for every method. Obtained results are presented in Table \ref{tab:all_publishers_no_fs}.
 
 \begin{table}
-\caption{Predicting Total sales for all editors (all the features). 30 repetitions, 10-fold cross validation.
-\label{tab:all_editors_no_fs}}
+\caption{Predicting Total sales for all publishers (all the features). 30 repetitions, 10-fold cross validation.
+\label{tab:all_publishers_no_fs}}
 \centering{}%
@@
 Moreover, in these experiments it has been seen the difficulty to process 
-information related to categorical variables, such as \emph{editorial} and 
+information related to categorical variables, such as \emph{publisher} and 
 \emph{collection}.
@@
 Then, the dataset has been projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
-An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features Editorial and Collection have been
+An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features \emph{publisher} and \emph{collection} have been
 removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
@@
 
-Thus, we have run the same experiments as in Section \ref{subsec:results_all_editors} with the whole dataset (all the editors), but considering the selected features by each method.
+Thus, we have run the same experiments as in Section \ref{subsec:results_all_publishers} with the whole dataset (all the publishers), but considering the selected features by each method.
 The results are shown in Table
@@
 \centering{}%
-\caption{Predicting Total sales for all editors based on features selected
+\caption{Predicting Total sales for all publishers based on features selected
 by each method.
-\label{tab:results_all_editors_fs}}
+\label{tab:results_all_publishers_fs}}
 
@@
 
-\section{Experiments of special editorial cases}
+\section{Experiments of special publishing houses cases}
 \label{example_cases}
 
-This section presents further experiments conducted on data concerning four interesting special editorial cases.
-These editorials were selected as representative cases which could be very interesting for decision makers and managers in the domain.
+This section presents further experiments conducted on data concerning four interesting special publishing house cases.
+These publishing houses were selected as representative cases which could be very interesting for decision makers and managers in the domain.
 The four cases are described as follows:
@@
 \begin{itemize}
-    \item Best seller editorial: this case represents the editorial that sells the highest number of copies regardless the title of the books sold.
+    \item Best seller publishing house: this case represents the publishing house that sells the highest number of copies regardless the title of the books sold.
 Therefore, it is an example of a case on a higher business scale.
-    \item Medium seller editorial: this represents an editorial that sells medium number of copies compared to the other editorials (Medium business scale). 
-    \item Highest variation editorial: this is an example of an editorial that follows a strategy in publishing a very wide range of different titles.
-    \item Medium varied editorial: this case represents an editorial that has a median rank between the other editorial regarding the variety of titles sold.
+    \item Medium seller publishing house: this represents an publishing house that sells medium number of copies compared to the other publishing houses (Medium business scale). 
+    \item Highest variation publishing house: this is an example of an publishing house that follows a strategy in publishing a very wide range of different titles.
+    \item Medium varied publishing house: this case represents an publishing house that has a median rank between the other publishing house regarding the variety of titles sold.
 \end{itemize}
 
-Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected editorials.
+Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected publishing houses.
 
 \begin{table}
-\caption{Description of editorials considered as special cases.
-\label{tab:desc_editorials}}
+\caption{Description of publishing houses considered as special cases.
+\label{tab:desc_publishing houses}}
 \centering{}%
@@
 \hline 
-\textit{All editorials} & 6083 & 3201645 & 209 editorials\\
-\hline 
-\textit{UDL929} & 216 & 460752 & Best selling editorial\\
-\hline 
-\textit{UDLW12} & 97 & 2635 & Medium selling editorial\\
-\hline 
-\textit{UDL704} & 293 & 58236 & Editorial with most different\\ 
+\textit{All publishing houses} & 6083 & 3201645 & 209 publishing houses\\
+\hline 
+\textit{UDL929} & 216 & 460752 & Best selling publishing house\\
+\hline 
+\textit{UDLW12} & 97 & 2635 & Medium selling publishing house\\
+\hline 
+\textit{UDL704} & 293 & 58236 & Publishing house with most different\\ 
        &     &       & books sold\\
 \hline 
-\textit{UDLU11} & 180 & 249481 & Editorial with medium number\\ 
+\textit{UDLU11} & 180 & 249481 & Publishing house with medium number\\ 
        &     &       &  of different books sold\\
@@
 \begin{table}
-\caption{Predicting Total sales for Editorial-UDL929 (The best selling editorial) }
+\caption{Predicting Total sales for PublishingHouse-UDL929 (The best selling publishing house) }
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for Editorial-UDLW12 (The median selling editorial) }
+\caption{Predicting Total sales for PublishingHouse-UDLW12 (The median selling publishing house) }
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for Editorial704 (highest number of different titles sold)}
+\caption{Predicting Total sales for PublishingHouse704 (highest number of different titles sold)}
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for Editorial-UDLU11 (medium number of different books sold))}
+\caption{Predicting Total sales for PublishingHouse-UDLU11 (medium number of different books sold))}
 \centering{}%
@@
 Case 1-A: Developing prediction models to predict Total sales for
-Editorial704 with ReliefFAttributeEval feature selection.
+PublishingHouse704 with ReliefFAttributeEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial704 (ReliefFAttributeEval-FS) }
+\caption{Predicting Total sales for PublishingHouse704 (ReliefFAttributeEval-FS) }
 \centering{}%
@@
 Case 1-B: Developing prediction models to predict Total sales for
-Editorial-UDLU11 with ReliefFAttributeEval feature selection
+PublishingHouse-UDLU11 with ReliefFAttributeEval feature selection
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLU11 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDLU11 (ReliefFAttributeEval-FS)}
 
@@
 Case 2-A: Developing prediction models to predict Total sales for
-Editorial-UDL929 with ReliefFAttributeEval feature selection.
+PublishingHouse-UDL929 with ReliefFAttributeEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDL929 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDL929 (ReliefFAttributeEval-FS)}
 
@@
 Case 2-B: Developing prediction models to predict Total sales for
-Editorial-UDLW12 with ReliefFAttributeEval feature selection.
+PublishingHouse-UDLW12 with ReliefFAttributeEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLW12 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDLW12 (ReliefFAttributeEval-FS)}
 
@@
 
-In this section we show the output of one of the models built during the regression, namely we present one of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate an useful decision-aid tool for and expert (editor) to see what sales can be expected for the different values of the input variables (including the print-run).
+In this section we show the output of one of the models built during the regression, namely we present one of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate an useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).
 
@@
 
-Figure \ref{fig:decision_tree_best_seller} depicts the obtained decision tree for the best seller editorial (UDL929).
+Figure \ref{fig:decision_tree_best_seller} depicts the obtained decision tree for the best seller publishing house (UDL929).
 The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales.
@@
   \epsfig{file=decision_tree_no_fs.eps,width=12cm}
-\caption{Decision Tree built by the M5P method for the best seller editorial with all the pre-sales features.}
+\caption{Decision Tree built by the M5P method for the best seller publishing house with all the pre-sales features.}
 \label{fig:decision_tree_best_seller}
@@
 
-***TO DO***: comments on the figure\\
-
-Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same editorial (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).
+%***TO DO***: comments on the figure\\
+
+Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same publishing house (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).
 
@@
   \epsfig{file=decision_tree_fs.eps,width=12cm}
-\caption{Decision Tree built by the M5P method for the best seller editorial with the features selected by the ReliefAttributeEval method.}
+\caption{Decision Tree built by the M5P method for the best seller publishing house with the features selected by the ReliefAttributeEval method.}
 \label{fig:decision_tree_best_seller_fs}
@@
 soft-computing standard techniques to solve a new challenging problem.
-Moreover, proposed method could be implemented, not only in the editorial 
+Moreover, proposed method could be implemented, not only in the publishing 
 industry, but also in other domains where the specificity of products is similar, 

### 2016-04-28 paper.tex
References #23. Sorry, I missed some T_T

@@
 Case 1-A: Developing prediction models to predict Total sales for
-Editorial704 with CfsSubsetEval feature selection.
+PublishingHouse704 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial704 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingHouse704 (CfsSubsetEval-FS)}
 \centering{}%
@@
 Case 1-A: Developing prediction models to predict Total sales for
-Editorial704 with SOM feature selection.
+PublishingHouse704 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial704 (SOM-FS)}
+\caption{Predicting Total sales for PublishingHouse704 (SOM-FS)}
 \centering{}%
@@
 Case 1-B: Developing prediction models to predict Total sales for
-Editorial-UDLU11 with CfsSubsetEval feature selection.
+PublishingHouse-UDLU11 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLU11 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDLU11 (CfsSubsetEval-FS)}
 \centering{}%
@@
 Case 1-B: Developing prediction models to predict Total sales for
-Editorial-UDLU11 with SOM feature selection.
+PublishingHouse-UDLU11 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLU11 (SOM-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDLU11 (SOM-FS)}
 \centering{}%
@@
 Case 2-A: Developing prediction models to predict Total sales for
-Editorial-UDL929 with CfsSubsetEval feature selection.
+PublishingHouse-UDL929 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDL929 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDL929 (CfsSubsetEval-FS)}
 \centering{}%
@@
 Case 2-A: Developing prediction models to predict Total sales for
-Editorial-UDL929 with SOM feature selection.
+PublishingHouse-UDL929 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDL929 (SOM-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDL929 (SOM-FS)}
 \centering{}%
@@
 Case 2-B: Developing prediction models to predict Total sales for
-Editorial-UDLW12 with CfsSubsetEval feature selection.
+PublishingHouse-UDLW12 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLW12 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDLW12 (CfsSubsetEval-FS)}
 \centering{}%
@@
 Case 2-B: Developing prediction models to predict Total sales for
-Editorial-UDLW12 with SOM feature selection.
+PublishingHouse-UDLW12 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for Editorial-UDLW12 (SOM-FS)}
+\caption{Predicting Total sales for PublishingHouse-UDLW12 (SOM-FS)}
 \centering{}%

### 2016-04-29 paper.tex
Reducing fig.1, references #24. I think it is readable, but please check
updating the experiments section

@@
 \begin{table}
-\caption{Predicting Total sales for all publishers (all the features). 30 repetitions, 10-fold cross validation.
+\caption{Predicting Total sales for all publishers (all the features). 10 repetitions, 10-fold cross validation.
 \label{tab:all_publishers_no_fs}}
 \centering{}%
-%{\scriptsize
+\scalebox{0.85}{
+
 \begin{tabular}{|c|l|l|l|l|l|l|}
@@
 \hline 
-\end{tabular}%}
-%}
+\end{tabular}
+}
 \end{table}
@@
 
-As far as the different methods are concerned, M5P model obtained good results, 
-both in time and error, and as stated before, this method can learn and tackle 
-tasks with high dimensionality and it generates reproducible and comprehensible 
-representations that provide information on the decision process and does not 
-require human intervention either for the operation or for interpretation. 
-Thus, it is very suitable in order to be incorporated in a publishing company 
+As far as the different methods are concerned, M5P model obtained the best results, 
+both in time and error. The advantage of M5P is that it can learn and tackle 
+classification tasks that have high dimensionality and categorical variables efficiently.
+Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation.
+Thus, it is very suitable model be incorporated in a publishing company
 processes.
 
-The Linear Regression model outperforms some other complex methods, both in time 
-(as it is a simple method to train) and in obtained errors.
-However not in all cases, as more powerful models that obtain better results 
-can be obtained in comparable time.
-
-Taking into account the SVM model obtained results, this method obtains comparable 
-errors to those of M5P. Even when used using the default parameter values it exhibit 
-a good generalisation performance.
-However, it is much slower than the others to build the model, not only when 
-using the dataset with categorical input variables, but also when using the 
-datasets with numerical variables.
-
-kNN is the faster method used in this study, as it is the simpler method.
-However, the model is slow when classifying (as there are a large number of 
-training examples), and it exhibit a poor generalisation ability, as it does not 
+Taking into account the obtained results by SVM model, this method obtains comparable 
+errors to those of M5P. Even when using roughly tuned parameter values, it shows 
+a good generalisation performance. However, SVM is much slower than the others to build the model, not only when using the dataset with categorical input variables, but also when using the 
+datasets with numerical variables, not to mention the extra time needed to optimize its hyperparameters.
+
+According to Table \ref{tab:all_publishers_no_fs}, it can be noticed also that the Linear Regression model outperformed some other complex methods like the random forest, both in time and in obtained errors.
+Although, Linear regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.
+
+kNN is the fastest method used in this study in terms of training time, as it is the simplest method. However, the model is slow when classifying large number of 
+training examples, and it exhibits a poor generalisation ability since it does not 
 learn anything from the training data.
 
-Moreover, in these experiments it has been seen the difficulty to process 
-information related to categorical variables, such as \emph{publisher} and 
+Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \emph{publisher} and 
 \emph{collection}.
-
-%[Pedro] ¿aplicamos tests estadísticos para ver si hay diferencias entre métodos?
 
@@
 how many books should be printed when a new book is published.
-This forecasting method, as an additional advantage, can be used for products 
+This forecasting method, with these additional advantages, can be used for products 
 with historical sales data and for new products with little or no historical 
@@
 \begin{center}
-\includegraphics[scale=0.4]{som_planes.eps}
+\includegraphics[scale=0.28]{som_planes.eps}
 \end{center}
@@
 % RELIEFATTRIBUTEEVAL
+
 \begin{tabular}{|c|l|l|l|l|l|l|}

### 2016-04-29 paper.tex
Updating feature selection experiments

@@
 
-Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \emph{publisher} and 
-\emph{collection}.
+Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \emph{collection} and 
+\emph{binding}.
 
@@
 
-Then, the dataset has been projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
-An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features \emph{publisher} and \emph{collection} have been
+The dataset has been also projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
+An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features \emph{collection} and \emph{binding} have been
 removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
 However, since they have a large number of unique different values this would be finally impracticable and useless.
-
-Moreover,
-four features (i.e; Subject1, Subject2, Subject3 and Book-binding)
-have more than 10\% missing values so they are removed also.
 
@@
 
+Examining the component planes shown in Figure \ref{fig:componentplanes}, it can be noticed that some variables have very similar color maps which means that they are highly correlated.
+In this case, we have two examples; the first is the \emph{distrib\_novelty} and \emph{print\_run}variables while the second is the \emph{tot\_points\_sale} and \emph{tot\_points\_sale\_1st\_year}.
+In order to make the dataset having less number of uncorrelated features with each other, one of the redundant features is removed from each pair of features.
+Therefore, the \emph{distrib\_novelty} and \emph{tot\_points\_sale\_1st\_year} were omitted from the dataset.
+
 %***TODO***: Justify the selected features by SOM (why have we chosen them?).

### 2016-04-29 paper.tex
more on feature selection experiments

@@
 
-%***TODO***: Justify the selected features by SOM (why have we chosen them?).
-% Sam will do it
-
 \begin{figure*}[ht]
@@
 
-%\begin{figure*}[http] 
-%\begin{center} 
-%\begin{tabular}{cc}
-%\includegraphics[scale=0.55]{Umatrix.eps}  &
-%\includegraphics[scale=0.55]{Labels.eps}  \\
-%U-matrix & Labels 
-%\end{tabular}
-%\end{center} 
-%\caption{Labeling the U-matrix using the total-sales variable.}
-%\label{fig:Umatrix} 
-%\end{figure*}
-
 The selected features per method are shown in Table \ref{tab:features_selected}. Logically, just the independent or input variables are considered.
@@
 
-Thus, we have run the same experiments as in Section \ref{subsec:results_all_publishers} with the whole dataset (all the publishers), but considering the selected features by each method.
-The results are shown in Table
+After applying the feature selection methods, we have run the same forecasting models as in Section \ref{subsec:results_all_publishers} for the whole dataset (all the publishers), but considering only the selected features by each method.
+The results are shown in Table \ref{tab:results_all_publishers_fs}.
 
 \begin{table}
-
 \centering{}%
@@
 \label{tab:results_all_publishers_fs}}
-
 % RELIEFATTRIBUTEEVAL
-
 \begin{tabular}{|c|l|l|l|l|l|l|}

### 2016-04-30 paper.tex
New abstract
Please, have a look. ;)

@@
 \author {
-P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
+P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, P. de las Cuevas$^1$, M.G. Arenas$^1$
 }
@@
   jmerelo@geneura.ugr.es, pgarcia@geneura.ugr.es,
-  antares.es@gmail.com, mgarenas@ugr.es, palomacd@ugr.es}
+  antares.es@gmail.com, palomacd@ugr.es, mgarenas@ugr.es}
 }
+% Antonio - Hossam add your 'official' e-mail here. ;)
 
@@
 \begin{abstract}
-%***TO DO***: rewrite this considering the new contents and results\\
-% Has it been done?
-
 When a new book is launched the publisher faces the problem of how
@@
 many is the main issue, since it implies a loss of investment due to
-inventory excess. In this paper, we are tackling the problem of
-predicting total sales in order to print the right amount of books and
-doing so even before the book has reached the stores.  We have been
-working on a data set that includes the complete sales data for books
-published in Spain across several years. After an initial exploratory
-analysis phase using visualisation techniques, we have applied several
-feature selection techniques in order to find out what are the
-variables that have more impact on sales, and then used machine
-learning to create a model and forecast sales. The initial methodology
-was used in a commercial product by Grupo Trevenque, but the
-methodology described here improves the running time %with
-                                %respect to what?- JJ
-and is eventually able to predict sales from pre-publication data with
-remarkable accuracy, thus creating a useful tool for publishers, for
-whom obtained models can provide a reliable guidance on the decision
-process of publishing a book, without human intervention either for
-the operation or for interpretation.
-% Antonio - esto es cierto??? :D
-% We should simply say: 
-% The method presented here provides a reliable data processing
-% technique for editorial data and also yields a reasonable result
-% that allows publishers to forecast sales and then create the
-% appropriate print run without incurring in losses. 
-%
-% Besides, if this is true:
-% It also provides a method that is able to provide insight on the
-% decisions that have an influence on the print run for publishers. 
+inventory excess, but printing too few will have also a negative economical impact.
+In this paper, we are tackling the problem of predicting total sales in order to print the right amount of books and doing so even before the book has reached the stores.
+A real dataset including the complete sales data for books published in Spain across several years has been used.
+We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualization techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods have been applied to create forecasting models for book sales.
+The obtained models are able to predict sales from pre-publication data with
+remarkable accuracy, and can be visualized as simple decision trees.
+Thus, these can be used as decision-aid tools for publishers, which can provide a reliable guidance on the decision process of publishing a book.
+This is also shown in the paper addressing example cases of four representative publishers, regarding their number of sales and the number of different books they sale.
 \end{abstract}
@@
 
+% Antonio - TO BE INCLUDED IN THIS SECTION
+% The method presented here provides a reliable data processing
+% technique for editorial data and also yields a reasonable result
+% that allows publishers to forecast sales and then create the
+% appropriate print run without incurring in losses. 
+%
+% Besides, if this is true:
+% It also provides a method that is able to provide insight on the
+% decisions that have an influence on the print run for publishers.
+
 %********************************************************************************

### 2016-05-03 paper.tex
Introduction rewriten
Some parts have been changed or completed.

Please revise. ;)

@@
 A real dataset including the complete sales data for books published in Spain across several years has been used.
-We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualization techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods have been applied to create forecasting models for book sales.
+We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualisation techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods have been applied to create forecasting models for book sales.
 The obtained models are able to predict sales from pre-publication data with
-remarkable accuracy, and can be visualized as simple decision trees.
+remarkable accuracy, and can be visualised as simple decision trees.
 Thus, these can be used as decision-aid tools for publishers, which can provide a reliable guidance on the decision process of publishing a book.
@@
 
-Publishing a book, in the same way as releasing any other cultural product with a
-physical substrate, implies several types of risks and costs due to
+Publishing a book, in the same way as releasing any other cultural product with a physical substrate, implies several types of risks and costs due to
 the complexity, and derived expenses, of the production,
@@
 to the number of books actually printed. But the problem is further
-complicated for completely new products, in the sense that it is an unknown
-author or a new topic with no track record, sales forecasts can
-only be based on the experience obtained from other similar products,
-but the definition of ``similar'' itself is obscure and, sometimes,
-subjective. Even if it is a known author or topic, having accurate
-estimations of future sales of the new product is extremely important, so 
-that production runs do not exceed predicted sales by too much. 
-Indeed, several studies have demonstrated that improving sales predictions 
+complicated for completely new products, in the sense that there is an unknown
+author or a new topic with no track record. Sales forecasts can
+only be based on the knowledge obtained from other similar products,
+but the definition of ``similar'' itself is fuzzy and, sometimes,
+subjective. Even if the author or the topic is known, doing accurate
+estimations of future sales of the new product is quite difficult, and extremely important, so that production runs heed predicted sales. 
+Indeed,several studies have demonstrated that improving sales predictions 
 (a reduction of forecasting errors) results in an enhancement in the 
@@
 
-% In this sense, the publishing industry is based on very particular and
-% established production process, and publishing a book requires several
-% steps, between which the distribution is important and plays an
-% important role. The publishing process and individual decisions at each step are very
-% important. One of those decisions is the number of copies to print. 
-  % ¿Esto que tiene que ver con la frase anterior? - JJ
-% Thus, a suitable prediction system for new books should take into
-% account many details about how the editorial process works. % y? - JJ
-
-% Implementing a good forecasting tool requires not only a good study of
-% the state of the art in this field, but also an accurate knowledge of
-% the operations and challenges facing the publishing industry and its
-% supply chain. % ¿eso es lo que vamos a hacer? - JJ
-
-The problem is specially acute for book publishers, who, among other
+This problem is specially acute for book publishers, who, among other
 content providers, release new {\em products} more frequently than
-other industries, so that they face the 
-problem of predicting sales quite often. The issue, in this case, is to print an
-adequate number of copies but not too many, as the unsold volumes will
-lead to losses and sunk inventory cost, 
+other industries, so that they face the problem of predicting sales quite often.
+The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost,
 whereas if the number of printed copies was not enough, a new print
-run can be made, resulting in temporary losses due to lack of supply;
-a real problem, to be sure, but less dire than having too many unsold
-books.  
-%FERGU: el you ese es muy coloquial, reescribir
-% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema.
-Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción.
-;)
-% Se podría señalar, por ejemplo:
-% - repetición de costes de distribución
-% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
-% - algunas más... :D
-% Corregido - JJ
-In this sense, errors in one or the other direction do not have the same impact.
-% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
-%FERGU: lo de one or the other direction creo que confunde
-% Lo que habría que decir es hablar de cómo hemos tratado una u otra
-% cosa. ¿Estamos sesgando hacia predecir menos ventas de las que
-% habría? ¿O simplemente es por tener un poco de background? Igual
-% deberíamos haberlas tratado de forma diferente. - JJ
-
-Thus, it is extremely important to develop an accurate predictive method
-which could forecast the future sales a new book will
-achieve, in order to optimise production schedules, improve the publishing
-company profits or minimise losses \cite{Zhao2001}, 
-being this the main objective of this paper: optimizing sales and
-improving profit margins by selling the whole print-run.
-
-In any case, the accuracy of the predictive method we intend to design is affected
-negatively by several factors, related to decisions on purchases, to freight 
-traffic, or with the distribution strategy \cite{Little1998}.
-Thus, it is very important to know the product and the variables that
+run can be made, resulting in temporary losses due to a lack of supply or in bad marketing for the customers, for instance.
+
+In this sense, errors in one or the other direction do not have the same impact, however, it is extremely important to develop an accurate predictive method
+which could forecast the future sales a new book will achieve, in order to optimise production schedules, improve the publishing company profits and minimise losses \cite{Zhao2001}, being this the main objective of this paper.
+
+It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors, related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
+Thus, it is mandatory to know the product and the variables that
 might affect the sales, and how an expert manager takes them into 
 account \cite{Armstrong2001,SThomassey2014}. 
-Their impact is difficult to estimate and it is not constant over time, 
-hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
+Moreover, their impact is difficult to estimate and it is not constant over time, hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
 In addition, some may have correlations between them. 
 However, these correlations can be detected using data analysis methods, 
-such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
-or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
-                                % do? What are the results?
-% This is a state of the art? Are we already in the state of the art?
-% - JJ
-
-In the research published in this paper, the problem of how many units should be printed 
-when a new book is published is faced using data provided by the 
-Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
-a company that provides management systems and services for bookshops,
-publishers and distributors. 
-Usually, the company's expert sales managers analysed historical data 
-and applied their knowledge using external variables to compute
-correct estimations (predictions), for instance, she can decide
-increasing or decreasing the sales forecast based on season or sales
-period.
-However, carrying out the analysis and forecasting process as a human expert,
-may lead to imprecise predictions which may not take all the variables into account. 
+such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.
+
+So, we will analyze in this work the data by means of different data mining methods and create predictive models that can be used mainly as decision-aid tools for book publishers.
+Then, they will be able to combine their expert-knowledge about the market with the created forecasting models in order to get a reliable estimation of book sales.
+
+% Antonio - I think this is the main idea we have to sell in this paper.
+Due to the  difficulty of the book sales market (and its variables), we cannot give an accurate tool for predicting book sales, but a decision-aid tool for publishers.
+Do you agree?
+
+In the research published in this paper, the problem of how many units should be printed  when a new book is published is faced using real data provided by the 
+Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers and distributors. 
+Usually, the company's expert sales managers analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions), for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
+However, just carrying out the analysis and forecasting process as a human expert, may lead to imprecise predictions which may not take all the variables into account. 
 In addition, the process might be tedious, especially when the amount
-of data is quite large, and even, different experts can reach different
-predictions from the same dataset \cite{Sanders1994}. A
-initial version of this method was developed under contract with that
-company and eventually integrated in their product. This paper
-represents an improved version of that method based on the same data.
-
+of data is quite large. Moreover, different experts can reach different
+predictions from the same dataset \cite{Sanders1994}.
+
+%An initial version of this method was developed under a contract with that company and eventually integrated in their product.
+This paper represents an improved version of that method based on the same data.
 % We should also mention what data we actually mean, I don't think
 % we've published it here. - JJ
-
-With this issue in mind, in this paper a data visualisation and
-preprocessing strategy to find out what are the relevant variables
-describing a book in the prediction of book sales is proposed; then
-several standard data mining models  
-for sales forecasting are evaluated so a publishing company 
-can deduce and optimise print-run.
-% Antonio - cambiar este párrafo para describirlo como un proceso en dos pasos:
-% - análisis y extracción
-% - predicción
-After this initial processing phase, we apply machine learning
-techniques to create a sales model and use it to predict them.
-
-% Antonio - Además habría que justificar bien (con citas) el por qué de la extracción/selección de características, por ejemplo:
-% - menor tiempo de procesamiento
-% - mejores resultados (si algunas variables interfieren entre sí)
-% - Permiten saber qué variables son las que influyen realmente en el
-% resultado. Esto es lo único importante - JJ
-
-%***TO DO***: rewrite this considering the new structure of the paper\\
-
-The rest of this paper is structured as follows: next, 
-Section \ref{sec:soa} presents a comprehensive review of the
-approaches found in the bibliography related to the prediction of
-sales from product characteristics. 
-Then, Section \ref{sec:problem} describes the 
-problem of how many books should be printed when a new book is published, 
-followed by Section \ref{sec:methodology} where the
-experimental setup and the methodology considered in the study is
-presented.  Section \ref{sec:experiments} reports and analyses the obtained results with a 
-real dataset. Finally, conclusions and future work are presented in Section
-\ref{sec:conclusionsAndFutureWork}. 
-% Antonio - TODO: rescribir con los contenidos finales del artículo. ;)
+% Antonio - I think this information is not relevant for the paper...
+
+With this issue in mind, in this paper we firstly present an analysis on the aforementioned real dataset, by means of data mining and visualisation techniques.
+Then, a feature selection process is conducted using three different methods, in order to find out what are the relevant variables describing a book in the prediction (or regression) procedure.
+After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets (considering a different number of variables).
+The value of this methodology is contrasted considering four different publishing houses being representative as top sellers, medium sellers, the most varied and one which sells a medium amount of different books.
+
+The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to the prediction of sales in similar scopes.
+Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run for new books, along with a description of the considered dataset.
+Section \ref{sec:methodology} details the methodology considered in the study, from the data collection and preprocessing stages, to the selection of the forecasting methods to be applied in the experiments.
+These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets (with different amounts of features) for all the publishing houses.
+The results obtained for the four considered special cases are commented in Section \ref{sec:example_cases}.
+Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.
 
@@
 In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
-% Antonio - quizá habría que comentar alguno o todos bervemente...
+% Antonio - Maybe we should describe them briefly...
 %
@@
 
-SOM is a type of unsupervised neural network inspired by the topographical organization of the sensory cortex of human brain \cite{kohonen1998}.
+SOM is a type of unsupervised neural network inspired by the topographical organisation of the sensory cortex of human brain \cite{kohonen1998}.
 It maps highly dimensional data into a lower dimensional space where similar data patterns are located in more adjacent areas on the grid.
-It is a very useful analysis tool for visualizing complex data with high number of variables in a simple geometric plane.
-Therefore, it could be used for different tasks such as feature selection and data clustering and visualization.
+It is a very useful analysis tool for visualising complex data with high number of variables in a simple geometric plane.
+Therefore, it could be used for different tasks such as feature selection and data clustering and visualisation.
 
@@
 \section{Experiments of special publishing houses cases}
-\label{example_cases}
+\label{sec:example_cases}
 

### 2016-05-03 paper.tex
updating the discussion on feature selection results

@@
 
-%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
-% Antonio - arreglado 
-% And this is going to be useful because... - JJ
-% This is copied from the HIV paper. Please rephrase and adapt to the
-% particular venue - JJ
-
 This method is usually applied to analyse data as similar items tend to be 
@@
 %This method works well even if the space is highly dimensional and the problem is not linearly separable.
-
-% Antonio - MLP no se ha aplicado al final...
-
- % weka.classifiers.functions.MultilayerPerceptron
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
-% \item \emph{Multilayer Perceptron}:
-%A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
-%artificial neural network model that maps the input data onto an appropriate output. 
-%It is an artificial neural network generally used for classification or 
-%approximation problems.
-%
-%This model is a generalisation of the standard linear perceptron that uses several 
-%layers of nodes (called neurons) and that is able to solve linearly inseparable 
-%problems \cite{SteinwenderBitzer2003}.
-%Each neuron consists of a linear combination of weighted inputs which is passed 
-%though a non-linear activation function to produce its output.
-%
-%This kind of artificial neural network is trained using a supervised learning 
-%technique called back-propagation.
-%This training method was developed independently by Werbos \cite{Werbos1974}, 
-%Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
-%in updating the weights of the output layer neurons once the erroneous output 
-%has been obtained, and then, propagating the successive weight layers back to 
-%the input layer.
-%
-%A key issue when designing an MLP is the number of hidden layers of neurons.
-%Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
-%create classifying regions of any kind. This result was then confirmed in later 
-%works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
 
@@
 
-%***TODO***: Revise and fix the following text...
-
 As far as the different methods are concerned, M5P model obtained the best results, 
@@
 The results are shown in Table \ref{tab:results_all_publishers_fs}.
+Examining the obtained results for each feature selection method, it can be seen that RFE got the best results compared to SOM and CSE.
+It can be noticed also that the performance of M5P, kNN and RF has been improved with RFE compared to the case of using all features.
+In general, all feature selection methods have reduced the training time needed to build the forecasting methods, this is because they reduced the features and excluded the categorical features that have many possible values.
+On the other side, CSE and SOM did not perform as good as RAE which could be explained due to the extensive reduction made by CSE and due to the human intervention in the case of SOM.
 
@@
 \end{table}
-
-%***TO DO***: comment the results
-% Sam will do it - JJ
-
-%***TO DO***: Think if including the graphs (scatter plots).
-
-%In Figures \ref{conv2}, \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} we depict scatter plots for the values of the actual total sales values against the predicted ones obtained by the developed models.
-%Those figures also show the correlation between the two variables and the proportion of variation in actual total sales that is explained by the predicted ones. 
-%Figure \ref{conv2} corresponds to the results obtained using all available features without performing any feature selection method.
-In this figure, it can be noticed that SVM achieved the best results by explaining 88.2\% of the actual values while $k$-NN showed very poor results with only 49.8\%.
-%Figures \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} show same plots after performing ReliefAttributeEval, CfsSubsetEval and SOM feature selection methods, respectively.
-%According to these figures, we can notice that there wasn't almost any significant degradation in the performance of the M5P, LR, SVM and MLP. 
-%On the other side, the performance of $k$-NN was dramatically improved after the feature selection process by explaining 84.5\% of variation on average.
-%
-%
-
-% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
-%Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
-%\ref{tabla:resultsSOM}, \ref{tabla:results9} and \ref{tabla:results4},
-%using those categorical variables as part of a big dataset makes the problem 
-%hard to solve, both in required time to build the forecasting models as well as 
-%in the obtained errors.
-
-%Moreover, some methods are unable to build the models in a reasonable time.
-%However, as stated before, Trevenque expert sales manager, taking into account 
-%his knowledge in industry experience and their perceptions, decided that 
-%\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.
-
-% - indicar pros y contras de los diferentes métodos
-% - indicar qué método da mejores resultados
-% - indicar qué método es tipo "caja-negra" y cuáles ofrecen modelos "explicables"
 

### 2016-05-04 paper.tex
discussing the results

@@
 \hline 
-
 \end{tabular}
@@
 The experiments applied on the selected special cases follow the same methodology used previously for the whole dataset.
-First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (ReliefAttributeEval, CfsSubsetEval and SOM) are used to reduce the set of features in each case.
-Finally, the classification models are applied again on the reduced datasets to evaluate their performance.
+First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (RFE, CSE and SOM) are used to reduce the set of features in each case.
+Second, the classification models are applied again on the reduced datasets to evaluate their performance.
 
 Evaluation results of the developed models (without performing any feature selection method) for the selected four cases are shown in Table \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
+The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}.
+In general, M5P, RF and SVM performed better than the simple classifiers kNN and LR.
+In the case of Best selling publisher houses (i.e.
+UDL929) and publishers who publish wide range of different books (i.e.
+UDL704), M5P could be recommended as it shows more accurate forecasting results than the other models.
+While in the case of medium sized publishers, in terms of sales and number of published books, the RF model is recommended.
 
 \begin{table}
-\caption{Predicting Total sales for PublishingHouse-UDL929 (The best selling publishing house) }
+\caption{Predicting Total sales for Publishing house-UDL929 (The best selling publishing house) }
 \centering{}%
@@
 
-Case 1-A: Developing prediction models to predict Total sales for
-PublishingHouse704 with ReliefFAttributeEval feature selection.
+In the second stage of the experiments for the special cases, the feature selection methods (RFE, CSE and SOM) are applied for each case independently.
+For clarity purpose, we present here only the results after applying RFE method for the four cases in Table \ref{Table:case1results-RAE}, \ref{Table:case2results-RAE}, \ref{Table:case3results-RAE} and \ref{Table:case4results-RAE}.
+The RFE  was chosen for representation since the selected features by this method showed higher predictive power in all classifiers than the other selection methods.
+According to the aforementioned tables, RFE has noticeably improved the performance of all classifiers specially in the case of the best selling publisher house (i.e.
+UDL929) and the publisher who publishes wide range of different books (i.e.
+UDL704).
+For the rest of the results which are obtained by CSE and SOM feature selection methods we refer the reader to the appendix of tables at the end of this paper.
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for PublishingHouse-UDL929 (ReliefFAttributeEval-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
+\hline 
+LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
+\hline 
+\end{tabular}
+\label{Table:case1results-RAE}
+\end{table}
+
+\begin{table}[!ht]
+\caption{Predicting Total sales for PublishingHouse-UDLW12 (ReliefFAttributeEval-FS)}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
+\hline 
+K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
+\hline 
+RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
+\hline 
+LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
+\hline 
+\end{tabular}
+\label{Table:case2results-RAE}
+\end{table}
 
@@
 \end{tabular}
-\end{table}
-
-Case 1-B: Developing prediction models to predict Total sales for
-PublishingHouse-UDLU11 with ReliefFAttributeEval feature selection
+\label{Table:case3results-RAE}
+\end{table}
 
@@
 \caption{Predicting Total sales for PublishingHouse-UDLU11 (ReliefFAttributeEval-FS)}
-
 \centering{}%
@@
 \end{tabular}
-\end{table}
-
-Case 2-A: Developing prediction models to predict Total sales for
-PublishingHouse-UDL929 with ReliefFAttributeEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDL929 (ReliefFAttributeEval-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
-\hline 
-LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
-\hline 
-\end{tabular}
-\end{table}
-
-Case 2-B: Developing prediction models to predict Total sales for
-PublishingHouse-UDLW12 with ReliefFAttributeEval feature selection.
-
-\begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDLW12 (ReliefFAttributeEval-FS)}
-
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
-\hline 
-K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
-\hline 
-RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
-\hline 
-LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
-\hline 
-\end{tabular}
+\label{Table:case4results-RAE}
 \end{table}

### 2016-05-04 paper.tex
Reviewing abstract

@@
 many is the main issue, since it implies a loss of investment due to
-inventory excess, but printing too few will have also a negative economical impact.
+inventory excess, but printing too few will also have a negative economical impact.
 In this paper, we are tackling the problem of predicting total sales in order to print the right amount of books and doing so even before the book has reached the stores.
@@
 Thus, these can be used as decision-aid tools for publishers, which can provide a reliable guidance on the decision process of publishing a book.
-This is also shown in the paper addressing example cases of four representative publishers, regarding their number of sales and the number of different books they sale.
+This is also shown in the paper by addressing four example cases of representative publishers, regarding their number of sales and the number of different books they sell.
 \end{abstract}

### 2016-05-04 paper.tex
Reviewing Introduction pt. I

@@
 the complexity, and derived expenses, of the production,
-distribution and storage processes; most of these costs are associated
+distribution, and storage processes; most of these costs are associated
 to the number of books actually printed. But the problem is further
@@
 
-In this sense, errors in one or the other direction do not have the same impact, however, it is extremely important to develop an accurate predictive method
-which could forecast the future sales a new book will achieve, in order to optimise production schedules, improve the publishing company profits and minimise losses \cite{Zhao2001}, being this the main objective of this paper.
+Despite the fact that errors in one or the other direction do not have the same impact, it is extremely important to develop an accurate predictive method
+which could forecast the future sales a new book will achieve, in order to optimise production schedules, improve the publishing company profits and minimise losses \cite{Zhao2001}, being the latter the main objective of this paper.
 

### 2016-05-04 paper.tex
Reviewing Introduction pt. II

@@
 
-It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors, related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
+It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
 Thus, it is mandatory to know the product and the variables that
@@
 account \cite{Armstrong2001,SThomassey2014}. 
-Moreover, their impact is difficult to estimate and it is not constant over time, hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
-In addition, some may have correlations between them. 
-However, these correlations can be detected using data analysis methods, 
+Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
+In addition, some may have correlations between them, although these correlations can be detected using data analysis methods, 
 such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.
 
-So, we will analyze in this work the data by means of different data mining methods and create predictive models that can be used mainly as decision-aid tools for book publishers.
-Then, they will be able to combine their expert-knowledge about the market with the created forecasting models in order to get a reliable estimation of book sales.
+Therefore, in this work we analyse the data by means of different data mining methods and create predictive models that can be mainly used as decision-aid tools for book publishers.
+Then, they will be able to combine their expert knowledge about the market with the created forecasting models in order to get a reliable estimation of book sales.
 
@@
 Do you agree?
+% (Paloma) Agree
 

### 2016-05-04 paper.tex
Replacing 'publishing house/s' for 'company/ies' to unify the text and also because the names used for the examples look cooler with the 'Co'

@@
 After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets (considering a different number of variables).
-The value of this methodology is contrasted considering four different publishing houses being representative as top sellers, medium sellers, the most varied and one which sells a medium amount of different books.
+The value of this methodology is contrasted considering four different publishing companies being representative as top sellers, medium sellers, the most varied and one which sells a medium amount of different books.
 
@@
 Section \ref{sec:methodology} details the methodology considered in the study, from the data collection and preprocessing stages, to the selection of the forecasting methods to be applied in the experiments.
-These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets (with different amounts of features) for all the publishing houses.
+These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets (with different amounts of features) for all the publishing companies.
 The results obtained for the four considered special cases are commented in Section \ref{sec:example_cases}.
@@
 
-First, after the publishing house has provided the raw data
+First, after the publishing company has provided the raw data
 (extracted directly from its database), a preprocessing method has
@@
 
-Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing houses) in order to prove the value of the proposal.
+Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing companies) in order to prove the value of the proposal.
 Some specific interpretable models have been created as a final result of the work.
@@
 Regarding the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
-In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing houses for predicting its own sales.
+In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing companies for predicting its own sales.
 % Antonio - Think about this... should we mention this?
@@
 
-We have analysed the whole dataset (all the publishing houses), but also performed some experiments considering specific publishing houses as example cases.
+We have analysed the whole dataset (all the publishing companies), but also performed some experiments considering specific publishing companies as example cases.
 The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for publishers.
@@
 
-\section{Experiments of special publishing houses cases}
+\section{Experiments of special publishing companies cases}
 \label{sec:example_cases}
 
-This section presents further experiments conducted on data concerning four interesting special publishing house cases.
-These publishing houses were selected as representative cases which could be very interesting for decision makers and managers in the domain.
+This section presents further experiments conducted on data concerning four interesting special publishing company cases.
+These publishing companies were selected as representative cases which could be very interesting for decision makers and managers in the domain.
 The four cases are described as follows:
@@
 \begin{itemize}
-    \item Best seller publishing house: this case represents the publishing house that sells the highest number of copies regardless the title of the books sold.
+    \item Best seller publishing company: this case represents the publishing company that sells the highest number of copies regardless the title of the books sold.
 Therefore, it is an example of a case on a higher business scale.
-    \item Medium seller publishing house: this represents an publishing house that sells medium number of copies compared to the other publishing houses (Medium business scale). 
-    \item Highest variation publishing house: this is an example of an publishing house that follows a strategy in publishing a very wide range of different titles.
-    \item Medium varied publishing house: this case represents an publishing house that has a median rank between the other publishing house regarding the variety of titles sold.
+    \item Medium seller publishing company: this represents an publishing company that sells medium number of copies compared to the other publishing companies (Medium business scale). 
+    \item Highest variation publishing company: this is an example of an publishing company that follows a strategy in publishing a very wide range of different titles.
+    \item Medium varied publishing company: this case represents an publishing company that has a median rank between the other publishing company regarding the variety of titles sold.
 \end{itemize}
 
-Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected publishing houses.
+Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected publishing companies.
 
 \begin{table}
-\caption{Description of publishing houses considered as special cases.
-\label{tab:desc_publishing houses}}
+\caption{Description of publishing companies considered as special cases.
+\label{tab:desc_publishing companies}}
 \centering{}%
@@
 \hline 
-\textit{All publishing houses} & 6083 & 3201645 & 209 publishing houses\\
-\hline 
-\textit{UDL929} & 216 & 460752 & Best selling publishing house\\
-\hline 
-\textit{UDLW12} & 97 & 2635 & Medium selling publishing house\\
-\hline 
-\textit{UDL704} & 293 & 58236 & Publishing house with most different\\ 
+\textit{All publishing companies} & 6083 & 3201645 & 209 publishing companies\\
+\hline 
+\textit{UDL929} & 216 & 460752 & Best selling publishing company\\
+\hline 
+\textit{UDLW12} & 97 & 2635 & Medium selling publishing company\\
+\hline 
+\textit{UDL704} & 293 & 58236 & publishing company with most different\\ 
        &     &       & books sold\\
 \hline 
-\textit{UDLU11} & 180 & 249481 & Publishing house with medium number\\ 
+\textit{UDLU11} & 180 & 249481 & publishing company with medium number\\ 
        &     &       &  of different books sold\\
@@
 \begin{table}
-\caption{Predicting Total sales for Publishing house-UDL929 (The best selling publishing house) }
+\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company) }
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingHouse-UDLW12 (The median selling publishing house) }
+\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company) }
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingHouse704 (highest number of different titles sold)}
+\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold)}
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingHouse-UDLU11 (medium number of different books sold))}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold))}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDL929 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS)}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDLW12 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS)}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse704 (ReliefFAttributeEval-FS) }
+\caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS) }
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDLU11 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (ReliefFAttributeEval-FS)}
 \centering{}%
@@
 
-Figure \ref{fig:decision_tree_best_seller} depicts the obtained decision tree for the best seller publishing house (UDL929).
+Figure \ref{fig:decision_tree_best_seller} depicts the obtained decision tree for the best seller publishing company (UDL929).
 The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales.
@@
   \epsfig{file=decision_tree_no_fs.eps,width=12cm}
-\caption{Decision Tree built by the M5P method for the best seller publishing house with all the pre-sales features.}
+\caption{Decision Tree built by the M5P method for the best seller publishing company with all the pre-sales features.}
 \label{fig:decision_tree_best_seller}
@@
 
-Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same publishing house (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).
+Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same publishing company (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).
 
@@
   \epsfig{file=decision_tree_fs.eps,width=12cm}
-\caption{Decision Tree built by the M5P method for the best seller publishing house with the features selected by the ReliefAttributeEval method.}
+\caption{Decision Tree built by the M5P method for the best seller publishing company with the features selected by the ReliefAttributeEval method.}
 \label{fig:decision_tree_best_seller_fs}
@@
 Moreover, proposed method was validated by the company and incorporated in a 
-business intelligence tool for publishing houses. %FERGU: no hay más info de esto? estaría guay describirlo
+business intelligence tool for publishing companies. %FERGU: no hay más info de esto? estaría guay describirlo
 
@@
 Case 1-A: Developing prediction models to predict Total sales for
-PublishingHouse704 with CfsSubsetEval feature selection.
+PublishingCo704 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse704 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS)}
 \centering{}%
@@
 Case 1-A: Developing prediction models to predict Total sales for
-PublishingHouse704 with SOM feature selection.
+PublishingCo704 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse704 (SOM-FS)}
+\caption{Predicting Total sales for PublishingCo704 (SOM-FS)}
 \centering{}%
@@
 Case 1-B: Developing prediction models to predict Total sales for
-PublishingHouse-UDLU11 with CfsSubsetEval feature selection.
+PublishingCo-UDLU11 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDLU11 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS)}
 \centering{}%
@@
 Case 1-B: Developing prediction models to predict Total sales for
-PublishingHouse-UDLU11 with SOM feature selection.
+PublishingCo-UDLU11 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDLU11 (SOM-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS)}
 \centering{}%
@@
 Case 2-A: Developing prediction models to predict Total sales for
-PublishingHouse-UDL929 with CfsSubsetEval feature selection.
+PublishingCo-UDL929 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDL929 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS)}
 \centering{}%
@@
 Case 2-A: Developing prediction models to predict Total sales for
-PublishingHouse-UDL929 with SOM feature selection.
+PublishingCo-UDL929 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDL929 (SOM-FS)}
+\caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS)}
 \centering{}%
@@
 Case 2-B: Developing prediction models to predict Total sales for
-PublishingHouse-UDLW12 with CfsSubsetEval feature selection.
+PublishingCo-UDLW12 with CfsSubsetEval feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDLW12 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS)}
 \centering{}%
@@
 Case 2-B: Developing prediction models to predict Total sales for
-PublishingHouse-UDLW12 with SOM feature selection.
+PublishingCo-UDLW12 with SOM feature selection.
 
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingHouse-UDLW12 (SOM-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS)}
 \centering{}%

### 2016-05-04 paper.tex
Reviewing Introduction pt. III and final

@@
 
-In the research published in this paper, the problem of how many units should be printed  when a new book is published is faced using real data provided by the 
-Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers and distributors. 
-Usually, the company's expert sales managers analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions), for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
-However, just carrying out the analysis and forecasting process as a human expert, may lead to imprecise predictions which may not take all the variables into account. 
+In the research published in this paper, the problem of how many units should be printed  when a new book is published is faced using actual data provided by the 
+Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
+Usually, the company's experts sales manager analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions); for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
+Nevertheless, just carrying out the analysis and forecasting process as a human expert may lead to imprecise predictions, and they may not take all the variables into account. 
 In addition, the process might be tedious, especially when the amount
@@
 Then, a feature selection process is conducted using three different methods, in order to find out what are the relevant variables describing a book in the prediction (or regression) procedure.
-After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets (considering a different number of variables).
-The value of this methodology is contrasted considering four different publishing companies being representative as top sellers, medium sellers, the most varied and one which sells a medium amount of different books.
-
-The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to the prediction of sales in similar scopes.
+After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets, also considering a different number of variables.
+The value of this methodology is contrasted considering four different publishing companies being representative as top sellers, medium sellers, the most varied, and one which sells a medium amount of different books.
+
+The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes. 
 Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run for new books, along with a description of the considered dataset.
 Section \ref{sec:methodology} details the methodology considered in the study, from the data collection and preprocessing stages, to the selection of the forecasting methods to be applied in the experiments.
-These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets (with different amounts of features) for all the publishing companies.
+These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies.
 The results obtained for the four considered special cases are commented in Section \ref{sec:example_cases}.

### 2016-05-04 paper.tex
Changed a thing and was mistaken, sorry T_T

@@
 Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
-Usually, the company's experts sales manager analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions); for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
+Usually, the company's expert sales managers analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions); for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
 Nevertheless, just carrying out the analysis and forecasting process as a human expert may lead to imprecise predictions, and they may not take all the variables into account. 

### 2016-05-04 paper.tex
Reduced all table sizes to fix in the page. Slighty related with the closed issue #24 :P

@@
 e-mail: {\tt pacv@ugr.es, amorag@geneura.ugr.es,
-  jmerelo@geneura.ugr.es, pgarcia@geneura.ugr.es,
+  jmerelo@geneura.ugr.es, pablogarcia@ugr.es,
   antares.es@gmail.com, palomacd@ugr.es, mgarenas@ugr.es}
@@
 % RELIEFATTRIBUTEEVAL
+\resizebox{12cm}{!}{
 \begin{tabular}{|c|l|l|l|l|l|l|}
@@
 \end{tabular}
-
+}
 % CFSSUBEVAL
+\resizebox{12cm}{!}{
 \begin{tabular}{|c|l|l|l|l|l|l|}
@@
 \hline
-\end{tabular}\\
-
+\end{tabular}
+}
 % SOM
 \centering{}% SOM
+\resizebox{12cm}{!}{
 \begin{tabular}{|c|c|c|c|c|c|c|}
@@
 \end{tabular}
+}
 \end{table}
@@
 \begin{table}
-\caption{Description of publishing companies considered as special cases.
-\label{tab:desc_publishing companies}}
-\centering{}%
+\caption{Description of publishing companies considered as special cases.}
+\centering{}%
+\resizebox{12cm}{!}{
 \begin{tabular}{|c|l|l|l|}
@@
 \end{tabular}
+}
 \label{Table:special_cases}
@@
 \centering{}%
+\resizebox{12cm}{!}{
 \begin{tabular}{|c|c|c|c|c|c|c|}
@@
 \end{tabular}
+}
 \label{Table:case1results}
@@
 \end{tabular}
+}
 \label{Table:case2results}
@@
 \end{tabular}
+}
 \label{Table:case3results}
@@
 \end{tabular}
+}
 \label{Table:case4results}
@@
 \end{tabular}
+}
 \label{Table:case1results-RAE}
@@
 \end{tabular}
+}
 \label{Table:case2results-RAE}
@@
 \end{tabular}
+}
 \label{Table:case3results-RAE}
@@
 \end{tabular}
+}
 \label{Table:case4results-RAE}

### 2016-05-05 paper.tex
added my email

@@
 $^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
-e-mail: {\tt pacv@ugr.es, amorag@geneura.ugr.es,
+e-mail: {\tt pacv@ugr.es, amorag@geneura.ugr.es, hossam.faris@ju.edu.jo,
   jmerelo@geneura.ugr.es, pablogarcia@ugr.es,
@@
 }
-% Antonio - Hossam add your 'official' e-mail here. ;)
 

### 2016-05-05 paper.tex
Fixed error measurements
Some comments for @7ossam81
And some grammar corrections, too.

@@
         \begin{equation}\label{eq:RAE}
-            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid p_{i-1} - o_i\mid} }
+            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid \bar{o} - o_i\mid} }
         \end{equation}
@@
         \begin{equation}\label{eq:RRSE}
-            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(p_{i-1} - o_i)}^2 }  }
+            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
         \end{equation}
 \end{itemize}
-where $o_i$ is the individual data $i = {1,...,n}$ and $p_i$ is the obtained prediction.
+where $o_i$ is the actual value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
 
@@
 
-In the second stage of the experiments for the special cases, the feature selection methods (RFE, CSE and SOM) are applied for each case independently.
-For clarity purpose, we present here only the results after applying RFE method for the four cases in Table \ref{Table:case1results-RAE}, \ref{Table:case2results-RAE}, \ref{Table:case3results-RAE} and \ref{Table:case4results-RAE}.
-The RFE  was chosen for representation since the selected features by this method showed higher predictive power in all classifiers than the other selection methods.
-According to the aforementioned tables, RFE has noticeably improved the performance of all classifiers specially in the case of the best selling publisher house (i.e.
-UDL929) and the publisher who publishes wide range of different books (i.e.
-UDL704).
-For the rest of the results which are obtained by CSE and SOM feature selection methods we refer the reader to the appendix of tables at the end of this paper.
+In the second stage of the experiments for the special cases, the
+feature selection methods (RFE, CSE and SOM) are applied for each case
+independently, since publishers with different sales ranges, and
+targets, might in fact include different factors or have different
+leverage when deciding how much to print. For clarity purpose, we present here only the results
+after applying the RFE method for the four cases in Table
+\ref{Table:case1results-RAE}, \ref{Table:case2results-RAE},
+\ref{Table:case3results-RAE} and \ref{Table:case4results-RAE}, this
+one was chosen since the selected features by this
+method showed the highest predictive power among all classifiers. 
+%According to the aforementioned tables, 
+%It's not according to a table. It's according to the results there - JJ
+RFE
+has noticeably improved % with respect to what? -JJ
+the performance of all classifiers specially
+in the case of the best selling publisher house (i.e. UDL929) and the
+publisher who publishes a wide range of different books
+(i.e. UDL704). For the rest of the results which are obtained by CSE
+and SOM feature selection methods we refer the reader to the appendix
+of tables at the end of this paper.
 
 \begin{table}[!ht]
+% Why the capital in Total? If it's a variable use Small Caps or Sans
+% Serif - JJ
 \caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS)}

### 2016-05-05 paper.tex
Changed "medium seller" to mid-range seller
Please check @unintendedbear that it "sounds" better now.

@@
 After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets, also considering a different number of variables.
-The value of this methodology is contrasted considering four different publishing companies being representative as top sellers, medium sellers, the most varied, and one which sells a medium amount of different books.
+The value of this methodology is contrasted considering four different publishing companies being representative as top sellers, mid-range sellers, the most varied, and one which sells a medium amount of different books.
 
@@
 Therefore, it is an example of a case on a higher business scale.
-    \item Medium seller publishing company: this represents an publishing company that sells medium number of copies compared to the other publishing companies (Medium business scale). 
+    \item Mid-range seller publishing company: this represents an publishing company that sells medium number of copies compared to the other publishing companies (Medium business scale). 
     \item Highest variation publishing company: this is an example of an publishing company that follows a strategy in publishing a very wide range of different titles.
@@
 \hline 
-\textit{UDLW12} & 97 & 2635 & Medium selling publishing company\\
+\textit{UDLW12} & 97 & 2635 & Mid-range selling publishing company\\
 \hline 

### 2016-05-05 paper.tex
Revising SOM stuff
The main problem is that motivation is still missing. There are many comments and questions inserted by me that have not been answered. Please @amorag mainly, but also @7ossam81 take a look at them.

@@
 
-SOM is a type of unsupervised neural network inspired by the topographical organisation of the sensory cortex of human brain \cite{kohonen1998}.
-It maps highly dimensional data into a lower dimensional space where similar data patterns are located in more adjacent areas on the grid.
-It is a very useful analysis tool for visualising complex data with high number of variables in a simple geometric plane.
-Therefore, it could be used for different tasks such as feature selection and data clustering and visualisation.
-
-Basically, SOM consists of two layers; input layer and output layer (also known as Kohen layer).
-Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e.
-units).
-This means that every neuron is linked to every input in the input layer.
-
-The learning process of SOM is an iterative process applied in two stages.
-First, the weights of the network are initialized randomly then the n-dimensional input vectors are presented to the network sequentially so the distance between the weights of the neurons and the inputs are computed using the simple Euclidean distance.
-In the second stage, the neuron which has the shortest distance with the presented input vector is updated along with its neighbor neurons.
-This neuron is called the best matching unit (BMU).
-The goal of the learning process is to minimize the neighborhood distance in the output clusters.
-
-When the learning process is done a visual representation method like the Unified Distance Matrix, or U-matrix for short, is used to visualize the distances between neurons in the output space.
-In the U-matrix, the distance between adjacent neurons is measured and assigned different colors.
-Dark colors between neurons indicate large distances (boundaries) while light colors represent similar areas (clusters).
+SOM is a type of unsupervised neural network inspired by the
+topographical organisation of the sensory cortex of human brain
+\cite{kohonen1998}. It maps highly dimensional data into a lower
+dimensional space where similar data patterns are located in more
+adjacent areas on the grid. 
+It is a very useful analysis tool for visualising complex data with
+high number of variables in a simple geometric plane. Therefore, it
+could be used for different tasks such as feature selection and data
+clustering and visualisation.
+
+Basically, SOM consists of two layers: input layer and output, also
+known as Kohonen, layer. Input layer is fully connected with the 
+Kohen layer which is usually a two dimensional grid of neurons
+(i.e. units). This means that every neuron is linked to every input in
+the input layer.
+
+SOM follows an iterative process applied in two stages: First, the
+weights of the network are initialized randomly then the n-dimensional
+input vectors are presented to the network sequentially so the
+distance between the weights of the neurons and the inputs are
+computed using the simple Euclidean distance; in the second stage, the
+neuron which has the shortest distance with the presented input vector
+is updated along with its neighbor neurons. This neuron is called the
+best matching unit (BMU). The goal of the learning process is to
+minimize the neighborhood distance in the output clusters.
+
+When the learning process is done a visual representation method like
+the Unified Distance Matrix, or U-matrix for short, is used to
+visualize the distances between neurons in the output space. In the
+U-matrix, the distance between adjacent neurons is measured and
+assigned different colors. Dark colors between neurons indicate large
+distances (boundaries) while light colors represent similar areas
+(clusters).
 

### 2016-05-05 paper.tex
Question for @amorag
More questions for @amorag
Fixed typo in tree label and reduced table size
More questions for @amorag re: UMatrix
And more stuff for @amorag
More comments from reviewer #3 for @amorag
Reviewing state of the art pt. I

@@
 \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
-is perhaps the most used technique to tackle the sales forecasting
+is perhaps the most used technique to tackle sales forecasting
 problems. The efficiency of these techniques strongly depends on the field of application 
@@
  They analyse data about
-sales and, taking into account their knowledge in industry, their
+sales and, taking into account their knowledge of industry, their
 experience, and their perception about trends, could make decisions on
@@
 external variables that must be taken into account, such as
-seasonality, promotions or fashions that expert managers might
+seasonality, promotions, or fashions that expert managers might
 subjectively apply \cite{Lapide1999,ChernWSF15}. % This
@@
 However, the authors used in these papers historical data from published books, 
-so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
+so their proposed methodology can not be applied to the problem of unpublished books sales prediction.
 %FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?
@@
 
-The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data.
-The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.
+The SOM algorithm is applied with a large map size of $26 \times 16$
+in order to represent the data. % Not enough justification. Did you
+                                % try others? - jj
+ The best SOM training results are obtained with a final quantisation
+ error of 0.691 and topographic error of 0.046. % explain what is
+                                % quantisation and topographic error
+                                % and why it is important - JJ
 
@@
 variables resulted from SOM training. The term component is used in
-SOM to refer to the features. The component planes in Figure
+% really, are you reading this with the mind of someone that has no
+% idea what is SOM or U-Matrix or whatever? Tell first what you are
+% going to do, then tell why you are doing it, explain all the
+% terminology and then show the results. You can't keep saying "I have
+% done this and this is the result. You have to explain why you are
+% doing it, what you are doing, how you are doing it and then how to
+% interpret the results - JJ
+SOM to refer to the features. %use features!!!! - JJ
+ The component planes in Figure %what is a plane? Really, you don't
+                                %know what's in the mind of the reader
+                                %(or reviewer#3, who is a son of a
+                                %bitch - JJ
 \ref{fig:componentplanes} show the trend of values of the prototype
@@
 there are more hexagons in the U-matrix than component planes since
-the distances between units is also represented as hexagons.
+the distances between units is also represented as hexagons. % but
+                                % explain that at the beginning!
+                                % Devote one or two paragraphs to tell
+                                % the reader what is U-Matrix, a
+                                % reference, why we are using it and
+                                % how it conveys more information that
+                                % a pure and simple feature selection
+                                % (which we are doing anyway). If we
+                                % don't, Reviewer #3 (who is,
+                                % remember, a son of a bitch) will
+                                % tell you to just suppress that whole
+                                % section - JJ
 

### 2016-05-05 paper.tex
Table 5 rows were only centered for the third method
Comment for @amorag, who wrote this sentence
Couple of typos fixed in abstract and introduction

--- 2016-05-05 paper.tex
@@
 many is the main issue, since it implies a loss of investment due to
-inventory excess, but printing too few will also have a negative economical impact.
+inventory excess, but printing too few will also have a negative economic impact.
 In this paper, we are tackling the problem of predicting total sales in order to print the right amount of books and doing so even before the book has reached the stores.
 A real dataset including the complete sales data for books published in Spain across several years has been used.
-We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualisation techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods have been applied to create forecasting models for book sales.
+We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualisation techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods has been applied to create forecasting models for book sales.
 The obtained models are able to predict sales from pre-publication data with
@@
 distribution, and storage processes; most of these costs are associated
-to the number of books actually printed. But the problem is further
+with the number of books actually printed. But the problem is further
 complicated for completely new products, in the sense that there is an unknown

### 2016-05-05 paper.tex

@@
 \resizebox{12cm}{!}{
-\begin{tabular}{|c|l|l|l|l|l|l|}
+\begin{tabular}{|c|c|c|c|c|c|c|}
 \hline 

### 2016-05-05 paper.tex
Reviewing state of the art pt. II and final, plus some comments.

--- 2016-05-05 paper.tex
@@
 %FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?
+% (Paloma) Agree with Fergu, I don't think we should say this... Please review it.
 
@@
 %
-In the same line, Thomassey et al. \cite{SThomassey2014} propose using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
-a very similar issue to the new book publishing one.
+In the same line, Thomassey et al. \cite{SThomassey2014} proposed using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
+a very similar issue to the new book publishing one. % (Paloma) Very similar? Why?
 The same problem was previously faced by Xia et al. \cite{Xia2012} using a 
@@
 % Antonio - of -> as???
+% (Paloma) It's "of" in the title...
 The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
@@
 In those cases where historical data are available, classical time series 
-forecasting methods can be applied, which is what the authors do in
+forecasting methods can be applied, which is what the authors did in
 \cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
@@
                    % of application and the available problem data. - pedro
-A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
-historical data along online reviews, reviewer characteristics and review 
+A similar method is described by Chern et al. \cite{ChernWSF15}, who analysed 
+historical data throughout online reviews, reviewer characteristics, and review 
 influences to understand how electronic `word-of-mouth' influences product sales. 

### 2016-05-05 paper.tex
Reviewing problem description and leaving a comment

@@
 %FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
-descriptive and variables known in advance related to the new book. In
+descriptive and variables are known in advance related to the new book. In
 order to do that, we have used a training dataset which includes
-historical sales data for a big amount of books published in Spain for
+historical sales data % (Paloma) so, have we or have we not historical data? It's all contradictory
+ for a big amount of books published in Spain for
 several years, with a set of 50 features or variables per pattern.
@@
 In this prediction problem there are other external variables that also affect 
-the sales of a new book, such as those related to seasonality, trends or 
+the sales of a new book, such as those related to seasonality, trends, or 
 promotions, that classical prediction methods can not deal with. %FERGU: por qué?
@@
 external data. 
-Thus, the proposed method, will analyse the provided data and
+Thus, the proposed method will analyse the provided data and
 variables and will yield a forecast of sales according to them. This
 result could be used as a reference for a human expert, who would
-consider it in his/her own prediction process.
+consider it in his or her own prediction process.
 

### 2016-05-05 paper.tex
Reviewing Methodology pt. I, with some comments also

@@
 such as those with null values in required variables, or with negative
-sales, for instance. Moreover, the initial set of variables (presented
-in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
+sales, for instance. % (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
+Furthermore, the initial set of variables, presented
+in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to
 use just those that can be known in advance when a new book is
-launched, i.e. \textit{pre-sales data}.
+launched, i.e. \textit{pre-sales data}. % (Paloma) Where are they? In table 2?
 
@@
 prediction problem. 
-  In this stage, both, numerical and visualisation-based approaches have been applied in this paper, in order to select the best variables for the forecasting 
+  In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
 methods.  
@@
 
-Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing companies) in order to prove the value of the proposal.
+Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal.
 Some specific interpretable models have been created as a final result of the work.
-The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).
+The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.
 

### 2016-05-05 paper.tex
Don't use don't in papers :P Also, couple of questions

@@
 
-In general, historical data are used to make time series, and from them extracting common patterns and obtaining accurate predictions.
+In general, historical data are used to make time series, and extracting common patterns and obtaining accurate predictions from them.
 However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
-\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem.
+\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem. %PABLO: pre-sales data is mentioned briefly in introduction, expand it
 
 Moreover, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
-those whose value don't depend on the book sales.
+those whose value do not depend on the book sales.
 So, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
@@
 So the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
+%Pablo: still waiting the definition of the variables
 
@@
 
-Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass.
+Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books\footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass.
 So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance.

### 2016-05-05 paper.tex
Reviewing Methodology pt. II, hoping that this commit does not conflict with @fergunet 's previous one

--- 2016-05-05 paper.tex
@@
 
-Moreover, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
+Due to this situation, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
 those whose value don't depend on the book sales.
-So, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
+Therefore, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
 
@@
 % preliminary selection - JJ
-\caption{Considered pre-sales features and their types. It also shows
-  the names of the variables used in the applied methods and if everyone is an input (independent) or an output (dependent) variable.} 
+\caption{Considered pre-sales features and their types. The third column shows
+  the names of the variables used in the applied methods, and the last one indicates if it has been used as an input (independent) or an output (dependent) variable.} 
 \label{tabla:params_pre_sales}
@@
 As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods.
-\texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
+On the other hand, \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
 In addition, this variable could be interesting to be used to test the prediction model, once it is built.
-So the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
+Hence, the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
 

### 2016-05-05 paper.tex

--- 2016-05-05 paper.tex
@@
 
-Moreover, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
+Due to this situation, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
 those whose value do not depend on the book sales.
-So, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
+Therefore, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
 
@@
 As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods.
-\texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
+On the other hand, \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
 In addition, this variable could be interesting to be used to test the prediction model, once it is built.
-So the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
+Hence, the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
 %Pablo: still waiting the definition of the variables

### 2016-05-05 paper.tex
Reviewing Methodology pt. III

@@
 
-In general, historical data are used to make time series, and extracting common patterns and obtaining accurate predictions from them.
+In general, historical data are used to make time series, as well as for extracting common patterns and obtaining accurate predictions from them.
 However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
@@
 \caption{Considered pre-sales features and their types. The third column shows
-  the names of the variables used in the applied methods, and the last one indicates if it has been used as an input (independent) or an output (dependent) variable.} 
+  the names of the variables used in the applied methods, and the last one indicates if they have been used as an input (independent) or an output (dependent) variable.} 
 \label{tabla:params_pre_sales}
@@
 
-Regarding the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
+With regard to the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
 In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing companies for predicting its own sales.
 % Antonio - Think about this... should we mention this?
+% (Paloma) If you finally leave it, please review it because this last sentence is a bit confusing
 

### 2016-05-05 paper.tex
Changing a footnote into a reference as asked by @JJ :D

@@
 
-Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books\footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass.
+Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \cite{wiki:dewey}, and the existing similarity relationship between the books inside a class or subclass.
 So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance.

### 2016-05-05 paper.tex
Better tables
Reviewing Methodology pt. IV, rewriting a bit and mostly killing parenthesis and 'moreovers'

@@
 
-Once a dataset has been composed it must be preprocessed, i.e. it
-should be revised in order to fix the existing errors (such as wrong
-or duplicated patterns), or to complete (or address) the absence of
-information, for instance. The aim is looking for the correctness,
-homogeneity and completeness of the data. % useless paragraph - JJ
+Preprocessing a dataset means that it is revised in order to reduce errors, such as wrong or duplicated patterns, or for completing missing values. The aim is to look for the correctness,
+homogeneity, and completeness of the data. % useless paragraph - JJ
 
@@
 
-After this, the features describing every pattern are frequently analysed.
+After this process, the features describing every pattern are frequently analysed.
 In this case, among the variables describing a new book, some may affect 
-predictions (those variables provide information), while others may not be 
+predictions as they provide information, while others may not be 
 necessary and even redundant.
@@
 % target? - JJ
-Moreover, the algorithm running time grows with the number of
+Additionally, the algorithm running time grows with the number of
 features, making it impractical for problems with a large number of features 

### 2016-05-05 paper.tex
Reduce size tabla 3
Explaining SOM dimensions and errors

@@
 \hline 
-M5P  & 89.0 $\pm$ 0.09  & 214.37 $\pm$ 22.96  & 634.23 $\pm$ 307.76  & 37.46 $\pm$ 3.12  & 48.32 $\pm$ 25.16  & 18.85 $\pm$ 0.61\tabularnewline
-\hline 
-K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  & 0.001 $\pm$ 0.01\tabularnewline
+M5P  &  \textbf{89.0 $\pm$ 0.09}  &  \textbf{214.37 $\pm$ 22.96}  &  \textbf{634.23 $\pm$ 307.76}  &  \textbf{37.46 $\pm$ 3.12}  &  \textbf{48.32 $\pm$ 25.16} & 18.85 $\pm$ 0.61\tabularnewline
+\hline 
+K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
 \hline 
@@
 
-The SOM algorithm is applied with a large map size of $26 \times 16$
-in order to represent the data. % Not enough justification. Did you
-                                % try others? - jj
- The best SOM training results are obtained with a final quantisation
- error of 0.691 and topographic error of 0.046. % explain what is
-                                % quantisation and topographic error
-                                % and why it is important - JJ
+Several configurations for SOM has been tested and the one regarding both the \textit{quantisation error} and \textit{topographic error} has been chosen.
+The first is a measure which represents the average distance between every input pattern and its BMU (i.e.
+how good the map fits the dataset).
+The second error refers to the topology of the map and its preservation, so it measures an average value computed looking at both, the first and the second BMUs for every pattern.
+If they are neighbours (directly connected in the map) a '1' is considered, otherwise a '0' is taken.
+A small value would mean that the map preserves well its topology.
+
+Thus, the chosen map to represent the data has $26 \times 16$ neurons and an hexagonal neighbourhood topology.
+The best SOM training results have been obtained with a final quantisation error of 0.691 and topographic error of 0.046.
+% explain what is quantisation and topographic error and why it is important - JJ
+% Antonio - done. ;)
 
@@
 \hline 
-K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 & 0.002 $\pm$0.004\\
-\hline 
-RF & 91.0 $\pm$0.05 & 198.16 $\pm$19.50 & 589.35 $\pm$195.80 & 34.61 $\pm$2.27 & 44.21 $\pm$11.63 & 3.63 $\pm$0.20\\
+K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
+\hline 
+RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
 \hline 
@@
 \hline 
-M5P & 87.0 $\pm$0.09 & 266.78 $\pm$23.12 & 662.32 $\pm$245.27 & 46.66 $\pm$3.25 & 50.9 $\pm$20.35 & 0.41 $\pm$0.04\\
-\hline 
-K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 & 0.001 $\pm$0.001\\
+M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
+\hline 
+K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
 \hline 
@@
 \hline 
-K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  & 0.001 $\pm$0.004\tabularnewline
-\hline 
-RF & 89.8 $\pm$0.05  & 211.87 $\pm$20.07  & 617.78 $\pm$187.16  & 37.02 $\pm$2.46  & 46.58 $\pm$11.14  & 2.93 $\pm$0.11\tabularnewline
+K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
+\hline 
+RF &  \textbf{89.8 $\pm$0.05}  &  \textbf{211.87 $\pm$20.07}  &  \textbf{617.78 $\pm$187.16}  &  \textbf{37.02 $\pm$2.46}  &  \textbf{46.58 $\pm$11.14}  & 2.93 $\pm$0.11\tabularnewline
 \hline 
@@
 \hline 
-M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
-\hline 
-K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
+M5P  &  \textbf{90.0 $\pm$0.10} &  \textbf{670.24 $\pm$181.05}  &  \textbf{1065.34 $\pm$413.84}  &  \textbf{40.83 $\pm$10.86}  &  \textbf{43.56 $\pm$19.87}  & 0.03 $\pm$0.002\tabularnewline
+\hline 
+K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
 \hline 
@@
 \hline 
-K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
+K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
 \hline 
@@
 \hline 
-SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
+SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
 \hline 
@@
 \hline 
-M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
-\hline 
-K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
+M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
+\hline 
+K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 \hline 
-K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
-\hline 
-RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
+K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
+\hline 
+RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
 \hline 
@@
 \hline 
-M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
+M5P &  \textbf{90.5 $\pm$0.1} &  \textbf{661.81 $\pm$186.17} &  \textbf{1070.24 $\pm$425.66} &  \textbf{40.18 $\pm$10.50} &  \textbf{43.56 $\pm$19.77} & 0.02 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
-\hline 
-RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
-\hline 
-LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
+K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
+\hline 
+RF &  \textbf{86.7 $\pm$0.16} & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
+\hline 
+LR & 84.4 $\pm$0.25 &  \textbf{12.79 $\pm$6.65} &  \textbf{21.52 $\pm$12.54} & 39.47 $\pm$23.35 &  \textbf{50.14 $\pm$35.26} & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 &  \textbf{38.24 $\pm$15.41} & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
 \hline 
@@
 \hline 
-M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
-\hline 
-K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
+M5P  &  \textbf{89.3 $\pm$0.08}  &  \textbf{69.70 $\pm$19.85}  &  \textbf{122.48 $\pm$47.28}  & {38.49 $\pm$11.53}  &  \textbf{46.68 $\pm$16.02} & 0.028 $\pm$0.003\tabularnewline
+\hline 
+K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
+K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF &  \textbf{85.3 $\pm$0.09} &  \textbf{455.7 $\pm$123.96} &  \textbf{686.54 $\pm$198.16} &  \textbf{46.32 $\pm$10.20} &  \textbf{53.03 $\pm$13.05} & 0.07 $\pm$0.003\tabularnewline
 \hline 

### 2016-05-05 paper.tex
Add bold description.

@@
 \begin{table}
-\caption{Predicting Total sales for all publishers (all the features). 10 repetitions, 10-fold cross validation.
+\caption{Predicting Total sales for all publishers (all the features). 10 repetitions, 10-fold cross validation. Best values in bold.
 \label{tab:all_publishers_no_fs}}
 \centering{}%
-\scalebox{0.85}{
+\scalebox{0.78}{
 
@@
 
-Several configurations for SOM has been tested and the one regarding both the \textit{quantisation error} and \textit{topographic error} has been chosen.
-The first is a measure which represents the average distance between every input pattern and its BMU (i.e.
-how good the map fits the dataset).
-The second error refers to the topology of the map and its preservation, so it measures an average value computed looking at both, the first and the second BMUs for every pattern.
-If they are neighbours (directly connected in the map) a '1' is considered, otherwise a '0' is taken.
-A small value would mean that the map preserves well its topology.
-
-Thus, the chosen map to represent the data has $26 \times 16$ neurons and an hexagonal neighbourhood topology.
-The best SOM training results have been obtained with a final quantisation error of 0.691 and topographic error of 0.046.
-% explain what is quantisation and topographic error and why it is important - JJ
-% Antonio - done. ;)
+The SOM algorithm is applied with a large map size of $26 \times 16$
+in order to represent the data. % Not enough justification. Did you
+                                % try others? - jj
+ The best SOM training results are obtained with a final quantisation
+ error of 0.691 and topographic error of 0.046. % explain what is
+                                % quantisation and topographic error
+                                % and why it is important - JJ
 
@@
 \caption{Predicting Total sales for all publishers based on features selected
-by each method.
+by each method. Best values in bold.
 \label{tab:results_all_publishers_fs}}
@@
 \begin{table}
-\caption{Description of publishing companies considered as special cases.}
+\caption{Description of publishing companies considered as special cases.Best values in bold.}
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company) }
+\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company). Best values in bold. }
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company) }
+\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company). Best values in bold. }
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold)}
+\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold). Best values in bold.}
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold))}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold)). Best values in bold.}
 \centering{}%
@@
 % Serif - JJ
-\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS) }
+\caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS). Best values in bold. }
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (ReliefFAttributeEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (SOM-FS)}
+\caption{Predicting Total sales for PublishingCo704 (SOM-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS)}
+\caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS)}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS). Best values in bold.}
 \centering{}%

### 2016-05-05 paper.tex
Extremely minor changes in section 4.2

@@
 could be used for different tasks such as feature selection and data
-clustering and visualisation.
+clustering and visualisation. %Pablo: some cite here?
 
@@
 SOM follows an iterative process applied in two stages: First, the
-weights of the network are initialized randomly then the n-dimensional
+weights of the network are initialized randomly, then the n-dimensional
 input vectors are presented to the network sequentially so the
@@
 assigned different colors. Dark colors between neurons indicate large
-distances (boundaries) while light colors represent similar areas
+distances (boundaries) while ligh colors represent similar areas
 (clusters).
@@
 Also, the SOM graph represents and highlight very clearly those
-regions (clusters) with high training sample concentration and fewer
+regions, or clusters, with high training sample concentration and fewer
 where the samples are scarce.  

### 2016-05-05 paper.tex
answering a comment
Removed parentheses from section 4.3

@@
 
-However, as in the case of new books only some descriptive data are available 
-(compared to those cases in which historical data on sales of published books 
-is available), not all forecasting methods can be used in this specific problem.
+However, as in the case of new books only some descriptive data are available,
+compared to those cases in which historical data on sales of published books 
+is available, not all forecasting methods can be used in this specific problem.
 
@@
 
-Model tree models can learn and tackle tasks with high dimensionality (up to 
-hundreds of attributes) and generate reproducible and comprehensible representations, 
+Model tree models can learn and tackle tasks with high dimensionality, even up to 
+hundreds of attributes, and generate reproducible and comprehensible representations, 
 what makes them potentially more successful in the eyes of decision makers.
@@
 which the unknown instances are classified by relating them to the known 
-instances using a distance measurement/function (Euclidean, Minkowsky or minimax).
+instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
 
@@
 
- \item \emph{Random Forest}: This method is based in the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm.
+ \item \emph{Random Forest}: This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm.
 It was proposed by Breiman \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution.
@@
 the data points to the hyperplane. 
-In both cases, the hyperplane is defined by a subset of training set samples 
-(called support vectors).
+In both cases, the hyperplane is defined by a subset of training set samples, 
+called support vectors.
 %This method works well even if the space is highly dimensional and the problem is not linearly separable.

### 2016-05-05 paper.tex
Discussing M5P models

--- 2016-05-05 paper.tex
@@
 % (Paloma) Agree with Fergu, I don't think we should say this... Please review it.
+
+% [pedro] La cosa es que esta gente toma libros ya publicados y de los que tienen todos los datos de ventas para analizar y obtener patrones de ventas.
+Nosotros trabajamos con datos de libros que ni siquiera se han impreso aún, por lo que no tenemos ni idea de cómo van a funcionar.
+Esta gente dispone de datos de ventas, mientras que nosotros sólo vamos a tener datos relativos a "¿dónde lo vas a poner a la venta?" o "¿vas a dar algún regalo para intentar vender más?" (cosas así).
 
@@
 
-In this section we show the output of one of the models built during the regression, namely we present one of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate an useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).
-
-%***TO DO:*** better explain this
-% Sam will do it
-
-We have considered the publisher that sells the most as a good example case to show.
-
-Figure \ref{fig:decision_tree_best_seller} depicts the obtained decision tree for the best seller publishing company (UDL929).
+In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate a useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).
+The first decision tree is considered for the publisher that sells the most.
+Figure \ref{fig:decision_tree_best_seller} depicts the decision tree for the best seller publishing company (UDL929).
 The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales.
-This tree has been created considering the 10 pre-sales features.
+The second decision tree is for the same publishing company (the same data, but just considering the selected features by RAE method, since it is the one which yields the best results).
+The latter tree is shown in Figure \ref{fig:decision_tree_best_seller_fs}.
+
+Examining both decision trees, it can be noticed that the \texttt{tot\_points\_sale} variable appeared twice in the tree and one of them was at the root.
+This indicates that the total number of points of sale has a major role in forecasting the total sales.
+We can also notice that \texttt{distrib\_novelty} appears at the top of the trees at a higher level compared to the \texttt{ret\_price} variable.
+In addition, both tree models reveal that marketing variables such as the total number of points of sale and the number of units distributed as novelty have higher influence on the prediction than the selling price of the book.
+This interpretation leads us to suggest that companies could probably improve the accuracy of their sales forecasting models by incorporating more marketing related variables in their models.
 
@@
 
-%***TO DO***: comments on the figure\\
-
-Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same publishing company (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).
-
-%***TO DO***: better justify this\\
-
 \begin{figure}[!ht] 
@@
 \end{figure}
-
-%***TO DO***: comments on the figure\\
 
@@
 
-Case 1-A: Developing prediction models to predict Total sales for
-PublishingCo704 with CfsSubsetEval feature selection.
-
 \begin{table}[!ht]
@@
 
-Case 1-A: Developing prediction models to predict Total sales for
-PublishingCo704 with SOM feature selection.
-
 \begin{table}[!ht]
@@
 
-Case 1-B: Developing prediction models to predict Total sales for
-PublishingCo-UDLU11 with CfsSubsetEval feature selection.
-
 \begin{table}[!ht]
@@
 
-Case 1-B: Developing prediction models to predict Total sales for
-PublishingCo-UDLU11 with SOM feature selection.
-
 \begin{table}[!ht]
@@
 
-Case 2-A: Developing prediction models to predict Total sales for
-PublishingCo-UDL929 with CfsSubsetEval feature selection.
-
 \begin{table}[!ht]
@@
 
-Case 2-A: Developing prediction models to predict Total sales for
-PublishingCo-UDL929 with SOM feature selection.
-
 \begin{table}[!ht]
@@
 
-Case 2-B: Developing prediction models to predict Total sales for
-PublishingCo-UDLW12 with CfsSubsetEval feature selection.
-
 \begin{table}[!ht]
@@
 \end{table}
-
-Case 2-B: Developing prediction models to predict Total sales for
-PublishingCo-UDLW12 with SOM feature selection.
 

### 2016-05-06 paper.tex
Corrections and new text about SOM here and there. Please @JJ and @7ossam81 check it

@@
 and to choose an appropriate set of variables, the Self-Organizing Map
-(SOM) \cite{kohonen1998} method has been also applied. % Why? Is that
-                                % one of the two forms of feature
-                                % selection? What do we expect to
-                                % learn from it? - JJ
+(SOM) \cite{kohonen1998} method has been also applied as a `subjective' (based on expert's opinion) feature selection technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.
+
+% Why? Is that one of the two forms of feature selection? What do we expect to learn from it? - JJ 
+% Antonio - explained here and below. Please check.
 
@@
 adjacent areas on the grid. 
-It is a very useful analysis tool for visualising complex data with
-high number of variables in a simple geometric plane. Therefore, it
-could be used for different tasks such as feature selection and data
-clustering and visualisation. %Pablo: some cite here?
+% It is a very useful analysis tool for visualising complex data with high number of variables in a simple geometric plane. 
+%Therefore, it could be used for different tasks such as feature selection and data clustering and visualisation. %Pablo: some cite here?
+This method is normally used as a data visualization tool, since it allows to project any multi-variated dataset in a two-dimensional display, so an expert can detect topological relations among its neurons and thus make inferences or find interesting relationships on the input dataset (such as clusters, for instance).
 
@@
 
-When the learning process is done a visual representation method like
-the Unified Distance Matrix, or U-matrix for short, is used to
-visualize the distances between neurons in the output space. In the
-U-matrix, the distance between adjacent neurons is measured and
-assigned different colors. Dark colors between neurons indicate large
-distances (boundaries) while ligh colors represent similar areas
-(clusters).
+Once the SOM learning process is finished, a visual representation technique, named the Unified distance matrix (U-matrix) \cite{UmatUlts}, has been applied.
+This method uses the obtained codevectors (vectors of variables of the problem) as data source, and generates a matrix where each component is a distance measure between two adjacent neurons.
+In the U-matrix, the distance between adjacent neurons is measured and assigned different colors.
+Different colors between neurons indicate large distances (boundaries) while similar colors represent close areas (clusters).
+
+% Antonio - a better description of U-Matrix. ;D
 
@@
 where the samples are scarce.
+U-Matrix graph, together with the projection of variables into separate planes, the so-called component planes analysis (that SOM yields), will aid an expert to identify the most relevant features on every cluster, i.e.
+those that can have a higher influence on the creation of that cluster.
 %FERGU: mencionarlo en la intro
 % Which is interesting because... JJ
-
-As far as the feature selection methods are concerned, Weka software separates the process into two parts:
-%FERGU: por qué mencionamos a Weka aquí y no antes?
-% Antonio - se ha mencionado, pero sí, habría que destacarlo un poco más desde la intro quizá.
+% Antonio - explained. ;)
+
+With respect to feature selection methods, the used Weka software separates the process into two parts:
+
 \begin{itemize}
@@
 (predictive of) the class, yet uncorrelated with (not predictive of) each other''.
-This evaluator needs the numeric features to be transformed to nominal features first, by being discretised.
+This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.
 The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation.
@@
 
-Figure \ref{fig:componentplanes} shows the U-matrix and component
-variables resulted from SOM training. The term component is used in
+Figure \ref{fig:componentplanes} shows the U-matrix along with the component planes analysis resulted from SOM training. The term component refers in SOM to a variable or feature of the problem.
 % really, are you reading this with the mind of someone that has no
@@
 % interpret the results - JJ
-SOM to refer to the features. %use features!!!! - JJ
- The component planes in Figure %what is a plane? Really, you don't
-                                %know what's in the mind of the reader
-                                %(or reviewer#3, who is a son of a
-                                %bitch - JJ
+% Antonio - now it must be clearer with the new explanations given before
+The component planes in Figure 
+%what is a plane? Really, you don't know what's in the mind of the reader (or reviewer#3, who is a son of a bitch - JJ
+% Antonio - now it should be clear. This is the accurate term for the output of SOM: component planes analysis
 \ref{fig:componentplanes} show the trend of values of the prototype
@@
 there are more hexagons in the U-matrix than component planes since
-the distances between units is also represented as hexagons. % but
+the distances between units are also represented as inter-neuron hexagons. 
+                                % but
                                 % explain that at the beginning!
@@
                                 % section - JJ
+% Antonio - I have done it. However Ihave focused the explanation on the feature selection 'ability' of the method. ;)
 

### 2016-05-09 paper.tex
Revised the descriptio of example decision trees
#Closes 27

Please @7ossam81  and @JJ check this.
Maybe something else could be added to better interpret the models.

@@
 
-In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate a useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).
-The first decision tree is considered for the publisher that sells the most.
-Figure \ref{fig:decision_tree_best_seller} depicts the decision tree for the best seller publishing company (UDL929).
+In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method applied to the data of the publisher that sells the most.
+These aim to demonstrate the value of the proposal to generate a useful decision-aid tool for an expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).
+
+First, Figure \ref{fig:decision_tree_best_seller} depicts the decision tree for the publishing company UDL929.
 The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales.
-The second decision tree is for the same publishing company (the same data, but just considering the selected features by RAE method, since it is the one which yields the best results).
-The latter tree is shown in Figure \ref{fig:decision_tree_best_seller_fs}.
-
-Examining both decision trees, it can be noticed that the \texttt{tot\_points\_sale} variable appeared twice in the tree and one of them was at the root.
-This indicates that the total number of points of sale has a major role in forecasting the total sales.
-We can also notice that \texttt{distrib\_novelty} appears at the top of the trees at a higher level compared to the \texttt{ret\_price} variable.
-In addition, both tree models reveal that marketing variables such as the total number of points of sale and the number of units distributed as novelty have higher influence on the prediction than the selling price of the book.
+The second decision tree (Figure \ref{fig:decision_tree_best_seller_fs}) corresponds to the same publishing company, so the same data were used, but the RAE feature selection method was applied.
+Thus, the main difference in the simplification of the regression models in the second tree and the remove of \texttt{print\_run} as part of the decision process after the feature selection.
+
+Examining both trees, it can be noticed that \texttt{tot\_points\_sale} variable appears twice in the trees, being also the root.
+This indicates that the total number of points of sale has a big influence on the decision models and also a major role in forecasting the total sales.
+This is an interesting clue for the experts, who could check the expected impact of different number of selling points
+According to the trees, \texttt{distrib\_novelty} has also a big repercussion, appearing at the second level of the top of the trees.
+
+An important fact that these tree models reveal is that marketing variables, such as the total number of points of sale and the number of units distributed as novelty have higher influence on the prediction than the selling price of the book, which could be, initially, considered as one of the most important parameters to determine sales.
 This interpretation leads us to suggest that companies could probably improve the accuracy of their sales forecasting models by incorporating more marketing related variables in their models.
@@
 In this paper, the problem of how many books should be printed 
-when a new book is published is faced using several data-mining and
+when a new book is going to be published is faced using several data-mining and
 forecasting methods.

### 2016-05-09 paper.tex
Cambios locales

--- 2016-05-05 paper.tex
@@
 many is the main issue, since it implies a loss of investment due to
-inventory excess, but printing too few will also have a negative economic impact.
+inventory excess, but printing too few will also have a negative economical impact.
 In this paper, we are tackling the problem of predicting total sales in order to print the right amount of books and doing so even before the book has reached the stores.
 A real dataset including the complete sales data for books published in Spain across several years has been used.
-We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualisation techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods has been applied to create forecasting models for book sales.
+We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualisation techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods have been applied to create forecasting models for book sales.
 The obtained models are able to predict sales from pre-publication data with
@@
 distribution, and storage processes; most of these costs are associated
-with the number of books actually printed. But the problem is further
+to the number of books actually printed. But the problem is further
 complicated for completely new products, in the sense that there is an unknown
@@
 \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
-is perhaps the most used technique to tackle sales forecasting
+is perhaps the most used technique to tackle the sales forecasting
 problems. The efficiency of these techniques strongly depends on the field of application 
@@
  They analyse data about
-sales and, taking into account their knowledge of industry, their
+sales and, taking into account their knowledge in industry, their
 experience, and their perception about trends, could make decisions on
@@
 external variables that must be taken into account, such as
-seasonality, promotions, or fashions that expert managers might
+seasonality, promotions or fashions that expert managers might
 subjectively apply \cite{Lapide1999,ChernWSF15}. % This
@@
 However, the authors used in these papers historical data from published books, 
-so their proposed methodology can not be applied to the problem of unpublished books sales prediction.
+so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
 %FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?
-% (Paloma) Agree with Fergu, I don't think we should say this... Please review it.
-
-% [pedro] La cosa es que esta gente toma libros ya publicados y de los que tienen todos los datos de ventas para analizar y obtener patrones de ventas.
-Nosotros trabajamos con datos de libros que ni siquiera se han impreso aún, por lo que no tenemos ni idea de cómo van a funcionar.
-Esta gente dispone de datos de ventas, mientras que nosotros sólo vamos a tener datos relativos a "¿dónde lo vas a poner a la venta?" o "¿vas a dar algún regalo para intentar vender más?" (cosas así).
 
@@
 %
-In the same line, Thomassey et al. \cite{SThomassey2014} proposed using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
-a very similar issue to the new book publishing one. % (Paloma) Very similar? Why?
+In the same line, Thomassey et al. \cite{SThomassey2014} propose using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
+a very similar issue to the new book publishing one.
 The same problem was previously faced by Xia et al. \cite{Xia2012} using a 
@@
 % Antonio - of -> as???
-% (Paloma) It's "of" in the title...
 The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
@@
 In those cases where historical data are available, classical time series 
-forecasting methods can be applied, which is what the authors did in
+forecasting methods can be applied, which is what the authors do in
 \cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
@@
                    % of application and the available problem data. - pedro
-A similar method is described by Chern et al. \cite{ChernWSF15}, who analysed 
-historical data throughout online reviews, reviewer characteristics, and review 
+A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
+historical data along online reviews, reviewer characteristics and review 
 influences to understand how electronic `word-of-mouth' influences product sales. 
@@
 %FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
-descriptive and variables are known in advance related to the new book. In
+descriptive and variables known in advance related to the new book. In
 order to do that, we have used a training dataset which includes
-historical sales data % (Paloma) so, have we or have we not historical data? It's all contradictory
- for a big amount of books published in Spain for
+historical sales data for a big amount of books published in Spain for
 several years, with a set of 50 features or variables per pattern.
@@
 In this prediction problem there are other external variables that also affect 
-the sales of a new book, such as those related to seasonality, trends, or 
+the sales of a new book, such as those related to seasonality, trends or 
 promotions, that classical prediction methods can not deal with. %FERGU: por qué?
@@
 external data. 
-Thus, the proposed method will analyse the provided data and
+Thus, the proposed method, will analyse the provided data and
 variables and will yield a forecast of sales according to them. This
 result could be used as a reference for a human expert, who would
-consider it in his or her own prediction process.
+consider it in his/her own prediction process.
 
@@
 such as those with null values in required variables, or with negative
-sales, for instance. % (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
-Furthermore, the initial set of variables, presented
-in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to
+sales, for instance. Moreover, the initial set of variables (presented
+in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
 use just those that can be known in advance when a new book is
-launched, i.e. \textit{pre-sales data}. % (Paloma) Where are they? In table 2?
+launched, i.e. \textit{pre-sales data}.
 
@@
 prediction problem. 
-  In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
+  In this stage, both, numerical and visualisation-based approaches have been applied in this paper, in order to select the best variables for the forecasting 
 methods.  
@@
 
-Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal.
+Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing companies) in order to prove the value of the proposal.
 Some specific interpretable models have been created as a final result of the work.
-The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.
+The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).
 
@@
 
-In general, historical data are used to make time series, as well as for extracting common patterns and obtaining accurate predictions from them.
+In general, historical data are used to make time series, and from them extracting common patterns and obtaining accurate predictions.
 However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
-\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem. %PABLO: pre-sales data is mentioned briefly in introduction, expand it
-
-Due to this situation, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
-those whose value do not depend on the book sales.
-Therefore, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
+\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem.
+
+Moreover, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
+those whose value don't depend on the book sales.
+So, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
 
@@
 % preliminary selection - JJ
-\caption{Considered pre-sales features and their types. The third column shows
-  the names of the variables used in the applied methods, and the last one indicates if they have been used as an input (independent) or an output (dependent) variable.} 
+\caption{Considered pre-sales features and their types. It also shows
+  the names of the variables used in the applied methods and if everyone is an input (independent) or an output (dependent) variable.} 
 \label{tabla:params_pre_sales}
@@
 As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods.
-On the other hand, \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
+\texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
 In addition, this variable could be interesting to be used to test the prediction model, once it is built.
-Hence, the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
-%Pablo: still waiting the definition of the variables
+So the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
 
@@
 
-With regard to the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
+Regarding the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
 In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing companies for predicting its own sales.
 % Antonio - Think about this... should we mention this?
-% (Paloma) If you finally leave it, please review it because this last sentence is a bit confusing
-
-Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \cite{wiki:dewey}, and the existing similarity relationship between the books inside a class or subclass.
+
+Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass.
 So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance.
@@
 
-Preprocessing a dataset means that it is revised in order to reduce errors, such as wrong or duplicated patterns, or for completing missing values. The aim is to look for the correctness,
-homogeneity, and completeness of the data. % useless paragraph - JJ
+Once a dataset has been composed it must be preprocessed, i.e. it
+should be revised in order to fix the existing errors (such as wrong
+or duplicated patterns), or to complete (or address) the absence of
+information, for instance. The aim is looking for the correctness,
+homogeneity and completeness of the data. % useless paragraph - JJ
 
@@
 
-After this process, the features describing every pattern are frequently analysed.
+After this, the features describing every pattern are frequently analysed.
 In this case, among the variables describing a new book, some may affect 
-predictions as they provide information, while others may not be 
+predictions (those variables provide information), while others may not be 
 necessary and even redundant.
@@
 % target? - JJ
-Additionally, the algorithm running time grows with the number of
+Moreover, the algorithm running time grows with the number of
 features, making it impractical for problems with a large number of features 
@@
 could be used for different tasks such as feature selection and data
-clustering and visualisation. %Pablo: some cite here?
+clustering and visualisation.
 
@@
 SOM follows an iterative process applied in two stages: First, the
-weights of the network are initialized randomly, then the n-dimensional
+weights of the network are initialized randomly then the n-dimensional
 input vectors are presented to the network sequentially so the
@@
 assigned different colors. Dark colors between neurons indicate large
-distances (boundaries) while ligh colors represent similar areas
+distances (boundaries) while light colors represent similar areas
 (clusters).
@@
 Also, the SOM graph represents and highlight very clearly those
-regions, or clusters, with high training sample concentration and fewer
+regions (clusters) with high training sample concentration and fewer
 where the samples are scarce.  
@@
 \begin{table}
-\caption{Predicting Total sales for all publishers (all the features). 10 repetitions, 10-fold cross validation. Best values in bold.
+\caption{Predicting Total sales for all publishers (all the features). 10 repetitions, 10-fold cross validation.
 \label{tab:all_publishers_no_fs}}
 \centering{}%
-\scalebox{0.78}{
+\scalebox{0.85}{
 
@@
 \hline 
-M5P  &  \textbf{89.0 $\pm$ 0.09}  &  \textbf{214.37 $\pm$ 22.96}  &  \textbf{634.23 $\pm$ 307.76}  &  \textbf{37.46 $\pm$ 3.12}  &  \textbf{48.32 $\pm$ 25.16} & 18.85 $\pm$ 0.61\tabularnewline
-\hline 
-K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
+M5P  & 89.0 $\pm$ 0.09  & 214.37 $\pm$ 22.96  & 634.23 $\pm$ 307.76  & 37.46 $\pm$ 3.12  & 48.32 $\pm$ 25.16  & 18.85 $\pm$ 0.61\tabularnewline
+\hline 
+K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  & 0.001 $\pm$ 0.01\tabularnewline
 \hline 
@@
 
-After applying the feature selection methods, we have run the same forecasting models as in Section \ref{subsec:results_all_publishers} for the whole dataset (all the publishers), but considering only the selected features by each method.
-The results are shown in Table \ref{tab:results_all_publishers_fs}.
-Examining the obtained results for each feature selection method, it can be seen that RFE got the best results compared to SOM and CSE.
-It can be noticed also that the performance of M5P, kNN and RF has been improved with RFE compared to the case of using all features.
+After applying the feature selection methods, we have run the same
+forecasting models as in Section \ref{subsec:results_all_publishers}
+for the whole dataset (all the publishers), but considering only the
+selected features by each method. The results are shown in Table
+\ref{tab:results_all_publishers_fs}. Examining the obtained results
+for each feature selection method, it can be seen that RFE got the
+best results compared to SOM and CSE. It can be noticed also that we
+obtain better performance in M5P, kNN and RF using only features
+selected by RFE than using all features. %Better publish results in
+                                %the same table or refer to the table
+                                %where it was published. Is this
+                                %difference statistically significant?
+                                %- JJ
  In general, all feature selection methods have reduced the training time needed to build the forecasting methods, this is because they reduced the features and excluded the categorical features that have many possible values.
@@
 \caption{Predicting Total sales for all publishers based on features selected
-by each method. Best values in bold.
+by each method.
 \label{tab:results_all_publishers_fs}}
@@
 \resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
+\begin{tabular}{|c|l|l|l|l|l|l|}
 \hline 
@@
 \hline 
-K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
-\hline 
-RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
+K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 & 0.002 $\pm$0.004\\
+\hline 
+RF & 91.0 $\pm$0.05 & 198.16 $\pm$19.50 & 589.35 $\pm$195.80 & 34.61 $\pm$2.27 & 44.21 $\pm$11.63 & 3.63 $\pm$0.20\\
 \hline 
@@
 \hline 
-M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
-\hline 
-K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
+M5P & 87.0 $\pm$0.09 & 266.78 $\pm$23.12 & 662.32 $\pm$245.27 & 46.66 $\pm$3.25 & 50.9 $\pm$20.35 & 0.41 $\pm$0.04\\
+\hline 
+K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 & 0.001 $\pm$0.001\\
 \hline 
@@
 \hline 
-K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
-\hline 
-RF &  \textbf{89.8 $\pm$0.05}  &  \textbf{211.87 $\pm$20.07}  &  \textbf{617.78 $\pm$187.16}  &  \textbf{37.02 $\pm$2.46}  &  \textbf{46.58 $\pm$11.14}  & 2.93 $\pm$0.11\tabularnewline
+K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  & 0.001 $\pm$0.004\tabularnewline
+\hline 
+RF & 89.8 $\pm$0.05  & 211.87 $\pm$20.07  & 617.78 $\pm$187.16  & 37.02 $\pm$2.46  & 46.58 $\pm$11.14  & 2.93 $\pm$0.11\tabularnewline
 \hline 
@@
 \begin{table}
-\caption{Description of publishing companies considered as special cases.Best values in bold.}
+\caption{Description of publishing companies considered as special cases.}
 \centering{}%
@@
 \begin{table}
-\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company). Best values in bold. }
+\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company) }
 \centering{}%
@@
 \hline 
-M5P  &  \textbf{90.0 $\pm$0.10} &  \textbf{670.24 $\pm$181.05}  &  \textbf{1065.34 $\pm$413.84}  &  \textbf{40.83 $\pm$10.86}  &  \textbf{43.56 $\pm$19.87}  & 0.03 $\pm$0.002\tabularnewline
-\hline 
-K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
+M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
+\hline 
+K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
 \hline 
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company). Best values in bold. }
+\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company) }
 \centering{}%
@@
 \hline 
-K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
+K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
+\hline 
+RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
 \hline 
@@
 \hline 
-SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
+SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
 \hline 
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold)}
 \centering{}%
@@
 \hline 
-M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
-\hline 
-K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
+\hline 
+K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
 \hline 
@@
 \begin{table}
-\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold)). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold))}
 \centering{}%
@@
 \hline 
-K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
-\hline 
-RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
+K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
+\hline 
+RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
 \hline 
@@
 % Serif - JJ
-\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS)}
 \centering{}%
@@
 \hline 
-M5P &  \textbf{90.5 $\pm$0.1} &  \textbf{661.81 $\pm$186.17} &  \textbf{1070.24 $\pm$425.66} &  \textbf{40.18 $\pm$10.50} &  \textbf{43.56 $\pm$19.77} & 0.02 $\pm$0.002\tabularnewline
-\hline 
-K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
+\hline 
+K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
 \hline 
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS)}
 \centering{}%
@@
 \hline 
-K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
-\hline 
-RF &  \textbf{86.7 $\pm$0.16} & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
-\hline 
-LR & 84.4 $\pm$0.25 &  \textbf{12.79 $\pm$6.65} &  \textbf{21.52 $\pm$12.54} & 39.47 $\pm$23.35 &  \textbf{50.14 $\pm$35.26} & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 &  \textbf{38.24 $\pm$15.41} & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
+K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
+\hline 
+RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
+\hline 
+LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
 \hline 
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS). Best values in bold. }
+\caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS) }
 \centering{}%
@@
 \hline 
-M5P  &  \textbf{89.3 $\pm$0.08}  &  \textbf{69.70 $\pm$19.85}  &  \textbf{122.48 $\pm$47.28}  & {38.49 $\pm$11.53}  &  \textbf{46.68 $\pm$16.02} & 0.028 $\pm$0.003\tabularnewline
-\hline 
-K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
+\hline 
+K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
 \hline 
@@
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (ReliefFAttributeEval-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (ReliefFAttributeEval-FS)}
 \centering{}%
@@
 \hline 
-K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF &  \textbf{85.3 $\pm$0.09} &  \textbf{455.7 $\pm$123.96} &  \textbf{686.54 $\pm$198.16} &  \textbf{46.32 $\pm$10.20} &  \textbf{53.03 $\pm$13.05} & 0.07 $\pm$0.003\tabularnewline
+K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
+\hline 
+RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
 \hline 
@@
 
-In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate a useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).
-The first decision tree is considered for the publisher that sells the most.
-Figure \ref{fig:decision_tree_best_seller} depicts the decision tree for the best seller publishing company (UDL929).
+In this section we show the output of one of the models built during the regression, namely we present one of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate an useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).
+
+%***TO DO:*** better explain this
+% Sam will do it
+
+We have considered the publisher that sells the most as a good example case to show.
+
+Figure \ref{fig:decision_tree_best_seller} depicts the obtained decision tree for the best seller publishing company (UDL929).
 The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales.
-The second decision tree is for the same publishing company (the same data, but just considering the selected features by RAE method, since it is the one which yields the best results).
-The latter tree is shown in Figure \ref{fig:decision_tree_best_seller_fs}.
-
-Examining both decision trees, it can be noticed that the \texttt{tot\_points\_sale} variable appeared twice in the tree and one of them was at the root.
-This indicates that the total number of points of sale has a major role in forecasting the total sales.
-We can also notice that \texttt{distrib\_novelty} appears at the top of the trees at a higher level compared to the \texttt{ret\_price} variable.
-In addition, both tree models reveal that marketing variables such as the total number of points of sale and the number of units distributed as novelty have higher influence on the prediction than the selling price of the book.
-This interpretation leads us to suggest that companies could probably improve the accuracy of their sales forecasting models by incorporating more marketing related variables in their models.
+This tree has been created considering the 10 pre-sales features.
 
@@
 
+%***TO DO***: comments on the figure\\
+
+Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same publishing company (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).
+
+%***TO DO***: better justify this\\
+
 \begin{figure}[!ht] 
@@
 \end{figure}
+
+%***TO DO***: comments on the figure\\
 
@@
 
+Case 1-A: Developing prediction models to predict Total sales for
+PublishingCo704 with CfsSubsetEval feature selection.
+
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS)}
 \centering{}%
@@
 
+Case 1-A: Developing prediction models to predict Total sales for
+PublishingCo704 with SOM feature selection.
+
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (SOM-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo704 (SOM-FS)}
 \centering{}%
@@
 
+Case 1-B: Developing prediction models to predict Total sales for
+PublishingCo-UDLU11 with CfsSubsetEval feature selection.
+
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS)}
 \centering{}%
@@
 
+Case 1-B: Developing prediction models to predict Total sales for
+PublishingCo-UDLU11 with SOM feature selection.
+
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS)}
 \centering{}%
@@
 
+Case 2-A: Developing prediction models to predict Total sales for
+PublishingCo-UDL929 with CfsSubsetEval feature selection.
+
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS)}
 \centering{}%
@@
 
+Case 2-A: Developing prediction models to predict Total sales for
+PublishingCo-UDL929 with SOM feature selection.
+
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS)}
 \centering{}%
@@
 
+Case 2-B: Developing prediction models to predict Total sales for
+PublishingCo-UDLW12 with CfsSubsetEval feature selection.
+
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS)}
 \centering{}%
@@
 
+Case 2-B: Developing prediction models to predict Total sales for
+PublishingCo-UDLW12 with SOM feature selection.
+
 \begin{table}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS)}
 \centering{}%

### 2016-05-09 paper.tex
Adding reference to justify why we follow these steps in the methodology

--- 2016-05-09 paper.tex
@@
 
-There is not a standard methodology to solve the general problem of sales forecasting. The steps we have followed in this paper are described below.
+There is not a standard methodology to solve the general problem of sales forecasting.
+This is why the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}.
+These are described below.
 % Antonio - quito esto porque ya no es lo que se ha hecho. El objetivo del paper no es la metodología a seguir, eso es estándar. ;)
@@
 \subsection{Data collection}
+\label{subsec:data_collection}
 
@@
 \subsection{Selecting an appropriate forecasting method}
+\label{subsec:select_method}
 
@@
 
-After applying the feature selection methods, we have run the same
-forecasting models as in Section \ref{subsec:results_all_publishers}
-for the whole dataset (all the publishers), but considering only the
-selected features by each method. The results are shown in Table
-\ref{tab:results_all_publishers_fs}. Examining the obtained results
-for each feature selection method, it can be seen that RFE got the
-best results compared to SOM and CSE. It can be noticed also that we
-obtain better performance in M5P, kNN and RF using only features
-selected by RFE than using all features. %Better publish results in
-                                %the same table or refer to the table
-                                %where it was published. Is this
-                                %difference statistically significant?
-                                %- JJ
+After applying the feature selection methods, we have run the same forecasting models as in Section \ref{subsec:results_all_publishers} for the whole dataset (all the publishers), but considering only the selected features by each method.
+The results are shown in Table \ref{tab:results_all_publishers_fs}.
+Examining the obtained results for each feature selection method, it can be seen that RFE got the best results compared to SOM and CSE.
+It can be noticed also that the performance of M5P, kNN and RF has been improved with RFE compared to the case of using all features.
 In general, all feature selection methods have reduced the training time needed to build the forecasting methods, this is because they reduced the features and excluded the categorical features that have many possible values.

### 2016-05-09 paper.tex
Created a subsection for the evaluation measures

--- 2016-05-09 paper.tex
@@
 %
-The obtained results have been compared and analysed, computing, in addition to the obtained \textit{correlation coefficient}, some error measures from the literature \cite{ChingChin2010,Madsen2008}.
-We have considered the widely accepted standard formulae \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
-Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
-%FERGU: have been selected for this methodology, for this work... algo así
-% Antonio - ya se ha dicho. ;)
-
-\begin{itemize}
-  \item \emph{Mean Absolute Error} (MAE):
-        \begin{equation}\label{eq:MAE}
-            MAE = \frac{1}{n}\sum_{i=1}^n {\mid p_i - o_i\mid}
-        \end{equation}
-
-  \item \emph{Root Mean Squared Error} (RMSE):
-        \begin{equation}\label{eq:RMSE}
-            RMSE = \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 }
-        \end{equation}
-
-  \item \emph{Relative absolute error} (RAE):
-        \begin{equation}\label{eq:RAE}
-            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid \bar{o} - o_i\mid} }
-        \end{equation}
-
-  \item \emph{Root relative squared error} (RRSE):
-        \begin{equation}\label{eq:RRSE}
-            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
-        \end{equation}
-\end{itemize}
-where $o_i$ is the actual value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
 
@@
 published.
+
+\subsection{Models evaluation}
+
+At this step, the developed forecasting models are evaluated and assessed based on different evaluation criteria.
+In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
+Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
+%FERGU: have been selected for this methodology, for this work... algo así
+% Antonio - ya se ha dicho. ;)
+
+\begin{itemize}
+  \item \emph{Mean Absolute Error} (MAE):
+        \begin{equation}\label{eq:MAE}
+            MAE = \frac{1}{n}\sum_{i=1}^n {\mid p_i - o_i\mid}
+        \end{equation}
+
+  \item \emph{Root Mean Squared Error} (RMSE):
+        \begin{equation}\label{eq:RMSE}
+            RMSE = \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 }
+        \end{equation}
+
+  \item \emph{Relative absolute error} (RAE):
+        \begin{equation}\label{eq:RAE}
+            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid \bar{o} - o_i\mid} }
+        \end{equation}
+
+  \item \emph{Root relative squared error} (RRSE):
+        \begin{equation}\label{eq:RRSE}
+            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
+        \end{equation}
+\end{itemize}
+where $o_i$ is the actual value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
 

### 2016-05-12 paper.tex
Sections 3 and 4 Improved

@@
 \cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
-them are categorical, which makes them harder to process, even more so if the number
-of categories is high. As stated in those works, given these issues, finding adequate
-forecasting techniques and selecting the best method to use is also a problem.
+them are categorical, which makes them harder to process, even more so if the number of categories is high.
+As stated in those works, given these issues, finding adequate forecasting techniques and selecting the best method to use is also a problem.
 
@@
 been generally based on experts' experience.% Reference - JJ
- They analyse data about
-sales and, taking into account their knowledge of industry, their
-experience, and their perception about trends, could make decisions on
-the companies production, i.e. how many books should be printed when a new
-book is published. 
+ They analyse data about sales and, taking into account their knowledge of industry, their experience, and their perception about trends, could make decisions on the companies production, i.e.
+how many books should be printed when a new book is published.
 This is a complex problem, since the predictions are influenced by
@@
   %     Moon2010ICEC
-Recently, some works have proposed analysing relationships between on-line information 
-and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
-et al. propose using the number of blog references as an indicator of
+Recently, some works have proposed analysing relationships between on-line information and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}.
+Specifically, Moon et al.
+propose using the number of blog references as an indicator of
 the success of a book, and thus, its sales. Different sales patterns
-are observed by analysing data obtained. 
+are observed by analysing the obtained data. 
 % Antonio - describir esos 'sales patterns'. ;)
 % FERGU: y también cuales son esos 'data obtained'
-However, the authors used in these papers historical data from published books, 
-so their proposed methodology can not be applied to the problem of unpublished books sales prediction.
+%The authors considered in these papers historical data from published books, 
+%so their proposed methodology can not be applied to the problem of unpublished %books sales prediction.
 %FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?
@@
 Esta gente dispone de datos de ventas, mientras que nosotros sólo vamos a tener datos relativos a "¿dónde lo vas a poner a la venta?" o "¿vas a dar algún regalo para intentar vender más?" (cosas así).
+
+% Antonio - He intentado escribirlo, pero no me queda claro...
+Los datos que tenemos son también de libros ya publicados, ¿no?.
+Estamos considerando variables pre-venta sólamente, eso sí, pero usando datos históricos queremos predecir ventas futuras.
+% Quizá lo que habría que señalar (aquí y en los demás sitios que se dice lo de los datos históricos) es lo de las variables que se consideran, si son variables post-venta o pre-venta, como es nuestro caso.
+;)
 
@@
 
+In general, historical data are used to make time series, as well as for extracting common patterns and obtaining accurate predictions from them.
+However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
+\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem. %PABLO: pre-sales data is mentioned briefly in introduction, expand it
+
 In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
@@
 forecasting method based on extreme machine learning with adaptive metrics of inputs.
-% Antonio - of -> as???
-% (Paloma) It's "of" in the title...
+
 The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
-% Antonio - ver si está bien el cambio 'large number' -> 'majority'
 and on the influence of variables such as promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
@@
 historical data are available, the classical forecasting methods based
-on time-series are not 
-adequate, although they can obviously be used once the book has been launched for sale. 
+on time-series are not adequate, although they can obviously be used once the book has been launched for sale. 
 In our work the relevant variables in the prediction of sales are identified
@@
 
-The main objective of this paper is to forecast sales for 
-%FERGU: el objetivo es la herramienta o la predicción?
-unpublished books for which no historical data are available. Instead, just some
-%FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
-descriptive and variables are known in advance related to the new book. In
-order to do that, we have used a training dataset which includes
-historical sales data % (Paloma) so, have we or have we not historical data? It's all contradictory
- for a big amount of books published in Spain for
-several years, with a set of 50 features or variables per pattern.
-
-The initial dataset, provided in the framework of a contract by
-Trevenque Editorial S.L., included 3159 books. Table
+The problem to solve in this work is the forecasting of sales for new launched books in the Spanish market, considering a set of `pre-sales variables'.
+The objective is to offer a tool for publishers which will aid them to decide the best print run for a new book which before its publication process starts.
+This is a forecasting problem for which no specific historical data are available, since the same book has not been previously published.
+However, we have considered data about other previously published books and have taken as reference a set of variables (or features), related with the book publication process.
+
+The training dataset included historical data about 6083 books published in Spain for several years, with an initial set of 50 variables per pattern.
+It was provided by the Spanish publishing company Trevenque Editorial S.L..
+Table
 \ref{tabla:paramsOrig50} shows the initial set of variables describing
@@
 
-% Antonio - briefly describe the variables
-
-In this prediction problem there are other external variables that also affect 
-the sales of a new book, such as those related to seasonality, trends, or 
-promotions, that classical prediction methods can not deal with. %FERGU: por qué?
-However, an expert can consider them to modify the forecast obtained by 
-the automatic method. Even publishing companies tend to define rules or 
-indexes to subjectively adjust the results of prediction based on
-external data. 
-Thus, the proposed method will analyse the provided data and
-variables and will yield a forecast of sales according to them. This
-result could be used as a reference for a human expert, who would
-consider it in his or her own prediction process.
-
-% This section is too short and really does not describe the problem
-% to its full extent. First, it should say if some of these variables
-% were discarded for some reason. Group the variables we have in those
-% available to publisher and those that can be used afterwards. And
-% then give an idea of the complexity of the problem and how difficult
-% it should be to find a solution - JJ
-
-%********************************************************************************
-\section{Methodology}
-\label{sec:methodology}
-
-There is not a standard methodology to solve the general problem of sales forecasting.
-This is why the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}.
-These are described below.
-% Antonio - quito esto porque ya no es lo que se ha hecho. El objetivo del paper no es la metodología a seguir, eso es estándar. ;)
-%FERGU: hacer más hincapié de esto en la intro entonces
-%In this work we have followed these steps: %FERGU: por qué estos steps y no otros? Ponerlo aquí. Esta metodología es general o solo para este paper?
-%\hspace{2cm}
-%\begin{verbatim}
-%  Step 1: Collect and analyse data
-%       - Data preprocessing
-%       - Feature selection
-%  Step 2: Select the best forecasting method
-%       - Evaluate forecasting models
-%       - Perform forecast
-%  Step 3: Subjectively adjust obtained results
-%      - Apply additional expert knowledge, such as information 
-%        about seasonality or trends.
-%\end{verbatim}
-
-%Usually, a preliminary analysis of the data is carried out to eliminate those 
-%variables that describe the product but do not provide useful information during 
-%the prediction process.
-
-First, after the publishing company has provided the raw data
-(extracted directly from its database), a preprocessing method has
-% This should go to the previous section. 
-been performed in order to remove incorrect or incoherent patterns,
-such as those with null values in required variables, or with negative
-sales, for instance. % (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
-Furthermore, the initial set of variables, presented
-in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to
-use just those that can be known in advance when a new book is
-launched, i.e. \textit{pre-sales data}. % (Paloma) Where are they? In table 2?
-
-% You have to present the problem and not the solution. It's not "what
-% you did last summer", it is SCIENCE. Why did you think FS was
-% needed? What procedure did you use for it?
-Then, a Feature Selection (FS) process \cite{kittler1986feature} has
-been carried out, as it is an effective dimensionality reduction
-technique and an essential preprocessing method to discard `noisy'
-(non-useful) features \cite{Krishnapuram2004}. The aim of these
-% Did you know there were noisy features? Why? 
-% You should include in the previous section an exploratory data
-% analysis that describes the range of variables, how many categories
-% those variables have, and so an do forth - JJ 
-algorithms is exploring the space of attributes to find out which
-subset of them yields the best results in a classification or
-prediction problem. 
-  In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
-methods.  
-% Antonio - Decidir si es 'forecasting' o 'regression' (o si son indiferentes) y usarlo siempre en el texto
-  This task may also help to identify leading indicators to be considered by a human expert to make predictions.
-
-Moreover, the application of FS also aims to reduce the computational time for building the forecasting models, along with the complexity of the obtained models themselves.
-This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).
-
-After this process, several forecasting techniques have been tested, such as rule- or tree-based, together with numerical methods. 
-% Antonio - is 'numerical' the best term for these kind of methods?
-%FERGU: OJO que en esta sección a veces usáis el presente perfecto (have been) y otras el presente (is performed)
-% Antonio - Corregido. ;)
-%
-
-Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal.
-Some specific interpretable models have been created as a final result of the work.
-The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.
-
-%The created forecasting models and results, along with the selected subset of features, are analysed and presented to the experts in order to aid his/her decision.
-They might manually adjust the forecasting results taking into account their knowledge in industry experience and their perception about trends.
-
-%FERGU: poner aquí algo de un párrafo que explique como se valida la metodología
-% Antonio - TODO: esto habrá que explicarlo mejor cuando esté hecho y veamos lo que sale. ;)
-
-%-------------------------------------------------
-\subsection{Data collection}
-\label{subsec:data_collection}
-
-In general, historical data are used to make time series, as well as for extracting common patterns and obtaining accurate predictions from them.
-However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
-\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem. %PABLO: pre-sales data is mentioned briefly in introduction, expand it
-
-Due to this situation, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e.
-those whose value do not depend on the book sales.
-Therefore, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.
+Starting from these raw data, a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance.
+% (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
+% Antonio - because we should not fill important variables automatically, this adds noise to the data, so I think it is better to remove these patterns, since there are still a lot in the dataset. 
+% Indeed, there were just a couple of patterns without important values, that probably were errors of the extraction process or bad insertions in the database.
+Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to use just those that can be known before a new book is launched, i.e.
+\textit{pre-sales data}.
+Thus, their value do not depend on the book sales.
+The selected the subset of features is described in Table \ref{tabla:params_pre_sales}.
 
@@
 % preliminary selection - JJ
+% Antonio - done
 \caption{Considered pre-sales features and their types. The third column shows
@@
 \begin{center}
+\resizebox{12cm}{!}{
 \begin{tabular}{|c|l|l|c|c|}
@@
 \end{tabular}
+}
 \end{center}
@@
 
-With regard to the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}.
-In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing companies for predicting its own sales.
+With regard to the feature \textit{publisher}, it has been removed from the final dataset since it is indeed included in the code of \texttt{collection}.
+In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers probably will not want to use the results of other publishing companies for predicting their own sales.
 % Antonio - Think about this... should we mention this?
 % (Paloma) If you finally leave it, please review it because this last sentence is a bit confusing
+% Antonio - I guess it is now clearer
 
@@
 
+In this prediction problem there are other external variables that also affect 
+the sales of a new book, such as those related to seasonality, trends, or 
+promotions, that classical prediction methods can not deal with, since they are not included in the dataset due to the difficulty to model them. %FERGU: why?
+% Antonio - explained.
+However, an expert can consider them to modify the forecast obtained by 
+the automatic method. Even publishing companies tend to define rules or 
+indexes to subjectively adjust the results of prediction based on
+external data. 
+Thus, the proposed method will analyse the provided data and
+variables and will yield a forecast of sales according to them. This
+result could be used as a reference for a human expert, who would
+consider it in his or her own prediction process.
+
+% This section is too short and really does not describe the problem
+% to its full extent. First, it should say if some of these variables
+% were discarded for some reason. Group the variables we have in those
+% available to publisher and those that can be used afterwards. And
+% then give an idea of the complexity of the problem and how difficult
+% it should be to find a solution - JJ
+% Antonio - I have included much more contents form other sections. could you do the rest?
+
+% You should include data visualization in problem description,
+% because it shows the distribution of problem variables and then
+% suggests ways to deal with it - JJ
+% You should include in the section an exploratory data
+% analysis that describes the range of variables, how many categories
+% those variables have, and so an do forth - JJ
+% Antonio - as you know SOM has been applied later as a feature selection method...
+I don't know if we could reference the figure of SOM here or the other way round (do the analysis here and reference later), but in that case, we should explain SOM before, which could be a mess...
+% Antonio - If you meant using other visualization methods... could you do it also?
+
+%********************************************************************************
+\section{Methodology}
+\label{sec:methodology}
+
+There is not a standard methodology to solve the general problem of sales forecasting.
+This is why the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}.
+These are described in the following sections.
+
+As a summary, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques are applied, such as Feature Selection (FS) \cite{kittler1986feature} (see Section \ref{subsec:data_preproces}).
+These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain easier-to-interpret models, in a less amount of time (due to their lower complexity), and with a fair or, hopefully, better accuracy.
+This task may also help to identify leading indicators to be considered by a human expert to make predictions.
+
+% You have to present the problem and not the solution. It's not "what
+% you did last summer", it is SCIENCE. Why did you think FS was
+% needed? What procedure did you use for it?
+% Antonio - done
+In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
+methods.  
+% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Coudl they be used with the same meaning?
+
+After this process (in Section \ref{subsec:select_method}), a selection of the best forecasting techniques have been conducted, looking for those rule- or tree-based, together with numerical methods which could yield the best results.
+
+Once the models and results have been obtained for the whole dataset (Section \ref{sec:experiments}), the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}).
+Some specific interpretable models have been created as a final result of the work.
+The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.
+
 %-------------------------------------------------
-\subsection{Data preprocessing and initial analysis}
+%\subsection{Data collection}
+%\label{subsec:data_collection}
+
+%-------------------------------------------------
+\subsection{Data preprocessing by feature selection}
 \label{subsec:data_preproces}
+
+Then, a Feature Selection (FS) process  has
+been carried out, as  It is an effective dimensionality reduction
+technique and an essential preprocessing method to discard `noisy'
+(non-useful) features \cite{Krishnapuram2004}.
+
+The aim of these
+% Did you know there were noisy features? Why?
+
+algorithms is exploring the space of attributes to find out which
+subset of them yields the best results in a classification or
+prediction problem.
+
+Moreover, the application of FS also aims to reduce the computational time for building the forecasting models, along with the complexity of the obtained models themselves.
+This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).
 
@@
 Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
-%FERGU: have been selected for this methodology, for this work... algo así
-% Antonio - ya se ha dicho. ;)
 
@@
 %La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
-A dataset consisting of 3159 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
+A dataset consisting of 6000 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
 publishing company Trevenque Editorial S.L. has been used.

### 2016-05-12 paper.tex
Section about Feature Selection Revised and Improved

@@
 
-Then, a Feature Selection (FS) process  has
-been carried out, as  It is an effective dimensionality reduction
-technique and an essential preprocessing method to discard `noisy'
-(non-useful) features \cite{Krishnapuram2004}.
-
-The aim of these
-% Did you know there were noisy features? Why?
-
-algorithms is exploring the space of attributes to find out which
-subset of them yields the best results in a classification or
-prediction problem.
-
-Moreover, the application of FS also aims to reduce the computational time for building the forecasting models, along with the complexity of the obtained models themselves.
-This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).
-
-Preprocessing a dataset means that it is revised in order to reduce errors, such as wrong or duplicated patterns, or for completing missing values. The aim is to look for the correctness,
-homogeneity, and completeness of the data. % useless paragraph - JJ
-
+At this stage, a Feature Selection (FS) process has been carried out, since it is an effective dimensionality reduction technique and an essential preprocessing method to discard less relevant or non-useful features \cite{Krishnapuram2004}.
+
+The aim of these algorithms is exploring the space of attributes to find out which subset of them yields the best results in a classification or prediction problem.
+To this end, the features describing every pattern are analysed.
+In this case, among the variables describing a new book, some may affect predictions as they provide information, while others may not be necessary and even redundant.
+
+The application of FS also aims to reduce the complexity of the obtained forecasting models themselves, which, in turn, implies a reduction in the computational time for building these models.
+The first has been a key factor in this work, because one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).
+Regarding the algorithm running, it time grows with the number of
+features, making it impractical for problems with a large number of features 
+\cite{Selvakuberan2008}, but this is a secondary objective in this work.
 %You need to lay out to the reader what you are going to do here. In
@@
 %z. After using z, we prove that we have done y and thus reached
-%objective x. For instance
-% A exploratory data analysis that shows the distribution of variables
-% as well as a priori clusters is the first phase in any data
-% processing method
-% (BTW, you should include data visualization in problem description,
-% because it shows the distribution of problem variables and then
-% suggests ways to deal with it) - JJ
-% and so on...
-
-After this process, the features describing every pattern are frequently analysed.
-In this case, among the variables describing a new book, some may affect 
-predictions as they provide information, while others may not be 
-necessary and even redundant.
+%objective x. For instance - JJ
+% Antonio - Now it has been explained
 
@@
 % target? - JJ
-Additionally, the algorithm running time grows with the number of
-features, making it impractical for problems with a large number of features 
-\cite{Selvakuberan2008}. Feature reduction is a task that is usually
-applied in these kind of situations, having two ways of performance
-\cite{kittler1986feature}: feature extraction and feature selection.  
-% two ways of performance? WTF? Do you mean "being performed in two
-% different ways?" - JJ
-%Feature selection task is usually carried out by 
-%searching through all possible combinations of features, evaluating each one.
+% Antonio - I have explained before. The aim is not reducing the time, but the complexity of the obtained models in order to be more useful for a human
 
@@
 
-Feature extraction is a ``transformation-based approach'', therefore
-it transforms the original meaning of the features. This approach
+FS is one of the ways of performing a feature reduction, the other one is feature extraction \cite{kittler1986feature}. 
+Feature extraction is a `transformation-based approach', therefore
+it transforms the original meaning of the features. This method
 involves creating a subset of new features by combinations of the
@@
 original dataset will not be needed by any future process. On the
-contrary, feature selection attempts to retain the meaning of the
+contrary, FS attempts to retain the meaning of the
 original feature set. It is part of what is called semantic-preserving
-techniques, known as ``selection-based approaches". By searching
-through all possible combinations of features, the aim of these
-techniques is to determine a minimal feature subset to reduce
-processing time, while obtaining the same or higher accuracy as the
-initial feature set \cite{liu1998feature}. In the problem this work
-addresses, it is very important to maintain the semantics of the set of
-initial variables, and therefore several feature selection methods
-have been applied.
+techniques, known as `selection-based approaches' \cite{liu1998feature}. 
+In the problem this work addresses, it is very important to maintain the semantics of the set of initial variables, and therefore just FS methods have been applied.
+
+We have used some numerical FS methods included in Weka software \cite{Hall2009,Witten2011}. This tool separates the process into two parts:
+
+\begin{itemize}
+  \item Attribute evaluator: This is the method by which the feature subsets are assessed.
+In this work, both a correlation-based feature subset evaluation method ({\tt CfsSubsetEval}) and an adaptation of relief for attribute estimation ({\tt ReliefFAttributeEval}) evaluation method are used.
+
+  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
+(predictive of) the class, yet uncorrelated with (not predictive of) each other''.
+This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.
+The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation.
+In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.
+
+``Relief'' is the second evaluator used in this work.
+It is important to note that the relief method implemented in Weka is an updated version \cite{RobnikSikonja1997}, called RRELIEFF, of the original by Kira \& Rendell \cite{Kira1992}.
+The algorithm works by evaluating single attributes, and not whole subsets of attributes as CFS does.
+Also, it is applicable even working with both nominal and numeric features, without the need for transformations.
+For this algorithm, the weight of an attribute depends on the difference of an attribute value inside an instance with its neighbours, being these the nearest instance of the same class, and the nearest of the different class.
+Therefore, a good attribute is that which gives similar values for instances of the same class, and different values for instances of different class.
+  \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator.
+With regard to the used search criteria, it is important to take into account that CFS evaluates attribute subsets, and Relief evaluates attributes separately.
+
+For this reason, the search method used with CFS has been BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility.
+On the other hand, Ranker is the searching criteria used with the Relief evaluator.
+This method ranks features by their individual evaluations.
+\end{itemize}
 
@@
 and to choose an appropriate set of variables, the Self-Organizing Map
-(SOM) \cite{kohonen1998} method has been also applied as a `subjective' (based on expert's opinion) feature selection technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.
+(SOM) \cite{kohonen1998} method has been also applied as a `subjective' (based on expert's opinion) FS technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.
 
@@
 
-With respect to feature selection methods, the used Weka software separates the process into two parts:
-
-\begin{itemize}
-  \item Attribute evaluator: This is the method by which the feature subsets are assessed.
-In this work, both a correlation-based feature subset evaluation method ({\tt CfsSubsetEval}) and an adaptation of relief for attribute estimation ({\tt ReliefFAttributeEval}) evaluation method are used.
-
-  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
-(predictive of) the class, yet uncorrelated with (not predictive of) each other''.
-This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.
-The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation.
-In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.
-
-``Relief'' is the second evaluator used in this work.
-It is important to note that the relief method implemented in Weka is an updated version \cite{RobnikSikonja1997}, called RRELIEFF, of the original by Kira \& Rendell \cite{Kira1992}.
-The algorithm works by evaluating single attributes, and not whole subsets of attributes as CFS does.
-Also, it is applicable even working with both nominal and numeric features, without the need for transformations.
-For this algorithm, the weight of an attribute depends on the difference of an attribute value inside an instance with its neighbours, being these the nearest instance of the same class, and the nearest of the different class.
-Therefore, a good attribute is that which gives similar values for instances of the same class, and different values for instances of different class.
-  \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator.
-With regard to the used search criteria, it is important to take into account that CFS evaluates attribute subsets, and Relief evaluates attributes separately.
-
-For this reason, the search method used with CFS has been BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility.
-On the other hand, Ranker is the searching criteria used with the Relief evaluator.
-This method ranks features by their individual evaluations.
-\end{itemize}
-
 Finally, Section \ref{sec:experiments} provides a comparison between the feature reduction through SOM, and the feature selection techniques that have been described.
@@
 \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
-Well known forecasting methods implemented in the Weka tool
-\cite{Hall2009,Witten2011} have been chosen, as these methods are
-widely known, and could be very helpful for practitioners to reproduce
-experiments and even to solve similar sales prediction problems using
+Well known forecasting methods implemented in the Weka tool have been chosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using
 these methods. % Why these and not others? Exploratory data analysis?

### 2016-05-12 paper.tex
let's take a look to the SoA

@@
   % New soft drink product
-In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
+Ching et al. propose in \cite{ChingChin2010} a decision-support system for new product sales
 forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.

### 2016-05-12 paper.tex
let's take a look to the SoA

@@
 For this reason, usually the methods used to predict book sales have
-been generally based on experts' experience.% Reference - JJ
+been generally based on experts' experience.
+% Reference - JJ
+% [pedro] I have not found a reference. This is based on what Santiago told us.
+% We can remove this sentence if you think it only should appear together with a reference...
  They analyse data about sales and, taking into account their knowledge of industry, their experience, and their perception about trends, could make decisions on the companies production, i.e.

### 2016-05-12 paper.tex
let's take a look to the SoA
Changed format style with Expert System with Applications template. Closes #28

@@
-\documentclass{llncs}
+\documentclass[final,1p,times]{elsarticle}
 \usepackage{graphics}
@@
 
-\def\CC{{C\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}~}
-\addtolength{\textfloatsep}{-0.5cm}
-\addtolength{\intextsep}{-0.5cm}
+%\def\CC{{C\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}~}
+%\addtolength{\textfloatsep}{-0.5cm}
+%\addtolength{\intextsep}{-0.5cm}
+
+\journal{Expert Systems with Applications}
+
+\begin{document}
+
+\begin{frontmatter}
 
@@
 %%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
-\author {
-P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, P. de las Cuevas$^1$, M.G. Arenas$^1$
-}
-\institute{
-$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
-$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
-e-mail: {\tt pacv@ugr.es, amorag@geneura.ugr.es, hossam.faris@ju.edu.jo,
-  jmerelo@geneura.ugr.es, pablogarcia@ugr.es,
-  antares.es@gmail.com, palomacd@ugr.es, mgarenas@ugr.es}
-}
-
-\date{}
-
-\begin{document}
-\maketitle
+
+\author[ugr]{Pedro A. Castillo Valdivieso}
+\ead{pacv@ugr.es}
+\author[ugr]{Antonio Miguel Mora}
+\ead{amorag@geneura.ugr.es}
+\author[abd]{H. Faris}
+\ead{hossam.faris@ju.edu.jo}
+\author[ugr]{J.J. Merelo}
+\ead{jmerelo@geneura.ugr.es}
+\author[ugr]{Pablo Garc\'{\i}a-S\'anchez}
+\ead{pablogarcia@ugr.es}
+\author[ugr]{Antonio Javier Fern\'andez-Ares}
+\ead{antares.es@gmail.com}
+\author[ugr]{Paloma de las Cuevas}
+\ead{palomacd@ugr.es}
+\author[ugr]{María Isabel García Arenas}
+\ead{mgarenas@ugr.es}
+
+\address[ugr]{Department of Computer Architecture and Computer Technology and CITIC-UGR, University of Granada, Granada, Spain. Tel: +34958241778. Fax: +34958248993}
+\address[abd]{Business Information Technology Department, King Abdullah II School for Information Technology, The University of Jordan, Amman, Jordan. Tel: +. Fax: +}
 
@@
 
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+Book sales forecasting \sep Decision-aid models \sep Feature selection \sep Regression  
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+\end{keyword}
+
+\end{frontmatter}
+
 %********************************************************************************
@@
 \cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
-them are categorical, which makes them harder to process, even more so if the number of categories is high.
-As stated in those works, given these issues, finding adequate forecasting techniques and selecting the best method to use is also a problem.
+them are categorical, which makes them harder to process, even more so if 
+the number of categories is high. As stated in those works, given these issues, 
+finding adequate forecasting techniques and selecting the best method to use 
+is also a problem.
 
@@
 % We can remove this sentence if you think it only should appear together with a reference...
- They analyse data about sales and, taking into account their knowledge of industry, their experience, and their perception about trends, could make decisions on the companies production, i.e.
-how many books should be printed when a new book is published.
+They analyse data about sales and, taking into account their knowledge of industry, 
+their experience, and their perception about trends, could make decisions 
+on the companies production, i.e. how many books should be printed when 
+a new book is published. 
 This is a complex problem, since the predictions are influenced by
@@
 \begin{center}
-  \epsfig{file=decision_tree_no_fs.eps,width=12cm}
+  \epsfig{file=decision_tree_no_fs.eps,width=13cm}
 \caption{Decision Tree built by the M5P method for the best seller publishing company with all the pre-sales features.}
@@
 \begin{center}
-  \epsfig{file=decision_tree_fs.eps,width=12cm}
+  \epsfig{file=decision_tree_fs.eps,width=13cm}
 \caption{Decision Tree built by the M5P method for the best seller publishing company with the features selected by the ReliefAttributeEval method.}
@@
 %********************************************************************************
-\bibliographystyle{plain}
+\bibliographystyle{elsarticle-num}
 \bibliography{refs}

### 2016-05-12 paper.tex
updating the SoA

@@
 is perhaps the most used technique to tackle sales forecasting
-problems. The efficiency of these techniques strongly depends on the field of application 
-and the correctness of the problem data. However, since they require a
-large amount of data for predicting sales, these methods are not the
-most suitable for this task \cite{ChingChin2010}. And they cannot be
-applied before the book is published, as is the objective of this paper.
-
+problems, although the efficiency of these techniques strongly depends on the 
+field of application and the correctness of the problem data. However, since 
+they require a large amount of data for predicting sales, these methods are not 
+the most suitable for this task \cite{ChingChin2010}. 
+Moreover, this kind of methods cannot be applied before the book is published, 
+as is the objective of this paper. 
 In this case, just a few variables are known in advance
 \cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
-them are categorical, which makes them harder to process, even more so if 
+them are categorical, which makes them harder to process, even more if 
 the number of categories is high. As stated in those works, given these issues, 
@@
 is also a problem.
-
+An additional issue makes this a complex problem, since the predictions are 
+influenced by external variables that must be taken into account, such as
+seasonality, promotions, or fashions that expert managers might
+subjectively apply \cite{Lapide1999,ChernWSF15}.
+% [pedro] I have not found a reference. This is based on what Santiago told us.
+% We can remove next sentence if you think it only should appear together with a reference...
 For this reason, usually the methods used to predict book sales have
-been generally based on experts' experience.
-% Reference - JJ
-% [pedro] I have not found a reference. This is based on what Santiago told us.
-% We can remove this sentence if you think it only should appear together with a reference...
-They analyse data about sales and, taking into account their knowledge of industry, 
-their experience, and their perception about trends, could make decisions 
-on the companies production, i.e. how many books should be printed when 
-a new book is published. 
-This is a complex problem, since the predictions are influenced by
-external variables that must be taken into account, such as
-seasonality, promotions, or fashions that expert managers might
-subjectively apply \cite{Lapide1999,ChernWSF15}. % This
-                                % has something to do with the
-                                % previous paragraph? Put it there!!! 
-%
+been generally based on experts' experience, who analyse data about sales and, 
+taking into account their knowledge of industry, their experience, 
+and their perception about trends, could make decisions on the companies 
+production, i.e. how many books should be printed when a new book is published.
+
   %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.

### 2016-05-12 paper.tex
I have reviewed the first part of the SoA

@@
   %     Moon2010ICEC
-Recently, some works have proposed analysing relationships between on-line information and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}.
-Specifically, Moon et al.
-propose using the number of blog references as an indicator of
-the success of a book, and thus, its sales. Different sales patterns
-are observed by analysing the obtained data. 
-% Antonio - describir esos 'sales patterns'. ;)
-% FERGU: y también cuales son esos 'data obtained'
-%The authors considered in these papers historical data from published books, 
-%so their proposed methodology can not be applied to the problem of unpublished %books sales prediction.
-%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?
-% (Paloma) Agree with Fergu, I don't think we should say this... Please review it.
-
-% [pedro] La cosa es que esta gente toma libros ya publicados y de los que tienen todos los datos de ventas para analizar y obtener patrones de ventas.
-Nosotros trabajamos con datos de libros que ni siquiera se han impreso aún, por lo que no tenemos ni idea de cómo van a funcionar.
-Esta gente dispone de datos de ventas, mientras que nosotros sólo vamos a tener datos relativos a "¿dónde lo vas a poner a la venta?" o "¿vas a dar algún regalo para intentar vender más?" (cosas así).
-
-% Antonio - He intentado escribirlo, pero no me queda claro...
-Los datos que tenemos son también de libros ya publicados, ¿no?.
-Estamos considerando variables pre-venta sólamente, eso sí, pero usando datos históricos queremos predecir ventas futuras.
-% Quizá lo que habría que señalar (aquí y en los demás sitios que se dice lo de los datos históricos) es lo de las variables que se consideran, si son variables post-venta o pre-venta, como es nuestro caso.
-;)
+Recently, some works have proposed analysing relationships between on-line 
+information and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. 
+Specifically, Moon et al. propose using the number of blog references as an 
+indicator of the success of a book, and thus, its sales. 
+Obtained results confirm relationships between the number of blog references 
+and book sales, and at the same time different sales patterns are observed 
+by analyzing books in series (the first book published takes the longest period 
+to achieve every single sales scale, while the second book takes the second 
+longest period, and so on).
 
@@
 historical data are available, the classical forecasting methods based
-on time-series are not adequate, although they can obviously be used once the book has been launched for sale. 
+on time-series are not adequate, although they can obviously be used once 
+the book has been launched for sale. 
 In our work the relevant variables in the prediction of sales are identified
-by means of data visualisation and feature selection methods. Then, machine learning techniques are applied to predict sales and to infer the ideal print-run of a book.
+by means of data visualisation and feature selection methods. 
+Then, machine learning techniques are applied to predict sales and to infer 
+the ideal print-run of a book.
 In addition, since publishers need models to explain obtained predictions, 

### 2016-05-12 paper.tex
Reviewing part of the SoA

@@
 as is the objective of this paper. 
-In this case, just a few variables are known in advance
+In this case, just a few variables are known in advance (pre-sales data)
 \cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
@@
 However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
-\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem. %PABLO: pre-sales data is mentioned briefly in introduction, expand it
+\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem, i.e. variables known before the book is on sale.
 
@@
 %
-In the same line, Thomassey et al. \cite{SThomassey2014} proposed using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
-a very similar issue to the new book publishing one. % (Paloma) Very similar? Why?
+In the same line, Thomassey et al. \cite{SThomassey2014} proposed using a 
+clustering method together with decision trees for sales forecasting in 
+textile-apparel fashion industry, a very similar issue to the new book 
+publishing problem.
 The same problem was previously faced by Xia et al. \cite{Xia2012} using a 
@@
 Ching et al. propose in \cite{ChingChin2010} a decision-support system for new product sales
-forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.
-% Antonio - qué significa eso?
+forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products.
 In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern.
@@
 In those cases where historical data are available, classical time series 
-forecasting methods can be applied, which is what the authors did in
-\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
-neural networks to forecast the future sales of a printed circuit
-board is proposed. % We have been talking above that above and SAID IT
-                   % DIDN'T WORK? Why do we say it here again? - JJ
-                   % No, above we said that the efficiency depends on the field 
-                   % of application and the available problem data. - pedro
+forecasting methods have beeen applied, such as in \cite{Chang2009}, 
+where a hybrid model integrating K-Means and fuzzy neural networks to forecast 
+the future sales of a printed circuit board is proposed.
 A similar method is described by Chern et al. \cite{ChernWSF15}, who analysed 

### 2016-05-12 paper.tex
I have reviewed the second part of the SoA

@@
 
-In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
-% Antonio - Maybe we should describe them briefly...
+In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods, such as 
+"Accurate Response", an approach for demand estimation and production planning \cite{Hammond1990}, 
+data clustering and fuzzy neural networks \cite{Chang2009} or 
+extreme learning machine with adaptive metrics of inputs \cite{Xia2012}. 
 %
@@
 
-The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
-and on the influence of variables such as promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
+The complexity of this problem relies on the lack of historical data, on the 
+short lifetime of the majority of items, and on the influence of variables such 
+as promotions, fashions, or economic environment
+ \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
 %FERGU: completar con: "In our case, these ideas ..."
+% [pedro] no sé a qué te refieres. Please, detalla un poco esto   :)
 
@@
   % New soft drink product
-Ching et al. propose in \cite{ChingChin2010} a decision-support system for new product sales
-forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products.
-In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern.
+Ching et al. propose in \cite{ChingChin2010} a decision-support system for new 
+product sales forecasting is proposed to solve three real-world sales forecasting 
+problems, namely: new tea, cosmetics, and soft drink products. 
+In that study, products are classified based on their sales patterns, so it is 
+assumed that products in the same class would follow a similar sales pattern. 
 However, as the authors state, the proposed system can not deal with qualitative 
@@
 influences to understand how electronic `word-of-mouth' influences product sales. 
-The proposed method is suitable for those sales forecasting problems 
+In this case, the proposed method is suitable for those sales forecasting problems 
 with a big amount of online reviews and historical data.

### 2016-05-16 paper.tex
closing some issues: Closes #31
we will send the paper by May 20: Closes #20
Changed English from the Colonies to Her Majesty English. Closes #35

@@
 estimations of future sales of the new product is quite difficult, and extremely important, so that production runs heed predicted sales. 
-Indeed,several studies have demonstrated that improving sales predictions 
+Indeed, several studies have demonstrated that improving sales predictions 
 (a reduction of forecasting errors) results in an enhancement in the 
@@
 % [pedro] I have not found a reference. This is based on what Santiago told us.
-% We can remove next sentence if you think it only should appear together with a reference...
+% We can remove next sentence if you think it only should appear together with a reference.
 For this reason, usually the methods used to predict book sales have
@@
   %  sobre "Use Blog Information As Book Sales Prediction":
-  %     Moon2010ICSSSM
-  %     Moon2010ICEC
+  %     Moon2010ICSSSM , Moon2010ICEC
 Recently, some works have proposed analysing relationships between on-line 
@@
 and book sales, and at the same time different sales patterns are observed 
-by analyzing books in series (the first book published takes the longest period 
+by analysing books in series (the first book published takes the longest period 
 to achieve every single sales scale, while the second book takes the second 
@@
 In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods, such as 
-"Accurate Response", an approach for demand estimation and production planning \cite{Hammond1990}, 
+``Accurate Response'', an approach for demand estimation and production planning \cite{Hammond1990}, 
 data clustering and fuzzy neural networks \cite{Chang2009} or 
@@
 In those cases where historical data are available, classical time series 
-forecasting methods have beeen applied, such as in \cite{Chang2009}, 
+forecasting methods have been applied, such as in \cite{Chang2009}, 
 where a hybrid model integrating K-Means and fuzzy neural networks to forecast 
@@
 (predictive of) the class, yet uncorrelated with (not predictive of) each other''.
-This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.
+This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.%Pablo: the Oxford dictionary accepts both (zed and sed), but the one with Z is the one that appears as main in the entry
  The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation.
@@
 SOM follows an iterative process applied in two stages: First, the
-weights of the network are initialized randomly, then the n-dimensional
+weights of the network are initialised randomly, then the n-dimensional
 input vectors are presented to the network sequentially so the
@@
 neuron which has the shortest distance with the presented input vector
-is updated along with its neighbor neurons. This neuron is called the
+is updated along with its neighbour neurons. This neuron is called the
 best matching unit (BMU). The goal of the learning process is to
-minimize the neighborhood distance in the output clusters.
+minimise the neighbourhood distance in the output clusters.
 
@@
 This method uses the obtained codevectors (vectors of variables of the problem) as data source, and generates a matrix where each component is a distance measure between two adjacent neurons.
-In the U-matrix, the distance between adjacent neurons is measured and assigned different colors.
-Different colors between neurons indicate large distances (boundaries) while similar colors represent close areas (clusters).
+In the U-matrix, the distance between adjacent neurons is measured and assigned different colours.
+Different colours between neurons indicate large distances (boundaries) while similar colours represent close areas (clusters).
 
@@
 The second error refers to the topology of the map and its preservation, so it measures an average value computed looking at both, the first and the second BMUs for every pattern.
-If they are neighbours (directly connected in the map) a '1' is considered, otherwise a '0' is taken.
+If they are neighbours (directly connected in the map) a `1' is considered, otherwise a `0' is taken.
 A small value would mean that the map preserves well its topology.
@@
 vectors of the SOM map units. These values are represented as
-colours. The colorbar on the right of each component plane shows the
+colours. The colourbar on the right of each component plane shows the
 indication of each colour. On the other side, the U-matrix on the top
@@
 
-Examining the component planes shown in Figure \ref{fig:componentplanes}, it can be noticed that some variables have very similar color maps which means that they are highly correlated.
+Examining the component planes shown in Figure \ref{fig:componentplanes}, it can be noticed that some variables have very similar colour maps which means that they are highly correlated.
 In this case, we have two examples; the first is the \emph{distrib\_novelty} and \emph{print\_run}variables while the second is the \emph{tot\_points\_sale} and \emph{tot\_points\_sale\_1st\_year}.

### 2016-05-16 paper.tex
Reviewing section 4, Methodology, introduction. Closes #29

@@
 There is not a standard methodology to solve the general problem of sales forecasting.
-This is why the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}.
-These are described in the following sections.
-
-As a summary, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques are applied, such as Feature Selection (FS) \cite{kittler1986feature} (see Section \ref{subsec:data_preproces}).
-These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain easier-to-interpret models, in a less amount of time (due to their lower complexity), and with a fair or, hopefully, better accuracy.
+However, the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}.
+%These are described in the following sections.
+
+Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques are applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}.
+These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
 This task may also help to identify leading indicators to be considered by a human expert to make predictions.
-
 % You have to present the problem and not the solution. It's not "what
@@
 
-After this process (in Section \ref{subsec:select_method}), a selection of the best forecasting techniques have been conducted, looking for those rule- or tree-based, together with numerical methods which could yield the best results.
+Next, Section \ref{subsec:select_method} reports a selection of the best forecasting techniques that have been conducted, looking for those rule- or tree-based, together with numerical methods which could yield the best results.
 

### 2016-05-16 paper.tex
Reducing variables size in table 1. Closes #37

@@
 
-\begin{minipage}{2.45in} \begin{verbatim}
+\begin{minipage}{2.45in}\begin{small}
+ \begin{verbatim}
 reference
@@
 distrib. through delegates 1st year
-\end{verbatim} \end{minipage}     &
-
-\begin{minipage}{2.3in} \begin{verbatim}
+\end{verbatim}
+\end{small} \end{minipage}     &
+
+\begin{minipage}{2.3in} \begin{small}
+\begin{verbatim}
 rest of distributed 1st year
@@
 negative sales environment
-\end{verbatim} \end{minipage}    \\
+\end{verbatim}
+\end{small} \end{minipage}    \\
 

### 2016-05-18 paper.tex
Add style files and some minimum changes

@@
 
-\author[ugr]{Pedro A. Castillo Valdivieso}
+\author[ugr]{Pedro A. Castillo}
 \ead{pacv@ugr.es}
-\author[ugr]{Antonio Miguel Mora}
+\author[ugr]{Antonio M. Mora}
 \ead{amorag@geneura.ugr.es}
@@
 \ead{pablogarcia@ugr.es}
-\author[ugr]{Antonio Javier Fern\'andez-Ares}
+\author[ugr]{Antonio J. Fern\'andez-Ares}
 \ead{antares.es@gmail.com}
-\author[ugr]{Paloma de las Cuevas}
+\author[ugr]{Paloma De las Cuevas}
 \ead{palomacd@ugr.es}
-\author[ugr]{María Isabel García Arenas}
+\author[ugr]{María I. García-Arenas}
 \ead{mgarenas@ugr.es}
 
-\address[ugr]{Department of Computer Architecture and Computer Technology and CITIC-UGR, University of Granada, Granada, Spain. Tel: +34958241778. Fax: +34958248993}
-\address[abd]{Business Information Technology Department, King Abdullah II School for Information Technology, The University of Jordan, Amman, Jordan. Tel: +. Fax: +}
+\address[ugr]{Department of Computer Architecture and Computer Technology, ETSIIT and CITIC \\
+University of Granada, Granada, Spain. Tel: +34958241778. Fax: +34958248993}
+\address[abd]{Business Information Technology Department, King Abdullah II School for Information Technology \\
+The University of Jordan, Amman, Jordan. Tel: +. Fax: +}
 

### 2016-05-18 paper.tex
Added 3 more updated references

@@
 Specifically, time-series prediction methods
-\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
+\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10}  
 is perhaps the most used technique to tackle sales forecasting
@@
  \item \emph{Linear Regression}:
- Linear regression \cite{Cohen2003,Yan2009,Rencher2102} method models the 
+ Linear regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
 relationship between a scalar dependent variable (outcome) and several independent 
@@
  \item \emph{Support Vector Machine for Regression (SVM)}:
-Support vector machine (SVM) \cite{Cortes1995,Shevade1999} method is based on  
+Support vector machine (SVM) \cite{Cortes1995,Shevade1999,MinSVM05} method is based on  
 statistical learning theory and has successfully used in classification and  
@@
 In classification problems the algorithm searches for an optimal hyperplane 
-that separates two classes, maximising the margin between two classes. 
+that separates two classes, maximising the mthe argin between two classes. 
 In the case of regression the algorithm chooses a hyperplane close to as many 

### 2016-05-18 paper.tex
Conclusions rewritten and some other minor changes

@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
- \item \emph{M5 Model trees}: 
+ \item \emph{M5 Model trees (M5P)}: 
 A decision tree consists of answer-nodes, that indicate a class, and decision-nodes, 
@@
 
- \item \emph{Random Forest}: This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm.
+ \item \emph{Random Forest (RF)}: This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm.
 It was proposed by Breiman \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution.
@@
  %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
- \item \emph{Linear Regression}:
- Linear regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
+ \item \emph{Linear Regression (LR)}:
+ Linear Regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
 relationship between a scalar dependent variable (outcome) and several independent 
@@
 In classification problems the algorithm searches for an optimal hyperplane 
-that separates two classes, maximising the mthe argin between two classes. 
+that separates two classes, maximising the margin between them. 
 In the case of regression the algorithm chooses a hyperplane close to as many 
@@
 \hline 
-K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
+kNN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
+kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
 \hline 
@@
 \hline 
-K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
+kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
 \hline 
@@
 \hline 
-K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
+kNN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
 \hline 
@@
 \hline 
-K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
+kNN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
 \hline 
@@
 \hline 
-K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
+kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
 \hline 
@@
 \hline 
-K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 \hline 
-K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
+kNN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+kNN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
+kNN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
 \hline 
@@
 \hline 
-K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+kNN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+kNN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 
-%***TO DO***: rewrite these conclusions with the new experiments, examples and results\\
-
-In this paper, the problem of how many books should be printed 
-when a new book is going to be published is faced using several data-mining and
-forecasting methods.
+In this paper, the problem of how many books should be printed when a new book is going to be published is faced using several data-mining and forecasting methods.
 
 This is a very challenging problem in this industry, because printing a higher 
-number of volumes than those finally sold will lead to losses, 
-while printing an adequate number of copies will optimise sales and company earnings.
-In addition, there are several difficulties inherent to the new book sales forecasting, 
-such as dealing with limited data, finding adequate forecasting methods, and 
-selecting the best method to use.
-
-%La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
-A dataset consisting of 6000 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
-publishing company Trevenque Editorial S.L. has been used.
-
-In this paper, a data visualisation method has been used to find out what are 
-the relevant variables describing a book in the prediction of book sales.
-Then, several standard data mining models for sales forecasting have been used 
-to forecast new book sales, and from them deduce print-run, based on those 
-variables.
-
-The most relevant variables when predicting sales have been determined, 
-while unrelated or superfluous ones have been removed, 
-and sales predictions have been obtained using five different forecasting 
-standard methods.
-Not only the obtained forecasting error has been taking into account to evaluate
-those methods, but also the cost of model building as parameter setting and 
-the required time to train the model.
-
-In this sense, the decision trees proved to be a suitable model because of the 
-ease to explain how the prediction is obtained from the variables that describe 
-the new book. 
-This, compared to the black-box models such as the artificial neural network, 
-was decisive from the point of view of the needs of experts and Trevenque company.
-Moreover, proposed method was validated by the company and incorporated in a 
-business intelligence tool for publishing companies. %FERGU: no hay más info de esto? estaría guay describirlo
-
-%FERGU: no mencionais el SOM en las conclusiones
-
-Overall, this study contributes to the literature by proposing the use of different 
-soft-computing standard techniques to solve a new challenging problem.
+number of volumes than those finally sold will lead to losses, while printing an adequate number of copies will optimise sales and company earnings.
+In addition, there are several difficulties inherent to the new book sales forecasting, such as the limited amount of historical data to consider or the variability of the market (fashions, seasonality), which do a difficult task finding an adequate forecasting method.
+
+A dataset consisting of 6000 books provided by the Spanish publishing company Trevenque Editorial S.L.
+has been used.
+These data have been analysed by means of Self-Organizing Maps as a visualisation tool, and two other Feature Selection techniques, namely a correlation-based feature subset evaluation method, and an adaptation of relief for attribute estimation.
+Using these methods the most relevant variables when predicting sales have been determined, while unrelated or superfluous ones have been removed.
+
+Four different datasets have been also extracted from the original one, everyone corresponding to a Publishing house which we have considered as representative: the one with the most number of sales, the one with the medium number of sales, with the most varied sales (different books), and with a medium number of different books sold.
+
+Considering these datasets and the complete one, five machine learning models for sales forecasting have been configured (according to the problem requirements) and used to predict new book sales, from which the optimal print-run could be estimated.
+These algorithms include some based on Decision Trees (M5P and Random Forest), kNN, Support Vector Machines and Linear Regression.
+These methods have been evaluated considering several performance indicators (error measures) and also the time consumed to build the corresponding models.
+
+As a conclusion, M5P yields the best results overall, obtaining the best accuracy (lowest error) on average, even with acceptable values regarding the training time.
+In addition, the Decision Trees obtained with this method have been presented as an excellent decision-aid tool for publishers, since they are accurate and quite easy to understand and apply.
+They are also able to provide insights on the decisions that have a higher influence on the print-run for these publishers.
+
+This, compared to the output of black-box models such as artificial neural networks, was a determining advantage from the point of view of the needs of experts and Trevenque company.
+
+%Moreover, proposed method was validated by the company and incorporated in a 
+%business intelligence tool for publishing companies. %FERGU: no hay más info de esto? estaría guay describirlo
+
+The feature selection techniques have also shown to positively affect all the results, yielding a better performance in time to train while maintaining good accuracy.
+Moreover, their application leads to obtain even simpler models.
+
+Overall, this study contributes to the literature by proposing the use of different soft-computing standard techniques to solve a new challenging problem.
 Moreover, proposed method could be implemented, not only in the publishing 
-industry, but also in other domains where the specificity of products is similar, 
-and might be of interest to other academic researches and industrial practitioners.
-
-%---------- trabajo futuro
-
-As future work, it would be interesting to compare the obtained forecasting results 
-with other methods based on soft-computing, such as genetic programming or fuzzy logic.
-Moreover, as default parameters have been used for proposed forecasting methods,
-it would be of interest carrying out some parameter tuning procedure in order to
-improve obtained results.
+industry, but also in other domains where the specificity of products is similar, and might be of interest to other academic researches and industrial practitioners.
+% Antonio - I don't know if we should say this...
+
+%Thus, the methodology presented here provides a reliable data processing technique for editorial data and also yields a reasonable result that allows publishers to forecast sales and then create the appropriate print run without incurring in losses.
+
+% -------- Future Work ---------
+
+As future work, it would be interesting to compare the obtained forecasting results with those yielded by other soft-computing methods, such as genetic programming or fuzzy logic.
+Moreover, even if the methods have been configured to obtain the best forecasting results, it would be of interest carrying out some automatic parameter-tuning procedure by means of optimisation meta-algorithms,
+% Antonio - add an ESWA reference to this. :D
+for instance.
 
 Furthermore, since there are some characteristics that may affect product sales 
-significantly, another way to improve sales predictions could be making a thorough 
-study of the effect of the application of discounts and promotions.
-
-Finally, there are some variables over which the published has some
-control once the book has been published, such as the initial print
-run or the books given out as gifts to reviewers or what proportion is
-going to be sent to each possible point of sale. This can be
-incorporated into an optimisation model that optimises those values to
-obtain desired sales. This is left as future work.
-
-% Antonio - TO BE INCLUDED IN THIS SECTION
-% The method presented here provides a reliable data processing
-% technique for editorial data and also yields a reasonable result
-% that allows publishers to forecast sales and then create the
-% appropriate print run without incurring in losses. 
-%
-% Besides, if this is true:
-% It also provides a method that is able to provide insight on the
-% decisions that have an influence on the print run for publishers.
+significantly, another way to improve sales predictions could be making a thorough study of the effect of the application of discounts and promotions.
+
+Finally, there are some variables over which the publisher has some
+control once the book has been published, such as the initial print-run, the books offered as gifts to reviewers, or what proportion is going to be sent to each possible point of sale.
+These can be incorporated into an optimisation model that will optimise those values to obtain desired sales.
 
@@
 
-***TO DO***: revise the projects\\
-
-This work has been supported in part by projects 
-PreTEL (PRM Consultores - Trevenque S.L.),
-TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitiveness), 
-SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), 
-PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), 
-PROY-PP2015-06 (Plan Propio 2015 UGR), 
-and project CEI2015-MP-V17 of the Microprojects program 2015 from CEI BioTIC Granada.
+This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
 
@@
 \hline 
-K-NN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
+kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
+kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
+kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
+kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
+kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
+kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
+kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
 \hline 
@@
 \hline 
-K-NN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
+kNN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
 \hline 

### 2016-05-19 paper.tex
fixing some expresions

@@
 \address[abd]{Business Information Technology Department, King Abdullah II School for Information Technology \\
-The University of Jordan, Amman, Jordan. Tel: +. Fax: +}
+The University of Jordan, Amman, Jordan}
 
@@
 Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
-In addition, some may have correlations between them, although these correlations can be detected using data analysis methods, 
+In addition, some variables may have correlations between them, although these correlations can be detected using data analysis methods, 
 such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.
@@
 
-The training dataset included historical data about 6083 books published in Spain for several years, with an initial set of 50 variables per pattern.
-It was provided by the Spanish publishing company Trevenque Editorial S.L..
+The training dataset includes historical data about 6083 books published in Spain for several years, with an initial set of 50 variables per pattern.
+It has been provided by the Spanish publishing company Trevenque Editorial S.L..
 Table
@@
 Thus, their value do not depend on the book sales.
-The selected the subset of features is described in Table \ref{tabla:params_pre_sales}.
+The selected subset of features is described in Table \ref{tabla:params_pre_sales}.
 
@@
 result could be used as a reference for a human expert, who would
-consider it in his or her own prediction process.
+consider it for his or her own prediction process.
 
@@
 
-Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques are applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}.
+Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}.
 These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.

### 2016-05-19 paper.tex
fixing some expresions
fixing some expresions and typos

@@
 
-The application of FS also aims to reduce the complexity of the obtained forecasting models themselves, which, in turn, implies a reduction in the computational time for building these models.
-The first has been a key factor in this work, because one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).
-Regarding the algorithm running, it time grows with the number of
+The application of FS also aims to reduce the complexity of the obtained 
+forecasting models themselves, which, in turn, implies a reduction in the 
+computational time for building these models. This has been a key 
+factor in this work, because one of the objectives is to obtain `easily' 
+interpretable decision models, which can be useful for human experts (publishers).
+Regarding the algorithm, running time grows with the number of
 features, making it impractical for problems with a large number of features 
@@
 
-FS is one of the ways of performing a feature reduction, the other one is feature extraction \cite{kittler1986feature}. 
+FS is one of the ways of performing a feature reduction, the other one is 
+feature extraction \cite{kittler1986feature}. 
 Feature extraction is a `transformation-based approach', therefore
 it transforms the original meaning of the features. This method
-involves creating a subset of new features by combinations of the
-existing features, thus it is employed when the semantics of the
+involves creating a subset of new features by combining the
+existing ones; thus it is employed when the semantics of the
 original dataset will not be needed by any future process. On the
@@
 techniques, known as `selection-based approaches' \cite{liu1998feature}. 
-In the problem this work addresses, it is very important to maintain the semantics of the set of initial variables, and therefore just FS methods have been applied.
+In the problem this work addresses, it is very important to maintain the 
+semantics of initial variables set, and therefore just FS methods 
+have been applied.
 
@@
 
-Basically, SOM consists of two layers: input layer and output, also
+Basically, SOM consists of two layers: input and output layer, also
 known as Kohonen, layer. Input layer is fully connected with the 
@@
 neuron which has the shortest distance with the presented input vector
-is updated along with its neighbour neurons. This neuron is called the
+is updated along with the neurons in its neighbourhood. This neuron is called the
 best matching unit (BMU). The goal of the learning process is to

### 2016-05-19 paper.tex
fixing Apendix A tables

@@
 U-Matrix graph, together with the projection of variables into separate planes, the so-called component planes analysis (that SOM yields), will aid an expert to identify the most relevant features on every cluster, i.e.
-those that can have a higher influence on the creation of that cluster.
+those with a higher influence on the creation of that cluster.
 %FERGU: mencionarlo en la intro
@@
 
-Thus, in this research five forecasting methods, based on the literature 
-review in the introduction 
+Thus, in this research five forecasting methods, based on the State of the Art literature 
+review (see Section \ref{sec:soa}) 
 \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
@@
 relationship between a scalar dependent variable (outcome) and several independent 
-variables (predictor) over the range of values in the dataset. 
+variables (predictors) over the range of values in the dataset. 
 In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.
@@
 solved using the least squares method, that minimises the error between the 
-actual data and the regression line \cite{McClendon2015}.
+current data and the regression line \cite{McClendon2015}.
 
@@
 The objective is finding the most appropriate forecasting method that minimises 
-the error between the obtained forecast and the actual sales for each new book 
+the error between the obtained forecast and the current sales for each new book 
 published.
@@
 \end{itemize}
-where $o_i$ is the actual value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
+where $o_i$ is the current value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
 
@@
 
-kNN is the fastest method used in this study in terms of training time, as it is the simplest method. However, the model is slow when classifying large number of 
+kNN is the fastest method used in this study in terms of training time, as it 
+is the simplest one. However, the model is slow when classifying large number of 
 training examples, and it exhibits a poor generalisation ability since it does not 
@@
 Furthermore, since there are some characteristics that may affect product sales 
-significantly, another way to improve sales predictions could be making a thorough study of the effect of the application of discounts and promotions.
+significantly, another way to improve sales predictions could be making a 
+thorough study of the effect of the application of discounts and promotions.
 
 Finally, there are some variables over which the publisher has some
-control once the book has been published, such as the initial print-run, the books offered as gifts to reviewers, or what proportion is going to be sent to each possible point of sale.
-These can be incorporated into an optimisation model that will optimise those values to obtain desired sales.
+control once the book has been published, such as the initial print-run, 
+the books offered as gifts to reviewers, or what proportion is going to be sent 
+to each possible point of sale. These can be incorporated into an optimisation 
+model that will optimise those values to obtain desired sales.
 
@@
 \hline 
-kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
+kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & \textbf{170.83 $\pm$46.34} & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 \hline 
-SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
+SVM & \textbf{81.8 $\pm$0.08} & \textbf{94.29 $\pm$25.52} & 180.54 $\pm$62.67 & \textbf{50.79 $\pm$8.48} & \textbf{65.62 $\pm$6.25} & 0.040 $\pm$0.02\tabularnewline
 \hline 
@@
 \hline 
-M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
-\hline 
-kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
+M5P & \textbf{89.2 $\pm$0.07} & \textbf{71.536 $\pm$18.95} & \textbf{123.06 $\pm$42.13} & \textbf{39.43 $\pm$10.58} & \textbf{47.20 $\pm$15.16} & 0.031 $\pm$0.007\tabularnewline
+\hline 
+kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
 \hline 
@@
 \hline 
-kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
-\hline 
-RF & 65.3 $\pm$0.19 & 685.56 $\pm$195.28 & 1021.37 $\pm$352.88 & 69.74 $\pm$16.96 & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
-\hline 
-LR & 67.0 $\pm$0.23\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
+kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & \textbf{1008.39 $\pm$305.87} & 71.41 $\pm$13.95 & \textbf{78.47 $\pm$22.70} & \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 65.3 $\pm$0.19 & \textbf{685.56 $\pm$195.28} & 1021.37 $\pm$352.88 & \textbf{69.74 $\pm$16.96} & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
+\hline 
+LR & \textbf{67.0 $\pm$0.23}\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
 \hline 
@@
 \hline 
-kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
-\hline 
-RF & 85.6 $\pm$0.08 & 446.25 $\pm$119.79 & 673.46 $\pm$189.06 & 45.38 $\pm$9.78 & 52.24 $\pm$13.09 & 0.0594 $\pm$0.0049\tabularnewline
+kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & \textbf{0 $\pm$0.0002}\tabularnewline
+\hline 
+RF & \textbf{85.6 $\pm$0.08} & \textbf{446.25 $\pm$119.79} & \textbf{673.46 $\pm$189.06} & \textbf{45.38 $\pm$9.78} & \textbf{52.24 $\pm$13.09} & 0.0594 $\pm$0.0049\tabularnewline
 \hline 
@@
 \hline 
-M5P & 88.0 $\pm$0.13 & 738.28 $\pm$188.53 & 1141.79 $\pm$472.025 & 45.45 $\pm$13.62 & 47.58 $\pm$24.84 & 0.017 $\pm$0.002\tabularnewline
-\hline 
-kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
+M5P & \textbf{88.0 $\pm$0.13} & \textbf{738.28 $\pm$188.53} & \textbf{1141.79 $\pm$472.025} & \textbf{45.45 $\pm$13.62} & \textbf{47.58 $\pm$24.84} & 0.017 $\pm$0.002\tabularnewline
+\hline 
+kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
 \hline 
@@
 \hline 
-M5P & 89.7 $\pm$0.10 & 685.67 $\pm$185.99 & 1116.42 $\pm$478.06 & 42.09 $\pm$12.8 & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
-\hline 
-kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
+M5P & \textbf{89.7 $\pm$0.10} & \textbf{685.67 $\pm$185.99} & \textbf{1116.42 $\pm$478.06} & \textbf{42.09 $\pm$12.8} & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
+\hline 
+kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & \textbf{46.25 $\pm$14.41} & \textbf{0.0001 $\pm$0.0003}\tabularnewline
 \hline 
@@
 \hline 
-kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
-\hline 
-RF & 75.1 $\pm$0.26 & 15.61 $\pm$7.19 & 26.83 $\pm$13.36 & 47.38 $\pm$20.10 & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
-\hline 
-LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & 25.49 $\pm$11.63 & 47.97 $\pm$18.85 & 60.28 $\pm$30.62 & 0.0002 $\pm$0.0004\tabularnewline
-\hline 
-SVM & 81.8 $\pm$0.21 & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
+kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 75.1 $\pm$0.26 & \textbf{15.61 $\pm$7.19} & 26.83 $\pm$13.36 & \textbf{47.38 $\pm$20.10} & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
+\hline 
+LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & \textbf{25.49 $\pm$11.63} & 47.97 $\pm$18.85 & \textbf{60.28 $\pm$30.62} & 0.0002 $\pm$0.0004\tabularnewline
+\hline 
+SVM & \textbf{81.8 $\pm$0.21} & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
 \hline 
@@
 \hline 
-M5P & 86.0 $\pm$0.19 & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
-\hline 
-kNN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
-\hline 
-RF & 85.5 $\pm$0.19 & 13.66 $\pm$6.47 & 22.51 $\pm$11.03 & 41.38 $\pm$17.87 & 52.20 $\pm$27.09 & 0.026 $\pm$0.0019\tabularnewline
+M5P & \textbf{86.0 $\pm$0.19} & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
+\hline 
+kNN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & \textbf{0 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 85.5 $\pm$0.19 & \textbf{13.66 $\pm$6.47} & \textbf{22.51 $\pm$11.03} & \textbf{41.38 $\pm$17.87} & \textbf{52.20 $\pm$27.09} & 0.026 $\pm$0.0019\tabularnewline
 \hline 

### 2016-05-19 paper.tex
improving (making clear) some sentences

@@
 These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies.
-The results obtained for the four considered special cases are commented in Section \ref{sec:example_cases}.
+Obtained results for the four considered special cases are commented in Section \ref{sec:example_cases}.
 Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.
@@
 Ching et al. propose in \cite{ChingChin2010} a decision-support system for new 
-product sales forecasting is proposed to solve three real-world sales forecasting 
+product sales forecasting  to solve three real-world sales forecasting 
 problems, namely: new tea, cosmetics, and soft drink products. 
@@
   % sales forecasting in printed circuit board industry.
-In those cases where historical data are available, classical time series 
+In another hand, in those cases where historical data are available, classical time series 
 forecasting methods have been applied, such as in \cite{Chang2009}, 
@@
 % Indeed, there were just a couple of patterns without important values, that probably were errors of the extraction process or bad insertions in the database.
-Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to use just those that can be known before a new book is launched, i.e.
-\textit{pre-sales data}.
-Thus, their value do not depend on the book sales.
+Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, 
+has been reduced by an expert to use just those that can be known before a new book 
+is launched, i.e. \textit{pre-sales data}. 
+%Thus, their value do not depend on the book sales. 
 The selected subset of features is described in Table \ref{tabla:params_pre_sales}.
@@
 
-As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods.
+As it can be seen in this table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods.
 On the other hand, \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
@@
 features, making it impractical for problems with a large number of features 
-\cite{Selvakuberan2008}, but this is a secondary objective in this work.
+\cite{Selvakuberan2008}; however, this is a secondary objective in this work.
 %You need to lay out to the reader what you are going to do here. In

### 2016-05-19 paper.tex
improving (making clear) some sentences

@@
 
-In the research published in this paper, the problem of how many units should be printed  when a new book is published is faced using actual data provided by the 
+In the research published in this paper, the problem of how many units should be printed  when a new book is published is faced using real data provided by the 
 Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 

### 2016-05-19 paper.tex
improving (making clear) some sentences

@@
 The problem to solve in this work is the forecasting of sales for new launched books in the Spanish market, considering a set of `pre-sales variables'.
-The objective is to offer a tool for publishers which will aid them to decide the best print run for a new book which before its publication process starts.
+The objective is to offer a tool for publishers which will aid them to decide the best print run for a new book before its publication process starts.
 This is a forecasting problem for which no specific historical data are available, since the same book has not been previously published.

### 2016-05-19 paper.tex
fixing some expresions and some typos

@@
 and to choose an appropriate set of variables, the Self-Organizing Map
-(SOM) \cite{kohonen1998} method has been also applied as a `subjective' (based on expert's opinion) FS technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.
+(SOM) \cite{kohonen1998} method has also been applied as a `subjective' (based on expert's opinion) FS technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.
 
@@
 This section presents the experiments conducted over the dataset considering the pre-sales variables forecasting new book sales.
-Feature selection techniques have been also applied in order to test their utility by comparing the obtained results.
+Feature selection techniques have also been applied in order to test their utility by comparing the obtained results.
 
@@
 data \cite{yu2004ec,chao2015construction,huang2006ga}. Two important
-parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of
+parameters should be tuned in SVM: the Cost $(C)$ and Gamma $(\gamma)$ of
 the RBF kernel. We apply grid search which is the most common approach
 to find $C$ and $\gamma$. The best performance of SVM was found at
-$C=200$ and Gamma $\gamma = 0.01$. For MLP, we apply it with one
+$C=200$ and $\gamma = 0.01$. For MLP, we apply it with one
 hidden layer since it was proven in the literature that an MLP with
@@
 
-The dataset has been also projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
+The dataset has also been projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
 An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features \emph{collection} and \emph{binding} have been
@@
 
-Several configurations for SOM has been tested and the one regarding both the \textit{quantisation error} and \textit{topographic error} has been chosen.
+Several configurations for SOM have been tested and the one regarding both the \textit{quantisation error} and \textit{topographic error} has been chosen.
 The first is a measure which represents the average distance between every input pattern and its BMU (i.e.
@@
 
-Evaluation results of the developed models (without performing any feature selection method) for the selected four cases are shown in Table \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
+Evaluation results of the developed models (without performing any feature selection method) for the selected four cases are shown in Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
 The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}.
@@
 leverage when deciding how much to print. For clarity purpose, we present here only the results
-after applying the RFE method for the four cases in Table
+after applying the RFE method for the four cases in Tables
 \ref{Table:case1results-RAE}, \ref{Table:case2results-RAE},
@@
 In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method applied to the data of the publisher that sells the most.
-These aim to demonstrate the value of the proposal to generate a useful decision-aid tool for an expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).
+These aim to demonstrate the value of the proposal to generate a useful decision-aid tool for an expert (publisher) to determine what sales can be expected for the different values of the input variables (including the print-run).
 
@@
 
-Four different datasets have been also extracted from the original one, everyone corresponding to a Publishing house which we have considered as representative: the one with the most number of sales, the one with the medium number of sales, with the most varied sales (different books), and with a medium number of different books sold.
+Four different datasets have also been extracted from the original one, each one corresponding to a Publishing house which we have considered as representative: the one with the most number of sales, the one with the medium number of sales, with the most varied sales (different books), and with a medium number of different books sold.
 

### 2016-05-20 paper.tex
making clear (along the text) the main objective of the paper

@@
 inventory excess, but printing too few will also have a negative economic impact. 
-In this paper, we are tackling the problem of predicting total sales in order to print the right amount of books and doing so even before the book has reached the stores.
+In this paper, we are tackling the problem of predicting total sales 
+in order to print the right amount of books and doing so even before the book has reached the stores.
 A real dataset including the complete sales data for books published in Spain across several years has been used.
@@
 remarkable accuracy, and can be visualised as simple decision trees. 
-Thus, these can be used as decision-aid tools for publishers, which can provide a reliable guidance on the decision process of publishing a book.
-This is also shown in the paper by addressing four example cases of representative publishers, regarding their number of sales and the number of different books they sell.
+Thus, these can be used as decision-aid tools for publishers, which can provide 
+a reliable guidance on the decision process of publishing a book. 
+This is also shown in the paper by addressing four example cases of representative 
+publishers, regarding their number of sales and the number of different books they sell.
 \end{abstract}
@@
 
-In the research published in this paper, the problem of how many units should be printed  when a new book is published is faced using real data provided by the 
+In the research published in this paper, the problem 
+of predicting total sales in order to print the right amount of books
+%of how many units should be printed  when a new book is published 
+is faced using real data provided by the 
 Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
@@
 
-As far as we know, no previous attempt can be found in the literature in which 
-prediction methods have been applied to estimate the print run. 
+As far as we know, no previous attempt can be found in the literature 
+%in which prediction methods have been applied to estimate the print run. 
+in which prediction methods have been applied to estimate sales for new launched books.
 However, similar techniques to those proposed in this paper, e.g. 
@@
 
-In this paper, the problem of how many books should be printed when a new book is going to be published is faced using several data-mining and forecasting methods.
+In this paper, the problem of 
+predicting total sales in order to print the right amount of books
+%how many books should be printed 
+when a new book is going to be published is faced using several data-mining and forecasting methods.
 
@@
 
-As a conclusion, M5P yields the best results overall, obtaining the best accuracy (lowest error) on average, even with acceptable values regarding the training time.
-In addition, the Decision Trees obtained with this method have been presented as an excellent decision-aid tool for publishers, since they are accurate and quite easy to understand and apply.
-They are also able to provide insights on the decisions that have a higher influence on the print-run for these publishers.
+As a conclusion, M5P yields the best results overall, obtaining the best accuracy 
+(lowest error) on average, even with acceptable values regarding the training time.
+In addition, the Decision Trees obtained with this method have been presented 
+as an excellent decision-aid tool for publishers, since they are accurate 
+and quite easy to understand and apply. 
+They are also able to provide insights on the decisions that have a higher influence on the 
+expected sales 
+%print-run 
+for these publishers.
 

### 2016-05-21 paper.tex
Justifying use of `print_run`
Refs #39. I will also check it later when examining resulting trees.

@@
 
-As it can be seen in this table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods.
-On the other hand, \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher.
-In addition, this variable could be interesting to be used to test the prediction model, once it is built.
-Hence, the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
-%Pablo: still waiting the definition of the variables
-
-Initially, there were three different features describing the subjects and subsubjects of every book \textit{subject1,2,3} (see Table \ref{tabla:paramsOrig50}), but for most of the patterns (books) there is no value for subjects2 and 3, so we have discarded these features.
+As it can be seen in this table, \texttt{total\_sales} is the output
+variable, so it is the objective of the prediction methods. {\tt
+  total_sales} are a variable percentage of the {\tt print_run}, and
+thus there is obviously some correlation between them, which might
+prevent us from using it to predict sales; it is quite obvious that
+just increasing the print run, by itself, will not boost
+sales. However, several of the other variables include implicitly a
+certain size of the print run; for instance, you have to actually
+print books to distribute them as novelty and at least one, for every
+point of sale, so including the print run makes sense to get more
+accurate estimates of the total sales that you are going to obtain out
+of the total print run and check its influence on the overall sales
+volume. Once this is included in the model and also as part of the
+tree nodes, changing the print run might give the publisher an idea of
+how many books are going to be actually sold out of that print run,
+and taking that into account decide on the actual number of books that
+are going to be printed. Just to be clear, printing book does not
+actually sell them, but it is obviously necessary to print books
+before you sell them, and once you have to do it, the publisher might
+make decisions on printing a few more and check, with this model, what
+would be the influence in sales if, for instance, you decide to send
+more books to every point of sale or distribute more in novelty. We
+will come back to this choice later on when examining the resulting
+models.
+
+Initially, there were three different features describing the subjects
+and subsubjects of every book \textit{subject1,2,3} (see Table
+\ref{tabla:paramsOrig50}), but for most of the patterns (books) there
+is no value for subjects2 and 3, so we have discarded these features.
 

### 2016-05-21 paper.tex
Revising English
Changing sentences which sound awkward and merging them so that text flows more easily

Refs #11

@@
 
-The problem to solve in this work is the forecasting of sales for new launched books in the Spanish market, considering a set of `pre-sales variables'.
-The objective is to offer a tool for publishers which will aid them to decide the best print run for a new book before its publication process starts.
-This is a forecasting problem for which no specific historical data are available, since the same book has not been previously published.
-However, we have considered data about other previously published books and have taken as reference a set of variables (or features), related with the book publication process.
-
-The training dataset includes historical data about 6083 books published in Spain for several years, with an initial set of 50 variables per pattern.
-It has been provided by the Spanish publishing company Trevenque Editorial S.L..
-Table
+The problem to solve in this work is the forecasting of sales for new
+launched books in the Spanish market, considering a set of `pre-sales
+variables' or at least variables that are under the control of the
+publisher before the book is going to be released to bookstores. The
+objective is to offer a tool for publishers which will help them to
+decide the best print run for a new book before its publication
+process starts. This is a forecasting problem for which no specific
+historical data are available and thus it is not simply a matter of
+analyzing a time series, instead, we have considered data about other,
+previously published, books and have taken as reference a set of
+variables (or features), 
+related with the book publication process.
+
+The training dataset includes historical data about 6083 books
+published in Spain for several years, with an initial set of 50
+variables per pattern. It has been provided by the Spanish publishing
+company Trevenque Editorial S.L. Table 
 \ref{tabla:paramsOrig50} shows the initial set of variables describing
@@
 
-Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \cite{wiki:dewey}, and the existing similarity relationship between the books inside a class or subclass.
-So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance.
-The same reasoning can be applied to subclasses.
+Therefore, in order to create simpler and more accurate prediction
+models, and with the aim to provide them as a useful decision-aid tool
+for the publisher, we have transformed the categorical variable
+\texttt{subject1} into a numerical one, considering it refers to a
+code of the Dewey Decimal Classification system for books
+\cite{wiki:dewey}, and the existing similarity relationship between
+the books inside a class or subclass. So, for instance, all the books
+inside subdivisions of class 200, `Religion', are considered as
+similar regarding their topics, so they could be also close in terms
+of distance. The same reasoning can be applied to subclasses.
 

### 2016-05-21 paper.tex
Working on the explanation of the trees
This is one of the main results of our paper and it was dispatched with a couple of lookie here, this graphic and some paragraphs. What we have to do in this paper is to actually look at the factors that make a book sell, and that is contained within those trees so I have added a good amount of explanation to them.

Refs #39 #25

@@
 variable, so it is the objective of the prediction methods. {\tt
-  total_sales} are a variable percentage of the {\tt print_run}, and
+  total\_sales} are a variable percentage of the {\tt print\_run}, and
 thus there is obviously some correlation between them, which might
@@
 
- \item \emph{Random Forest (RF)}: This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm.
-It was proposed by Breiman \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution.
+ \item \emph{Random Forest (RF)}: This method is based on the
+   construction of a set of decision trees using a stochastic process
+   over the basis of C4.5 algorithm. It was proposed by Breiman
+   \cite{Breiman2001} and aims to create independent and uncorrelated
+   trees based on different and random input vectors, following the
+   same distribution. 
 The result is the average of the generated trees during the process.
@@
 
-In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method applied to the data of the publisher that sells the most.
-These aim to demonstrate the value of the proposal to generate a useful decision-aid tool for an expert (publisher) to determine what sales can be expected for the different values of the input variables (including the print-run).
-
-First, Figure \ref{fig:decision_tree_best_seller} depicts the decision tree for the publishing company UDL929.
-The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales.
-The second decision tree (Figure \ref{fig:decision_tree_best_seller_fs}) corresponds to the same publishing company, so the same data were used, but the RAE feature selection method was applied.
-Thus, the main difference in the simplification of the regression models in the second tree and the remove of \texttt{print\_run} as part of the decision process after the feature selection.
-
-Examining both trees, it can be noticed that \texttt{tot\_points\_sale} variable appears twice in the trees, being also the root.
-This indicates that the total number of points of sale has a big influence on the decision models and also a major role in forecasting the total sales.
-This is an interesting clue for the experts, who could check the expected impact of different number of selling points
-According to the trees, \texttt{distrib\_novelty} has also a big repercussion, appearing at the second level of the top of the trees.
-
-An important fact that these tree models reveal is that marketing variables, such as the total number of points of sale and the number of units distributed as novelty have higher influence on the prediction than the selling price of the book, which could be, initially, considered as one of the most important parameters to determine sales.
-This interpretation leads us to suggest that companies could probably improve the accuracy of their sales forecasting models by incorporating more marketing related variables in their models.
+What is, then, the model obtained with our method? What factors have
+the biggest influence in sales and how can publisher use them to gauge
+sales of a new book? In order to do that, we have examined the models
+built during the regression, namely we present two of the decision
+trees generated by M5P method applied to the data of the publisher
+that sells the most. By looking at these trees, the publisher should
+be able to decide how many actual books should be printed to put them
+for sale, which was the initial objective of our research.
+
+The model obtained for the publishing company UDL929 is shown in
+Figure \ref{fig:decision_tree_best_seller}, which was the company that
+sold the most books in our data set. It makes sense to use data for a
+single company, since book sales for all companies is only available
+if you buy it; a single company, however, will have complete data on
+its own sales. This company is also representative because, being the
+one that sells the most, will have the biggest range of sales for
+individual books. In this figure, tree {\em leaves} correspond to
+linear regression models that can be easily computed to obtain the
+final predicted value for book sales.
+The second decision tree (Figure
+\ref{fig:decision_tree_best_seller_fs}) corresponds to the same
+publishing company, so the same data were used, but the RAE feature
+selection method was applied. This simplification, besides making the
+tree easier to understand, reduces training time to a fraction of what
+was needed before it.
+
+Examining both trees, it can be noticed that
+\texttt{tot\_points\_sale} variable appears twice in the trees, being
+also the root. This indicates that the total number of points of sale
+has the biggest influence on the decision models and also a major role in
+forecasting the total sales, implying that buyers have to actually
+{\em see}, maybe browse the book, before buying it. Books have to
+physically {\em be} in the point of sale, so this number gives a lower
+bound to the number of books that have to be printed; a stack of book
+will have to be present in each point of sale to attain that effect. 
+ This is an interesting clue for the
+experts, who could check the expected impact of different number of
+selling points. This feature also shows that there are different
+regimes depending on the number of points of sale, with best sellers
+being those that are distributed to more than roughly 500 points.
+
+The second {\em splitting} feature, number of books distributed as a
+novelty, gives the publisher a hint on how many books have to be sent
+to bookstores to stack on the {\em novelty} table. You need to sell
+roughly 5, the result of dividing 2807.5 y 550.5, to have a lower
+bound in sales at 1006, which is negatively impacted by the retail
+price and the number of points of sale in the first year of
+distribution. In all cases, the last number in the formula featured in
+the box gives you a baseline for sales, which the rest of the
+variables impacting positively or negatively. A whole treatise could
+be written on this decision tree but, in this case, let us look a bit
+more closely at this box and try and interpret it. For instance, price
+in this case will impact negatively on sales. For a typical retail
+price of a trade paperback of 12€, we would be looking at negative
+sales (if we disregard the rest of the variables) , which in this case
+will indicate that these are the kind of books, maybe paperbacks, that
+sell for a low price of around 5€. You also have to look at the
+relation between the factor for total points of sale and the total
+point of sales the first year. The fact that this last one is bigger
+indicates that the publisher will have to {\em increase} the number of
+points of sale after the first year, distributing it more shops at a
+more capilar level; the number of points of sale will have to be
+increased by 10\% to achieve a bit more than the baseline. All in all,
+the conclusion with this part of the tree is that you will have to
+print around 3000 books to sell a quantity that will start at 1000,
+one third of the print run, and changes depending on a number of
+factors, including price.
+
+An important fact that these tree models reveal is that marketing
+variables, such as the total number of points of sale and the number
+of units distributed as novelty have higher influence on the
+prediction than the selling price of the book, which could be,
+initially, considered as one of the most important parameters to
+determine sales. This interpretation leads us to suggest that
+companies could probably improve the accuracy of their sales
+forecasting models by incorporating more marketing related variables
+in their models. This does not mean that the retail price is not a
+factor; it appears in all models, but it will be a secondary factor
+that will have to be decided once the main ones are settled.
 
@@
   \epsfig{file=decision_tree_no_fs.eps,width=13cm}
-\caption{Decision Tree built by the M5P method for the best seller publishing company with all the pre-sales features.}
+\caption{Decision tree built by the M5P method for the best seller publishing company including all pre-sales features.}
 \label{fig:decision_tree_best_seller}
@@
   \epsfig{file=decision_tree_fs.eps,width=13cm}
-\caption{Decision Tree built by the M5P method for the best seller publishing company with the features selected by the ReliefAttributeEval method.}
+\caption{Decision tree built by the M5P method for the best seller
+  publishing company using  the subset of features selected by the
+  {\sf ReliefAttributeEval} method.} 
 \label{fig:decision_tree_best_seller_fs}

### 2016-05-21 paper.tex
Extended justification of results
With a deeper analysis of trees and what they imply. Closes #39.

@@
 points of sale after the first year, distributing it more shops at a
-more capilar level; the number of points of sale will have to be
+more capillary level; the number of points of sale will have to be
 increased by 10\% to achieve a bit more than the baseline. All in all,
@@
 factors, including price.
+
+The right hand side of the tree include those books that are
+distributed in a bigger percentage of the total amount of point of
+sale available in Spain, which in Spain includes not only proper
+bookstores, but also press stands and even supermarkets and hovers
+around several tens of thousands (around 24000, according to
+\ref{POS}), so we are clearly talking best sellers here distributed in
+as many places as possible. The first tree
+\ref{fig:decision_tree_best_seller} gives an idea of what we
+are talking about, sales start at 1000 but the single factor that has
+a bigger influence in sales is the topic, which has to be either 23 or
+1. '1' is the first digit of the classification used for all kind of
+general literary books. '23' includes philology, which includes either
+textbooks of maybe books in a foreign language; there are just a few
+of those, with '1' being far more common. So in principle these would
+be the typical best-sellers, literary prizes and big hits, but we
+would have to look more closely at the second tree
+\ref{fig:decision_tree_best_seller_fs} to check what are other factors
+influencing sales. It is also interesting that the number of total
+points of sale comes multiplied by 7, which would be a good baseline
+of books sold per outlet and give the publisher with a ballpark,
+around 4000 books, to print in the first print run. The picture
+painted by the second tree is a bit more bleak; obviously, even big
+publishing house produce flops from time to time, and those would be
+books which eventually print less than around 12500, indicating that
+there has not been a second print run, since best-seller print runs
+used to start at 15000 books\footnote{Nowadays in Spain that number
+  would be closer to 5000}. In general, that branch of the tree paints
+a pretty bleak picture: no matter how you combine the variable values,
+it will end up with sales much lower than the print run. The main
+problem with this tree is that its predictive value, with the
+variables that we have, is not too high, except for the hint we have
+on the subject matter. At the end of the day, there is a certain
+amount of unpredictability in how much a book sells and the only
+information we can give the publisher if he finds books sales adapt to
+this model is to boost points of sale and lower price so that sales
+pick a bit; in this sense and in certain cases our model is more
+informative than predictive, but having numeric models helps anyway
+the publisher with tailoring print runs and even increasing sales of
+books that have been already printed.
+
+The last box on the right of Figure
+\ref{fig:decision_tree_best_seller_fs} has a negative baseline, but
+this only indicates that the influence of the print run will be
+bigger. This probably indicates books that have been reprinted due to
+demand and it also tells how many are sold in every outlet: around 29
+books. The price, number of initial points of sale, number of books
+distributed as novelty and gifts all have a negative factor, but this
+is related to the fact that they will have to be selling for a long
+time, that is, not only be best, but also long sellers, which is also
+indicated by the positive factor in the number of weeks they are for
+sale.
+
+All in all, these seven groups revealed by the tree in Figure
+\ref{fig:decision_tree_best_seller_fs} constitute not only an accurate
+model for predicting book sales based on data available to the
+publisher, but also an informative tool that will allow publishers to
+estimate print runs based on forecasted sales, and establish other
+factors such as price, number of points of sale, and number of books
+distributed to outlets.
 

### 2016-05-21 paper.tex
Changing € symbol to avoid errors

@@
 in this case will impact negatively on sales. For a typical retail
-price of a trade paperback of 12€, we would be looking at negative
+price of a trade paperback of 12 euro, we would be looking at negative
 sales (if we disregard the rest of the variables) , which in this case
 will indicate that these are the kind of books, maybe paperbacks, that
-sell for a low price of around 5€. You also have to look at the
+sell for a low price of around 5 euro. You also have to look at the
 relation between the factor for total points of sale and the total

### 2016-05-21 paper.tex
Correcting @mgarenas name
Revised conclusion and introduction.
Addding a complete explanation of the book selling cycle and adding also more features to future work.

Closes #25
Closes #21

And I think that #11 should be closed too if @unintendedbear agrees.

@@
 \ead{palomacd@ugr.es}
-\author[ugr]{María I. García-Arenas}
+\author[ugr]{Mar\'ia I. Garc\'ia-Arenas}
 \ead{mgarenas@ugr.es}
@@
 
-Therefore, in this work we analyse the data by means of different data mining methods and create predictive models that can be mainly used as decision-aid tools for book publishers.
-Then, they will be able to combine their expert knowledge about the market with the created forecasting models in order to get a reliable estimation of book sales.
-
-% Antonio - I think this is the main idea we have to sell in this paper.
-Due to the  difficulty of the book sales market (and its variables), we cannot give an accurate tool for predicting book sales, but a decision-aid tool for publishers.
-Do you agree?
-% (Paloma) Agree
+In Spain, the process of releasing a book goes like this: the
+publisher decides, based on past experience, how many books to
+print. These books are distributed to points of sale, but also given
+out to reviewers and literary magazines, the number of these will
+depend on how many you have printed. Books then go, in some cases, to
+the {\em novelty} table, that is, prominently displayed in the
+bookstore, shown in the window, or highlighted using props or other
+kind of advertisement. Books stay for sale for as long as the
+publisher or the store want until the bookseller decides to return it
+to the publisher or just, in some cases, move it away from shelves to
+storage. Books returned to the publisher are pulped, sold back or
+given to the author or distributed in second-hand channels such as
+book stalls or second-hand bookstores. If the print run has been fully
+distributed and there are more requests from bookstores, on the other
+hand, a new print run is made and distributed to bookstores. 
+Even if the process has changed
+in the last few years since Amazon started to sell in Spain, which
+actually happened {\em after} the data used for this paper was
+collected, it roughly stays the same. Other countries will have a
+similar model, although scale will be different.
+
+Our intention in this paper is to find out the main factor influencing
+sales in order to give a tool that the publisher can use to decide how
+many books should be printed, as well as how to leverage these printed
+copies to maximize sales using the decision variables under his
+control. That is why, using data obtained from a  company that sells
+software for publishers, we analyse it by means of different data
+mining methods and create predictive models that can be mainly used as
+decision-aid tools for book publishers. With these models, publishers
+will be able to 
+combine their expert knowledge about the market with the created
+forecasting models in order to get a reliable estimation of book
+sales, and, based on it, act upon it to maximize the books sold for a
+particular print run.
 
@@
 
-\subsection{Decision trees for best seller}
+\subsection{Case study: publisher with the most sales}
 \label{subsec:decision_trees}
@@
 
-This is a very challenging problem in this industry, because printing a higher 
-number of volumes than those finally sold will lead to losses, while printing an adequate number of copies will optimise sales and company earnings.
-In addition, there are several difficulties inherent to the new book sales forecasting, such as the limited amount of historical data to consider or the variability of the market (fashions, seasonality), which do a difficult task finding an adequate forecasting method.
-
-A dataset consisting of 6000 books provided by the Spanish publishing company Trevenque Editorial S.L.
-has been used.
-These data have been analysed by means of Self-Organizing Maps as a visualisation tool, and two other Feature Selection techniques, namely a correlation-based feature subset evaluation method, and an adaptation of relief for attribute estimation.
-Using these methods the most relevant variables when predicting sales have been determined, while unrelated or superfluous ones have been removed.
-
-Four different datasets have also been extracted from the original one, each one corresponding to a Publishing house which we have considered as representative: the one with the most number of sales, the one with the medium number of sales, with the most varied sales (different books), and with a medium number of different books sold.
-
-Considering these datasets and the complete one, five machine learning models for sales forecasting have been configured (according to the problem requirements) and used to predict new book sales, from which the optimal print-run could be estimated.
-These algorithms include some based on Decision Trees (M5P and Random Forest), kNN, Support Vector Machines and Linear Regression.
-These methods have been evaluated considering several performance indicators (error measures) and also the time consumed to build the corresponding models.
+This is a very challenging problem in this industry, because printing
+a much higher 
+number of volumes than those finally sold will lead to losses, while
+printing an adequate number of copies will optimise sales and company
+earnings.  
+In addition, there are several difficulties inherent to the new book
+sales forecasting, such as the limited amount of historical data to
+consider or the variability of the market (fashions, seasonality),
+which do a difficult task finding an adequate forecasting method.
+
+A dataset consisting of 6000 books provided by the Spanish publishing
+company Trevenque Editorial S.L. has been used. This data has been
+analysed by means of Self-Organizing Maps as a visualisation tool, and
+two other Feature Selection techniques, namely a correlation-based
+feature subset evaluation method, and an adaptation of relief for
+attribute estimation. Using these methods the most relevant variables
+when predicting sales have been determined, while unrelated or
+superfluous ones have been removed.
+
+Four different datasets have also been extracted from the original
+one, each one corresponding to a publishing house which we have
+considered as representative: the one with the most number of sales,
+the one with the medium number of sales, with the most varied sales
+(different books), and with a medium number of different books sold.
+
+Considering these datasets and the complete one, five machine learning
+models for sales forecasting have been configured (according to the
+problem requirements) and used to predict new book sales, from which
+the optimal print-run could be estimated. These algorithms include
+some based on Decision Trees (M5P and Random Forest), kNN, Support
+Vector Machines and Linear Regression. 
+These methods have been evaluated considering several performance
+indicators (error measures) and also the time consumed to build the
+corresponding models.
 
@@
 (lowest error) on average, even with acceptable values regarding the training time.
-In addition, the Decision Trees obtained with this method have been presented 
-as an excellent decision-aid tool for publishers, since they are accurate 
+In addition, the Decision Trees obtained with this method have been
+shown to be an excellent decision-aid tool for publishers, since they are accurate 
 and quite easy to understand and apply. 
-They are also able to provide insights on the decisions that have a higher influence on the 
-expected sales 
-%print-run 
-for these publishers.
-
-This, compared to the output of black-box models such as artificial neural networks, was a determining advantage from the point of view of the needs of experts and Trevenque company.
-
-%Moreover, proposed method was validated by the company and incorporated in a 
-%business intelligence tool for publishing companies. %FERGU: no hay más info de esto? estaría guay describirlo
-
-The feature selection techniques have also shown to positively affect all the results, yielding a better performance in time to train while maintaining good accuracy.
-Moreover, their application leads to obtain even simpler models.
-
-Overall, this study contributes to the literature by proposing the use of different soft-computing standard techniques to solve a new challenging problem.
-Moreover, proposed method could be implemented, not only in the publishing 
-industry, but also in other domains where the specificity of products is similar, and might be of interest to other academic researches and industrial practitioners.
+They are also able to provide insights on the decision variables that
+have a higher influence on the predicted sales for these publishers.
+
+This, compared to the output of black-box models such as artificial
+neural networks, was a determining advantage from the point of view of
+the needs of experts and the company that initially contacted us for
+this work.
+
+The feature selection techniques have also shown to positively affect
+all the results, yielding a better performance in time to train while
+maintaining good accuracy. Moreover, their application leads to obtain
+even simpler models.
+
+Overall, this study contributes to the literature by proposing the use
+of different soft-computing standard techniques to solve a new
+challenging problem. 
+Moreover, proposed method, consisting in selecting features and
+applying different models for different types of publishers could be
+implemented, not only in the publishing  
+industry, but also in other domains where the specificity of products
+is similar such as novelty items or toys, and might be of interest to other academic researches and
+industrial practitioners.  
 % Antonio - I don't know if we should say this...
@@
 
-As future work, it would be interesting to compare the obtained forecasting results with those yielded by other soft-computing methods, such as genetic programming or fuzzy logic.
-Moreover, even if the methods have been configured to obtain the best forecasting results, it would be of interest carrying out some automatic parameter-tuning procedure by means of optimisation meta-algorithms,
+As future work, it would be interesting to compare the obtained
+forecasting results with those yielded by other soft-computing
+methods, such as genetic programming or fuzzy logic. 
+Moreover, even if the methods have been configured to obtain the best
+forecasting results, it would be of interest carrying out some
+automatic parameter-tuning procedure by means of optimisation
+meta-algorithms,  
 % Antonio - add an ESWA reference to this. :D
-for instance.
+for instance. If data for other countries were available, it would be
+interesting to observe, and factor in the method, country differences,
+even considering the same book and how it sells in different
+countries.
 

### 2016-05-23 paper.tex
fixing the 'POS' citation
Revision of Experiments section and new contents
Add a couple of refererences for future work.

Closes #38.

@@
   % sales forecasting in printed circuit board industry.
-In another hand, in those cases where historical data are available, classical time series 
-forecasting methods have been applied, such as in \cite{Chang2009}, 
+In another hand, in those cases where historical data are available, classical time series forecasting methods have been applied, such as in \cite{Chang2009}, 
 where a hybrid model integrating K-Means and fuzzy neural networks to forecast 
@@
 and taking that into account decide on the actual number of books that
-are going to be printed. Just to be clear, printing book does not
+are going to be printed. Just to be clear, printing books does not
 actually sell them, but it is obviously necessary to print books
@@
 neuron which has the shortest distance with the presented input vector
-is updated along with the neurons in its neighbourhood. This neuron is called the
-best matching unit (BMU). The goal of the learning process is to
+is updated along with the neurons in its neighbourhood. This neuron is called the best matching unit (BMU). The goal of the learning process is to
 minimise the neighbourhood distance in the output clusters.
@@
 
-We have analysed the whole dataset (all the publishing companies), but also performed some experiments considering specific publishing companies as example cases.
-The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for publishers.
+We have analysed the whole dataset (all the publishing companies), but also performed some experiments considering specific and representative publishing companies as example cases.
+Some of the obtained decision trees have been plotted to show their simplicity and to remark their real value as a decision-aid tool for publishers.
 
@@
 In most data mining and machine learning algorithms, the values of
-some parameters have a high influence on its performance. In our
-experiments, the best value of $k$ in the $k$-nearest neighbour was
-empirically found at $k=3$. % What???? - JJ
- For SVM, the widely used Radial Basis
-Function (RBF) kernel is selected. As reported in several studies, RBF
-kernel has a reliable performance and can analyse higher dimensional
-data \cite{yu2004ec,chao2015construction,huang2006ga}. Two important
+some parameters have a high influence on its performance.
+We have conducted a systematic experimentation process, along with a revision of the bibliography describing the best configuration parameters for the methods we have applied here.
+
+Thus, in our experiments, the best value of $k$ in the $k$-nearest neighbour was empirically found at $k=3$. % What???? - JJ
+For SVM, the widely used Radial Basis Function (RBF) kernel is selected.
+As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}.
+Two important
 parameters should be tuned in SVM: the Cost $(C)$ and Gamma $(\gamma)$ of
@@
 function \cite{hornik1989multilayer,mirjalili2014let}. However, there
-is no rule of thumb on selecting the best number of neurons in the
+is no rule of thumb for selecting the best number of neurons in the
 hidden layer. One suggested method that is followed in this work is to
@@
 
-All experiments are performed using 10-fold cross validation \cite{Geisser1993,Kohavi1995,Devijver1982}.
-The dataset is partitioned into 10 parts where the training process is carried out on 9 parts then the resulted model is tested on the left 10th part.
-This process is repeated 10 times, each time the model is trained using different 9 parts.
+All experiments have been performed using the standard 10-fold cross validation \cite{Geisser1993,Kohavi1995,Devijver1982}: then, the dataset is partitioned into 10 parts where the training process is carried out on 9 parts and after this, the resulting model is tested on the left 10th part.
+This process is repeated 10 times, training the models using different 9 parts.
 At the end of the process the 10 evaluation results on the testing parts are averaged.
@@
 
-In addition, due to the stochastic component present in some of the methods and also in order to evaluate the running time, 30 repetitions of each experiment have been done per method.
+In addition, due to the stochastic component present in some of the methods and also in order to fairly evaluate the running time, 30 repetitions of each experiment have been done per method.
 Then the average and standard deviation have been computed.
@@
 applied to the whole dataset. All the pre-sales features have been
-considered, including the categorical ones, which make it harder to
-process the instances and build the different models. SVM for
+considered, including the categorical ones, which makes it harder to
+process the input patterns and build the different models. SVM for
 instance, must previously transform these categories into binary
@@
 \begin{table}
-\caption{Predicting Total sales for all publishers (all the features). 10 repetitions, 10-fold cross validation. Best values in bold.
+\caption{Predicting Total sales for all publishers (all the features). 30 repetitions, 10-fold cross validation. Best values in bold.
 \label{tab:all_publishers_no_fs}}
@@
 
-As far as the different methods are concerned, M5P model obtained the best results, 
-both in time and error. The advantage of M5P is that it can learn and tackle 
-classification tasks that have high dimensionality and categorical variables efficiently.
+As far as the different methods are concerned, M5P model obtained the best results, both in time and error.
+The advantage of M5P is that it can learn and tackle classification tasks that have high dimensionality and categorical variables efficiently.
 Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation.
 Thus, it is very suitable model be incorporated in a publishing company
-processes.
-
-Taking into account the obtained results by SVM model, this method obtains comparable 
-errors to those of M5P. Even when using roughly tuned parameter values, it shows 
-a good generalisation performance. However, SVM is much slower than the others to build the model, not only when using the dataset with categorical input variables, but also when using the 
-datasets with numerical variables, not to mention the extra time needed to optimize its hyperparameters.
-
-According to Table \ref{tab:all_publishers_no_fs}, it can be noticed also that the Linear Regression model outperformed some other complex methods like the random forest, both in time and in obtained errors.
+processes (as we will show in Section \ref{subsec:decision_trees}).
+
+Taking into account the obtained results by SVM model, this method obtains comparable errors to those of M5P.
+Even when using roughly tuned parameter values, it shows a good generalisation performance.
+However, SVM is much slower than the others to build the model, not only when using the dataset with categorical input variables, such as \emph{collection} and \emph{binding}, but also when using the datasets with numerical variables, not to mention the extra time needed to optimize its hyperparameters.
+
+According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that the Linear Regression model outperforms some other complex methods like the Random Forest, both in time and in obtained errors.
 Although, Linear regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.
@@
 is the simplest one. However, the model is slow when classifying large number of 
-training examples, and it exhibits a poor generalisation ability since it does not 
-learn anything from the training data.
-
-Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \emph{collection} and 
-\emph{binding}.
-
-Finally, paying attention to the cost in time to obtain the forecasting models 
-and their accuracy, the M5P model is the most adequate to solve the problem of 
-how many books should be printed when a new book is published.
-This forecasting method, with these additional advantages, can be used for products 
-with historical sales data and for new products with little or no historical 
-data available.
+training examples, and it exhibits a poor generalisation ability since it does not learn anything from the training data.
+
+%Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \emph{collection} and \emph{binding}.
+
+As a first conclusion, paying attention both to the cost in time to obtain the forecasting models and their accuracy, the M5P model would be the most adequate to solve the problem of how many books should be printed when a new book is published.
+This forecasting method, with these additional advantages, can be used for products with historical sales data and for new products with little or no historical data available.
 
@@
 The aim of these methods is to reduce the number of features considered in developing the forecasting models which consequently simplify the complexity of the models, improve their interpretability and decrease the training time.
-The simpler models generated after performing feature selection could give the decision maker a better insight on the underlying process by identifying the more influencing variables.
+The simpler models generated after performing feature selection could give the decision maker a better insight on the underlying process by identifying the most influencing variables.
 
@@
 
-The dataset has also been projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
-An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features \emph{collection} and \emph{binding} have been
-removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
+The dataset has also been analysed using SOM, and a visual exploration of the obtained results has been performed in order to determine the best variables to consider.
+An important preprocessing step has been carried out before conducting the SOM analysis.
+Thus, the two categorical features \emph{collection} and \emph{binding} have been removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
 However, since they have a large number of unique different values this would be finally impracticable and useless.
 
-Several configurations for SOM have been tested and the one regarding both the \textit{quantisation error} and \textit{topographic error} has been chosen.
-The first is a measure which represents the average distance between every input pattern and its BMU (i.e.
+In the analysis, several configurations for SOM have been tested, and the best one regarding both the \textit{quantisation error} and \textit{topographic error} has been chosen.
+The first error is a measure which represents the average distance between every input pattern and its BMU (i.e.
 how good the map fits the dataset).
-The second error refers to the topology of the map and its preservation, so it measures an average value computed looking at both, the first and the second BMUs for every pattern.
+The latter refers to the topology of the map and its preservation, so it measures an average value computed looking at both, the first and the second BMUs for every pattern.
 If they are neighbours (directly connected in the map) a `1' is considered, otherwise a `0' is taken.
@@
 The best SOM training results have been obtained with a final quantisation error of 0.691 and topographic error of 0.046.
-% explain what is quantisation and topographic error and why it is important - JJ
-% Antonio - done. ;)
 
 Figure \ref{fig:componentplanes} shows the U-matrix along with the component planes analysis resulted from SOM training. The term component refers in SOM to a variable or feature of the problem.
-% really, are you reading this with the mind of someone that has no
-% idea what is SOM or U-Matrix or whatever? Tell first what you are
-% going to do, then tell why you are doing it, explain all the
-% terminology and then show the results. You can't keep saying "I have
-% done this and this is the result. You have to explain why you are
-% doing it, what you are doing, how you are doing it and then how to
-% interpret the results - JJ
-% Antonio - now it must be clearer with the new explanations given before
-The component planes in Figure 
-%what is a plane? Really, you don't know what's in the mind of the reader (or reviewer#3, who is a son of a bitch - JJ
-% Antonio - now it should be clear. This is the accurate term for the output of SOM: component planes analysis
-\ref{fig:componentplanes} show the trend of values of the prototype
-vectors of the SOM map units. These values are represented as
-colours. The colourbar on the right of each component plane shows the
-indication of each colour. On the other side, the U-matrix on the top
+The component planes in Figure \ref{fig:componentplanes} show the trend of values of the prototype vectors of the SOM map units.
+These values are represented as colours.
+The colourbar on the right of each component plane shows the indication of each colour.
+On the other side, the U-matrix on the top
 left corner shows the distances between the adjacent units. It is
@@
 the distances between units are also represented as inter-neuron hexagons.
-                                % but
-                                % explain that at the beginning!
-                                % Devote one or two paragraphs to tell
-                                % the reader what is U-Matrix, a
-                                % reference, why we are using it and
-                                % how it conveys more information that
-                                % a pure and simple feature selection
-                                % (which we are doing anyway). If we
-                                % don't, Reviewer #3 (who is,
-                                % remember, a son of a bitch) will
-                                % tell you to just suppress that whole
-                                % section - JJ
-% Antonio - I have done it. However Ihave focused the explanation on the feature selection 'ability' of the method. ;)
 
@@
 
-The selected features per method are shown in Table \ref{tab:features_selected}. Logically, just the independent or input variables are considered.
+The selected features using each one of the three methods are shown in Table \ref{tab:features_selected}. Logically, just the independent or input variables are considered.
 
@@
 
-After applying the feature selection methods, we have run the same
+After applying the feature selection process, we have run the same
 forecasting models as in Section \ref{subsec:results_all_publishers}
@@
                                 %- JJ
- In general, all feature selection methods have reduced the training time needed to build the forecasting methods, this is because they reduced the features and excluded the categorical features that have many possible values.
-On the other side, CSE and SOM did not perform as good as RAE which could be explained due to the extensive reduction made by CSE and due to the human intervention in the case of SOM.
+As expected, in general, all feature selection methods have reduced the training time needed to build the forecasting methods.
+This is because they reduced the considered features and mainly because they excluded the categorical features, which are the hardest to be managed (they have many possible values).
+On the other side, CSE and SOM did not perform as good as RA.
+This could be explained due to the extensive reduction made by CSE and due to the `subjective' (but not so accurate) human intervention in the case of SOM.
 
@@
 Therefore, it is an example of a case on a higher business scale.
-    \item Mid-range seller publishing company: this represents an publishing company that sells medium number of copies compared to the other publishing companies (Medium business scale). 
-    \item Highest variation publishing company: this is an example of an publishing company that follows a strategy in publishing a very wide range of different titles.
-    \item Medium varied publishing company: this case represents an publishing company that has a median rank between the other publishing company regarding the variety of titles sold.
+    \item Mid-range seller publishing company: this represents a publishing company that sells medium number of copies compared to other publishing companies (Medium business scale). 
+    \item Highest variation publishing company: this is an example of a publishing company that follows a strategy in publishing a very wide range of different titles.
+    \item Medium varied publishing company: this case represents a publishing company that has a median rank between the other publishing companies regarding the variety of titles sold.
 \end{itemize}
 
-Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected publishing companies.
+Table \ref{Table:special_cases} shows the number of sold copies and the number of titles published by the selected companies.
 
@@
 The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}.
-In general, M5P, RF and SVM performed better than the simple classifiers kNN and LR.
+In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR.
 In the case of Best selling publisher houses (i.e.
@@
 UDL704), M5P could be recommended as it shows more accurate forecasting results than the other models.
-While in the case of medium sized publishers, in terms of sales and number of published books, the RF model is recommended.
+While in the case of medium sized publishers, in terms of sales and number of published books, the RF model would be adequate.
 
@@
 
-In the second stage of the experiments for the special cases, the
+In this stage of the experiments for the special cases, the
 feature selection methods (RFE, CSE and SOM) are applied for each case
@@
 one was chosen since the selected features by this
-method showed the highest predictive power among all classifiers. 
+method showed in the previous experiment the highest predictive power among all classifiers. 
 %According to the aforementioned tables, 
 %It's not according to a table. It's according to the results there - JJ
-RFE
-has noticeably improved % with respect to what? -JJ
-the performance of all classifiers specially
-in the case of the best selling publisher house (i.e. UDL929) and the
-publisher who publishes a wide range of different books
-(i.e. UDL704). For the rest of the results which are obtained by CSE
-and SOM feature selection methods we refer the reader to the appendix
-of tables at the end of this paper.
+RFE reduction has noticeably improved the performance of all classifiers specially in the case of the best selling publisher house (i.e. UDL929) and the
+publisher which publishes a wide range of different books (i.e.
+UDL704).
+For the rest of the results which are obtained by CSE and SOM feature selection methods we refer the reader to the appendix of tables at the end of this paper.
 
@@
 What is, then, the model obtained with our method? What factors have
-the biggest influence in sales and how can publisher use them to gauge
+the biggest influence in sales and how can a publisher use them to gauge
 sales of a new book? In order to do that, we have examined the models
-built during the regression, namely we present two of the decision
+built during the regression. Namely we present two of the decision
 trees generated by M5P method applied to the data of the publisher
@@
 around several tens of thousands (around 24000, according to
-\ref{POS}), so we are clearly talking best sellers here distributed in
+\cite{POS}), so we are clearly talking best sellers here distributed in
 as many places as possible. The first tree
@@
 automatic parameter-tuning procedure by means of optimisation
-meta-algorithms,  
+meta-algorithms \cite{Cheng2006_tunningSVM,Lessmann2011_tunningDM},  
 % Antonio - add an ESWA reference to this. :D
-for instance. If data for other countries were available, it would be
+% Antonio - I have done it.
+for instance.
+
+In addition, if data for other countries were available, it would be
 interesting to observe, and factor in the method, country differences,

### 2016-06-03 paper.tex
closing issues: Closes #11
closing issues: Closes #30
Revising references and including some new in KBS

@@
 
-At this stage, a Feature Selection (FS) process has been carried out, since it is an effective dimensionality reduction technique and an essential preprocessing method to discard less relevant or non-useful features \cite{Krishnapuram2004}.
+At this stage, a Feature Selection (FS) process has been carried out, since it is an effective dimensionality reduction technique and an essential preprocessing method to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.
 
@@
 For SVM, the widely used Radial Basis Function (RBF) kernel is selected.
-As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}.
-Two important
-parameters should be tuned in SVM: the Cost $(C)$ and Gamma $(\gamma)$ of
-the RBF kernel. We apply grid search which is the most common approach
+As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction}.
+Two important parameters should be tuned in SVM: the Cost $(C)$ and Gamma $(\gamma)$ of the RBF kernel.
+We apply grid search which is the most common approach
 to find $C$ and $\gamma$. The best performance of SVM was found at
@@
 automatic parameter-tuning procedure by means of optimisation
-meta-algorithms \cite{Cheng2006_tunningSVM,Lessmann2011_tunningDM},  
-% Antonio - add an ESWA reference to this. :D
-% Antonio - I have done it.
+meta-algorithms \cite{huang2006ga,Mookiah2013_EA_Tuning,Shen2016_FFly_Tuning},  
+% Antonio - changed to include KBS references
 for instance.
@@
 
-This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
+This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness and FEDER), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
 

### 2016-08-05 Response to reviewers.tex
Uploaded a template for response
We can add our response to reviewers' comments here

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment: Response to Reviewers\' comments}

\noindent
Dear Sirs,\\

First, we would like to express our gratitude to you, the editorial team, and the reviewers whose valuable comments on this paper have significantly improved its quality. We have addressed all the comments in the new version of the paper and will list all the changes item-by-item in response to the mentioned comments below. \\

\noindent
Yours sincerely,\\
The authors.

\section{Comments by Reviewer \#1}

\noindent There are some issues needed to be aaddressed further: \\

\noindent (1) Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF ? \\

\begin{verbatim}
Our response here
\end{verbatim}

\noindent (2) In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ? For RF, how many trees are set ?\\

\begin{verbatim}
Our response here
\end{verbatim}

\noindent (3) As we known, tree-based mehods (e.g.,M5P and RF) themselve embed feature selection procedure. That is, some features are choosen to build trees. It is not fair enough to compare five methods in Table 3. \\

\begin{verbatim}
Our response here
\end{verbatim}

\noindent (4) It seems more reasonable to organize and write that paper according to regression viewpoint only.\\

\begin{verbatim}
Our response here
\end{verbatim}

\noindent (5) It is necessary to write that paper more concisely.\\

\begin{verbatim}
Our response here
\end{verbatim}

\section{Comments by Reviewer \#2}

\noindent This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors:\\

\noindent (1) The ANN and ELM (extreme learning machine) should be added into the experiments;\\

\noindent (2) The authors should clarify their main contributions in the introduction parts.\\

\noindent (3) Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part.\\

\noindent (4) Some tables should be transfer to figures because there are too many figures.\\

\noindent (5) Graphical abstract should be added.
This paper is organized well. The authors should revise their work according to above comments.\\

\section{Comments by Reviewer \#3}

\noindent There are several concerns should be considered. \\

\noindent (1) In section introduction, this manuscript should describe the contribution of this work.\\

\noindent (2) In sections 4.1 and 4.2 should be moved to section 2.\\

\noindent (3) In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it.\\

\noindent (4) In Section 5, parameter settings of M5P, kNN and RF also should be shown.

\end{document}

### 2016-08-05 paper.tex
New Title
Please all, have a look
New title (again due to an error)
updating with the KBS format version

@@
-\documentclass[final,1p,times]{elsarticle}
+%\documentclass[final,1p,times]{elsarticle}
+%\documentclass[twocolumn]{elsarticle}
+\documentclass[a4paper,10pt,twocolumn,preprint,3p]{elsarticle}
+
 \usepackage{graphics}
@@
 
-\journal{Expert Systems with Applications}
+\journal{Knowledge-Based Systems}
 
@@
 %%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
-\title{Enhancing the prediction of sales for newly published books by
- means of computational intelligence methods}
+\title{Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment}
+
+%\setlength\textwidth\columnwidth
 
 %%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
-
 \author[ugr]{Pedro A. Castillo}
@@
 
-\begin{table}[!ht]
+\begin{table*}[!ht]
 \caption{Parameters describing a book, provided by the company Trevenque S.L.}
@@
 \end{center}
-\end{table}
+\end{table*}
 
@@
 
-\begin{table}
+\begin{table*}
 % Shouldn't this table go to "Problem description"? It is a
@@
 
-\begin{table}
+\begin{table*}
 \caption{Predicting Total sales for all publishers (all the features). 30 repetitions, 10-fold cross validation. Best values in bold.
@@
 }
-\end{table}
+\end{table*}
 
@@
 
-\begin{table}
+\begin{table*}
 \caption{Input features/variables selected by each method
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
 
-\begin{table}
+\begin{table*}
 \centering{}%
@@
 
-\begin{table}
+\begin{table*}
 \caption{Description of publishing companies considered as special cases.}
@@
 \label{Table:special_cases}
-\end{table}
+\end{table*}
 
@@
 
-\begin{table}
+\begin{table*}
 \caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company). Best values in bold. }
@@
 \label{Table:case1results}
-\end{table}
-
-\begin{table}
+\end{table*}
+
+\begin{table*}
 \caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company). Best values in bold. }
@@
 \label{Table:case2results}
-\end{table}
-
-\begin{table}
+\end{table*}
+
+\begin{table*}
 \caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold). Best values in bold.}
@@
 \label{Table:case3results}
-\end{table}
-
-\begin{table}
+\end{table*}
+
+\begin{table*}
 \caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold)). Best values in bold.}
@@
 \label{Table:case4results}
-\end{table}
+\end{table*}
 
@@
 
-\begin{table}[!ht]
+\begin{table*}[!ht]
 % Why the capital in Total? If it's a variable use Small Caps or Sans
@@
 \label{Table:case1results-RAE}
-\end{table}
-
-\begin{table}[!ht]
+\end{table*}
+
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
@@
 \label{Table:case2results-RAE}
-\end{table}
-
-\begin{table}[!ht]
+\end{table*}
+
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS). Best values in bold. }
@@
 \label{Table:case3results-RAE}
-\end{table}
-
-\begin{table}[!ht]
+\end{table*}
+
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo-UDLU11 (ReliefFAttributeEval-FS). Best values in bold.}
@@
 \label{Table:case4results-RAE}
-\end{table}
+\end{table*}
 
@@
 
-\begin{figure}[!ht] 
+\begin{figure*}[!ht] 
 \begin{center}
@@
 \end{center}
-\end{figure}
-
-\begin{figure}[!ht] 
+\end{figure*}
+
+\begin{figure*}[!ht] 
 \begin{center}
@@
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{refs}
+%\bibliography{refs}
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\expandafter\ifx\csname href\endcsname\relax
+  \def\href#1#2{#2} \def\path#1{#1}\fi
+
+\bibitem{Fildes2010}
+R.~Fildes, B.~Kingsman, {Incorporating demand uncertainty and forecast error in
+  supply chain planning models}, J Oper Res Soc 62 (2010) 483--500.
+
+\bibitem{Saeed2008}
+K.~Saeed, {Trend forecasting for stability in supply chains}, J Bus Res 61
+  (2008) 1113--1124.
+
+\bibitem{Zhao2001}
+X.~Zhao, J.~Xie, R.~Lau, {Improving the supply chain performance: use of
+  forecasting models versus early order commitments}, Int J Prod Res 39~(17)
+  (2001) 3923--3939.
+
+\bibitem{Little1998}
+J.~Little, {Integrated measures of sales, merchandising and distribution}, Int
+  J Res Mark 15 (1998) 473--485.
+
+\bibitem{Armstrong2001}
+J.~Armstrong, {Principles of forecasting. A handbook for researchers and
+  practitioners}, Kluwer, Norwell, 2001.
+
+\bibitem{SThomassey2014}
+S.~Thomassey, {Sales Forecasting in Apparel and Fashion Industry: A Review},
+  Intell Fashion Forecasting Syst: Models and App (2014) 2--27.
+
+\bibitem{DeToni2000}
+A.~D. Toni, A.~Meneghetti, {The production planning process for a network of
+  firms in the textile-apparel industry}, Int J Prod Econ 65 (2000) 17--32.
+
+\bibitem{kohonen1998}
+T.~Kohonen, {The self-organizing map}, Neurocomputing 21~(1-3) (1998) 1--6.
+
+\bibitem{Chang2009}
+P.~Chang, C.~Liu, C.~Fan, {Data clustering and fuzzy neural network for sales
+  forecasting: A case study in printed circuit board industry}, Knowl Based
+  Syst (2009) 344--355.
+
+\bibitem{Sanders1994}
+N.~Sanders, K.~Manrodt, {Forecasting practices in US corporations: Survey
+  results}, Interfaces 24~(2) (1994) 92--100.
+
+\bibitem{Papalexopoulos1990}
+A.~Papalexopoulos, T.~Hesterberg, {A regression-based approach to short-term
+  system load forecasting}, IEEE Trans Power Syst 5 (1990) 1535--1547.
+
+\bibitem{Yoo1999}
+H.~Yoo, R.~Pimmel, {Short-term load forecasting using a self-supervised
+  adaptive neural network}, IEEE Trans Power Syst 14~(2) (1999) 779--784.
+
+\bibitem{Mastorocostas2001}
+P.~Mastorocostas, J.~Theocharis, V.~Petridis, {A constrained orthogonal
+  least-squares method for generating TSK fuzzy models: application to
+  short-term load forecasting}, Fuzzy Set Syst 118 (2001) 215--233.
+
+\bibitem{Chu2003}
+C.~Chu, P.~Zhang, {A comparative study of linear and nonlinear models for
+  aggregate retail sales forecasting}, Int J Prod Econ 86 (2003) 217--231.
+
+\bibitem{Brown1959}
+R.~Brown, {Smoothing forecasting and prediction of discrete time series},
+  Prentice Hall, Englewood Cliffs, 1959.
+
+\bibitem{Winters1960}
+P.~Winters, {Forecasting sales by exponential weighed moving averages}, Manag
+  Sci 6 (1960) 324--342.
+
+\bibitem{Box1969}
+G.~Box, G.~Jenkins, {Time series analysis forecasting and control}, Prentice
+  Hall, Englewood Cliffs, 1969.
+
+\bibitem{KayacanUK10}
+E.~Kayacan, B.~Ulutas, O.~Kaynak, Grey system theory-based models in time
+  series prediction, Expert Syst Appl 37~(2) (2010) 1784--1789.
+
+\bibitem{ChingChin2010}
+C.~Ching-Chin, A.~I.~K. Ieng, W.~Ling-Ling, K.~Ling-Chieh, {Designing a
+  decision-support system for new product sales forecasting}, Expert Syst Appl
+  37~(2) (2010) 1654--1665.
+
+\bibitem{FaderHardie2005}
+S.~Fader, B.~Hardie, {The value of simple models in new product forecasting and
+  customer-base analysis}, Appl Stoch Model Bus (2005) 461--473.
+
+\bibitem{Madsen2008}
+H.~Madsen, {Time series analysis}, Chapman and Hall. CRC Co., 2008.
+
+\bibitem{Lapide1999}
+L.~Lapide, {New developments in business forecasting}, J Bus Forecasting (1999)
+  29--30.
+
+\bibitem{ChernWSF15}
+C.-C. Chern, C.-P. Wei, F.-Y. Shen, Y.-N. Fan, A sales forecasting model for
+  consumer products based on the influence of online word-of-mouth., Inf Syst E
+  Bus Manag 13 (2015) 445--473.
+
+\bibitem{Moon2010ICSSSM}
+G.~Moon, G.~Kikuta, T.~Yamada, A.~Yoshikawa, T.~Terano, {Blog information
+  considered useful for book sales prediction}, in: 7th International
+  Conference on Service Systems and Service Management (ICSSSM), IEEE. Tokyo,
+  2010, pp. 1--5.
+
+\bibitem{Moon2010ICEC}
+G.~Moon, G.~Kikuta, T.~Yamada, A.~Yoshikawa, T.~Terano, Categorization of sales
+  patterns to use blog information as book sales prediction, in: Proceedings of
+  the 12th International Conference on Electronic Commerce: Roadmap for the
+  Future of Electronic Business, ICEC '10, ACM, New York, NY, USA, 2010, pp.
+  1--7.
+
+\bibitem{Hammond1990}
+J.~Hammond, {Quick response in apparel industries}, Havard Business school,
+  Cambridge, 1990.
+
+\bibitem{Xia2012}
+M.~Xia, Y.~Zhang, L.~W.~S. Ye, {Fashion retailing forecasting based on extreme
+  learning machine with adaptive metrics of inputs}, Knowl Based Syst 36 (2012)
+  253--259.
+
+\bibitem{Thomassey2012}
+S.~Thomassey, {Sales forecasts in clothing industry. The key success factor of
+  the supply chain management}, Int J Prod Econ 128 (2012) 470--483.
+
+\bibitem{wiki:dewey}
+Wikipedia,
+  \href{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}{List
+  of dewey decimal classes}, [Online; accessed 05-May-2016].
+\newline\urlprefix\url{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}
+
+\bibitem{fayyad1996data}
+U.~Fayyad, G.~Piatetsky-Shapiro, P.~Smyth, From data mining to knowledge
+  discovery in databases, AI magazine 17~(3) (1996) 37.
+
+\bibitem{kittler1986feature}
+J.~Kittler, Handbook of pattern recognition and image processing, Academic
+  press, 1986.
+
+\bibitem{Krishnapuram2004}
+B.~Krishnapuram, A.~Hartemink, L.~Carin, M.~Figueiredo, {A Bayesian Approach to
+  Joint Feature Selection and Classifier Design}, IEEE T Pattern Anal 26~(9)
+  (2004) 1105--1111.
+
+\bibitem{Chen2011_FS_PTS}
+Y.~Chen, D.~Miao, R.~Wang, K.~Wu, A rough set approach to feature selection
+  based on power set tree, Knowl Based Syst 24~(2) (2011) 275 -- 281.
+
+\bibitem{Selvakuberan2008}
+K.~Selvakuberan, M.~Indradevi, R.~Rajaram, {Combined Feature Selection and
+  classification - A novel approach for the categorization of web pages}, J Inf
+  Comp Sci 3~(2) (2008) 083--089.
+
+\bibitem{liu1998feature}
+H.~Liu, H.~Motoda, {Feature extraction, construction and selection: A data
+  mining perspective}, Springer Science \& Business Media, 1998.
+
+\bibitem{Hall2009}
+M.~Hall, E.~Frank, G.~Holmes, B.~Pfahringer, P.~Reutemann, I.~Witten, {The WEKA
+  data mining software: an update}, ACM SIGKDD Explor Newslett 11~(1) (2009)
+  10--18.
+
+\bibitem{Witten2011}
+I.~Witten, E.~Frank, M.~Hall, {Data mining: Practical machine learning tools
+  and techniques}, Morgan Kaufmann, 2011.
+
+\bibitem{Hall1998}
+M.~A. Hall, Correlation-based feature subset selection for machine learning,
+  Ph.D. thesis, University of Waikato, Hamilton, New Zealand (1998).
+
+\bibitem{RobnikSikonja1997}
+M.~Robnik-Sikonja, I.~Kononenko, An adaptation of relief for attribute
+  estimation in regression, in: D.~H. Fisher (Ed.), Fourteenth International
+  Conference on Machine Learning, Morgan Kaufmann, 1997, pp. 296--304.
+
+\bibitem{Kira1992}
+K.~Kira, L.~A. Rendell, {A Practical Approach to Feature Selection}, in: D.~H.
+  Sleeman, P.~Edwards (Eds.), Ninth International Workshop on Machine Learning,
+  Morgan Kaufmann, 1992, pp. 249--256.
+
+\bibitem{UmatUlts}
+S.~Ultsch, Kohonen's self-organizing maps for exploratory data analysis, in:
+  Proc. of the INNC'90, 2000, pp. 305--308.
+
+\bibitem{Quinlan1986}
+J.~Quinlan, {Induction of decision trees}, Mach Learn 1 (1986) 181--186.
+
+\bibitem{Quinlan1992}
+R.~J. Quinlan, Learning with continuous classes, in: 5th Australian Joint
+  Conference on Artificial Intelligence, World Scientific, Singapore, 1992, pp.
+  343--348.
+
+\bibitem{Wang1997}
+Y.~Wang, I.~H. Witten,
+  \href{https://www.researchgate.net/profile/Ian_Witten/publication/33051395_Induction_of_model_trees_for_predicting_continuous_classes/links/545948ea0cf2cf516483ce67.pdf}{Induction
+  of model trees for predicting continuous classes}, Tech. rep., Dept. of
+  Computer Science, University of Waikato, working Paper 96/23, Poster papers
+  of the 9th European Conference on Machine Learning (1996).
+\newline\urlprefix\url{https://www.researchgate.net/profile/Ian_Witten/publication/33051395_Induction_of_model_trees_for_predicting_continuous_classes/links/545948ea0cf2cf516483ce67.pdf}
+
+\bibitem{WittenFrank2000}
+I.~Witten, E.~Frank, {Data mining}, Morgan Kaufmann, 2000.
+
+\bibitem{Solomatine2004}
+D.~Solomatine, Y.~Xue, {M5 Model Trees and Neural Networks: Application to
+  FloodForecasting in the Upper Reach of the Huai River in China}, J Hydrol Eng
+  9~(6) (2004) 491--501.
+
+\bibitem{Aha1991}
+D.~Aha, D.~Kibler, Instance-based learning algorithms, Mach Learn 6 (1991)
+  37--66.
+
+\bibitem{Mitchell1997}
+T.~Mitchell, {Machine Learning}, McGraw-Hill Companies, Inc., 1997.
+
+\bibitem{Breiman2001}
+L.~Breiman, Random forests, Mach Learn 45~(1) (2001) 5--32.
+
+\bibitem{Cohen2003}
+J.~Cohen, P.~Cohen, S.~West, L.~Aiken, {Applied multiple regression/correlation
+  analysis for the behavioral sciences}, Lawrence Erlbaum Associates, 2003.
+
+\bibitem{Yan2009}
+X.~Yan, {Linear Regression Analysis: Theory and Computing}, World Scientific,
+  2009.
+
+\bibitem{Rencher2102}
+A.~Rencher, W.~Christensen, {Multivariate regression}, Vol. 709 of Wiley Series
+  in Probability and Statistics, John Wiley and Sons, 2012.
+
+\bibitem{EnkeT05}
+D.~Enke, S.~Thawornwong, The use of data mining and neural networks for
+  forecasting stock market returns, Expert Syst Appl 29~(4) (2005) 927--940.
+
+\bibitem{McClendon2015}
+L.~McClendon, N.~Meghanathan, Using machine learning algorithms to analyze
+  crime data, Mach Learn and App 2~(1).
+
+\bibitem{Cortes1995}
+C.~Cortes, V.~Vapnik, {Support Vector Networks}, Mach Learn 20 (1995) 273--297.
+
+\bibitem{Shevade1999}
+S.~Shevade, S.~Keerthi, C.~Bhattacharyya, K.~Murthy, Improvements to the smo
+  algorithm for svm regression, IEEE T Neural Networ.
+
+\bibitem{MinSVM05}
+J.~H. Min, Y.~Lee, Bankruptcy prediction using support vector machine with
+  optimal choice of kernel function parameters, Expert Syst. Appl. 28~(4)
+  (2005) 603--614.
+
+\bibitem{Cao2003}
+L.~Cao, {Support vector machine experts for time series forcasting},
+  Neurocomputing 51 (2003) 321--339.
+
+\bibitem{Jari2008}
+C.~Jari, L.~Wen, L.~Kang, {Support vector machine classification for large data
+  set vis minmum enclosing ball clustering}, Neurocomputing 71 (2008) 611--619.
+
+\bibitem{gepsoft}
+{Gepsoft}, {Analyzing GeneXproTools Models Statistically. Statistical Analysis
+  of Time Series Prediction Models}, {\tt
+  http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} (Dec.
+  2015).
+
+\bibitem{pentaho}
+{pentaho}, {Pentaho Data Mining Community Documentation}, {\tt
+  http://wiki.pentaho.com/display/DATAMINING} (Dec. 2015).
+
+\bibitem{otexts}
+{otexts}, {Forecasting: principles and practice. The forecaster's toolbox.
+  Evaluating forecast accuracy}, {\tt https://www.otexts.org/fpp/2/5} (Dec.
+  2015).
+
+\bibitem{Hyndman2013}
+R.~Hyndman, G.~Athanasopoulos, Forecasting: principles and practice, OTexts,
+  2013.
+
+\bibitem{yu2004ec}
+X.~Yu, S.~Liong, V.~Babovic, Ec-svm approach for real-time hydrologic
+  forecasting., J Hydroinform 6 (2004) 209--223.
+
+\bibitem{chao2015construction}
+C.-F. Chao, M.-H. Horng, The construction of support vector machine classifier
+  using the firefly algorithm, Computat Intell Neurosci.
+
+\bibitem{hornik1989multilayer}
+K.~Hornik, M.~Stinchcombe, H.~White, Multilayer feedforward networks are
+  universal approximators, Neural networks 2~(5) (1989) 359--366.
+
+\bibitem{mirjalili2014let}
+S.~Mirjalili, S.~M. Mirjalili, A.~Lewis, Let a biogeography-based optimizer
+  train your multi-layer perceptron, Inform Sciences 269 (2014) 188--209.
+
+\bibitem{wdaa2008differential}
+A.~S.~I. Wdaa, Differential evolution for neural networks learning enhancement,
+  Ph.D. thesis, Universiti Teknologi Malaysia (2008).
+
+\bibitem{mirjalili2015effective}
+S.~Mirjalili, \href{http://dx.doi.org/10.1007/s10489-014-0645-7}{How effective
+  is the grey wolf optimizer in training multi-layer perceptrons}, Appl Intell
+  43~(1) (2015) 150--161.
+\newblock \href {http://dx.doi.org/10.1007/s10489-014-0645-7}
+  {\path{doi:10.1007/s10489-014-0645-7}}.
+\newline\urlprefix\url{http://dx.doi.org/10.1007/s10489-014-0645-7}
+
+\bibitem{Geisser1993}
+S.~Geisser, {Predictive Inference}, Chapman and Hall, 1993.
+
+\bibitem{Kohavi1995}
+R.~Kohavi, A study of cross-validation and bootstrap for accuracy estimation
+  and model selection, in: Proceedings of the Fourteenth International Joint
+  Conference on Artificial Intelligence, {IJCAI} 95, Montr{\'{e}}al
+  Qu{\'{e}}bec, Canada, August 20-25 1995, 2 Volumes, Morgan Kaufmann, 1995,
+  pp. 1137--1145.
+
+\bibitem{Devijver1982}
+P.~Devijver, J.~Kittler, {Pattern Recognition: A Statistical Approach},
+  Prentice-Hall, 1982.
+
+\bibitem{POS}
+M.~Gil, Puntos de venta de prensa y libros,
+  \url{https://antinomiaslibro.wordpress.com/2013/11/21/puntos-de-venta/},
+  consulted on May 21st, 2016 (November 2013).
+
+\bibitem{huang2006ga}
+C.-L. Huang, C.-J. Wang, A ga-based feature selection and parameters
+  optimization for support vector machines, Expert Syst Appl 31~(2) (2006)
+  231--240.
+
+\bibitem{Mookiah2013_EA_Tuning}
+M.~Mookiah, U.~Acharya, R.~Martis, C.~Chua, C.~Lim, E.~Ng, A.~Laude,
+  Evolutionary algorithm based classifier parameter tuning for automatic
+  diabetic retinopathy grading: A hybrid feature extraction approach, Knowl
+  Based Syst 39 (2013) 9--22.
+
+\bibitem{Shen2016_FFly_Tuning}
+L.~Shen, H.~Chen, Z.~Yu, W.~Kang, B.~Zhang, H.~Li, B.~Yang, D.~Liu, Evolving
+  support vector machines using fruit fly optimization for medical data
+  classification, Knowledge-Based Systems 96 (2016) 61--75.
+
+\end{thebibliography}
 
@@
 
-\begin{table}[!ht]
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS). Best values in bold.}
@@
 }
-\end{table}
-
-\begin{table}[!ht]
+\end{table*}
+
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo704 (SOM-FS). Best values in bold.}
@@
 
-\begin{table}[!ht]
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.}
@@
 }
-\end{table}
-
-\begin{table}[!ht]
+\end{table*}
+
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS). Best values in bold.}
@@
 
-\begin{table}[!ht]
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.}
@@
 }
-\end{table}
-
-\begin{table}[!ht]
+\end{table*}
+
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS). Best values in bold.}
@@
 
-\begin{table}[!ht]
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.}
@@
 }
-\end{table}
-
-\begin{table}[!ht]
+\end{table*}
+
+\begin{table*}[!ht]
 \caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS). Best values in bold.}

### 2016-08-12 paper.tex
Waiting at the airport
And revising introduction as instructed by #45. Maybe @pacastillo or @fergunet could have a look. I have the impression that it is excessively iterative and that it does not follow a clear line of reasoning, not to mention that it does not hightlight our actual contribution. I will continue with this anyway.

@@
 Publishing a book, in the same way as releasing any other cultural product with a physical substrate, implies several types of risks and costs due to
-the complexity, and derived expenses, of the production,
-distribution, and storage processes; most of these costs are associated
-with the number of books actually printed. But the problem is further
-complicated for completely new products, in the sense that there is an unknown
-author or a new topic with no track record. Sales forecasts can
-only be based on the knowledge obtained from other similar products,
+the complexity, and derived expenses, of its processes of production,
+distribution, and storage. Most of these costs are associated
+with the number of books actually printed, the so called {\em print run}. But the problem is further
+complicated for completely new products, in the sense that they have been written by an unknown
+author or deal with a new topic with no track record. In order to make
+the print run as close as possible to actual sales, it is essential to
+have an estimation of those sales; that is the challenge we are taking
+in this paper.
+
+In general, forecasting the sales of cultural products can
+only be based on the knowledge obtained from sales of other, similar, ones,
 but the definition of ``similar'' itself is fuzzy and, sometimes,
-subjective. Even if the author or the topic is known, doing accurate
-estimations of future sales of the new product is quite difficult, and extremely important, so that production runs heed predicted sales. 
-Indeed, several studies have demonstrated that improving sales predictions 
-(a reduction of forecasting errors) results in an enhancement in the 
-production process \cite{Fildes2010,Saeed2008}.
-
-This problem is specially acute for book publishers, who, among other
-content providers, release new {\em products} more frequently than
+subjective. Even if the author or the topic is known, making accurate
+estimations of future sales of the new product is quite difficult, and
+extremely important, so that production runs follow predicted sales.  
+Indeed, several studies have demonstrated that improving sales
+predictions, that is reducing the error in estimated sales, results in an enhancement in the 
+production process \cite{Fildes2010,Saeed2008}, so not only cost
+associated to the book itself are associated, but also the whole
+production process.
+
+Within the general area of cultural products, the problem of
+predicting sales is specially acute for book publishers, who, among other
+providers of content in physical form, release new {\em products} more frequently than
 other industries, so that they face the problem of predicting sales quite often.
@@
 whereas if the number of printed copies was not enough, a new print
-run can be made, resulting in temporary losses due to a lack of supply or in bad marketing for the customers, for instance.
+run can be made, resulting in temporary losses due to a lack of supply
+or in bad marketing for the customers, for instance.
 

### 2016-08-12 paper.tex
Continuing with #45
But there's a paragraph I don't know what to do with. Please @pacastillo take a look.

@@
 whereas if the number of printed copies was not enough, a new print
-run can be made, resulting in temporary losses due to a lack of supply
-or in bad marketing for the customers, for instance.
-
-Despite the fact that errors in one or the other direction do not have the same impact, it is extremely important to develop an accurate predictive method
-which could forecast the future sales a new book will achieve, in order to optimise production schedules, improve the publishing company profits and minimise losses \cite{Zhao2001}, being the latter the main objective of this paper.
-
-It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
+run can always be made, resulting in temporary losses due to a lack of supply
+or in bad marketing for the customers, for instance. However, in
+practice predicting lower sales than the actual ones is not such a big
+problem because when inventory is close to exhaustion new print runs
+are made; however, this new print run presents the same problem as the
+initial one of printing only as many as forecasted, although its cost
+is not as hight as the initial one and we are not so concerned with
+this issue in this paper.
+
+Despite the fact that errors in one or the other direction do not have
+the same impact, it is extremely important to develop an accurate
+predictive method 
+which could forecast the future sales a new book will achieve, in
+order to optimise production schedules, improve the publishing company
+profits and minimise losses \cite{Zhao2001}, being the latter the main
+objective of this paper.  This is the main problem we are going to
+tackle in this paper.
+
+% I don't know what to make with this paragraph. Move it to the
+% presentation of the problem, move it to the state of the art, or
+% eliminate it completely. Whoever wrote it please help - JJ
+It is important to notice that the accuracy of the predictive method
+that we intend to design is affected negatively by several factors
+related to decisions on purchases, to freight traffic, or with the
+distribution strategy \cite{Little1998}. 
 Thus, it is mandatory to know the product and the variables that

### 2016-08-13 paper.tex
Terminating the revision to the intro
Refs #45

@@
 print. These books are distributed to points of sale, but also given
-out to reviewers and literary magazines, the number of these will
-depend on how many you have printed. Books then go, in some cases, to
-the {\em novelty} table, that is, prominently displayed in the
-bookstore, shown in the window, or highlighted using props or other
-kind of advertisement. Books stay for sale for as long as the
-publisher or the store want until the bookseller decides to return it
-to the publisher or just, in some cases, move it away from shelves to
-storage. Books returned to the publisher are pulped, sold back or
-given to the author or distributed in second-hand channels such as
+out to reviewers and literary magazines; the number of these will
+depend on how many you have printed. In bookstores books  go, in some cases, to
+the {\em novelty} table, that is, they are prominently displayed, shown in the window, or highlighted using props or other 
+kind of advertisement. From these displays they then move to shelves
+or, in some cases and eventually, to storage. Books stay for sale in the store as long as the
+publisher or the store want or until the bookseller decides to return it
+to the publisher. Books returned to the publisher are pulped, sold back or
+given to the author or distributed in used-books channels such as
 book stalls or second-hand bookstores. If the print run has been fully
@@
 hand, a new print run is made and distributed to bookstores. 
-Even if the process has changed
-in the last few years since Amazon started to sell in Spain, which
+Even if the process has changed slightly 
+in the last few years since Amazon started to sell in Spain, in the
+sense that many books are sold through this new channel and do not
+undergo the cycle novelty table-shelf-storage-back to publisher, which
 actually happened {\em after} the data used for this paper was
@@
 
-Our intention in this paper is to find out the main factor influencing
-sales in order to give a tool that the publisher can use to decide how
+Our intention in this paper is to find out the main factors influencing
+sales in order to create a tool that the publisher can use to decide how
 many books should be printed, as well as how to leverage these printed
@@
 sales, and, based on it, act upon it to maximize the books sold for a
-particular print run.
+particular print run. Our main contribution is, thus, to develop a
+methodology to process book sales data in order to first find out
+relevant variables and then use these variables to process data so
+that the publisher, using them, can estimate sales and from them order
+a specific print run, instead of standard ones, which are around 300
+copies for standard books and around 5000 for those that are
+considered, in advance, {\em best sellers}.
 
@@
 %of how many units should be printed  when a new book is published 
-is faced using real data provided by the 
+is approached using real data provided by the 
 Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
-Usually, the company's expert sales managers analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions); for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
-Nevertheless, just carrying out the analysis and forecasting process as a human expert may lead to imprecise predictions, and they may not take all the variables into account. 
+Usually, the company's expert sales managers analysed historical data
+and applied their knowledge on external variables to compute correct
+estimations (predictions); for instance, they can decide increasing or
+decreasing the sales forecast based on season or sales period. 
+Nevertheless, just carrying out the analysis and forecasting process
+as a human expert may lead to imprecise predictions, and they may not
+take all the variables into account.  
 In addition, the process might be tedious, especially when the amount
@@
 
-With this issue in mind, in this paper we firstly present an analysis on the aforementioned real dataset, by means of data mining and visualisation techniques.
-Then, a feature selection process is conducted using three different methods, in order to find out what are the relevant variables describing a book in the prediction (or regression) procedure.
-After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets, also considering a different number of variables.
-The value of this methodology is contrasted considering four different publishing companies being representative as top sellers, mid-range sellers, the most varied, and one which sells a medium amount of different books.
+With this issue in mind, in this paper we firstly present an analysis
+on the aforementioned real dataset, by means of data mining and
+visualisation techniques. Then, a feature selection process is
+conducted using three different methods, in order to find out what are
+the relevant variables describing a book in the prediction (or
+regression) procedure. After this, a forecasting stage is performed
+applying a set of regression algorithms to the different datasets,
+also considering a different number of variables. 
+The value of this methodology is contrasted considering four different
+publishing companies being representative as top sellers, mid-range
+sellers, the most varied, and one which sells a medium amount of
+different books. From this, we draw insight on what are the important
+factors when selling a book and some rule of thumbs extracted from the
+prediction methods.
 

### 2016-08-13 Response to reviewers.tex
Added response to reviewers
If everyone is OK with it, this closes #45

Please @unintendedbear and @fergunet and whoever else is not in deep holiday mode check English and grammar and everything, and reopen the issue if something is wrong

@@
 
+\begin{verbatim}
+We have rewritten the introduction and introduced this new text:
+
+Our main contribution is, thus, to develop a
+methodology to process book sales data in order to first find out
+relevant variables and then use these variables to process data so
+that the publisher, using them, can estimate sales and from them order
+a specific print run, instead of standard ones, which are around 300
+copies for standard books and around 5000 for those that are
+considered, in advance, {\em best sellers}.
+
+Also, in the next-to-last paragraph, we have laid out our methodology and the main contributions of this paper.
+
+\end{verbatim}
+
 \noindent (3) Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part.\\

### 2016-08-18 Response to reviewers.tex
extending some responses

@@
 
-First, we would like to express our gratitude to you, the editorial team, and the reviewers whose valuable comments on this paper have significantly improved its quality.
-We have addressed all the comments in the new version of the paper and will list all the changes item-by-item in response to the mentioned comments below.
+First, we would like to express our gratitude to the Editor in Chief, the editorial team, and the reviewers whose valuable comments on this paper have significantly improved its quality.
+All suggestions are highly appreciated and we have added a line in the acknowledgements section thanking the reviewers.
 \\
+
+In this new revision, we carefully have addressed all the comments in the new version of the paper. We will enumerate below these comments (in italics) and our correspondent answer to each of them. \\
+
+We will look forward to hearing from you about the final decision on our paper. \\
 
@@
 
+%------------------------------------------------------------------------------------
 \section{Comments by Reviewer \#1}
@@
 
+%------------------------------------------------------------------------------------
 \section{Comments by Reviewer \#2}
@@
 \noindent (1) The ANN and ELM (extreme learning machine) should be added into the experiments;\\
+
+\begin{verbatim}
+Our response here
+\end{verbatim}
 
@@
 
-Also, in the next-to-last paragraph, we have laid out our methodology and the main contributions of this paper.
+Also, in the next-to-last paragraph, we have laid out our methodology 
+and the main contributions of this paper.
 
@@
 
+\begin{verbatim}
+Our response here
+\end{verbatim}
+
 \noindent (4) Some tables should be transfer to figures because there are too many figures.\\
 
-\noindent (5) Graphical abstract should be added.
-This paper is organized well. The authors should revise their work according to above comments.\\
+\begin{verbatim}
+Our response here
+\end{verbatim}
 
+\noindent (5) Graphical abstract should be added. This paper is organized well. The authors should revise their work according to above comments.\\
+
+\begin{verbatim}
+Our response here
+\end{verbatim}
+
+%------------------------------------------------------------------------------------
 \section{Comments by Reviewer \#3}
@@
 
+\begin{verbatim}
+We have rewritten the introduction and introduced this new text:
+
+Our main contribution is, thus, to develop a
+methodology to process book sales data in order to first find out
+relevant variables and then use these variables to process data so
+that the publisher, using them, can estimate sales and from them order
+a specific print run, instead of standard ones, which are around 300
+copies for standard books and around 5000 for those that are
+considered, in advance, {\em best sellers}.
+
+Also, in the next-to-last paragraph, we have laid out our methodology 
+and the main contributions of this paper.
+
+\end{verbatim}
+
 \noindent (2) In sections 4.1 and 4.2 should be moved to section 2.\\
+
+\begin{verbatim}
+Our response here
+\end{verbatim}
 
@@
 
+\begin{verbatim}
+Our response here
+\end{verbatim}
+
 \noindent (4) In Section 5, parameter settings of M5P, kNN and RF also should be shown.
 
+\begin{verbatim}
+Our response here
+\end{verbatim}
+
 \end{document}

### 2016-08-19 Response to reviewers.tex
extending some responses

@@
 
-\noindent There are some issues needed to be aaddressed further: \\
+\noindent \emph{There are some issues needed to be addressed further:} \\
 
-\noindent (1) Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one).
+\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one).
 Both CFS and RelieFF are originally designed for classification problem.
 When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales).
-Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF ?
-\\
+Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF?
+}
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
 
-\noindent (2) In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM.
+~\\
+\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM.
 In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ?
-For RF, how many trees are set ?\\
+For RF, how many trees are set?
+}
 
 \begin{verbatim}
-Our response here
+In sub-section 5.1 the MLP was described as our initial intention was 
+to include it in this study. Thus, as suggested by the reviewer (see 
+next comment), obtained results with this method have been included
+in the new version of this paper.
+
+As far as the number of trees is related, TODO.
 \end{verbatim}
 
-\noindent (3) As we known, tree-based mehods (e.g.,M5P and RF) themselve embed feature selection procedure.
+~\\
+\noindent (3) \emph{As we known, tree-based mehods (e.g.,M5P and RF) themselve embed feature selection procedure.
 That is, some features are choosen to build trees.
 It is not fair enough to compare five methods in Table 3.
-\\
+}
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
 
-\noindent (4) It seems more reasonable to organize and write that paper according to regression viewpoint only.\\
+~\\
+\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
 
-\noindent (5) It is necessary to write that paper more concisely.\\
+~\\
+\noindent (5) \emph{It is necessary to write that paper more concisely. }
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
@@
 
-\noindent This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors:\\
+\noindent \emph{This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors: } \\
 
-\noindent (1) The ANN and ELM (extreme learning machine) should be added into the experiments;\\
+\noindent (1) \emph{The ANN and ELM (extreme learning machine) should be added into the experiments; }
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
 
-\noindent (2) The authors should clarify their main contributions in the introduction parts.\\
+~\\
+\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts. }
 
@@
 and the main contributions of this paper.
-
 \end{verbatim}
 
-\noindent (3) Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part.\\
+~\\
+\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
 
-\noindent (4) Some tables should be transfer to figures because there are too many figures.\\
+~\\
+\noindent (4) \emph{Some tables should be transfer to figures because there are too many figures. }
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
 
-\noindent (5) Graphical abstract should be added. This paper is organized well. The authors should revise their work according to above comments.\\
+~\\
+\noindent (5) \emph{Graphical abstract should be added. This paper is organized well. The authors should revise their work according to above comments. }
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
@@
 
-\noindent There are several concerns should be considered. \\
+\noindent \emph{There are several concerns should be considered. } \\
 
-\noindent (1) In section introduction, this manuscript should describe the contribution of this work.\\
+\noindent (1) \emph{In section introduction, this manuscript should describe the contribution of this work. }
 
@@
 and the main contributions of this paper.
-
 \end{verbatim}
 
-\noindent (2) In sections 4.1 and 4.2 should be moved to section 2.\\
+~\\
+\noindent (2) \emph{sections 4.1 and 4.2 should be moved to section 2. }
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}
 
-\noindent (3) In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it.\\
+~\\
+\noindent (3) \emph{In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it. }
 
 \begin{verbatim}
-Our response here
+Taking into account the reviewer's comment, we have improved the methodology description by including a flowchart (see Figure 1 at page 6).
 \end{verbatim}
 
-\noindent (4) In Section 5, parameter settings of M5P, kNN and RF also should be shown.
+~\\
+\noindent (4) \emph{In Section 5, parameter settings of M5P, kNN and RF also should be shown. }
 
 \begin{verbatim}
-Our response here
+TODO
 \end{verbatim}

### 2016-08-19 Response to reviewers.tex
extending some responses

@@
 \begin{verbatim}
-In sub-section 5.1 the MLP was described as our initial intention was 
-to include it in this study. Thus, as suggested by the reviewer (see 
-next comment), obtained results with this method have been included
-in the new version of this paper.
+In sub-section 5.1 the MLP was described as our initial intention 
+was to include it in this study. Thus, as suggested by the second 
+reviewer (see first comment), obtained results with this method 
+have been included in the new version of this paper.
 
@@
 \begin{verbatim}
-TODO
+Following your suggestion we have reorganized some parts of the 
+text and several paragraphs have been rewritten in order to make 
+them clearer and to improve its comprehension.
+
+Finally, the paper has been completely revised and several 
+typographic errors have been fixed.
 \end{verbatim}
@@
 Our main contribution is, thus, to develop a
-methodology to process book sales data in order to first find out
-relevant variables and then use these variables to process data so
-that the publisher, using them, can estimate sales and from them order
-a specific print run, instead of standard ones, which are around 300
-copies for standard books and around 5000 for those that are
-considered, in advance, {\em best sellers}.
+methodology to process book sales data in order to first find 
+out relevant variables and then use these variables to process 
+data so that the publisher, using them, can estimate sales and 
+from them order a specific print run, instead of standard ones, 
+which are around 300 copies for standard books and around 5000 
+for those that are considered, in advance, best sellers.
 
-Also, in the next-to-last paragraph, we have laid out our methodology 
-and the main contributions of this paper.
+Also, in the next-to-last paragraph, we have laid out our 
+methodology and the main contributions of this paper.
 \end{verbatim}
@@
 methodology to process book sales data in order to first find out
-relevant variables and then use these variables to process data so
-that the publisher, using them, can estimate sales and from them order
-a specific print run, instead of standard ones, which are around 300
-copies for standard books and around 5000 for those that are
-considered, in advance, {\em best sellers}.
+relevant variables and then use these variables to process data 
+so that the publisher, using them, can estimate sales and from 
+them order a specific print run, instead of standard ones, which 
+are around 300 copies for standard books and around 5000 for those 
+that are considered, in advance, best sellers.
 
-Also, in the next-to-last paragraph, we have laid out our methodology 
-and the main contributions of this paper.
+Also, in the next-to-last paragraph, we have laid out our 
+methodology and the main contributions of this paper.
 \end{verbatim}
@@
 \begin{verbatim}
-Taking into account the reviewer's comment, we have improved the methodology description by including a flowchart (see Figure 1 at page 6).
+Taking into account the reviewer's comment, we have improved the 
+methodology description by including a flowchart (see Figure 1 at 
+page 6).
 \end{verbatim}

### 2016-08-19 Response to reviewers.tex
closing issue 43: Closes #43

@@
 ~\\
-\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts. }
+\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts.}
 
@@
 
-Our main contribution is, thus, to develop a
-methodology to process book sales data in order to first find 
-out relevant variables and then use these variables to process 
-data so that the publisher, using them, can estimate sales and 
-from them order a specific print run, instead of standard ones, 
-which are around 300 copies for standard books and around 5000 
-for those that are considered, in advance, best sellers.
+Our main contribution is, thus, to develop a methodology to 
+process book sales data in order to first find out relevant 
+variables and then use these variables to process data so that 
+the publisher, using them, can estimate sales and from them order 
+a specific print run, instead of standard ones, which are around 
+300 copies for standard books and around 5000 for those that are 
+considered, in advance, best sellers.
 
@@
 
-\noindent \emph{There are several concerns should be considered. } \\
+\noindent \emph{There are several concerns should be considered.}\\
 
@@
 \begin{verbatim}
-TODO
+Following your suggestion we have reorganized these sub-sections, 
+moving them to the section 2.
 \end{verbatim}

### 2016-08-19 Response to reviewers.tex
including some responses

@@
 \begin{verbatim}
-TODO
+THIS HAS TO BE DONE.
 \end{verbatim}
@@
 \begin{verbatim}
-TODO
+THIS HAS TO BE DONE.
+
+Taking into account the reviewer's comment, we have designed 
+a graphical abstract as a visual summary of the main findings 
+of the article.
+
+We would like to thank this reviewer for his suggestions and 
+advice about our paper.
 \end{verbatim}
@@
 
-Our main contribution is, thus, to develop a
-methodology to process book sales data in order to first find out
-relevant variables and then use these variables to process data 
-so that the publisher, using them, can estimate sales and from 
-them order a specific print run, instead of standard ones, which 
-are around 300 copies for standard books and around 5000 for those 
-that are considered, in advance, best sellers.
+Our main contribution is, thus, to develop a methodology to 
+process book sales data in order to first find out relevant 
+variables and then use these variables to process data so that 
+the publisher, using them, can estimate sales and from them order 
+a specific print run, instead of standard ones, which are around 
+300 copies for standard books and around 5000 for those that are 
+considered, in advance, best sellers.
 
@@
 \begin{verbatim}
-TODO
+THIS HAS TO BE DONE.
+
+Taking into account the reviewer's comment, we have improved the 
+section 5, including the parameter settings of M5P, kNN and RF 
+methods.
 \end{verbatim}

### 2016-08-20 paper.tex
Added MLP results to all tables
Added methodology diagram for issue #48. Please @pacastillo or @amorag check if it is correct or if I should modify anything
moving sub-sections 4.1 and 4.2 to the Section 2 (comment 2 by Rev.3): Closes #47

@@
 on decision rules have been tested as an alternative.
+
+% following two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)
+
+%-------------------------------------------------
+\subsection{Selecting an appropriate forecasting method}
+\label{subsec:select_method}
+
+As previously stated, there are many prediction methods available in the 
+literature, each one with a different parameter set that may affect the 
+obtained results.
+
+However, as in the case of new books only some descriptive data are available,
+compared to those cases in which historical data on sales of published books 
+is available, not all forecasting methods can be used in this specific problem.
+
+Thus, in this research five forecasting methods, based on the State of the Art 
+literature review (see above, Section \ref{sec:soa}) 
+\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, 
+have been used. 
+Well known forecasting methods implemented in the Weka tool have been chosen, 
+as these methods are widely known, and could be very helpful for practitioners 
+to reproduce experiments and even to solve similar sales prediction problems 
+using these methods.
+
+Specifically, the following forecasting methods are proposed:
+
+\begin{itemize}
+
+ % weka.classifiers.trees.M5P
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
+ \item \emph{M5 Model trees (M5P)}: 
+A decision tree consists of answer-nodes, that indicate a class, and decision-nodes, 
+that contain an attribute name and branches to other sub-decision trees.
+Building a decision tree can be done using many algorithms, i.e. ID3 and C4.5 \cite{Quinlan1986}.
+However, in order to use this model in regression problems, some authors have 
+extended the model using methods such as the M5 model tree \cite{Quinlan1986,Quinlan1992,Wang1997,WittenFrank2000}, 
+by combining a conventional decision tree and generating linear regression 
+functions at the nodes.
+
+The construction of a model tree is similar to that of classical decision 
+trees \cite{Solomatine2004}:
+The process breaks the input space of the training data through decision points 
+(nodes) to assign a linear model suitable for that sub-area of the input space. 
+This process may lead to a complex model tree.
+
+Model tree models can learn and tackle tasks with high dimensionality, even up to 
+hundreds of attributes, and generate reproducible and comprehensible representations, 
+what makes them potentially more successful in the eyes of decision makers.
+
+The final model consists of the collection of linear sub-models that brings the 
+required non-linearity in dealing with the regression problem
+and both the predicted values at the answer-nodes along with the path from the 
+root to that node is given as a result.
+
+ % weka.classifiers.lazy.IBk 
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
+ \item \emph{k-Nearest Neighbours (kNN)}: 
+The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
+which the unknown instances are classified by relating them to the known 
+instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
+
+The main idea behind the algorithm is that two instances far enough in the space, 
+taking into account the distance function, are less likely to belong to the 
+same class than two closely situated instances.
+
+The classification algorithm locates the nearest neighbour in instance space and 
+assigns the class of that neighbour to the unknown instance.
+In order to improve the robustness of the model, several neighbours can be 
+located, assigning the resulting class to an unclassified vector using the 
+closest $k$ vectors found in the training set by majority vote.
+
+ \item \emph{Random Forest (RF)}: This method is based on the
+   construction of a set of decision trees using a stochastic process
+   over the basis of C4.5 algorithm. It was proposed by Breiman
+   \cite{Breiman2001} and aims to create independent and uncorrelated
+   trees based on different and random input vectors, following the
+   same distribution. 
+The result is the average of the generated trees during the process.
+
+ % weka.classifiers.functions.LinearRegression
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
+ \item \emph{Linear Regression (LR)}:
+ Linear Regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
+relationship between a scalar dependent variable (outcome) and several independent 
+variables (predictors) over the range of values in the dataset. 
+In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.
+
+This method of regression provides an adequate and interpretable description of 
+how the input affects the output as it models the dependent variable as a linear 
+function of the independent variables. Moreover, the linear relation can be 
+solved using the least squares method, that minimises the error between the 
+current data and the regression line \cite{McClendon2015}.
+
+ % weka.classifiers.functions.SMOreg
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
+ \item \emph{Support Vector Machine for Regression (SVM)}:
+Support vector machine (SVM) \cite{Cortes1995,Shevade1999,MinSVM05} method is based on  
+statistical learning theory and has successfully used in classification and  
+regression problems \cite{Cao2003,Jari2008}.
+
+In classification problems the algorithm searches for an optimal hyperplane 
+that separates two classes, maximising the margin between them. 
+In the case of regression the algorithm chooses a hyperplane close to as many 
+of the data points as possible, minimising the sum of the distances from 
+the data points to the hyperplane. 
+In both cases, the hyperplane is defined by a subset of training set samples, 
+called support vectors.
+%This method works well even if the space is highly dimensional and the problem is not linearly separable.
+
+ % weka.classifiers.functions.MultilayerPerceptron
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
+ \item \emph{Multilayer Perceptron}:
+A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
+artificial neural network model that maps the input data onto an appropriate output. 
+It is an artificial neural network generally used for classification or 
+approximation problems.
+
+This model is a generalisation of the standard linear perceptron that uses several 
+layers of nodes (called neurons) and that is able to solve linearly inseparable 
+problems \cite{SteinwenderBitzer2003}.
+Each neuron consists of a linear combination of weighted inputs which is passed 
+though a non-linear activation function to produce its output.
+
+This kind of artificial neural network is trained using a supervised learning 
+technique called back-propagation.
+This training method was developed independently by Werbos \cite{Werbos1974}, 
+Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
+in updating the weights of the output layer neurons once the erroneous output 
+has been obtained, and then, propagating the successive weight layers back to 
+the input layer.
+
+A key issue when designing an MLP is the number of hidden layers of neurons.
+Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
+create classifying regions of any kind. This result was then confirmed in later 
+works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
+
+\end{itemize}
+
+The objective is finding the most appropriate forecasting method that minimises 
+the error between the obtained forecast and the current sales for each new book 
+published.
+
+%-------------------------------------------------
+\subsection{Models evaluation}
+\label{subsec:models_evaluation}
+
+At this step, the developed forecasting models are evaluated and assessed based on different evaluation criteria.
+In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
+Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
+
+\begin{itemize}
+  \item \emph{Mean Absolute Error} (MAE):
+        \begin{equation}\label{eq:MAE}
+            MAE = \frac{1}{n}\sum_{i=1}^n {\mid p_i - o_i\mid}
+        \end{equation}
+
+  \item \emph{Root Mean Squared Error} (RMSE):
+        \begin{equation}\label{eq:RMSE}
+            RMSE = \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 }
+        \end{equation}
+
+  \item \emph{Relative absolute error} (RAE):
+        \begin{equation}\label{eq:RAE}
+            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid \bar{o} - o_i\mid} }
+        \end{equation}
+
+  \item \emph{Root relative squared error} (RRSE):
+        \begin{equation}\label{eq:RRSE}
+            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
+        \end{equation}
+\end{itemize}
+where $o_i$ is the current value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
+
+% previous two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)
 
@@
 However, the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}.
+Figure \ref{fig:methodology} summarizes these followed steps.
+
+\begin{figure}[!ht] 
+\begin{center}
+  \epsfig{file=metodologia.eps,width=4cm}
+\caption{Steps followed in the proposed methodology.}
+\label{fig:methodology}
+\end{center}
+\end{figure}
+
 %These are described in the following sections.
@@
 These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
-This task may also help to identify leading indicators to be considered by a human expert to make predictions.
+This task may also help to identify leading indicators to be considered 
+by a human expert to make predictions.
 % You have to present the problem and not the solution. It's not "what
@@
 % Antonio - done
-In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
-methods.  
+In this stage, both numerical and visualisation-based approaches have been 
+applied, in order to select the best variables for the forecasting methods.  
 % Antonio - Should we speak about 'forecasting' or 'regression', Sam? Coudl they be used with the same meaning?
 
-Next, Section \ref{subsec:select_method} reports a selection of the best forecasting techniques that have been conducted, looking for those rule- or tree-based, together with numerical methods which could yield the best results.
+In Section \ref{subsec:select_method}, a selection of the best forecasting techniques that have been conducted has been reported, looking for those rule- or tree-based, together with numerical methods which could yield the best results.
 
@@
 %-------------------------------------------------
-%\subsection{Data collection}
-%\label{subsec:data_collection}
-
-%-------------------------------------------------
 \subsection{Data preprocessing by feature selection}
@@
 
-At this stage, a Feature Selection (FS) process has been carried out, since it is an effective dimensionality reduction technique and an essential preprocessing method to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.
-
-The aim of these algorithms is exploring the space of attributes to find out which subset of them yields the best results in a classification or prediction problem.
-To this end, the features describing every pattern are analysed.
-In this case, among the variables describing a new book, some may affect predictions as they provide information, while others may not be necessary and even redundant.
+At this stage, a Feature Selection (FS) process has been carried out, 
+since it is an effective dimensionality reduction technique and an essential 
+preprocessing method to discard less relevant or non-useful features 
+\cite{Krishnapuram2004,Chen2011_FS_PTS}.
+
+The aim of these algorithms is exploring the space of attributes to find out 
+which subset of them yields the best results in a classification or prediction 
+problem. To this end, the features describing every pattern are analysed. 
+In this case, among the variables describing a new book, some may affect 
+predictions as they provide information, while others may not be necessary 
+and even redundant.
 
@@
 %Therefore, it could be used for different tasks such as feature selection and data clustering and visualisation. %Pablo: some cite here?
-This method is normally used as a data visualization tool, since it allows to project any multi-variated dataset in a two-dimensional display, so an expert can detect topological relations among its neurons and thus make inferences or find interesting relationships on the input dataset (such as clusters, for instance).
+This method is normally used as a data visualization tool, since it allows 
+to project any multi-variated dataset in a two-dimensional display, 
+so an expert can detect topological relations among its neurons and thus 
+make inferences or find interesting relationships on the input dataset 
+(such as clusters, for instance).
 
@@
 neuron which has the shortest distance with the presented input vector
-is updated along with the neurons in its neighbourhood. This neuron is called the best matching unit (BMU). The goal of the learning process is to
-minimise the neighbourhood distance in the output clusters.
-
-Once the SOM learning process is finished, a visual representation technique, named the Unified distance matrix (U-matrix) \cite{UmatUlts}, has been applied.
-This method uses the obtained codevectors (vectors of variables of the problem) as data source, and generates a matrix where each component is a distance measure between two adjacent neurons.
-In the U-matrix, the distance between adjacent neurons is measured and assigned different colours.
-Different colours between neurons indicate large distances (boundaries) while similar colours represent close areas (clusters).
+is updated along with the neurons in its neighbourhood. 
+This neuron is called the best matching unit (BMU). 
+The goal of the learning process is to minimise the neighbourhood distance 
+in the output clusters.
+
+Once the SOM learning process is finished, a visual representation technique, 
+named the Unified distance matrix (U-matrix) \cite{UmatUlts}, has been applied. 
+This method uses the obtained codevectors (vectors of variables of the problem) 
+as data source, and generates a matrix where each component is a distance 
+measure between two adjacent neurons. In the U-matrix, the distance between 
+adjacent neurons is measured and assigned different colours. Different colours 
+between neurons indicate large distances (boundaries) while similar colours 
+represent close areas (clusters).
 
@@
 regions, or clusters, with high training sample concentration and fewer
-where the samples are scarce.
-U-Matrix graph, together with the projection of variables into separate planes, the so-called component planes analysis (that SOM yields), will aid an expert to identify the most relevant features on every cluster, i.e.
-those with a higher influence on the creation of that cluster.
-%FERGU: mencionarlo en la intro
-% Which is interesting because... JJ
-% Antonio - explained. ;)
-
-Finally, Section \ref{sec:experiments} provides a comparison between the feature reduction through SOM, and the feature selection techniques that have been described.
-
-%-------------------------------------------------
-\subsection{Selecting an appropriate forecasting method}
-\label{subsec:select_method}
-
-As previously stated, there are many prediction methods available in the 
-literature, each one with a different parameter set that may affect the 
-obtained results.
-
-However, as in the case of new books only some descriptive data are available,
-compared to those cases in which historical data on sales of published books 
-is available, not all forecasting methods can be used in this specific problem.
-
-Thus, in this research five forecasting methods, based on the State of the Art literature 
-review (see Section \ref{sec:soa}) 
-\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
-Well known forecasting methods implemented in the Weka tool have been chosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using
-these methods. % Why these and not others? Exploratory data analysis?
-               % - JJ
-
-Specifically, the following forecasting methods are proposed: 
-        % Proposed why? - JJ
-        % because those methods were those that could lead with the problem data - pedro
-\begin{itemize}
-
- % weka.classifiers.trees.M5P
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
- \item \emph{M5 Model trees (M5P)}: 
-A decision tree consists of answer-nodes, that indicate a class, and decision-nodes, 
-that contain an attribute name and branches to other sub-decision trees.
-Building a decision tree can be done using many algorithms, i.e. ID3 and C4.5 \cite{Quinlan1986}.
-However, in order to use this model in regression problems, some authors have 
-extended the model using methods such as the M5 model tree \cite{Quinlan1986,Quinlan1992,Wang1997,WittenFrank2000}, 
-by combining a conventional decision tree and generating linear regression 
-functions at the nodes.
-
-The construction of a model tree is similar to that of classical decision 
-trees \cite{Solomatine2004}:
-The process breaks the input space of the training data through decision points 
-(nodes) to assign a linear model suitable for that sub-area of the input space. 
-This process may lead to a complex model tree.
-
-Model tree models can learn and tackle tasks with high dimensionality, even up to 
-hundreds of attributes, and generate reproducible and comprehensible representations, 
-what makes them potentially more successful in the eyes of decision makers.
-
-The final model consists of the collection of linear sub-models that brings the 
-required non-linearity in dealing with the regression problem
-and both the predicted values at the answer-nodes along with the path from the 
-root to that node is given as a result.
-
- % weka.classifiers.lazy.IBk 
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
- \item \emph{k-Nearest Neighbours (kNN)}: 
-The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
-which the unknown instances are classified by relating them to the known 
-instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
-
-The main idea behind the algorithm is that two instances far enough in the space, 
-taking into account the distance function, are less likely to belong to the 
-same class than two closely situated instances.
-
-The classification algorithm locates the nearest neighbour in instance space and 
-assigns the class of that neighbour to the unknown instance.
-In order to improve the robustness of the model, several neighbours can be 
-located, assigning the resulting class to an unclassified vector using the 
-closest $k$ vectors found in the training set by majority vote.
-
- \item \emph{Random Forest (RF)}: This method is based on the
-   construction of a set of decision trees using a stochastic process
-   over the basis of C4.5 algorithm. It was proposed by Breiman
-   \cite{Breiman2001} and aims to create independent and uncorrelated
-   trees based on different and random input vectors, following the
-   same distribution. 
-The result is the average of the generated trees during the process.
-
- % weka.classifiers.functions.LinearRegression
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
- \item \emph{Linear Regression (LR)}:
- Linear Regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
-relationship between a scalar dependent variable (outcome) and several independent 
-variables (predictors) over the range of values in the dataset. 
-In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.
-
-This method of regression provides an adequate and interpretable description of 
-how the input affects the output as it models the dependent variable as a linear 
-function of the independent variables. Moreover, the linear relation can be 
-solved using the least squares method, that minimises the error between the 
-current data and the regression line \cite{McClendon2015}.
-
- % weka.classifiers.functions.SMOreg
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
- \item \emph{Support Vector Machine for Regression (SVM)}:
-Support vector machine (SVM) \cite{Cortes1995,Shevade1999,MinSVM05} method is based on  
-statistical learning theory and has successfully used in classification and  
-regression problems \cite{Cao2003,Jari2008}.
-
-In classification problems the algorithm searches for an optimal hyperplane 
-that separates two classes, maximising the margin between them. 
-In the case of regression the algorithm chooses a hyperplane close to as many 
-of the data points as possible, minimising the sum of the distances from 
-the data points to the hyperplane. 
-In both cases, the hyperplane is defined by a subset of training set samples, 
-called support vectors.
-%This method works well even if the space is highly dimensional and the problem is not linearly separable.
-
-\end{itemize}
-
-The objective is finding the most appropriate forecasting method that minimises 
-the error between the obtained forecast and the current sales for each new book 
-published.
-
-\subsection{Models evaluation}
-
-At this step, the developed forecasting models are evaluated and assessed based on different evaluation criteria.
-In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
-Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
-
-\begin{itemize}
-  \item \emph{Mean Absolute Error} (MAE):
-        \begin{equation}\label{eq:MAE}
-            MAE = \frac{1}{n}\sum_{i=1}^n {\mid p_i - o_i\mid}
-        \end{equation}
-
-  \item \emph{Root Mean Squared Error} (RMSE):
-        \begin{equation}\label{eq:RMSE}
-            RMSE = \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 }
-        \end{equation}
-
-  \item \emph{Relative absolute error} (RAE):
-        \begin{equation}\label{eq:RAE}
-            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid \bar{o} - o_i\mid} }
-        \end{equation}
-
-  \item \emph{Root relative squared error} (RRSE):
-        \begin{equation}\label{eq:RRSE}
-            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
-        \end{equation}
-\end{itemize}
-where $o_i$ is the current value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
+where the samples are scarce. U-Matrix graph, together with the projection 
+of variables into separate planes, the so-called component planes analysis 
+(that SOM yields), will aid an expert to identify the most relevant features 
+on every cluster, i.e. those with a higher influence on the creation of that 
+cluster.
+
+Finally, Section \ref{sec:experiments} provides a comparison between 
+the feature reduction through SOM, and the feature selection techniques 
+that have been described.
 
@@
 \label{sec:experiments}
-
-% An intro should go here - JJ
-% Antonio - done
 
@@
 SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
+\hline 
+MLP	& 88.01 $\pm$ 0.11	& 350.99 $\pm$ 185.53	& 730.93 $\pm$ 374.84	& 61.64 $\pm$ 33.61	& 56.33 $\pm$ 31.6	& 7014.06 $\pm$ 110.095 \tabularnewline
 \hline 
@@
 \hline  
+MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
+\hline
+
 \end{tabular}
@@
 SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
+\hline
+MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
 \hline
@@
 SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
+\hline 
+MLP	& 84.3 $\pm$ 0.12	& 388.79 $\pm$ 274.18	& 851.01 $\pm$ 422.03	& 68.26 $\pm$ 49.64	& 65.85 $\pm$ 36.49	& 3.29 $\pm$ 0.042\tabularnewline
 \hline
@@
 \hline 
+MLP	& 84.42 $\pm$ 0.12	& 1105.61 $\pm$ 445.66	& 1776.68 $\pm$ 1148.31	& 66.52 $\pm$ 23.63	& 70.41 $\pm$ 41.88	& 1.65 $\pm$ 0.008 \tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 80.83 $\pm$ 0.12	& 122.8 $\pm$ 56.86	& 207.12 $\pm$ 100.44	& 67.13 $\pm$ 31.38	& 78.14 $\pm$ 39.92	& 2.83 $\pm$ 0.012\tabularnewline
+\hline
 \end{tabular}
@@
 SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 0.7649 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
 \hline
@@
 \hline 
+MLP	& 87.66 $\pm$ 0.14	& 897.02 $\pm$ 411.58	& 1332.54 $\pm$ 969.05	& 56.43 $\pm$ 33.1	& 58.52 $\pm$ 57.68	& 0.17 $\pm$ 0.002\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 79.26 $\pm$ 0.27	& 20.28 $\pm$ 13.25	& 35.05 $\pm$ 29.44	& 61.89 $\pm$ 37.64	& 81.51 $\pm$ 63.39	& 0.07 $\pm$ 0.002\tabularnewline
+\hline 
 \end{tabular}
@@
 \hline 
+MLP	& 84.11 $\pm$ 0.13	& 104.55 $\pm$ 50.32	& 180.42 $\pm$ 87.44	& 56.99 $\pm$ 26.01	& 67.68 $\pm$ 32.15	& 0.22 $\pm$ 0.003\tabularnewline
+\hline
 \end{tabular}
@@
 SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 77.3 $\pm$ 0.13	& 709.2 $\pm$ 235.87	& 960.43 $\pm$ 345.28	& 73.11 $\pm$ 24.95	& 75.19 $\pm$ 25.74	& 0.14 $\pm$ 0.003\tabularnewline
 \hline
@@
 \bibliographystyle{elsarticle-num}
-%\bibliography{refs}
-\begin{thebibliography}{10}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\expandafter\ifx\csname href\endcsname\relax
-  \def\href#1#2{#2} \def\path#1{#1}\fi
-
-\bibitem{Fildes2010}
-R.~Fildes, B.~Kingsman, {Incorporating demand uncertainty and forecast error in
-  supply chain planning models}, J Oper Res Soc 62 (2010) 483--500.
-
-\bibitem{Saeed2008}
-K.~Saeed, {Trend forecasting for stability in supply chains}, J Bus Res 61
-  (2008) 1113--1124.
-
-\bibitem{Zhao2001}
-X.~Zhao, J.~Xie, R.~Lau, {Improving the supply chain performance: use of
-  forecasting models versus early order commitments}, Int J Prod Res 39~(17)
-  (2001) 3923--3939.
-
-\bibitem{Little1998}
-J.~Little, {Integrated measures of sales, merchandising and distribution}, Int
-  J Res Mark 15 (1998) 473--485.
-
-\bibitem{Armstrong2001}
-J.~Armstrong, {Principles of forecasting. A handbook for researchers and
-  practitioners}, Kluwer, Norwell, 2001.
-
-\bibitem{SThomassey2014}
-S.~Thomassey, {Sales Forecasting in Apparel and Fashion Industry: A Review},
-  Intell Fashion Forecasting Syst: Models and App (2014) 2--27.
-
-\bibitem{DeToni2000}
-A.~D. Toni, A.~Meneghetti, {The production planning process for a network of
-  firms in the textile-apparel industry}, Int J Prod Econ 65 (2000) 17--32.
-
-\bibitem{kohonen1998}
-T.~Kohonen, {The self-organizing map}, Neurocomputing 21~(1-3) (1998) 1--6.
-
-\bibitem{Chang2009}
-P.~Chang, C.~Liu, C.~Fan, {Data clustering and fuzzy neural network for sales
-  forecasting: A case study in printed circuit board industry}, Knowl Based
-  Syst (2009) 344--355.
-
-\bibitem{Sanders1994}
-N.~Sanders, K.~Manrodt, {Forecasting practices in US corporations: Survey
-  results}, Interfaces 24~(2) (1994) 92--100.
-
-\bibitem{Papalexopoulos1990}
-A.~Papalexopoulos, T.~Hesterberg, {A regression-based approach to short-term
-  system load forecasting}, IEEE Trans Power Syst 5 (1990) 1535--1547.
-
-\bibitem{Yoo1999}
-H.~Yoo, R.~Pimmel, {Short-term load forecasting using a self-supervised
-  adaptive neural network}, IEEE Trans Power Syst 14~(2) (1999) 779--784.
-
-\bibitem{Mastorocostas2001}
-P.~Mastorocostas, J.~Theocharis, V.~Petridis, {A constrained orthogonal
-  least-squares method for generating TSK fuzzy models: application to
-  short-term load forecasting}, Fuzzy Set Syst 118 (2001) 215--233.
-
-\bibitem{Chu2003}
-C.~Chu, P.~Zhang, {A comparative study of linear and nonlinear models for
-  aggregate retail sales forecasting}, Int J Prod Econ 86 (2003) 217--231.
-
-\bibitem{Brown1959}
-R.~Brown, {Smoothing forecasting and prediction of discrete time series},
-  Prentice Hall, Englewood Cliffs, 1959.
-
-\bibitem{Winters1960}
-P.~Winters, {Forecasting sales by exponential weighed moving averages}, Manag
-  Sci 6 (1960) 324--342.
-
-\bibitem{Box1969}
-G.~Box, G.~Jenkins, {Time series analysis forecasting and control}, Prentice
-  Hall, Englewood Cliffs, 1969.
-
-\bibitem{KayacanUK10}
-E.~Kayacan, B.~Ulutas, O.~Kaynak, Grey system theory-based models in time
-  series prediction, Expert Syst Appl 37~(2) (2010) 1784--1789.
-
-\bibitem{ChingChin2010}
-C.~Ching-Chin, A.~I.~K. Ieng, W.~Ling-Ling, K.~Ling-Chieh, {Designing a
-  decision-support system for new product sales forecasting}, Expert Syst Appl
-  37~(2) (2010) 1654--1665.
-
-\bibitem{FaderHardie2005}
-S.~Fader, B.~Hardie, {The value of simple models in new product forecasting and
-  customer-base analysis}, Appl Stoch Model Bus (2005) 461--473.
-
-\bibitem{Madsen2008}
-H.~Madsen, {Time series analysis}, Chapman and Hall. CRC Co., 2008.
-
-\bibitem{Lapide1999}
-L.~Lapide, {New developments in business forecasting}, J Bus Forecasting (1999)
-  29--30.
-
-\bibitem{ChernWSF15}
-C.-C. Chern, C.-P. Wei, F.-Y. Shen, Y.-N. Fan, A sales forecasting model for
-  consumer products based on the influence of online word-of-mouth., Inf Syst E
-  Bus Manag 13 (2015) 445--473.
-
-\bibitem{Moon2010ICSSSM}
-G.~Moon, G.~Kikuta, T.~Yamada, A.~Yoshikawa, T.~Terano, {Blog information
-  considered useful for book sales prediction}, in: 7th International
-  Conference on Service Systems and Service Management (ICSSSM), IEEE. Tokyo,
-  2010, pp. 1--5.
-
-\bibitem{Moon2010ICEC}
-G.~Moon, G.~Kikuta, T.~Yamada, A.~Yoshikawa, T.~Terano, Categorization of sales
-  patterns to use blog information as book sales prediction, in: Proceedings of
-  the 12th International Conference on Electronic Commerce: Roadmap for the
-  Future of Electronic Business, ICEC '10, ACM, New York, NY, USA, 2010, pp.
-  1--7.
-
-\bibitem{Hammond1990}
-J.~Hammond, {Quick response in apparel industries}, Havard Business school,
-  Cambridge, 1990.
-
-\bibitem{Xia2012}
-M.~Xia, Y.~Zhang, L.~W.~S. Ye, {Fashion retailing forecasting based on extreme
-  learning machine with adaptive metrics of inputs}, Knowl Based Syst 36 (2012)
-  253--259.
-
-\bibitem{Thomassey2012}
-S.~Thomassey, {Sales forecasts in clothing industry. The key success factor of
-  the supply chain management}, Int J Prod Econ 128 (2012) 470--483.
-
-\bibitem{wiki:dewey}
-Wikipedia,
-  \href{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}{List
-  of dewey decimal classes}, [Online; accessed 05-May-2016].
-\newline\urlprefix\url{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}
-
-\bibitem{fayyad1996data}
-U.~Fayyad, G.~Piatetsky-Shapiro, P.~Smyth, From data mining to knowledge
-  discovery in databases, AI magazine 17~(3) (1996) 37.
-
-\bibitem{kittler1986feature}
-J.~Kittler, Handbook of pattern recognition and image processing, Academic
-  press, 1986.
-
-\bibitem{Krishnapuram2004}
-B.~Krishnapuram, A.~Hartemink, L.~Carin, M.~Figueiredo, {A Bayesian Approach to
-  Joint Feature Selection and Classifier Design}, IEEE T Pattern Anal 26~(9)
-  (2004) 1105--1111.
-
-\bibitem{Chen2011_FS_PTS}
-Y.~Chen, D.~Miao, R.~Wang, K.~Wu, A rough set approach to feature selection
-  based on power set tree, Knowl Based Syst 24~(2) (2011) 275 -- 281.
-
-\bibitem{Selvakuberan2008}
-K.~Selvakuberan, M.~Indradevi, R.~Rajaram, {Combined Feature Selection and
-  classification - A novel approach for the categorization of web pages}, J Inf
-  Comp Sci 3~(2) (2008) 083--089.
-
-\bibitem{liu1998feature}
-H.~Liu, H.~Motoda, {Feature extraction, construction and selection: A data
-  mining perspective}, Springer Science \& Business Media, 1998.
-
-\bibitem{Hall2009}
-M.~Hall, E.~Frank, G.~Holmes, B.~Pfahringer, P.~Reutemann, I.~Witten, {The WEKA
-  data mining software: an update}, ACM SIGKDD Explor Newslett 11~(1) (2009)
-  10--18.
-
-\bibitem{Witten2011}
-I.~Witten, E.~Frank, M.~Hall, {Data mining: Practical machine learning tools
-  and techniques}, Morgan Kaufmann, 2011.
-
-\bibitem{Hall1998}
-M.~A. Hall, Correlation-based feature subset selection for machine learning,
-  Ph.D. thesis, University of Waikato, Hamilton, New Zealand (1998).
-
-\bibitem{RobnikSikonja1997}
-M.~Robnik-Sikonja, I.~Kononenko, An adaptation of relief for attribute
-  estimation in regression, in: D.~H. Fisher (Ed.), Fourteenth International
-  Conference on Machine Learning, Morgan Kaufmann, 1997, pp. 296--304.
-
-\bibitem{Kira1992}
-K.~Kira, L.~A. Rendell, {A Practical Approach to Feature Selection}, in: D.~H.
-  Sleeman, P.~Edwards (Eds.), Ninth International Workshop on Machine Learning,
-  Morgan Kaufmann, 1992, pp. 249--256.
-
-\bibitem{UmatUlts}
-S.~Ultsch, Kohonen's self-organizing maps for exploratory data analysis, in:
-  Proc. of the INNC'90, 2000, pp. 305--308.
-
-\bibitem{Quinlan1986}
-J.~Quinlan, {Induction of decision trees}, Mach Learn 1 (1986) 181--186.
-
-\bibitem{Quinlan1992}
-R.~J. Quinlan, Learning with continuous classes, in: 5th Australian Joint
-  Conference on Artificial Intelligence, World Scientific, Singapore, 1992, pp.
-  343--348.
-
-\bibitem{Wang1997}
-Y.~Wang, I.~H. Witten,
-  \href{https://www.researchgate.net/profile/Ian_Witten/publication/33051395_Induction_of_model_trees_for_predicting_continuous_classes/links/545948ea0cf2cf516483ce67.pdf}{Induction
-  of model trees for predicting continuous classes}, Tech. rep., Dept. of
-  Computer Science, University of Waikato, working Paper 96/23, Poster papers
-  of the 9th European Conference on Machine Learning (1996).
-\newline\urlprefix\url{https://www.researchgate.net/profile/Ian_Witten/publication/33051395_Induction_of_model_trees_for_predicting_continuous_classes/links/545948ea0cf2cf516483ce67.pdf}
-
-\bibitem{WittenFrank2000}
-I.~Witten, E.~Frank, {Data mining}, Morgan Kaufmann, 2000.
-
-\bibitem{Solomatine2004}
-D.~Solomatine, Y.~Xue, {M5 Model Trees and Neural Networks: Application to
-  FloodForecasting in the Upper Reach of the Huai River in China}, J Hydrol Eng
-  9~(6) (2004) 491--501.
-
-\bibitem{Aha1991}
-D.~Aha, D.~Kibler, Instance-based learning algorithms, Mach Learn 6 (1991)
-  37--66.
-
-\bibitem{Mitchell1997}
-T.~Mitchell, {Machine Learning}, McGraw-Hill Companies, Inc., 1997.
-
-\bibitem{Breiman2001}
-L.~Breiman, Random forests, Mach Learn 45~(1) (2001) 5--32.
-
-\bibitem{Cohen2003}
-J.~Cohen, P.~Cohen, S.~West, L.~Aiken, {Applied multiple regression/correlation
-  analysis for the behavioral sciences}, Lawrence Erlbaum Associates, 2003.
-
-\bibitem{Yan2009}
-X.~Yan, {Linear Regression Analysis: Theory and Computing}, World Scientific,
-  2009.
-
-\bibitem{Rencher2102}
-A.~Rencher, W.~Christensen, {Multivariate regression}, Vol. 709 of Wiley Series
-  in Probability and Statistics, John Wiley and Sons, 2012.
-
-\bibitem{EnkeT05}
-D.~Enke, S.~Thawornwong, The use of data mining and neural networks for
-  forecasting stock market returns, Expert Syst Appl 29~(4) (2005) 927--940.
-
-\bibitem{McClendon2015}
-L.~McClendon, N.~Meghanathan, Using machine learning algorithms to analyze
-  crime data, Mach Learn and App 2~(1).
-
-\bibitem{Cortes1995}
-C.~Cortes, V.~Vapnik, {Support Vector Networks}, Mach Learn 20 (1995) 273--297.
-
-\bibitem{Shevade1999}
-S.~Shevade, S.~Keerthi, C.~Bhattacharyya, K.~Murthy, Improvements to the smo
-  algorithm for svm regression, IEEE T Neural Networ.
-
-\bibitem{MinSVM05}
-J.~H. Min, Y.~Lee, Bankruptcy prediction using support vector machine with
-  optimal choice of kernel function parameters, Expert Syst. Appl. 28~(4)
-  (2005) 603--614.
-
-\bibitem{Cao2003}
-L.~Cao, {Support vector machine experts for time series forcasting},
-  Neurocomputing 51 (2003) 321--339.
-
-\bibitem{Jari2008}
-C.~Jari, L.~Wen, L.~Kang, {Support vector machine classification for large data
-  set vis minmum enclosing ball clustering}, Neurocomputing 71 (2008) 611--619.
-
-\bibitem{gepsoft}
-{Gepsoft}, {Analyzing GeneXproTools Models Statistically. Statistical Analysis
-  of Time Series Prediction Models}, {\tt
-  http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} (Dec.
-  2015).
-
-\bibitem{pentaho}
-{pentaho}, {Pentaho Data Mining Community Documentation}, {\tt
-  http://wiki.pentaho.com/display/DATAMINING} (Dec. 2015).
-
-\bibitem{otexts}
-{otexts}, {Forecasting: principles and practice. The forecaster's toolbox.
-  Evaluating forecast accuracy}, {\tt https://www.otexts.org/fpp/2/5} (Dec.
-  2015).
-
-\bibitem{Hyndman2013}
-R.~Hyndman, G.~Athanasopoulos, Forecasting: principles and practice, OTexts,
-  2013.
-
-\bibitem{yu2004ec}
-X.~Yu, S.~Liong, V.~Babovic, Ec-svm approach for real-time hydrologic
-  forecasting., J Hydroinform 6 (2004) 209--223.
-
-\bibitem{chao2015construction}
-C.-F. Chao, M.-H. Horng, The construction of support vector machine classifier
-  using the firefly algorithm, Computat Intell Neurosci.
-
-\bibitem{hornik1989multilayer}
-K.~Hornik, M.~Stinchcombe, H.~White, Multilayer feedforward networks are
-  universal approximators, Neural networks 2~(5) (1989) 359--366.
-
-\bibitem{mirjalili2014let}
-S.~Mirjalili, S.~M. Mirjalili, A.~Lewis, Let a biogeography-based optimizer
-  train your multi-layer perceptron, Inform Sciences 269 (2014) 188--209.
-
-\bibitem{wdaa2008differential}
-A.~S.~I. Wdaa, Differential evolution for neural networks learning enhancement,
-  Ph.D. thesis, Universiti Teknologi Malaysia (2008).
-
-\bibitem{mirjalili2015effective}
-S.~Mirjalili, \href{http://dx.doi.org/10.1007/s10489-014-0645-7}{How effective
-  is the grey wolf optimizer in training multi-layer perceptrons}, Appl Intell
-  43~(1) (2015) 150--161.
-\newblock \href {http://dx.doi.org/10.1007/s10489-014-0645-7}
-  {\path{doi:10.1007/s10489-014-0645-7}}.
-\newline\urlprefix\url{http://dx.doi.org/10.1007/s10489-014-0645-7}
-
-\bibitem{Geisser1993}
-S.~Geisser, {Predictive Inference}, Chapman and Hall, 1993.
-
-\bibitem{Kohavi1995}
-R.~Kohavi, A study of cross-validation and bootstrap for accuracy estimation
-  and model selection, in: Proceedings of the Fourteenth International Joint
-  Conference on Artificial Intelligence, {IJCAI} 95, Montr{\'{e}}al
-  Qu{\'{e}}bec, Canada, August 20-25 1995, 2 Volumes, Morgan Kaufmann, 1995,
-  pp. 1137--1145.
-
-\bibitem{Devijver1982}
-P.~Devijver, J.~Kittler, {Pattern Recognition: A Statistical Approach},
-  Prentice-Hall, 1982.
-
-\bibitem{POS}
-M.~Gil, Puntos de venta de prensa y libros,
-  \url{https://antinomiaslibro.wordpress.com/2013/11/21/puntos-de-venta/},
-  consulted on May 21st, 2016 (November 2013).
-
-\bibitem{huang2006ga}
-C.-L. Huang, C.-J. Wang, A ga-based feature selection and parameters
-  optimization for support vector machines, Expert Syst Appl 31~(2) (2006)
-  231--240.
-
-\bibitem{Mookiah2013_EA_Tuning}
-M.~Mookiah, U.~Acharya, R.~Martis, C.~Chua, C.~Lim, E.~Ng, A.~Laude,
-  Evolutionary algorithm based classifier parameter tuning for automatic
-  diabetic retinopathy grading: A hybrid feature extraction approach, Knowl
-  Based Syst 39 (2013) 9--22.
-
-\bibitem{Shen2016_FFly_Tuning}
-L.~Shen, H.~Chen, Z.~Yu, W.~Kang, B.~Zhang, H.~Li, B.~Yang, D.~Liu, Evolving
-  support vector machines using fruit fly optimization for medical data
-  classification, Knowledge-Based Systems 96 (2016) 61--75.
-
-\end{thebibliography}
+\bibliography{refs}
 
@@
 \hline 
+MLP	& 81.28 $\pm$ 0.11	& 135.01 $\pm$ 56.89	& 193.56 $\pm$ 61.91	& 74.12 $\pm$ 31.58	& 75.43 $\pm$ 28.35	& 0.05 $\pm$ 0.002\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 87.25 $\pm$ 0.09	& 98.45 $\pm$ 46.65	& 156.48 $\pm$ 62.89	& 53.68 $\pm$ 23.35	& 59.5 $\pm$ 22.56	& 0.15 $\pm$ 0.002\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 66.09 $\pm$ 0.21	& 817.79 $\pm$ 242.44	& 1127.02 $\pm$ 381.75	& 84.48 $\pm$ 27.39	& 88.59 $\pm$ 33.21	& 0.03 $\pm$ 0.002\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 77.06 $\pm$ 0.18	& 714.48 $\pm$ 259.22	& 1025.29 $\pm$ 569.79	& 74.3 $\pm$ 29.92	& 81.44 $\pm$ 47.9	& 0.09 $\pm$ 0.002\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 87.67 $\pm$ 0.12	& 947.71 $\pm$ 388.67	& 1294.58 $\pm$ 458.44	& 58.62 $\pm$ 27.65	& 54.89 $\pm$ 27.53	& 0.04 $\pm$ 0.002\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 87.02 $\pm$ 0.13	& 1015.85 $\pm$ 518.44	& 1603.91 $\pm$ 1145.56	& 61.99 $\pm$ 32.97	& 67.74 $\pm$ 62.08	& 0.11 $\pm$ 0.002\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 80.08 $\pm$ 0.25	& 19.6 $\pm$ 11.66	& 29.32 $\pm$ 14.5	& 59.97 $\pm$ 35.66	& 70.05 $\pm$ 42.31	& 0.02 $\pm$ 0.002\tabularnewline
+\hline
 \end{tabular}
@@
 \hline 
+MLP	& 77.76 $\pm$ 0.33	& 19.24 $\pm$ 11.58	& 33.05 $\pm$ 24.27	& 59.53 $\pm$ 36.38	& 78.43 $\pm$ 57.62	& 0.05 $\pm$ 0.002\tabularnewline
+
 \end{tabular}

### 2016-08-20 paper.tex
references update, after the MLP has been included again
reviewing some text along the paper
including the recommend systems in the future works part (comment 3 by Rev.2): Closes #46

@@
 In this paper, we are tackling the problem of predicting total sales 
-in order to print the right amount of books and doing so even before the book has reached the stores.
-A real dataset including the complete sales data for books published in Spain across several years has been used.
-We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualisation techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods has been applied to create forecasting models for book sales.
+in order to print the right amount of books and doing so even before the book 
+has reached the stores. A real dataset including the complete sales data for 
+books published in Spain across several years has been used.
+We have conducted an analysis in three stages: an initial exploratory analysis, 
+by means of data visualisation techniques; a feature selection process, using 
+different techniques to find out what are the variables that have more impact on sales; 
+and a regression or prediction stage, in which a set of machine learning methods 
+has been applied to create forecasting models for book sales. 
 The obtained models are able to predict sales from pre-publication data with
@@
 
-This section presents the experiments conducted over the dataset considering the pre-sales variables forecasting new book sales.
-Feature selection techniques have also been applied in order to test their utility by comparing the obtained results.
-
-We have analysed the whole dataset (all the publishing companies), but also performed some experiments considering specific and representative publishing companies as example cases.
-Some of the obtained decision trees have been plotted to show their simplicity and to remark their real value as a decision-aid tool for publishers.
+This section presents the experiments conducted over the dataset considering the 
+pre-sales variables forecasting new book sales.
+Feature selection techniques have also been applied in order to test their utility 
+by comparing the obtained results.
+
+We have analysed the whole dataset (all the publishing companies), but also 
+performed some experiments considering specific and representative publishing 
+companies as example cases.
+Some of the obtained decision trees have been plotted to show their simplicity 
+and to remark their real value as a decision-aid tool for publishers.
 
@@
 
-In most data mining and machine learning algorithms, the values of
-some parameters have a high influence on its performance.
-We have conducted a systematic experimentation process, along with a revision of the bibliography describing the best configuration parameters for the methods we have applied here.
-
-Thus, in our experiments, the best value of $k$ in the $k$-nearest neighbour was empirically found at $k=3$. % What???? - JJ
+In most data mining and machine learning algorithms, the values of some 
+parameters have a high influence on its performance. We have conducted a 
+systematic experimentation process, along with a revision of the bibliography 
+describing the best configuration parameters for the methods we have applied here.
+
+Thus, in our experiments, the best value of $k$ in the $k$-nearest neighbour 
+was empirically found at $k=3$. % What???? - JJ
 For SVM, the widely used Radial Basis Function (RBF) kernel is selected. 
-As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction}.
-Two important parameters should be tuned in SVM: the Cost $(C)$ and Gamma $(\gamma)$ of the RBF kernel.
-We apply grid search which is the most common approach
-to find $C$ and $\gamma$. The best performance of SVM was found at
-$C=200$ and $\gamma = 0.01$. For MLP, we apply it with one
-hidden layer since it was proven in the literature that an MLP with
-one hidden layer can approximate any continuous or discontinuous
+As reported in several studies, RBF kernel has a reliable performance and 
+can analyse higher dimensional data \cite{yu2004ec,chao2015construction}. 
+Two important parameters should be tuned in SVM: the Cost $(C)$ and 
+Gamma $(\gamma)$ of the RBF kernel. 
+We apply grid search which is the most common approach to find $C$ and $\gamma$. 
+The best performance of SVM was found at $C=200$ and $\gamma = 0.01$. 
+For MLP, we apply it with one hidden layer since it was proven in the literature 
+that an MLP with one hidden layer can approximate any continuous or discontinuous
 function \cite{hornik1989multilayer,mirjalili2014let}. However, there
@@
 
-The selected features using each one of the three methods are shown in Table \ref{tab:features_selected}. Logically, just the independent or input variables are considered.
+The selected features using each one of the three methods are shown in 
+Table \ref{tab:features_selected}. 
+Logically, just the independent or input variables are considered.
 
@@
 
-This section presents further experiments conducted on data concerning four interesting special publishing company cases.
-These publishing companies were selected as representative cases which could be very interesting for decision makers and managers in the domain.
-The four cases are described as follows:
+This section presents further experiments conducted on data concerning four 
+interesting special publishing company cases. These publishing companies were 
+selected as representative cases which could be very interesting for decision 
+makers and managers in the domain. The four cases are described as follows:
 
@@
 
-Table \ref{Table:special_cases} shows the number of sold copies and the number of titles published by the selected companies.
+Table \ref{Table:special_cases} shows the number of sold copies and the number 
+of titles published by the selected companies.
 
@@
 targets, might in fact include different factors or have different
-leverage when deciding how much to print. For clarity purpose, we present here only the results
-after applying the RFE method for the four cases in Tables
+leverage when deciding how much to print. For clarity purpose, we present 
+here only the results after applying the RFE method for the four cases in Tables
 \ref{Table:case1results-RAE}, \ref{Table:case2results-RAE},
@@
 one was chosen since the selected features by this
-method showed in the previous experiment the highest predictive power among all classifiers. 
+method showed in the previous experiment the highest predictive power among 
+all classifiers. 
 %According to the aforementioned tables, 
 %It's not according to a table. It's according to the results there - JJ
-RFE reduction has noticeably improved the performance of all classifiers specially in the case of the best selling publisher house (i.e. UDL929) and the
-publisher which publishes a wide range of different books (i.e.
-UDL704).
-For the rest of the results which are obtained by CSE and SOM feature selection methods we refer the reader to the appendix of tables at the end of this paper.
+RFE reduction has noticeably improved the performance of all classifiers 
+specially in the case of the best selling publisher house (i.e. UDL929) and the
+publisher which publishes a wide range of different books (i.e. UDL704). 
+For the rest of the results which are obtained by CSE and SOM feature selection 
+methods we refer the reader to the appendix of tables at the end of this paper.
 
@@
   \epsfig{file=decision_tree_no_fs.eps,width=13cm}
-\caption{Decision tree built by the M5P method for the best seller publishing company including all pre-sales features.}
+\caption{Decision tree built by the M5P method for the best seller publishing 
+	company including all pre-sales features.}
 \label{fig:decision_tree_best_seller}
@@
 %how many books should be printed 
-when a new book is going to be published is faced using several data-mining and forecasting methods.
+when a new book is going to be published is faced using several data-mining 
+and forecasting methods.
 
@@
 industry, but also in other domains where the specificity of products
-is similar such as novelty items or toys, and might be of interest to other academic researches and
-industrial practitioners.  
-% Antonio - I don't know if we should say this...
+is similar such as novelty items or toys, and might be of interest to other 
+academic researches and industrial practitioners.
 
@@
 forecasting results with those yielded by other soft-computing
-methods, such as genetic programming or fuzzy logic. 
+methods, such as genetic programming, recommend systems or fuzzy logic. 
 Moreover, even if the methods have been configured to obtain the best
@@
 \bibliography{refs}
+% TODO:
+% the final list of references should be imported here from the .bbl file 
+% obtained after compiling the main LaTeX file.
+% And the previous line (\bibliography{refs}) has then to be commented.
 

### 2016-08-20 Response to reviewers.tex
including the recommend systems in the future works part (comment 3 by Rev.2): Closes #46
Intro to response reviewed

@@
 
-First, we would like to express our gratitude to the Editor in Chief, the editorial team, and the reviewers whose valuable comments on this paper have significantly improved its quality.
-All suggestions are highly appreciated and we have added a line in the acknowledgements section thanking the reviewers.
-\\
+First, we would like to express our gratitude to the Editor in Chief,
+the editorial team and the reviewers whose valuable comments on this
+paper have significantly improved its quality. All suggestions are
+highly appreciated and we have added a line in the acknowledgements
+section thanking the reviewers. \\
 
-In this new revision, we carefully have addressed all the comments in the new version of the paper. We will enumerate below these comments (in italics) and our correspondent answer to each of them. \\
+In this new revision, we have carefully addressed all the comments in
+the new version of the paper. We will enumerate below these comments
+(in italics) and our corresponding response. \\
 
-We will look forward to hearing from you about the final decision on our paper. \\
+We look forward to hearing from you about the final decision on our paper. \\
 
@@
 \begin{verbatim}
-THIS HAS TO BE DONE.
+Taking into account the reviewer's comment, the recommend systems
+have been added to the future works, at the end of Section 7 
+(see page 19).
 \end{verbatim}

### 2016-08-20 Response to reviewers.tex
Reviewing responses
Please @pacastillo or @fergunet re-write and re-address response to the first reviewer which mentions the MLP. I don't think it is addressed properly. Please see comment at the beginning of the response (search for JJ)

@@
 was to include it in this study. Thus, as suggested by the second 
-reviewer (see first comment), obtained results with this method 
+reviewer (see first comment), the results obtained with this method 
 have been included in the new version of this paper.
@@
 \end{verbatim}
-
+%The first answer does not address the question. It only asks why is
+%it described in 5.1 and not in 4.2. Probably the right response would
+%be to move it to 4.2 - JJ
 ~\\

### 2016-08-20 Response to reviewers.tex
Same thing about shortening the paper
Making it more concise is just making it shorter. Please @fergunet and @pacastillo check my comment and re-work stuff on the paper and response. Maybe a new issue for synthesizing or re-organizing things should be made.
Revised responses so far

@@
 \end{verbatim}
+% But it says we should shorten the paper, not to reorganize it. The
+% right response should be to say what parts have been shortened - JJ
 
@@
 \begin{verbatim}
-Taking into account the reviewer's comment, the recommend systems
-have been added to the future works, at the end of Section 7 
+Taking into account the reviewer's comment, the recommendation systems
+have been added to the future works section, at the end of Section 7 
 (see page 19).
 \end{verbatim}
-
+% Page might change with revision, so check it at the end - JJ
 ~\\
@@
 Following your suggestion we have reorganized these sub-sections, 
-moving them to the section 2.
+moving them to section 2.
 \end{verbatim}
@@
 Taking into account the reviewer's comment, we have improved the 
-methodology description by including a flowchart (see Figure 1 at 
+description of the methodology by including a flowchart (see Figure 1 at 
 page 6).

### 2016-08-20 paper.tex
addressing part of 1st point of reviewer#1

@@
  The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation.
-In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.
+For continuous class problems (regression), the correlation between the attributes is estimated based on a standard linear correlation
+using the Pearson's correlation coefficient as given in Equation \ref{eq:corr} \cite{hall2000correlation}.
+
+\begin{equation}
+r_{XY}=\frac{\sum xy}{n\sigma_{x}\sigma_{y}}
+\label{eq:corr}
+\end{equation}
+
+Where $X$ and $Y$ are two continuous variables expressed in terms
+of deviation.
 

### 2016-08-23 paper.tex
Just minor changes, this is not a thorough revision, though is highly needed. I will do it as soon as all the new content is added

@@
 initial one of printing only as many as forecasted, although its cost
-is not as hight as the initial one and we are not so concerned with
+is not as high as the initial one and we are not so concerned with
 this issue in this paper.
@@
   % sales forecasting in printed circuit board industry.
-In another hand, in those cases where historical data are available, classical time series forecasting methods have been applied, such as in \cite{Chang2009}, 
+On the other hand, in those cases where historical data are available, classical time series forecasting methods have been applied, such as in \cite{Chang2009}, 
 where a hybrid model integrating K-Means and fuzzy neural networks to forecast 
@@
 Figure \ref{fig:decision_tree_best_seller}, which was the company that
-sold the most books in our data set. It makes sense to use data for a
+sold the most books in our dataset. It makes sense to use data for a
 single company, since book sales for all companies is only available
@@
 \ref{fig:decision_tree_best_seller_fs}) corresponds to the same
-publishing company, so the same data were used, but the RAE feature
+publishing company, so the same data were used, but the RAE % Problem here: everytime you use RAE in the paper it means Relative Absolute Error, so I don't think we should use just "RAE" here, but ReliefAttributeEval.
+feature
 selection method was applied. This simplification, besides making the

### 2016-08-24 Response to reviewers.tex
Updating response to reviewers, as the graphical abstract is done

--- 2016-08-20 Response to reviewers.tex
@@
 
-First, we would like to express our gratitude to the Editor in Chief,
-the editorial team and the reviewers whose valuable comments on this
-paper have significantly improved its quality. All suggestions are
-highly appreciated and we have added a line in the acknowledgements
-section thanking the reviewers. \\
+First, we would like to express our gratitude to the Editor in Chief, the editorial team, and the reviewers whose valuable comments on this paper have significantly improved its quality.
+All suggestions are highly appreciated and we have added a line in the acknowledgements section thanking the reviewers.
+\\
 
-In this new revision, we have carefully addressed all the comments in
-the new version of the paper. We will enumerate below these comments
-(in italics) and our corresponding response. \\
+In this new revision, we carefully have addressed all the comments in the new version of the paper. We will enumerate below these comments (in italics) and our correspondent answer to each of them. \\
 
-We look forward to hearing from you about the final decision on our paper. \\
+We will look forward to hearing from you about the final decision on our paper. \\
 
@@
 \begin{verbatim}
-THIS HAS TO BE DONE.
-
 Taking into account the reviewer's comment, we have designed 

### 2016-08-25 Response to reviewers.tex
completing some responses/comments

--- 2016-08-20 Response to reviewers.tex
@@
 In sub-section 5.1 the MLP was described as our initial intention 
-was to include it in this study. Thus, as suggested by the second 
-reviewer (see first comment), the results obtained with this method 
-have been included in the new version of this paper.
+was to include it in this study. Thus, in sub-section 
+''2.1. Selecting an appropriate forecasting method'' (old 
+sub-section 4.2) six methods have been introduced M5P, kNN, 
+RF, LR, SVM and MLP.
+Also, as suggested by the second reviewer (see his first comment), 
+the results obtained with this method have been included in the 
+new version of this paper.
 
-As far as the number of trees is related, TODO.
+As far as the number of trees is related, THIS HAS TO BE DONE.
 \end{verbatim}
@@
 %be to move it to 4.2 - JJ
+% Yes, that is what has been done. However, you're right, it was necessary 
+% to comment on that point  ;)
 ~\\
@@
 % right response should be to say what parts have been shortened - JJ
+% I'm working on shortening some parts. Thank you!  - Pedro
 
@@
 % Page might change with revision, so check it at the end - JJ
+% of course! you are right!  - Pedro
 ~\\

### 2016-08-25 paper.tex
fixing some typos

@@
 variable, so it is the objective of the prediction methods. {\tt
-  total\_sales} are a variable percentage of the {\tt print\_run}, and
+  total\_sales} is a variable percentage of the {\tt print\_run}, and
 thus there is obviously some correlation between them, which might

### 2016-08-25 paper.tex
fixing some typos
addressing part of 1st point of reviewer#1

@@
 \ref{tabla:paramsOrig50}), but for most of the patterns (books) there
-is no value for subjects2 and 3, so we have discarded these features.
+is no value for \textit{subjects2} and \textit{3}, so we have discarded 
+these features.
 
@@
 
-``Relief'' is the second evaluator used in this work.
-It is important to note that the relief method implemented in Weka is an updated version \cite{RobnikSikonja1997}, called RRELIEFF, of the original by Kira \& Rendell \cite{Kira1992}.
+``ReliefF'' is the second evaluator used in this work. It is important to note 
+we have applied the Weka's implementation of the ReliefF algorithm for regression problems.
+This relief method is an updated version, called Regressional ReliefF or RReliefF for short \cite{RobnikSikonja1997}, of the original ReliefF by Kira \& Rendell \cite{Kira1992}.
 The algorithm works by evaluating single attributes, and not whole subsets of attributes as CFS does.

### 2016-08-25 Response to reviewers.tex
added response to 1st point of reviewer#1

@@
 \begin{verbatim}
-THIS HAS TO BE DONE.
+In all our experiments we have applied the Weka's implementation of the ReliefF algorithm in the regression problems.
+This version is called "Regressional ReliefF" or "RReliefF" for short which was first introduced and implemented by Robnik-Sikonja and Kononenko in Ref XX for numeric targets.
+Therefore, we have clarified this point in the text to remove any ambiguity.
+
+For CSF, estimating the correlation between attributes is standard linear (Pearson's) correlation.
+The details have been added to the text to clarify this point.
 \end{verbatim}

### 2016-08-29 paper.tex
Added a brief description of ELM

@@
 works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
+
+\item \emph{Extreme learning machine (ELM)}: 
+ELM is an algorithm for training a single hidden 
+layer feedforward neural network which was first proposed by Guang-Bin Huang \cite
+{huang2006extreme}. A typical implementation of ELM is a single hidden layer network where the 
+connection weights between the input layer and the hidden layer are randomly initialized and 
+fixed, while the connection weights between the hidden layer the output layer are learned 
+analytically in a single step of linear parameters solving. In ELM the hidden layer maps the 
+input data into a feature space called ELM feature space using non-linear activation functions 
+such as Sigmoid, Hyperbolic and Gaussian functions \cite{huang2015trends}.The main advantages 
+of ELM are the ease of use and the very efficient learning speed compared to other traditional 
+training methods such as the Backpropagation algorithm.
 

### 2016-08-29 paper.tex
fixing some typos

@@
 Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation.
-Thus, it is very suitable model be incorporated in a publishing company
+Thus, it is a very suitable model be incorporated in a publishing company
 processes (as we will show in Section \ref{subsec:decision_trees}).
@@
 
-According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that the Linear Regression model outperforms some other complex methods like the Random Forest, both in time and in obtained errors.
-Although, Linear regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.
+According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that 
+the Linear Regression model outperforms some other complex methods like the 
+Random Forest, both in time and in obtained errors. 
+Although, Linear Regression is considered as a simple model to build, more 
+powerful models can obtain better results in comparable time.
 
@@
 best results compared to SOM and CSE. It can be noticed also that we
-obtain better performance in M5P, kNN and RF using only features
+obtain better performance using M5P, kNN and RF with the set of features
 selected by RFE than using all features. %Better publish results in

### 2016-08-31 paper.tex
reducing some paragraphs + fixing some typos

@@
 This section presents further experiments conducted on data concerning four 
-interesting special publishing company cases. These publishing companies were 
+specially interesting publishing company cases. These publishing companies were 
 selected as representative cases which could be very interesting for decision 
@@
 
-Evaluation results of the developed models (without performing any feature selection method) for the selected four cases are shown in Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
+Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases are shown in Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
 The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}.
@@
 its own sales. This company is also representative because, being the
-one that sells the most, will have the biggest range of sales for
+one that sells the most, it will have the biggest range of sales for
 individual books. In this figure, tree {\em leaves} correspond to
@@
 tree easier to understand, reduces training time to a fraction of what
-was needed before it.
+was needed before the selection method was applied.
 
 Examining both trees, it can be noticed that
-\texttt{tot\_points\_sale} variable appears twice in the trees, being
-also the root. This indicates that the total number of points of sale
-has the biggest influence on the decision models and also a major role in
-forecasting the total sales, implying that buyers have to actually
-{\em see}, maybe browse the book, before buying it. Books have to
-physically {\em be} in the point of sale, so this number gives a lower
-bound to the number of books that have to be printed; a stack of book
-will have to be present in each point of sale to attain that effect. 
+\texttt{tot\_points\_sale} variable appears twice in the trees, being also the root
+% I'm reducing some paragraphs by eliminating some sentences that appears repeated.
+(it has the biggest influence on the decision models and also a major role in forecasting the total sales, implying that books have to physically {\em be} in the point of sale).
+% This indicates that the total number of points of sale has the biggest influence on the decision models and also a major role in forecasting the total sales, implying that buyers have to actually {\em see}, maybe browse the book, before buying it.
+Books have to physically {\em be} in the point of sale, so this number gives a lower bound to the number of books that have to be printed; a stack of book will have to be present in each point of sale to attain that effect.
 This is an interesting clue for the
@@
 to bookstores to stack on the {\em novelty} table. You need to sell
-roughly 5, the result of dividing 2807.5 y 550.5, to have a lower
+roughly 5, the result of dividing 2807.5 and 550.5, to have a lower
 bound in sales at 1006, which is negatively impacted by the retail
@@
 as many places as possible. The first tree
-\ref{fig:decision_tree_best_seller} gives an idea of what we
+(in Figure \ref{fig:decision_tree_best_seller}) gives an idea of what we
 are talking about, sales start at 1000 but the single factor that has
@@
 would have to look more closely at the second tree
-\ref{fig:decision_tree_best_seller_fs} to check what are other factors
+(in Figure \ref{fig:decision_tree_best_seller_fs}) to check what are other factors
 influencing sales. It is also interesting that the number of total

### 2016-08-31 paper.tex
changing the meaning of a strange sentence
closing the issue about the flowchart (comment 3 by Rev.3): Closes #48

@@
 Some specific interpretable models have been created as a final result of the work. 
-The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.
+%The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.
 
@@
 Random Forest, both in time and in obtained errors. 
-Although, Linear Regression is considered as a simple model to build, more 
-powerful models can obtain better results in comparable time.
+%Although, Linear Regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.
+% I change this sentence as its meaning is 'strange'...
+[pedro]
+Although, Linear Regression is considered as a simple model to build, it can obtain better results than more powerful models in comparable time.
 

### 2016-09-01 Tables_to_figures/generador.r
Datasets and chaotic R-file to process it

@@ -1,0 +1,171 @@
+library(stringr)
+library(reshape2)
+library(ggplot2)
+
+
+#Multiplot
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                     ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+  
+  if (numPlots==1) {
+    print(plots[[1]])
+    
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+    
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+      
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+
+
+
+filenames_all <- list.files(path = "datasets/AllAttributes/",pattern = ".csv",full.names = TRUE)
+ldf <- lapply(filenames_all, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
+for(i in seq(from=1,to=length(filenames_all),by = 1)){
+  ldf[[i]]$Dataset <- sapply(str_split(filenames_all, '/'), '[', 4)[i]
+  ldf[[i]]$Attributes <- "All"
+}
+
+
+filenames_sel <- list.files(path = "datasets/ReliefFAttributeEval-FS//",pattern = ".csv",full.names = TRUE)
+ldf_s <- lapply(filenames_sel, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
+for(i in seq(from=1,to=length(filenames_sel),by = 1)){
[…]

### 2016-09-02 paper.tex
Reduction of text in introduction. Some errors fixed. Classification term changed by regression

@@
 order to optimise production schedules, improve the publishing company
-profits and minimise losses \cite{Zhao2001}, being the latter the main
-objective of this paper.  This is the main problem we are going to
-tackle in this paper.
+profits and minimise losses \cite{Zhao2001}. This is the main objective of this paper.
 
@@
 control. That is why, using data obtained from a  company that sells
-software for publishers, we analyse it by means of different data
-mining methods and create predictive models that can be mainly used as
-decision-aid tools for book publishers. With these models, publishers
-will be able to 
-combine their expert knowledge about the market with the created
-forecasting models in order to get a reliable estimation of book
-sales, and, based on it, act upon it to maximize the books sold for a
-particular print run. Our main contribution is, thus, to develop a
-methodology to process book sales data in order to first find out
-relevant variables and then use these variables to process data so
-that the publisher, using them, can estimate sales and from them order
-a specific print run, instead of standard ones, which are around 300
-copies for standard books and around 5000 for those that are
-considered, in advance, {\em best sellers}.
-
-In the research published in this paper, the problem 
-of predicting total sales in order to print the right amount of books
-%of how many units should be printed  when a new book is published 
-is approached using real data provided by the 
-Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
+software for publishers, we analyse them and compute predictive models that can be mainly used as decision-aid tools for book publishers.
+With these models, publishers will be able to combine their expert knowledge about the market with the created forecasting models in order to get a reliable estimation of book
+sales, and, based on it, act consequently in order to maximize the books sold for a particular print run.
+This will improve the current decision flow that the publishers follow, which consist in analysing (in a subjective way) the quality of the book and its features (author, genre, etc), and take a `fuzzy' decision roughly between printing 300 copies (standard book) or 5000 (best seller).
+
+Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out
+relevant variables, and then, use these variables to process the data to accurately estimate future sales.
+
+In the research published in this paper, the problem of predicting total sales is approached using real data provided by the 
+Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. This company offers management systems and services for bookshops, publishers, and distributors. 
 Usually, the company's expert sales managers analysed historical data
@@
 instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
+% Antonio - should we change the term 'classification' by 'regression' somehow?
 
@@
 
-In classification problems the algorithm searches for an optimal hyperplane 
-that separates two classes, maximising the margin between them. 
-In the case of regression the algorithm chooses a hyperplane close to as many 
+%In classification problems the algorithm searches for an optimal hyperplane 
+%that separates two classes, maximising the margin between them.
+% Antonio - remove this classification thing due to a reviewer's comment 
+In regression problems, the algorithm chooses a hyperplane close to as many 
 of the data points as possible, minimising the sum of the distances from 
@@
 approximation problems.
+% Antonio - something about regression?
 
@@
 The aim of these algorithms is exploring the space of attributes to find out 
-which subset of them yields the best results in a classification or prediction 
+which subset of them yields the best results in a regression or prediction 
 problem. To this end, the features describing every pattern are analysed. 
@@
 
-As far as the different methods are concerned, M5P model obtained the best results, both in time and error.
-The advantage of M5P is that it can learn and tackle classification tasks that have high dimensionality and categorical variables efficiently.
+As far as the different methods are concerned, M5P model obtained the best results, both in time and error. The advantage of M5P is that it can learn and tackle regression
+% Antonio - I think we can change classification by regression. I have done. Check it out. ;)
+ tasks that have high dimensionality and categorical variables efficiently.
 Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation.
@@
 First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (RFE, CSE and SOM) are used to reduce the set of features in each case.
-Second, the classification models are applied again on the reduced datasets to evaluate their performance.
+Second, the regression models are applied again on the reduced datasets to evaluate their performance.
 
@@
 \begin{table*}
-\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company). Best values in bold. }
+\caption{Predicting Total sales for publishing company UDL929 (The best selling publishing company). Best values in bold. }
 \centering{}%
@@
 \begin{table*}
-\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company). Best values in bold. }
+\caption{Predicting Total sales for publishing company UDLW12 (The median selling publishing company). Best values in bold. }
 \centering{}%
@@
 \begin{table*}
-\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold). Best values in bold.}
+\caption{Predicting Total sales for publishing company UDL704 (highest number of different titles sold). Best values in bold.}
 \centering{}%
@@
 \begin{table*}
-\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold)). Best values in bold.}
+\caption{Predicting Total sales for publishing company UDLU11 (medium number of different books sold)). Best values in bold.}
 \centering{}%
@@
 all classifiers. 
+% Antonio - could we use any sinonym of classifier but for regression... I guess 'regressor' is not appropriate. :D
+%
 %According to the aforementioned tables, 
@@
 % Serif - JJ
-\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
+\caption{Predicting Total sales for publishing company UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
+\caption{Predicting Total sales for publishing company UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%
@@
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS). Best values in bold. }
+\caption{Predicting Total sales for publishing company UDL704 (ReliefFAttributeEval-FS). Best values in bold. }
 \centering{}%
@@
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (ReliefFAttributeEval-FS). Best values in bold.}
+\caption{Predicting Total sales for publishing company UDLU11 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%

### 2016-09-02 paper.tex
my name :)

--- 2016-08-31 paper.tex
@@
 \ead{amorag@geneura.ugr.es}
-\author[abd]{H. Faris}
+\author[abd]{Hossam Faris}
 \ead{hossam.faris@ju.edu.jo}
@@
 Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation.
-Thus, it is a very suitable model be incorporated in a publishing company
+Thus, it is very suitable model be incorporated in a publishing company
 processes (as we will show in Section \ref{subsec:decision_trees}).
@@
 
-According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that 
-the Linear Regression model outperforms some other complex methods like the 
-Random Forest, both in time and in obtained errors. 
-Although, Linear Regression is considered as a simple model to build, more 
-powerful models can obtain better results in comparable time.
+According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that the Linear Regression model outperforms some other complex methods like the Random Forest, both in time and in obtained errors.
+Although, Linear regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.
 
@@
 best results compared to SOM and CSE. It can be noticed also that we
-obtain better performance using M5P, kNN and RF with the set of features
+obtain better performance in M5P, kNN and RF using only features
 selected by RFE than using all features. %Better publish results in
@@
 This section presents further experiments conducted on data concerning four 
-specially interesting publishing company cases. These publishing companies were 
+interesting special publishing company cases. These publishing companies were 
 selected as representative cases which could be very interesting for decision 
@@
 
-Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases are shown in Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
+Evaluation results of the developed models (without performing any feature selection method) for the selected four cases are shown in Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
 The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}.
@@
 its own sales. This company is also representative because, being the
-one that sells the most, it will have the biggest range of sales for
+one that sells the most, will have the biggest range of sales for
 individual books. In this figure, tree {\em leaves} correspond to
@@
 tree easier to understand, reduces training time to a fraction of what
-was needed before the selection method was applied.
+was needed before it.
 
 Examining both trees, it can be noticed that
-\texttt{tot\_points\_sale} variable appears twice in the trees, being also the root
-% I'm reducing some paragraphs by eliminating some sentences that appears repeated.
-(it has the biggest influence on the decision models and also a major role in forecasting the total sales, implying that books have to physically {\em be} in the point of sale).
-% This indicates that the total number of points of sale has the biggest influence on the decision models and also a major role in forecasting the total sales, implying that buyers have to actually {\em see}, maybe browse the book, before buying it.
-Books have to physically {\em be} in the point of sale, so this number gives a lower bound to the number of books that have to be printed; a stack of book will have to be present in each point of sale to attain that effect.
+\texttt{tot\_points\_sale} variable appears twice in the trees, being
+also the root. This indicates that the total number of points of sale
+has the biggest influence on the decision models and also a major role in
+forecasting the total sales, implying that buyers have to actually
+{\em see}, maybe browse the book, before buying it. Books have to
+physically {\em be} in the point of sale, so this number gives a lower
+bound to the number of books that have to be printed; a stack of book
+will have to be present in each point of sale to attain that effect. 
  This is an interesting clue for the
@@
 to bookstores to stack on the {\em novelty} table. You need to sell
-roughly 5, the result of dividing 2807.5 and 550.5, to have a lower
+roughly 5, the result of dividing 2807.5 y 550.5, to have a lower
 bound in sales at 1006, which is negatively impacted by the retail
@@
 as many places as possible. The first tree
-(in Figure \ref{fig:decision_tree_best_seller}) gives an idea of what we
+\ref{fig:decision_tree_best_seller} gives an idea of what we
 are talking about, sales start at 1000 but the single factor that has
@@
 would have to look more closely at the second tree
-(in Figure \ref{fig:decision_tree_best_seller_fs}) to check what are other factors
+\ref{fig:decision_tree_best_seller_fs} to check what are other factors
 influencing sales. It is also interesting that the number of total

### 2016-09-03 Tables_to_figures/generador.r
New dataset (attributes selection methods) added.

@@ -57,12 +57,37 @@ for(i in seq(from=1,to=length(filenames_sel),by = 1)){
   ldf_s[[i]]$Attributes <- "ReliefFAttributeEval-FS"
 }
 
+filenames_som <- list.files(path = "datasets/SOM-FS//",pattern = ".csv",full.names = TRUE)
+ldf_som <- lapply(filenames_som, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
+for(i in seq(from=1,to=length(filenames_som),by = 1)){
+  ldf_som[[i]]$Dataset <- sapply(str_split(filenames_som, '/'), '[', 5)[i]
+  ldf_som[[i]]$Attributes <- "SOM-FS"
+}
+
+filenames_som <- list.files(path = "datasets/SOM-FS//",pattern = ".csv",full.names = TRUE)
+ldf_som <- lapply(filenames_som, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
+for(i in seq(from=1,to=length(filenames_som),by = 1)){
+  ldf_som[[i]]$Dataset <- sapply(str_split(filenames_som, '/'), '[', 5)[i]
+  ldf_som[[i]]$Attributes <- "SOM-FS"
+}
+
+filenames_cfs <- list.files(path = "datasets/CfsSubsetEval-FS//",pattern = ".csv",full.names = TRUE)
+ldf_cfs <- lapply(filenames_cfs, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
+for(i in seq(from=1,to=length(filenames_cfs),by = 1)){
+  ldf_cfs[[i]]$Dataset <- sapply(str_split(filenames_cfs, '/'), '[', 5)[i]
+  ldf_cfs[[i]]$Attributes <- "CfsSubsetEval-FS"
+}
+
 m_all <- do.call(rbind,ldf)
 m_sel <- do.call(rbind,ldf_s)
+m_som <- do.call(rbind,ldf_som)
+m_cfs <- do.call(rbind,ldf_cfs)
 
 m <- rbind(m_all,m_sel)
+m <- rbind(m,m_som)
+m <- rbind(m,m_cfs)
 
[…]

### 2016-09-03 paper.tex
Revert "my name :)"
This reverts commit f3c42def2db9ec1def81b65e647918d728b8b7df.
My name
Fixed correlation symbol
Added parameters settings for M5P and ELM

--- 2016-09-02 paper.tex
@@
 Thus, in our experiments, the best value of $k$ in the $k$-nearest neighbour 
-was empirically found at $k=3$. % What???? - JJ
+was empirically found at $k=3$.
+For the RF, the best performance was achieved with a number of trees equal to 50.
+In M5P, the batch size was set to 100 and the minimum number of instances allowed at a leaf node is set to 2.
+In ELM, since the network has an extreme learning speed, we have tried different possible numbers of hidden neurons starting from 1 up to 100.
+Also, different activation functions were tested for the ELM.
+The best performance was obtained with an RBF activation function.
+
 For SVM, the widely used Radial Basis Function (RBF) kernel is selected. 
@@
 MLP	& 88.01 $\pm$ 0.11	& 350.99 $\pm$ 185.53	& 730.93 $\pm$ 374.84	& 61.64 $\pm$ 33.61	& 56.33 $\pm$ 31.6	& 7014.06 $\pm$ 110.095 \tabularnewline
+\hline 
+ELM & 	86.79	 $\pm$ 	0.11	 & 	271.01	 $\pm$ 	28.53	 & 	684.98	 $\pm$ 	329.39	 & 	47.73	 $\pm$ 	0.06	 & 	52.42	 $\pm$ 	0.26	 & 	0.203	 $\pm$ 	0.03  \tabularnewline
+
 \hline 
@@
 \hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
 \hline 
@@
 MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
+\hline  
+ELM & 	87.55	 $\pm$ 	0.1	 & 	250.88	 $\pm$ 	28.78	 & 	677.94	 $\pm$ 	356.41	 & 	44.16	 $\pm$ 	0.05	 & 	50.86	 $\pm$ 	0.24	 & 	0.1106	 $\pm$ 	0.02\\
 \hline
@@
 \hline
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
 \hline 
@@
 \hline
+ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
+\hline
+
 \end{tabular}
@@
 \hline 
- &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+ &  $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
 \hline 
@@
 MLP	& 84.3 $\pm$ 0.12	& 388.79 $\pm$ 274.18	& 851.01 $\pm$ 422.03	& 68.26 $\pm$ 49.64	& 65.85 $\pm$ 36.49	& 3.29 $\pm$ 0.042\tabularnewline
+\hline
+ELM & 	85.3	 $\pm$ 	0.09	 & 	301.42	 $\pm$ 	31.43	 & 	704.9	 $\pm$ 	221.83	 & 	53.22	 $\pm$ 	0.07	 & 	54.57	 $\pm$ 	0.18	 & 	0.0229	 $\pm$ 	0.02\\
 \hline
@@
 \hline 
- & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+ & $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
 \hline 
@@
 MLP	& 84.42 $\pm$ 0.12	& 1105.61 $\pm$ 445.66	& 1776.68 $\pm$ 1148.31	& 66.52 $\pm$ 23.63	& 70.41 $\pm$ 41.88	& 1.65 $\pm$ 0.008 \tabularnewline
+\hline
+ELM & 	53.38	 $\pm$ 	0.24	 & 	1898.17	 $\pm$ 	728.63	 & 	3104.85	 $\pm$ 	1503.83	 & 	136.82	 $\pm$ 	0.76	 & 	146.75	 $\pm$ 	0.95	 & 	0.0184	 $\pm$ 	0.02
+ \tabularnewline
 \hline
@@
 MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
+\hline
+ELM & 	60.52	 $\pm$ 	0.39	 & 	24.28	 $\pm$ 	13.57	 & 	38.83	 $\pm$ 	26.43	 & 	118.09	 $\pm$ 	1.35	 & 	131.51	 $\pm$ 	1.37	 & 	0.0036	 $\pm$ 	0.01 \tabularnewline
 \hline
@@
 \hline
+ELM & 	65.13	 $\pm$ 	0.21	 & 	336.33	 $\pm$ 	1414.85	 & 	1279.83	 $\pm$ 	7128.87	 & 	189.38	 $\pm$ 	7.49	 & 	501.38	 $\pm$ 	26.56	 & 	0.0042	 $\pm$ 	0.01
+ \tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline 
-MLP	& 0.7649 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
+MLP	& 76.49 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
+\hline
+ELM & 	61.55	 $\pm$ 	0.24	 & 	1350.19	 $\pm$ 	3934.54	 & 	3681.73	 $\pm$ 	19380.44	 & 	140.16	 $\pm$ 	3.02	 & 	264.72	 $\pm$ 	10.87	 & 	0.009	 $\pm$ 	0.02
+ \tabularnewline
 \hline
@@
 \hline 
- & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
 \hline 
@@
 MLP	& 87.66 $\pm$ 0.14	& 897.02 $\pm$ 411.58	& 1332.54 $\pm$ 969.05	& 56.43 $\pm$ 33.1	& 58.52 $\pm$ 57.68	& 0.17 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	84.08	 $\pm$ 	0.17	 & 	890.49	 $\pm$ 	343.61	 & 	1470.33	 $\pm$ 	993.74	 & 	61.76	 $\pm$ 	0.32	 & 	65.14	 $\pm$ 	0.5	 & 	0.0119	 $\pm$ 	0.02 \tabularnewline
 \hline
@@
 MLP	& 79.26 $\pm$ 0.27	& 20.28 $\pm$ 13.25	& 35.05 $\pm$ 29.44	& 61.89 $\pm$ 37.64	& 81.51 $\pm$ 63.39	& 0.07 $\pm$ 0.002\tabularnewline
+\hline 
+ELM & 	70.58	 $\pm$ 	0.34	 & 	19.52	 $\pm$ 	9.91	 & 	30.49	 $\pm$ 	18.09	 & 	145.28	 $\pm$ 	2.94	 & 	167.8	 $\pm$ 	3.39	 & 	0.0027	 $\pm$ 	0.01 \tabularnewline
 \hline
@@
 \hline
+ELM & 	83.47	 $\pm$ 	0.1	 & 	89.65	 $\pm$ 	25.9	 & 	167.99	 $\pm$ 	82.63	 & 	51.51	 $\pm$ 	0.14	 & 	65.11	 $\pm$ 	0.28	 & 	0.0041	 $\pm$ 	0.01\tabularnewline
+\hline
+
 \end{tabular}
@@
 MLP	& 77.3 $\pm$ 0.13	& 709.2 $\pm$ 235.87	& 960.43 $\pm$ 345.28	& 73.11 $\pm$ 24.95	& 75.19 $\pm$ 25.74	& 0.14 $\pm$ 0.003\tabularnewline
+\hline
+ELM & 	79.73	 $\pm$ 	0.14	 & 	569.2	 $\pm$ 	161.37	 & 	841.75	 $\pm$ 	322.13	 & 	61.87	 $\pm$ 	0.21	 & 	69.99	 $\pm$ 	0.3	 & 	0.007	 $\pm$ 	0.02 \tabularnewline
 \hline
@@
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDL704 (CfsSubsetEval-FS). Best values in bold.}
 \centering{}%
@@
 \hline
+ELM & 	78.42	 $\pm$ 	0.15	 & 	109.24	 $\pm$ 	52.6	 & 	203.11	 $\pm$ 	215.35	 & 	62.28	 $\pm$ 	0.24	 & 	78.75	 $\pm$ 	0.68	 & 	0.0019	 $\pm$ 	0.01 \tabularnewline
+\hline
 \end{tabular}
@@
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo704 (SOM-FS). Best values in bold.}
+\caption{Predicting Total sales for PublishingCo-UDL704 (SOM-FS). Best values in bold.}
 \centering{}%
@@
 MLP	& 87.25 $\pm$ 0.09	& 98.45 $\pm$ 46.65	& 156.48 $\pm$ 62.89	& 53.68 $\pm$ 23.35	& 59.5 $\pm$ 22.56	& 0.15 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	85.22	 $\pm$ 	0.11	 & 	85.57	 $\pm$ 	25.92	 & 	141.17	 $\pm$ 	62.02	 & 	49.48	 $\pm$ 	0.16	 & 	56.58	 $\pm$ 	0.25	 & 	0.0014	 $\pm$ 	0.01\tabularnewline
 \hline
@@
 MLP	& 66.09 $\pm$ 0.21	& 817.79 $\pm$ 242.44	& 1127.02 $\pm$ 381.75	& 84.48 $\pm$ 27.39	& 88.59 $\pm$ 33.21	& 0.03 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	65.66	 $\pm$ 	0.25	 & 	859.21	 $\pm$ 	836.34	 & 	1691.61	 $\pm$ 	3053.2	 & 	92.4	 $\pm$ 	0.81	 & 	134.53	 $\pm$ 	2.18	 & 	0.0009	 $\pm$ 	0.01 \tabularnewline
 \hline
@@
 MLP	& 77.06 $\pm$ 0.18	& 714.48 $\pm$ 259.22	& 1025.29 $\pm$ 569.79	& 74.3 $\pm$ 29.92	& 81.44 $\pm$ 47.9	& 0.09 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	79.52	 $\pm$ 	0.12	 & 	606.38	 $\pm$ 	153.83	 & 	818.18	 $\pm$ 	243.54	 & 	65.7	 $\pm$ 	0.18	 & 	67.17	 $\pm$ 	0.21	 & 	0.0044	 $\pm$ 	0.01 \tabularnewline
 \hline
@@
 MLP	& 87.67 $\pm$ 0.12	& 947.71 $\pm$ 388.67	& 1294.58 $\pm$ 458.44	& 58.62 $\pm$ 27.65	& 54.89 $\pm$ 27.53	& 0.04 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	87.25	 $\pm$ 	0.14	 & 	776.49	 $\pm$ 	209.23	 & 	1171.43	 $\pm$ 	455.5	 & 	53.63	 $\pm$ 	0.25	 & 	53.14	 $\pm$ 	0.37	 & 	0.0031	 $\pm$ 	0.01\tabularnewline
 \hline
@@
 MLP	& 87.02 $\pm$ 0.13	& 1015.85 $\pm$ 518.44	& 1603.91 $\pm$ 1145.56	& 61.99 $\pm$ 32.97	& 67.74 $\pm$ 62.08	& 0.11 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	83.44	 $\pm$ 	0.17	 & 	884.83	 $\pm$ 	297.95	 & 	1430.42	 $\pm$ 	874.32	 & 	64.61	 $\pm$ 	0.37	 & 	69.69	 $\pm$ 	0.68	 & 	0.002	 $\pm$ 	0.01\tabularnewline
 \hline
@@
 MLP	& 80.08 $\pm$ 0.25	& 19.6 $\pm$ 11.66	& 29.32 $\pm$ 14.5	& 59.97 $\pm$ 35.66	& 70.05 $\pm$ 42.31	& 0.02 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	77.62	 $\pm$ 	0.3	 & 	16.53	 $\pm$ 	9.12	 & 	27.18	 $\pm$ 	18.2	 & 	72.75	 $\pm$ 	0.64	 & 	86.09	 $\pm$ 	0.86	 & 	0.0012	 $\pm$ 	0.01\tabularnewline
+
 \hline
@@
 MLP	& 77.76 $\pm$ 0.33	& 19.24 $\pm$ 11.58	& 33.05 $\pm$ 24.27	& 59.53 $\pm$ 36.38	& 78.43 $\pm$ 57.62	& 0.05 $\pm$ 0.002\tabularnewline
-
+\hline
+ELM & 	73.42	 $\pm$ 	0.31	 & 	20.08	 $\pm$ 	9.8	 & 	31.45	 $\pm$ 	18.84	 & 	85.55	 $\pm$ 	0.6	 & 	93.42	 $\pm$ 	0.64	 & 	0.0036	 $\pm$ 	0.01\tabularnewline
+\hline
 \end{tabular}

### 2016-09-03 Response to reviewers.tex
fixing some typos
adding text to answer R1 comments #3 and #4
Added a response to 1st point of Reviewer#2
closing the issue about M5P and RF embed feature selection (comment 3 by Rev.1): Closes #44

@@
 \begin{verbatim}
-In all our experiments we have applied the Weka's implementation of the ReliefF algorithm in the regression problems.
-This version is called "Regressional ReliefF" or "RReliefF" for short which was first introduced and implemented by Robnik-Sikonja and Kononenko in Ref XX for numeric targets.
-Therefore, we have clarified this point in the text to remove any ambiguity.
+In all our experiments we have applied the Weka's implementation 
+of the ReliefF algorithm in the regression problems. 
+This version is called "Regressional ReliefF" or "RReliefF" for 
+short which was first introduced and implemented by Robnik-Sikonja 
+and Kononenko in Ref XX for numeric targets. 
+Therefore, we have clarified this point in the text to remove 
+any ambiguity.
 
-For CSF, estimating the correlation between attributes is standard linear (Pearson's) correlation.
+For CSF, estimating the correlation between attributes is 
+standard linear (Pearson's) correlation.
 The details have been added to the text to clarify this point.
@@
 \end{verbatim}
-%The first answer does not address the question. It only asks why is
-%it described in 5.1 and not in 4.2. Probably the right response would
-%be to move it to 4.2 - JJ
-% Yes, that is what has been done. However, you're right, it was necessary 
-% to comment on that point  ;)
+
 ~\\
@@
 \begin{verbatim}
-THIS HAS TO BE DONE.
+Although we agree with the reviewer's comment, and the RF and M5P 
+have an embedded feature selection mechanism, we believe that it 
+is unfair to compare them with the filter based feature selection 
+methods we have deployed in our research. 
+The idea is simply to show the decision maker what are the possible 
+results when we apply one of the off-the-shelf classifiers available 
+in a common open source framework such as WEKA. 
+Moreover, it is not uncommon in the literature to see such comparison 
+between classifiers, such as in the paper:
+  M. Fernández-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
+  Do we need hundreds of classifiers to solve real world 
+  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
+which incorporates a general comparison between all these classifiers.
 \end{verbatim}
@@
 \begin{verbatim}
-THIS HAS TO BE DONE.
+According to the reviewer's comment, we have addressed this issue
+at the same time that comment #1, where the application procedure 
+of feature selection methods for regression problems has been 
+clarified. 
+Also, we have added the ''regression'' term all along the paper 
+including the description of the dataset.
 \end{verbatim}
@@
 them clearer and to improve its comprehension. 
+Also, several tables have been moved to the Appendix and that
+data has been presented now as the new Figure X.
 
@@
 \begin{verbatim}
-THIS HAS TO BE DONE.
+We have added the results of ANN(MLP) and ELM to all tables 
+accordingly. A description of both approaches have been also 
+added to subsection 2.1.
 \end{verbatim}
@@
 \begin{verbatim}
-Taking into account the reviewer's comment, the recommendation systems
-have been added to the future works section, at the end of Section 7 
-(see page 19).
+Taking into account the reviewer's comment, the recommendation 
+systems have been added to the future works section, at the end 
+of Section 7 (see page 19).
 \end{verbatim}
@@
 Taking into account the reviewer's comment, we have improved the 
-description of the methodology by including a flowchart (see Figure 1 at 
-page 6).
+description of the methodology by including a flowchart (see Figure 1 
+at page 6).
 \end{verbatim}

### 2016-09-03 Response to reviewers.tex
closing the issue about regression viewpoint (comment 4 by Rev.1): Closes #50
closing the issue about graphical abstract (comment 5 by Rev.2): Closes #51
closing the issue about adding MLP and ELM results (comment 1 by Rev.2): Closes #41
closing the issue about parameter settings of M5P, kNN and RF (comment 4 by Rev.3): Closes #49

@@
 of feature selection methods for regression problems has been 
-clarified. 
-Also, we have added the ''regression'' term all along the paper 
-including the description of the dataset.
+clarified. Also, we have added the ''regression'' term all along 
+the paper including the description of the dataset.
 \end{verbatim}
@@
 \begin{verbatim}
-We have added the results of ANN(MLP) and ELM to all tables 
+We have added the results of ANN (MLP) and ELM to all tables 
 accordingly. A description of both approaches have been also 
@@
 \begin{verbatim}
-THIS HAS TO BE DONE.
-
 Taking into account the reviewer's comment, we have improved the 

### 2016-09-03 Tables_to_figures/generador.r
Added ELM to process file

@@ -89,17 +89,19 @@ m <- rbind(m,m_cfs)
 
 rm(m_all,m_sel,m_som,m_cfs,ldf,ldf_s,ldf_som,ldf_cfs,filenames_sel,filenames_all,filenames_som,filenames_cfs,i)
 
-datos <- melt(data = m,id.vars = c("Method","Dataset","Attributes"),measure.vars = c("R2","MAE","RMSE","RAE","RRSE","TIME"),)
+datos <- melt(data = m,id.vars = c("Method","Dataset","Attributes"),measure.vars = c("R.","MAE","RMSE","RAE","RRSE","TIME"),)
 
 datos$Dataset <- str_replace(datos$Dataset,".csv","")
 
 datos$error <- as.numeric(sapply(str_split(datos$value, '_'), '[', 2))
 datos$value <- as.numeric(sapply(str_split(datos$value, '_'), '[', 1))
 
+datos$variable <- as.character(datos$variable)
+datos[datos$variable=="R.","variable"] <- "R^2"
 dataset = unique(datos$Dataset)
 
 ggplot(data = subset(datos,Dataset==dataset[1]), aes(x=Attributes,y=value,color=Attributes,shape=Attributes)) + geom_point(stat="identity",size=3) + 
-  facet_grid(variable ~ Method,scales = "free_y",) + 
+  facet_grid(variable ~ Method,scales = "free_y",labeller = as_labeller(expression()) + 
   scale_color_grey(start=0.0,end=0.2) + labs(title=dataset[1],x="",y="") + 
   geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="bottom", axis.title.x=element_blank(),
                                                                                                    axis.text.x=element_blank(),
@@ -152,6 +154,21 @@ p2 <- ggplot(data = subset(datos,Attributes==att[2]), aes(x=Method,y=value,color
   geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="none")
 
 multiplot(p1,p2,cols=1)
+
+#Time dataset, selection, method
+
+
+ggplot(data = subset(datos,variable=="TIME"), aes(x=Method,y=value)) + geom_point(stat="identity",size=3) + 
+  facet_grid(Dataset ~ Attributes,scales = "free_y") + 
[…]

### 2016-09-03 Tables_to_figures/generador.r
Commented unused plots in R file

@@ -3,45 +3,6 @@ library(reshape2)
 library(ggplot2)
 
 
-#Multiplot
-multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
-  library(grid)
-  
-  # Make a list from the ... arguments and plotlist
-  plots <- c(list(...), plotlist)
-  
-  numPlots = length(plots)
-  
-  # If layout is NULL, then use 'cols' to determine layout
-  if (is.null(layout)) {
-    # Make the panel
-    # ncol: Number of columns of plots
-    # nrow: Number of rows needed, calculated from # of cols
-    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
-                     ncol = cols, nrow = ceiling(numPlots/cols))
-  }
-  
-  if (numPlots==1) {
-    print(plots[[1]])
-    
-  } else {
-    # Set up the page
-    grid.newpage()
-    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
-    
-    # Make each plot, in the correct location
-    for (i in 1:numPlots) {
-      # Get the i,j matrix positions of the regions that contain this subplot
-      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
-      
-      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
-                                      layout.pos.col = matchidx$col))
-    }
-  }
-}
-
-
-
 filenames_all <- list.files(path = "datasets/AllAttributes/",pattern = ".csv",full.names = TRUE)
 ldf <- lapply(filenames_all, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
 for(i in seq(from=1,to=length(filenames_all),by = 1)){
@@ -64,12 +25,6 @@ for(i in seq(from=1,to=length(filenames_som),by = 1)){
   ldf_som[[i]]$Attributes <- "SOM-FS"
 }
 
-filenames_som <- list.files(path = "datasets/SOM-FS//",pattern = ".csv",full.names = TRUE)
-ldf_som <- lapply(filenames_som, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
-for(i in seq(from=1,to=length(filenames_som),by = 1)){
[…]

### 2016-09-03 Tables_to_figures/generador.r
Added files in EPS and PNG

@@ -77,11 +77,11 @@ dataset = unique(datos$Dataset)
 for(i in dataset){
   print(ggplot(data = subset(datos,Dataset==i), aes(x=Attributes,y=value,fill=Attributes,shape=Attributes)) + geom_point(size=2) + geom_bar(stat="identity") + 
     facet_grid(variable ~ Method,scales = "free_y") + 
-    scale_fill_grey(start=0.2,end=0.6) + labs(title=i,x="",y="") + 
+    scale_fill_grey(start=0.6,end=0.8) + labs(title=i,x="",y="") + 
     geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.5,size=0.5) + theme_bw()  + theme(legend.position="bottom", axis.title.x=element_blank(),
                                                                                                     axis.text.x=element_blank(),
                                                                                              axis.ticks.x=element_blank()))
-  ggsave(file=paste0("../imgs/datasets_",i,".png"),scale=1.2)
+  ggsave(file=paste0("../imgs/datasets_",i,".eps"),scale=2,units = "cm", width = 16, height = 8,dpi = 800)
   
 }
 
@@ -98,7 +98,7 @@ print(ggplot(data = subset(datos,Attributes==j & Dataset==i), aes(x=Method,y=val
   scale_color_grey(start=0.0,end=0.2) + labs(title="",x="",y="") + 
   geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="none"))
 
-  ggsave(file=paste0("../imgs/attribute_",j,".png"),scale=1.2)
+  ggsave(file=paste0("../imgs/attribute_",j,".eps"),scale=2,units = "cm", width = 8, height = 12,dpi = 800)
 
   }
 
@@ -113,7 +113,7 @@ for(i in var){
     geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="bottom")
   
   
-  ggsave(file=paste0("../imgs/metric_",i,".png"),scale=1.2)
+  ggsave(file=paste0("../imgs/metric_",i,".eps"),scale=2.5,units = "cm", width = 16, height = 8,dpi = 800)
 }
 
 

### 2016-09-04 paper.tex
closing the issue about moving tables to the appendix: Closes #53

@@
 
+\begin{figure*}[ht]
+\begin{center}
+\includegraphics[scale=0.25]{som_planes.eps}
+\end{center}
+\caption{U-matrix and component planes.}
+\label{fig:componentplanes}
+\end{figure*}
+
+\begin{table*}
+\caption{Input features/variables selected by each method
+\label{tab:features_selected}}
+\centering{}%
+\begin{tabular}{|c|c|c|c|c|}
+\hline 
+No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
+\hline 
+1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+2 & \texttt{subject1} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
+\hline 
+3 &  \texttt{collection} &  &  & \\
+\hline 
+4 & \texttt{binding} &  &  & \\
+\hline 
+5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
+\hline 
+7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
+\hline 
+9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+10 & \texttt{print\_run} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
+\hline 
+\end{tabular}
+\end{table*}
+
 Figure \ref{fig:componentplanes} shows the U-matrix along with the component planes analysis resulted from SOM training. The term component refers in SOM to a variable or feature of the problem.
@@
 
-\begin{figure*}[ht]
-\begin{center}
-\includegraphics[scale=0.28]{som_planes.eps}
-\end{center}
-\caption{U-matrix and component planes.}
-\label{fig:componentplanes}
-\end{figure*}
-
 The selected features using each one of the three methods are shown in 
@@
 \begin{table*}
-\caption{Input features/variables selected by each method
-\label{tab:features_selected}}
 \centering{}%
-\begin{tabular}{|c|c|c|c|c|}
-\hline 
-No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
-\hline 
-1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-2 & \texttt{subject1} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
-\hline 
-3 &  \texttt{collection} &  &  & \\
-\hline 
-4 & \texttt{binding} &  &  & \\
-\hline 
-5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
-\hline 
-7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
-\hline 
-9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-10 & \texttt{print\_run} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
-\hline 
-\end{tabular}
+\caption{Predicting Total sales for all publishers based on features selected
+by each method. Best values in bold.
+\label{tab:results_all_publishers_fs}}
+% RELIEFATTRIBUTEEVAL
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
+\hline 
+kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
+\hline 
+RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
+\hline 
+LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
+\hline 
+SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
+\hline  
+MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
+\hline  
+ELM & 	87.55	 $\pm$ 	0.1	 & 	250.88	 $\pm$ 	28.78	 & 	677.94	 $\pm$ 	356.41	 & 	44.16	 $\pm$ 	0.05	 & 	50.86	 $\pm$ 	0.24	 & 	0.1106	 $\pm$ 	0.02\\
+\hline
+
+\end{tabular}
+}
+% CFSSUBEVAL
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
+\hline
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
+\hline 
+kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
+\hline 
+RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
+\hline 
+LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
+\hline 
+SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
+\hline
+MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
+\hline
+ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
+\hline
+
+\end{tabular}
+}
+% SOM
+\centering{}% SOM
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
+\hline 
+ &  $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
+\hline 
+kNN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
+\hline 
+RF &  \textbf{89.8 $\pm$0.05}  &  \textbf{211.87 $\pm$20.07}  &  \textbf{617.78 $\pm$187.16}  &  \textbf{37.02 $\pm$2.46}  &  \textbf{46.58 $\pm$11.14}  & 2.93 $\pm$0.11\tabularnewline
+\hline 
+LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
+\hline 
+SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
+\hline 
+MLP	& 84.3 $\pm$ 0.12	& 388.79 $\pm$ 274.18	& 851.01 $\pm$ 422.03	& 68.26 $\pm$ 49.64	& 65.85 $\pm$ 36.49	& 3.29 $\pm$ 0.042\tabularnewline
+\hline
+ELM & 	85.3	 $\pm$ 	0.09	 & 	301.42	 $\pm$ 	31.43	 & 	704.9	 $\pm$ 	221.83	 & 	53.22	 $\pm$ 	0.07	 & 	54.57	 $\pm$ 	0.18	 & 	0.0229	 $\pm$ 	0.02\\
+\hline
+\end{tabular}
+}
 \end{table*}
@@
 
-\begin{table*}
-\centering{}%
-\caption{Predicting Total sales for all publishers based on features selected
-by each method. Best values in bold.
-\label{tab:results_all_publishers_fs}}
-% RELIEFATTRIBUTEEVAL
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
-\hline 
- & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
-\hline 
-kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
-\hline 
-RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
-\hline 
-LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
-\hline 
-SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
-\hline  
-MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
-\hline  
-ELM & 	87.55	 $\pm$ 	0.1	 & 	250.88	 $\pm$ 	28.78	 & 	677.94	 $\pm$ 	356.41	 & 	44.16	 $\pm$ 	0.05	 & 	50.86	 $\pm$ 	0.24	 & 	0.1106	 $\pm$ 	0.02\\
-\hline
-
-\end{tabular}
-}
-% CFSSUBEVAL
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
-\hline
- & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
-\hline 
-kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
-\hline 
-RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
-\hline 
-LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
-\hline 
-SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
-\hline
-MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
-\hline
-ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
-\hline
-
-\end{tabular}
-}
-% SOM
-\centering{}% SOM
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
-\hline 
- &  $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
-\hline 
-kNN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
-\hline 
-RF &  \textbf{89.8 $\pm$0.05}  &  \textbf{211.87 $\pm$20.07}  &  \textbf{617.78 $\pm$187.16}  &  \textbf{37.02 $\pm$2.46}  &  \textbf{46.58 $\pm$11.14}  & 2.93 $\pm$0.11\tabularnewline
-\hline 
-LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
-\hline 
-SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
-\hline 
-MLP	& 84.3 $\pm$ 0.12	& 388.79 $\pm$ 274.18	& 851.01 $\pm$ 422.03	& 68.26 $\pm$ 49.64	& 65.85 $\pm$ 36.49	& 3.29 $\pm$ 0.042\tabularnewline
-\hline
-ELM & 	85.3	 $\pm$ 	0.09	 & 	301.42	 $\pm$ 	31.43	 & 	704.9	 $\pm$ 	221.83	 & 	53.22	 $\pm$ 	0.07	 & 	54.57	 $\pm$ 	0.18	 & 	0.0229	 $\pm$ 	0.02\\
-\hline
-\end{tabular}
-}
-\end{table*}
-
 %********************************************************************************
@@
 
-The experiments applied on the selected special cases follow the same methodology used previously for the whole dataset.
-First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (RFE, CSE and SOM) are used to reduce the set of features in each case.
-Second, the regression models are applied again on the reduced datasets to evaluate their performance.
-
-Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases are shown in Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}.
-The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}.
+\begin{figure*}[ht]
+\begin{center}
+\includegraphics[scale=0.55]{./imgs/attribute_All.eps}
+\end{center}
+\caption{Predicting \texttt{total\_sales} for publishing companies UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).}
+\label{fig:attributeAll}
+\end{figure*}
+
+The experiments applied on the selected special cases follow the same methodology 
+used previously for the whole dataset. First, the forecasting models are applied 
+on each dataset using all features, then, the three feature selection methods 
+(RFE, CSE and SOM) are used to reduce the set of features in each case. 
+Second, the regression models are applied again on the reduced datasets to 
+evaluate their performance.
+
+Evaluation results of the obtained models (without performing any feature selection 
+method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
+(detailed numeric results can be shown in Tables \ref{Table:case1results} to \ref{Table:case4results} 
+in the appendix of tables at the end of this paper).
+Results in this Figure show that the models performed similarly to the case of 
+the global models for all publishers, which were previously presented in 
+Table \ref{tab:all_publishers_no_fs}. 
+In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR. 
+In the case of Best selling publisher houses (i.e. UDL929) and publishers who 
+publish wide range of different books (i.e. UDL704), M5P could be recommended 
+as it shows more accurate forecasting results than the other models. 
+While in the case of medium sized publishers, in terms of sales and number 
+of published books, the RF model would be adequate.
+
+% tables have been moved to the Appendix and they have been substituted by the new Figure. Comments (text) have been adapted accordingly  -  [pedro]
+%Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}. 
+%The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}.
 In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR.
@@
 
-\begin{table*}
-\caption{Predicting Total sales for publishing company UDL929 (The best selling publishing company). Best values in bold. }
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P  &  \textbf{90.0 $\pm$0.10} &  \textbf{670.24 $\pm$181.05}  &  \textbf{1065.34 $\pm$413.84}  &  \textbf{40.83 $\pm$10.86}  &  \textbf{43.56 $\pm$19.87}  & 0.03 $\pm$0.002\tabularnewline
-\hline 
-kNN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
-\hline 
-RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
-\hline 
-LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
-\hline 
-SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
-\hline 
-MLP	& 84.42 $\pm$ 0.12	& 1105.61 $\pm$ 445.66	& 1776.68 $\pm$ 1148.31	& 66.52 $\pm$ 23.63	& 70.41 $\pm$ 41.88	& 1.65 $\pm$ 0.008 \tabularnewline
-\hline
-ELM & 	53.38	 $\pm$ 	0.24	 & 	1898.17	 $\pm$ 	728.63	 & 	3104.85	 $\pm$ 	1503.83	 & 	136.82	 $\pm$ 	0.76	 & 	146.75	 $\pm$ 	0.95	 & 	0.0184	 $\pm$ 	0.02
- \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case1results}
-\end{table*}
-
-\begin{table*}
-\caption{Predicting Total sales for publishing company UDLW12 (The median selling publishing company). Best values in bold. }
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
-\hline 
-kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
-\hline 
-LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
-\hline 
-SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
-\hline 
-MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
-\hline
-ELM & 	60.52	 $\pm$ 	0.39	 & 	24.28	 $\pm$ 	13.57	 & 	38.83	 $\pm$ 	26.43	 & 	118.09	 $\pm$ 	1.35	 & 	131.51	 $\pm$ 	1.37	 & 	0.0036	 $\pm$ 	0.01 \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case2results}
-\end{table*}
-
-\begin{table*}
-\caption{Predicting Total sales for publishing company UDL704 (highest number of different titles sold). Best values in bold.}
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- &  $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
-\hline 
-kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
-\hline 
-LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
-\hline 
-SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
-\hline 
-MLP	& 80.83 $\pm$ 0.12	& 122.8 $\pm$ 56.86	& 207.12 $\pm$ 100.44	& 67.13 $\pm$ 31.38	& 78.14 $\pm$ 39.92	& 2.83 $\pm$ 0.012\tabularnewline
-\hline
-ELM & 	65.13	 $\pm$ 	0.21	 & 	336.33	 $\pm$ 	1414.85	 & 	1279.83	 $\pm$ 	7128.87	 & 	189.38	 $\pm$ 	7.49	 & 	501.38	 $\pm$ 	26.56	 & 	0.0042	 $\pm$ 	0.01
- \tabularnewline
-\hline
-
-\end{tabular}
-}
-\label{Table:case3results}
-\end{table*}
-
-\begin{table*}
-\caption{Predicting Total sales for publishing company UDLU11 (medium number of different books sold)). Best values in bold.}
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
-\hline 
-kNN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
-\hline 
-RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
-\hline 
-LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
-\hline 
-SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
-\hline 
-MLP	& 76.49 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
-\hline
-ELM & 	61.55	 $\pm$ 	0.24	 & 	1350.19	 $\pm$ 	3934.54	 & 	3681.73	 $\pm$ 	19380.44	 & 	140.16	 $\pm$ 	3.02	 & 	264.72	 $\pm$ 	10.87	 & 	0.009	 $\pm$ 	0.02
- \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case4results}
-\end{table*}
-
 %--------------------------------------------------------------------------
-
 %\subsection{Sales forecasting with feature selection}
 %\label{subsec:case_sales_feature_selection}
-
-%***TO DO***: explain we have chosen the best Feature selection method (ReliefAttributeEval???). The rest of tables have been moved to an appendix.
-%Sam will do it - JJ
 
@@
 targets, might in fact include different factors or have different
-leverage when deciding how much to print. For clarity purpose, we present 
-here only the results after applying the RFE method for the four cases in Tables
-\ref{Table:case1results-RAE}, \ref{Table:case2results-RAE},
-\ref{Table:case3results-RAE} and \ref{Table:case4results-RAE}, this
-one was chosen since the selected features by this
-method showed in the previous experiment the highest predictive power among 
-all classifiers. 
-% Antonio - could we use any sinonym of classifier but for regression... I guess 'regressor' is not appropriate. :D
-%
-%According to the aforementioned tables, 
-%It's not according to a table. It's according to the results there - JJ
-RFE reduction has noticeably improved the performance of all classifiers 
+leverage when deciding how much to print. 
+For clarity purpose, obtained results have been shown in Tables
+\ref{Table:case1results-RAE} to \ref{Table:case4resultsSOMFS}
+in the appendix of tables at the end of this paper.
+In those tables it can be seen that, as in the previous experiment, the highest 
+predictive power is exhibited by RFE over CSE and SOM feature selection methods.
+In this sense, RFE reduction has noticeably improved the performance of all models, 
 specially in the case of the best selling publisher house (i.e. UDL929) and the 
 publisher which publishes a wide range of different books (i.e. UDL704).
-For the rest of the results which are obtained by CSE and SOM feature selection 
-methods we refer the reader to the appendix of tables at the end of this paper.
-
-\begin{table*}[!ht]
-% Why the capital in Total? If it's a variable use Small Caps or Sans
-% Serif - JJ
-\caption{Predicting Total sales for publishing company UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P &  \textbf{90.5 $\pm$0.1} &  \textbf{661.81 $\pm$186.17} &  \textbf{1070.24 $\pm$425.66} &  \textbf{40.18 $\pm$10.50} &  \textbf{43.56 $\pm$19.77} & 0.02 $\pm$0.002\tabularnewline
-\hline 
-kNN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
-\hline 
-LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
-\hline 
-MLP	& 87.66 $\pm$ 0.14	& 897.02 $\pm$ 411.58	& 1332.54 $\pm$ 969.05	& 56.43 $\pm$ 33.1	& 58.52 $\pm$ 57.68	& 0.17 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	84.08	 $\pm$ 	0.17	 & 	890.49	 $\pm$ 	343.61	 & 	1470.33	 $\pm$ 	993.74	 & 	61.76	 $\pm$ 	0.32	 & 	65.14	 $\pm$ 	0.5	 & 	0.0119	 $\pm$ 	0.02 \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case1results-RAE}
-\end{table*}
-
-\begin{table*}[!ht]
-\caption{Predicting Total sales for publishing company UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
-\hline 
-kNN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
-\hline 
-RF &  \textbf{86.7 $\pm$0.16} & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
-\hline 
-LR & 84.4 $\pm$0.25 &  \textbf{12.79 $\pm$6.65} &  \textbf{21.52 $\pm$12.54} & 39.47 $\pm$23.35 &  \textbf{50.14 $\pm$35.26} & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 &  \textbf{38.24 $\pm$15.41} & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
-\hline 
-MLP	& 79.26 $\pm$ 0.27	& 20.28 $\pm$ 13.25	& 35.05 $\pm$ 29.44	& 61.89 $\pm$ 37.64	& 81.51 $\pm$ 63.39	& 0.07 $\pm$ 0.002\tabularnewline
-\hline 
-ELM & 	70.58	 $\pm$ 	0.34	 & 	19.52	 $\pm$ 	9.91	 & 	30.49	 $\pm$ 	18.09	 & 	145.28	 $\pm$ 	2.94	 & 	167.8	 $\pm$ 	3.39	 & 	0.0027	 $\pm$ 	0.01 \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case2results-RAE}
-\end{table*}
-
-\begin{table*}[!ht]
-\caption{Predicting Total sales for publishing company UDL704 (ReliefFAttributeEval-FS). Best values in bold. }
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P  &  \textbf{89.3 $\pm$0.08}  &  \textbf{69.70 $\pm$19.85}  &  \textbf{122.48 $\pm$47.28}  & {38.49 $\pm$11.53}  &  \textbf{46.68 $\pm$16.02} & 0.028 $\pm$0.003\tabularnewline
-\hline 
-kNN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
-\hline 
-LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
-\hline 
-SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
-\hline 
-MLP	& 84.11 $\pm$ 0.13	& 104.55 $\pm$ 50.32	& 180.42 $\pm$ 87.44	& 56.99 $\pm$ 26.01	& 67.68 $\pm$ 32.15	& 0.22 $\pm$ 0.003\tabularnewline
-\hline
-ELM & 	83.47	 $\pm$ 	0.1	 & 	89.65	 $\pm$ 	25.9	 & 	167.99	 $\pm$ 	82.63	 & 	51.51	 $\pm$ 	0.14	 & 	65.11	 $\pm$ 	0.28	 & 	0.0041	 $\pm$ 	0.01\tabularnewline
-\hline
-
-\end{tabular}
-}
-\label{Table:case3results-RAE}
-\end{table*}
-
-\begin{table*}[!ht]
-\caption{Predicting Total sales for publishing company UDLU11 (ReliefFAttributeEval-FS). Best values in bold.}
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
- & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
-\hline 
-\hline 
-M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
-\hline 
-kNN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF &  \textbf{85.3 $\pm$0.09} &  \textbf{455.7 $\pm$123.96} &  \textbf{686.54 $\pm$198.16} &  \textbf{46.32 $\pm$10.20} &  \textbf{53.03 $\pm$13.05} & 0.07 $\pm$0.003\tabularnewline
-\hline 
-LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 77.3 $\pm$ 0.13	& 709.2 $\pm$ 235.87	& 960.43 $\pm$ 345.28	& 73.11 $\pm$ 24.95	& 75.19 $\pm$ 25.74	& 0.14 $\pm$ 0.003\tabularnewline
-\hline
-ELM & 	79.73	 $\pm$ 	0.14	 & 	569.2	 $\pm$ 	161.37	 & 	841.75	 $\pm$ 	322.13	 & 	61.87	 $\pm$ 	0.21	 & 	69.99	 $\pm$ 	0.3	 & 	0.007	 $\pm$ 	0.02 \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case4results-RAE}
-\end{table*}
+
+% tables have been moved to the Appendix and they have been substituted by the new Figure. Comments (text) have been adapted accordingly  -  [pedro]
+%For clarity purpose, we present here only the results after applying the RFE method for the four cases in Tables \ref{Table:case1results-RAE}, \ref{Table:case2results-RAE}, \ref{Table:case3results-RAE} and \ref{Table:case4results-RAE}, this one was chosen since the selected features by this method showed in the previous experiment the highest predictive power among  all classifiers.
+%RFE reduction has noticeably improved the performance of all classifiers specially in the case of the best selling publisher house (i.e.
+UDL929) and the publisher which publishes a wide range of different books (i.e.
+UDL704).
+For the rest of the results which are obtained by CSE and SOM feature selection methods we refer the reader to the appendix of tables at the end of this paper.
 
@@
 
-\begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDL704 (CfsSubsetEval-FS). Best values in bold.}
+%--------------- old Tables 7, 8, 9, 10 (before revision)
+
+\begin{table*}
+\caption{Predicting \texttt{total\_sales} for publishing company UDL929 (the best selling publishing company). Best values in bold. }
 \centering{}%
@@
 \hline 
-M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
-\hline 
-kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & \textbf{170.83 $\pm$46.34} & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
-\hline 
-LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & \textbf{81.8 $\pm$0.08} & \textbf{94.29 $\pm$25.52} & 180.54 $\pm$62.67 & \textbf{50.79 $\pm$8.48} & \textbf{65.62 $\pm$6.25} & 0.040 $\pm$0.02\tabularnewline
-\hline 
-MLP	& 81.28 $\pm$ 0.11	& 135.01 $\pm$ 56.89	& 193.56 $\pm$ 61.91	& 74.12 $\pm$ 31.58	& 75.43 $\pm$ 28.35	& 0.05 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	78.42	 $\pm$ 	0.15	 & 	109.24	 $\pm$ 	52.6	 & 	203.11	 $\pm$ 	215.35	 & 	62.28	 $\pm$ 	0.24	 & 	78.75	 $\pm$ 	0.68	 & 	0.0019	 $\pm$ 	0.01 \tabularnewline
+M5P  &  \textbf{90.0 $\pm$0.10} &  \textbf{670.24 $\pm$181.05}  &  \textbf{1065.34 $\pm$413.84}  &  \textbf{40.83 $\pm$10.86}  &  \textbf{43.56 $\pm$19.87}  & 0.03 $\pm$0.002\tabularnewline
+\hline 
+kNN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
+\hline 
+RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
+\hline 
+LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
+\hline 
+MLP	& 84.42 $\pm$ 0.12	& 1105.61 $\pm$ 445.66	& 1776.68 $\pm$ 1148.31	& 66.52 $\pm$ 23.63	& 70.41 $\pm$ 41.88	& 1.65 $\pm$ 0.008 \tabularnewline
+\hline
+ELM & 	53.38	 $\pm$ 	0.24	 & 	1898.17	 $\pm$ 	728.63	 & 	3104.85	 $\pm$ 	1503.83	 & 	136.82	 $\pm$ 	0.76	 & 	146.75	 $\pm$ 	0.95	 & 	0.0184	 $\pm$ 	0.02
+ \tabularnewline
 \hline
@@
 }
+\label{Table:case1results}
 \end{table*}
 
-\begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDL704 (SOM-FS). Best values in bold.}
+\begin{table*}
+\caption{Predicting \texttt{total\_sales} for publishing company UDLW12 (the median selling publishing company). Best values in bold. }
 \centering{}%
@@
 \hline 
-M5P & \textbf{89.2 $\pm$0.07} & \textbf{71.536 $\pm$18.95} & \textbf{123.06 $\pm$42.13} & \textbf{39.43 $\pm$10.58} & \textbf{47.20 $\pm$15.16} & 0.031 $\pm$0.007\tabularnewline
-\hline 
-kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
-\hline 
-LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
-\hline 
-MLP	& 87.25 $\pm$ 0.09	& 98.45 $\pm$ 46.65	& 156.48 $\pm$ 62.89	& 53.68 $\pm$ 23.35	& 59.5 $\pm$ 22.56	& 0.15 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	85.22	 $\pm$ 	0.11	 & 	85.57	 $\pm$ 	25.92	 & 	141.17	 $\pm$ 	62.02	 & 	49.48	 $\pm$ 	0.16	 & 	56.58	 $\pm$ 	0.25	 & 	0.0014	 $\pm$ 	0.01\tabularnewline
+M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
+\hline 
+kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
+\hline 
+LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
+\hline 
+SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
+\hline
+ELM & 	60.52	 $\pm$ 	0.39	 & 	24.28	 $\pm$ 	13.57	 & 	38.83	 $\pm$ 	26.43	 & 	118.09	 $\pm$ 	1.35	 & 	131.51	 $\pm$ 	1.37	 & 	0.0036	 $\pm$ 	0.01 \tabularnewline
 \hline
@@
 }
+\label{Table:case2results}
 \end{table*}
 
-%-----------------------------------
-
-\begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.}
+\begin{table*}
+\caption{Predicting \texttt{total\_sales} for publishing company UDL704 (highest number of different titles sold). Best values in bold.}
 \centering{}%
@@
 \hline 
-M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
-\hline 
-kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & \textbf{1008.39 $\pm$305.87} & 71.41 $\pm$13.95 & \textbf{78.47 $\pm$22.70} & \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF & 65.3 $\pm$0.19 & \textbf{685.56 $\pm$195.28} & 1021.37 $\pm$352.88 & \textbf{69.74 $\pm$16.96} & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
-\hline 
-LR & \textbf{67.0 $\pm$0.23}\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 66.09 $\pm$ 0.21	& 817.79 $\pm$ 242.44	& 1127.02 $\pm$ 381.75	& 84.48 $\pm$ 27.39	& 88.59 $\pm$ 33.21	& 0.03 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	65.66	 $\pm$ 	0.25	 & 	859.21	 $\pm$ 	836.34	 & 	1691.61	 $\pm$ 	3053.2	 & 	92.4	 $\pm$ 	0.81	 & 	134.53	 $\pm$ 	2.18	 & 	0.0009	 $\pm$ 	0.01 \tabularnewline
-\hline
+M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
+\hline 
+kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
+\hline 
+LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
+\hline 
+MLP	& 80.83 $\pm$ 0.12	& 122.8 $\pm$ 56.86	& 207.12 $\pm$ 100.44	& 67.13 $\pm$ 31.38	& 78.14 $\pm$ 39.92	& 2.83 $\pm$ 0.012\tabularnewline
+\hline
+ELM & 	65.13	 $\pm$ 	0.21	 & 	336.33	 $\pm$ 	1414.85	 & 	1279.83	 $\pm$ 	7128.87	 & 	189.38	 $\pm$ 	7.49	 & 	501.38	 $\pm$ 	26.56	 & 	0.0042	 $\pm$ 	0.01
+ \tabularnewline
+\hline
+
 \end{tabular}
 }
+\label{Table:case3results}
 \end{table*}
 
-\begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS). Best values in bold.}
+\begin{table*}
+\caption{Predicting \texttt{total\_sales} for publishing company UDLU11 (medium number of different books sold). Best values in bold.}
 \centering{}%
@@
 \hline 
-M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
-\hline 
-kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & \textbf{0 $\pm$0.0002}\tabularnewline
-\hline 
-RF & \textbf{85.6 $\pm$0.08} & \textbf{446.25 $\pm$119.79} & \textbf{673.46 $\pm$189.06} & \textbf{45.38 $\pm$9.78} & \textbf{52.24 $\pm$13.09} & 0.0594 $\pm$0.0049\tabularnewline
-\hline 
-LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 77.06 $\pm$ 0.18	& 714.48 $\pm$ 259.22	& 1025.29 $\pm$ 569.79	& 74.3 $\pm$ 29.92	& 81.44 $\pm$ 47.9	& 0.09 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	79.52	 $\pm$ 	0.12	 & 	606.38	 $\pm$ 	153.83	 & 	818.18	 $\pm$ 	243.54	 & 	65.7	 $\pm$ 	0.18	 & 	67.17	 $\pm$ 	0.21	 & 	0.0044	 $\pm$ 	0.01 \tabularnewline
+M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
+\hline 
+kNN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
+\hline 
+RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
+\hline 
+LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 76.49 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
+\hline
+ELM & 	61.55	 $\pm$ 	0.24	 & 	1350.19	 $\pm$ 	3934.54	 & 	3681.73	 $\pm$ 	19380.44	 & 	140.16	 $\pm$ 	3.02	 & 	264.72	 $\pm$ 	10.87	 & 	0.009	 $\pm$ 	0.02
+ \tabularnewline
 \hline
@@
 }
+\label{Table:case4results}
 \end{table*}
 
-%-----------------------------------
+%--------------- old Tables 11, 12, 13, 14 (before revision)
 
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for publishing company UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%
@@
 \hline 
-M5P & \textbf{88.0 $\pm$0.13} & \textbf{738.28 $\pm$188.53} & \textbf{1141.79 $\pm$472.025} & \textbf{45.45 $\pm$13.62} & \textbf{47.58 $\pm$24.84} & 0.017 $\pm$0.002\tabularnewline
-\hline 
-kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
-\hline 
-LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
-\hline 
-MLP	& 87.67 $\pm$ 0.12	& 947.71 $\pm$ 388.67	& 1294.58 $\pm$ 458.44	& 58.62 $\pm$ 27.65	& 54.89 $\pm$ 27.53	& 0.04 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	87.25	 $\pm$ 	0.14	 & 	776.49	 $\pm$ 	209.23	 & 	1171.43	 $\pm$ 	455.5	 & 	53.63	 $\pm$ 	0.25	 & 	53.14	 $\pm$ 	0.37	 & 	0.0031	 $\pm$ 	0.01\tabularnewline
+M5P &  \textbf{90.5 $\pm$0.1} &  \textbf{661.81 $\pm$186.17} &  \textbf{1070.24 $\pm$425.66} &  \textbf{40.18 $\pm$10.50} &  \textbf{43.56 $\pm$19.77} & 0.02 $\pm$0.002\tabularnewline
+\hline 
+kNN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
+\hline 
+LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
+\hline 
+MLP	& 87.66 $\pm$ 0.14	& 897.02 $\pm$ 411.58	& 1332.54 $\pm$ 969.05	& 56.43 $\pm$ 33.1	& 58.52 $\pm$ 57.68	& 0.17 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	84.08	 $\pm$ 	0.17	 & 	890.49	 $\pm$ 	343.61	 & 	1470.33	 $\pm$ 	993.74	 & 	61.76	 $\pm$ 	0.32	 & 	65.14	 $\pm$ 	0.5	 & 	0.0119	 $\pm$ 	0.02 \tabularnewline
 \hline
@@
 }
+\label{Table:case1results-RAE}
 \end{table*}
@@
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for publishing company UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%
@@
 \hline 
-M5P & \textbf{89.7 $\pm$0.10} & \textbf{685.67 $\pm$185.99} & \textbf{1116.42 $\pm$478.06} & \textbf{42.09 $\pm$12.8} & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
-\hline 
-kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & \textbf{46.25 $\pm$14.41} & \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
-\hline 
-LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
-\hline 
-MLP	& 87.02 $\pm$ 0.13	& 1015.85 $\pm$ 518.44	& 1603.91 $\pm$ 1145.56	& 61.99 $\pm$ 32.97	& 67.74 $\pm$ 62.08	& 0.11 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	83.44	 $\pm$ 	0.17	 & 	884.83	 $\pm$ 	297.95	 & 	1430.42	 $\pm$ 	874.32	 & 	64.61	 $\pm$ 	0.37	 & 	69.69	 $\pm$ 	0.68	 & 	0.002	 $\pm$ 	0.01\tabularnewline
+M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
+\hline 
+kNN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
+\hline 
+RF &  \textbf{86.7 $\pm$0.16} & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
+\hline 
+LR & 84.4 $\pm$0.25 &  \textbf{12.79 $\pm$6.65} &  \textbf{21.52 $\pm$12.54} & 39.47 $\pm$23.35 &  \textbf{50.14 $\pm$35.26} & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 &  \textbf{38.24 $\pm$15.41} & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
+\hline 
+MLP	& 79.26 $\pm$ 0.27	& 20.28 $\pm$ 13.25	& 35.05 $\pm$ 29.44	& 61.89 $\pm$ 37.64	& 81.51 $\pm$ 63.39	& 0.07 $\pm$ 0.002\tabularnewline
+\hline 
+ELM & 	70.58	 $\pm$ 	0.34	 & 	19.52	 $\pm$ 	9.91	 & 	30.49	 $\pm$ 	18.09	 & 	145.28	 $\pm$ 	2.94	 & 	167.8	 $\pm$ 	3.39	 & 	0.0027	 $\pm$ 	0.01 \tabularnewline
 \hline
@@
 }
+\label{Table:case2results-RAE}
 \end{table*}
 
-%-----------------------------------
-
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for publishing company UDL704 (ReliefFAttributeEval-FS). Best values in bold. }
 \centering{}%
@@
 \hline 
-M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
-\hline 
-kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 75.1 $\pm$0.26 & \textbf{15.61 $\pm$7.19} & 26.83 $\pm$13.36 & \textbf{47.38 $\pm$20.10} & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
-\hline 
-LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & \textbf{25.49 $\pm$11.63} & 47.97 $\pm$18.85 & \textbf{60.28 $\pm$30.62} & 0.0002 $\pm$0.0004\tabularnewline
-\hline 
-SVM & \textbf{81.8 $\pm$0.21} & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 80.08 $\pm$ 0.25	& 19.6 $\pm$ 11.66	& 29.32 $\pm$ 14.5	& 59.97 $\pm$ 35.66	& 70.05 $\pm$ 42.31	& 0.02 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	77.62	 $\pm$ 	0.3	 & 	16.53	 $\pm$ 	9.12	 & 	27.18	 $\pm$ 	18.2	 & 	72.75	 $\pm$ 	0.64	 & 	86.09	 $\pm$ 	0.86	 & 	0.0012	 $\pm$ 	0.01\tabularnewline
-
-\hline
+M5P  &  \textbf{89.3 $\pm$0.08}  &  \textbf{69.70 $\pm$19.85}  &  \textbf{122.48 $\pm$47.28}  & {38.49 $\pm$11.53}  &  \textbf{46.68 $\pm$16.02} & 0.028 $\pm$0.003\tabularnewline
+\hline 
+kNN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
+\hline 
+LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
+\hline 
+SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 84.11 $\pm$ 0.13	& 104.55 $\pm$ 50.32	& 180.42 $\pm$ 87.44	& 56.99 $\pm$ 26.01	& 67.68 $\pm$ 32.15	& 0.22 $\pm$ 0.003\tabularnewline
+\hline
+ELM & 	83.47	 $\pm$ 	0.1	 & 	89.65	 $\pm$ 	25.9	 & 	167.99	 $\pm$ 	82.63	 & 	51.51	 $\pm$ 	0.14	 & 	65.11	 $\pm$ 	0.28	 & 	0.0041	 $\pm$ 	0.01\tabularnewline
+\hline
+
 \end{tabular}
 }
+\label{Table:case3results-RAE}
 \end{table*}
@@
 \begin{table*}[!ht]
-\caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for publishing company UDLU11 (ReliefFAttributeEval-FS). Best values in bold.}
 \centering{}%
@@
 \hline 
+M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
+\hline 
+kNN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF &  \textbf{85.3 $\pm$0.09} &  \textbf{455.7 $\pm$123.96} &  \textbf{686.54 $\pm$198.16} &  \textbf{46.32 $\pm$10.20} &  \textbf{53.03 $\pm$13.05} & 0.07 $\pm$0.003\tabularnewline
+\hline 
+LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 77.3 $\pm$ 0.13	& 709.2 $\pm$ 235.87	& 960.43 $\pm$ 345.28	& 73.11 $\pm$ 24.95	& 75.19 $\pm$ 25.74	& 0.14 $\pm$ 0.003\tabularnewline
+\hline
+ELM & 	79.73	 $\pm$ 	0.14	 & 	569.2	 $\pm$ 	161.37	 & 	841.75	 $\pm$ 	322.13	 & 	61.87	 $\pm$ 	0.21	 & 	69.99	 $\pm$ 	0.3	 & 	0.007	 $\pm$ 	0.02 \tabularnewline
+\hline
+\end{tabular}
+}
+\label{Table:case4results-RAE}
+\end{table*}
+
+%--------------- Tables in the Appendix
+
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL704 (CfsSubsetEval-FS). Best values in bold.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
+\hline 
+kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & \textbf{170.83 $\pm$46.34} & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
+\hline 
+LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & \textbf{81.8 $\pm$0.08} & \textbf{94.29 $\pm$25.52} & 180.54 $\pm$62.67 & \textbf{50.79 $\pm$8.48} & \textbf{65.62 $\pm$6.25} & 0.040 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 81.28 $\pm$ 0.11	& 135.01 $\pm$ 56.89	& 193.56 $\pm$ 61.91	& 74.12 $\pm$ 31.58	& 75.43 $\pm$ 28.35	& 0.05 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	78.42	 $\pm$ 	0.15	 & 	109.24	 $\pm$ 	52.6	 & 	203.11	 $\pm$ 	215.35	 & 	62.28	 $\pm$ 	0.24	 & 	78.75	 $\pm$ 	0.68	 & 	0.0019	 $\pm$ 	0.01 \tabularnewline
+\hline
+\end{tabular}
+}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL704 (SOM-FS). Best values in bold.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & \textbf{89.2 $\pm$0.07} & \textbf{71.536 $\pm$18.95} & \textbf{123.06 $\pm$42.13} & \textbf{39.43 $\pm$10.58} & \textbf{47.20 $\pm$15.16} & 0.031 $\pm$0.007\tabularnewline
+\hline 
+kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
+\hline 
+LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
+\hline 
+MLP	& 87.25 $\pm$ 0.09	& 98.45 $\pm$ 46.65	& 156.48 $\pm$ 62.89	& 53.68 $\pm$ 23.35	& 59.5 $\pm$ 22.56	& 0.15 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	85.22	 $\pm$ 	0.11	 & 	85.57	 $\pm$ 	25.92	 & 	141.17	 $\pm$ 	62.02	 & 	49.48	 $\pm$ 	0.16	 & 	56.58	 $\pm$ 	0.25	 & 	0.0014	 $\pm$ 	0.01\tabularnewline
+\hline
+\end{tabular}
+}
+\end{table*}
+
+%-----------------------------------
+
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & \textbf{1008.39 $\pm$305.87} & 71.41 $\pm$13.95 & \textbf{78.47 $\pm$22.70} & \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 65.3 $\pm$0.19 & \textbf{685.56 $\pm$195.28} & 1021.37 $\pm$352.88 & \textbf{69.74 $\pm$16.96} & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
+\hline 
+LR & \textbf{67.0 $\pm$0.23}\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 66.09 $\pm$ 0.21	& 817.79 $\pm$ 242.44	& 1127.02 $\pm$ 381.75	& 84.48 $\pm$ 27.39	& 88.59 $\pm$ 33.21	& 0.03 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	65.66	 $\pm$ 	0.25	 & 	859.21	 $\pm$ 	836.34	 & 	1691.61	 $\pm$ 	3053.2	 & 	92.4	 $\pm$ 	0.81	 & 	134.53	 $\pm$ 	2.18	 & 	0.0009	 $\pm$ 	0.01 \tabularnewline
+\hline
+\end{tabular}
+}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLU11 (SOM-FS). Best values in bold.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
+\hline 
+kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & \textbf{0 $\pm$0.0002}\tabularnewline
+\hline 
+RF & \textbf{85.6 $\pm$0.08} & \textbf{446.25 $\pm$119.79} & \textbf{673.46 $\pm$189.06} & \textbf{45.38 $\pm$9.78} & \textbf{52.24 $\pm$13.09} & 0.0594 $\pm$0.0049\tabularnewline
+\hline 
+LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 77.06 $\pm$ 0.18	& 714.48 $\pm$ 259.22	& 1025.29 $\pm$ 569.79	& 74.3 $\pm$ 29.92	& 81.44 $\pm$ 47.9	& 0.09 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	79.52	 $\pm$ 	0.12	 & 	606.38	 $\pm$ 	153.83	 & 	818.18	 $\pm$ 	243.54	 & 	65.7	 $\pm$ 	0.18	 & 	67.17	 $\pm$ 	0.21	 & 	0.0044	 $\pm$ 	0.01 \tabularnewline
+\hline
+\end{tabular}
+}
+\end{table*}
+
+%-----------------------------------
+
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & \textbf{88.0 $\pm$0.13} & \textbf{738.28 $\pm$188.53} & \textbf{1141.79 $\pm$472.025} & \textbf{45.45 $\pm$13.62} & \textbf{47.58 $\pm$24.84} & 0.017 $\pm$0.002\tabularnewline
+\hline 
+kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
+\hline 
+MLP	& 87.67 $\pm$ 0.12	& 947.71 $\pm$ 388.67	& 1294.58 $\pm$ 458.44	& 58.62 $\pm$ 27.65	& 54.89 $\pm$ 27.53	& 0.04 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	87.25	 $\pm$ 	0.14	 & 	776.49	 $\pm$ 	209.23	 & 	1171.43	 $\pm$ 	455.5	 & 	53.63	 $\pm$ 	0.25	 & 	53.14	 $\pm$ 	0.37	 & 	0.0031	 $\pm$ 	0.01\tabularnewline
+\hline
+\end{tabular}
+}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL929 (SOM-FS). Best values in bold.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & \textbf{89.7 $\pm$0.10} & \textbf{685.67 $\pm$185.99} & \textbf{1116.42 $\pm$478.06} & \textbf{42.09 $\pm$12.8} & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
+\hline 
+kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & \textbf{46.25 $\pm$14.41} & \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
+\hline 
+MLP	& 87.02 $\pm$ 0.13	& 1015.85 $\pm$ 518.44	& 1603.91 $\pm$ 1145.56	& 61.99 $\pm$ 32.97	& 67.74 $\pm$ 62.08	& 0.11 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	83.44	 $\pm$ 	0.17	 & 	884.83	 $\pm$ 	297.95	 & 	1430.42	 $\pm$ 	874.32	 & 	64.61	 $\pm$ 	0.37	 & 	69.69	 $\pm$ 	0.68	 & 	0.002	 $\pm$ 	0.01\tabularnewline
+\hline
+\end{tabular}
+}
+\end{table*}
+
+%-----------------------------------
+
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
+M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
+\hline 
+kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 75.1 $\pm$0.26 & \textbf{15.61 $\pm$7.19} & 26.83 $\pm$13.36 & \textbf{47.38 $\pm$20.10} & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
+\hline 
+LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & \textbf{25.49 $\pm$11.63} & 47.97 $\pm$18.85 & \textbf{60.28 $\pm$30.62} & 0.0002 $\pm$0.0004\tabularnewline
+\hline 
+SVM & \textbf{81.8 $\pm$0.21} & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 80.08 $\pm$ 0.25	& 19.6 $\pm$ 11.66	& 29.32 $\pm$ 14.5	& 59.97 $\pm$ 35.66	& 70.05 $\pm$ 42.31	& 0.02 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	77.62	 $\pm$ 	0.3	 & 	16.53	 $\pm$ 	9.12	 & 	27.18	 $\pm$ 	18.2	 & 	72.75	 $\pm$ 	0.64	 & 	86.09	 $\pm$ 	0.86	 & 	0.0012	 $\pm$ 	0.01\tabularnewline
+
+\hline
+\end{tabular}
+}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLW12 (SOM-FS). Best values in bold.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
+\hline 
+\hline 
 M5P & \textbf{86.0 $\pm$0.19} & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
@@
 }
+\label{Table:case4resultsSOMFS}
 \end{table*}

### 2016-09-04 Response to reviewers.tex
improving some responses to reviewers' comments

@@
 This version is called "Regressional ReliefF" or "RReliefF" for 
-short which was first introduced and implemented by Robnik-Sikonja 
-and Kononenko in Ref XX for numeric targets. 
+short, which was first introduced and implemented by Robnik-Sikonja 
+and Kononenko (in ref. [73] for numeric targets). 
 Therefore, we have clarified this point in the text to remove 
@@
 For CSF, estimating the correlation between attributes is 
-standard linear (Pearson's) correlation.
-The details have been added to the text to clarify this point.
+standard linear (Pearson's) correlation. The details have 
+been added to the text to clarify this point.
 \end{verbatim}
@@
 RF, LR, SVM and MLP.
+
 Also, as suggested by the second reviewer (see his first comment), 
@@
 between classifiers, such as in the paper:
-  M. Fernández-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
+  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
   Do we need hundreds of classifiers to solve real world 
@@
 text and several paragraphs have been rewritten in order to make 
-them clearer and to improve its comprehension. 
+them shorter, clearer and to improve its comprehension.
+
 Also, several tables have been moved to the Appendix and that
-data has been presented now as the new Figure X.
+data has been presented now as the new Figure 3.
 
@@
 \end{verbatim}
-% But it says we should shorten the paper, not to reorganize it. The
-% right response should be to say what parts have been shortened - JJ
-% I'm working on shortening some parts. Thank you!  - Pedro
 
@@
 \end{verbatim}
-% Page might change with revision, so check it at the end - JJ
-% of course! you are right!  - Pedro
+
 ~\\
-\noindent (4) \emph{Some tables should be transfer to figures because there are too many figures. }
+\noindent (4) \emph{Some tables should be transfer to figures because there are too many tables. }
 
 \begin{verbatim}
-THIS HAS TO BE DONE.
+Following your suggestion several tables have been moved to 
+the Appendix and that data has been summarized and presented 
+as the new Figure 3 in order to make that numeric data clearer 
+and to improve its comprehension.
 \end{verbatim}

### 2016-09-04 Response to reviewers.tex
adding another response to reviewers' comments
Response to reviewers revised
It has spawned issue #54, but once that is done, I think we can submit it back.

@@
 \begin{verbatim}
-In all our experiments we have applied the Weka's implementation 
+In all our experiments we have applied  WEKA's implementation 
 of the ReliefF algorithm in the regression problems. 
@@
 \begin{verbatim}
-In sub-section 5.1 the MLP was described as our initial intention 
-was to include it in this study. Thus, in sub-section 
-''2.1. Selecting an appropriate forecasting method'' (old 
-sub-section 4.2) six methods have been introduced M5P, kNN, 
+The current paper includes in sub-section 
+''2.1. Selecting an appropriate forecasting method'' (former
+sub-section 4.2) six methods: M5P, kNN, 
 RF, LR, SVM and MLP.
@@
 
-As far as the number of trees is related, THIS HAS TO BE DONE.
+As far as the number of trees is concerned, in the experiments 
+section, when describing the parameter settings, it has been 
+mentioned that the best performance was obtained with a number of 
+trees equal to 50.
 \end{verbatim}
@@
 \end{verbatim}
+%Every response should end with changes made in the paper, even if it
+%is only clarification. It is not an invitation to discussion.
 
@@
 Finally, the paper has been completely revised and several 
-typographic errors have been fixed.
+typographic errors have been fixed. We are grateful for your
+suggestions and comments. 
 \end{verbatim}

### 2016-09-05 Response to reviewers.tex
Response to reviewers revised. See CONCERNS and TODOs

@@
 
-\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one).
+\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression problem (numerical output) rather than classification (categorical one).
 Both CFS and RelieFF are originally designed for classification problem.
@@
 any ambiguity.
-
+\end{verbatim}
+% Antonio - TODO: say where is this clarification in the text (page/paragraph) and/or copy the text here
+\begin{verbatim}
 For CSF, estimating the correlation between attributes is 
@@
 \end{verbatim}
+% Antonio - TODO: say where is this clarification in the text (page/paragraph) and/or copy the text here
 
 ~\\
-\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM.
-In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ?
-For RF, how many trees are set?
-}
+\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ?}
 
@@
 The current paper includes in sub-section 
-''2.1. Selecting an appropriate forecasting method'' (former
-sub-section 4.2) six methods: M5P, kNN, 
-RF, LR, SVM and MLP.
+`2.1. Selecting an appropriate forecasting method' (former
+sub-section 4.2) six methods: M5P, kNN, RF, LR, SVM, MLP,
+ and ELM (requested by Reviewer #2).
 
-Also, as suggested by the second reviewer (see his first comment), 
-the results obtained with this method have been included in the 
-new version of this paper.
-
-As far as the number of trees is concerned, in the experiments 
-section, when describing the parameter settings, it has been 
-mentioned that the best performance was obtained with a number of 
-trees equal to 50.
+Moreover, as suggested by the Reviewer #2 (see his/her first comment), 
+the results obtained with the two last methods have been included in 
+this new version of the paper.
 \end{verbatim}
+% Antonio - TODO: say where are these results (table/figure/page)
 
 ~\\
-\noindent (3) \emph{As we known, tree-based mehods (e.g.,M5P and RF) themselve embed feature selection procedure.
-That is, some features are choosen to build trees.
+\noindent (2) \emph{For RF, how many trees are set? }
+
+\begin{verbatim}
+As far as the number of trees is concerned, in the experiments 
+section, when describing the parameter settings, 
+it has been mentioned that the best performance was obtained with a 
+number of trees equal to 50.
+\end{verbatim}
+% Antonio - TODO: say where is this clarification in the text (page/paragraph) and/or copy the text here
+
+~\\
+\noindent (3) \emph{As we known, tree-based methods (e.g., M5P and RF) themselves embed feature selection procedure.
+That is, some features are chosen to build trees.
 It is not fair enough to compare five methods in Table 3.
@@
 methods we have deployed in our research. 
-The idea is simply to show the decision maker what are the possible 
+The aim is simply to show to the decision maker what are the possible 
 results when we apply one of the off-the-shelf classifiers available 
@@
 Moreover, it is not uncommon in the literature to see such comparison 
-between classifiers, such as in the paper:
+between classifiers, as in the paper:
   M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
@@
 %is only clarification. It is not an invitation to discussion. 
+% Antonio - TODO: say how this has been addressed in the paper (where it is clarified). Say if this reference has been included as new.
 
@@
 \begin{verbatim}
-According to the reviewer's comment, we have addressed this issue
-at the same time that comment #1, where the application procedure 
-of feature selection methods for regression problems has been 
-clarified. Also, we have added the ''regression'' term all along 
-the paper including the description of the dataset.
+The reviewer is right, thus, we have revised the whole paper referring 
+to the term `regression' instead of `classification'. Moreover this have 
+been also addressed solving the issue related to comment #1, where the
+application procedure of feature selection methods for regression problems 
+has been clarified. 
 \end{verbatim}
+% Antonio - CONCERN: I'm a bit afraid about the term 'organize' which I don't know if has been addressed in any way in the new version...
 
@@
 \begin{verbatim}
-Following your suggestion we have reorganized some parts of the 
+Following reviewer's suggestion we have reorganized some parts of the 
 text and several paragraphs have been rewritten in order to make 
@@
 Finally, the paper has been completely revised and several 
-typographic errors have been fixed. We are grateful for your
-suggestions and comments. 
+typographic errors have been fixed.
+
+We are very grateful for your valuable suggestions and comments. 
 \end{verbatim}
+% Antonio - TODO: show some examples of reduced text (page/paragraph), there will be some new figures, I think.
+
+~\\
 
@@
 \begin{verbatim}
-We have added the results of ANN (MLP) and ELM to all tables 
-accordingly. A description of both approaches have been also 
-added to subsection 2.1.
+Following the reviewer's request, we have conducted several new experiments 
+and added the results of ANN (MLP) and ELM to Tables XX, YY, ZZ and
+ Figures AA, BB accordingly. 
+A description of both approaches have been also included in subsection 2.1.
+
+In addition new references has been added to the paper related to these 
+methods, namely [REF_XX, REF_YY].
 \end{verbatim}
+% Antonio - TODO: Complete with the number of tables and figures, along with the new references
 
@@
 \begin{verbatim}
-We have rewritten the introduction and introduced this new text:
+We have rewritten the introduction and included this new text:
 
-Our main contribution is, thus, to develop a methodology to 
+"Our main contribution is, thus, to develop a methodology to 
 process book sales data in order to first find out relevant 
@@
 300 copies for standard books and around 5000 for those that are 
-considered, in advance, best sellers.
+considered, in advance, best sellers."
 
 Also, in the next-to-last paragraph, we have laid out our 
-methodology and the main contributions of this paper.
+methodology and clarified the main contributions of this paper 
+to the state of the art.
 \end{verbatim}
+% Antonio - TODO: I rewritten this text, so we should copy the new one here. But I think we all should contribute to create a very good justification (see next CONCERN). :D
+% Antonio - CONCERN: We should definitely write a convincing text which separates this work from existing approaches.
+Maybe the use of real data is a good point.
+And also emphasize the contribution to the SotA.
 
@@
 Taking into account the reviewer's comment, the recommendation 
-systems have been added to the future works section, at the end 
-of Section 7 (see page 19).
+systems have been added to the future work section, at the end 
+of Section 7 (see page XX).
 \end{verbatim}
+% Antonio - TODO: put the correct page when the text is finished. Cooy the text here.
 
@@
 \begin{verbatim}
-Following your suggestion several tables have been moved to 
+Following reviewer's suggestion, several tables have been moved to 
 the Appendix and that data has been summarized and presented 
 as the new Figure 3 in order to make that numeric data clearer 
-and to improve its comprehension.
+and to improve their comprehension.
 \end{verbatim}
+% Antonio - CONCERN: I think we should move ALL the results tables and include a couple of figures more. Please see my e-mail on this respect. ;)
+% Antonio - TODO: Talk about the final tables and figures.
 
@@
 \begin{verbatim}
-Taking into account the reviewer's comment, we have designed 
-a graphical abstract as a visual summary of the main findings 
-of the article.
+We agree with the reviewer and have designed (and uploaded) a 
+graphical abstract as a visual summary of the paper structure 
+and the utility of the obtained results.
 
-We would like to thank this reviewer for his suggestions and 
-advice about our paper.
+We would like to thank this reviewer for his/her suggestions 
+and comments to improve the quality of our paper.
 \end{verbatim}
+
+~\\
 
@@
 \begin{verbatim}
-We have rewritten the introduction and introduced this new text:
 
-Our main contribution is, thus, to develop a methodology to 
-process book sales data in order to first find out relevant 
-variables and then use these variables to process data so that 
-the publisher, using them, can estimate sales and from them order 
-a specific print run, instead of standard ones, which are around 
-300 copies for standard books and around 5000 for those that are 
-considered, in advance, best sellers.
+********* TO WRITE ***********
 
-Also, in the next-to-last paragraph, we have laid out our 
-methodology and the main contributions of this paper.
 \end{verbatim}
+% Antonio - TODO: we can't write the same answer for two reviewers. We'll answer the same, once we have the response for the previour reviewer but in other words. ;)
 
@@
 \begin{verbatim}
-Following your suggestion we have reorganized these sub-sections, 
+Following reviewer's suggestion we have reorganized these sub-sections, 
 moving them to section 2.
 \end{verbatim}
+% Antonio - TODO: we have also to link them properly to the new section and to remove them from the text describing Section 4 where they were... Then, say this in the response.
 
@@
 Taking into account the reviewer's comment, we have improved the 
-description of the methodology by including a flowchart (see Figure 1 
-at page 6).
+description of the methodology including a flowchart (see Figure XX 
+at page YY).
 \end{verbatim}
+% Antonio - CONCERN: I don't know if te reviewer is speaking about the whole methodology or just about the regression/forecasting part... The figure shows a rough summary of the methodology.
+% Antonio - TODO: Improve the figure, which is a bit 'generic'. Put the correct figure and page.
 
 ~\\
-\noindent (4) \emph{In Section 5, parameter settings of M5P, kNN and RF also should be shown. }
+\noindent (4) \emph{In Section 5, parameter settings of 
+M5P, kNN and RF also should be shown. }
 
 \begin{verbatim}
-Taking into account the reviewer's comment, we have improved the 
-section 5, including the parameter settings of M5P, kNN and RF 
-methods.
+We have improved Section 5, including the parameter settings of 
+M5P, kNN and RF methods.
+
+The authors want to express our gratitude to this reviewer 
+for his/her suggestions.
 \end{verbatim}
+% Antonio - CONCERN: don't we also put the configuration of the rest of the methods? And say it. :D 
+% Could we use a table for showing them easily?
+% Antonio - TODO: say paragraph/page where they are and maybe put here the text.
 
 \end{document}
+% Antonio - TODO: Say if there are new references and include them in a final section in this letter.

### 2016-09-05 Tables_to_figures/generador.r
Nuevas imágenes

@@ -52,7 +52,7 @@ datos$error <- as.numeric(sapply(str_split(datos$value, '_'), '[', 2))
 datos$value <- as.numeric(sapply(str_split(datos$value, '_'), '[', 1))
 
 datos$variable <- as.character(datos$variable)
-datos[datos$variable=="R.","variable"] <- "R^2"
+datos[datos$variable=="R.","variable"] <- "R"
 dataset = unique(datos$Dataset)
 
 #ggplot(data = subset(datos,Dataset==dataset[1]), aes(x=Attributes,y=value,color=Attributes,shape=Attributes)) + geom_point(stat="identity",size=3) + 
@@ -82,6 +82,7 @@ for(i in dataset){
                                                                                                     axis.text.x=element_blank(),
                                                                                              axis.ticks.x=element_blank()))
   ggsave(file=paste0("../imgs/datasets_",i,".eps"),scale=2,units = "cm", width = 16, height = 8,dpi = 800)
+  ggsave(file=paste0("../imgs/datasets_",i,".png"),scale=2,units = "cm", width = 16, height = 8,dpi = 800)
   
 }
 
@@ -92,13 +93,17 @@ att = unique(datos$Attributes)
 #for(i in dataset){
   for(j in att){
   
-print(ggplot(data = subset(datos,Attributes==j & Dataset==i), aes(x=Method,y=value,color=Attributes,shape=Attributes)) + 
-        geom_point(stat="identity",size=2)  +geom_bar(stat="identity") + 
+print(ggplot(data = subset(datos,Attributes==j), aes(x=Method,y=value,fill=Method)) + 
+  geom_point(stat="identity",size=2)  + geom_bar(stat="identity") + 
   facet_grid(variable ~ Dataset,scales = "free_y") + 
-  scale_color_grey(start=0.0,end=0.2) + labs(title="",x="",y="") + 
-  geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="none"))
+  scale_fill_grey(start=0.2,end=0.6) + labs(title="",x="",y="") + 
+  geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="right") +
+    scale_y_continuous(limits = c(0, NA))
+  )
+      
 
[…]

### 2016-09-05 Tables_to_figures/generador.r
Figure to replace Table 5

@@ -2,7 +2,6 @@ library(stringr)
 library(reshape2)
 library(ggplot2)
 
-
 filenames_all <- list.files(path = "datasets/AllAttributes/",pattern = ".csv",full.names = TRUE)
 ldf <- lapply(filenames_all, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
 for(i in seq(from=1,to=length(filenames_all),by = 1)){
@@ -119,12 +118,73 @@ for(i in var){
   
   
   ggsave(file=paste0("../imgs/metric_",i,".eps"),scale=2.5,units = "cm", width = 16, height = 8,dpi = 800)
+  ggsave(file=paste0("../imgs/metric_",i,".png"),scale=2.5,units = "cm", width = 16, height = 8,dpi = 800)
 }
 
+
+#Figure to replace Table 3
+all <- read.csv(file = "datasets/all.csv",skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
+
+all <- melt(data = all,id.vars = c("Method"),measure.vars = c("R.","MAE","RMSE","RAE","RRSE","TIME"))
+
+all$error <- as.numeric(sapply(str_split(all$value, '_'), '[', 2))
+all$value <- as.numeric(sapply(str_split(all$value, '_'), '[', 1))
+
+all$variable <- as.character(all$variable)
+all[all$variable=="R.","variable"] <- "R"
+
+
+
+ggplot(data = subset(all), aes(x=Method,y=value)) + 
+  geom_bar(stat="identity",size=3) + geom_point(stat="identity",size=3) +
+  facet_grid(variable ~ . ,scales = "free_y") + 
+  scale_fill_grey(start=0.2,end=0.8) + labs(title="",x="Method",y="") + 
+  geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="bottom")
+
+
+ggsave(file=paste0("../imgs/prediction_all_publisher_all_features_Table3.eps"),scale=2.5,units = "cm", width = 16, height = 8,dpi = 800)
[…]

### 2016-09-05 paper.tex
closing the issue about making the new Figure: Closes #52
Response to reviewers revised. See CONCERNS and TODOs
moving old tables 3 and 5 to appendix and substitute them by corresponding Figures

@@
 
-Correlation coefficient, error measures and time to build the model have been computed for every method. Obtained results are presented in Table \ref{tab:all_publishers_no_fs}.
-
-\begin{table*}
-\caption{Predicting Total sales for all publishers (all the features). 30 repetitions, 10-fold cross validation. Best values in bold.
-\label{tab:all_publishers_no_fs}}
-\centering{}%
-\scalebox{0.78}{
-
-\begin{tabular}{|c|l|l|l|l|l|l|}
-\hline 
- & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-M5P  &  \textbf{89.0 $\pm$ 0.09}  &  \textbf{214.37 $\pm$ 22.96}  &  \textbf{634.23 $\pm$ 307.76}  &  \textbf{37.46 $\pm$ 3.12}  &  \textbf{48.32 $\pm$ 25.16} & 18.85 $\pm$ 0.61\tabularnewline
-\hline 
-kNN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
-\hline 
-RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
-\hline 
-LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
-\hline 
-SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
-\hline 
-MLP	& 88.01 $\pm$ 0.11	& 350.99 $\pm$ 185.53	& 730.93 $\pm$ 374.84	& 61.64 $\pm$ 33.61	& 56.33 $\pm$ 31.6	& 7014.06 $\pm$ 110.095 \tabularnewline
-\hline 
-ELM & 	86.79	 $\pm$ 	0.11	 & 	271.01	 $\pm$ 	28.53	 & 	684.98	 $\pm$ 	329.39	 & 	47.73	 $\pm$ 	0.06	 & 	52.42	 $\pm$ 	0.26	 & 	0.203	 $\pm$ 	0.03  \tabularnewline
-
-\hline 
-\end{tabular}
-}
-\end{table*}
-
-As far as the different methods are concerned, M5P model obtained the best results, both in time and error. The advantage of M5P is that it can learn and tackle regression
-% Antonio - I think we can change classification by regression. I have done. Check it out. ;)
- tasks that have high dimensionality and categorical variables efficiently.
-Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation.
-Thus, it is a very suitable model be incorporated in a publishing company
-processes (as we will show in Section \ref{subsec:decision_trees}).
-
-Taking into account the obtained results by SVM model, this method obtains comparable errors to those of M5P.
-Even when using roughly tuned parameter values, it shows a good generalisation performance.
-However, SVM is much slower than the others to build the model, not only when using the dataset with categorical input variables, such as \emph{collection} and \emph{binding}, but also when using the datasets with numerical variables, not to mention the extra time needed to optimize its hyperparameters.
-
-According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that 
+Correlation coefficient, error measures and time to build the model have been 
+computed for every method. Obtained results are presented in 
+Figure \ref{fig:all_publishers_no_fs}
+(detailed numeric results can be shown in Table Table \ref{tab:all_publishers_no_fs}
+in the appendix of tables at the end of this paper).
+
+\begin{figure*}[ht]
+\begin{center}
+\includegraphics[scale=0.35]{./imgs/prediction_all_publisher_all_features_Table3.eps}
+\end{center}
+\caption{Predicting \texttt{total\_sales} for all publishers (all the features). 30 repetitions, 10-fold cross validation.}
+\label{fig:all_publishers_no_fs}
+\end{figure*}
+
+As far as the different methods are concerned, M5P model obtained the best results, 
+both in time and error. The advantage of M5P is that it can learn and tackle 
+regression tasks that have high dimensionality and categorical variables efficiently. 
+Moreover, M5P generates reproducible and comprehensible representations that 
+provide information on the decision process and does not require human intervention 
+either for the operation or for interpretation. Thus, it is a very suitable model 
+be incorporated in a publishing company processes (as we will show in 
+Section \ref{subsec:decision_trees}).
+
+Taking into account the obtained results by SVM model, this method obtains comparable 
+errors to those of M5P. Even when using roughly tuned parameter values, it shows 
+a good generalisation performance. However, SVM is much slower than the others to build 
+the model, not only when using the dataset with categorical input variables, such 
+as \emph{collection} and \emph{binding}, but also when using the datasets with 
+numerical variables, not to mention the extra time needed to optimize its hyperparameters.
+
+According to Figure \ref{fig:all_publishers_no_fs}, it can also be noticed that 
 the Linear Regression model outperforms some other complex methods like the 
@@
 is the simplest one. However, the model is slow when classifying large number of 
-training examples, and it exhibits a poor generalisation ability since it does not learn anything from the training data.
+training examples, and it exhibits a poor generalisation ability since it does 
+not learn anything from the training data.
 
@@
 
-As a first conclusion, paying attention both to the cost in time to obtain the forecasting models and their accuracy, the M5P model would be the most adequate to solve the problem of how many books should be printed when a new book is published.
-This forecasting method, with these additional advantages, can be used for products with historical sales data and for new products with little or no historical data available.
+As a first conclusion, paying attention both to the cost in time to obtain the 
+forecasting models and their accuracy, the M5P model would be the most adequate 
+to solve the problem of how many books should be printed when a new book is 
+published. This forecasting method, with these additional advantages, can be used 
+for products with historical sales data and for new products with little or 
+no historical data available.
 
@@
 We have used both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.
-
-The dataset has also been analysed using SOM, and a visual exploration of the obtained results has been performed in order to determine the best variables to consider.
-An important preprocessing step has been carried out before conducting the SOM analysis.
-Thus, the two categorical features \emph{collection} and \emph{binding} have been removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
-However, since they have a large number of unique different values this would be finally impracticable and useless.
-
-In the analysis, several configurations for SOM have been tested, and the best one regarding both the \textit{quantisation error} and \textit{topographic error} has been chosen.
-The first error is a measure which represents the average distance between every input pattern and its BMU (i.e.
-how good the map fits the dataset).
-The latter refers to the topology of the map and its preservation, so it measures an average value computed looking at both, the first and the second BMUs for every pattern.
-If they are neighbours (directly connected in the map) a `1' is considered, otherwise a `0' is taken.
-A small value would mean that the map preserves well its topology.
-
-Thus, the chosen map to represent the data has $26 \times 16$ neurons and an hexagonal neighbourhood topology.
-The best SOM training results have been obtained with a final quantisation error of 0.691 and topographic error of 0.046.
 
@@
 
-\begin{table*}
-\caption{Input features/variables selected by each method
-\label{tab:features_selected}}
-\centering{}%
-\begin{tabular}{|c|c|c|c|c|}
-\hline 
-No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
-\hline 
-1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-2 & \texttt{subject1} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
-\hline 
-3 &  \texttt{collection} &  &  & \\
-\hline 
-4 & \texttt{binding} &  &  & \\
-\hline 
-5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
-\hline 
-7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
-\hline 
-9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-10 & \texttt{print\_run} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
-\hline 
-\end{tabular}
-\end{table*}
-
-Figure \ref{fig:componentplanes} shows the U-matrix along with the component planes analysis resulted from SOM training. The term component refers in SOM to a variable or feature of the problem.
-The component planes in Figure \ref{fig:componentplanes} show the trend of values of the prototype vectors of the SOM map units.
-These values are represented as colours.
-The colourbar on the right of each component plane shows the indication of each colour.
-On the other side, the U-matrix on the top
+The dataset has also been analysed using SOM, and a visual exploration of the obtained results has been performed in order to determine the best variables to consider.
+An important preprocessing step has been carried out before conducting the SOM analysis.
+Thus, the two categorical features \emph{collection} and \emph{binding} have been removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
+However, since they have a large number of unique different values this would be finally impracticable and useless.
+
+In the analysis, several configurations for SOM have been tested, and the best one regarding both the \textit{quantisation error} and \textit{topographic error} has been chosen.
+The first error is a measure which represents the average distance between every input pattern and its BMU (i.e.
+how good the map fits the dataset).
+The latter refers to the topology of the map and its preservation, so it measures an average value computed looking at both, the first and the second BMUs for every pattern.
+If they are neighbours (directly connected in the map) a `1' is considered, otherwise a `0' is taken.
+A small value would mean that the map preserves well its topology.
+
+Thus, the chosen map to represent the data has $26 \times 16$ neurons and an hexagonal neighbourhood topology.
+The best SOM training results have been obtained with a final quantisation error of 0.691 and topographic error of 0.046.
+
+Figure \ref{fig:componentplanes} shows the U-matrix along with the component 
+planes analysis resulted from SOM training. The term component refers in SOM 
+to a variable or feature of the problem.
+The component planes in Figure \ref{fig:componentplanes} show the trend of 
+values of the prototype vectors of the SOM map units. These values are represented 
+as colours. The colourbar on the right of each component plane shows the indication 
+of each colour. On the other side, the U-matrix on the top
 left corner shows the distances between the adjacent units. It is
@@
 
+\begin{table*}
+\caption{Input features/variables selected by each method
+\label{tab:features_selected}}
+\centering{}%
+{\footnotesize
+\begin{tabular}{|c|c|c|c|c|}
+\hline 
+No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
+\hline 
+1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+2 & \texttt{subject1} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
+\hline 
+3 &  \texttt{collection} &  &  & \\
+\hline 
+4 & \texttt{binding} &  &  & \\
+\hline 
+5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
+\hline 
+7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
+\hline 
+9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
+\hline 
+10 & \texttt{print\_run} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
+\hline 
+\end{tabular}
+}
+\end{table*}
+
+\begin{figure*}[ht]
+\begin{center}
+\includegraphics[scale=0.35]{./imgs/prediction_all_publisher_Table5.eps}
+\end{center}
+\caption{Predicting \texttt{total\_sales} for all publishers based on features selected by each method.}
+\label{fig:results_all_publishers_fs}
+\end{figure*}
+
 Examining the component planes shown in Figure \ref{fig:componentplanes}, it can be noticed that some variables have very similar colour maps which means that they are highly correlated.
@@
 
-\begin{table*}
-\centering{}%
-\caption{Predicting Total sales for all publishers based on features selected
-by each method. Best values in bold.
-\label{tab:results_all_publishers_fs}}
-% RELIEFATTRIBUTEEVAL
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
-\hline 
- & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
-\hline 
-kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
-\hline 
-RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
-\hline 
-LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
-\hline 
-SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
-\hline  
-MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
-\hline  
-ELM & 	87.55	 $\pm$ 	0.1	 & 	250.88	 $\pm$ 	28.78	 & 	677.94	 $\pm$ 	356.41	 & 	44.16	 $\pm$ 	0.05	 & 	50.86	 $\pm$ 	0.24	 & 	0.1106	 $\pm$ 	0.02\\
-\hline
-
-\end{tabular}
-}
-% CFSSUBEVAL
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
-\hline
- & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
-\hline 
-kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
-\hline 
-RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
-\hline 
-LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
-\hline 
-SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
-\hline
-MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
-\hline
-ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
-\hline
-
-\end{tabular}
-}
-% SOM
-\centering{}% SOM
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
-\hline 
- &  $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
-\hline 
-M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
-\hline 
-kNN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
-\hline 
-RF &  \textbf{89.8 $\pm$0.05}  &  \textbf{211.87 $\pm$20.07}  &  \textbf{617.78 $\pm$187.16}  &  \textbf{37.02 $\pm$2.46}  &  \textbf{46.58 $\pm$11.14}  & 2.93 $\pm$0.11\tabularnewline
-\hline 
-LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
-\hline 
-SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
-\hline 
-MLP	& 84.3 $\pm$ 0.12	& 388.79 $\pm$ 274.18	& 851.01 $\pm$ 422.03	& 68.26 $\pm$ 49.64	& 65.85 $\pm$ 36.49	& 3.29 $\pm$ 0.042\tabularnewline
-\hline
-ELM & 	85.3	 $\pm$ 	0.09	 & 	301.42	 $\pm$ 	31.43	 & 	704.9	 $\pm$ 	221.83	 & 	53.22	 $\pm$ 	0.07	 & 	54.57	 $\pm$ 	0.18	 & 	0.0229	 $\pm$ 	0.02\\
-\hline
-\end{tabular}
-}
-\end{table*}
-
 After applying the feature selection process, we have run the same
@@
 for the whole dataset (all the publishers), but considering only the
-selected features by each method. The results are shown in Table
-\ref{tab:results_all_publishers_fs}. Examining the obtained results
-for each feature selection method, it can be seen that RFE got the
-best results compared to SOM and CSE. It can be noticed also that we
-obtain better performance using M5P, kNN and RF with the set of features
-selected by RFE than using all features. %Better publish results in
+selected features by each method. 
+The results are shown in Figure \ref{fig:results_all_publishers_fs} 
+(detailed numeric results can be shown in Table \ref{tab:results_all_publishers_fs}
+in the appendix of tables at the end of this paper).
+Examining the obtained results for each feature selection method, 
+it can be seen that RFE got the best results compared to SOM and CSE. 
+It can be noticed also that we obtain better performance using M5P, 
+kNN and RF with the set of features selected by RFE than using all features. 
+                                %Better publish results in
                                 %the same table or refer to the table
@@
                                 %- JJ
-As expected, in general, all feature selection methods have reduced the training time needed to build the forecasting methods.
-This is because they reduced the considered features and mainly because they excluded the categorical features, which are the hardest to be managed (they have many possible values).
+As expected, in general, all feature selection methods have reduced the training 
+time needed to build the forecasting methods. This is because they reduced the 
+considered features and mainly because they excluded the categorical features, 
+which are the hardest to be managed (they have many possible values). 
 On the other side, CSE and SOM did not perform as good as RA. 
-This could be explained due to the extensive reduction made by CSE and due to the `subjective' (but not so accurate) human intervention in the case of SOM.
+This could be explained due to the extensive reduction made by CSE and due to 
+the `subjective' (but not so accurate) human intervention in the case of SOM.
 
@@
 makers and managers in the domain. The four cases are described as follows:
+
+\begin{table*}
+\caption{Description of publishing companies considered as special cases.}
+\centering{}%
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|l|l|l|}
+\hline 
+ Case & Different books sold & Total copies sold & Description\\
+\hline 
+\textit{All publishing companies} & 6083 & 3201645 & 209 publishing companies\\
+\hline 
+\textit{UDL929} & 216 & 460752 & Best selling publishing company\\
+\hline 
+\textit{UDLW12} & 97 & 2635 & Mid-range selling publishing company\\
+\hline 
+\textit{UDL704} & 293 & 58236 & publishing company with most different\\ 
+       &     &       & books sold\\
+\hline 
+\textit{UDLU11} & 180 & 249481 & publishing company with medium number\\ 
+       &     &       &  of different books sold\\
+\hline 
+\end{tabular}
+}
+\label{Table:special_cases}
+\end{table*}
+
+\begin{figure*}[ht]
+\begin{center}
+\includegraphics[scale=0.55]{./imgs/attribute_All.eps}
+\end{center}
+\caption{Predicting \texttt{total\_sales} for publishing companies UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).}
+\label{fig:attributeAll}
+\end{figure*}
 
@@
 of titles published by the selected companies.
-
-\begin{table*}
-\caption{Description of publishing companies considered as special cases.}
-\centering{}%
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|l|l|l|}
-\hline 
- Case & Different books sold & Total copies sold & Description\\
-\hline 
-\textit{All publishing companies} & 6083 & 3201645 & 209 publishing companies\\
-\hline 
-\textit{UDL929} & 216 & 460752 & Best selling publishing company\\
-\hline 
-\textit{UDLW12} & 97 & 2635 & Mid-range selling publishing company\\
-\hline 
-\textit{UDL704} & 293 & 58236 & publishing company with most different\\ 
-       &     &       & books sold\\
-\hline 
-\textit{UDLU11} & 180 & 249481 & publishing company with medium number\\ 
-       &     &       &  of different books sold\\
-\hline 
-\end{tabular}
-}
-\label{Table:special_cases}
-\end{table*}
-
-\begin{figure*}[ht]
-\begin{center}
-\includegraphics[scale=0.55]{./imgs/attribute_All.eps}
-\end{center}
-\caption{Predicting \texttt{total\_sales} for publishing companies UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).}
-\label{fig:attributeAll}
-\end{figure*}
 
@@
 factors, including price.
+
+\begin{figure*}[!ht] 
+\begin{center}
+  \epsfig{file=decision_tree_no_fs.eps,width=13cm}
+\caption{Decision tree built by the M5P method for the best seller publishing 
+	company including all pre-sales features.}
+\label{fig:decision_tree_best_seller}
+\end{center}
+\end{figure*}
+
+\begin{figure*}[!ht] 
+\begin{center}
+  \epsfig{file=decision_tree_fs.eps,width=13cm}
+\caption{Decision tree built by the M5P method for the best seller
+  publishing company using  the subset of features selected by the
+  {\sf ReliefAttributeEval} method.} 
+\label{fig:decision_tree_best_seller_fs}
+\end{center}
+\end{figure*}
 
@@
 
-\begin{figure*}[!ht] 
-\begin{center}
-  \epsfig{file=decision_tree_no_fs.eps,width=13cm}
-\caption{Decision tree built by the M5P method for the best seller publishing 
-	company including all pre-sales features.}
-\label{fig:decision_tree_best_seller}
-\end{center}
-\end{figure*}
-
-\begin{figure*}[!ht] 
-\begin{center}
-  \epsfig{file=decision_tree_fs.eps,width=13cm}
-\caption{Decision tree built by the M5P method for the best seller
-  publishing company using  the subset of features selected by the
-  {\sf ReliefAttributeEval} method.} 
-\label{fig:decision_tree_best_seller_fs}
-\end{center}
-\end{figure*}
-
 %********************************************************************************
@@
 
+%--------------- old Tables 3, 5 (before revision)
+
+\begin{table*}
+\caption{Predicting \texttt{total\_sales} for all publishers (all the features). 30 repetitions, 10-fold cross validation. Best values in bold.
+\label{tab:all_publishers_no_fs}}
+\centering{}%
+\scalebox{0.78}{
+
+\begin{tabular}{|c|l|l|l|l|l|l|}
+\hline 
+ & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+M5P  &  \textbf{89.0 $\pm$ 0.09}  &  \textbf{214.37 $\pm$ 22.96}  &  \textbf{634.23 $\pm$ 307.76}  &  \textbf{37.46 $\pm$ 3.12}  &  \textbf{48.32 $\pm$ 25.16} & 18.85 $\pm$ 0.61\tabularnewline
+\hline 
+kNN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
+\hline 
+RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
+\hline 
+LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
+\hline 
+SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
+\hline 
+MLP	& 88.01 $\pm$ 0.11	& 350.99 $\pm$ 185.53	& 730.93 $\pm$ 374.84	& 61.64 $\pm$ 33.61	& 56.33 $\pm$ 31.6	& 7014.06 $\pm$ 110.095 \tabularnewline
+\hline 
+ELM & 	86.79	 $\pm$ 	0.11	 & 	271.01	 $\pm$ 	28.53	 & 	684.98	 $\pm$ 	329.39	 & 	47.73	 $\pm$ 	0.06	 & 	52.42	 $\pm$ 	0.26	 & 	0.203	 $\pm$ 	0.03  \tabularnewline
+
+\hline 
+\end{tabular}
+}
+\end{table*}
+
+\begin{table*}
+\centering{}%
+\caption{Predicting \texttt{total\_sales} for all publishers based on features selected by each method. Best values in bold.
+\label{tab:results_all_publishers_fs}}
+% RELIEFATTRIBUTEEVAL
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
+\hline 
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
+\hline 
+kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
+\hline 
+RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
+\hline 
+LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
+\hline 
+SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
+\hline  
+MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
+\hline  
+ELM & 	87.55	 $\pm$ 	0.1	 & 	250.88	 $\pm$ 	28.78	 & 	677.94	 $\pm$ 	356.41	 & 	44.16	 $\pm$ 	0.05	 & 	50.86	 $\pm$ 	0.24	 & 	0.1106	 $\pm$ 	0.02\\
+\hline
+
+\end{tabular}
+}
+% CFSSUBEVAL
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{7}{|c|}{\textit{CfsSubsetEval}}\\
+\hline
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
+\hline 
+kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
+\hline 
+RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
+\hline 
+LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
+\hline 
+SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
+\hline
+MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
+\hline
+ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
+\hline
+
+\end{tabular}
+}
+% SOM
+\centering{}% SOM
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
+\hline 
+ &  $R$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
+\hline 
+M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
+\hline 
+kNN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
+\hline 
+RF &  \textbf{89.8 $\pm$0.05}  &  \textbf{211.87 $\pm$20.07}  &  \textbf{617.78 $\pm$187.16}  &  \textbf{37.02 $\pm$2.46}  &  \textbf{46.58 $\pm$11.14}  & 2.93 $\pm$0.11\tabularnewline
+\hline 
+LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
+\hline 
+SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
+\hline 
+MLP	& 84.3 $\pm$ 0.12	& 388.79 $\pm$ 274.18	& 851.01 $\pm$ 422.03	& 68.26 $\pm$ 49.64	& 65.85 $\pm$ 36.49	& 3.29 $\pm$ 0.042\tabularnewline
+\hline
+ELM & 	85.3	 $\pm$ 	0.09	 & 	301.42	 $\pm$ 	31.43	 & 	704.9	 $\pm$ 	221.83	 & 	53.22	 $\pm$ 	0.07	 & 	54.57	 $\pm$ 	0.18	 & 	0.0229	 $\pm$ 	0.02\\
+\hline
+\end{tabular}
+}
+\end{table*}
+
 %--------------- old Tables 7, 8, 9, 10 (before revision)

### 2016-09-06 paper.tex
New text and adjustments on figures

@@
 \begin{center}
-\includegraphics[scale=0.35]{./imgs/prediction_all_publisher_all_features_Table3.eps}
+\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_all_features_Table3.eps}
 \end{center}
-\caption{Predicting \texttt{total\_sales} for all publishers (all the features). 30 repetitions, 10-fold cross validation.}
+\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation).
+All publishers and all the features have been considered.}
 \label{fig:all_publishers_no_fs}
@@
 \begin{center}
-\includegraphics[scale=0.25]{som_planes.eps}
+\includegraphics[scale=0.35]{som_planes.eps}
 \end{center}
@@
 \hline 
-No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
-\hline 
-1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
+No. & Variable & CfsSubsetEval & ReliefFAttributeEval & SOM\\
+\hline 
+1 & \texttt{ret\_price} &  & $\checkmark$ & $\checkmark$\\
 \hline 
@@
 \hline 
-5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
-\hline 
-7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
-\hline 
-8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
-\hline 
-9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
+5 & \texttt{gifts} &  & $\checkmark$ & $\checkmark$\\
+\hline 
+6 & \texttt{distrib\_novelty} &  & $\checkmark$ & \\
+\hline 
+7 & \texttt{tot\_points\_sale} &  & $\checkmark$ & $\checkmark$\\
+\hline 
+8 & \texttt{tot\_points\_sale\_1st\_year} & & $\checkmark$ & \\
+\hline 
+9 & \texttt{weeks\_sale} &  & $\checkmark$ & $\checkmark$\\
 \hline 
@@
 \begin{center}
-\includegraphics[scale=0.35]{./imgs/prediction_all_publisher_Table5.eps}
+\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_Table5.eps}
 \end{center}
-\caption{Predicting \texttt{total\_sales} for all publishers based on features selected by each method.}
+\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation).
+All publishers and just those features selected by each method have been considered in every case.}
 \label{fig:results_all_publishers_fs}
@@
 \begin{center}
-\includegraphics[scale=0.55]{./imgs/attribute_All.eps}
+\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
 \end{center}
-\caption{Predicting \texttt{total\_sales} for publishing companies UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).}
+\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation).
+Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
+Just the features selected by ReliefFAttributeEval method have been considered.}
 \label{fig:attributeAll}
 \end{figure*}
+% Antonio - CONCERN - The text and the results must be contrasted.
+If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best).
+But there are plotted apparently the results for all the features.
+Anyway, in the text, it is said that the process is using all the features, then apply FS.
+But here just the results for all the features are shown.
+Why don't we show also the results for the corresponding sets of features selected by each FS method?
 

### 2016-09-06 paper.tex
A typo fixed

@@
 \ref{fig:decision_tree_best_seller_fs}) corresponds to the same
-publishing company, so the same data were used, but the RAE % Problem here: everytime you use RAE in the paper it means Relative Absolute Error, so I don't think we should use just "RAE" here, but ReliefAttributeEval.
+publishing company, so the same data were used, but the RAE % Problem here: everytime you use RAE in the paper it means Relative Absolute Error, so I don't think we should use just "RAE" here, but ReliefFAttributeEval.
 feature
@@
   publishing company using  the subset of features selected by the
-  {\sf ReliefAttributeEval} method.} 
+  {\sf ReliefFAttributeEval} method.} 
 \label{fig:decision_tree_best_seller_fs}
@@
 \label{tab:results_all_publishers_fs}}
-% RELIEFATTRIBUTEEVAL
+% RELIEFFATTRIBUTEEVAL
 \resizebox{12cm}{!}{
@@
 \hline 
-\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
+\multicolumn{7}{|c|}{\textit{ReliefFAttributeEval}}\\
 \hline 

### 2016-09-07 paper.tex
fixing a typo in the first table of appendix
Changes, reordering and new CONCERNS

@@
 \label{sec:soa}
+% Antonio - TODO: Since two new sections have been added here, maybe we should change the title of the section... Maybe 'Background and related works'?
 
@@
 
+% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before.
+
 %-------------------------------------------------
@@
 instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
-% Antonio - should we change the term 'classification' by 'regression' somehow?
+% Antonio - CONCERN - should we change the term 'classification' by 'regression' somehow?
 
@@
 %that separates two classes, maximising the margin between them.
-% Antonio - remove this classification thing due to a reviewer's comment 
+% Antonio - CONCERN - remove this classification thing due to a reviewer's comment 
 In regression problems, the algorithm chooses a hyperplane close to as many 
@@
 approximation problems.
-% Antonio - something about regression?
+% Antonio - CONCERN - something about regression?
 
@@
 
+% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before. And rewrite the initial paragraphs to separate it from section 4 (methodology)
+
 %-------------------------------------------------
@@
 % previous two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)
+% Antonio - TODO - revise them
 
@@
 \begin{table*}
-% Shouldn't this table go to "Problem description"? It is a
-% preliminary selection - JJ
-% Antonio - done
 \caption{Considered pre-sales features and their types. The third column shows
@@
 \begin{center}
-\resizebox{12cm}{!}{
+\resizebox{14cm}{!}{
 \begin{tabular}{|c|l|l|c|c|}
@@
 In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers probably will not want to use the results of other publishing companies for predicting their own sales.
-% Antonio - Think about this... should we mention this?
-% (Paloma) If you finally leave it, please review it because this last sentence is a bit confusing
-% Antonio - I guess it is now clearer
 
@@
 the sales of a new book, such as those related to seasonality, trends, or 
-promotions, that classical prediction methods can not deal with, since they are not included in the dataset due to the difficulty to model them. %FERGU: why?
-% Antonio - explained.
+promotions, that classical prediction methods can not deal with, since they are not included in the dataset due to the difficulty to model them. 
 However, an expert can consider them to modify the forecast obtained by 
@@
 \begin{center}
-  \epsfig{file=metodologia.eps,width=4cm}
+  \epsfig{file=metodologia.eps,width=5.5cm}
 \caption{Steps followed in the proposed methodology.}
@@
 
-%These are described in the following sections.
-
 Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}.
@@
 by a human expert to make predictions.
-% You have to present the problem and not the solution. It's not "what
-% you did last summer", it is SCIENCE. Why did you think FS was
-% needed? What procedure did you use for it?
-% Antonio - done
+
 In this stage, both numerical and visualisation-based approaches have been 
 applied, in order to select the best variables for the forecasting methods.  
-% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Coudl they be used with the same meaning?
-
+% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Could they be used with the same meaning?
+
+% Antonio - TODO: The next paragraph is referring to Section 2.1. We must change it.
 In Section \ref{subsec:select_method}, a selection of the best forecasting techniques that have been conducted has been reported, looking for those rule- or tree-based, together with numerical methods which could yield the best results.
@@
 Some specific interpretable models have been created as a final result of the work.
-%The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.
 
@@
 \cite{Selvakuberan2008}; however, this is a secondary objective in this work.
-%You need to lay out to the reader what you are going to do here. In
-%order to reach objective x, we need to do y, that is why we use
-%z. After using z, we prove that we have done y and thus reached
-%objective x. For instance - JJ
-% Antonio - Now it has been explained
-
-% You have to justify its application to this particular problem. What
-% was the runnning time with all variables? What reduction was your
-% target? - JJ
-% Antonio - I have explained before. The aim is not reducing the time, but the complexity of the obtained models in order to be more useful for a human
-
-% During the evaluation, the set of all possible features is analyzed in order 
-% to find the best set of features, ranking them according to some metric.
-% In this process, the feature's predictive ability along with the degree 
-% of redundancy between them is considered.
 
@@
   The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
-(predictive of) the class, yet uncorrelated with (not predictive of) each other''.
-This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.%Pablo: the Oxford dictionary accepts both (zed and sed), but the one with Z is the one that appears as main in the entry
+(predictive of) the class, yet uncorrelated with (not predictive of) each other''. This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.
  The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation.
@@
 adjacent areas on the grid.
-% It is a very useful analysis tool for visualising complex data with high number of variables in a simple geometric plane. 
-%Therefore, it could be used for different tasks such as feature selection and data clustering and visualisation. %Pablo: some cite here?
+
 This method is normally used as a data visualization tool, since it allows 
@@
 \begin{center}
-\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_Table5.eps}
+\includegraphics[scale=0.42]{./imgs/prediction_all_publisher_Table5.eps}
 \end{center}
@@
 \centering{}%
-\resizebox{12cm}{!}{
+\resizebox{14cm}{!}{
 \begin{tabular}{|c|l|l|l|}
@@
 Why don't we show also the results for the corresponding sets of features selected by each FS method?
+% Actually in the previous version there were several tables with these results than have been moved to the Appendix.
+I think we should include another figure fro them.
+They show important information.
+;)
 
@@
 
-Evaluation results of the obtained models (without performing any feature selection 
-method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
-(detailed numeric results can be shown in Tables \ref{Table:case1results} to \ref{Table:case4results} 
-in the appendix of tables at the end of this paper).
+Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
+(detailed numeric results can be seen in Tables \ref{Table:case1results_no_fs}, \ref{Table:case2results_no_fs}, \ref{Table:case3results_no_fs} and \ref{Table:case4results_no_fs} in the appendix of tables at the end of this paper).
 Results in this Figure show that the models performed similarly to the case of 
@@
 For clarity purpose, obtained results have been shown in Tables
-\ref{Table:case1results-RAE} to \ref{Table:case4resultsSOMFS}
+\ref{Table:case1results_no_fs} to \ref{Table:case4results_fs_som}
 in the appendix of tables at the end of this paper.
@@
 
-%Thus, the methodology presented here provides a reliable data processing technique for editorial data and also yields a reasonable result that allows publishers to forecast sales and then create the appropriate print run without incurring in losses.
-
 % -------- Future Work ---------
@@
 meta-algorithms \cite{huang2006ga,Mookiah2013_EA_Tuning,Shen2016_FFly_Tuning},  
-% Antonio - changed to include KBS references
 for instance.
@@
 
+\pagebreak
+
 \appendix
-\section{APENDIX TABLES}
+\section{APPENDIX TABLES}
+
+% ----------------------- Tables in the Appendix---------------------------
 
@@
 \label{tab:results_all_publishers_fs}}
+% CFSSUBEVAL
+\resizebox{12cm}{!}{
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{7}{|c|}{\textit{CfsSubsetEval}}\\
+\hline
+ & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
+\hline 
+M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
+\hline 
+kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
+\hline 
+RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
+\hline 
+LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
+\hline 
+SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
+\hline
+MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
+\hline
+ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
+\hline
+\end{tabular}
+}
 % RELIEFFATTRIBUTEEVAL
@@
 \hline
-
-\end{tabular}
-}
-% CFSSUBEVAL
-\resizebox{12cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{7}{|c|}{\textit{CfsSubsetEval}}\\
-\hline
- & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
-\hline 
-M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
-\hline 
-kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
-\hline 
-RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
-\hline 
-LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
-\hline 
-SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
-\hline
-MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
-\hline
-ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
-\hline
-
 \end{tabular}
@@
 
-%--------------- old Tables 7, 8, 9, 10 (before revision)
-
+% Antonio - I have reordered the tables correctly. ;D
+
+%--------------- old Table 7 (before revision)
 \begin{table*}
-\caption{Predicting \texttt{total\_sales} for publishing company UDL929 (the best selling publishing company). Best values in bold. }
+\caption{Predicting \texttt{total\_sales} for publishing company UDL929 (the best selling publishing company). Best values in bold. 
+\label{Table:case1results_no_fs}}
 \centering{}%
@@
 }
-\label{Table:case1results}
 \end{table*}
 
-\begin{table*}
-\caption{Predicting \texttt{total\_sales} for publishing company UDLW12 (the median selling publishing company). Best values in bold. }
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.
+\label{Table:case1results_fs_cf}}
 \centering{}%
@@
 \hline 
-M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
-\hline 
-kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
-\hline 
-LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
-\hline 
-SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
-\hline 
-MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
-\hline
-ELM & 	60.52	 $\pm$ 	0.39	 & 	24.28	 $\pm$ 	13.57	 & 	38.83	 $\pm$ 	26.43	 & 	118.09	 $\pm$ 	1.35	 & 	131.51	 $\pm$ 	1.37	 & 	0.0036	 $\pm$ 	0.01 \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case2results}
+M5P & \textbf{88.0 $\pm$0.13} & \textbf{738.28 $\pm$188.53} & \textbf{1141.79 $\pm$472.025} & \textbf{45.45 $\pm$13.62} & \textbf{47.58 $\pm$24.84} & 0.017 $\pm$0.002\tabularnewline
+\hline 
+kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
+\hline 
+MLP	& 87.67 $\pm$ 0.12	& 947.71 $\pm$ 388.67	& 1294.58 $\pm$ 458.44	& 58.62 $\pm$ 27.65	& 54.89 $\pm$ 27.53	& 0.04 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	87.25	 $\pm$ 	0.14	 & 	776.49	 $\pm$ 	209.23	 & 	1171.43	 $\pm$ 	455.5	 & 	53.63	 $\pm$ 	0.25	 & 	53.14	 $\pm$ 	0.37	 & 	0.0031	 $\pm$ 	0.01\tabularnewline
+\hline
+\end{tabular}
+}
 \end{table*}
 
-\begin{table*}
-\caption{Predicting \texttt{total\_sales} for publishing company UDL704 (highest number of different titles sold). Best values in bold.}
+% --- old table 11 (before revision)
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for publishing company UDL929 (ReliefFAttributeEval-FS). Best values in bold.
+\label{Table:case1results_fs_rf}}
 \centering{}%
@@
 \hline 
-M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
-\hline 
-kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
-\hline 
-LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
-\hline 
-SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
-\hline 
-MLP	& 80.83 $\pm$ 0.12	& 122.8 $\pm$ 56.86	& 207.12 $\pm$ 100.44	& 67.13 $\pm$ 31.38	& 78.14 $\pm$ 39.92	& 2.83 $\pm$ 0.012\tabularnewline
-\hline
-ELM & 	65.13	 $\pm$ 	0.21	 & 	336.33	 $\pm$ 	1414.85	 & 	1279.83	 $\pm$ 	7128.87	 & 	189.38	 $\pm$ 	7.49	 & 	501.38	 $\pm$ 	26.56	 & 	0.0042	 $\pm$ 	0.01
- \tabularnewline
-\hline
-
-\end{tabular}
-}
-\label{Table:case3results}
+M5P &  \textbf{90.5 $\pm$0.1} &  \textbf{661.81 $\pm$186.17} &  \textbf{1070.24 $\pm$425.66} &  \textbf{40.18 $\pm$10.50} &  \textbf{43.56 $\pm$19.77} & 0.02 $\pm$0.002\tabularnewline
+\hline 
+kNN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
+\hline 
+LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
+\hline 
+MLP	& 87.66 $\pm$ 0.14	& 897.02 $\pm$ 411.58	& 1332.54 $\pm$ 969.05	& 56.43 $\pm$ 33.1	& 58.52 $\pm$ 57.68	& 0.17 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	84.08	 $\pm$ 	0.17	 & 	890.49	 $\pm$ 	343.61	 & 	1470.33	 $\pm$ 	993.74	 & 	61.76	 $\pm$ 	0.32	 & 	65.14	 $\pm$ 	0.5	 & 	0.0119	 $\pm$ 	0.02 \tabularnewline
+\hline
+\end{tabular}
+}
 \end{table*}
 
-\begin{table*}
-\caption{Predicting \texttt{total\_sales} for publishing company UDLU11 (medium number of different books sold). Best values in bold.}
+\begin{table*}[!ht]
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL929 (SOM-FS). Best values in bold.
+\label{Table:case1results_fs_som}}
 \centering{}%
@@
 \hline 
-M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
-\hline 
-kNN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
-\hline 
-RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
-\hline 
-LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
-\hline 
-SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
-\hline 
-MLP	& 76.49 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
-\hline
-ELM & 	61.55	 $\pm$ 	0.24	 & 	1350.19	 $\pm$ 	3934.54	 & 	3681.73	 $\pm$ 	19380.44	 & 	140.16	 $\pm$ 	3.02	 & 	264.72	 $\pm$ 	10.87	 & 	0.009	 $\pm$ 	0.02
- \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case4results}
+M5P & \textbf{89.7 $\pm$0.10} & \textbf{685.67 $\pm$185.99} & \textbf{1116.42 $\pm$478.06} & \textbf{42.09 $\pm$12.8} & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
+\hline 
+kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & \textbf{46.25 $\pm$14.41} & \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
+\hline 
+LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
+\hline 
+MLP	& 87.02 $\pm$ 0.13	& 1015.85 $\pm$ 518.44	& 1603.91 $\pm$ 1145.56	& 61.99 $\pm$ 32.97	& 67.74 $\pm$ 62.08	& 0.11 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	83.44	 $\pm$ 	0.17	 & 	884.83	 $\pm$ 	297.95	 & 	1430.42	 $\pm$ 	874.32	 & 	64.61	 $\pm$ 	0.37	 & 	69.69	 $\pm$ 	0.68	 & 	0.002	 $\pm$ 	0.01\tabularnewline
+\hline
+\end{tabular}
+}
 \end{table*}
 
-%--------------- old Tables 11, 12, 13, 14 (before revision)
-
-\begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for publishing company UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
+%-----------------------------------
+
+%--------------- old Table 8 (before revision)
+\begin{table*}
+\caption{Predicting \texttt{total\_sales} for publishing company UDLW12 (the median selling publishing company). Best values in bold. 
+\label{Table:case2results_no_fs}}
 \centering{}%
@@
 \hline 
-M5P &  \textbf{90.5 $\pm$0.1} &  \textbf{661.81 $\pm$186.17} &  \textbf{1070.24 $\pm$425.66} &  \textbf{40.18 $\pm$10.50} &  \textbf{43.56 $\pm$19.77} & 0.02 $\pm$0.002\tabularnewline
-\hline 
-kNN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
-\hline 
-LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
-\hline 
-MLP	& 87.66 $\pm$ 0.14	& 897.02 $\pm$ 411.58	& 1332.54 $\pm$ 969.05	& 56.43 $\pm$ 33.1	& 58.52 $\pm$ 57.68	& 0.17 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	84.08	 $\pm$ 	0.17	 & 	890.49	 $\pm$ 	343.61	 & 	1470.33	 $\pm$ 	993.74	 & 	61.76	 $\pm$ 	0.32	 & 	65.14	 $\pm$ 	0.5	 & 	0.0119	 $\pm$ 	0.02 \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case1results-RAE}
+M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
+\hline 
+kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
+\hline 
+LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
+\hline 
+SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
+\hline
+ELM & 	60.52	 $\pm$ 	0.39	 & 	24.28	 $\pm$ 	13.57	 & 	38.83	 $\pm$ 	26.43	 & 	118.09	 $\pm$ 	1.35	 & 	131.51	 $\pm$ 	1.37	 & 	0.0036	 $\pm$ 	0.01 \tabularnewline
+\hline
+\end{tabular}
+}
 \end{table*}
@@
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for publishing company UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.
+\label{Table:case2results_fs_cf}}
 \centering{}%
@@
 \hline 
-M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
-\hline 
-kNN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
-\hline 
-RF &  \textbf{86.7 $\pm$0.16} & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
-\hline 
-LR & 84.4 $\pm$0.25 &  \textbf{12.79 $\pm$6.65} &  \textbf{21.52 $\pm$12.54} & 39.47 $\pm$23.35 &  \textbf{50.14 $\pm$35.26} & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 &  \textbf{38.24 $\pm$15.41} & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
-\hline 
-MLP	& 79.26 $\pm$ 0.27	& 20.28 $\pm$ 13.25	& 35.05 $\pm$ 29.44	& 61.89 $\pm$ 37.64	& 81.51 $\pm$ 63.39	& 0.07 $\pm$ 0.002\tabularnewline
-\hline 
-ELM & 	70.58	 $\pm$ 	0.34	 & 	19.52	 $\pm$ 	9.91	 & 	30.49	 $\pm$ 	18.09	 & 	145.28	 $\pm$ 	2.94	 & 	167.8	 $\pm$ 	3.39	 & 	0.0027	 $\pm$ 	0.01 \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case2results-RAE}
+M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
+\hline 
+kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 75.1 $\pm$0.26 & \textbf{15.61 $\pm$7.19} & 26.83 $\pm$13.36 & \textbf{47.38 $\pm$20.10} & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
+\hline 
+LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & \textbf{25.49 $\pm$11.63} & 47.97 $\pm$18.85 & \textbf{60.28 $\pm$30.62} & 0.0002 $\pm$0.0004\tabularnewline
+\hline 
+SVM & \textbf{81.8 $\pm$0.21} & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 80.08 $\pm$ 0.25	& 19.6 $\pm$ 11.66	& 29.32 $\pm$ 14.5	& 59.97 $\pm$ 35.66	& 70.05 $\pm$ 42.31	& 0.02 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	77.62	 $\pm$ 	0.3	 & 	16.53	 $\pm$ 	9.12	 & 	27.18	 $\pm$ 	18.2	 & 	72.75	 $\pm$ 	0.64	 & 	86.09	 $\pm$ 	0.86	 & 	0.0012	 $\pm$ 	0.01\tabularnewline
+
+\hline
+\end{tabular}
+}
 \end{table*}
 
+% --- old table 12 (before revision)
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for publishing company UDL704 (ReliefFAttributeEval-FS). Best values in bold. }
+\caption{Predicting \texttt{total\_sales} for publishing company UDLW12 (ReliefFAttributeEval-FS). Best values in bold.
+\label{Table:case2results_fs_rf}}
 \centering{}%
@@
 \hline 
-M5P  &  \textbf{89.3 $\pm$0.08}  &  \textbf{69.70 $\pm$19.85}  &  \textbf{122.48 $\pm$47.28}  & {38.49 $\pm$11.53}  &  \textbf{46.68 $\pm$16.02} & 0.028 $\pm$0.003\tabularnewline
-\hline 
-kNN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
-\hline 
-LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
-\hline 
-SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
-\hline 
-MLP	& 84.11 $\pm$ 0.13	& 104.55 $\pm$ 50.32	& 180.42 $\pm$ 87.44	& 56.99 $\pm$ 26.01	& 67.68 $\pm$ 32.15	& 0.22 $\pm$ 0.003\tabularnewline
-\hline
-ELM & 	83.47	 $\pm$ 	0.1	 & 	89.65	 $\pm$ 	25.9	 & 	167.99	 $\pm$ 	82.63	 & 	51.51	 $\pm$ 	0.14	 & 	65.11	 $\pm$ 	0.28	 & 	0.0041	 $\pm$ 	0.01\tabularnewline
-\hline
-
-\end{tabular}
-}
-\label{Table:case3results-RAE}
+M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
+\hline 
+kNN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
+\hline 
+RF &  \textbf{86.7 $\pm$0.16} & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
+\hline 
+LR & 84.4 $\pm$0.25 &  \textbf{12.79 $\pm$6.65} &  \textbf{21.52 $\pm$12.54} & 39.47 $\pm$23.35 &  \textbf{50.14 $\pm$35.26} & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 &  \textbf{38.24 $\pm$15.41} & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
+\hline 
+MLP	& 79.26 $\pm$ 0.27	& 20.28 $\pm$ 13.25	& 35.05 $\pm$ 29.44	& 61.89 $\pm$ 37.64	& 81.51 $\pm$ 63.39	& 0.07 $\pm$ 0.002\tabularnewline
+\hline 
+ELM & 	70.58	 $\pm$ 	0.34	 & 	19.52	 $\pm$ 	9.91	 & 	30.49	 $\pm$ 	18.09	 & 	145.28	 $\pm$ 	2.94	 & 	167.8	 $\pm$ 	3.39	 & 	0.0027	 $\pm$ 	0.01 \tabularnewline
+\hline
+\end{tabular}
+}
 \end{table*}
@@
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for publishing company UDLU11 (ReliefFAttributeEval-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLW12 (SOM-FS). Best values in bold.
+\label{Table:case2results_fs_som}}
 \centering{}%
@@
 \hline 
-M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
-\hline 
-kNN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF &  \textbf{85.3 $\pm$0.09} &  \textbf{455.7 $\pm$123.96} &  \textbf{686.54 $\pm$198.16} &  \textbf{46.32 $\pm$10.20} &  \textbf{53.03 $\pm$13.05} & 0.07 $\pm$0.003\tabularnewline
-\hline 
-LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 77.3 $\pm$ 0.13	& 709.2 $\pm$ 235.87	& 960.43 $\pm$ 345.28	& 73.11 $\pm$ 24.95	& 75.19 $\pm$ 25.74	& 0.14 $\pm$ 0.003\tabularnewline
-\hline
-ELM & 	79.73	 $\pm$ 	0.14	 & 	569.2	 $\pm$ 	161.37	 & 	841.75	 $\pm$ 	322.13	 & 	61.87	 $\pm$ 	0.21	 & 	69.99	 $\pm$ 	0.3	 & 	0.007	 $\pm$ 	0.02 \tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case4results-RAE}
+M5P & \textbf{86.0 $\pm$0.19} & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
+\hline 
+kNN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & \textbf{0 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 85.5 $\pm$0.19 & \textbf{13.66 $\pm$6.47} & \textbf{22.51 $\pm$11.03} & \textbf{41.38 $\pm$17.87} & \textbf{52.20 $\pm$27.09} & 0.026 $\pm$0.0019\tabularnewline
+\hline 
+LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 77.76 $\pm$ 0.33	& 19.24 $\pm$ 11.58	& 33.05 $\pm$ 24.27	& 59.53 $\pm$ 36.38	& 78.43 $\pm$ 57.62	& 0.05 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	73.42	 $\pm$ 	0.31	 & 	20.08	 $\pm$ 	9.8	 & 	31.45	 $\pm$ 	18.84	 & 	85.55	 $\pm$ 	0.6	 & 	93.42	 $\pm$ 	0.64	 & 	0.0036	 $\pm$ 	0.01\tabularnewline
+\hline
+\end{tabular}
+}
 \end{table*}
 
-%--------------- Tables in the Appendix
-
-\begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL704 (CfsSubsetEval-FS). Best values in bold.}
+%-----------------------------------
+
+%--------------- old Table 9 (before revision)
+\begin{table*}
+\caption{Predicting \texttt{total\_sales} for publishing company UDL704 (highest number of different titles sold). Best values in bold.
+\label{Table:case3results_no_fs}}
 \centering{}%
@@
 \hline 
-M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
-\hline 
-kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & \textbf{170.83 $\pm$46.34} & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
-\hline 
-LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & \textbf{81.8 $\pm$0.08} & \textbf{94.29 $\pm$25.52} & 180.54 $\pm$62.67 & \textbf{50.79 $\pm$8.48} & \textbf{65.62 $\pm$6.25} & 0.040 $\pm$0.02\tabularnewline
-\hline 
-MLP	& 81.28 $\pm$ 0.11	& 135.01 $\pm$ 56.89	& 193.56 $\pm$ 61.91	& 74.12 $\pm$ 31.58	& 75.43 $\pm$ 28.35	& 0.05 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	78.42	 $\pm$ 	0.15	 & 	109.24	 $\pm$ 	52.6	 & 	203.11	 $\pm$ 	215.35	 & 	62.28	 $\pm$ 	0.24	 & 	78.75	 $\pm$ 	0.68	 & 	0.0019	 $\pm$ 	0.01 \tabularnewline
-\hline
+M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
+\hline 
+kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
+\hline 
+LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
+\hline 
+MLP	& 80.83 $\pm$ 0.12	& 122.8 $\pm$ 56.86	& 207.12 $\pm$ 100.44	& 67.13 $\pm$ 31.38	& 78.14 $\pm$ 39.92	& 2.83 $\pm$ 0.012\tabularnewline
+\hline
+ELM & 	65.13	 $\pm$ 	0.21	 & 	336.33	 $\pm$ 	1414.85	 & 	1279.83	 $\pm$ 	7128.87	 & 	189.38	 $\pm$ 	7.49	 & 	501.38	 $\pm$ 	26.56	 & 	0.0042	 $\pm$ 	0.01
+ \tabularnewline
+\hline
+
 \end{tabular}
@@
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL704 (SOM-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL704 (CfsSubsetEval-FS). Best values in bold.
+\label{Table:case3results_fs_cf}}
 \centering{}%
@@
 \hline 
-M5P & \textbf{89.2 $\pm$0.07} & \textbf{71.536 $\pm$18.95} & \textbf{123.06 $\pm$42.13} & \textbf{39.43 $\pm$10.58} & \textbf{47.20 $\pm$15.16} & 0.031 $\pm$0.007\tabularnewline
-\hline 
-kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
-\hline 
-LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
-\hline 
-MLP	& 87.25 $\pm$ 0.09	& 98.45 $\pm$ 46.65	& 156.48 $\pm$ 62.89	& 53.68 $\pm$ 23.35	& 59.5 $\pm$ 22.56	& 0.15 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	85.22	 $\pm$ 	0.11	 & 	85.57	 $\pm$ 	25.92	 & 	141.17	 $\pm$ 	62.02	 & 	49.48	 $\pm$ 	0.16	 & 	56.58	 $\pm$ 	0.25	 & 	0.0014	 $\pm$ 	0.01\tabularnewline
+M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
+\hline 
+kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & \textbf{170.83 $\pm$46.34} & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
+\hline 
+LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & \textbf{81.8 $\pm$0.08} & \textbf{94.29 $\pm$25.52} & 180.54 $\pm$62.67 & \textbf{50.79 $\pm$8.48} & \textbf{65.62 $\pm$6.25} & 0.040 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 81.28 $\pm$ 0.11	& 135.01 $\pm$ 56.89	& 193.56 $\pm$ 61.91	& 74.12 $\pm$ 31.58	& 75.43 $\pm$ 28.35	& 0.05 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	78.42	 $\pm$ 	0.15	 & 	109.24	 $\pm$ 	52.6	 & 	203.11	 $\pm$ 	215.35	 & 	62.28	 $\pm$ 	0.24	 & 	78.75	 $\pm$ 	0.68	 & 	0.0019	 $\pm$ 	0.01 \tabularnewline
 \hline
@@
 
-%-----------------------------------
-
+% --- old table 13 (before revision)
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for publishing company UDL704 (ReliefFAttributeEval-FS). Best values in bold. 
+\label{Table:case3results_fs_rf}}
 \centering{}%
@@
 \hline 
-M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
-\hline 
-kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & \textbf{1008.39 $\pm$305.87} & 71.41 $\pm$13.95 & \textbf{78.47 $\pm$22.70} & \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF & 65.3 $\pm$0.19 & \textbf{685.56 $\pm$195.28} & 1021.37 $\pm$352.88 & \textbf{69.74 $\pm$16.96} & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
-\hline 
-LR & \textbf{67.0 $\pm$0.23}\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 66.09 $\pm$ 0.21	& 817.79 $\pm$ 242.44	& 1127.02 $\pm$ 381.75	& 84.48 $\pm$ 27.39	& 88.59 $\pm$ 33.21	& 0.03 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	65.66	 $\pm$ 	0.25	 & 	859.21	 $\pm$ 	836.34	 & 	1691.61	 $\pm$ 	3053.2	 & 	92.4	 $\pm$ 	0.81	 & 	134.53	 $\pm$ 	2.18	 & 	0.0009	 $\pm$ 	0.01 \tabularnewline
-\hline
+M5P  &  \textbf{89.3 $\pm$0.08}  &  \textbf{69.70 $\pm$19.85}  &  \textbf{122.48 $\pm$47.28}  & {38.49 $\pm$11.53}  &  \textbf{46.68 $\pm$16.02} & 0.028 $\pm$0.003\tabularnewline
+\hline 
+kNN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
+\hline 
+LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
+\hline 
+SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 84.11 $\pm$ 0.13	& 104.55 $\pm$ 50.32	& 180.42 $\pm$ 87.44	& 56.99 $\pm$ 26.01	& 67.68 $\pm$ 32.15	& 0.22 $\pm$ 0.003\tabularnewline
+\hline
+ELM & 	83.47	 $\pm$ 	0.1	 & 	89.65	 $\pm$ 	25.9	 & 	167.99	 $\pm$ 	82.63	 & 	51.51	 $\pm$ 	0.14	 & 	65.11	 $\pm$ 	0.28	 & 	0.0041	 $\pm$ 	0.01\tabularnewline
+\hline
+
 \end{tabular}
@@
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLU11 (SOM-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL704 (SOM-FS). Best values in bold.
+\label{Table:case3results_fs_som}}
 \centering{}%
@@
 \hline 
-M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
-\hline 
-kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & \textbf{0 $\pm$0.0002}\tabularnewline
-\hline 
-RF & \textbf{85.6 $\pm$0.08} & \textbf{446.25 $\pm$119.79} & \textbf{673.46 $\pm$189.06} & \textbf{45.38 $\pm$9.78} & \textbf{52.24 $\pm$13.09} & 0.0594 $\pm$0.0049\tabularnewline
-\hline 
-LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 77.06 $\pm$ 0.18	& 714.48 $\pm$ 259.22	& 1025.29 $\pm$ 569.79	& 74.3 $\pm$ 29.92	& 81.44 $\pm$ 47.9	& 0.09 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	79.52	 $\pm$ 	0.12	 & 	606.38	 $\pm$ 	153.83	 & 	818.18	 $\pm$ 	243.54	 & 	65.7	 $\pm$ 	0.18	 & 	67.17	 $\pm$ 	0.21	 & 	0.0044	 $\pm$ 	0.01 \tabularnewline
+M5P & \textbf{89.2 $\pm$0.07} & \textbf{71.536 $\pm$18.95} & \textbf{123.06 $\pm$42.13} & \textbf{39.43 $\pm$10.58} & \textbf{47.20 $\pm$15.16} & 0.031 $\pm$0.007\tabularnewline
+\hline 
+kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
+\hline 
+LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
+\hline 
+MLP	& 87.25 $\pm$ 0.09	& 98.45 $\pm$ 46.65	& 156.48 $\pm$ 62.89	& 53.68 $\pm$ 23.35	& 59.5 $\pm$ 22.56	& 0.15 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	85.22	 $\pm$ 	0.11	 & 	85.57	 $\pm$ 	25.92	 & 	141.17	 $\pm$ 	62.02	 & 	49.48	 $\pm$ 	0.16	 & 	56.58	 $\pm$ 	0.25	 & 	0.0014	 $\pm$ 	0.01\tabularnewline
 \hline
@@
 
-\begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.}
+%--------------- old Table 11 (before revision)
+\begin{table*}
+\caption{Predicting \texttt{total\_sales} for publishing company UDLU11 (medium number of different books sold). Best values in bold.
+\label{Table:case4results_no_fs}}
 \centering{}%
@@
 \hline 
-M5P & \textbf{88.0 $\pm$0.13} & \textbf{738.28 $\pm$188.53} & \textbf{1141.79 $\pm$472.025} & \textbf{45.45 $\pm$13.62} & \textbf{47.58 $\pm$24.84} & 0.017 $\pm$0.002\tabularnewline
-\hline 
-kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
-\hline 
-RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
-\hline 
-LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
-\hline 
-MLP	& 87.67 $\pm$ 0.12	& 947.71 $\pm$ 388.67	& 1294.58 $\pm$ 458.44	& 58.62 $\pm$ 27.65	& 54.89 $\pm$ 27.53	& 0.04 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	87.25	 $\pm$ 	0.14	 & 	776.49	 $\pm$ 	209.23	 & 	1171.43	 $\pm$ 	455.5	 & 	53.63	 $\pm$ 	0.25	 & 	53.14	 $\pm$ 	0.37	 & 	0.0031	 $\pm$ 	0.01\tabularnewline
+M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
+\hline 
+kNN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
+\hline 
+RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
+\hline 
+LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
+\hline 
+SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
+\hline 
+MLP	& 76.49 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
+\hline
+ELM & 	61.55	 $\pm$ 	0.24	 & 	1350.19	 $\pm$ 	3934.54	 & 	3681.73	 $\pm$ 	19380.44	 & 	140.16	 $\pm$ 	3.02	 & 	264.72	 $\pm$ 	10.87	 & 	0.009	 $\pm$ 	0.02
+ \tabularnewline
 \hline
@@
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for PublishingCo-UDL929 (SOM-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.
+\label{Table:case4results_fs_cf}}
 \centering{}%
@@
 \hline 
-M5P & \textbf{89.7 $\pm$0.10} & \textbf{685.67 $\pm$185.99} & \textbf{1116.42 $\pm$478.06} & \textbf{42.09 $\pm$12.8} & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
-\hline 
-kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & \textbf{46.25 $\pm$14.41} & \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
-\hline 
-LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
-\hline 
-MLP	& 87.02 $\pm$ 0.13	& 1015.85 $\pm$ 518.44	& 1603.91 $\pm$ 1145.56	& 61.99 $\pm$ 32.97	& 67.74 $\pm$ 62.08	& 0.11 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	83.44	 $\pm$ 	0.17	 & 	884.83	 $\pm$ 	297.95	 & 	1430.42	 $\pm$ 	874.32	 & 	64.61	 $\pm$ 	0.37	 & 	69.69	 $\pm$ 	0.68	 & 	0.002	 $\pm$ 	0.01\tabularnewline
+M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
+\hline 
+kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & \textbf{1008.39 $\pm$305.87} & 71.41 $\pm$13.95 & \textbf{78.47 $\pm$22.70} & \textbf{0.0001 $\pm$0.0002}\tabularnewline
+\hline 
+RF & 65.3 $\pm$0.19 & \textbf{685.56 $\pm$195.28} & 1021.37 $\pm$352.88 & \textbf{69.74 $\pm$16.96} & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
+\hline 
+LR & \textbf{67.0 $\pm$0.23}\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 66.09 $\pm$ 0.21	& 817.79 $\pm$ 242.44	& 1127.02 $\pm$ 381.75	& 84.48 $\pm$ 27.39	& 88.59 $\pm$ 33.21	& 0.03 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	65.66	 $\pm$ 	0.25	 & 	859.21	 $\pm$ 	836.34	 & 	1691.61	 $\pm$ 	3053.2	 & 	92.4	 $\pm$ 	0.81	 & 	134.53	 $\pm$ 	2.18	 & 	0.0009	 $\pm$ 	0.01 \tabularnewline
 \hline
@@
 
-%-----------------------------------
-
+% --- old table 14 (before revision)
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for publishing company UDLU11 (ReliefFAttributeEval-FS). Best values in bold.
+\label{Table:case4results_fs_rf}}
 \centering{}%
@@
 \hline 
-M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
-\hline 
-kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
-\hline 
-RF & 75.1 $\pm$0.26 & \textbf{15.61 $\pm$7.19} & 26.83 $\pm$13.36 & \textbf{47.38 $\pm$20.10} & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
-\hline 
-LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & \textbf{25.49 $\pm$11.63} & 47.97 $\pm$18.85 & \textbf{60.28 $\pm$30.62} & 0.0002 $\pm$0.0004\tabularnewline
-\hline 
-SVM & \textbf{81.8 $\pm$0.21} & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 80.08 $\pm$ 0.25	& 19.6 $\pm$ 11.66	& 29.32 $\pm$ 14.5	& 59.97 $\pm$ 35.66	& 70.05 $\pm$ 42.31	& 0.02 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	77.62	 $\pm$ 	0.3	 & 	16.53	 $\pm$ 	9.12	 & 	27.18	 $\pm$ 	18.2	 & 	72.75	 $\pm$ 	0.64	 & 	86.09	 $\pm$ 	0.86	 & 	0.0012	 $\pm$ 	0.01\tabularnewline
-
+M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
+\hline 
+kNN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
+\hline 
+RF &  \textbf{85.3 $\pm$0.09} &  \textbf{455.7 $\pm$123.96} &  \textbf{686.54 $\pm$198.16} &  \textbf{46.32 $\pm$10.20} &  \textbf{53.03 $\pm$13.05} & 0.07 $\pm$0.003\tabularnewline
+\hline 
+LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 77.3 $\pm$ 0.13	& 709.2 $\pm$ 235.87	& 960.43 $\pm$ 345.28	& 73.11 $\pm$ 24.95	& 75.19 $\pm$ 25.74	& 0.14 $\pm$ 0.003\tabularnewline
+\hline
+ELM & 	79.73	 $\pm$ 	0.14	 & 	569.2	 $\pm$ 	161.37	 & 	841.75	 $\pm$ 	322.13	 & 	61.87	 $\pm$ 	0.21	 & 	69.99	 $\pm$ 	0.3	 & 	0.007	 $\pm$ 	0.02 \tabularnewline
 \hline
@@
 \begin{table*}[!ht]
-\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLW12 (SOM-FS). Best values in bold.}
+\caption{Predicting \texttt{total\_sales} for PublishingCo-UDLU11 (SOM-FS). Best values in bold.
+\label{Table:case4results_fs_som}}
 \centering{}%
@@
 \hline 
-M5P & \textbf{86.0 $\pm$0.19} & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
-\hline 
-kNN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & \textbf{0 $\pm$0.0002}\tabularnewline
-\hline 
-RF & 85.5 $\pm$0.19 & \textbf{13.66 $\pm$6.47} & \textbf{22.51 $\pm$11.03} & \textbf{41.38 $\pm$17.87} & \textbf{52.20 $\pm$27.09} & 0.026 $\pm$0.0019\tabularnewline
-\hline 
-LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
-\hline 
-SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
-\hline 
-MLP	& 77.76 $\pm$ 0.33	& 19.24 $\pm$ 11.58	& 33.05 $\pm$ 24.27	& 59.53 $\pm$ 36.38	& 78.43 $\pm$ 57.62	& 0.05 $\pm$ 0.002\tabularnewline
-\hline
-ELM & 	73.42	 $\pm$ 	0.31	 & 	20.08	 $\pm$ 	9.8	 & 	31.45	 $\pm$ 	18.84	 & 	85.55	 $\pm$ 	0.6	 & 	93.42	 $\pm$ 	0.64	 & 	0.0036	 $\pm$ 	0.01\tabularnewline
-\hline
-\end{tabular}
-}
-\label{Table:case4resultsSOMFS}
+M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
+\hline 
+kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & \textbf{0 $\pm$0.0002}\tabularnewline
+\hline 
+RF & \textbf{85.6 $\pm$0.08} & \textbf{446.25 $\pm$119.79} & \textbf{673.46 $\pm$189.06} & \textbf{45.38 $\pm$9.78} & \textbf{52.24 $\pm$13.09} & 0.0594 $\pm$0.0049\tabularnewline
+\hline 
+LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
+\hline 
+SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
+\hline 
+MLP	& 77.06 $\pm$ 0.18	& 714.48 $\pm$ 259.22	& 1025.29 $\pm$ 569.79	& 74.3 $\pm$ 29.92	& 81.44 $\pm$ 47.9	& 0.09 $\pm$ 0.002\tabularnewline
+\hline
+ELM & 	79.52	 $\pm$ 	0.12	 & 	606.38	 $\pm$ 	153.83	 & 	818.18	 $\pm$ 	243.54	 & 	65.7	 $\pm$ 	0.18	 & 	67.17	 $\pm$ 	0.21	 & 	0.0044	 $\pm$ 	0.01 \tabularnewline
+\hline
+\end{tabular}
+}
 \end{table*}

### 2016-09-07 paper.tex
commenting some TODOs and CONCERNs

@@
 % Antonio - TODO: Since two new sections have been added here, maybe we should change the title of the section... Maybe 'Background and related works'?
+% I don't see how or what the new title might change ....  ???   we can discuss this item later this morning.
 
@@
 % Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before.
+Many of the previous papers propose using different prediction methods.
+Thus, next subsections describe several forecasting methods and different 
+evaluation criteria, commonly used in the bibliography that have been chosen 
+to face the problem at hand.
 
@@
 % Antonio - CONCERN - should we change the term 'classification' by 'regression' somehow?
+% I don't think so in this case. That is what kNN is...
 
@@
 % Antonio - CONCERN - remove this classification thing due to a reviewer's comment 
+% ok    :)
 In regression problems, the algorithm chooses a hyperplane close to as many 
@@
 % Antonio - CONCERN - something about regression?
+% in that sentence, approximation is used as synonymous of regression   ;)
 
@@
 % Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before. And rewrite the initial paragraphs to separate it from section 4 (methodology)
+% I have addressed this "todo" before (lin. 353)
 
@@
 % Antonio - TODO - revise them
+% What have to be revised?   :/
 
@@
 
-With regard to the feature \textit{publisher}, it has been removed from the final dataset since it is indeed included in the code of \texttt{collection}.
-In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers probably will not want to use the results of other publishing companies for predicting their own sales.
+With regard to the feature \textit{publisher}, it has been removed from the 
+final dataset since it is indeed included in the code of \texttt{collection}. 
+In addition, we think it is not really relevant for the accuracy of the models 
+and, moreover, publishers probably will not want to use the results of other 
+publishing companies for predicting their own sales.
 
@@
 the sales of a new book, such as those related to seasonality, trends, or 
-promotions, that classical prediction methods can not deal with, since they are not included in the dataset due to the difficulty to model them. 
+promotions, that classical prediction methods can not deal with, since they 
+are not included in the dataset due to the difficulty to model them. 
 However, an expert can consider them to modify the forecast obtained by 
@@
 % Antonio - Should we speak about 'forecasting' or 'regression', Sam? Could they be used with the same meaning?
+% I think so.
 
 % Antonio - TODO: The next paragraph is referring to Section 2.1. We must change it.
-In Section \ref{subsec:select_method}, a selection of the best forecasting techniques that have been conducted has been reported, looking for those rule- or tree-based, together with numerical methods which could yield the best results.
-
-Once the models and results have been obtained for the whole dataset (Section \ref{sec:experiments}), the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}).
+% Why? anyway, I add "As stated before,"
+As stated before, in Section \ref{subsec:select_method} a selection of the best 
+forecasting techniques that have been conducted has been reported, looking for 
+those rule- or tree-based, together with numerical methods which could yield 
+the best results.
+
+Once the models and results have been obtained for the whole dataset 
+(Section \ref{sec:experiments}), the same methodology has been applied to some 
+specific cases of publishing companies in order to prove the value of the 
+proposal (Section \ref{sec:example_cases}).
 Some specific interpretable models have been created as a final result of the work.
@@
 and to choose an appropriate set of variables, the Self-Organizing Map
-(SOM) \cite{kohonen1998} method has also been applied as a `subjective' (based on expert's opinion) FS technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.
+(SOM) \cite{kohonen1998} method has also been applied as a `subjective' 
+(based on expert's opinion) FS technique based on the visualisation of the 
+data as a set of 2D planes (one per feature of the dataset), and their 
+interpretation for finding out relationships between these features.
 
@@
 % Antonio - a better description of U-Matrix. ;D
+% thanks!
 
@@
 ;)
+% we can discuss this point later this morning. If necessary, we can design and include a new plot.
 
@@
 % Antonio - I have reordered the tables correctly. ;D
+% thanks!!! (again)
 

### 2016-09-07 Response to reviewers.tex
commenting some TODOs and CONCERNs
commenting comments

@@
 \end{verbatim}
-% Antonio - TODO: say where is this clarification in the text (page/paragraph) and/or copy the text here
+% Antonio - TODO: say where is this clarification in the text (page/paragraph) 
 \begin{verbatim}
@@
 \end{verbatim}
-% Antonio - TODO: say where is this clarification in the text (page/paragraph) and/or copy the text here
+% Antonio - TODO: say where is this clarification in the text (page/paragraph)
 
@@
 % Antonio - CONCERN: I'm a bit afraid about the term 'organize' which I don't know if has been addressed in any way in the new version...
+% you are right... but the way the reviewer has expressed it is quite strange.
 
@@
 % Antonio - TODO: show some examples of reduced text (page/paragraph), there will be some new figures, I think.
+% we have to say: "Paragraph #X in subsection #Y" (naming the paragraphs that we identified and gathered-joined)
 
@@
 % Antonio - TODO: Complete with the number of tables and figures, along with the new references
+% I don't know what references have been added in this revision. I'll ask Hossam.
 
@@
 And also emphasize the contribution to the SotA.
+% well, no previous work on "print run & book sales prediction" has been done (at least, I have not found anything in the bibliography)
 
@@
 \end{verbatim}
-% Antonio - TODO: put the correct page when the text is finished. Cooy the text here.
+% Antonio - TODO: put the correct page when the text is finished
 
@@
 % Antonio - TODO: Talk about the final tables and figures.
+% Let's talk about them!   :)
 
@@
 % Antonio - TODO: we have also to link them properly to the new section and to remove them from the text describing Section 4 where they were... Then, say this in the response.
+% I have linked them, but I think we should leave that sentence in Section 4 refering to the methods we have used.
 
@@
 % Antonio - TODO: Improve the figure, which is a bit 'generic'. Put the correct figure and page.
+% Almost every paper I have read (and that has been cited in the SotA) shows a very generic flowchat
 
@@
 We have improved Section 5, including the parameter settings of 
-M5P, kNN and RF methods.
+M5P, kNN and RF methods (see paragraph XX at page YY).
 
@@
 % Could we use a table for showing them easily?
-% Antonio - TODO: say paragraph/page where they are and maybe put here the text.
+% Antonio - TODO: say paragraph/page where they are.
+
+% Antonio - TODO: Say if there are new references and include them in a final section in this letter.
+% yes, there are some, but is Hossam who knows what references have been added in this revision.
+%------------------------------------------------------------------------------------
+\section{New references added in this revision}
+
+[XX] Authors, Title, Journal, pages, Year
+
+[YY] Authors, Title, Journal, pages, Year
+
+[ZZ] Authors, Title, Journal, pages, Year
 
 \end{document}
-% Antonio - TODO: Say if there are new references and include them in a final section in this letter.

### 2016-09-07 paper.tex
clarifying some details in section-6

@@
 
-Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
-(detailed numeric results can be seen in Tables \ref{Table:case1results_no_fs}, \ref{Table:case2results_no_fs}, \ref{Table:case3results_no_fs} and \ref{Table:case4results_no_fs} in the appendix of tables at the end of this paper).
+Evaluation results of the obtained models (without performing any feature selection 
+method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
+(detailed numeric results can be seen in Tables 
+\ref{Table:case1results_no_fs}, \ref{Table:case2results_no_fs}, 
+\ref{Table:case3results_no_fs} and \ref{Table:case4results_no_fs} 
+in the appendix of tables at the end of this paper).
 Results in this Figure show that the models performed similarly to the case of 
@@
 leverage when deciding how much to print. 
-For clarity purpose, obtained results have been shown in Tables
-\ref{Table:case1results_no_fs} to \ref{Table:case4results_fs_som}
+For clarity purpose, obtained results after applying feature selection methods
+have been shown in Tables \ref{Table:case1results_no_fs} to \ref{Table:case4results_fs_som}
 in the appendix of tables at the end of this paper.

### 2016-09-07 paper.tex
clarifying some details in section-6
solving some TODOs

@@
 %********************************************************************************
-\section{State of the art on sales forecasting} 
+\section{Background and State of the art on sales forecasting} 
 \label{sec:soa}
-% Antonio - TODO: Since two new sections have been added here, maybe we should change the title of the section... Maybe 'Background and related works'?
-% I don't see how or what the new title might change ....  ???   we can discuss this item later this morning.
 
@@
 
-% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before.
 Many of the previous papers propose using different prediction methods.
 Thus, next subsections describe several forecasting methods and different 
-evaluation criteria, commonly used in the bibliography that have been chosen 
+evaluation metrics, commonly used in the bibliography that have been chosen 
 to face the problem at hand.
@@
 %-------------------------------------------------
-\subsection{Selecting an appropriate forecasting method}
+\subsection{Regression methods}
 \label{subsec:select_method}
@@
 
-Thus, in this research five forecasting methods, based on the State of the Art 
+Thus, in this research six forecasting methods, based on the State of the Art 
 literature review (see above, Section \ref{sec:soa}) 
@@
 \end{center}
-\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation).
+\caption{Boxplots showing the values obtained predicting \texttt{total\_sales}, using all features, with different regression methods (30 repetitions, 10-fold cross validation).
 Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
-Just the features selected by ReliefFAttributeEval method have been considered.}
+% Just the features selected by ReliefFAttributeEval method have been considered.
+}
 \label{fig:attributeAll}
@@
 ;)
-% we can discuss this point later this morning. If necessary, we can design and include a new plot.
+% we can discuss this point later this morning.
+% The thing is that in this plot we are using all features!! (here, no feature selection method has been used)
 
@@
 For the rest of the results which are obtained by CSE and SOM feature selection methods we refer the reader to the appendix of tables at the end of this paper.
+
+% [pedro]  TODO => una vez hecha la nueva figura, volver a meter este comentario anterior (lin.1297)
 

### 2016-09-07 Response to reviewers.tex
commenting comments
commenting in the responses

@@
 % Antonio - TODO: say where are these results (table/figure/page)
+% [pedro] TODO => decir que se han añadido ciertas refs sobre ELM
 
@@
 The reviewer is right, thus, we have revised the whole paper referring 
-to the term `regression' instead of `classification'. Moreover this have 
-been also addressed solving the issue related to comment #1, where the
-application procedure of feature selection methods for regression problems 
-has been clarified. 
+to the term `regression' instead of `classification'. 
+In addition, some sections have been renamed, such as subsection 2.1, 
+in order to better suit the regression viewpoint.
+Moreover this have been also addressed solving the issue related 
+to comment #1, where the application procedure of feature selection 
+methods for regression problems has been clarified. 
 \end{verbatim}
 % Antonio - CONCERN: I'm a bit afraid about the term 'organize' which I don't know if has been addressed in any way in the new version...
-% you are right... but the way the reviewer has expressed it is quite strange.
+% [Pedro] you are right... but the way the reviewer has expressed it is quite strange.
+% [Hossam]: Regarding your first concern, the reviewer asked for organizing and writing not reorganizing, so we have just addressed that by emphasizing the term regression in all the paper and we have clarified how we applied the FS methods customized for regression problems.
+So I think we addressed this issue adequately.
 
@@
 text and several paragraphs have been rewritten in order to make 
-them shorter, clearer and to improve its comprehension.
+them shorter, clearer and to improve its comprehension 
+(i.e. paragraph XX in page YY, and paragraph XX in page YY).
 
 Also, several tables have been moved to the Appendix and that
-data has been presented now as the new Figure 3.
+data has been presented now as the new Figures XX, YY, ZZ.
 
@@
 And also emphasize the contribution to the SotA.
-% well, no previous work on "print run & book sales prediction" has been done (at least, I have not found anything in the bibliography)
+% [Pedro] well, no previous work on "print run & book sales prediction" has been done (at least, I have not found anything in the bibliography)
+% [Hossam] about the contribution, I agree with you. We can mention that we used real data in our work.
 
@@
 the Appendix and that data has been summarized and presented 
-as the new Figure 3 in order to make that numeric data clearer 
+as the new Figures XX, YY, ZZ in order to make that numeric data clearer 
 and to improve their comprehension.
@@
 \end{verbatim}
-% Antonio - TODO: we have also to link them properly to the new section and to remove them from the text describing Section 4 where they were... Then, say this in the response.
-% I have linked them, but I think we should leave that sentence in Section 4 refering to the methods we have used.
 
@@
 % Could we use a table for showing them easily?
+% [pedro] TODO: design the table taken the parameters/values shown in section 5.1
 % Antonio - TODO: say paragraph/page where they are.

### 2016-09-07 paper.tex
solving some TODOs

@@
 
-% Antonio - TODO: The next paragraph is referring to Section 2.1. We must change it.
-% Why? anyway, I add "As stated before,"
-As stated before, in Section \ref{subsec:select_method} a selection of the best 
-forecasting techniques that have been conducted has been reported, looking for 
-those rule- or tree-based, together with numerical methods which could yield 
-the best results.
+As stated before, in Section \ref{subsec:select_method}, a selection of the best 
+forecasting techniques has been reported, looking for those rule- or tree-based, 
+together with numerical regression methods which could yield the best results.
 

### 2016-09-07 paper.tex
Reviewing introduction, leaving a comment.

@@
 production process \cite{Fildes2010,Saeed2008}, so not only cost
-associated to the book itself are associated, but also the whole
+associated to the book itself are associated,
+% (Paloma) I was about to change this second "associated" for "affected" (seems the right thing to do).
+However, what's after this comma is also confusing, given that we already said that is affects to the whole production process.
+Maybe who wrote this should re-think what he/she meant to say here and change it.
+ but also the whole
 production process.
@@
 related with the book publication process.
-
-The training dataset includes historical data about 6083 books
-published in Spain for several years, with an initial set of 50
-variables per pattern. It has been provided by the Spanish publishing
-company Trevenque Editorial S.L. Table 
-\ref{tabla:paramsOrig50} shows the initial set of variables describing
-each book.
 
@@
 
+The training dataset includes historical data about 6083 books
+published in Spain for several years, with an initial set of 50
+variables per pattern. It has been provided by the Spanish publishing
+company Trevenque Editorial S.L. Table 
+\ref{tabla:paramsOrig50} shows the initial set of variables describing
+each book.
+
 Starting from these raw data, a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance.
@@
 
-\begin{figure}[!ht] 
+\begin{figure}[!h] 
 \begin{center}

### 2016-09-07 paper.tex
including new Figure (RFE + 4 editorials): Closes #52

--- 2016-09-07 paper.tex
@@
 leverage when deciding how much to print.
-For clarity purpose, obtained results after applying feature selection methods
-have been shown in Tables \ref{Table:case1results_no_fs} to \ref{Table:case4results_fs_som}
-in the appendix of tables at the end of this paper.
-In those tables it can be seen that, as in the previous experiment, the highest 
-predictive power is exhibited by RFE over CSE and SOM feature selection methods.
-In this sense, RFE reduction has noticeably improved the performance of all models, 
-specially in the case of the best selling publisher house (i.e. UDL929) and the 
-publisher which publishes a wide range of different books (i.e. UDL704).
-
-% tables have been moved to the Appendix and they have been substituted by the new Figure. Comments (text) have been adapted accordingly  -  [pedro]
-%For clarity purpose, we present here only the results after applying the RFE method for the four cases in Tables \ref{Table:case1results-RAE}, \ref{Table:case2results-RAE}, \ref{Table:case3results-RAE} and \ref{Table:case4results-RAE}, this one was chosen since the selected features by this method showed in the previous experiment the highest predictive power among  all classifiers.
-%RFE reduction has noticeably improved the performance of all classifiers specially in the case of the best selling publisher house (i.e.
+
+%  esta frase siguiente ya no, ya que además de pasar las tablas al apéndice, vamos a mostrar la figura:
+%For clarity purpose, obtained results after applying feature selection methods have been shown in Tables \ref{Table:case1results_no_fs} to \ref{Table:case4results_fs_som} in the appendix of tables at the end of this paper.
+In those tables it can be seen that, as in the previous experiment, the highest predictive power is exhibited by RFE over CSE and SOM feature selection methods.
+In this sense, RFE reduction has noticeably improved the performance of all models, specially in the case of the best selling publisher house (i.e.
+UDL929) and the publisher which publishes a wide range of different books (i.e.
+UDL704).
+
+%  esta frase siguiente ya no, porque vamos a pasar las tablas al apéndice
+%For clarity purpose, we present here only the results after applying the RFE method for the four cases in Tables \ref{Table:case1results_fs_rf}, \ref{Table:case2results_fs_rf}, \ref{Table:case4results_fs_rf} and \ref{Table:case4results_fs_rf}, this one was chosen since the selected features by this method showed in the previous experiment the highest predictive power among  all classifiers.
+RFE reduction has noticeably improved the performance of all classifiers specially in the case of the best selling publisher house (i.e.
 UDL929) and the publisher which publishes a wide range of different books (i.e.
@@
 
-% [pedro]  TODO => una vez hecha la nueva figura, volver a meter este comentario anterior (lin.1297)
+%  dejamos ésta finalmente: tablas al apéndice + incluimos nueva figura con los datos del RFE.
+For clarity purpose, only obtained results after applying the RFE method for the 
+four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}
+ (detailed numeric results can be shown in 
+Tables \ref{Table:case1results_fs_rf}, \ref{Table:case2results_fs_rf}, 
+\ref{Table:case3results_fs_rf} and \ref{Table:case4results_fs_rf}
+in the appendix of tables at the end of this paper).
+This one was chosen since the selected features by RFE method showed in the 
+previous experiment the highest predictive power among all models.
+As can be shown, RFE reduction has noticeably improved the performance of all 
+classifiers specially in the case of the best selling publisher house (i.e. UDL929) 
+and the publisher which publishes a wide range of different books (i.e. UDL704). 
+For the rest of the results which are obtained by CSE and SOM feature selection 
+methods we refer the reader to the appendix of tables at the end of this paper.
+
+\begin{figure*}[ht]
+\begin{center}
+\includegraphics[scale=0.6]{./imgs/attribute_ReliefFAttributeEval-FS.eps}
+\end{center}
+\caption{Boxplots showing the values obtained predicting \texttt{total\_sales}, considering just the features selected by ReliefFAttributeEval method, with different regression methods (30 repetitions, 10-fold cross validation).
+Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
+}
+\label{fig:casesReliefFAttributeEval}
+\end{figure*}
 
@@
 \ref{fig:decision_tree_best_seller_fs}) corresponds to the same
-publishing company, so the same data were used, but the RAE % Problem here: everytime you use RAE in the paper it means Relative Absolute Error, so I don't think we should use just "RAE" here, but ReliefFAttributeEval.
-feature
-selection method was applied. This simplification, besides making the
+publishing company, so the same data were used, but the RFE %ReliefFAttributeEval
+feature selection method was applied. This simplification, besides making the
 tree easier to understand, reduces training time to a fraction of what
@@
 being those that are distributed to more than roughly 500 points.
+
+\begin{figure*}[!ht] 
+\begin{center}
+  \epsfig{file=decision_tree_no_fs.eps,width=13cm}
+\caption{Decision tree built by the M5P method for the best seller publishing 
+	company including all pre-sales features.}
+\label{fig:decision_tree_best_seller}
+\end{center}
+\end{figure*}
+
+\begin{figure*}[!ht] 
+\begin{center}
+  \epsfig{file=decision_tree_fs.eps,width=13cm}
+\caption{Decision tree built by the M5P method for the best seller
+  publishing company using  the subset of features selected by the
+  {\sf ReliefFAttributeEval} method.} 
+\label{fig:decision_tree_best_seller_fs}
+\end{center}
+\end{figure*}
 
@@
 factors, including price.
-
-\begin{figure*}[!ht] 
-\begin{center}
-  \epsfig{file=decision_tree_no_fs.eps,width=13cm}
-\caption{Decision tree built by the M5P method for the best seller publishing 
-	company including all pre-sales features.}
-\label{fig:decision_tree_best_seller}
-\end{center}
-\end{figure*}
-
-\begin{figure*}[!ht] 
-\begin{center}
-  \epsfig{file=decision_tree_fs.eps,width=13cm}
-\caption{Decision tree built by the M5P method for the best seller
-  publishing company using  the subset of features selected by the
-  {\sf ReliefFAttributeEval} method.} 
-\label{fig:decision_tree_best_seller_fs}
-\end{center}
-\end{figure*}
 
@@
 
-\pagebreak
+\newpage
+\clearpage
+\onecolumn
 
@@
 
-\begin{table*}
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for all publishers (all the features). 30 repetitions, 10-fold cross validation. Best values in bold.
@@
 }
-\end{table*}
-
-\begin{table*}
+\end{table}
+
+\begin{table}[!ht]
 \centering{}%
@@
 }
-\end{table*}
+\end{table}
 
@@
 %--------------- old Table 7 (before revision)
-\begin{table*}
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for publishing company UDL929 (the best selling publishing company). Best values in bold. 
@@
 }
-\end{table*}
-
-\begin{table*}[!ht]
+\end{table}
+
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.
@@
 }
-\end{table*}
+\end{table}
 
 % --- old table 11 (before revision)
-\begin{table*}[!ht]
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for publishing company UDL929 (ReliefFAttributeEval-FS). Best values in bold.
@@
 }
-\end{table*}
-
-\begin{table*}[!ht]
+\end{table}
+
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for PublishingCo-UDL929 (SOM-FS). Best values in bold.
@@
 %--------------- old Table 8 (before revision)
-\begin{table*}
+\begin{table}
 \caption{Predicting \texttt{total\_sales} for publishing company UDLW12 (the median selling publishing company). Best values in bold. 
@@
 }
-\end{table*}
-
-\begin{table*}[!ht]
+\end{table}
+
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.
@@
 }
-\end{table*}
+\end{table}
 
 % --- old table 12 (before revision)
-\begin{table*}[!ht]
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for publishing company UDLW12 (ReliefFAttributeEval-FS). Best values in bold.
@@
 }
-\end{table*}
-
-\begin{table*}[!ht]
+\end{table}
+
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for PublishingCo-UDLW12 (SOM-FS). Best values in bold.
@@
 %--------------- old Table 9 (before revision)
-\begin{table*}
+\begin{table}
 \caption{Predicting \texttt{total\_sales} for publishing company UDL704 (highest number of different titles sold). Best values in bold.
@@
 }
-\end{table*}
-
-\begin{table*}[!ht]
+\end{table}
+
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for PublishingCo-UDL704 (CfsSubsetEval-FS). Best values in bold.
@@
 }
-\end{table*}
+\end{table}
 
 % --- old table 13 (before revision)
-\begin{table*}[!ht]
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for publishing company UDL704 (ReliefFAttributeEval-FS). Best values in bold. 
@@
 }
-\end{table*}
-
-\begin{table*}[!ht]
+\end{table}
+
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for PublishingCo-UDL704 (SOM-FS). Best values in bold.
@@
 %--------------- old Table 11 (before revision)
-\begin{table*}
+\begin{table}
 \caption{Predicting \texttt{total\_sales} for publishing company UDLU11 (medium number of different books sold). Best values in bold.
@@
 }
-\end{table*}
-
-\begin{table*}[!ht]
+\end{table}
+
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.
@@
 }
-\end{table*}
+\end{table}
 
 % --- old table 14 (before revision)
-\begin{table*}[!ht]
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for publishing company UDLU11 (ReliefFAttributeEval-FS). Best values in bold.
@@
 }
-\end{table*}
-
-\begin{table*}[!ht]
+\end{table}
+
+\begin{table}[!ht]
 \caption{Predicting \texttt{total\_sales} for PublishingCo-UDLU11 (SOM-FS). Best values in bold.
@@
 }
-\end{table*}
+\end{table}
+
+\twocolumn
 

### 2016-09-07 paper.tex
Another paragraph reviewed and commented in the introduction.

--- 2016-09-07 paper.tex
@@
 Within the general area of cultural products, the problem of
-predicting sales is specially acute for book publishers, who, among other
+predicting sales is specially acute for book publishers who, among other
 providers of content in physical form, release new {\em products} more frequently than
@@
 problem because when inventory is close to exhaustion new print runs
-are made; however, this new print run presents the same problem as the
+are made; % (Paloma) I think that the thing that should be highlighted here is that is not big deal because the print run is made _before_ the inventory is exhausted.
+I mean, the sentence highlights the fact that a new print run is made, and not that maybe the situation where there's any book never happens.
+% Suggestion:  However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is orderer before the inventory is exhausted;
+ nevertheless, this new print run presents the same problem as the
 initial one of printing only as many as forecasted, although its cost
-is not as high as the initial one and we are not so concerned with
+is not as high as the initial one 
+% (Paloma) Should we really say this next sentence? :\
+and we are not so concerned with
 this issue in this paper.

### 2016-09-08 Response to reviewers.tex
solving some TODOs
Working on the paper: Sections 1-4
Intro, SotA, Problem, Methodology.

Responses to reviewers improved.

@@
 \begin{verbatim}
-The reviewer is right, thus, we have revised the whole paper referring 
-to the term `regression' instead of `classification'. 
-In addition, some sections have been renamed, such as subsection 2.1, 
+The reviewer is right, thus, we have revised the whole paper remarking 
+the regression topic present on the work. We have clarified in several
+ paragraphs that the problem has been addressed by means of regression 
+methods (for instance, note the new title of Section 2.1), or we have 
+generally referred to the term `regression' instead of `classification', 
 in order to better suit the regression viewpoint.
-Moreover this have been also addressed solving the issue related 
-to comment #1, where the application procedure of feature selection 
-methods for regression problems has been clarified. 
+Moreover this suggestion have been also addressed solving the issue 
+related to comment #1, where the application procedure of feature 
+selection methods for regression problems has been clarified. 
 \end{verbatim}
-% Antonio - CONCERN: I'm a bit afraid about the term 'organize' which I don't know if has been addressed in any way in the new version...
-% [Pedro] you are right... but the way the reviewer has expressed it is quite strange.
-% [Hossam]: Regarding your first concern, the reviewer asked for organizing and writing not reorganizing, so we have just addressed that by emphasizing the term regression in all the paper and we have clarified how we applied the FS methods customized for regression problems.
-So I think we addressed this issue adequately.
 
@@
 \begin{verbatim}
-Following reviewer's suggestion we have reorganized some parts of the 
-text and several paragraphs have been rewritten in order to make 
-them shorter, clearer and to improve its comprehension 
-(i.e. paragraph XX in page YY, and paragraph XX in page YY).
+Following reviewer's suggestion we have reorganized some parts 
+of the text, removed some sentences, and rewritten several paragraphs 
+in order to make them shorter, clearer and to improve its comprehension.
 
-Also, several tables have been moved to the Appendix and that
-data has been presented now as the new Figures XX, YY, ZZ.
+Also, all the tables of results have been moved to the Appendix and 
+that data has been presented now as the new Figures XX, YY, ZZ.
 
@@
 
-We are very grateful for your valuable suggestions and comments. 
+We are very grateful the reviewer's valuable suggestions and comments. 
 \end{verbatim}
@@
 \begin{verbatim}
-We have rewritten the introduction and included this new text:
+We have rewritten the introduction and included new paragraphs to better 
+explain the problem and the aim of the paper. We have also remarked the
+ contribution with the paragraphs:
 
-"Our main contribution is, thus, to develop a methodology to 
-process book sales data in order to first find out relevant 
-variables and then use these variables to process data so that 
-the publisher, using them, can estimate sales and from them order 
-a specific print run, instead of standard ones, which are around 
-300 copies for standard books and around 5000 for those that are 
-considered, in advance, best sellers."
+"Our intention in this paper is to find out the main factors influencing
+sales in order to create a tool that the publisher can use to decide how
+many books should be printed, as well as how to leverage these printed
+copies to maximize sales using the decision variables under his control. 
+That is why, using data obtained from a company that sells software for 
+publishers, we analyse them and compute predictive models that can be 
+mainly used as decision-aid tools for book publishers. With these models,
+ publishers will be able to combine their expert knowledge about the market 
+with the created forecasting models in order to get a reliable estimation of
+ book sales, and, based on it, act consequently in order to maximize the 
+books sold for a particular print run. This will improve the current 
+decision flow that the publishers follow, which consist in analysing (in a
+ subjective way) the quality of the book and its features (author, genre, 
+etc), and take a `fuzzy' decision roughly between printing 300 copies 
+(standard book) or 5000 (best seller).
 
-Also, in the next-to-last paragraph, we have laid out our 
-methodology and clarified the main contributions of this paper 
-to the state of the art.
+Our main contribution is, thus, the development of the methodology 
+to process book sales data in order to, first find out relevant variables, 
+and then, use these variables to process the data to accurately estimate 
+future sales. To our knowledge this is the first work in which regression
+ methods have been applied to estimate sales for new launched books. 
+Moreover, the use of a real dataset of book sales is another point to 
+remark with respect to other works."
+
+Also, in the following paragraphs, we have laid out our 
+methodology to differentiate it from other approaches.
+
 \end{verbatim}
@@
 \begin{verbatim}
-Following reviewer's suggestion, several tables have been moved to 
-the Appendix and that data has been summarized and presented 
-as the new Figures XX, YY, ZZ in order to make that numeric data clearer 
-and to improve their comprehension.
+Following reviewer's suggestion, all the results tables have been 
+moved to the Appendix and that data has been summarized and 
+presented as the new Figures XX, YY, ZZ in order to make that numeric 
+data clearer and to improve their comprehension.
 \end{verbatim}
-% Antonio - CONCERN: I think we should move ALL the results tables and include a couple of figures more. Please see my e-mail on this respect. ;)
-% Antonio - TODO: Talk about the final tables and figures.
-% Let's talk about them!   :)
+% Antonio - TODO: put the correct page when the text is finished
 
@@
 
-********* TO WRITE ***********
+The reviewer is right. The main contribution of this paper to the 
+state of the art was not properly described. Thus, as stated above 
+in the second response to Reviewer #2, we have clarified this in 
+the introduction adding new sentences and the paragraph:
+
+"Our main contribution is, thus, the development of the methodology 
+to process book sales data in order to, first find out relevant variables, 
+and then, use these variables to process the data to accurately estimate 
+future sales. To our knowledge this is the first work in which regression
+ methods have been applied to estimate sales for new launched books. 
+Moreover, the use of a real dataset of book sales is another point to 
+remark with respect to other works."
 
 \end{verbatim}
-% Antonio - TODO: we can't write the same answer for two reviewers. We'll answer the same, once we have the response for the previour reviewer but in other words. ;)
+% Antonio - TODO - put here the paragraph as it will finally be (if it is changed again).
 
@@
 \begin{verbatim}
-We have improved Section 5, including the parameter settings of 
-M5P, kNN and RF methods (see paragraph XX at page YY).
+Reviewer is right, so we have improved Section 5, including the 
+parameter settings of M5P, kNN and RF methods (see paragraph XX at 
+page YY), along with the configuration parameters for the rest of 
+methods.
 
@@
 %------------------------------------------------------------------------------------
-\section{New references added in this revision}
+\section{New references added after revision}
 
@@
 
+%Antonio - [REF-Dewey is new] 
+\cite{wiki:dewey}
+
 \end{document}

### 2016-09-08 Response to reviewers.tex
including the new references in the responses file

@@
 
-[XX] Authors, Title, Journal, pages, Year
-
-[YY] Authors, Title, Journal, pages, Year
-
-[ZZ] Authors, Title, Journal, pages, Year
+[53] G.B. Huang, Q.Y. Zhu, C.K. Siew, Extreme learning machine: theory and applications, Neurocomputing 70 (1) (2006) 489-501.
+[54] G. Huang, G.B. Huang, S. Song, K. You, Trends in extreme learning machines: a review, Neural Networks 61 (2015) 32-48.
+[71] M.
+A.
+Hall, Correlation-based feature selection for discrete and numeric class machine learning, in: Proceedings of the Seventeenth International Conference on Machine Learning, ICML2000, Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 2000, pp.
+359-366.
 

### 2016-09-09 Response to reviewers.tex
fixing references
changing font for variable names
Answering @amorag concerns
Improving contribution and Methodology section
A big CONCERN is there. :(

@@
 % Antonio - TODO: say how this has been addressed in the paper (where it is clarified). Say if this reference has been included as new.
-
+% JJ - Antonio, TODO by whom? If it's an issue, put it in the repo and assign it or do it yourself.
 ~\\
@@
 
-Our main contribution is, thus, the development of the methodology 
-to process book sales data in order to, first find out relevant variables, 
-and then, use these variables to process the data to accurately estimate 
-future sales. To our knowledge this is the first work in which regression
- methods have been applied to estimate sales for new launched books. 
-Moreover, the use of a real dataset of book sales is another point to 
-remark with respect to other works."
+Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
+To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.
+Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark."
 
@@
 \end{verbatim}
-% Antonio - TODO: I rewritten this text, so we should copy the new one here. But I think we all should contribute to create a very good justification (see next CONCERN). :D
-% Antonio - CONCERN: We should definitely write a convincing text which separates this work from existing approaches.
-Maybe the use of real data is a good point.
-And also emphasize the contribution to the SotA.
-% [Pedro] well, no previous work on "print run & book sales prediction" has been done (at least, I have not found anything in the bibliography)
-% [Hossam] about the contribution, I agree with you. We can mention that we used real data in our work.
 
@@
 
-"Our main contribution is, thus, the development of the methodology 
-to process book sales data in order to, first find out relevant variables, 
-and then, use these variables to process the data to accurately estimate 
-future sales. To our knowledge this is the first work in which regression
- methods have been applied to estimate sales for new launched books. 
-Moreover, the use of a real dataset of book sales is another point to 
-remark with respect to other works."
+"Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
+To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.
+Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark."
 
@@
 
-[53] G.B. Huang, Q.Y. Zhu, C.K. Siew, Extreme learning machine: theory and applications, Neurocomputing 70 (1) (2006) 489-501.
-[54] G. Huang, G.B. Huang, S. Song, K. You, Trends in extreme learning machines: a review, Neural Networks 61 (2015) 32-48.
-[71] M.
-A.
-Hall, Correlation-based feature selection for discrete and numeric class machine learning, in: Proceedings of the Seventeenth International Conference on Machine Learning, ICML2000, Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 2000, pp.
-359-366.
+\begin{verbatim}
+[53] G.B. Huang, Q.Y. Zhu, C.K. Siew, Extreme learning machine: 
+theory and applications, Neurocomputing 70 (1) (2006) 489-501.
 
-%Antonio - [REF-Dewey is new] 
-\cite{wiki:dewey}
+[54] G. Huang, G.B. Huang, S. Song, K. You, Trends in extreme 
+learning machines: a review, Neural Networks 61 (2015) 32-48.
+
+[60] Wikipedia, List of Dewey decimal classes, [Online; accessed 
+05-May-2016]. https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes
+
+[71] M. A. Hall, Correlation-based feature selection for discrete 
+and numeric class machine learning, in: Proceedings of the 
+Seventeenth International Conference on Machine Learning, ICML2000, 
+Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 2000, 
+pp. 359-366.
+\end{verbatim}
 

### 2016-09-09 paper.tex
all tables of results in the appendix: Closes #53
Let's finish the graphical abstract  ;)  Closes #51
the appendix is now in one column format (the section title too)
Improving contribution and Methodology section
A big CONCERN is there. :(

@@
 Indeed, several studies have demonstrated that improving sales
-predictions, that is reducing the error in estimated sales, results in an enhancement in the 
-production process \cite{Fildes2010,Saeed2008}, so not only cost
-associated to the book itself are associated,
+predictions, that is reducing the error in estimated sales, results in an enhancement in the whole production process \cite{Fildes2010,Saeed2008}, so not only the costs associated to the book itself are affected.
 % (Paloma) I was about to change this second "associated" for "affected" (seems the right thing to do).
@@
 Maybe who wrote this should re-think what he/she meant to say here and change it.
- but also the whole
-production process.
+% Antonio - I guess it was a mistake. I think now it is correct.
 
@@
 whereas if the number of printed copies was not enough, a new print
-run can always be made, resulting in temporary losses due to a lack of supply
-or in bad marketing for the customers, for instance. However, in
-practice predicting lower sales than the actual ones is not such a big
-problem because when inventory is close to exhaustion new print runs
-are made; % (Paloma) I think that the thing that should be highlighted here is that is not big deal because the print run is made _before_ the inventory is exhausted.
+run can always be made, but this will result in temporary losses due to a lack of supply or in bad marketing for the customers, for instance.
+However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is ordered before the inventory is exhausted;
+% (Paloma) I think that the thing that should be highlighted here is that is not big deal because the print run is made _before_ the inventory is exhausted.
 I mean, the sentence highlights the fact that a new print run is made, and not that maybe the situation where there's any book never happens.
 % Suggestion:  However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is orderer before the inventory is exhausted;
+% Antonio - fixed then
  nevertheless, this new print run presents the same problem as the
 initial one of printing only as many as forecasted, although its cost
-is not as high as the initial one 
+is not as high as the initial one. 
 % (Paloma) Should we really say this next sentence? :\
-and we are not so concerned with
-this issue in this paper.
+%and we are not so concerned with
+%this issue in this paper.
+% Antonio - yes, no need to say this
 
@@
 profits and minimise losses \cite{Zhao2001}. This is the main objective of this paper.
-
-% I don't know what to make with this paragraph. Move it to the
-% presentation of the problem, move it to the state of the art, or
-% eliminate it completely. Whoever wrote it please help - JJ
-It is important to notice that the accuracy of the predictive method
-that we intend to design is affected negatively by several factors
-related to decisions on purchases, to freight traffic, or with the
-distribution strategy \cite{Little1998}. 
-Thus, it is mandatory to know the product and the variables that
-might affect the sales, and how an expert manager takes them into 
-account \cite{Armstrong2001,SThomassey2014}. 
-Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
-In addition, some variables may have correlations between them, although these correlations can be detected using data analysis methods, 
-such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.
 
@@
 to the publisher. Books returned to the publisher are pulped, sold back or
-given to the author or distributed in used-books channels such as
+given to the author, or finally distributed in used-books channels such as
 book stalls or second-hand bookstores. If the print run has been fully
 distributed and there are more requests from bookstores, on the other
-hand, a new print run is made and distributed to bookstores. 
+hand, a new print run is made and distributed to these shops. 
 Even if the process has changed slightly 
@@
 collected, it roughly stays the same. Other countries will have a
-similar model, although scale will be different.
+similar model, although the scale will be different.
 
@@
 
-Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out
-relevant variables, and then, use these variables to process the data to accurately estimate future sales.
-
-In the research published in this paper, the problem of predicting total sales is approached using real data provided by the 
-Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. This company offers management systems and services for bookshops, publishers, and distributors. 
+Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
+To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.
+Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark.
+
+Therefore, in this paper, the problem of predicting total sales is approached using real data provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}.
+This company offers management systems and services for bookshops, publishers, and distributors.
 Usually, the company's expert sales managers analysed historical data
@@
 predictions from the same dataset \cite{Sanders1994}.
-
-%An initial version of this method was developed under a contract with that company and eventually integrated in their product.
-This paper represents an improved version of that method based on the same data.
-% We should also mention what data we actually mean, I don't think
-% we've published it here. - JJ
-% Antonio - I think this information is not relevant for the paper...
 
@@
 
-The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes. 
+The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes and shows a set of definitions of the regression methods applied in the paper and the evaluation metrics considered.
 Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run for new books, along with a description of the considered dataset.
-Section \ref{sec:methodology} details the methodology considered in the study, from the data collection and preprocessing stages, to the selection of the forecasting methods to be applied in the experiments.
+Section \ref{sec:methodology} details the methodology considered in the study.
 These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies.
@@
 
-As far as we know, no previous attempt can be found in the literature 
-%in which prediction methods have been applied to estimate the print run. 
-in which prediction methods have been applied to estimate sales for new launched books.
+As far as we know, no previous attempt can be found in the literature in which prediction methods have been applied to estimate sales for new launched books in a whole country market.
 However, similar techniques to those proposed in this paper, e.g.
-regression models \cite{Papalexopoulos1990}, 
-neural networks \cite{Yoo1999} 
-or fuzzy systems \cite{Mastorocostas2001}, 
-have been applied to solve sales prediction problems in other industrial sectors.
+regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001}, have been applied to solve sales prediction problems in other industrial sectors.
 
@@
 
-  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
-  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
-  %  o aconsejar acerca de la cantidad de libros a imprimir.
-  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
-  %  sobre "Use Blog Information As Book Sales Prediction":
-  %     Moon2010ICSSSM , Moon2010ICEC
 Recently, some works have proposed analysing relationships between on-line 
@@
 longest period, and so on).
-
-%
-% pasar a contar los casos de la predicción de ventas en la 
-% industria de la moda (SThomassey2014) y de nuevos productos (ChingChin2010)
-%
-% Son problemas muy similares, ya que no hay datos históricos de los nuevos productos,
-% al igual que no los hay sobre ventas, y en los que además influyen mucho las variables 
-% externas (estacionalidad, modas, fama del author, etc).
-% Hay que echar mano de productos similares o simplemente de los datos que describen el nuevo producto.
-%
 
@@
  \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
-%FERGU: completar con: "In our case, these ideas ..."
-% [pedro] no sé a qué te refieres. Please, detalla un poco esto   :)
-
-  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
-  % New tea product
-  % New cosmetic product
-  % New soft drink product
+
 Ching et al. propose in \cite{ChingChin2010} a decision-support system for new 
@@
 
-  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
-  % sales forecasting in printed circuit board industry.
 On the other hand, in those cases where historical data are available, classical time series forecasting methods have been applied, such as in \cite{Chang2009}, 
@@
 influences to understand how electronic `word-of-mouth' influences product sales. 
-In this case, the proposed method is suitable for those sales forecasting problems 
-with a big amount of online reviews and historical data.
+In this case, the proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.
 
@@
 
-Many of the previous papers propose using different prediction methods.
+Many of these previous papers propose using different prediction methods to find out which one performs the best.
 Thus, next subsections describe several forecasting methods and different 
 evaluation metrics, commonly used in the bibliography that have been chosen 
-to face the problem at hand.
+to address the problem of book sales prediction.
 
@@
 instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
-% Antonio - CONCERN - should we change the term 'classification' by 'regression' somehow?
-% I don't think so in this case. That is what kNN is...
 
@@
 
-%In classification problems the algorithm searches for an optimal hyperplane 
-%that separates two classes, maximising the margin between them.
-% Antonio - CONCERN - remove this classification thing due to a reviewer's comment 
-% ok    :)
 In regression problems, the algorithm chooses a hyperplane close to as many 
@@
 It is an artificial neural network generally used for classification or 
-approximation problems.
-% Antonio - CONCERN - something about regression?
-% in that sentence, approximation is used as synonymous of regression   ;)
-
-This model is a generalisation of the standard linear perceptron that uses several 
-layers of nodes (called neurons) and that is able to solve linearly inseparable 
-problems \cite{SteinwenderBitzer2003}.
+approximation/regression problems.
+
+This model is a generalisation of the standard linear perceptron that uses several layers of nodes (called neurons) and that is able to solve linearly inseparable problems \cite{SteinwenderBitzer2003}.
 Each neuron consists of a linear combination of weighted inputs which is passed 
@@
 connection weights between the input layer and the hidden layer are randomly initialized and 
-fixed, while the connection weights between the hidden layer the output layer are learned 
+fixed, while the connection weights between the hidden layer the output layer are learnt 
 analytically in a single step of linear parameters solving. In ELM the hidden layer maps the 
@@
 the error between the obtained forecast and the current sales for each new book 
-published.
-
-% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before. And rewrite the initial paragraphs to separate it from section 4 (methodology)
-% I have addressed this "todo" before (lin. 353)
+published. To this end, the results will be evaluated using different metrics, as described in the following section.
+
+% Antonio - I have linked the section also here for a more fluent reading. ;)
 
@@
 
-At this step, the developed forecasting models are evaluated and assessed based on different evaluation criteria.
+The developed forecasting models must be evaluated and assessed based on different evaluation criteria.
 In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
@@
 where $o_i$ is the current value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
-
-% previous two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)
-% Antonio - TODO - revise them
-% What have to be revised?   :/
 
@@
 variables per pattern. It has been provided by the Spanish publishing
-company Trevenque Editorial S.L. Table 
-\ref{tabla:paramsOrig50} shows the initial set of variables describing
-each book.
+company Trevenque Editorial S.L. Table \ref{tabla:paramsOrig50} shows the initial set of variables describing each book.
 
 Starting from these raw data, a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance.
-% (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
-% Antonio - because we should not fill important variables automatically, this adds noise to the data, so I think it is better to remove these patterns, since there are still a lot in the dataset. 
-% Indeed, there were just a couple of patterns without important values, that probably were errors of the extraction process or bad insertions in the database.
-Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, 
-has been reduced by an expert to use just those that can be known before a new book 
-is launched, i.e. \textit{pre-sales data}. 
+Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to use just those that can be known before a new book is launched, i.e.
+\textit{pre-sales data}.
 %Thus, their value do not depend on the book sales. 
@@
 Initially, there were three different features describing the subjects
-and subsubjects of every book \textit{subject1,2,3} (see Table
+and subsubjects of every book \texttt{subject1,2,3} (see Table
 \ref{tabla:paramsOrig50}), but for most of the patterns (books) there
-is no value for \textit{subjects2} and \textit{3}, so we have discarded 
+is no value for \texttt{subjects2} and \texttt{3}, so we have discarded 
 these features.
 
-With regard to the feature \textit{publisher}, it has been removed from the 
+With regard to the feature \texttt{publisher}, it has been removed from the 
 final dataset since it is indeed included in the code of \texttt{collection}. 
@@
 In this prediction problem there are other external variables that also affect 
-the sales of a new book, such as those related to seasonality, trends, or 
-promotions, that classical prediction methods can not deal with, since they 
-are not included in the dataset due to the difficulty to model them. 
+the sales of a new book \cite{Little1998}, such as those related to seasonality, trends, or promotions, that classical prediction methods can not deal with, since they are not included in the dataset due to the difficulty to model them.
 However, an expert can consider them to modify the forecast obtained by 
-the automatic method. Even publishing companies tend to define rules or 
-indexes to subjectively adjust the results of prediction based on
-external data. 
+the automatic method \cite{Armstrong2001}. Even publishing companies tend to define rules or  indexes to subjectively adjust the results of prediction based on external data. 
 Thus, the proposed method will analyse the provided data and
@@
 
-% This section is too short and really does not describe the problem
-% to its full extent. First, it should say if some of these variables
-% were discarded for some reason. Group the variables we have in those
-% available to publisher and those that can be used afterwards. And
-% then give an idea of the complexity of the problem and how difficult
-% it should be to find a solution - JJ
-% Antonio - I have included much more contents form other sections. could you do the rest?
-
-% You should include data visualization in problem description,
-% because it shows the distribution of problem variables and then
-% suggests ways to deal with it - JJ
-% You should include in the section an exploratory data
-% analysis that describes the range of variables, how many categories
-% those variables have, and so an do forth - JJ
-% Antonio - as you know SOM has been applied later as a feature selection method...
-I don't know if we could reference the figure of SOM here or the other way round (do the analysis here and reference later), but in that case, we should explain SOM before, which could be a mess...
-% Antonio - If you meant using other visualization methods... could you do it also?
-
 %********************************************************************************
@@
 
-Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}.
-These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
+Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.
+
+FS methods check the relevance of all the variables of the patterns, aiming to reduce the set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
 This task may also help to identify leading indicators to be considered 
 by a human expert to make predictions.
-
-In this stage, both numerical and visualisation-based approaches have been 
-applied, in order to select the best variables for the forecasting methods.  
-% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Could they be used with the same meaning?
-% I think so.
-
-As stated before, in Section \ref{subsec:select_method}, a selection of the best 
-forecasting techniques has been reported, looking for those rule- or tree-based, 
-together with numerical regression methods which could yield the best results.
-
-Once the models and results have been obtained for the whole dataset 
-(Section \ref{sec:experiments}), the same methodology has been applied to some 
-specific cases of publishing companies in order to prove the value of the 
-proposal (Section \ref{sec:example_cases}).
-Some specific interpretable models have been created as a final result of the work.
+At this stage of the methodology, both numerical and visualisation-based approaches have been applied, in order to select the best set of variables for the forecasting methods.
+
+After this process has been conducted, different prediction methods have been applied on the dataset.
+These methods have been described in Section \ref{subsec:select_method}, and include rule- and tree-based algorithms, together with numerical regression methods.
+
+As a result, several prediction models are obtained.
+Then the obtained models for the whole dataset have been evaluated by means of the metrics described in Section \ref{subsec:models_evaluation}.
+The results are presented in Section \ref{sec:experiments}.
+
+After this, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}).
+Specific interpretable models have been created as a final result of the work (Section \ref{subsec:decision_trees}).
+
+% Antonio - CONCERN - The following section seems to be misplaced after moving the rest to Section 2.
+Thus, the Methodology Section is now a bit strange with just this subsection.
+We should think on moving this section and reorganize/improve the methodology description.
 
@@
 \label{subsec:data_preproces}
-
-At this stage, a Feature Selection (FS) process has been carried out, 
-since it is an effective dimensionality reduction technique and an essential 
-preprocessing method to discard less relevant or non-useful features 
-\cite{Krishnapuram2004,Chen2011_FS_PTS}.
 
@@
 
-% Why? Is that one of the two forms of feature selection? What do we expect to learn from it? - JJ 
-% Antonio - explained here and below. Please check.
-
-%--- new SOM description % -Sam
-
 SOM is a type of unsupervised neural network inspired by the
@@
 
-% Antonio - a better description of U-Matrix. ;D
-% thanks!
-
 %---
@@
 
-Finally, Section \ref{sec:experiments} provides a comparison between 
-the feature reduction through SOM, and the feature selection techniques 
-that have been described.
+Next section provides a comparison between the feature reduction through SOM, and the feature selection techniques that have been described.
 
@@
 a different (and new) variable per each possible value. Thus, in the
-case of \emph{publisher} or \emph{collection} this would imply the definition of
+case of \texttt{publisher} or \texttt{collection} this would imply the definition of
 hundreds of new variables.
@@
 \end{center}
-\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation).
+\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, including errorbars, with different regression methods (30 repetitions, 10-fold cross validation).
 All publishers and all the features have been considered.}
+%This is not a boxplot - JJ
 \label{fig:all_publishers_no_fs}
@@
 the model, not only when using the dataset with categorical input variables, such 
-as \emph{collection} and \emph{binding}, but also when using the datasets with 
+as \texttt{collection} and \texttt{binding}, but also when using the datasets with 
 numerical variables, not to mention the extra time needed to optimize its hyperparameters.
@@
 
-%Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \emph{collection} and \emph{binding}.
+%Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \texttt{collection} and \texttt{binding}.
 
@@
 An important preprocessing step has been carried out before conducting the SOM analysis.
-Thus, the two categorical features \emph{collection} and \emph{binding} have been removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
+Thus, the two categorical features \texttt{collection} and \texttt{binding} have been removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones.
 However, since they have a large number of unique different values this would be finally impracticable and useless.
@@
 \end{center}
-\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation).
+\caption{Barplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation).
 All publishers and just those features selected by each method have been considered in every case.}
@@
 Examining the component planes shown in Figure \ref{fig:componentplanes}, it can be noticed that some variables have very similar colour maps which means that they are highly correlated.
-In this case, we have two examples; the first is the \emph{distrib\_novelty} and \emph{print\_run}variables while the second is the \emph{tot\_points\_sale} and \emph{tot\_points\_sale\_1st\_year}.
+In this case, we have two examples; the first is the \texttt{distrib\_novelty} and \texttt{print\_run}variables while the second is the \texttt{tot\_points\_sale} and \texttt{tot\_points\_sale\_1st\_year}.
 In order to make the dataset having less number of uncorrelated features with each other, one of the redundant features is removed from each pair of features.
-Therefore, the \emph{distrib\_novelty} and \emph{tot\_points\_sale\_1st\_year} were omitted from the dataset.
+Therefore, the \texttt{distrib\_novelty} and \texttt{tot\_points\_sale\_1st\_year} were omitted from the dataset.
 
@@
 \end{center}
-\caption{Boxplots showing the values obtained predicting \texttt{total\_sales}, using all features, with different regression methods (30 repetitions, 10-fold cross validation).
-Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
+\caption{Barplots showing the values obtained predicting
+  \texttt{total\_sales}, using all features, with different regression
+  methods (30 repetitions, 10-fold cross validation). Results obtained
+  for different special publishing companies: UDL929 (the best selling
+  publishing company), UDLW12 (the median selling publishing company),
+  UDL704 (highest number of different titles sold) and UDLU11 (medium
+  number of different books sold). 
 % Just the features selected by ReliefFAttributeEval method have been considered.
@@
 \end{center}
-\caption{Boxplots showing the values obtained predicting \texttt{total\_sales}, considering just the features selected by ReliefFAttributeEval method, with different regression methods (30 repetitions, 10-fold cross validation).
+\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, considering just the features selected by ReliefFAttributeEval method, with different regression methods (30 repetitions, 10-fold cross validation).
 Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).

### 2016-09-09 paper.tex
Working on Experiments section
Improving the analysis of results and fixing some things

@@
 
-Next section provides a comparison between the feature reduction through SOM, and the feature selection techniques that have been described.
+These FS techniques have been applied in the following section, including a comparison between all of them.
 
@@
 pre-sales variables forecasting new book sales.
-Feature selection techniques have also been applied in order to test their utility 
-by comparing the obtained results.
+Feature selection techniques have also been applied in order to test their utility by comparing the obtained results.
 
@@
 a different (and new) variable per each possible value. Thus, in the
-case of \texttt{publisher} or \texttt{collection} this would imply the definition of
-hundreds of new variables.
+case of \texttt{publisher} or \texttt{collection} this would imply the definition of hundreds of new variables.
 
@@
 Figure \ref{fig:all_publishers_no_fs}
-(detailed numeric results can be shown in Table Table \ref{tab:all_publishers_no_fs}
+(detailed numeric results can be seen in Table \ref{tab:all_publishers_no_fs}
 in the appendix of tables at the end of this paper).
@@
 All publishers and all the features have been considered.}
-%This is not a boxplot - JJ
+% Antonio - Should we explain the meaning of the dot and the small lines in every barplot? I guess they are mean and standard deviation, aren't they?
 \label{fig:all_publishers_no_fs}
@@
 provide information on the decision process and does not require human intervention 
-either for the operation or for interpretation. Thus, it is a very suitable model 
-be incorporated in a publishing company processes (as we will show in 
+either for the operation or for interpretation. Thus, it is a very suitable model to be incorporated in a publishing company processes (as we will show in 
 Section \ref{subsec:decision_trees}).
@@
 According to Figure \ref{fig:all_publishers_no_fs}, it can also be noticed that 
-the Linear Regression model outperforms some other complex methods like the 
-Random Forest, both in time and in obtained errors. 
+the Linear Regression model gets a better correlation value and some error measures than other complex methods like the Random Forest. 
 %Although, Linear Regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.
@@
 [pedro]
-Although, Linear Regression is considered as a simple model to build, it can obtain better results than more powerful models in comparable time.
+% Antonio - I have rewritten it. ;)
+So even though Linear Regression is considered as a simple model to build, it can obtain better results than more powerful models in comparable time.
 
@@
 training examples, and it exhibits a poor generalisation ability since it does 
-not learn anything from the training data.
+not learn enough from the training data.
 
 %Moreover, in these experiments it has been seen the difficulty for some classifiers like the SVM to process information related to categorical variables, such as \texttt{collection} and \texttt{binding}.
+
+MLP also gets a very good correlation coefficient, however it takes the largest time to built the models, and obtains high error measures.
+ELM shows a good balance, since it is very fast in the training phase (the second faster) and yields good results according to the correlation and the error metrics.
 
@@
 to solve the problem of how many books should be printed when a new book is 
-published. This forecasting method, with these additional advantages, can be used 
-for products with historical sales data and for new products with little or 
-no historical data available.
+published considering all the pre-sales data.
+Therefore this forecasting method, with these additional advantages, can be used for products with historical sales data and for new products with little or no historical data available.
 
@@
 
-We have used both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.
+We have used both the {\tt CfsSubsetEval} (CSE) \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval (RFE) \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.
 
@@
 The results are shown in Figure \ref{fig:results_all_publishers_fs} 
-(detailed numeric results can be shown in Table \ref{tab:results_all_publishers_fs}
-in the appendix of tables at the end of this paper).
+(numeric results are shown in Table \ref{tab:results_all_publishers_fs}
+in the appendix of tables).
 Examining the obtained results for each feature selection method, 
-it can be seen that RFE got the best results compared to SOM and CSE. 
-It can be noticed also that we obtain better performance using M5P, 
-kNN and RF with the set of features selected by RFE than using all features. 
-                                %Better publish results in
-                                %the same table or refer to the table
-                                %where it was published. Is this
-                                %difference statistically significant?
-                                %- JJ
+it can be seen that RFE got the best results in the comparison with SOM and CSE, both considering the quality/accuracy and also the standard deviation.
+This could be explained due to the extensive reduction made by CSE and due to 
+the `subjective' (but not so accurate) human intervention in the case of SOM. 
+It can be noticed also that we obtain better results using M5P, kNN, and RF with the set of features selected by RFE than using all features, so the application of FS has improved their overall performance.
+
 As expected, in general, all feature selection methods have reduced the training 
-time needed to build the forecasting methods. This is because they reduced the 
+time needed to build the forecasting models, considerably in the most time expensive in previous experiment. This is because they reduced the 
 considered features and mainly because they excluded the categorical features, 
 which are the hardest to be managed (they have many possible values). 
-On the other side, CSE and SOM did not perform as good as RA. 
-This could be explained due to the extensive reduction made by CSE and due to 
-the `subjective' (but not so accurate) human intervention in the case of SOM.
+On the other side, CSE and SOM did not perform as good as RFE.
 
@@
 This section presents further experiments conducted on data concerning four 
-specially interesting publishing company cases. These publishing companies were 
+specially relevant publishing company cases. These companies were 
 selected as representative cases which could be very interesting for decision 
@@
   number of different books sold). 
-% Just the features selected by ReliefFAttributeEval method have been considered.
 }
@@
 \end{figure*}
-% Antonio - CONCERN - The text and the results must be contrasted.
-If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best).
-But there are plotted apparently the results for all the features.
-Anyway, in the text, it is said that the process is using all the features, then apply FS.
-But here just the results for all the features are shown.
-Why don't we show also the results for the corresponding sets of features selected by each FS method?
-% Actually in the previous version there were several tables with these results than have been moved to the Appendix.
-I think we should include another figure fro them.
-They show important information.
-;)
-% we can discuss this point later this morning.
-% The thing is that in this plot we are using all features!! (here, no feature selection method has been used)
 
 \begin{itemize}
-    \item Best seller publishing company: this case represents the publishing company that sells the highest number of copies regardless the title of the books sold.
+    \item \textit{Best seller publishing company}: this case represents the publishing company that sells the highest number of copies regardless the title of the books sold.
 Therefore, it is an example of a case on a higher business scale.
-    \item Mid-range seller publishing company: this represents a publishing company that sells medium number of copies compared to other publishing companies (Medium business scale). 
-    \item Highest variation publishing company: this is an example of a publishing company that follows a strategy in publishing a very wide range of different titles.
-    \item Medium varied publishing company: this case represents a publishing company that has a median rank between the other publishing companies regarding the variety of titles sold.
+    \item \textit{Mid-range seller publishing company}: this represents a publishing company that sells medium number of copies compared to other publishing companies (Medium business scale). 
+    \item \textit{Highest variation publishing company}: this is an example of a publishing company that follows a strategy in publishing a very wide range of different titles.
+    \item \textit{Medium varied publishing company}: this case represents a publishing company that has a median rank between the other publishing companies regarding the variety of titles sold.
 \end{itemize}
@@
 
-The experiments applied on the selected special cases follow the same methodology 
-used previously for the whole dataset. First, the forecasting models are applied 
-on each dataset using all features, then, the three feature selection methods 
-(RFE, CSE and SOM) are used to reduce the set of features in each case. 
-Second, the regression models are applied again on the reduced datasets to 
-evaluate their performance.
-
-Evaluation results of the obtained models (without performing any feature selection 
-method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
-(detailed numeric results can be seen in Tables 
+The experiments applied on the selected special cases follow the same methodology used previously for the whole dataset.
+First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (RFE, CSE and SOM) are used to reduce the set of features in each case.
+Second, the regression models are applied again on the reduced datasets to evaluate their performance.
+
+Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
+(numeric results can be seen in Tables 
 \ref{Table:case1results_no_fs}, \ref{Table:case2results_no_fs}, 
 \ref{Table:case3results_no_fs} and \ref{Table:case4results_no_fs} 
-in the appendix of tables at the end of this paper).
-Results in this Figure show that the models performed similarly to the case of 
+in the appendix of tables).
+Results in the figure show that the models performed similarly to the case of 
 the global models for all publishers, which were previously presented in 
-Table \ref{tab:all_publishers_no_fs}. 
+Figure \ref{fig:all_publishers_no_fs}. 
 In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR. 
@@
 four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}
- (detailed numeric results can be shown in 
+ (detailed numeric results can be seen in 
 Tables \ref{Table:case1results_fs_rf}, \ref{Table:case2results_fs_rf}, 
 \ref{Table:case3results_fs_rf} and \ref{Table:case4results_fs_rf}
-in the appendix of tables at the end of this paper).
+in the appendix of tables).
 This one was chosen since the selected features by RFE method showed in the 

### 2016-09-09 Response to reviewers.tex
Working on Experiments section
Improving the analysis of results and fixing some things
improving some responses (today I will finish all of them)

@@
 sub-section 4.2) six methods: M5P, kNN, RF, LR, SVM, MLP,
- and ELM (requested by Reviewer #2).
+ and ELM (requested by Reviewer #2). After having included
+ ELM, new references have been added (the list of new references
+ can be found at the end of this letter).
 
@@
 % Antonio - TODO: say where are these results (table/figure/page)
-% [pedro] TODO => decir que se han añadido ciertas refs sobre ELM
 
@@
 section, when describing the parameter settings, 
-it has been mentioned that the best performance was obtained with a 
-number of trees equal to 50.
+it has been mentioned that the best performance was obtained 
+with a number of trees equal to 50.
 \end{verbatim}
@@
 % JJ - Antonio, TODO by whom? If it's an issue, put it in the repo and assign it or do it yourself.
+
 ~\\
@@
 Figures AA, BB accordingly. 
+Their results have been also analyzed with the rest of methods, in the 
+paragraphs below each one of the new figures.
 A description of both approaches have been also included in subsection 2.1.
 
-In addition new references has been added to the paper related to these 
-methods, namely [REF_XX, REF_YY].
+In addition new references have been added to the paper, related to these 
+methods, namely [REF_XX, REF_YY]. In any case, the list of new references
+can be found at the end of this letter.
 \end{verbatim}
 % Antonio - TODO: Complete with the number of tables and figures, along with the new references
-% I don't know what references have been added in this revision. I'll ask Hossam.
 
@@
 explain the problem and the aim of the paper. We have also remarked the
- contribution with the paragraphs:
+contribution with the paragraphs (see page XX):
 
@@
 
-Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
-To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.
-Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark."
+Our main contribution is, thus, the development of the methodology to 
+process book sales data in order to, first find out relevant variables, 
+and then, use these variables to process the data to accurately estimate 
+future sales. To our knowledge this is the first work in which regression 
+methods have been applied to estimate sales for new launched books. 
+Moreover, we have considered a real dataset of book sales (related to 
+the Spanish market), which is another point to remark."
 
@@
 methodology to differentiate it from other approaches.
-
 \end{verbatim}
+% TODO: update with the correct page where those paragraphs can be found
 
@@
 \begin{verbatim}
-
 The reviewer is right. The main contribution of this paper to the 
@@
 in the second response to Reviewer #2, we have clarified this in 
-the introduction adding new sentences and the paragraph:
+the introduction adding new sentences and the paragraph (see page XX):
 
-"Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
-To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.
-Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark."
+"Our main contribution is, thus, the development of the methodology 
+to process book sales data in order to, first find out relevant 
+variables, and then, use these variables to process the data to 
+accurately estimate future sales. To our knowledge this is the first 
+work in which regression methods have been applied to estimate sales 
+for new launched books. Moreover, we have considered a real dataset 
+of book sales (related to the Spanish market), which is another 
+point to remark."
 
@@
 \end{verbatim}
-% Antonio - CONCERN: I don't know if te reviewer is speaking about the whole methodology or just about the regression/forecasting part... The figure shows a rough summary of the methodology.
-% Antonio - TODO: Improve the figure, which is a bit 'generic'. Put the correct figure and page.
-% Almost every paper I have read (and that has been cited in the SotA) shows a very generic flowchat
 
@@
 \end{verbatim}
-% Antonio - CONCERN: don't we also put the configuration of the rest of the methods? And say it. :D 
-% Could we use a table for showing them easily?
-% [pedro] TODO: design the table taken the parameters/values shown in section 5.1
 % Antonio - TODO: say paragraph/page where they are.
 
-% Antonio - TODO: Say if there are new references and include them in a final section in this letter.
-% yes, there are some, but is Hossam who knows what references have been added in this revision.
 %------------------------------------------------------------------------------------

### 2016-09-09 paper.tex
Erasing my last comments as @amorag addressed them

@@
 predictions, that is reducing the error in estimated sales, results in an enhancement in the whole production process \cite{Fildes2010,Saeed2008}, so not only the costs associated to the book itself are affected.
-% (Paloma) I was about to change this second "associated" for "affected" (seems the right thing to do).
-However, what's after this comma is also confusing, given that we already said that is affects to the whole production process.
-Maybe who wrote this should re-think what he/she meant to say here and change it.
-% Antonio - I guess it was a mistake. I think now it is correct.
 
@@
 run can always be made, but this will result in temporary losses due to a lack of supply or in bad marketing for the customers, for instance.
-However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is ordered before the inventory is exhausted;
-% (Paloma) I think that the thing that should be highlighted here is that is not big deal because the print run is made _before_ the inventory is exhausted.
-I mean, the sentence highlights the fact that a new print run is made, and not that maybe the situation where there's any book never happens.
-% Suggestion:  However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is orderer before the inventory is exhausted;
-% Antonio - fixed then
- nevertheless, this new print run presents the same problem as the
+However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is ordered before the inventory is exhausted; nevertheless, this new print run presents the same problem as the
 initial one of printing only as many as forecasted, although its cost
 is not as high as the initial one.
-% (Paloma) Should we really say this next sentence? :\
-%and we are not so concerned with
-%this issue in this paper.
-% Antonio - yes, no need to say this
 

### 2016-09-09 paper.tex
Reviewing another paragraph, avoiding the use of the first person.

@@
 out to reviewers and literary magazines; the number of these will
-depend on how many you have printed. In bookstores books go, in some cases, to
+depend on how many were printed. In bookstores books go, in some cases, to
 the {\em novelty} table, that is, they are prominently displayed, shown in the window, or highlighted using props or other 
@@
 or, in some cases and eventually, to storage. Books stay for sale in the store as long as the
-publisher or the store want or until the bookseller decides to return it
+publisher or the store wants or until the bookseller decides to return them
 to the publisher. Books returned to the publisher are pulped, sold back or

### 2016-09-09 Tables_to_figures/generador.r
The new order is coming! R square is now the spearhead in all the plots.

@@ -54,6 +54,8 @@ datos$variable <- as.character(datos$variable)
 datos[datos$variable=="R.","variable"] <- "R"
 dataset = unique(datos$Dataset)
 
+datos$Dataset <- factor(datos$Dataset,c("PublishingCo-UDL929","PublishingCo-UDLW12","PublishingCo-UDL704","PublishingCo-UDLU11"))
+
 #ggplot(data = subset(datos,Dataset==dataset[1]), aes(x=Attributes,y=value,color=Attributes,shape=Attributes)) + geom_point(stat="identity",size=3) + 
 #  facet_grid(variable ~ Method,scales = "free_y",labeller = as_labeller(expression()) + 
 #  scale_color_grey(start=0.0,end=0.2) + labs(title=dataset[1],x="",y="") + 
@@ -82,9 +84,9 @@ for(i in dataset){
                                                                                              axis.ticks.x=element_blank()))
   ggsave(file=paste0("../imgs/datasets_",i,".eps"),scale=2,units = "cm", width = 16, height = 8,dpi = 800)
   ggsave(file=paste0("../imgs/datasets_",i,".png"),scale=2,units = "cm", width = 16, height = 8,dpi = 800)
-  
 }
 
+  
 # Attribute Selection > Publisher > Method > Metric
 
 att = unique(datos$Attributes)
@@ -95,14 +97,14 @@ att = unique(datos$Attributes)
 print(ggplot(data = subset(datos,Attributes==j), aes(x=Method,y=value,fill=Method)) + 
   geom_point(stat="identity",size=2)  + geom_bar(stat="identity") + 
   facet_grid(variable ~ Dataset,scales = "free_y") + 
-  scale_fill_grey(start=0.2,end=0.6) + labs(title="",x="",y="") + 
+  scale_fill_grey(start=0.2,end=0.6) + labs(title=j,x="",y="") + 
   geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="right") +
     scale_y_continuous(limits = c(0, NA))
   )
       
 
-  ggsave(file=paste0("../imgs/attribute_",j,".png"),scale=2,units = "cm", width = 14, height = 8,dpi = 800)
-  ggsave(file=paste0("../imgs/attribute_",j,".eps"),scale=2,units = "cm", width = 14, height = 8,dpi = 800)
[…]

### 2016-09-09 Tables_to_figures/generador.r
New awesome plots by Dataset

@@ -55,6 +55,7 @@ datos[datos$variable=="R.","variable"] <- "R"
 dataset = unique(datos$Dataset)
 
 datos$Dataset <- factor(datos$Dataset,c("PublishingCo-UDL929","PublishingCo-UDLW12","PublishingCo-UDL704","PublishingCo-UDLU11"))
+datos$variable <- factor(datos$variable, c("R","MAE","RMSE","RAE","RRSE","TIME"))
 
 #ggplot(data = subset(datos,Dataset==dataset[1]), aes(x=Attributes,y=value,color=Attributes,shape=Attributes)) + geom_point(stat="identity",size=3) + 
 #  facet_grid(variable ~ Method,scales = "free_y",labeller = as_labeller(expression()) + 
@@ -79,9 +80,11 @@ for(i in dataset){
   print(ggplot(data = subset(datos,Dataset==i), aes(x=Attributes,y=value,fill=Attributes,shape=Attributes)) + geom_point(size=2) + geom_bar(stat="identity") + 
     facet_grid(variable ~ Method,scales = "free_y") + 
     scale_fill_grey(start=0.6,end=0.8) + labs(title=i,x="",y="") + 
-    geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.5,size=0.5) + theme_bw()  + theme(legend.position="bottom", axis.title.x=element_blank(),
-                                                                                                    axis.text.x=element_blank(),
-                                                                                             axis.ticks.x=element_blank()))
+    geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.5,size=0.5) + theme_bw()  +
+    theme(legend.position="bottom", axis.title.x=element_blank(),axis.ticks.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) + 
+    scale_y_continuous(limits = c(0, NA)))
+  
+  
   ggsave(file=paste0("../imgs/datasets_",i,".eps"),scale=2,units = "cm", width = 16, height = 8,dpi = 800)
   ggsave(file=paste0("../imgs/datasets_",i,".png"),scale=2,units = "cm", width = 16, height = 8,dpi = 800)
 }
@@ -103,8 +106,8 @@ print(ggplot(data = subset(datos,Attributes==j), aes(x=Method,y=value,fill=Metho
   )
       
[…]

### 2016-09-09 paper.tex
Finishing the review of the introduction, with some comments and little changes

@@
 
-Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
+Our main contribution is, thus, the development of the methodology to process book sales data in order to first, find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
 To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.
@@
 This company offers management systems and services for bookshops, publishers, and distributors.
+% (Paloma) From here:
 Usually, the company's expert sales managers analysed historical data
@@
 take all the variables into account.  
+% (Paloma) to here, is repeating all over again the process of deciding how many books to print.
+I think this paragraph should be unified somehow with the previous explanations and to re-order, because the previous paragraph seems like the end of the introduction, but then we go deep in the explanations again...
+It's not an easy read :(
 In addition, the process might be tedious, especially when the amount
@@
 the relevant variables describing a book in the prediction (or
-regression) procedure. After this, a forecasting stage is performed
+regression) procedure. 
+% (Paloma) Why brackets? Suggestions:
+% relevant variables describing a book in the prediction or regression procedure
+% relevant variables describing a book in the prediction, or regression, procedure
+% relevant variables describing a book in the prediction (regression) procedure <- here brackets are ok (me thinks)
+After this, a forecasting stage is performed
 applying a set of regression algorithms to the different datasets,
@@
 
-The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes and shows a set of definitions of the regression methods applied in the paper and the evaluation metrics considered.
-Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run for new books, along with a description of the considered dataset.
+The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes, and shows a set of definitions of the regression methods applied in the paper as well as the evaluation metrics considered.
+Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run
+% (Paloma) Guys, 'print run' is written a total of 28 times:
+% 23 are in the 'print-run' form
+% 5 are 'print-run' (with a dash), of which one is inside the list of variables. But what about the rest inside text? Shouldn't they go ALL either with or without the dash?
+for new books, along with a description of the considered dataset.
 Section \ref{sec:methodology} details the methodology considered in the study.

### 2016-09-09 paper.tex
Gingerizing abstract and intro for issue #55

@@
 Indeed, several studies have demonstrated that improving sales
-predictions, that is reducing the error in estimated sales, results in an enhancement in the whole production process \cite{Fildes2010,Saeed2008}, so not only the costs associated to the book itself are affected.
+predictions, that is reducing the error in estimated sales, results in an enhancement in the whole production process \cite{Fildes2010,Saeed2008}, so not only the costs associated with the book itself are affected.
 
@@
 out to reviewers and literary magazines; the number of these will
-depend on how many were printed. In bookstores books go, in some cases, to
-the {\em novelty} table, that is, they are prominently displayed, shown in the window, or highlighted using props or other 
+depend on how many were printed. Sometimes books go to
+the {\em novelty} table of the bookstore, that is, they are prominently displayed, shown in the window, or highlighted using props or other %Pablo: rephrasing and removing comas
 kind of advertisement. From these displays they then move to shelves
@@
 
-Our main contribution is, thus, the development of the methodology to process book sales data in order to first, find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
+Our main contribution is, thus, the development of the methodology to process book sales data in order to find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
 To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.

### 2016-09-09 paper.tex
Gingerizing to Problem description and a comment for @amoragar for issue #55

@@
 been generally based on experts' experience, who analyse data about sales and, 
-taking into account their knowledge of industry, their experience, 
+taking into account their knowledge of the industry, their experience, 
 and their perception about trends, could make decisions on the companies 
@@
 ELM is an algorithm for training a single hidden 
-layer feedforward neural network which was first proposed by Guang-Bin Huang \cite
+layer feedforward neural network, which was first proposed by Guang-Bin Huang \cite
 {huang2006extreme}. A typical implementation of ELM is a single hidden layer network where the 
@@
 variables (or features), 
-related with the book publication process.
+related to the book publication process.
 
@@
 are going to be printed. Just to be clear, printing books does not
+%PABLO: that "Just to be clear" is too informal
 actually sell them, but it is obviously necessary to print books
@@
 more books to every point of sale or distribute more in novelty. We 
+%PABLO: previous phrase is toooooo large, please divide
 will come back to this choice later on when examining the resulting
@@
 final dataset since it is indeed included in the code of \texttt{collection}. 
-In addition, we think it is not really relevant for the accuracy of the models 
+In addition, we think it is not really relevant to the accuracy of the models 
 and, moreover, publishers probably will not want to use the results of other 

### 2016-09-09 paper.tex
Gingerizing to Experimental setup for issue #55

@@
 
-Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.
+Therefore, after the data has been collected and initially preprocessed (as described in the previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.
 
@@
 features, making it impractical for problems with a large number of features 
-\cite{Selvakuberan2008}; however, this is a secondary objective in this work.
+\cite{Selvakuberan2008}; however, this is a secondary objective of this work.
 
@@
 In the problem this work addresses, it is very important to maintain the 
-semantics of initial variables set, and therefore just FS methods 
+semantics of the initial variables set, and therefore just FS methods 
 have been applied.
@@
 Correlation coefficient, error measures and time to build the model have been 
-computed for every method. Obtained results are presented in 
+computed for every method. The obtained results are presented in 
 Figure \ref{fig:all_publishers_no_fs}
@@
 kNN is the fastest method used in this study in terms of training time, as it 
-is the simplest one. However, the model is slow when classifying large number of 
+is the simplest one. However, the model is slow when classifying a large number of 
 training examples, and it exhibits a poor generalisation ability since it does 
@@
 
-MLP also gets a very good correlation coefficient, however it takes the largest time to built the models, and obtains high error measures.
-ELM shows a good balance, since it is very fast in the training phase (the second faster) and yields good results according to the correlation and the error metrics.
+MLP also gets a very good correlation coefficient.
+However, it takes the largest time to built the models, and obtains high error measures.
+ELM shows a good balance, since it is very fast in the training phase (the second fastest) and yields good results according to the correlation and the error metrics.
 
@@
 published considering all the pre-sales data.
-Therefore this forecasting method, with these additional advantages, can be used for products with historical sales data and for new products with little or no historical data available.
+Therefore, this forecasting method, with these additional advantages, can be used for products with historical sales data and for new products with little or no historical data available.
 
@@
 
-Thus, the chosen map to represent the data has $26 \times 16$ neurons and an hexagonal neighbourhood topology.
+Thus, the chosen map to represent the data has $26 \times 16$ neurons and a hexagonal neighbourhood topology.
 The best SOM training results have been obtained with a final quantisation error of 0.691 and topographic error of 0.046.
@@
 left corner shows the distances between the adjacent units. It is
-important to note that high values in the matrix indicates large
+important to note that high values in the matrix indicate large
 distance between the units of the map. It can be noticed also that

### 2016-09-10 Response to reviewers.tex
where (finally) are we going to put those subsections?   XD
Finishing all
But the final revision and 'Gingerization'. XD

Closes #54
Closes #56

@@
 \begin{verbatim}
-The current paper includes in sub-section 
-`2.1. Selecting an appropriate forecasting method' (former
-sub-section 4.2) six methods: M5P, kNN, RF, LR, SVM, MLP,
- and ELM (requested by Reviewer #2). After having included
- ELM, new references have been added (the list of new references
- can be found at the end of this letter).
+The current paper includes in sub-section 4.2 six methods: M5P, kNN, 
+RF, LR, SVM, MLP, and ELM (requested by Reviewer #2). After having 
+included ELM, new references have been added (the list of new 
+references can be found at the end of this letter).
 
-Moreover, as suggested by the Reviewer #2 (see his/her first comment), 
-the results obtained with the two last methods have been included in 
-this new version of the paper.
+Moreover, as suggested by Reviewer #2 (see his/her first comment), 
+the results obtained with the last two methods have been included and 
+analyzed in this new version of the paper.
 \end{verbatim}
 % Antonio - TODO: say where are these results (table/figure/page)
+% where (finally) are we going to put those subsections?   XD
 
@@
 which incorporates a general comparison between all these classifiers.
+
+This has been clarified in the text with the following sentence, at the end of section 5.2 (page XX):
+
+"It is important to note that both RF and M5P have an embedded feature selection mechanism (the variables which compose the final trees), however this is part of their inherent procedure.
+In the following section we will apply three filter-based feature selection techniques on the dataset, so all the methods will profit."
+
 \end{verbatim}
-%Every response should end with changes made in the paper, even if it
-%is only clarification. It is not an invitation to discussion. 
-% Antonio - TODO: say how this has been addressed in the paper (where it is clarified). Say if this reference has been included as new.
-% JJ - Antonio, TODO by whom? If it's an issue, put it in the repo and assign it or do it yourself.
+% Antonio - TODO: Put the number of page.
 
@@
  paragraphs that the problem has been addressed by means of regression 
-methods (for instance, note the new title of Section 2.1), or we have 
+methods (for instance, note the new title of Section 4.2), or we have 
 generally referred to the term `regression' instead of `classification', 
 in order to better suit the regression viewpoint.
+
 Moreover this suggestion have been also addressed solving the issue 
@@
 of the text, removed some sentences, and rewritten several paragraphs 
-in order to make them shorter, clearer and to improve its comprehension.
+in order to avoid repetition, and also to make them shorter, clearer, 
+and easier to comprehend.
 
@@
 Their results have been also analyzed with the rest of methods, in the 
-paragraphs below each one of the new figures.
-A description of both approaches have been also included in subsection 2.1.
+paragraphs related to each one of the new figures.
+A description of both approaches have been also included in subsection 4.2.
 
@@
 \begin{verbatim}
-We have rewritten the introduction and included new paragraphs to better 
-explain the problem and the aim of the paper. We have also remarked the
-contribution with the paragraphs (see page XX):
+Following reviewer's request, we have rewritten the introduction and 
+included new paragraphs to better explain the problem and the aim of 
+the paper. In addition, we have laid out our methodology to differentiate 
+it from other approaches.
+
+We have also remarked the contribution with the paragraphs (see page XX):
 
@@
 many books should be printed, as well as how to leverage these printed
-copies to maximize sales using the decision variables under his control. 
-That is why, using data obtained from a company that sells software for 
-publishers, we analyse them and compute predictive models that can be 
-mainly used as decision-aid tools for book publishers. With these models,
- publishers will be able to combine their expert knowledge about the market 
-with the created forecasting models in order to get a reliable estimation of
- book sales, and, based on it, act consequently in order to maximize the 
-books sold for a particular print run. This will improve the current 
-decision flow that the publishers follow, which consist in analysing (in a
- subjective way) the quality of the book and its features (author, genre, 
-etc), and take a `fuzzy' decision roughly between printing 300 copies 
-(standard book) or 5000 (best seller).
+copies to maximize sales using the decision variables under his
+control. That is why, using data obtained from a company that sells
+software for publishers, we analyse them and compute predictive models 
+that can be mainly used as decision-aid tools for book publishers. With 
+these models, publishers will be able to combine their expert knowledge 
+about the market with the created forecasting models in order to get a 
+reliable estimation of book sales, and, based on it, act consequently 
+in order to maximize the books sold for a particular print run.
 
-Our main contribution is, thus, the development of the methodology to 
-process book sales data in order to, first find out relevant variables, 
-and then, use these variables to process the data to accurately estimate 
-future sales. To our knowledge this is the first work in which regression 
-methods have been applied to estimate sales for new launched books. 
-Moreover, we have considered a real dataset of book sales (related to 
-the Spanish market), which is another point to remark."
+This will improve the current decision flow that the publishers follow, 
+which consist in analysing (in a subjective way) the quality of the book 
+and its features (author, genre, etc), and take a `fuzzy' decision roughly
+ between printing 300 copies (standard book) or 5000 (best seller).
 
-Also, in the following paragraphs, we have laid out our 
-methodology to differentiate it from other approaches.
+This process might be tedious, especially when the amount of data is quite
+ large. Moreover, different experts can reach different predictions from 
+the same dataset [4].
+
+With these issues in mind, in this paper, we firstly present an 
+analysis on a real dataset, provided by the Spanish publishing company 
+Trevenque Editorial S.L.
+This study has been conducted by means of data mining and visualisation
+ techniques. Then, a feature selection process is performed using three
+ different methods, in order to find out what are the relevant variables
+ describing a book  in the prediction, or estimation, procedure. 
+This procedure is performed by applying a set of regression algorithms 
+to the different datasets (those with a different number of variables), 
+yielding a set of models which could be used as the desired tool.
+
+Given this, the main contribution of this paper to the state of the art 
+is the development of the aforementioned methodology to process book sales 
+data, in which: firstly, the most relevant variables are identified, and then,
+ these variables are considered to `refine' the data in order to conduct
+ accurate predictions on future sales. To our knowledge this is the first 
+work in which regression methods have been applied to estimate sales for 
+new launched books. Moreover, as stated before, we have used in the study 
+a real dataset of book sales (related to the Spanish market), which is 
+another point to remark."
+
 \end{verbatim}
@@
 data clearer and to improve their comprehension.
+
+Their analysis has been also changed and improved considering Figures 
+instead of tables.
 \end{verbatim}
@@
 in the second response to Reviewer #2, we have clarified this in 
-the introduction adding new sentences and the paragraph (see page XX):
+the introduction improving some paragraphs and adding new sentences 
+(see page XX):
 
-"Our main contribution is, thus, the development of the methodology 
-to process book sales data in order to, first find out relevant 
-variables, and then, use these variables to process the data to 
-accurately estimate future sales. To our knowledge this is the first 
-work in which regression methods have been applied to estimate sales 
-for new launched books. Moreover, we have considered a real dataset 
-of book sales (related to the Spanish market), which is another 
-point to remark."
+"Our intention in this paper is to find out the main factors influencing
+sales in order to create a tool that the publisher can use to decide how 
+many books should be printed, as well as how to leverage these printed
+copies to maximize sales using the decision variables under his
+control. That is why, using data obtained from a company that sells
+software for publishers, we analyse them and compute predictive models 
+that can be mainly used as decision-aid tools for book publishers. With 
+these models, publishers will be able to combine their expert knowledge 
+about the market with the created forecasting models in order to get a 
+reliable estimation of book sales, and, based on it, act consequently 
+in order to maximize the books sold for a particular print run.
+
+This will improve the current decision flow that the publishers follow, 
+which consist in analysing (in a subjective way) the quality of the book 
+and its features (author, genre, etc), and take a `fuzzy' decision roughly
+ between printing 300 copies (standard book) or 5000 (best seller).
+
+This process might be tedious, especially when the amount of data is quite
+ large. Moreover, different experts can reach different predictions from 
+the same dataset [4].
+
+With these issues in mind, in this paper, we firstly present an 
+analysis on a real dataset, provided by the Spanish publishing company 
+Trevenque Editorial S.L.
+This study has been conducted by means of data mining and visualisation
+ techniques. Then, a feature selection process is performed using three
+ different methods, in order to find out what are the relevant variables
+ describing a book  in the prediction, or estimation, procedure. 
+This procedure is performed by applying a set of regression algorithms 
+to the different datasets (those with a different number of variables), 
+yielding a set of models which could be used as the desired tool.
+
+Given this, the main contribution of this paper to the state of the art 
+is the development of the aforementioned methodology to process book sales 
+data, in which: firstly, the most relevant variables are identified, and then,
+ these variables are considered to `refine' the data in order to conduct
+ accurate predictions on future sales. To our knowledge this is the first 
+work in which regression methods have been applied to estimate sales for 
+new launched books. Moreover, as stated before, we have used in the study 
+a real dataset of book sales (related to the Spanish market), which is 
+another point to remark."
 
 \end{verbatim}
-% Antonio - TODO - put here the paragraph as it will finally be (if it is changed again).
 
@@
 \begin{verbatim}
-Following reviewer's suggestion we have reorganized these sub-sections, 
-moving them to section 2.
+Although the reviewer is right, considering that those sections describe 
+methods and metrics used in the state of the art, the authors wanted to 
+have section 2 as independent from the rest, given it is a key section on 
+every work.
+
+The authors think that `mixing' background concepts there could mean, 
+somehow, a lost in quality for that section.
+
+In addition, we also guess that if those subsections would be moved 
+to section 2, maybe section 4.3 should be moved too, as it also describes 
+some background concepts (usual evaluation metrics). Thus, the methodology 
+section would be certainly quite short.
+
+Finally, the rest of the reviewers haven't requested to change the 
+organisation and, moreover, Reviewer #2 has remarked that the paper 
+is well organized in his/her last comment.
+
+For these reasons we have decided to maintain those as subsections 
+of methodology (section 4).
+
+We hope that the reviewer agrees with this decision.
 \end{verbatim}
+% Antonio - TODO - check this answer for not doing nothing. XD
+% Well, actually I have to undo several things. :(
 
@@
 at page YY).
+
+Every step/stage shown in that figure has been described in the 
+following paragraphs.
 \end{verbatim}
@@
 The authors want to express our gratitude to this reviewer 
-for his/her suggestions.
+for his/her valuable comments and suggestions.
 \end{verbatim}

### 2016-09-10 paper.tex
Finishing all
But the final revision and 'Gingerization'. XD

Closes #54
Closes #56

@@
 distribution, and storage. Most of these costs are associated
-with the number of books actually printed, the so called {\em print run}. But the problem is further
-complicated for completely new products, in the sense that they have been written by an unknown
-author or deal with a new topic with no track record. In order to make
-the print run as close as possible to actual sales, it is essential to
-have an estimation of those sales; that is the challenge we are taking
-in this paper.
+with the number of books actually printed, the so called {\em print run}.
+But the problem is further complicated for completely new products, in the sense that they have been written by an unknown author or deal with a new topic with no track record.
+In order to make the print run as close as possible to actual sales, it is essential to have an estimation of those sales; that is the challenge we are taking in this paper.
 
@@
 depend on how many were printed. Sometimes books go to
-the {\em novelty} table of the bookstore, that is, they are prominently displayed, shown in the window, or highlighted using props or other %Pablo: rephrasing and removing comas
+the {\em novelty} table of the bookstore, that is, they are prominently displayed, shown in the window, or highlighted using props or other 
+%Pablo: rephrasing and removing comas
 kind of advertisement. From these displays they then move to shelves
-or, in some cases and eventually, to storage. Books stay for sale in the store as long as the
-publisher or the store wants or until the bookseller decides to return them
-to the publisher. Books returned to the publisher are pulped, sold back or
-given to the author, or finally distributed in used-books channels such as
-book stalls or second-hand bookstores. If the print run has been fully
+or, in some cases and eventually, to storage.
+Books stay for sale in the store as long as the publisher or the store wants or until the bookseller decides to return them to the publisher.
+Books returned to the publisher are pulped, sold back or given to the author, or finally distributed in used-books channels such as book stalls or second-hand bookstores.
+If the print run has been fully
 distributed and there are more requests from bookstores, on the other
@@
 Our intention in this paper is to find out the main factors influencing
-sales in order to create a tool that the publisher can use to decide how
-many books should be printed, as well as how to leverage these printed
+sales in order to create a \textit{tool} that the publisher can use to decide how many books should be printed, as well as how to leverage these printed
 copies to maximize sales using the decision variables under his
@@
 sales, and, based on it, act consequently in order to maximize the books sold for a particular print run.
+
 This will improve the current decision flow that the publishers follow, which consist in analysing (in a subjective way) the quality of the book and its features (author, genre, etc), and take a `fuzzy' decision roughly between printing 300 copies (standard book) or 5000 (best seller).
 
-Our main contribution is, thus, the development of the methodology to process book sales data in order to find out relevant variables, and then, use these variables to process the data to accurately estimate future sales.
-To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.
-Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark.
-
-Therefore, in this paper, the problem of predicting total sales is approached using real data provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}.
-This company offers management systems and services for bookshops, publishers, and distributors.
-% (Paloma) From here:
-Usually, the company's expert sales managers analysed historical data
-and applied their knowledge on external variables to compute correct
-estimations (predictions); for instance, they can decide increasing or
-decreasing the sales forecast based on season or sales period. 
-Nevertheless, just carrying out the analysis and forecasting process
-as a human expert may lead to imprecise predictions, and they may not
-take all the variables into account.  
-% (Paloma) to here, is repeating all over again the process of deciding how many books to print.
-I think this paragraph should be unified somehow with the previous explanations and to re-order, because the previous paragraph seems like the end of the introduction, but then we go deep in the explanations again...
-It's not an easy read :(
-In addition, the process might be tedious, especially when the amount
-of data is quite large. Moreover, different experts can reach different
-predictions from the same dataset \cite{Sanders1994}.
-
-With this issue in mind, in this paper we firstly present an analysis
-on the aforementioned real dataset, by means of data mining and
-visualisation techniques. Then, a feature selection process is
-conducted using three different methods, in order to find out what are
-the relevant variables describing a book in the prediction (or
-regression) procedure. 
+This process might be tedious, especially when the amount of data is quite large. Moreover, different experts can reach different predictions from the same dataset \cite{Sanders1994}.
+
+With these issues in mind, in this paper, we firstly present an analysis on a real dataset, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}\\ Trevenque offers management systems and services for bookshops, publishers, and distributors}.
+This study has been conducted by means of data mining and visualisation techniques.
+Then, a feature selection process is performed using three different methods, in order to find out what are the relevant variables describing a book  in the prediction, or estimation, procedure.
 % (Paloma) Why brackets? Suggestions:
@@
 % relevant variables describing a book in the prediction (regression) procedure <- here brackets are ok (me thinks)
-After this, a forecasting stage is performed
-applying a set of regression algorithms to the different datasets,
-also considering a different number of variables. 
+% Antonio - I have chosen a better option for not repeating 'regression' in the following sentence
+This procedure is performed by applying a set of regression algorithms to the different datasets (those with a different number of variables), yielding a set of models which could be used as the desired tool.
+
+Given this, the main contribution of this paper to the state of the art is the development of the aforementioned methodology to process book sales data, in which: firstly, the most relevant variables are identified, and then, these variables are considered to `refine' the data in order to conduct accurate predictions on future sales.
+To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books.
+Moreover, as stated before, we have used in the study a real dataset of book sales (related to the Spanish market), which is another point to remark.
+
 The value of this methodology is contrasted considering four different
@@
 
+% (Paloma) From here:
+%Usually, the company's expert sales managers analysed historical data
+%and applied their knowledge on external variables to compute correct
+%estimations (predictions); for instance, they can decide increasing or
+%decreasing the sales forecast based on season or sales period. 
+%Nevertheless, just carrying out the analysis and forecasting process
+%as a human expert may lead to imprecise predictions, and they may not
+%take all the variables into account.
+% (Paloma) to here, is repeating all over again the process of deciding how many books to print.
+I think this paragraph should be unified somehow with the previous explanations and to re-order, because the previous paragraph seems like the end of the introduction, but then we go deep in the explanations again...
+It's not an easy read :(
+% Antonio - removed and fused/reordered
+
 The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes, and shows a set of definitions of the regression methods applied in the paper as well as the evaluation metrics considered.
-Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run
+Then, Section \ref{sec:problem} introduces the problem of the estimation of print run
 % (Paloma) Guys, 'print run' is written a total of 28 times:
@@
 % 5 are 'print-run' (with a dash), of which one is inside the list of variables. But what about the rest inside text? Shouldn't they go ALL either with or without the dash?
+% Antonio - I have replaced all of them by 'print run' as it seems to be the correct one
 for new books, along with a description of the considered dataset.
@@
 Then, machine learning techniques are applied to predict sales and to infer 
-the ideal print-run of a book.
+the ideal print run of a book.
 In addition, since publishers need models to explain obtained predictions, 
@@
 on decision rules have been tested as an alternative.
-
-% following two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)
-
-Many of these previous papers propose using different prediction methods to find out which one performs the best.
-Thus, next subsections describe several forecasting methods and different 
-evaluation metrics, commonly used in the bibliography that have been chosen 
-to address the problem of book sales prediction.
-
-%-------------------------------------------------
-\subsection{Regression methods}
-\label{subsec:select_method}
-
-As previously stated, there are many prediction methods available in the 
-literature, each one with a different parameter set that may affect the 
-obtained results.
-
-However, as in the case of new books only some descriptive data are available,
-compared to those cases in which historical data on sales of published books 
-is available, not all forecasting methods can be used in this specific problem.
-
-Thus, in this research six forecasting methods, based on the State of the Art 
-literature review (see above, Section \ref{sec:soa}) 
-\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, 
-have been used. 
-Well known forecasting methods implemented in the Weka tool have been chosen, 
-as these methods are widely known, and could be very helpful for practitioners 
-to reproduce experiments and even to solve similar sales prediction problems 
-using these methods.
-
-Specifically, the following forecasting methods are proposed:
-
-\begin{itemize}
-
- % weka.classifiers.trees.M5P
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
- \item \emph{M5 Model trees (M5P)}: 
-A decision tree consists of answer-nodes, that indicate a class, and decision-nodes, 
-that contain an attribute name and branches to other sub-decision trees.
-Building a decision tree can be done using many algorithms, i.e. ID3 and C4.5 \cite{Quinlan1986}.
-However, in order to use this model in regression problems, some authors have 
-extended the model using methods such as the M5 model tree \cite{Quinlan1986,Quinlan1992,Wang1997,WittenFrank2000}, 
-by combining a conventional decision tree and generating linear regression 
-functions at the nodes.
-
-The construction of a model tree is similar to that of classical decision 
-trees \cite{Solomatine2004}:
-The process breaks the input space of the training data through decision points 
-(nodes) to assign a linear model suitable for that sub-area of the input space. 
-This process may lead to a complex model tree.
-
-Model tree models can learn and tackle tasks with high dimensionality, even up to 
-hundreds of attributes, and generate reproducible and comprehensible representations, 
-what makes them potentially more successful in the eyes of decision makers.
-
-The final model consists of the collection of linear sub-models that brings the 
-required non-linearity in dealing with the regression problem
-and both the predicted values at the answer-nodes along with the path from the 
-root to that node is given as a result.
-
- % weka.classifiers.lazy.IBk 
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
- \item \emph{k-Nearest Neighbours (kNN)}: 
-The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
-which the unknown instances are classified by relating them to the known 
-instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
-
-The main idea behind the algorithm is that two instances far enough in the space, 
-taking into account the distance function, are less likely to belong to the 
-same class than two closely situated instances.
-
-The classification algorithm locates the nearest neighbour in instance space and 
-assigns the class of that neighbour to the unknown instance.
-In order to improve the robustness of the model, several neighbours can be 
-located, assigning the resulting class to an unclassified vector using the 
-closest $k$ vectors found in the training set by majority vote.
-
- \item \emph{Random Forest (RF)}: This method is based on the
-   construction of a set of decision trees using a stochastic process
-   over the basis of C4.5 algorithm. It was proposed by Breiman
-   \cite{Breiman2001} and aims to create independent and uncorrelated
-   trees based on different and random input vectors, following the
-   same distribution. 
-The result is the average of the generated trees during the process.
-
- % weka.classifiers.functions.LinearRegression
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
- \item \emph{Linear Regression (LR)}:
- Linear Regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
-relationship between a scalar dependent variable (outcome) and several independent 
-variables (predictors) over the range of values in the dataset. 
-In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.
-
-This method of regression provides an adequate and interpretable description of 
-how the input affects the output as it models the dependent variable as a linear 
-function of the independent variables. Moreover, the linear relation can be 
-solved using the least squares method, that minimises the error between the 
-current data and the regression line \cite{McClendon2015}.
-
- % weka.classifiers.functions.SMOreg
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
- \item \emph{Support Vector Machine for Regression (SVM)}:
-Support vector machine (SVM) \cite{Cortes1995,Shevade1999,MinSVM05} method is based on  
-statistical learning theory and has successfully used in classification and  
-regression problems \cite{Cao2003,Jari2008}.
-
-In regression problems, the algorithm chooses a hyperplane close to as many 
-of the data points as possible, minimising the sum of the distances from 
-the data points to the hyperplane. 
-In both cases, the hyperplane is defined by a subset of training set samples, 
-called support vectors.
-%This method works well even if the space is highly dimensional and the problem is not linearly separable.
-
- % weka.classifiers.functions.MultilayerPerceptron
- %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
- \item \emph{Multilayer Perceptron}:
-A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
-artificial neural network model that maps the input data onto an appropriate output. 
-It is an artificial neural network generally used for classification or 
-approximation/regression problems.
-
-This model is a generalisation of the standard linear perceptron that uses several layers of nodes (called neurons) and that is able to solve linearly inseparable problems \cite{SteinwenderBitzer2003}.
-Each neuron consists of a linear combination of weighted inputs which is passed 
-though a non-linear activation function to produce its output.
-
-This kind of artificial neural network is trained using a supervised learning 
-technique called back-propagation.
-This training method was developed independently by Werbos \cite{Werbos1974}, 
-Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
-in updating the weights of the output layer neurons once the erroneous output 
-has been obtained, and then, propagating the successive weight layers back to 
-the input layer.
-
-A key issue when designing an MLP is the number of hidden layers of neurons.
-Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
-create classifying regions of any kind. This result was then confirmed in later 
-works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
-
-\item \emph{Extreme learning machine (ELM)}: 
-ELM is an algorithm for training a single hidden 
-layer feedforward neural network, which was first proposed by Guang-Bin Huang \cite
-{huang2006extreme}. A typical implementation of ELM is a single hidden layer network where the 
-connection weights between the input layer and the hidden layer are randomly initialized and 
-fixed, while the connection weights between the hidden layer the output layer are learnt 
-analytically in a single step of linear parameters solving. In ELM the hidden layer maps the 
-input data into a feature space called ELM feature space using non-linear activation functions 
-such as Sigmoid, Hyperbolic and Gaussian functions \cite{huang2015trends}.The main advantages 
-of ELM are the ease of use and the very efficient learning speed compared to other traditional 
-training methods such as the Backpropagation algorithm.
-
-\end{itemize}
-
-The objective is finding the most appropriate forecasting method that minimises 
-the error between the obtained forecast and the current sales for each new book 
-published. To this end, the results will be evaluated using different metrics, as described in the following section.
-
-% Antonio - I have linked the section also here for a more fluent reading. ;)
-
-%-------------------------------------------------
-\subsection{Models evaluation}
-\label{subsec:models_evaluation}
-
-The developed forecasting models must be evaluated and assessed based on different evaluation criteria.
-In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
-Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
-
-\begin{itemize}
-  \item \emph{Mean Absolute Error} (MAE):
-        \begin{equation}\label{eq:MAE}
-            MAE = \frac{1}{n}\sum_{i=1}^n {\mid p_i - o_i\mid}
-        \end{equation}
-
-  \item \emph{Root Mean Squared Error} (RMSE):
-        \begin{equation}\label{eq:RMSE}
-            RMSE = \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 }
-        \end{equation}
-
-  \item \emph{Relative absolute error} (RAE):
-        \begin{equation}\label{eq:RAE}
-            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid \bar{o} - o_i\mid} }
-        \end{equation}
-
-  \item \emph{Root relative squared error} (RRSE):
-        \begin{equation}\label{eq:RRSE}
-            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
-        \end{equation}
-\end{itemize}
-where $o_i$ is the current value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
 
@@
 bookbinding
-print-run
+print run
 total sales
@@
 
-Therefore, after the data has been collected and initially preprocessed (as described in the previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.
-
-FS methods check the relevance of all the variables of the patterns, aiming to reduce the set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
+Therefore, after the data has been \textit{collected} and initially \textit{preprocessed} (as described in the previous section), other preprocessing techniques have been applied, such as \textit{Feature Selection} (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.
+
+FS methods check the relevance of all the variables of the patterns, aiming to reduce the set of features on a dataset, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
 This task may also help to identify leading indicators to be considered 
@@
 At this stage of the methodology, both numerical and visualisation-based approaches have been applied, in order to select the best set of variables for the forecasting methods.
-
-After this process has been conducted, different prediction methods have been applied on the dataset.
-These methods have been described in Section \ref{subsec:select_method}, and include rule- and tree-based algorithms, together with numerical regression methods.
-
-As a result, several prediction models are obtained.
-Then the obtained models for the whole dataset have been evaluated by means of the metrics described in Section \ref{subsec:models_evaluation}.
-The results are presented in Section \ref{sec:experiments}.
-
-After this, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}).
-Specific interpretable models have been created as a final result of the work (Section \ref{subsec:decision_trees}).
-
-% Antonio - CONCERN - The following section seems to be misplaced after moving the rest to Section 2.
-Thus, the Methodology Section is now a bit strange with just this subsection.
-We should think on moving this section and reorganize/improve the methodology description.
+These are described in Section \ref{subsec:fs_techniques}.
+
+After this process has been conducted, different rule-based, tree-based and numerical \textit{forecasting methods} have been applied on the dataset.
+They are regression techniques and have been described in Section \ref{subsec:regression_methods}.
+
+As a result of the previous step, several prediction models are obtained for the whole dataset.
+These have been \textit{evaluated} by means of the metrics described in Section \ref{subsec:evaluation_metrics}, and also \textit{analysed} in the experiments (Section \ref{sec:experiments}).
+
+After this, the same methodology has been applied to some specific cases of publishing companies in order to \textit{validate} the proposal (Section \ref{sec:example_cases}).
+To this end, also specific interpretable models have been created as a final result of the work (Section \ref{subsec:decision_trees}).
+
+In the following sections, the main techniques to be applied on these steps are described, along with the evaluation metrics computed to value the generated prediction models.
 
 %-------------------------------------------------
-\subsection{Data preprocessing by feature selection}
-\label{subsec:data_preproces}
+\subsection{Feature selection techniques}
+\label{subsec:fs_techniques}
 
@@
 
-These FS techniques have been applied in the following section, including a comparison between all of them.
+These FS techniques have been applied in Section \ref{subsec:feature_selection}, including a comparison between all of them.
+
+%-------------------------------------------------
+\subsection{Regression methods}
+\label{subsec:regression_methods}
+
+As previously stated, there are many prediction algorithms available in the 
+literature, each one with a different parameter set that may affect the 
+obtained results.
+
+However, as in the case of new books only some descriptive data are available,
+compared to those cases in which historical data on sales of published books 
+is available, not all forecasting methods can be used in this specific problem.
+
+Thus, in this research six forecasting methods, based on the State of the Art 
+literature review (see above, Section \ref{sec:soa}) 
+\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, 
+have been used. 
+Well known forecasting methods implemented in the Weka tool have been chosen, 
+as these methods are widely known, and could be very helpful for practitioners 
+to reproduce experiments and even to solve similar sales prediction problems 
+using these methods.
+
+Specifically, the following forecasting methods are proposed:
+
+\begin{itemize}
+
+ % weka.classifiers.trees.M5P
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
+ \item \emph{M5 Model trees (M5P)}: 
+A decision tree consists of answer-nodes, that indicate a class, and decision-nodes, 
+that contain an attribute name and branches to other sub-decision trees.
+Building a decision tree can be done using many algorithms, i.e. ID3 and C4.5 \cite{Quinlan1986}.
+However, in order to use this model in regression problems, some authors have 
+extended the model using methods such as the M5 model tree \cite{Quinlan1986,Quinlan1992,Wang1997,WittenFrank2000}, 
+by combining a conventional decision tree and generating linear regression 
+functions at the nodes.
+
+The construction of a model tree is similar to that of classical decision 
+trees \cite{Solomatine2004}:
+The process breaks the input space of the training data through decision points 
+(nodes) to assign a linear model suitable for that sub-area of the input space. 
+This process may lead to a complex model tree.
+
+Model tree models can learn and tackle tasks with high dimensionality, even up to 
+hundreds of attributes, and generate reproducible and comprehensible representations, 
+what makes them potentially more successful in the eyes of decision makers.
+
+The final model consists of the collection of linear sub-models that brings the 
+required non-linearity in dealing with the regression problem
+and both the predicted values at the answer-nodes along with the path from the 
+root to that node is given as a result.
+
+ % weka.classifiers.lazy.IBk 
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
+ \item \emph{k-Nearest Neighbours (kNN)}: 
+The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
+which the unknown instances are classified by relating them to the known 
+instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
+
+The main idea behind the algorithm is that two instances far enough in the space, 
+taking into account the distance function, are less likely to belong to the 
+same class than two closely situated instances.
+
+The classification algorithm locates the nearest neighbour in instance space and 
+assigns the class of that neighbour to the unknown instance.
+In order to improve the robustness of the model, several neighbours can be 
+located, assigning the resulting class to an unclassified vector using the 
+closest $k$ vectors found in the training set by majority vote.
+
+ \item \emph{Random Forest (RF)}: This method is based on the
+   construction of a set of decision trees using a stochastic process
+   over the basis of C4.5 algorithm. It was proposed by Breiman
+   \cite{Breiman2001} and aims to create independent and uncorrelated
+   trees based on different and random input vectors, following the
+   same distribution. 
+The result is the average of the generated trees during the process.
+
+ % weka.classifiers.functions.LinearRegression
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
+ \item \emph{Linear Regression (LR)}:
+ Linear Regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
+relationship between a scalar dependent variable (outcome) and several independent 
+variables (predictors) over the range of values in the dataset. 
+In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.
+
+This method of regression provides an adequate and interpretable description of 
+how the input affects the output as it models the dependent variable as a linear 
+function of the independent variables. Moreover, the linear relation can be 
+solved using the least squares method, that minimises the error between the 
+current data and the regression line \cite{McClendon2015}.
+
+ % weka.classifiers.functions.SMOreg
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
+ \item \emph{Support Vector Machine for Regression (SVM)}:
+Support vector machine (SVM) \cite{Cortes1995,Shevade1999,MinSVM05} method is based on  
+statistical learning theory and has successfully used in classification and  
+regression problems \cite{Cao2003,Jari2008}.
+
+In regression problems, the algorithm chooses a hyperplane close to as many 
+of the data points as possible, minimising the sum of the distances from 
+the data points to the hyperplane. 
+In both cases, the hyperplane is defined by a subset of training set samples, 
+called support vectors.
+%This method works well even if the space is highly dimensional and the problem is not linearly separable.
+
+ % weka.classifiers.functions.MultilayerPerceptron
+ %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
+ \item \emph{Multilayer Perceptron}:
+A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
+artificial neural network model that maps the input data onto an appropriate output. 
+It is an artificial neural network generally used for classification or 
+approximation/regression problems.
+
+This model is a generalisation of the standard linear perceptron that uses several layers of nodes (called neurons) and that is able to solve linearly inseparable problems \cite{SteinwenderBitzer2003}.
+Each neuron consists of a linear combination of weighted inputs which is passed 
+though a non-linear activation function to produce its output.
+
+This kind of artificial neural network is trained using a supervised learning 
+technique called back-propagation.
+This training method was developed independently by Werbos \cite{Werbos1974}, 
+Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
+in updating the weights of the output layer neurons once the erroneous output 
+has been obtained, and then, propagating the successive weight layers back to 
+the input layer.
+
+A key issue when designing an MLP is the number of hidden layers of neurons.
+Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
+create classifying regions of any kind. This result was then confirmed in later 
+works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.
+
+\item \emph{Extreme learning machine (ELM)}: 
+ELM is an algorithm for training a single hidden 
+layer feedforward neural network, which was first proposed by Guang-Bin Huang \cite
+{huang2006extreme}. A typical implementation of ELM is a single hidden layer network where the 
+connection weights between the input layer and the hidden layer are randomly initialized and 
+fixed, while the connection weights between the hidden layer the output layer are learnt 
+analytically in a single step of linear parameters solving. In ELM the hidden layer maps the 
+input data into a feature space called ELM feature space using non-linear activation functions 
+such as Sigmoid, Hyperbolic and Gaussian functions \cite{huang2015trends}.The main advantages 
+of ELM are the ease of use and the very efficient learning speed compared to other traditional 
+training methods such as the Backpropagation algorithm.
+
+\end{itemize}
+
+The objective is finding the most appropriate forecasting method that minimises 
+the error between the obtained forecast and the current sales for each new book 
+published. To this end, the results will be evaluated using different metrics, as described in the following section.
+
+% Antonio - I have linked the section also here for a more fluent reading. ;)
+
+%-------------------------------------------------
+\subsection{Evaluation metrics}
+\label{subsec:evaluation_metrics}
+
+The developed forecasting models must be evaluated and assessed based on different evaluation criteria.
+In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
+Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
+
+\begin{itemize}
+  \item \emph{Mean Absolute Error} (MAE):
+        \begin{equation}\label{eq:MAE}
+            MAE = \frac{1}{n}\sum_{i=1}^n {\mid p_i - o_i\mid}
+        \end{equation}
+
+  \item \emph{Root Mean Squared Error} (RMSE):
+        \begin{equation}\label{eq:RMSE}
+            RMSE = \sqrt{ \frac{1}{n}\sum_{i=1}^n {(p_i - o_i)}^2 }
+        \end{equation}
+
+  \item \emph{Relative absolute error} (RAE):
+        \begin{equation}\label{eq:RAE}
+            RAE = \frac{ \sum_{i=1}^n {\mid p_i - o_i\mid} }{ \sum_{i=1}^n {\mid \bar{o} - o_i\mid} }
+        \end{equation}
+
+  \item \emph{Root relative squared error} (RRSE):
+        \begin{equation}\label{eq:RRSE}
+            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
+        \end{equation}
+\end{itemize}
+where $o_i$ is the current value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.
 
@@
 
-Taking into account the obtained results by SVM model, this method obtains comparable 
-errors to those of M5P. Even when using roughly tuned parameter values, it shows 
-a good generalisation performance. However, SVM is much slower than the others to build 
-the model, not only when using the dataset with categorical input variables, such 
-as \texttt{collection} and \texttt{binding}, but also when using the datasets with 
-numerical variables, not to mention the extra time needed to optimize its hyperparameters.
+Taking into account the obtained results by SVM model, this method obtains comparable errors to those of M5P.
+Even when using roughly tuned parameter values, it shows a good generalisation performance.
+However, SVM is much slower than the others to build the model, not only when using the dataset with categorical input variables, such as \texttt{collection} and \texttt{binding}, but also when using the datasets with numerical variables, not to mention the extra time needed to optimize its hyperparameters.
 
@@
 
+It is important to note that both RF and M5P have an embedded feature selection mechanism (the variables which compose the final trees), however this is part of their inherent procedure.
+In the following section we will apply three filter-based feature selection techniques on the dataset, so all the methods will profit.
+
 %--------------------------------------------------------------------------
@@
 
-We have used both the {\tt CfsSubsetEval} (CSE) \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval (RFE) \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.
+We have used both the {\tt CfsSubsetEval} (CSE) \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval (RFE) \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:fs_techniques}.
 
@@
 in the appendix of tables).
+
 Results in the figure show that the models performed similarly to the case of 
@@
 Figure \ref{fig:all_publishers_no_fs}. 
-In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR. 
+In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR, and also better than MLP and ELM.
+Actually, the latter presents a low performance in these special cases (not previously for the whole dataset).
+This could be due to the reported low robustness of the basic ELM version \cite{ding2015deep}, which we have applied in this work.
+More advanced versions such as the Multi-layer ELM, Hierarchical ELM and ELM with kernels will be investigated and experimented in the future work in order to reach better generalization performance.
+
 In the case of Best selling publisher houses (i.e. UDL929) and publishers who 
@@
 
-% tables have been moved to the Appendix and they have been substituted by the new Figure. Comments (text) have been adapted accordingly  -  [pedro]
-%Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}. 
-%The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}.
-In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR.
-In the case of Best selling publisher houses (i.e.
-UDL929) and publishers who publish wide range of different books (i.e.
-UDL704), M5P could be recommended as it shows more accurate forecasting results than the other models.
-While in the case of medium sized publishers, in terms of sales and number of published books, the RF model would be adequate.
-
 %--------------------------------------------------------------------------
@@
 
-In this stage of the experiments for the special cases, the
-feature selection methods (RFE, CSE and SOM) are applied for each case
-independently, since publishers with different sales ranges, and
-targets, might in fact include different factors or have different
-leverage when deciding how much to print.
+Now the feature selection methods (RFE, CSE and SOM) are applied for each case
+independently, since publishers with different sales ranges, and targets, might in fact include different factors or have different leverage when deciding how much to print.
 
@@
 
-%  dejamos ésta finalmente: tablas al apéndice + incluimos nueva figura con los datos del RFE.
 For clarity purpose, only obtained results after applying the RFE method for the 
-four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}
- (detailed numeric results can be seen in 
+four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}.
+Detailed numeric results of RFE on the special cases can be seen in 
 Tables \ref{Table:case1results_fs_rf}, \ref{Table:case2results_fs_rf}, 
 \ref{Table:case3results_fs_rf} and \ref{Table:case4results_fs_rf}
-in the appendix of tables).
-This one was chosen since the selected features by RFE method showed in the 
-previous experiment the highest predictive power among all models.
-As can be shown, RFE reduction has noticeably improved the performance of all 
-classifiers specially in the case of the best selling publisher house (i.e. UDL929) 
-and the publisher which publishes a wide range of different books (i.e. UDL704). 
-For the rest of the results which are obtained by CSE and SOM feature selection 
-methods we refer the reader to the appendix of tables at the end of this paper.
+in the appendix of tables. 
+RFE was chosen since the selected features by this method showed in the experiment with the whole dataset the highest predictive power among all models.
+For the rest of the results which are obtained by CSE and SOM FS methods, we refer the reader also to the appendix of tables.
+
+As it can be seen, RFE reduction has noticeably improved the performance of all 
+classifiers specially in the case of the best selling publisher house (i.e. UDL929) and the one which publishes a wide range of different books (i.e. UDL704).
 
@@
 
-The right hand side of the tree include those books that are
+The right hand side of the tree includes those books that are
 distributed in a bigger percentage of the total amount of point of
@@
 problem requirements) and used to predict new book sales, from which
-the optimal print-run could be estimated. These algorithms include
+the optimal print run could be estimated. These algorithms include
 some based on Decision Trees (M5P and Random Forest), kNN, Support
@@
 Finally, there are some variables over which the publisher has some
-control once the book has been published, such as the initial print-run, 
+control once the book has been published, such as the initial print run, 
 the books offered as gifts to reviewers, or what proportion is going to be sent 

### 2016-09-10 Response to reviewers.tex
adding the new reference to the responses
completed responses to reviewer-1

@@
 short, which was first introduced and implemented by Robnik-Sikonja 
-and Kononenko (in ref. [73] for numeric targets). 
+and Kononenko (in ref. [38] for numeric targets). 
 Therefore, we have clarified this point in the text to remove 
-any ambiguity.
-\end{verbatim}
-% Antonio - TODO: say where is this clarification in the text (page/paragraph) 
-\begin{verbatim}
+any ambiguity (see page 7, second column, and page 13 first paragraph).
+
 For CSF, estimating the correlation between attributes is 
 standard linear (Pearson's) correlation. The details have 
-been added to the text to clarify this point.
+been added to the text to clarify this point (see page 7, 
+second column, and page 13 first paragraph).
 \end{verbatim}
-% Antonio - TODO: say where is this clarification in the text (page/paragraph)
 
@@
 analyzed in this new version of the paper.
+
+The ELM and MLP descriptions can be found in page 10, first paragraph.
+Obtained results have been shown in Figures 2, 4, 5, 6, and in tables
+in the appendix.
 \end{verbatim}
-% Antonio - TODO: say where are these results (table/figure/page)
-% where (finally) are we going to put those subsections?   XD
 
@@
 As far as the number of trees is concerned, in the experiments 
-section, when describing the parameter settings, 
-it has been mentioned that the best performance was obtained 
-with a number of trees equal to 50.
+section, when describing the parameter settings, it has been 
+mentioned that the best performance was obtained with a number of 
+trees equal to 50 (see page 11, second paragraph of subsection 5.1).
 \end{verbatim}
-% Antonio - TODO: say where is this clarification in the text (page/paragraph)
 
@@
 
-This has been clarified in the text with the following sentence, at the end of section 5.2 (page XX):
+This has been clarified in the text with the following sentence, at 
+the end of section 5.2 (page 12, second column):
 
-"It is important to note that both RF and M5P have an embedded feature selection mechanism (the variables which compose the final trees), however this is part of their inherent procedure.
-In the following section we will apply three filter-based feature selection techniques on the dataset, so all the methods will profit."
-
+"It is important to note that both RF and M5P have an embedded feature 
+selection mechanism (the variables which compose the final trees), 
+however this is part of their inherent procedure. In the following 
+section we will apply three filter-based feature selection techniques 
+on the dataset, so all the methods will profit."
 \end{verbatim}
-% Antonio - TODO: Put the number of page.
 
@@
 \begin{verbatim}
-The reviewer is right, thus, we have revised the whole paper remarking 
-the regression topic present on the work. We have clarified in several
- paragraphs that the problem has been addressed by means of regression 
-methods (for instance, note the new title of Section 4.2), or we have 
-generally referred to the term `regression' instead of `classification', 
-in order to better suit the regression viewpoint.
+In agreement with reviewer’s comment, we have revised the whole paper 
+remarking the regression topic present on the work. We have clarified 
+in several paragraphs along the text that the problem has been 
+addressed by means of regression methods (for instance, note the new 
+title of Section 4.2), or we have generally referred to the term 
+`regression' instead of `classification', in order to better suit 
+the regression viewpoint.
 
@@
 Also, all the tables of results have been moved to the Appendix and 
-that data has been presented now as the new Figures XX, YY, ZZ.
+that data has been presented now in Subsection 5.2 and Section 6 
+as the new Figures 2, 4, 5 and 6.
 
@@
 \end{verbatim}
-% Antonio - TODO: show some examples of reduced text (page/paragraph), there will be some new figures, I think.
-% we have to say: "Paragraph #X in subsection #Y" (naming the paragraphs that we identified and gathered-joined)
 
@@
 pp. 359-366.
+
+[84] S. Ding, N. Zhang, X. Xu, L. Guo, J. Zhang, Deep extreme 
+learning machine and its application in eeg classification, 
+Mathematical Problems in Engineering 2015.
+
 \end{verbatim}

### 2016-09-10 paper.tex
completed responses to reviewer-1

@@
 \begin{center}
-\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_all_features_Table3.eps}
+\includegraphics[scale=0.38]{./imgs/prediction_all_publisher_all_features_Table3.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=0.42]{./imgs/prediction_all_publisher_Table5.eps}
+\includegraphics[scale=0.40]{./imgs/prediction_all_publisher_Table5.eps}
 \end{center}
@@
 \hline 
-\textit{UDL704} & 293 & 58236 & publishing company with most different\\ 
+\textit{UDL704} & 293 & 58236 & Publishing company with most different\\ 
        &     &       & books sold\\
 \hline 
-\textit{UDLU11} & 180 & 249481 & publishing company with medium number\\ 
+\textit{UDLU11} & 180 & 249481 & Publishing company with medium number\\ 
        &     &       &  of different books sold\\
@@
 \begin{center}
-\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
+\includegraphics[scale=0.58]{./imgs/attribute_All.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=0.6]{./imgs/attribute_ReliefFAttributeEval-FS.eps}
+\includegraphics[scale=0.58]{./imgs/attribute_ReliefFAttributeEval-FS.eps}
 \end{center}

### 2016-09-10 Response to reviewers.tex
completed responses to reviewer-2

@@
 
-The ELM and MLP descriptions can be found in page 10, first paragraph.
+The ELM and MLP descriptions can be found in page 10, first column.
 Obtained results have been shown in Figures 2, 4, 5, 6, and in tables
@@
 Following the reviewer's request, we have conducted several new experiments 
-and added the results of ANN (MLP) and ELM to Tables XX, YY, ZZ and
-Figures AA, BB accordingly. 
+and added the results of ANN (MLP) and ELM to Tables in the appendix, and
+Figures 2, 4, 5 and 6 accordingly. 
 Their results have been also analyzed with the rest of methods, in the 
-paragraphs related to each one of the new figures.
-A description of both approaches have been also included in subsection 4.2.
+paragraphs related to each one of the new figures in Subsection 5.2 
+and Section 6.
+
+A description of both approaches have been also included in Subsection 4.2
+(page 10, first colum).
 
 In addition new references have been added to the paper, related to these 
-methods, namely [REF_XX, REF_YY]. In any case, the list of new references
-can be found at the end of this letter.
+methods, namely [53,54,84]. In any case, the list of new references can 
+be found at the end of this letter.
 \end{verbatim}
-% Antonio - TODO: Complete with the number of tables and figures, along with the new references
 
@@
 
-We have also remarked the contribution with the paragraphs (see page XX):
+We have also remarked the contribution with the paragraphs (see page 2,
+second column):
 
@@
 \end{verbatim}
-% TODO: update with the correct page where those paragraphs can be found
 
@@
 systems have been added to the future work section, at the end 
-of Section 7 (see page XX).
+of Section 7 (see page 20, last paragraph of first column).
 \end{verbatim}
-% Antonio - TODO: put the correct page when the text is finished
 
@@
 moved to the Appendix and that data has been summarized and 
-presented as the new Figures XX, YY, ZZ in order to make that numeric 
-data clearer and to improve their comprehension.
+presented as the new Figures 2, 4, 5 and 6 (in Subsection 5.2 and 
+Section 6) in order to make that numeric data clearer and to improve 
+their comprehension.
 
@@
 \end{verbatim}
-% Antonio - TODO: put the correct page when the text is finished
 
@@
 \begin{verbatim}
-We agree with the reviewer and have designed (and uploaded) a 
-graphical abstract as a visual summary of the paper structure 
-and the utility of the obtained results.
+In agreement with reviewer’s suggestion, we have designed (and 
+uploaded) a graphical abstract as a visual summary of the paper 
+structure and the utility of the obtained results.
 

### 2016-09-10 Response to reviewers.tex
completed responses to reviewer-3

@@
 another point to remark."
-
 \end{verbatim}
@@
 the introduction improving some paragraphs and adding new sentences 
-(see page XX):
+(see page 2, second column):
 
@@
 \begin{verbatim}
-Although the reviewer is right, considering that those sections describe 
-methods and metrics used in the state of the art, the authors wanted to 
-have section 2 as independent from the rest, given it is a key section on 
-every work.
+We appreciate the reviewer's suggestion, however, considering that those 
+sections describe methods and metrics used in the state of the art, 
+our aim was to make the Section 2 as independent as possible from the rest, 
+given that it is a key section on every work.
 
@@
 In addition, we also guess that if those subsections would be moved 
-to section 2, maybe section 4.3 should be moved too, as it also describes 
+to Section 2, maybe Section 4.3 should be moved too, as it also describes 
 some background concepts (usual evaluation metrics). Thus, the methodology 
-section would be certainly quite short.
+section would be certainly quite short and incomplete.
 
@@
 
-For these reasons we have decided to maintain those as subsections 
-of methodology (section 4).
+For these reasons we have decided to maintain those subsections as part
+of the methodology (section 4).
 
@@
 \end{verbatim}
-% Antonio - TODO - check this answer for not doing nothing. XD
-% Well, actually I have to undo several things. :(
 
@@
 Taking into account the reviewer's comment, we have improved the 
-description of the methodology including a flowchart (see Figure XX 
-at page YY).
+description of the methodology including a flowchart (see Figure 1 
+at page 6).
 
 Every step/stage shown in that figure has been described in the 
-following paragraphs.
+following paragraphs (Section 4, page 6).
 \end{verbatim}
@@
 \begin{verbatim}
-Reviewer is right, so we have improved Section 5, including the 
-parameter settings of M5P, kNN and RF methods (see paragraph XX at 
-page YY), along with the configuration parameters for the rest of 
-methods.
+In agreement with reviewer’s comment, Section 5 has been improved, 
+including the parameter settings of M5P, kNN and RF methods (see 
+Subsection 5.1, page 11, first column), along with the configuration 
+parameters for the rest of methods.
 
@@
 \end{verbatim}
-% Antonio - TODO: say paragraph/page where they are.
 

### 2016-09-10 Tables_to_figures/generador.r
New tittle in Figure 5.

@@ -111,6 +111,17 @@ print(ggplot(data = subset(datos,Attributes==j), aes(x=Method,y=value,fill=Metho
 
   }
 
+t <- subset(datos,Attributes=="All")
+
+print(ggplot(data = t, aes(x=Method,y=value,fill=Method)) + 
+        geom_point(stat="identity",size=2)  + geom_bar(stat="identity") + 
+        facet_grid(variable ~ Dataset,scales = "free_y") + 
+        scale_fill_grey(start=0.2,end=0.6) + labs(title="All features",x="",y="") + 
+        geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.5,size=0.5) + theme_bw()  + theme(legend.position="right") +
+        scale_y_continuous(limits = c(0, NA))
+)
+
+
 var = unique(datos$variable)
 
 for(i in var){
@@ -182,7 +193,7 @@ datos$variable <- factor(datos$variable, c("R","MAE","RMSE","RAE","RRSE","TIME")
 ggplot(data = subset(datos), aes(x=Method,y=value)) + 
   geom_bar(aes(fill=Method),stat="identity",size=3) + geom_point(stat="identity",size=3) +
   facet_grid(variable ~ Attributes ,scales = "free_y") + 
-  scale_fill_grey(start=0.2,end=0.6) + labs(title="",x="",y="") + 
+  scale_fill_grey(start=0.2,end=0.6) + labs(title="All features",x="",y="") + 
   geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="right") + 
   scale_y_continuous(limits = c(0, NA))
 

### 2016-09-10 Response to reviewers.tex
fixing some codification problems (latin-1)

@@
 \begin{verbatim}
-In agreement with reviewer’s comment, we have revised the whole paper 
+In agreement with reviewer's comment, we have revised the whole paper 
 remarking the regression topic present on the work. We have clarified 
@@
 title of Section 4.2), or we have generally referred to the term 
-`regression' instead of `classification', in order to better suit 
+'regression' instead of 'classification', in order to better suit 
 the regression viewpoint.
@@
 \begin{verbatim}
-In agreement with reviewer’s suggestion, we have designed (and 
+In agreement with reviewer's suggestion, we have designed (and 
 uploaded) a graphical abstract as a visual summary of the paper 
@@
 
-The authors think that `mixing' background concepts there could mean, 
+The authors think that 'mixing' background concepts there could mean, 
 somehow, a lost in quality for that section.
@@
 \begin{verbatim}
-In agreement with reviewer’s comment, Section 5 has been improved, 
+In agreement with reviewer's comment, Section 5 has been improved, 
 including the parameter settings of M5P, kNN and RF methods (see 
@@
 \end{verbatim}
+
+~\\
 

### 2016-09-10 Tables_to_figures/generador.r
New values of ELM in dataset files.

@@ -1,6 +1,8 @@
 library(stringr)
 library(reshape2)
 library(ggplot2)
+library(scales)
+
 
 filenames_all <- list.files(path = "datasets/AllAttributes/",pattern = ".csv",full.names = TRUE)
 ldf <- lapply(filenames_all, read.csv, skip=0, header=TRUE, sep=";",blank.lines.skip = TRUE,strip.white = TRUE, colClasses = rep("character",7))
@@ -82,7 +84,7 @@ for(i in dataset){
     scale_fill_grey(start=0.6,end=0.8) + labs(title=i,x="",y="") + 
     geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.5,size=0.5) + theme_bw()  +
     theme(legend.position="bottom", axis.title.x=element_blank(),axis.ticks.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) + 
-    scale_y_continuous(limits = c(0, NA)))
+    scale_y_continuous(limits = c(0, NA),oob=squish))
   
   
   ggsave(file=paste0("../imgs/datasets_",i,".eps"),scale=2,units = "cm", width = 16, height = 8,dpi = 800)
@@ -102,7 +104,7 @@ print(ggplot(data = subset(datos,Attributes==j), aes(x=Method,y=value,fill=Metho
   facet_grid(variable ~ Dataset,scales = "free_y") + 
   scale_fill_grey(start=0.2,end=0.6) + labs(title=j,x="",y="") + 
   geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.2,size=0.25) + theme_bw()  + theme(legend.position="right") +
-    scale_y_continuous(limits = c(0, NA))
+    scale_y_continuous(limits = c(0, NA),oob=squish)
   )
       
 
@@ -118,8 +120,11 @@ print(ggplot(data = t, aes(x=Method,y=value,fill=Method)) +
         facet_grid(variable ~ Dataset,scales = "free_y") + 
         scale_fill_grey(start=0.2,end=0.6) + labs(title="All features",x="",y="") + 
         geom_errorbar(aes(ymin=value-error,ymax=value+error), width=0.5,size=0.5) + theme_bw()  + theme(legend.position="right") +
-        scale_y_continuous(limits = c(0, NA))
+        scale_y_continuous(limits = c(0, NA),oob=squish)
 )
+j = "All"
[…]

### 2016-09-12 paper.tex
completed responses to reviewer-3
Updating ELM results
I have conducted new ELM experiments in order to get more robust results
removed extra spaces
adding an extra space :P  ...and 500 commits objective achieved  :D
Finished gingerization, so @pacastillo can send the paper. Closes #55

@@
 However, the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}.
-Figure \ref{fig:methodology} summarizes these followed steps.
+Figure \ref{fig:methodology} summarizes these steps.
 
@@
 In the case of Best selling publisher houses (i.e. UDL929) and publishers who 
-publish wide range of different books (i.e. UDL704), M5P could be recommended 
+publish a wide range of different books (i.e. UDL704), M5P could be recommended 
 as it shows more accurate forecasting results than the other models. 
@@
 
-Now the feature selection methods (RFE, CSE and SOM) are applied for each case
+Now the feature selection methods (RFE, CSE and SOM) are applied in each case
 independently, since publishers with different sales ranges, and targets, might in fact include different factors or have different leverage when deciding how much to print.
@@
 
-For clarity purpose, only obtained results after applying the RFE method for the 
+For clarity purposes, only obtained results after applying the RFE method for the 
 four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}.
@@
 
-What is, then, the model obtained with our method? What factors have
+What is, then, the model obtained by our method? What factors have
 the biggest influence in sales and how can a publisher use them to gauge
 sales of a new book? In order to do that, we have examined the models
-built during the regression. Namely we present two of the decision
+built during the regression. Namely, we present two of the decision
 trees generated by M5P method applied to the data of the publisher
@@
 % I'm reducing some paragraphs by eliminating some sentences that appears repeated.
-(it has the biggest influence on the decision models and also a major role in forecasting the total sales, implying that books have to physically {\em be} in the point of sale).
+(it has the biggest influence on the decision models and also a major role in forecasting the total sales, implying that the books have to physically {\em be} in the point of sale).
 % This indicates that the total number of points of sale has the biggest influence on the decision models and also a major role in forecasting the total sales, implying that buyers have to actually {\em see}, maybe browse the book, before buying it.
@@
 variables impacting positively or negatively. A whole treatise could
-be written on this decision tree but, in this case, let us look a bit
-more closely at this box and try and interpret it. For instance, price
+be written on this decision tree, but in this case, let us look a bit
+more closely at this box and try and interpret it. For instance, the price
 in this case will impact negatively on sales. For a typical retail
 price of a trade paperback of 12 euro, we would be looking at negative
-sales (if we disregard the rest of the variables) , which in this case
+sales (if we disregard the rest of the variables), which in this case
 will indicate that these are the kind of books, maybe paperbacks, that
@@
 are talking about, sales start at 1000 but the single factor that has
-a bigger influence in sales is the topic, which has to be either 23 or
-1. '1' is the first digit of the classification used for all kind of
-general literary books. '23' includes philology, which includes either
+a bigger influence on sales is the topic, which has to be either 23 or
+1. `1' is the first digit of the classification used for all kinds of
+general literary books. `23' includes philology, which includes either
 textbooks of maybe books in a foreign language; there are just a few
-of those, with '1' being far more common. So in principle these would
+of those, with `1' being far more common. So, in principle these would
 be the typical best-sellers, literary prizes and big hits, but we
@@
 painted by the second tree is a bit more bleak; obviously, even big
-publishing house produce flops from time to time, and those would be
+publishing house produces flops from time to time, and those would be
 books which eventually print less than around 12500, indicating that
@@
 this model is to boost points of sale and lower price so that sales
-pick a bit; in this sense and in certain cases our model is more
+pick a bit; in this sense and in certain cases, our model is more
 informative than predictive, but having numeric models helps anyway
@@
 is related to the fact that they will have to be selling for a long
-time, that is, not only be best, but also long sellers, which is also
+time, that is, not only be better, but also long sellers, which is also
 indicated by the positive factor in the number of weeks they are for
@@
 in their models. This does not mean that the retail price is not a
-factor; it appears in all models, but it will be a secondary factor
+factor; it appears on all models, but it will be a secondary factor
 that will have to be decided once the main ones are settled.
@@
 is similar such as novelty items or toys, and might be of interest to other 
-academic researches and industrial practitioners.
+academic researchers and industrial practitioners.
 
@@
 interesting to observe, and factor in the method, country differences,
-even considering the same book and how it sells in different
+even considering the same book and how it is sold in different
 countries.
@@
 \hline 
-ELM & 	86.79	 $\pm$ 	0.11	 & 	271.01	 $\pm$ 	28.53	 & 	684.98	 $\pm$ 	329.39	 & 	47.73	 $\pm$ 	0.06	 & 	52.42	 $\pm$ 	0.26	 & 	0.203	 $\pm$ 	0.03  \tabularnewline
+ELM & 	85.97	 $\pm$ 	0.11	 & 	285.64	 $\pm$ 	28.44	 & 	701.65	 $\pm$ 	293.66	 & 	50.41	 $\pm$ 	6.4	 & 	54.7	 $\pm$ 	26.93	 & 	0.1939	 $\pm$ 	0.004 \tabularnewline
 
@@
 \hline
-ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
+ELM & 	86.84	 $\pm$ 	0.09	 & 	283.07	 $\pm$ 	30.78	 & 	686.05	 $\pm$ 	278.37	 & 	49.88	 $\pm$ 	6.15	 & 	52.08	 $\pm$ 	20.64	 & 	0.0133	 $\pm$ 	0.003\\
 \hline
@@
 \hline  
-ELM & 	87.55	 $\pm$ 	0.1	 & 	250.88	 $\pm$ 	28.78	 & 	677.94	 $\pm$ 	356.41	 & 	44.16	 $\pm$ 	0.05	 & 	50.86	 $\pm$ 	0.24	 & 	0.1106	 $\pm$ 	0.02\\
-\hline
+ELM & 	87.25	 $\pm$ 	0.1	 & 	277.38	 $\pm$ 	27.54	 & 	669.29	 $\pm$ 	307.31	 & 	49	 $\pm$ 	6.59	 & 	51.81	 $\pm$ 	25.4	 & 	0.0677	 $\pm$ 	0.002\\
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	85.3	 $\pm$ 	0.09	 & 	301.42	 $\pm$ 	31.43	 & 	704.9	 $\pm$ 	221.83	 & 	53.22	 $\pm$ 	0.07	 & 	54.57	 $\pm$ 	0.18	 & 	0.0229	 $\pm$ 	0.02\\
+ELM & 	85.82	 $\pm$ 	0.08	 & 	299.48	 $\pm$ 	34.26	 & 	697.84	 $\pm$ 	229.85	 & 	52.78	 $\pm$ 	6.55	 & 	54.19	 $\pm$ 	19.44	 & 	0.0406	 $\pm$ 	0.003\\
 \hline
@@
 \hline
-ELM & 	53.38	 $\pm$ 	0.24	 & 	1898.17	 $\pm$ 	728.63	 & 	3104.85	 $\pm$ 	1503.83	 & 	136.82	 $\pm$ 	0.76	 & 	146.75	 $\pm$ 	0.95	 & 	0.0184	 $\pm$ 	0.02
- \tabularnewline
+
+ELM & 	53.41	 $\pm$ 	0.27	 & 	1922.9	 $\pm$ 	584.89	 & 	3118.51	 $\pm$ 	1207.6	 & 	141.11	 $\pm$ 	73.93	 & 	150.48	 $\pm$ 	102.6	 & 	0.0237	 $\pm$ 	0.003\tabularnewline
+
 \hline
@@
 \hline
-ELM & 	87.25	 $\pm$ 	0.14	 & 	776.49	 $\pm$ 	209.23	 & 	1171.43	 $\pm$ 	455.5	 & 	53.63	 $\pm$ 	0.25	 & 	53.14	 $\pm$ 	0.37	 & 	0.0031	 $\pm$ 	0.01\tabularnewline
-\hline
+ELM & 	86.46	 $\pm$ 	0.14	 & 	779.62	 $\pm$ 	229.99	 & 	1206.94	 $\pm$ 	528.2	 & 	55.97	 $\pm$ 	25.74	 & 	54.92	 $\pm$ 	30.91	 & 	0.0115	 $\pm$ 	0.003\tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	84.08	 $\pm$ 	0.17	 & 	890.49	 $\pm$ 	343.61	 & 	1470.33	 $\pm$ 	993.74	 & 	61.76	 $\pm$ 	0.32	 & 	65.14	 $\pm$ 	0.5	 & 	0.0119	 $\pm$ 	0.02 \tabularnewline
-\hline
+ELM & 	83.57	 $\pm$ 	0.19	 & 	913.77	 $\pm$ 	388.46	 & 	1542.56	 $\pm$ 	1133.02	 & 	63.24	 $\pm$ 	33.92	 & 	68.57	 $\pm$ 	60.88	 & 	0.0147	 $\pm$ 	0.003\tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	83.44	 $\pm$ 	0.17	 & 	884.83	 $\pm$ 	297.95	 & 	1430.42	 $\pm$ 	874.32	 & 	64.61	 $\pm$ 	0.37	 & 	69.69	 $\pm$ 	0.68	 & 	0.002	 $\pm$ 	0.01\tabularnewline
-\hline
+ELM & 	84.1	 $\pm$ 	0.15	 & 	857.92	 $\pm$ 	281.43	 & 	1358.86	 $\pm$ 	741.72	 & 	62.53	 $\pm$ 	33.22	 & 	65.09	 $\pm$ 	50.44	 & 	0.0126	 $\pm$ 	0.003\tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	60.52	 $\pm$ 	0.39	 & 	24.28	 $\pm$ 	13.57	 & 	38.83	 $\pm$ 	26.43	 & 	118.09	 $\pm$ 	1.35	 & 	131.51	 $\pm$ 	1.37	 & 	0.0036	 $\pm$ 	0.01 \tabularnewline
-\hline
+ELM & 	62.15	 $\pm$ 	0.39	 & 	22.89	 $\pm$ 	12.22	 & 	38.69	 $\pm$ 	25.55	 & 	94.78	 $\pm$ 	59.81	 & 	113.23	 $\pm$ 	73.08	 & 	0.008	 $\pm$ 	0.003
+\tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	77.62	 $\pm$ 	0.3	 & 	16.53	 $\pm$ 	9.12	 & 	27.18	 $\pm$ 	18.2	 & 	72.75	 $\pm$ 	0.64	 & 	86.09	 $\pm$ 	0.86	 & 	0.0012	 $\pm$ 	0.01\tabularnewline
-
-\hline
+ELM & 	75.5	 $\pm$ 	0.3	 & 	17.17	 $\pm$ 	14.77	 & 	29.6	 $\pm$ 	31.56	 & 	81.78	 $\pm$ 	109.48	 & 	105.73	 $\pm$ 	166.11	 & 	0	 $\pm$ 	0\tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline 
-ELM & 	70.58	 $\pm$ 	0.34	 & 	19.52	 $\pm$ 	9.91	 & 	30.49	 $\pm$ 	18.09	 & 	145.28	 $\pm$ 	2.94	 & 	167.8	 $\pm$ 	3.39	 & 	0.0027	 $\pm$ 	0.01 \tabularnewline
-\hline
+ELM & 	72.19	 $\pm$ 	0.33	 & 	19.41	 $\pm$ 	7.98	 & 	29.12	 $\pm$ 	14.42	 & 	97.45	 $\pm$ 	149.84	 & 	105.64	 $\pm$ 	168.71	 & 	0.0006	 $\pm$ 	0 \tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	73.42	 $\pm$ 	0.31	 & 	20.08	 $\pm$ 	9.8	 & 	31.45	 $\pm$ 	18.84	 & 	85.55	 $\pm$ 	0.6	 & 	93.42	 $\pm$ 	0.64	 & 	0.0036	 $\pm$ 	0.01\tabularnewline
-\hline
+ELM & 	73.42	 $\pm$ 	0.31	 & 	20.08	 $\pm$ 	9.8	 & 	31.45	 $\pm$ 	18.84	 & 	85.55	 $\pm$ 	60.0	 & 	93.42	 $\pm$ 	64.0	 & 	0.0036	 $\pm$ 	0.001\tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	65.13	 $\pm$ 	0.21	 & 	336.33	 $\pm$ 	1414.85	 & 	1279.83	 $\pm$ 	7128.87	 & 	189.38	 $\pm$ 	7.49	 & 	501.38	 $\pm$ 	26.56	 & 	0.0042	 $\pm$ 	0.01
- \tabularnewline
+ELM & 	62.51	 $\pm$ 	0.2	 & 	138.32	 $\pm$ 	60.39	 & 	254.59	 $\pm$ 	264.65	 & 	80.72	 $\pm$ 	33.46	 & 	99.64	 $\pm$ 	76.55	 & 	0.0115	 $\pm$ 	0.003 \tabularnewline
 \hline
@@
 \hline
-ELM & 	78.42	 $\pm$ 	0.15	 & 	109.24	 $\pm$ 	52.6	 & 	203.11	 $\pm$ 	215.35	 & 	62.28	 $\pm$ 	0.24	 & 	78.75	 $\pm$ 	0.68	 & 	0.0019	 $\pm$ 	0.01 \tabularnewline
-\hline
+ELM & 	78.9	 $\pm$ 	0.14	 & 	106.9	 $\pm$ 	37.57	 & 	196.6	 $\pm$ 	140.45	 & 	62.19	 $\pm$ 	23.31	 & 	79.09	 $\pm$ 	66.94	 & 	0.0092	 $\pm$ 	0.002 \tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	83.47	 $\pm$ 	0.1	 & 	89.65	 $\pm$ 	25.9	 & 	167.99	 $\pm$ 	82.63	 & 	51.51	 $\pm$ 	0.14	 & 	65.11	 $\pm$ 	0.28	 & 	0.0041	 $\pm$ 	0.01\tabularnewline
+ELM & 	83.37	 $\pm$ 	0.12	 & 	88.63	 $\pm$ 	27.52	 & 	160.87	 $\pm$ 	80.76	 & 	51.14	 $\pm$ 	15.13	 & 	64.64	 $\pm$ 	31.55	 & 	0.0136	 $\pm$ 	0.003 \tabularnewline
 \hline
@@
 \hline
-ELM & 	85.22	 $\pm$ 	0.11	 & 	85.57	 $\pm$ 	25.92	 & 	141.17	 $\pm$ 	62.02	 & 	49.48	 $\pm$ 	0.16	 & 	56.58	 $\pm$ 	0.25	 & 	0.0014	 $\pm$ 	0.01\tabularnewline
-\hline
+ELM & 	84.45	 $\pm$ 	0.15	 & 	83.31	 $\pm$ 	27.61	 & 	157.12	 $\pm$ 	90.42	 & 	47.49	 $\pm$ 	17.08	 & 	61.99	 $\pm$ 	39.19	 & 	0.017	 $\pm$ 	0.004 \tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	61.55	 $\pm$ 	0.24	 & 	1350.19	 $\pm$ 	3934.54	 & 	3681.73	 $\pm$ 	19380.44	 & 	140.16	 $\pm$ 	3.02	 & 	264.72	 $\pm$ 	10.87	 & 	0.009	 $\pm$ 	0.02
- \tabularnewline
-\hline
+ELM & 	59.71	 $\pm$ 	0.2	 & 	828.76	 $\pm$ 	237.23	 & 	1185.19	 $\pm$ 	502.91	 & 	88.99	 $\pm$ 	27.24	 & 	95.3	 $\pm$ 	35.96	 & 	0.0145	 $\pm$ 	0.003  \tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	65.66	 $\pm$ 	0.25	 & 	859.21	 $\pm$ 	836.34	 & 	1691.61	 $\pm$ 	3053.2	 & 	92.4	 $\pm$ 	0.81	 & 	134.53	 $\pm$ 	2.18	 & 	0.0009	 $\pm$ 	0.01 \tabularnewline
-\hline
+
+ELM & 	61.83	 $\pm$ 	0.23	 & 	873.34	 $\pm$ 	287.46	 & 	1308.26	 $\pm$ 	953.71	 & 	93.91	 $\pm$ 	35.3	 & 	108.29	 $\pm$ 	99.33	 & 	0.0039	 $\pm$ 	0.002 \tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	79.73	 $\pm$ 	0.14	 & 	569.2	 $\pm$ 	161.37	 & 	841.75	 $\pm$ 	322.13	 & 	61.87	 $\pm$ 	0.21	 & 	69.99	 $\pm$ 	0.3	 & 	0.007	 $\pm$ 	0.02 \tabularnewline
-\hline
+ELM & 	79.88	 $\pm$ 	0.13	 & 	586	 $\pm$ 	159.51	 & 	820.07	 $\pm$ 	306.71	 & 	63.01	 $\pm$ 	18.84	 & 	67.37	 $\pm$ 	28.33	 & 	0.0131	 $\pm$ 	0.003
+ \tabularnewline
+\hline
+
 \end{tabular}
@@
 \hline
-ELM & 	79.52	 $\pm$ 	0.12	 & 	606.38	 $\pm$ 	153.83	 & 	818.18	 $\pm$ 	243.54	 & 	65.7	 $\pm$ 	0.18	 & 	67.17	 $\pm$ 	0.21	 & 	0.0044	 $\pm$ 	0.01 \tabularnewline
+ELM & 	79.71	 $\pm$ 	0.14	 & 	599.43	 $\pm$ 	163.33	 & 	837.47	 $\pm$ 	288	 & 	66.62	 $\pm$ 	26.69	 & 	71.11	 $\pm$ 	34.37	 & 	0.0106	 $\pm$ 	0.002 \tabularnewline
 \hline

### 2016-09-12 paper.tex
I forgot to remove and rename this. :D

@@
 
-The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes, and shows a set of definitions of the regression methods applied in the paper as well as the evaluation metrics considered.
+The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes.
 Then, Section \ref{sec:problem} introduces the problem of the estimation of print run
@@
 %********************************************************************************
-\section{Background and State of the art on sales forecasting} 
+\section{State of the art on sales forecasting} 
 \label{sec:soa}
